### 2020-06-06 dominance_regions.tex
Initial version: basics of g-vector mutations and the boundaries for rank 2

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[margin=1in]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{theorem}{section}

\newcommand{\bfc}{\mathbf{c}}
\newcommand{\bfg}{\mathbf{g}}

\newcommand{\cC}{\mathcal{C}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

\newcommand{\fp}{\mathfrak{p}}

\newcommand{\CC}{\mathbb{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\TT}{\mathbb{T}}
\newcommand{\ZZ}{\mathbb{Z}}

\newcommand{\ol}[1]{{\overline{#1}}}

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}

\title{Dominance Regions for Imaginary $\bfg$-vectors}

\author{Dylan Rupel}
\author{Salvatore Stella}

\begin{document}
  \begin{abstract}
    We investigate the shapes of the polytopes defining the dominance order for imaginary $\bfg$-vectors in rank two.
    We conjecture how our observations might generalize to higher dimensions.
  \end{abstract}
  \maketitle

  \section{Introduction}
  The investigations of this paper are inspired by the dominance order for the tropical labellings for bases of cluster algebras.
  This dominance order is used by Qin to understand how these bases may be deformed in the case when there is a green-to-red sequence of mutations.

  \section{Lattice Mutations}
  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable matrix, i.e. there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric.
  For $b\in\ZZ$, write $[b]_+=max(b,0)$.
  Given a sign $\varepsilon\in\{\pm\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
  \[ e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise.} \end{cases} \]
  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_kB=(b'_{ij})$ given by
  \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
  To record sequences of these matrix mutations, we introduce the labelled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B_t$ for $t\in\TT_n$ satisfying:
  \begin{itemize}
    \item $B_{t_0}=B$;
    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $B_{t'}=\mu_k B_t$.
  \end{itemize}

  Define $\phi_k:\ZZ^n\to\ZZ^n$ as the piecewise-linear map $\phi_k(\lambda)=\begin{cases} E_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E_{k,-}\lambda & \text{if $\lambda_k<0$.} \end{cases}$.
  Define the piecewise-linear automorphisms $\phi_t:\ZZ^n\to\ZZ^n$ by
  \begin{itemize}
    \item $\phi_{t_0}=\Id$;
    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $\phi_{t'}=\phi_k \phi_t$.
  \end{itemize}
  For $\lambda\in\ZZ^n$, define the $B$-cone $\cC(\lambda)=\lambda+B\RR_{\ge0}^n$ pointed at $\lambda$.
  \begin{definition}
    For $\lambda\in\ZZ^n$, define the \emph{dominance polytope} 
    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC(\phi_t \lambda). \]
  \end{definition}
  Our goal is to understand the dominance polytopes for all $\lambda$.

  \section{Rank Two}
  Fix integers $b,c>0$ and assume $bc\ge4$.
  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.

  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2r}$ joined to $t_{2r+1}$ by an edge labelled $1$ and $t_{2r-1}$ joined to $t_{2r}$ by an edge labelled $2$.
  \begin{lemma}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    It is enough to consider $\phi_{t_{-2}}^{-1}\cC(\phi_{t_{-2}}\lambda) \cap \cC(\lambda) \cap \phi_{t_2}^{-1}\cC(\phi_{t_2}\lambda)$, we leave the details to the reader.
  \end{proof}

  \begin{theorem}
    For $\lambda\in\cI\cap\ZZ^2$, there are five classes of dominance polytopes.
    \begin{enumerate}
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
      \item if $\lambda$ lies on the ray spanned by $(2,-c)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cC(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
      \item if $\lambda$ lies on the ray spanned by $(b,-2)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(0,c\lambda_1+2\lambda_2)$.
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(0,c\lambda_1+2\lambda_2)$, and ???.
    \end{enumerate}
  \end{theorem}
  \begin{proof}
    Tedious calculation once we have proven what the slopes of the boundaries are.
  \end{proof}

\end{document}

### 2020-06-06 dominance_regions.tex
Better description of the points for triangular regions and corrected (I hope) points for the trapezoids

@@
     \begin{enumerate}
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
-      \item if $\lambda$ lies on the ray spanned by $(2,-c)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
+      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
+      \item if $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
       \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cC(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
-      \item if $\lambda$ lies on the ray spanned by $(b,-2)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(0,c\lambda_1+2\lambda_2)$.
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(0,c\lambda_1+2\lambda_2)$, and ???.
+      \item if $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
+      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and ???.
     \end{enumerate}

### 2020-06-07 dominance_regions.tex
One direction mutations in rank two

@@
   Write $\cI \subset \RR^2$ for the \emph{imaginary cone} spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
+  \begin{lemma}
+    The vectors $(2b, -bc+\sqrt{bc(bc-4)})$ (resp. $(2b, -bc-\sqrt{bc(bc-4)})$) and $(2c, bc+\sqrt{bc(bc-4)})$ (resp. $(2c, bc-\sqrt{bc(bc-4)})$) are perpendicular.
+  \end{lemma}
 
@@
 
+  \begin{lemma}
+    \label{le:one direction}
+    For $\lambda\in\cI\cap\ZZ^2$, 
+    \begin{enumerate}
+      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
+      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
+    \end{enumerate}
+  \end{lemma}
+
   \begin{theorem}
@@
     \begin{enumerate}
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
+      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
       \item if $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
@@
       \item if $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and ???.
+      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and ???.
     \end{enumerate}
@@
   \begin{proof}
-    Tedious calculation once we have proven what the slopes of the boundaries are.
+    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
+    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
+    or 
+    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
+    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
+    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
   \end{proof}
 
+  \begin{remark}
+    Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
+    This unexpected coincidence is our reason for writing these results.
+  \end{remark}
+
 \end{document}

### 2020-06-08 dominance_regions.tex
Lemma 3.3 proof started
Fixed statement
Stability of imaginary rays

@@
   Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
+  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2r}$ joined to $t_{2r+1}$ by an edge labelled $1$ and $t_{2r-1}$ joined to $t_{2r}$ by an edge labelled $2$.
+
+  Observe that $\phi_{t_2}=\phi_{t_{-2}}^{-1}$ is the piecewise-linear map given by
+  \begin{equation}
+    \label{eq:forward two step mutation}
+    \phi_{t_2}(\lambda)=\begin{cases} ((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\ (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\ (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}\end{cases}
+  \end{equation}
+  and $\phi_{t_2}^{-1}=\phi_{t_{-2}}$ is the piecewise-linear map given by
+  \begin{equation}
+    \label{eq:backward two step mutation}
+    \phi_{t_2}^{-1}(\lambda)=\begin{cases} (-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\ (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\ (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$;}\end{cases}
+  \end{equation}
+
+  By an eigenvector of a piecewise-linear map $\phi$ we mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\alpha_k$ so that $\phi^k(\lambda)=\alpha_k\lambda$.
+  \begin{lemma}
+    Any eigenvector of $\phi_{t_2}$ is a multiple of one of the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
+  \end{lemma}
+  \begin{proof}
+    First observe that the equation $\phi_{t_2}^k(\lambda)=\alpha_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
+    In this region, $\phi_{t_2}$ is linear with eigenvalue $\alpha$ satisfying $\alpha^2-(bc-2)+1=0$, i.e. $\alpha=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
+    We thus require that 
+    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
+    or
+    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
+    As these represent the same relation, the result follows.
+  \end{proof}
+
   Write $\cI \subset \RR^2$ for the \emph{imaginary cone} spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
@@
 
-  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2r}$ joined to $t_{2r+1}$ by an edge labelled $1$ and $t_{2r-1}$ joined to $t_{2r}$ by an edge labelled $2$.
   \begin{lemma}
@@
   \end{lemma}
+  \begin{proof}
+    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
+    We first show that $\cC(\lambda) \cap \phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)\supsetneq \cC(\lambda) \cap \phi_{t_j}^{-1}\cC(\phi_{t_j}\lambda)$ for $0\le i<j$.
+  \end{proof}
 

### 2020-06-08 dominance_regions.tex
Fixed a typo

@@
 
-  By an eigenvector of a piecewise-linear map $\phi$ we mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\alpha_k$ so that $\phi^k(\lambda)=\alpha_k\lambda$.
+  By an eigenvector of a piecewise-linear map $\phi$, we mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\alpha_k$ so that $\phi^k(\lambda)=\alpha_k\lambda$.
   \begin{lemma}
-    Any eigenvector of $\phi_{t_2}$ is a multiple of one of the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
+    Any nonzero eigenvector of $\phi_{t_2}$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
   \end{lemma}
@@
     First observe that the equation $\phi_{t_2}^k(\lambda)=\alpha_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
-    In this region, $\phi_{t_2}$ is linear with eigenvalue $\alpha$ satisfying $\alpha^2-(bc-2)+1=0$, i.e. $\alpha=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
+    In this region, $\phi_{t_2}$ is linear with eigenvalue $\alpha$ satisfying $\alpha^2-(bc-2)\alpha+1=0$, i.e. $\alpha=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
     We thus require that 

### 2020-06-08 dominance_regions.tex
Chebushev polynomials

@@
   \end{itemize}
-  For $\lambda\in\ZZ^n$, define the $B$-cone $\cC(\lambda)=\lambda+B\RR_{\ge0}^n$ pointed at $\lambda$.
+  For $\lambda\in\ZZ^n$, define the \emph{$B$-cone} $\cC(\lambda):=\lambda+B\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
   \begin{definition}
@@
   \end{definition}
-  Our goal is to understand the dominance polytopes for all $\lambda$.
+  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
 
@@
   Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2r}$ joined to $t_{2r+1}$ by an edge labelled $1$ and $t_{2r-1}$ joined to $t_{2r}$ by an edge labelled $2$.
+  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
 
@@
 
-  By an eigenvector of a piecewise-linear map $\phi$, we mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\alpha_k$ so that $\phi^k(\lambda)=\alpha_k\lambda$.
+  By an eigenvector of a piecewise-linear map $\phi$, we mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
   \begin{lemma}
@@
   \begin{proof}
-    First observe that the equation $\phi_{t_2}^k(\lambda)=\alpha_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
-    In this region, $\phi_{t_2}$ is linear with eigenvalue $\alpha$ satisfying $\alpha^2-(bc-2)\alpha+1=0$, i.e. $\alpha=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
+    First observe that the equation $\phi_{t_2}^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
+    In this region, $\phi_{t_2}$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
     We thus require that 
@@
   \end{lemma}
+
+  Define Chebyshev polynomials $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
 
@@
     Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
-    This unexpected coincidence is our reason for writing these results.
+    This unexpected coincidence is one of our reasons for deciding to write down these results.
   \end{remark}

### 2020-06-08 dominance_regions.tex
Limit statement
Inequalities

@@
   \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
+  \begin{lemma}
+    For $i\ge1$ and any $\varepsilon$, we have $u_{i,\varepsilon}>0$ and $u_{i-1,\varepsilon}u_{i+1,-\varepsilon}<u_{i,\varepsilon}u_{i,-\varepsilon}$.
+    Moreover,
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}\]
+  \end{lemma}
+  \begin{proof}
+    We prove the inequalities by induction, the base case $i=1$ being clear from the definitions.
+    Without loss of generality, assume $\varepsilon=+$.
+    For $i>1$, we have 
+    \[u_{i-1,\varepsilon}u_{i+1,-\varepsilon}=cu_{i-1,\varepsilon}u_{i,\varepsilon}-u_{i-1,\varepsilon}u_{i-1,-\varepsilon}<cu_{i-1,\varepsilon}u_{i,\varepsilon}-u_{i-2,-\varepsilon}u_{i,\varepsilon}=u_{i,-\varepsilon}u_{i,\varepsilon},\]
+    where the inequality follows by induction.
+
+    Thus we see that the sequence $\frac{-u_{i,-}}{u_{i-1,+}}$ is increasing and the sequence $\frac{-u_{i-1,-}}{u_{i,+}}$ is decreasing.
+    As the first is bounded above by $\frac{-1}{b}$ and the second is bounded below by $-c$, they both converge.
+  \end{proof}
 

### 2020-06-09 dominance_regions.tex
Limit proof

--- 2020-06-08 dominance_regions.tex
@@
   \section{Rank Two}
-  Fix integers $b,c>0$ and assume $bc\ge4$.
+  Fix integers $b,c>0$ and assume $bc\ge 4$.
   Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
@@
 
-  Define Chebyshev polynomials $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  Define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
   \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
+  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
+  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
+  By the equalities 
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
+  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+
+  \begin{lemma}
+    We have
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+  \end{lemma}
+  \begin{proof}
+    For any $i\ge 1$, we have
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
+    It follows that
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    which is equivalent to the desired expression.
+    Similarly, 
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
+    so that
+    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    which is again equivalent to the desired expression.
+  \end{proof}
 

### 2020-06-10 dominance_regions.tex
Stability of imaginary cones under mutations

@@
   \end{itemize}
-  For $\lambda\in\ZZ^n$, define the \emph{$B$-cone} $\cC(\lambda):=\lambda+B\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
+  For $\lambda\in\ZZ^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
   \begin{definition}
     For $\lambda\in\ZZ^n$, define the \emph{dominance polytope} 
-    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC(\phi_t \lambda). \]
+    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
   \end{definition}
@@
   Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
-  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2r}$ joined to $t_{2r+1}$ by an edge labelled $1$ and $t_{2r-1}$ joined to $t_{2r}$ by an edge labelled $2$.
+  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labelled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labelled $2$.
   We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
@@
   Write $\cI \subset \RR^2$ for the \emph{imaginary cone} spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
+  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} spanned by the vectors $(-bc\pm\sqrt{bc(bc-4)},2c)$.
   \begin{lemma}
@@
   \end{lemma}
+  \begin{proof}
+    This is immediate from the equality $(-bc+\sqrt{bc(bc-4)})(bc+\sqrt{bc(bc-4)})=-4bc$.
+  \end{proof}
+  \begin{lemma}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
+  \end{lemma}
+  \begin{proof}
+    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$ respectively.
+    The claim is immediate for $\phi_{t_2}$ since the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$ are eigenvectors.
+    Now, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\big( (2b,-bc\pm\sqrt{bc(bc-4)}) \big)=(-2b,bc\pm\sqrt{bc(bc-4)})$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows.
+  \end{proof}
 

### 2020-06-11 dominance_regions.tex
Half(?) proof of Lemma 3.4

@@
 
+  The Chebyshev polynomials, in particular, allow us to explicitly compute $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
+  \begin{lemma}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have
+    \begin{align*}
+      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,+}\lambda_2);\\
+      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,-}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2).
+    \end{align*}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $j$, the case $j=0$ being clear from the definitions.
+    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$.
+    For $j\ge 0$, using that $(bc-1)u_{2j+1,-}-bu_{2j,-}=u_{2j+3,-}$ and we have
+    \[\phi_{t_{2j+2}(\lambda)}=\phi_{t_2}\phi_{t_{2j}}(\lambda)=(u_{2j+3,-}\lambda_1
+  \end{proof}
+
   \begin{lemma}

### 2020-06-11 dominance_regions.tex
this might be better
Longer Chebyshev recursions

@@
   \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
+  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
+
+  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
+  This leads to the following more general recursive structure.
+  \begin{lemma}
+    For $i,k\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
+    \[u_{i+k,\varepsilon}=\begin{cases} u_{k+1,\varepsilon}u_{i,-\varepsilon}-u_{k,-\varepsilon}u_{i-1,\varepsilon} & \text{if $k$ is odd;}\\ u_{k+1,-\varepsilon}u_{i,\varepsilon}-u_{k,\varepsilon}u_{i-1,-\varepsilon} & \text{if $k$ is even.} \end{cases}\]
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $k$, the cases $k=0,1$ being tautological and reproducing the defining recursion respectively.
+    Using the claim for $k$ and then the defining recursion twice, we get
+    \begin{align*}
+      u_{i+k+1,\varepsilon}&=\begin{cases} u_{k+1,\varepsilon}u_{i+1,-\varepsilon}-u_{k,-\varepsilon}u_{i,\varepsilon} & \text{if $k$ is odd;}\\ u_{k+1,-\varepsilon}u_{i+1,\varepsilon}-u_{k,\varepsilon}u_{i,-\varepsilon} & \text{if $k$ is even;} \end{cases}\\
+      &=\begin{cases} (u_{2,-\varepsilon}u_{k+1,\varepsilon}-u_{k,-\varepsilon})u_{i,\varepsilon}-u_{k+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $k$ is odd;}\\ (u_{2,\varepsilon}u_{k+1,-\varepsilon}-u_{k,\varepsilon})u_{i,-\varepsilon}-u_{k+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $k$ is even;} \end{cases}\\
+      &=\begin{cases} u_{k+2,-\varepsilon}u_{i,\varepsilon}-u_{k+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $k+1$ is even;}\\ u_{k+2,\varepsilon}u_{i,-\varepsilon}-u_{k+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $k+1$ is odd;} \end{cases}
+    \end{align*}
+    which is the claimed recursion for $k+1$.
+  \end{proof}
+
   The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
@@
   \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+  Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
+  Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
 
@@
     As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$.
-    For $j\ge 0$, using that $(bc-1)u_{2j+1,-}-bu_{2j,-}=u_{2j+3,-}$ and we have
-    \[\phi_{t_{2j+2}(\lambda)}=\phi_{t_2}\phi_{t_{2j}}(\lambda)=(u_{2j+3,-}\lambda_1
+    For $j\ge 0$, using that $(bc-1)u_{2j+1,-}-bu_{2j,-}=u_{2j+3,-}$ and $(bc-1)u_{2j,+}-bu_{2j-1,+}=u_{2j+2,+}$, we have
+    \[\phi_{t_{2j+2}(\lambda)}=\phi_{t_2}\phi_{t_{2j}}(\lambda)=(u_{2j+3,-}\lambda_1+u_{2j+2,+}\lambda_2,-u_{2j+2,-}\lambda_1-u_{2j+1,+}\lambda_2).\]
   \end{proof}

### 2020-06-11 dominance_regions.tex
Proof of Lemma 3.5

@@
   Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labelled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labelled $2$.
-  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
+  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
 
@@
 
-  Define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  It will be useful to have explicit expressions for $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
+  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
   \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
@@
     For $i,k\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
-    \[u_{i+k,\varepsilon}=\begin{cases} u_{k+1,\varepsilon}u_{i,-\varepsilon}-u_{k,-\varepsilon}u_{i-1,\varepsilon} & \text{if $k$ is odd;}\\ u_{k+1,-\varepsilon}u_{i,\varepsilon}-u_{k,\varepsilon}u_{i-1,-\varepsilon} & \text{if $k$ is even.} \end{cases}\]
+    \begin{equation}
+      \label{eq:long Chebyshev recursion}
+      u_{i+k,\varepsilon}=\begin{cases} u_{k+1,\varepsilon}u_{i,-\varepsilon}-u_{k,-\varepsilon}u_{i-1,\varepsilon} & \text{if $k$ is odd;}\\ u_{k+1,-\varepsilon}u_{i,\varepsilon}-u_{k,\varepsilon}u_{i-1,-\varepsilon} & \text{if $k$ is even.} \end{cases}
+    \end{equation}
   \end{lemma}
@@
     We work by induction on $k$, the cases $k=0,1$ being tautological and reproducing the defining recursion respectively.
-    Using the claim for $k$ and then the defining recursion twice, we get
+    Using the claim for $k>0$ and then the defining recursion twice, we get
     \begin{align*}
@@
     which is the claimed recursion for $k+1$.
+    These calculations can be reverses to show the result for $k<0$.
+  \end{proof}
+
+  \begin{lemma}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have
+    \begin{align*}
+      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
+      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
+    \end{align*}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $j$, the case $j=0$ being clear from the definitions.
+    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$.
+    For $\lambda\in\cI$, the action of $\phi_{t_2}$ from \eqref{eq:forward two step mutation} can be rewritten as
+    \[\phi_{t_2}(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
+    and so
+    \begin{align*}
+      \phi_{t_{2j+2}(\lambda)}&=\phi_{t_2}\phi_{t_{2j}}(\lambda)\\
+      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
+      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
+      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2)
+    \end{align*}
+    where the last equality uses \eqref{eq:long Chebyshev recursion}.
+
+    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the given formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
   \end{proof}
@@
   Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
-
-  The Chebyshev polynomials, in particular, allow us to explicitly compute $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
-  \begin{lemma}
-    For $j\in\ZZ$ and $\lambda\in\cI$, we have
-    \begin{align*}
-      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,+}\lambda_2);\\
-      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,-}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2).
-    \end{align*}
-  \end{lemma}
-  \begin{proof}
-    We work by induction on $j$, the case $j=0$ being clear from the definitions.
-    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$.
-    For $j\ge 0$, using that $(bc-1)u_{2j+1,-}-bu_{2j,-}=u_{2j+3,-}$ and $(bc-1)u_{2j,+}-bu_{2j-1,+}=u_{2j+2,+}$, we have
-    \[\phi_{t_{2j+2}(\lambda)}=\phi_{t_2}\phi_{t_{2j}}(\lambda)=(u_{2j+3,-}\lambda_1+u_{2j+2,+}\lambda_2,-u_{2j+2,-}\lambda_1-u_{2j+1,+}\lambda_2).\]
-  \end{proof}
 

### 2020-06-14 dominance_regions.tex
Lemma 3.6 may only be correct when i is even

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{tikz}
 
@@
 
-  Observe that $\phi_{t_2}=\phi_{t_{-2}}^{-1}$ is the piecewise-linear map given by
+  Observe that $\phi_{t_1}$ is the piecewise-linear map given by
+  \[\phi_{t_1}(\lambda)=\begin{cases} (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1\ge0$;}\\ (-\lambda_1,\lambda_2) & \text{if $\lambda_1<0$;} \end{cases}\]
+  and $\phi_{t_2}=\phi_{t_{-2}}^{-1}$ is the piecewise-linear map given by
   \begin{equation}
@@
   \end{equation}
-  and $\phi_{t_2}^{-1}=\phi_{t_{-2}}$ is the piecewise-linear map given by
+  while $\phi_{t_2}^{-1}=\phi_{t_{-2}}$ is the piecewise-linear map given by
   \begin{equation}
@@
   \begin{lemma}
+    \label{le:imaginary transformations}
     For $j\in\ZZ$ and $\lambda\in\cI$, we have
@@
 
-    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the given formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
+    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
+  \end{proof}
+
+  \begin{lemma}
+    For $i\ge2$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+    \begin{align*}
+      u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
+      u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+    \end{align*}
+
+    given as in the figure below:
+    \[
+      \begin{tikzpicture}
+        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
+        \draw[-] (-8,0) -- (5,0);
+        \draw[-] (0,-5) -- (0,5);
+        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
+        \draw[-] (0,0) -- (5,-2.113);
+        \draw[-] (0,0) -- (3.17,-5);
+        \node at (1,-0.9) {$\cI$};
+        \draw[fill=black] (3.5,-3) circle (2pt);
+        \node[below right] at (3.5,-3) {$\lambda$};
+        \draw[->,thick] (3.5,-3) -- (47/10,-5);
+        \draw[-,thick] (3.5,-3) -- (0,26/10);
+        \draw[-,thick] (0,26/10) -- (-26/4,0);
+        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
+      \end{tikzpicture}
+    \]
+  \end{lemma}
+  \begin{proof}
+    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
+
+    For $i=2j$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
+
+    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2. \]
   \end{proof}
@@
   \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+  \begin{remark}
     Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
     Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
+  \end{remark}
 

### 2020-06-15 dominance_regions.tex
Transforming inequalities
Correct(?) transformation of inequalities
The proof of Lemma 3.7 stopped making sense so I am quitting, we need to check the inequalities in the statement

@@
   \begin{lemma}
+    \label{le:transformed inequalities}
+    Let $A=(a_{ij})$ be an invertible $2\times 2$ matrix.
+    Under the action of $A$, the region inside $\RR^2$ defined by the inequality $rx+sy\le t$ is transformed to the region defined by the inequality \[\frac{ra_{22}-sa_{21}}{a_{11}a_{22}-a_{12}a_{21}}x + \frac{-ra_{12}+sa_{11}}{a_{11}a_{22}-a_{12}a_{21}}y\le t.\]
+  \end{lemma}
+  \begin{proof}
+    Assume $r,s,t\ne0$, the cases when one of these vanishes follows by the continuity of the transformation.
+    Observe that the points $\big(\frac{t}{r},0\big)$ and $\big(0,\frac{t}{s}\big)$ lie on the boundary line of the region defined by the inequality $rx+sy\le t$.
+    These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
+    By the linearity of this transformation of $\RR^2$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
+  \end{proof}
+
+  \begin{lemma}
     For $i\ge2$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
-    \begin{align*}
-      u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
-      u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
-    \end{align*}
+    \begin{align}
+      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
+      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+    \end{align}
 
@@
         \draw[->,thick] (-26/4,0) -- (-16/4,-5);
+        \node at (4.5,-4) {\eqref{ineq:1}};
+        \node at (2.5,-0.5) {\eqref{ineq:2}};
+        \node at (-3,1.75) {\eqref{ineq:3}};
+        \node at (-5.5,-3) {\eqref{ineq:4}};
       \end{tikzpicture}
@@
 
-    For $i=2j$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
+    For $i=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
+    We inductively compute the region $\phi_{t_{2j}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{t_{2j}}^{-1}=\phi_{t_2}^{-j}$.
+
+    \subsubsection*{Claim:} For $k>0$, $\phi_{t_{2k}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ is the region determined by the inequalities 
+    \begin{align*}
+      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
+      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+    \end{align*}
+
+    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $-cx-y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$.
 

### 2020-06-16 dominance_regions.tex
More of the proof of Lemma 3.7

@@
   \begin{lemma}
-    For $i,k\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
+    For $i,j\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
     \begin{equation}
       \label{eq:long Chebyshev recursion}
-      u_{i+k,\varepsilon}=\begin{cases} u_{k+1,\varepsilon}u_{i,-\varepsilon}-u_{k,-\varepsilon}u_{i-1,\varepsilon} & \text{if $k$ is odd;}\\ u_{k+1,-\varepsilon}u_{i,\varepsilon}-u_{k,\varepsilon}u_{i-1,-\varepsilon} & \text{if $k$ is even.} \end{cases}
+      u_{i+j,\varepsilon}=\begin{cases} u_{j+1,\varepsilon}u_{i,-\varepsilon}-u_{j,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j$ is odd;}\\ u_{j+1,-\varepsilon}u_{i,\varepsilon}-u_{j,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j$ is even.} \end{cases}
     \end{equation}
@@
   \begin{proof}
-    We work by induction on $k$, the cases $k=0,1$ being tautological and reproducing the defining recursion respectively.
-    Using the claim for $k>0$ and then the defining recursion twice, we get
+    We work by induction on $j$, the cases $j=0,1$ being tautological and reproducing the defining recursion respectively.
+    Using the claim for $j>0$ and then the defining recursion twice, we get
     \begin{align*}
-      u_{i+k+1,\varepsilon}&=\begin{cases} u_{k+1,\varepsilon}u_{i+1,-\varepsilon}-u_{k,-\varepsilon}u_{i,\varepsilon} & \text{if $k$ is odd;}\\ u_{k+1,-\varepsilon}u_{i+1,\varepsilon}-u_{k,\varepsilon}u_{i,-\varepsilon} & \text{if $k$ is even;} \end{cases}\\
-      &=\begin{cases} (u_{2,-\varepsilon}u_{k+1,\varepsilon}-u_{k,-\varepsilon})u_{i,\varepsilon}-u_{k+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $k$ is odd;}\\ (u_{2,\varepsilon}u_{k+1,-\varepsilon}-u_{k,\varepsilon})u_{i,-\varepsilon}-u_{k+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $k$ is even;} \end{cases}\\
-      &=\begin{cases} u_{k+2,-\varepsilon}u_{i,\varepsilon}-u_{k+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $k+1$ is even;}\\ u_{k+2,\varepsilon}u_{i,-\varepsilon}-u_{k+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $k+1$ is odd;} \end{cases}
+      u_{i+j+1,\varepsilon}&=\begin{cases} u_{j+1,\varepsilon}u_{i+1,-\varepsilon}-u_{j,-\varepsilon}u_{i,\varepsilon} & \text{if $j$ is odd;}\\ u_{j+1,-\varepsilon}u_{i+1,\varepsilon}-u_{j,\varepsilon}u_{i,-\varepsilon} & \text{if $j$ is even;} \end{cases}\\
+      &=\begin{cases} (u_{2,-\varepsilon}u_{j+1,\varepsilon}-u_{j,-\varepsilon})u_{i,\varepsilon}-u_{j+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j$ is odd;}\\ (u_{2,\varepsilon}u_{j+1,-\varepsilon}-u_{j,\varepsilon})u_{i,-\varepsilon}-u_{j+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j$ is even;} \end{cases}\\
+      &=\begin{cases} u_{j+2,-\varepsilon}u_{i,\varepsilon}-u_{j+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j+1$ is even;}\\ u_{j+2,\varepsilon}u_{i,-\varepsilon}-u_{j+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j+1$ is odd;} \end{cases}
     \end{align*}
-    which is the claimed recursion for $k+1$.
-    These calculations can be reverses to show the result for $k<0$.
+    which is the claimed recursion for $j+1$.
+    These calculations can be reverses to show the result for $j<0$.
   \end{proof}
@@
     We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $-cx-y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$ which corresponds to (a) with $k=1$.
+    Similarly, the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\dagger$) intersects three domains of linearity in which $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $k=1$.
+    This establishes the base of an induction on $k$.
+
+    Assuming the inequalities (a-d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
+    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$.
+    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
+    \[(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2,\]
+    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying this to (d) gives the inequality 
+    \[(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}.
+    Similarly, the boundary segment corresponding to (b) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
+    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
+    \[(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
 
     For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2. \]
+    \[ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2. \]
   \end{proof}

### 2020-06-19 dominance_regions.tex
Lemma 3.7 is proved, I was expecting to need a change for i odd but this does not seem to be the case, some cleanup is needed but it is late

@@
   Observe that $\phi_{t_1}$ is the piecewise-linear map given by
-  \[\phi_{t_1}(\lambda)=\begin{cases} (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1\ge0$;}\\ (-\lambda_1,\lambda_2) & \text{if $\lambda_1<0$;} \end{cases}\]
+  \begin{equation}
+    \label{eq:forward mutation 1}
+    \phi_{t_1}(\lambda)=\begin{cases} (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1\ge0$;}\\ (-\lambda_1,\lambda_2) & \text{if $\lambda_1<0$;} \end{cases}
+  \end{equation}
   and $\phi_{t_2}=\phi_{t_{-2}}^{-1}$ is the piecewise-linear map given by
@@
   \begin{lemma}
+    \label{le:imaginary stability}
     For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
@@
   \begin{lemma}
-    For $i\ge2$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+    For $i\ge1$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
     \begin{align}
@@
 
-    Assuming the inequalities (a-d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
-    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$.
+    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
+    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
     \[(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2,\]
-    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying this to (d) gives the inequality 
+    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
     \[(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
-    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}.
-    Similarly, the boundary segment corresponding to (b) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
+    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
+    \[(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    which is the inequality (b) for $k+1$
+    .
+    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
     Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
@@
     which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
+    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
+    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
+    \[(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
+    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
 
-    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2. \]
+    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
+    Using that $\phi_{t_{2j+1}}^{-1}=\phi_{t_2}^{-j}\phi_{t_1}^{-1}$, we compute the image inductively as above.
+    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_{t_1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_{t_1}^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
+    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_{t_1}^{-1}$ and thus produces the inequalities
+    \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]
+
+    \subsubsection*{Claim:} For $k\ge 0$, $\phi_{t_{2k+1}}^{-1}\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ is the region determined by the inequalities 
+    \begin{align*}
+      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
+      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+    \end{align*}
+    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_{t_2}^{-1}$ and this completes the proof.
   \end{proof}

### 2020-07-11 dominance_regions.tex
small cleanup in section 2

@@
   \section{Lattice Mutations}
-  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable matrix, i.e. there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric.
+  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e.
+there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
   For $b\in\ZZ$, write $[b]_+=max(b,0)$.
   Given a sign $\varepsilon\in\{\pm\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
-  \[ e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise.} \end{cases} \]
+  \begin{equation}
+    \label{eq:mutation matrix}
+    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise.} \end{cases}
+  \end{equation}
   The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_kB=(b'_{ij})$ given by
   \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
-  To record sequences of these matrix mutations, we introduce the labelled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B_t$ for $t\in\TT_n$ satisfying:
+  One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
+
+  To record sequences of these matrix mutations, we introduce the labelled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
   \begin{itemize}
-    \item $B_{t_0}=B$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $B_{t'}=\mu_k B_t$.
+    \item $B^{t_0}=B$;
+    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $B^{t'}=\mu_k B^t$.
   \end{itemize}
 
-  Define $\phi_k:\ZZ^n\to\ZZ^n$ as the piecewise-linear map $\phi_k(\lambda)=\begin{cases} E_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E_{k,-}\lambda & \text{if $\lambda_k<0$.} \end{cases}$.
-  Define the piecewise-linear automorphisms $\phi_t:\ZZ^n\to\ZZ^n$ by
+  For $t\in\TT_n$, define $\phi^t_k:\ZZ^n\to\ZZ^n$ as the piecewise-linear map
+  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
+  where the entries of $E^t_{k,\varepsilon}$ is given by \eqref{eq:mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
+  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labelled $k$.
+  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\ZZ^n\to\ZZ^n$ by
   \begin{itemize}
     \item $\phi_{t_0}=\Id$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $\phi_{t'}=\phi_k \phi_t$.
+    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
   \end{itemize}

### 2020-07-12 dominance_regions.tex
Random edits in section 3

@@
 \usepackage{tikz}
+\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
 
@@
   Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
-  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labelled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labelled $2$.
+  Here we may take $\TT_2$ to have vertices labelled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labelled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labelled $2$.
   We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
@@
     \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
-    As these represent the same relation, the result follows.
+    As these represent the same relation, the result immediately follows by inspection.
   \end{proof}
 
-  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
-  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} spanned by the vectors $(-bc\pm\sqrt{bc(bc-4)},2c)$.
+  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
+  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $(-bc\pm\sqrt{bc(bc-4)},2c)$.
   \begin{lemma}
@@
     The claim is immediate for $\phi_{t_2}$ since the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$ are eigenvectors.
-    Now, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\big( (2b,-bc\pm\sqrt{bc(bc-4)}) \big)=(-2b,bc\pm\sqrt{bc(bc-4)})$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows.
+    Now, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\big( (2b,-bc\pm\sqrt{bc(bc-4)}) \big)=(-2b,bc\pm\sqrt{bc(bc-4)})$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity.
   \end{proof}
@@
   \begin{lemma}
-    For $i,j\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
+    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
     \begin{equation}
       \label{eq:long Chebyshev recursion}
-      u_{i+j,\varepsilon}=\begin{cases} u_{j+1,\varepsilon}u_{i,-\varepsilon}-u_{j,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j$ is odd;}\\ u_{j+1,-\varepsilon}u_{i,\varepsilon}-u_{j,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j$ is even.} \end{cases}
+      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
     \end{equation}
@@
   \begin{proof}
-    We work by induction on $j$, the cases $j=0,1$ being tautological and reproducing the defining recursion respectively.
+    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion respectively.
     Using the claim for $j>0$ and then the defining recursion twice, we get
     \begin{align*}
-      u_{i+j+1,\varepsilon}&=\begin{cases} u_{j+1,\varepsilon}u_{i+1,-\varepsilon}-u_{j,-\varepsilon}u_{i,\varepsilon} & \text{if $j$ is odd;}\\ u_{j+1,-\varepsilon}u_{i+1,\varepsilon}-u_{j,\varepsilon}u_{i,-\varepsilon} & \text{if $j$ is even;} \end{cases}\\
-      &=\begin{cases} (u_{2,-\varepsilon}u_{j+1,\varepsilon}-u_{j,-\varepsilon})u_{i,\varepsilon}-u_{j+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j$ is odd;}\\ (u_{2,\varepsilon}u_{j+1,-\varepsilon}-u_{j,\varepsilon})u_{i,-\varepsilon}-u_{j+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j$ is even;} \end{cases}\\
-      &=\begin{cases} u_{j+2,-\varepsilon}u_{i,\varepsilon}-u_{j+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j+1$ is even;}\\ u_{j+2,\varepsilon}u_{i,-\varepsilon}-u_{j+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j+1$ is odd;} \end{cases}
+      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
     \end{align*}
-    which is the claimed recursion for $j+1$.
-    These calculations can be reverses to show the result for $j<0$.
+    which is the claimed recursion for $\ell+1$.
+    These calculations can be reversed to show the result for $\ell<0$.
   \end{proof}
@@
       &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
-      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2)
+      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
     \end{align*}
-    where the last equality uses \eqref{eq:long Chebyshev recursion}.
+    where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
 
-    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
+    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
   \end{proof}
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-    \[(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2,\]
+    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2,\]
     which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
     which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-    \[(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
     which is the inequality (b) for $k+1$
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-    \[(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
     which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
@@
     Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
     which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
@@
     which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
+    This completes the induction on $k$, proving the Claim and the result for $i$ even.
 

### 2020-07-12 dominance_regions.tex
Lemma 3.7 edits

@@
     \begin{align*}
-      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
-      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
+      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
     \end{align*}
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2,\]
+    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
     which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
     which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
-    which is the inequality (b) for $k+1$
-    .
+    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (b) for $k+1$.
     Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
     Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
     which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
@@
     Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
     which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
+    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
     which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
@@
     \begin{align*}
-      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
-      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
+      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
+      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
     \end{align*}

### 2020-08-15 dominance_regions.tex
Added rough inequalities
Correct inequalities, finally!
Refactored your inequalities into a (hopefully) more intuitive form
Some more equivalent forms, playing the same game with the last two does not seem to produce nice results, are the signs correct in the numerators of the $\lambda$ terms?
Another proposal
Recording some thoughts in a new section, 'total domination' sounds really cool

@@
 \newcommand{\cC}{\mathcal{C}}
+\newcommand{\cD}{\mathcal{D}}
 \newcommand{\cI}{\mathcal{I}}
@@
 
-  For $t\in\TT_n$, define $\phi^t_k:\ZZ^n\to\ZZ^n$ as the piecewise-linear map
+  (DR: I changed to $\RR$ because it didn't seem like we really cared about integer points at the moment, when we try to link up with minors this will need to be added.)
+  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
   \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
@@
   We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labelled $k$.
-  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\ZZ^n\to\ZZ^n$ by
+  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
   \begin{itemize}
@@
   \end{itemize}
-  For $\lambda\in\ZZ^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
+  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
   \begin{definition}
-    For $\lambda\in\ZZ^n$, define the \emph{dominance polytope} 
+    For $\lambda\in\RR^n$, define the \emph{dominance polytope} 
     \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
+    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
   \end{definition}
   Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
+  \begin{lemma}
+    The sets $\cP(\lambda)$ are actually polytopes.
+  \end{lemma}
 
@@
 
+  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following six inequalities:
+  \begin{align}
+    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+    \\
+    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+    \\
+    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+    \\
+    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+    \\
+    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+    \\
+    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
+  \end{align}
+  Are any of these better forms?
+  \begin{align}
+    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+    \\
+    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
+    \\
+    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+    \\
+    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+    \\
+    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+    \\
+    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+    \\
+    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+    \\
+    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+    \\
+    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+    \\
+    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+  \end{align}
+  Another proposal (I also changed the order of the equations)
+  \begin{align}
+    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
+    \\
+    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 
+    \\
+    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2
+    \\
+    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
+    \\
+    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1
+    \\
+    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1-b\lambda_2
+  \end{align}
+
+  \section{The Total Domination Polyhedron}
+
+  Define the \emph{total domination polyhedron} $\cD:=\{(\lambda,\mu):\mu\in\cP(\lambda)\}$, i.e. this is the set of all pairs where $\lambda$ dominates $\mu$.
+  Write $\pi_1:\cD\to\RR^n$ for the projection to $\lambda$ and $\pi_2:\cD\to\RR^n$ for the projection to $\mu$.
+  \begin{itemize}
+    \item Is it a polyhedron?
+    \item The lemma below might suggest so.  
+      Indeed, if it is, by the Decomposition Theorem, we can write $\cD$ as the Minkowski sum of a polyhedral cone (almost certainly $\cI$) and a convex polytope (what is it?).
+      I am ignoring that it should really be the union of this polyhedron with a plane if the previous sentence holds any water.
+    \item Actually, we might need to take the union of several polyhedra to account for the variations in the fibers $\pi_1^{-1}(\lambda)$.
+  \end{itemize}
+
+  Is the following result true beyond rank 2?
+  \begin{lemma}
+    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
+  \end{lemma}
+  \begin{proof}
+    Maybe the vertex of this cone is given by $\lambda=(\lambda_1,\lambda_2)$ where
+    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
+  \end{proof}
+
 \end{document}

### 2020-08-15 dominance_regions.tex
Some notes

@@
   \begin{proof}
-    Maybe the vertex of this cone is given by $\lambda=(\lambda_1,\lambda_2)$ where
+    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_1,\lambda_2)$ where
     \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
+    (This comes from setting $\mu$ to be the vertex opposite $\lambda$ inside the dominance region $\cP(\lambda)$ and then solving for $\lambda$.)
   \end{proof}
+  \begin{remark}
+    We want to understand what the curve is that results when we have $\mu$ lie along the unit circle, this should be possible by plugging $(\cos(\theta),\sin(\theta))$ into this formula for $\lambda$ and seeing what ellipse we get.
+  \end{remark}
 

### 2020-10-03 dominance_regions.tex
Random minor edits through the first 3 pages.

@@
   \section{Introduction}
-  The investigations of this paper are inspired by the dominance order for the tropical labellings for bases of cluster algebras.
+  The investigations of this paper are inspired by the dominance order on the tropical labelings for bases of cluster algebras.
   This dominance order is used by Qin to understand how these bases may be deformed in the case when there is a green-to-red sequence of mutations.
+  In particular, these calculations can be carried out for any acyclic cluster algebra.
 
@@
 
-  To record sequences of these matrix mutations, we introduce the labelled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
+  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
   \begin{itemize}
     \item $B^{t_0}=B$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $B^{t'}=\mu_k B^t$.
+    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $B^{t'}=\mu_k B^t$.
   \end{itemize}
@@
   where the entries of $E^t_{k,\varepsilon}$ is given by \eqref{eq:mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
-  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labelled $k$.
+  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
   For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
@@
     \item $\phi_{t_0}=\Id$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
+    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
   \end{itemize}
@@
   \begin{definition}
-    For $\lambda\in\RR^n$, define the \emph{dominance polytope} 
+    For $\lambda\in\RR^n$, define the \emph{dominance region} 
     \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
@@
   \begin{lemma}
-    The sets $\cP(\lambda)$ are actually polytopes.
+    The sets $\cP(\lambda)$ are polytopes.
   \end{lemma}
@@
   Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
-  Here we may take $\TT_2$ to have vertices labelled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labelled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labelled $2$.
+  Here we may take the 2-regular tree $\TT_2$ to have vertices labeled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labeled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labeled $2$.
   We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
 
-  Observe that $\phi_{t_1}$ is the piecewise-linear map given by
+  Observe that $\phi_{t_1}:=\phi_1^{t_0}$ is the piecewise-linear map given by
   \begin{equation}
@@
   \end{equation}
-  and $\phi_{t_2}=\phi_{t_{-2}}^{-1}$ is the piecewise-linear map given by
+  and $\phi_{t_2}:=\phi_2^{t_1}\phi_1^{t_0}$ is the piecewise-linear map given by
   \begin{equation}
     \label{eq:forward two step mutation}
-    \phi_{t_2}(\lambda)=\begin{cases} ((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\ (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\ (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}\end{cases}
+    \phi_{t_2}(\lambda)=\begin{cases} \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\ (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\ (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}\end{cases}
   \end{equation}
@@
     \label{eq:backward two step mutation}
-    \phi_{t_2}^{-1}(\lambda)=\begin{cases} (-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\ (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\ (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$;}\end{cases}
+    \phi_{t_2}^{-1}(\lambda)=\begin{cases} \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\ (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\ (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$;}\end{cases}
   \end{equation}
 
-  By an eigenvector of a piecewise-linear map $\phi$, we mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
+  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
   \begin{lemma}
@@
     \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
-    or
+    or, equivalently, that
     \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
@@
 
-  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
-  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $(-bc\pm\sqrt{bc(bc-4)},2c)$.
+  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
   \begin{lemma}
-    The vectors $(2b, -bc+\sqrt{bc(bc-4)})$ (resp. $(2b, -bc-\sqrt{bc(bc-4)})$) and $(2c, bc+\sqrt{bc(bc-4)})$ (resp. $(2c, bc-\sqrt{bc(bc-4)})$) are perpendicular.
+    The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
   \end{lemma}
   \begin{proof}
-    This is immediate from the equality $(-bc+\sqrt{bc(bc-4)})(bc+\sqrt{bc(bc-4)})=-4bc$.
+    This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
   \end{proof}
@@
   \begin{proof}
-    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$ respectively.
-    The claim is immediate for $\phi_{t_2}$ since the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$ are eigenvectors.
-    Now, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\big( (2b,-bc\pm\sqrt{bc(bc-4)}) \big)=(-2b,bc\pm\sqrt{bc(bc-4)})$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity.
+    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$, respectively.
+    The claim is immediate for $\phi_{t_2}$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_{t_2}$ is linear in $\cI$.
+    Now, since $b>0$, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_{t_1}$ in this region.
   \end{proof}
@@
   \begin{proof}
-    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion respectively.
+    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
     Using the claim for $j>0$ and then the defining recursion twice, we get
@@
 
+  The following gives the desired expressions for $\phi_{t_i}(\lambda)$ when $\lambda\in\cI$.
   \begin{lemma}
@@
     \end{align*}
-    where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
+    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
 
@@
 
+  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP(\lambda)$ for $\lambda\in\cI$.
   \begin{lemma}
@@
     These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
-    By the linearity of this transformation of $\RR^2$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
+    By the linearity of the transformation of $\RR^2$ given by the matrix $A$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
   \end{proof}

### 2020-12-30 dominance_regions.tex
Minor edits, initial setup for affine types

@@
   \begin{abstract}
-    We investigate the shapes of the polytopes defining the dominance order for imaginary $\bfg$-vectors in rank two.
+    We investigate the shapes of the polytopes defining the dominance order for $\bfg$-vectors in acyclic affine cluster algebras and acyclic cluster algebras of rank two.
+    In both cases, we arrive at a complete description: 
+    \begin{itemize}
+      \item cluster monomials are never deformable;
+      \item in affine types, the imaginary $\bfg$-vectors have dominance polytopes which are segments of imaginary $\bfg$-vectors except possibly for a single point on the boundary of an imaginary cone;
+      \item a strange difference emerges in rank two wild types: the imaginary dominance polytopes are kites, triangles, or trapezoids which extend far outside the imaginary cone, the triangles appearing along rays corresponding to columns of the associated Cartan matrix.
+    \end{itemize}
     We conjecture how our observations might generalize to higher dimensions.
@@
   \begin{equation}
-    \label{eq:mutation matrix}
-    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise.} \end{cases}
+    \label{eq:left mutation matrix}
+    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise;} \end{cases}
+  \end{equation}
+  and a matrix $F_{k,\varepsilon}=(f_{ij})$ with
+  \begin{equation}
+    \label{eq:right mutation matrix}
+    f_{ij}=\begin{cases} 1 & \text{if $k\ne i=j$;}\\ -1 & \text{if $k=i=j$;}\\ [-\varepsilon b_{kj}]_+ & \text{if $k=i\ne j$;}\\ 0 & \text{otherwise.} \end{cases}
   \end{equation}
@@
   One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
+  Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
 
@@
   \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
-  where the entries of $E^t_{k,\varepsilon}$ is given by \eqref{eq:mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
+  where the entries of $E^t_{k,\varepsilon}$ is given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
   We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
@@
   \end{lemma}
+
+  \section{Affine Types}
+  Associated to an acyclic skew-symmetrizable matrix $B=(b_{ij})$ there is a Cartan matrix $A=(a_{ij})$ with $a_{ii}=2$ and $a_{ij}=-|b_{ij}|$.
+  We say that $B$ is of affine type if its associated Cartan matrix gives rise to an affine Dynkin diagram.
+  In this section, we focus on understanding the dominance polytopes for affine matrices $B$.
+
+  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable matrix of affine type with associated Cartan matrix $A=(a_{ij})$.
+
+  \begin{definition}
+    Describe imaginary $\bfg$-vectors and those corresponding to cluster monomials.
+  \end{definition}
+
+  \begin{lemma}
+    Let $\lambda\in\ZZ^n$ correspond to a cluster monomial.
+    Then $\cP(\lambda)=\{\lambda\}$.
+  \end{lemma}
+  \begin{proof}
+    An explicit sequence of sink/source mutations should suffice.
+  \end{proof}
 

### 2021-06-25 dominance_regions.tex
Minor edits

@@
 \newcommand{\Id}{\operatorname{Id}}
+\renewcommand{\Im}{\operatorname{Im}}
 \newcommand{\into}{\hookrightarrow}
@@
   \end{equation}
+  Observe that $E^2_{k,\varepsilon}=\Id$ and $F^2_{k,\varepsilon}=\Id$ for any $k$ and any choice of $\varepsilon$.
+
   The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_kB=(b'_{ij})$ given by
@@
   One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
+  \begin{remark}
     Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
+  \end{remark}
 
@@
   \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
-  where the entries of $E^t_{k,\varepsilon}$ is given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
+  where the entries of $E^t_{k,\varepsilon}$ are given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
   We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
+  \begin{lemma}
+    Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
+    If $\lambda\in\Im(B^t)$, then $\phi^t_k(\lambda)\in\Im(B^{t'})$.
+  \end{lemma}
+  \begin{proof}
+    Suppose $\lambda=B^t\alpha$ for some $\alpha\in\RR^n$.
+    Then 
+    \[\phi^t_k(\lambda)=E^t_{k,\pm}\lambda=E^t_{k,\pm} B^t\alpha=E^t_{k,\pm} B^t F^t_{k,\pm} F^t_{k,\pm}\alpha=B^{t'} F^t_{k,\pm}\alpha\]
+    so that $\phi^t_k(\lambda)\in\Im(B^{t'})$.
+  \end{proof}
+
   For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
@@
     \\
-    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 
+    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq \frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 
     \\
-    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2
+    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
     \\
@@
     \\
-    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1
+    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1
     \\
-    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1-b\lambda_2
+    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
   \end{align}

### 2021-06-28 dominance_regions.tex
Added some results

@@
 
-\newcommand{\bfc}{\mathbf{c}}
-\newcommand{\bfg}{\mathbf{g}}
+\newcommand{\bfc}{\boldsymbol{c}}
+\newcommand{\bfg}{\boldsymbol{g}}
+\newcommand{\bfr}{\boldsymbol{r}}
+\newcommand{\bfx}{\boldsymbol{x}}
+\newcommand{\bfy}{\boldsymbol{y}}
 
@@
 
+  \section{Questions}
+  \begin{enumerate}
+    \item To what extent can we explicitly/combinatorially describe the eigenvalues/eigenvectors of the twist automorphism/Auslander-Reiten translation acting on imaginary $\bfg$-vectors given a maximal green sequence?
+    \item What role do coefficients play in the dominance order on pointed bases?
+    \item Is any change required in the theory to handle quantum/generalized or both cases together?
+    \item What do our results mean geometrically in terms of the cluster variety?  Is this constructing an affine chart?
+  \end{enumerate}
+
   \section{Introduction}
@@
 
-  \section{Lattice Mutations}
+  \section{Lattice Mutations and Linear Inequalities}
   Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e.
 there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
+  Write $\Im(B)$ for the span of the columns of $B$ inside $\RR^n$ and $\Im^+(B)$ for their non-negative span.
+  Define $\Im_\ZZ(B)$ and $\Im^+_\ZZ(B)$ analogously over the integers.
+  The matrix $B$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_m,i_{m+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le m$.
+  In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_\ell k_{\ell'}}\ge 0$, such a sequence is called \emph{sink-adapted}.
+
   For $b\in\ZZ$, write $[b]_+=max(b,0)$.
@@
   \end{itemize}
+  \begin{lemma}
+    Suppose $B$ is acyclic with sink-adapted sequence $k_1,\ldots,k_n$.
+    Consider $t_1,\ldots,t_n\in\TT_n$ so that $t_{\ell-1}$ is joined to $t_\ell$ by an edge in $\TT_n$ labeled by $k_\ell$ for $1\le\ell\le n$.
+    For a sequence of signs $\varepsilon_1,\ldots,\varepsilon_n$, the product $E^{t_{n-1}}_{k_n,\varepsilon_n}\cdots E^{t_0}_{k_1,\varepsilon_1}$ is given by $A=(a_{ij})$ where
+    \[a_{k_{\ell'} k_\ell}=\sum_{U=\{\ell=\ell_1<\ldots<\ell_t\}\subseteq[\![\ell,n]}\prod_{s=1}^t \begin{cases} [-\varepsilon_{\ell_t}b_{k_{\ell'} k_{\ell_t}}]_+ & \text{if $s=t$ and $\ell_t>\ell'$}\\ -1 & \text{if $s=t$ and $\ell_t=\ell'$}\\ [\varepsilon_{\ell_s} b_{k_{\ell_{s+1}} k_{\ell_s}}]_+ & \text{if $s<t$ and $\ell_t\ge\ell'$}\\ 0 & \text{if $\ell'>\ell_t$} \end{cases} \]
+
+    Then $\phi_{t_n}$ is the following piecewise-linear automorphism:
+    \begin{equation}
+      \label{eq:tropical twist}
+      \text{(This is going to require casework with the possible signs, we'll really only need it for imaginary $\bfg$-vectors.)}
+    \end{equation}
+  \end{lemma}
+  \begin{proof}
+    We prove the following modified formula for the product $E^{t_{m-1}}_{k_m,\varepsilon_n}\cdots E^{t_0}_{k_1,\varepsilon_1}$ with $1\le m\le n$ by induction on $m$.
+    Writing this matrix as $A^{(m)}=(a^{(m)}_{ij})$, we claim that
+    \[a^{(m)}_{k_{\ell'} k_\ell}=\sum_{U=\{\ell=\ell_1<\ldots<\ell_t\}\subseteq[\![\ell,n]}\prod_{s=1}^t \begin{cases} [-\varepsilon_{\ell_t}b_{k_{\ell'} k_{\ell_t}}]_+ & \text{if $s=t$ and $m\ge\ell_t>\ell'$}\\ -1 & \text{if $s=t$ and $m\ge\ell_t=\ell'$}\\ [\varepsilon_{\ell_s} b_{k_{\ell_{s+1}} k_{\ell_s}}]_+ & \text{if $s<t$ and $\ell_t\ge\ell'$}\\ [\varepsilon_\ell b_{k_{\ell'} k_\ell}]_+ & \text{if $\ell'>m\ge\ell_t=\ell$}\\ 1 & \text{if $\ell=\ell_t=\ell'>m$}\\ 0 & \text{if $m\ge\ell'>\ell_t$ or $\ell_t>\ell'>m$} \end{cases} \]
+    Observe that the additional conditions vanish when $m=n$, proving the desired result once this formula is established.
+
+    Since the sequence $k_1,\ldots,k_n$ is sink-adapted, the matrix $E^{t_{\ell-1}}_{k_\ell,\varepsilon_\ell}$, for $1\le\ell\le n$, has entries $e^{(\ell)}_{ij}$ given by
+    \begin{equation}
+      \label{eq:sink mutation matrix}
+      e^{(\ell)}_{ij}=\begin{cases} 1 & \text{if $i=j\ne k_\ell$;}\\ -1 & \text{if $i=j=k_\ell$;}\\ [-\varepsilon_\ell b_{ik_\ell}]_+ & \text{if $i=k_{\ell'}$, $j=k_\ell$, $\ell>\ell'$;}\\ [\varepsilon_\ell b_{ik_\ell}]_+ & \text{if $i=k_{\ell'}$, $j=k_\ell$, $\ell'>\ell$;}\\ 0 & \text{otherwise;} \end{cases}
+    \end{equation}
+    the entries for $\ell'<\ell$ picking up this sign from the prior matrix mutations.
+    From this, it is easy to see that $a^{(1)}_{k_{\ell'} k_\ell}=e^{(1)}_{k_{\ell'} k_\ell}$ for $\ell,\ell'\in[1,n]$, this establishes the base of the induction on $m$.
+
+    Now suppose the matrix $A^{(m)}$ is given as above.
+    We need to check that 
+    \begin{equation}
+      \label{eq:twist matrix recursion}
+      a^{(m+1)}_{k_{\ell'} k_\ell}=\sum\limits_{\ell''=1}^n e^{(m+1)}_{k_{\ell'} k_{\ell''}} a^{(m)}_{k_{\ell''} k_\ell}.
+    \end{equation}
+    It will be convenient to distinguish cases:
+    \begin{itemize}
+      \item For $\ell'=m+1$, the right hand side of \eqref{eq:twist matrix recursion} becomes $-a^{(m)}_{k_{m+1} k_\ell}$.
+      \item If $\ell'>m+1$, the right hand side of \eqref{eq:twist matrix recursion} becomes $a^{(m)}_{k_{\ell'} k_\ell}+[\varepsilon_{m+1} b_{k_{\ell'} k_{m+1}}]_+ a^{(m)}_{k_{m+1} k_\ell}$.
+      \item If $m+1>\ell'$, the right hand side of \eqref{eq:twist matrix recursion} becomes $a^{(m)}_{k_{\ell'} k_\ell}+[-\varepsilon_{m+1} b_{k_{\ell'} k_{m+1}}]_+ a^{(m)}_{k_{m+1} k_\ell}$.
+    \end{itemize}
+  \end{proof}
+
   For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
@@
 
+  \begin{lemma}
+    \label{le:transformed inequalities}
+    Let $A$ be an invertible $n\times n$ matrix.
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equalities
+    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
+  \end{proof}
+
   \section{Affine Types}
@@
   Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable matrix of affine type with associated Cartan matrix $A=(a_{ij})$.
+
+  \begin{lemma}
+    One column is always in the positive span of the other columns.
+  \end{lemma}
 

### 2021-07-10 dominance_regions.tex
Better version of Lemma 3.3 with a proof, probably other random edits/comments as well.

--- 2021-06-25 dominance_regions.tex
@@
 \newtheorem{remark}[theorem]{Remark}
+\newtheorem{question}{Question}
 
@@
 \newcommand{\Aut}{\operatorname{Aut}}
+\newcommand{\Col}{\operatorname{Col}}
 \newcommand{\diag}{\operatorname{diag}}
 \newcommand{\Id}{\operatorname{Id}}
-\renewcommand{\Im}{\operatorname{Im}}
 \newcommand{\into}{\hookrightarrow}
@@
 \newcommand{\ot}{{\overline{t}}}
+\newcommand{\wt}{{\operatorname{wt}}}
 
@@
 
-  \section{Lattice Mutations}
+  \section{Lattice Mutations and Linear Inequalities}
   Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e.
 there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
+  Write $\Col(B)$ for the span of the columns of $B$ inside $\RR^n$ and $\Col^+(B)$ for their non-negative span.
+  Define $\Col_\ZZ(B)$ and $\Col^+_\ZZ(B)$ analogously over the integers.
+
+  The matrix $B$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_m,i_{m+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le m$.
+  This condition is naturally interpreted in terms of an associated quiver $Q_B$ with $n$ vertices and an arrow $i\to j$ whenever $b_{ji}>0$ (if we need to use representation theory at any point we'll have to change this to be $\gcd(b_{ij},b_{ji})$ arrows $i\to j$).
+  Indeed, this is precisely the condition that $Q_B$ has no oriented cycles.
+  In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_{\ell'} k_\ell}\ge 0$.
+  The sequence $(k_1,\ldots,k_n)$ (resp. $(k_n,\ldots,k_1)$) is said to be \emph{source-adapted} (resp. \emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
+  %\sayDR{We need to pin down this convention.}
+
   For $b\in\ZZ$, write $[b]_+=max(b,0)$.
@@
     Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-    If $\lambda\in\Im(B^t)$, then $\phi^t_k(\lambda)\in\Im(B^{t'})$.
+    If $\lambda\in\Col(B^t)$, then $\phi^t_k(\lambda)\in\Col(B^{t'})$.
   \end{lemma}
@@
     \[\phi^t_k(\lambda)=E^t_{k,\pm}\lambda=E^t_{k,\pm} B^t\alpha=E^t_{k,\pm} B^t F^t_{k,\pm} F^t_{k,\pm}\alpha=B^{t'} F^t_{k,\pm}\alpha\]
-    so that $\phi^t_k(\lambda)\in\Im(B^{t'})$.
+    so that $\phi^t_k(\lambda)\in\Col(B^{t'})$.
   \end{proof}
@@
   \end{itemize}
+
+  Suppose $B$ is acyclic.
+  Given a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, define a quiver $Q_{B,\varepsilon}$ from $Q_B$ by removing all arrows starting at vertex $i$ whenever $\varepsilon_i=-1$.
+  For $1\le j\le n$, define $\cP_j(Q_{B,\varepsilon})$ as the set of paths in $Q_{B,\varepsilon}$ starting at vertex $j$.
+  Elements of $\cP_j(Q_{B,\varepsilon})$ are sequences of vertices $(p_1,\ldots,p_r)$ with $p_1=j$ and $b_{p_{t+1}p_t}>0$ for $1\le t\le r-1$.
+  Given a path $p\in\cP_j(Q_{B,\varepsilon})$, a vertex $i\in Q_0$, and a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, set
+  \[\wt_{i,\varepsilon}(p):=-b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}\prod_{t=1}^{r-1} b_{p_{t+1}p_t},\]
+  where the prefactor $b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}$ is omitted if $i=p_r$ or $\varepsilon_{p_r}=-1$.
+  \begin{lemma}
+    Suppose $B$ is acyclic with source-adapted sequence $k_1,\ldots,k_n$.
+    Consider $t_1,\ldots,t_n\in\TT_n$ so that $t_{\ell-1}$ is joined to $t_\ell$ by an edge in $\TT_n$ labeled by $k_\ell$ for $1\le\ell\le n$.
+    For a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, the product $E^{t_{n-1}}_{k_n,\varepsilon_{k_n}}\cdots E^{t_0}_{k_1,\varepsilon_{k_1}}$ is given by $\tau=(\tau_{ij})$ with
+    \begin{equation}
+      \label{eq:tropical twist}
+      \tau_{ij}=\sum_{p\in\cP_j(Q_{B,\varepsilon})}^* \wt_{i,\varepsilon}(p),
+    \end{equation}
+    where the $*$ indicates that the summation includes the trivial path at $j$ only if $i\le j$ when $\varepsilon_j=1$ and only if $i=j$ when $\varepsilon_j=-1$.
+
+    Then $\phi_{t_n}$ is the following piecewise-linear automorphism:
+    \begin{equation}
+      \label{eq:tropical twist}
+      \text{(This is going to require casework with the possible signs, we'll really only need it for imaginary $\bfg$-vectors though.)}
+    \end{equation}
+    The answer comes from selectively ``turning off'' arrows out of chosen vertices as indicated by choosing $\varepsilon_i=-1$.
+  \end{lemma}
+  \begin{proof}
+    We prove the following modified formula for the product $E^{t_{n-1}}_{k_n,\varepsilon_{k_n}}\cdots E^{t_{m-1}}_{k_m,\varepsilon_{k_m}}$ for $1\le m\le n$ by reverse induction on $m$.
+    Writing this matrix as $\tau^{(m)}=(\tau^{(m)}_{ij})$, we claim that
+    \begin{equation}
+      \label{eq:tropical twist}
+      \tau^{(m)}_{ij}=\begin{cases} \sum\limits_{p\in\cP_j(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) & \text{if $j=k_\ell$ with $m\le\ell$;}\\ \delta_{ij} & \text{otherwise;} \end{cases}
+    \end{equation}
+    where $Q_{B,\varepsilon}^{(m)}$ is the full subquiver of $Q_{B,\varepsilon}$ on vertices $k_m,\ldots,k_n$.
+    Note that the weight function follows the same definition as above.
+
+    Since the sequence $k_1,\ldots,k_n$ is source-adapted, the matrix $E^{t_{m-1}}_{k_m,\varepsilon_m}$, for $1\le m\le n$, has entries $e^{(m)}_{ij}$ given by
+    \begin{equation}
+      \label{eq:source mutation matrix}
+      e^{(m)}_{ij}=\begin{cases} 1 & \text{if $i=j\ne k_m$;}\\ -1 & \text{if $i=j=k_m$;}\\ [-\varepsilon_{k_m} b_{ik_m}]_+ & \text{if $i=k_\ell$, $j=k_m$, $\ell<m$;}\\ [\varepsilon_{k_m} b_{ik_m}]_+ & \text{if $i=k_\ell$, $j=k_m$, $m<\ell$;}\\ 0 & \text{otherwise;} \end{cases}
+    \end{equation}
+    the entries for $\ell<m$ picking up the sign from the prior matrix mutations.
+
+    For $m=n$, it is clear that $\tau^{(n)}_{ij}=e^{(n)}_{ij}$ for $j\ne k_n$.
+    If $\varepsilon_{k_n}=1$, there is only the trivial path $(k_n)$ in $Q_{B,\varepsilon}^{(n)}$ and we have $\tau^{(n)}_{ik_n}=-b_{ik_n}$, which agrees with $e^{(n)}_{ik_n}$ in this case.
+    Otherwise, $\varepsilon_{k_n}=-1$ and the sum is empty for $i\ne k_n$ giving $\tau^{(n)}_{ik_n}=0=e^{(n)}_{ik_n}$ or only takes the trivial path for $i=k_n$ giving $\tau^{(n)}_{k_nk_n}=-1=e^{(n)}_{k_nk_n}$.
+    This gives the base of the induction.
+
+    Now suppose the matrix $\tau^{(m)}$ is given as above.
+    Using equation \eqref{eq:source mutation matrix}, we need to check that 
+    \begin{equation}
+      \label{eq:twist matrix recursion}
+      \tau^{(m-1)}_{ij}=\sum\limits_{p=1}^n \tau^{(m)}_{ip} e^{(m-1)}_{pj}=\begin{cases} \tau^{(m)}_{ij} & \text{if $j\ne k_{m-1}$;}\\ -\tau^{(m)}_{ik_{m-1}} + \sum\limits_{\ell=1}^{m-2} \tau^{(m)}_{i k_\ell} [-\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ + \sum\limits_{\ell=m}^n \tau^{(m)}_{i k_\ell} [\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ & \text{if $j=k_{m-1}$;}\end{cases}
+    \end{equation}
+    is computed by the formula above.
+    First observe that $\tau^{(m-1)}_{ij}=\tau^{(m)}_{ij}=\delta_{ij}$ if $j=k_\ell$ with $\ell<m-1$.  
+    Second observe that $\cP_j(Q_{B,\varepsilon}^{(m-1)})=\cP_j(Q_{B,\varepsilon}^{(m)})$ whenever $j=k_\ell$ with $m\le\ell$, i.e.
+the purported formulas for $\tau^{(m-1)}_{ij}$ and $\tau^{(m)}_{ij}$ agree in this case.
+    Therefore it remains to show that
+    \[
+      \tau^{(m-1)}_{i k_{m-1}}=-\delta_{ik_{m-1}} + \sum\limits_{\ell=1}^{m-2} \delta_{i k_\ell} [-\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ + \sum\limits_{\ell=m}^n \sum\limits_{p\in\cP_{k_\ell}(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) [\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+
+    \]
+    agrees with the desired expression.
+    Indeed, for $\varepsilon_{k_{m-1}}=-1$ this reduces to $\tau^{(m-1)}_{i k_{m-1}}=-\delta_{i k_{m-1}}$ which matches with the desired expression in this case.
+    Then assuming $\varepsilon_{k_{m-1}}=1$, we are comparing with
+    \[
+      \tau^{(m-1)}_{i k_{m-1}}=-\delta_{ik_{m-1}} - \sum\limits_{\ell=1}^{m-2} \delta_{i k_\ell} b_{k_\ell k_{m-1}} + \sum\limits_{\ell=m}^n \sum\limits_{p\in\cP_{k_\ell}(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) b_{k_\ell k_{m-1}}.
+    \]
+    But observe that the final summation above contributes the nontrivial paths to the summation $\sum\limits_{p\in\cP_{k_{m-1}}(Q_{B,\varepsilon}^{(m-1)})}^* \wt_{i,\varepsilon}(p)$ while the first two terms above give the contribution, depending on $i$, corresponding to the trivial path $(k_{m-1})$.
+  \end{proof}
+  \begin{question}
+    Is the trace of $\tau$ an invariant of matrix mutations?
+P.A.: It is invariant under sink and source mutations since the trace is a class function and these mutations simply enact a cyclic shift in the factors of $\tau$.
+  \end{question}
+
   For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
@@
 
+  \section{Ignore}
+  Rank 4 Skew-Symmetric $B$
+
+  $P(\lambda)=\lambda^4 + a\lambda^3 + b\lambda^2 + c\lambda + 1$
+
+  \begin{align*}
+    a
+    &=-b_{41}b_{21}b_{32}b_{43}-b_{31}b_{21}b_{32}-b_{41}b_{21}b_{42}-b_{41}b_{31}b_{43}-b_{42}b_{32}b_{43}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
+    c
+    &=-b_{21}b_{32}b_{43}b_{41}-b_{21}b_{32}b_{31}-b_{21}b_{42}b_{41}-b_{31}b_{43}b_{41}-b_{32}b_{43}b_{42}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
+    b
+    &=b_{41} b_{32} b_{32} b_{41} - b_{31} b_{42} b_{32} b_{41} - b_{31} b_{43} b_{21} b_{42} - b_{41} b_{32} b_{31} b_{42} + b_{31} b_{42} b_{31} b_{42} + b_{21} b_{43} b_{21} b_{43} - b_{21} b_{42} b_{31} b_{43} - b_{21} b_{32} b_{31} - b_{31} b_{21} b_{32} - b_{21} b_{42} b_{41} - b_{31} b_{43} b_{41} - b_{32} b_{43} b_{42} - b_{41} b_{21} b_{42} - b_{41} b_{31} b_{43} - b_{42} b_{32} b_{43} - 2 b_{21} b_{21} - 2 b_{31} b_{31} - 2 b_{32} b_{32} - 2 b_{41} b_{41} - 2 b_{42} b_{42} - 2 b_{43} b_{43} + 6\\
+    &=a+c-2+m\\
+    &=a+c-2+n^2\\
+    m
+    &=b_{41}b_{21}b_{32}b_{43}+b_{21}b_{32}b_{43}b_{41}+b_{41}b_{32}b_{32}b_{41}-b_{31}b_{42}b_{32}b_{41}-b_{31}b_{43}b_{21}b_{42}-b_{41}b_{32}b_{31}b_{42}+b_{31}b_{42}b_{31}b_{42}+b_{21}b_{43}b_{21}b_{43}\\
+    &\quad -b_{21}b_{42}b_{31}b_{43}\\
+    &=(b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43})^2\\
+    n
+    &=b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43}\\
+  \end{align*}
+
+  Observe that $P(-1)=n^2$.
+  What happens when $\lambda=\frac{-a+2\pm\sqrt{a(a-4)}}{2}$?  You get $P(\lambda)=(b-2)\lambda^2$.
+
 \end{document}

### 2021-07-24 dominance_regions.tex
Committing to pull

@@
 
+  \subsection{Deformation Support}
+  The greedy basis of Lee, Li, and Zelevinsky \cite{???} can be defined as the positive pointed basis with minimal support.
+  Here we identify the maximum possible support of its deformations.
+
+  Consider the deformation of the theta basis element with $\bfg$-vector $\lambda$.
+  \begin{theorem}
+    For $\lambda\in\cI\cap\ZZ^2$, the support of any deformation of the corresponding theta basis element is contained in the polytope defined by the following inequalities:
+    \begin{align*}
+       \lambda_1-b\lambda_2 &\le x\\
+       \lambda_2 &\le y\\
+    \end{align*}
+    is the convex hull of the following vertices:
+    \[\lambda, \qquad (\lambda_1-b\lambda_2,\lambda_2), \qquad (\lambda_1-b\lambda_2,\lambda_2-c\lambda_1), \qquad (?,?)\]
+    The $d$-vector is $(\lambda_1-b\lambda_2,\lambda_2)$
+
+    $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$
+
+    Slope:
+    \[\big(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(c\lambda_1+2\lambda_2)-(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)\big) /\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2)\]
+
+    $y=$
+
+    $(\lambda_1,\lambda_2)$ and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$
+
+    Slope: $-\frac{bc+\sqrt{bc(bc-4)}}{2b}$\\
+
+    Corner of dominant support?: 
+    \begin{align*}
+      \left(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2),-\frac{bc+\sqrt{bc(bc-4)}}{2b}\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2)+\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\right)\\
+      \left(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2),-\frac{bc+\sqrt{bc(bc-4)}}{2b}\frac{bc}{\sqrt{bc(bc-4)}}\lambda_1+-\frac{bc+\sqrt{bc(bc-4)}}{2}\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\lambda_2+\lambda_2\right)\\
+    \end{align*}
+
+  \end{theorem}
+
   \section{The Total Domination Polyhedron}
@@
     b
-    &=b_{41} b_{32} b_{32} b_{41} - b_{31} b_{42} b_{32} b_{41} - b_{31} b_{43} b_{21} b_{42} - b_{41} b_{32} b_{31} b_{42} + b_{31} b_{42} b_{31} b_{42} + b_{21} b_{43} b_{21} b_{43} - b_{21} b_{42} b_{31} b_{43} - b_{21} b_{32} b_{31} - b_{31} b_{21} b_{32} - b_{21} b_{42} b_{41} - b_{31} b_{43} b_{41} - b_{32} b_{43} b_{42} - b_{41} b_{21} b_{42} - b_{41} b_{31} b_{43} - b_{42} b_{32} b_{43} - 2 b_{21} b_{21} - 2 b_{31} b_{31} - 2 b_{32} b_{32} - 2 b_{41} b_{41} - 2 b_{42} b_{42} - 2 b_{43} b_{43} + 6\\
+    &=b_{41} b_{32} b_{32} b_{41} - b_{31} b_{42} b_{32} b_{41} - b_{31} b_{43} b_{21} b_{42} - b_{41} b_{32} b_{31} b_{42} + b_{31} b_{42} b_{31} b_{42} + b_{21} b_{43} b_{21} b_{43} - b_{21} b_{42} b_{31} b_{43}\\
+    &\quad - b_{21} b_{32} b_{31} - b_{31} b_{21} b_{32} - b_{21} b_{42} b_{41} - b_{31} b_{43} b_{41} - b_{32} b_{43} b_{42} - b_{41} b_{21} b_{42} - b_{41} b_{31} b_{43} - b_{42} b_{32} b_{43}\\
+    &\quad - 2 b_{21} b_{21} - 2 b_{31} b_{31} - 2 b_{32} b_{32} - 2 b_{41} b_{41} - 2 b_{42} b_{42} - 2 b_{43} b_{43} + 6\\
     &=a+c-2+m\\
@@
   Observe that $P(-1)=n^2$.
-  What happens when $\lambda=\frac{-a+2\pm\sqrt{a(a-4)}}{2}$?  You get $P(\lambda)=(b-2)\lambda^2$.
+  What happens when $\lambda=\frac{-a\pm\sqrt{a^2-4}}{2}$?  You get $P(\lambda)=(b-2)\lambda^2$.
 

### 2021-07-24 comparison-with-qin-kyoto/comparison.tex

\documentclass[12pt]{amsart}
% this is here to force arXiv to produce a nice output
\pdfoutput=1

\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amstext}
\usepackage{amsopn}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{verbatim}
\usepackage[margin=1in,marginparwidth=0.8in, marginparsep=0.1in]{geometry}
\renewcommand{\baselinestretch}{1.2} % changes page formatting
\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
\usepackage{newtxtext} % changes font appearance, replaces times
\usepackage{stmaryrd}
\usepackage{accents}
\usepackage{bbm}

% For setting off new terms
\newcommand{\newword}[1]{\textbf{\emph{#1}}}

% shorthands
\DeclareMathOperator{\corank}{corank}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\cl}{cl}
\DeclareMathOperator{\Cone}{Cone}
\newcommand{\Bdp}{\widetilde{B}_{dp}}
\newcommand{\bfa}{\mathbf{a}}
\newcommand{\bfc}{\mathbf{c}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfd}{\mathbf{d}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\Bpr}{\widetilde{B}_{pr}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cv}{\alpha}
\newcommand{\dashname}[1]{\stackrel{#1}{\begin{picture}(22,3)\put(0,2.5){\line(1,0){22}}\end{picture}}}
\newcommand{\dol}[1]{\overline{\overline{#1}}}
\newcommand{\grep}{\gv}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\gv}{\omega}
\newcommand{\into}{\hookrightarrow}
\newcommand{\kk}{\Bbbk}
\newcommand{\KQ}{K_0(Q)}
\newcommand{\loopvar}{z}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\onto}{\twoheadrightarrow}
\newcommand{\Qdp}{\widetilde{Q}_{dp}}
\newcommand{\Qrep}{M}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\TT}{\mathbb{T}}
\newcommand{\Zidx}{\ell}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\renewcommand{\mod}[1]{\langle {#1} \rangle}
\newcommand{\congto}{\xrightarrow{\sim}}
\newcommand{\wh}{\widehat}

% Commands for marginal notes below
\usepackage[draft]{say}
\newcommand{\sayS}[1]{\say[S]{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Macro double Bruhat cells and their exponents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{xparse}
% Short version
\NewDocumentCommand{\dbc}{ m O{#1} }{G^{#1}}
% Long version
%\NewDocumentCommand{\dbc}{ m O{{#1}^{-1}} }{G^{#1,#2}}

\newcommand{\muoc}{s_1cs_1}
\newcommand{\muoci}{s_1c^{-1}s_1}
\newcommand{\munc}{s_ncs_n}
\newcommand{\munci}{s_nc^{-1}s_n}

%\newcommand{\muoc}{c_1}
%\newcommand{\muoci}{c_1^{-1}}
%\newcommand{\muoc}{\mu_1\hspace{-1 pt}(c)}
%\newcommand{\muoci}{\mu_1\hspace{-1 pt}(c)^{-1}}
%\newcommand{\munc}{c_n}
%\newcommand{\munci}{c_n^{-1}}
%\newcommand{\munc}{\mu_n\hspace{-1 pt}(c)}
%\newcommand{\munci}{\mu_n\hspace{-1 pt}(c)^{-1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% done
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ambients and numbering
\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\numberwithin{equation}{section}
\numberwithin{figure}{section}

\begin{document}
\title{Comparison with Fan's construction}

\author[Dylan Rupel]{Dylan Rupel}
\address[Dylan Rupel]{University of Notre Dame, Department of Mathematics, Notre Dame, IN 46556, USA}
\email{drupel@nd.edu}

\author[Salvatore Stella]{Salvatore Stella}
\address[Salvatore Stella]{University of Haifa, Department of Mathematics, Haifa, 31905, Israel}
\email{stella@math.haifa.ac.il}

\author[Harold Williams]{Harold Williams}
\address[Harold Williams]{University of California, Davis, Department of Mathematics, Davis, CA 95616, USA}
\email{hwilliams@math.ucdavis.edu}

%\keywords{Cluster algebras, Kac-Moody groups}
%\subjclass[2010]{13F60, 20G44}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\setcounter{tocdepth}{1}
%
%\maketitle
%
%\tableofcontents
%
%\vspace{1cm}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We want to show that our continuous family of generalized minors from \cite[Theorem 4.6]{RSW19} coincide with the family of bases constructed in \cite[Theorem 1.2.1]{Qin19}.

This boils down to show, for any $n>1$, that
\begin{enumerate}
  \item 
    the set of $\bfg$-vectors that are dominated by $n\omega^\circ$ with respect to any seed is 
    \[
      \left\{(n-2r)\omega^\circ \right\}_{r\in\left[1,\left\lfloor\frac{1}{2}\right\rfloor\right]}
    \]

  \item
    we can choose a specific basis and rewrite the last formula in \cite[Proposition 4.4]{RSW19} as in \cite[Theorem 1.2.1]{Qin19} with coefficients being functions of the point $\bfa\in(\kk^\times)^n$. 
\end{enumerate}

For a partition $\lambda \vdash n$ let $e_\lambda$, $s_\lambda$, and $m_\lambda$ denote the elementary, Shur, and monomial symmetric functions associated to the partition $\lambda$ evaluated at $\bfa$.
Recall that $m_{1^{(n)}} = s_{1^{(n)}} = e_n$.

\begin{lemma}
  For every $r\in\left[1,\left\lfloor\frac{1}{2}\right\rfloor\right]$ we have $m_{1^{(n)}} S_{\bfa,r} = m_{2^{(r)},1^{(n-2r)}}$.
\end{lemma}
\begin{proof}
  This is immediate from the definition.
\end{proof}

Let $F_{n\omega^\circ}^\Delta$, $F_{n\omega^\circ}^{gr}$, $F_{n\omega^\circ}^{tr}$, and $F_{n\omega^\circ}^{ge}$ be the $F$-polynomials of the generalized minor, greedy basis element, triangular basis element, and generic basis element with $\bfg$-vector $n\omega^\circ$.
We think of $F$-polynomials as polynomials in the variables $u_1$ and $u_2$.

I did not try yet to prove (1) but it should be straightforward.
It suffices to establish (2) for the $F$-polynomials.

\begin{proposition}
  \[
    m_{1^{(n)}} F_{n\omega^\circ}^\Delta
    =
    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
    m_{2^{(k)},1^{(n-2r)}}
    u_1^r u_2^r
    F_{(n-2r)\omega^\circ}^{ge}
  \]
\end{proposition}
\begin{proof}
  From \cite[Proposition 4.4]{RSW19} we get the following expression for $F_{n\omega^\circ}^\Delta$:
  \[
     F_{n\omega^\circ}^\Delta 
     =
     \sum_{0 \le k \le \ell \le n}
     \sum_{r=0}^\ell
     {\ell -r \choose k}
     {n-2r \choose \ell-r}
     S_{\bfa,r}
     u_1^\ell u_2^{\ell-k}.
   \]
  From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor \frac{n}{2} \rfloor$.
  We compute
  \begin{align*}
    m_{1^{(n)}}  F_{n\omega^\circ}^\Delta 
    &
    =
    \sum_{0 \le k \le \ell \le n}
    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
    {\ell -r \choose k}
    {n-2r \choose \ell-r}
    m_{2^{(r)},1^{(n-2r)}}
    u_1^\ell u_2^{\ell-k}
    \\
    &=
    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
    m_{2^{(r)},1^{(n-2r)}}
    u_1^r u_2^r
    \sum_{0 \le k \le \ell \le n}
    {\ell -r \choose k}
    {n-2r \choose \ell-r}
    u_1^{\ell-r} u_2^{\ell-r-k}
    \\
    &=
    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
    m_{2^{(r)},1^{(n-2r)}}
    u_1^r u_2^r
    F_{(n-2r)\omega^\circ}^{ge}.
  \end{align*}
  The last identity follows immediately by comparing with the formula for generic basis elements in \cite{RSW19}.
  \sayS{Thank you Dylan for fixing my stupidity.}
\end{proof}

We do not need the following two formulas but I think they are still neat.
\begin{conjecture}
  \begin{align*} 
    m_{1^{(n)}} F_{n\omega^\circ}^\Delta
    &=
    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
    s_{2^{(k)},1^{(n-2r)}}
    u_1^r u_2^r
    F_{(n-2r)\omega^\circ}^{tr}
    \\&=
    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
    e_{r,n-r}
    u_1^r u_2^r
    F_{(n-2r)\omega^\circ}^{gr}
  \end{align*}
\end{conjecture}

\bibliographystyle{amsalpha}
\bibliography{bibliography}

\end{document}

### 2021-07-25 dominance_regions.tex
Modified inequalities
Compatible pairs and greedy basis elements.

@@
   \end{align}
+  Maybe this one:
+  \begin{align}
+    (b c-\sqrt{b c (b c-4)})(x-\lambda_1)+2b(y-\lambda_2) & \geq0
+    \\
+    (b c+\sqrt{b c (b c-4)})(x-\lambda_1)-2b(y-\lambda_2) & \geq (b c+\sqrt{b c (b c-4)})b\lambda_2 
+    \\
+    -(b c-\sqrt{b c (b c-4)})(x-\lambda_1)-2b(y-\lambda_2)& \geq 2bc\lambda_1+(b c+\sqrt{b c (b c-4)})b\lambda_2
+    \\
+    -2c(x-\lambda_1)-(b c-\sqrt{b c (b c-4)})(y-\lambda_2)& \geq0
+    \\
+    2c(x-\lambda_1)-(b c+\sqrt{b c (b c-4)})(y-\lambda_2) & \geq -(b c+\sqrt{b c (b c-4)})c\lambda_1
+    \\
+    2c(x-\lambda_1)+(b c-\sqrt{b c (b c-4)})(y-\lambda_2) & \geq -(b c+\sqrt{b c (b c-4)})c\lambda_1-2cb\lambda_2
+  \end{align}
 
@@
   Here we identify the maximum possible support of its deformations.
+
+  It will be convenient later to have explicit expressions for the greedy basis elements so we recall here the combinatorial construction of their Laurent expansions.
+  For a $\bfg$-vector $\lambda\in\ZZ^2\setminus\ZZ_{\ge0}^2$, define the \emph{maximal Dyck path} $D_\lambda\subset\ZZ^2$ to be the lattice path with corner vertices $(0,0)$ and $(a_1,a_2):=\big([-\lambda_1+b\lambda_2]_+,[-\lambda_2]_+\big)$ which is maximal in the following sense:
+  \begin{itemize}
+    \item every lattice point of $D_\lambda$ lies below the line connecting the corner vertices;
+    \item any lattice point above $D_\lambda$ lies above the line connecting the corner vertices.
+  \end{itemize}
+  For $\lambda\in\ZZ_{\ge0}^2$, we take $D_\lambda$ to be the empty path at $(0,0)$.
+
+  We consider $D_\lambda$ to be the set of its edges ordered from $(0,0)$.
+  Write $H_\lambda,V_\lambda\subset D_\lambda$ for the subsets of horizontal and vertical edges, respectively.
+  According to the ordering of $D_\lambda$, we denote $H_\lambda=\{h_1,\ldots,h_{a_1}\}$ and $V_\lambda=\{v_1,\ldots,v_{a_2}\}$.
+  For edges $e,e'\in D_\lambda$ with $e\le e'$, write $ee'\subset D_\lambda$ for the shortest subpath of $D_\lambda$ containing $e$ and $e'$.
+  For edges $e,e'\in D_\lambda$ with $e'<e$, write $ee'\subset D_\lambda$ for the subset $ev_{a_2} \sqcup h_1e'$, which can be seen as the subpath traversing from the edge $e$ to the end of $D_\lambda$ and then continuing from the beginning of $D_\lambda$ to the edge $e'$.
+  For any subset $S\subset D_\lambda$, write $|S|_H:=|S\cap H_\lambda|$ and $|S|_V:=|S\cap V_\lambda|$; in particular, for $e,e'\in D_\lambda$, write $|ee'|_H:=|ee'\cap H_\lambda|$ and $|ee'|_V:=|ee'\cap V_\lambda|$.
+  \begin{definition}
+    A subset $S\subset D_\lambda$ is said to be \emph{compatible} if: for every $h\in S\cap H_\lambda$ and $v\in S\cap V_\lambda$, there exists an edge $e\in hv$ so that one of the following conditions is satisfied:
+    \begin{align*}
+      e\ne v \quad \text{and} \quad |he|_V=c|he\cap S|_H;\\
+      e\ne h \quad \text{and} \quad |ev|_H=b|ev\cap S|_V.
+    \end{align*}
+    Write $\cC_\lambda$ for the set of all compatible subsets $S\subset D_\lambda$.
+  \end{definition}
+
+  The \emph{greedy basis element} $x^{gr}_\lambda$ is then given by the following Laurent polynomial
+  \begin{equation}
+    \label{eq:greedy}
+    x^{gr}_\lambda=x_1^{\lambda_1}x_2^{\lambda_2} \sum_{S\in \cC_\lambda} x_1^{b(|V_\lambda|-|S|_V)} x_2^{c|S|_H}.
+  \end{equation}
 

### 2021-08-23 dominance_regions.tex
Added some preliminary results on dominant Dyck paths

@@
 \documentclass{amsart}
-\usepackage{amsmath,amssymb,latexsym,color}
+\usepackage{amsmath,amssymb,latexsym,color,ulem}
 \usepackage[margin=1in]{geometry}
@@
 \usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
+
+\usepackage[draft]{say}
+\newcommand{\sayDR}[1]{\say[DR]{\color{red}{\bf DR:}\;#1}}
+\newcommand{\saySS}[1]{\say[SS]{\color{blue}{\bf SS:}\;#1}}
 
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
 \newtheorem{remark}[theorem]{Remark}
@@
 \newcommand{\ot}{{\overline{t}}}
+\newcommand{\WA}{{W\!\!A}}
 \newcommand{\wt}{{\operatorname{wt}}}
+\newcommand{\Sh}{{\operatorname{Sh}}}
 
@@
   In particular, these calculations can be carried out for any acyclic cluster algebra.
+
+  Our calculations reveal the maximal support possible for a pointed basis which reproduces under mutations.
+  In particular, any candidate basis can be ruled out using these results based upon their support alone.
 
@@
     \\
-    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq \frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 
+    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
     \\
@@
     \\
-    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1
+    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
     \\
@@
   \begin{align}
-    (b c-\sqrt{b c (b c-4)})(x-\lambda_1)+2b(y-\lambda_2) & \geq0
+    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
     \\
-    (b c+\sqrt{b c (b c-4)})(x-\lambda_1)-2b(y-\lambda_2) & \geq (b c+\sqrt{b c (b c-4)})b\lambda_2 
+    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
     \\
-    -(b c-\sqrt{b c (b c-4)})(x-\lambda_1)-2b(y-\lambda_2)& \geq 2bc\lambda_1+(b c+\sqrt{b c (b c-4)})b\lambda_2
+    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
     \\
-    -2c(x-\lambda_1)-(b c-\sqrt{b c (b c-4)})(y-\lambda_2)& \geq0
+    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
     \\
-    2c(x-\lambda_1)-(b c+\sqrt{b c (b c-4)})(y-\lambda_2) & \geq -(b c+\sqrt{b c (b c-4)})c\lambda_1
+    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
     \\
-    2c(x-\lambda_1)+(b c-\sqrt{b c (b c-4)})(y-\lambda_2) & \geq -(b c+\sqrt{b c (b c-4)})c\lambda_1-2cb\lambda_2
+    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
   \end{align}
@@
 
-  \section{Ignore}
-  Rank 4 Skew-Symmetric $B$
+  \section{Bases From Compatible Pairs on Dyck Paths}
+  \sayDR{This is a bit of a repetition of the above introduction to Dyck paths, but with slightly different goals it seemed that a modified exposition was more appropriate.}
+  For $a_1,a_2\in\ZZ_{\ge0}$, choose a Dyck path $D$ in the lattice rectangle $[0,a_1]\times[0,a_2]$.
+  Consider $D$ as the set of its edges taken as a totally ordered set along the natural labeling from $(0,0)$ to $(a_1,a_2)$.
+  It may be convenient to identify $D$ with the ordered set $[1,a_1+a_2]$.
+  Write $D=D_1\sqcup D_2$, where $D_1$ is the set of horizontal edges and $D_2$ is the set of vertical edges.
+  Clearly, $|D_1|=a_1$ and $|D_2|=a_2$.
 
-  $P(\lambda)=\lambda^4 + a\lambda^3 + b\lambda^2 + c\lambda + 1$
+  Write $D^{max}=D^{max}[a_1,a_2]$ for the maximal Dyck path in the lattice rectangle $[0,a_1]\times[0,a_2]$, i.e.
+$D^{max}$ never crosses above the diagonal line joining $(0,0)$ to $(a_1,a_2)$ and any lattice point above $D_{max}$ also lies above the diagonal.
 
-  \begin{align*}
-    a
-    &=-b_{41}b_{21}b_{32}b_{43}-b_{31}b_{21}b_{32}-b_{41}b_{21}b_{42}-b_{41}b_{31}b_{43}-b_{42}b_{32}b_{43}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
-    c
-    &=-b_{21}b_{32}b_{43}b_{41}-b_{21}b_{32}b_{31}-b_{21}b_{42}b_{41}-b_{31}b_{43}b_{41}-b_{32}b_{43}b_{42}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
-    b
-    &=b_{41} b_{32} b_{32} b_{41} - b_{31} b_{42} b_{32} b_{41} - b_{31} b_{43} b_{21} b_{42} - b_{41} b_{32} b_{31} b_{42} + b_{31} b_{42} b_{31} b_{42} + b_{21} b_{43} b_{21} b_{43} - b_{21} b_{42} b_{31} b_{43}\\
-    &\quad - b_{21} b_{32} b_{31} - b_{31} b_{21} b_{32} - b_{21} b_{42} b_{41} - b_{31} b_{43} b_{41} - b_{32} b_{43} b_{42} - b_{41} b_{21} b_{42} - b_{41} b_{31} b_{43} - b_{42} b_{32} b_{43}\\
-    &\quad - 2 b_{21} b_{21} - 2 b_{31} b_{31} - 2 b_{32} b_{32} - 2 b_{41} b_{41} - 2 b_{42} b_{42} - 2 b_{43} b_{43} + 6\\
-    &=a+c-2+m\\
-    &=a+c-2+n^2\\
-    m
-    &=b_{41}b_{21}b_{32}b_{43}+b_{21}b_{32}b_{43}b_{41}+b_{41}b_{32}b_{32}b_{41}-b_{31}b_{42}b_{32}b_{41}-b_{31}b_{43}b_{21}b_{42}-b_{41}b_{32}b_{31}b_{42}+b_{31}b_{42}b_{31}b_{42}+b_{21}b_{43}b_{21}b_{43}\\
-    &\quad -b_{21}b_{42}b_{31}b_{43}\\
-    &=(b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43})^2\\
-    n
-    &=b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43}\\
-  \end{align*}
+  Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
 
-  Observe that $P(-1)=n^2$.
-  What happens when $\lambda=\frac{-a\pm\sqrt{a^2-4}}{2}$?  You get $P(\lambda)=(b-2)\lambda^2$.
+  For $e<e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
+  \begin{definition}
+    A subset $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ is \emph{compatible} if: for every $h\in H$ and $v\in V$ with $h<v$, there exists an edge $e\in hv$ such that one of the following conditions is satisfied
+    \[e\ne v \quad \text{and} \quad |he\cap D_2|=c|he\cap D_1|\]
+    \[e\ne h \quad \text{and} \quad |ev\cap D_1|=b|ev\cap D_2|\]
+    Write $\cC_D$ for the collection of all compatible subsets of $D$.
+  \end{definition}
+  \begin{remark}
+    In the construction of the greedy basis, it is necessary to consider $D$ as closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
+    When we wish to emphasize that this condition should be imposed, we denote the Dyck path $D$ instead by $D_\WA$.
+    For $(a_1,a_2)=(u_{m+1,+},u_{m,-})$ or $(u_{m,+},u_{m+1,-})$, the wrap around condition does not restrict compatibility and can thus safely be omitted.
+  \end{remark}
+
+  We associate to $D$ the element $x_D\in\ZZ_{\ge0}[x_1^{\pm1},x_2^{\pm1}]$ defined as follows
+  \[x_D:=x_1^{-a_1} x_2^{-a_2} \sum_{H\sqcup V\in\cC_D} x_1^{b|V|} x_2^{c|H|}.\]
+
+  \begin{theorem}[\cite{lee-li-zelevinsky}]
+    For $(a_1,a_2)=(u_{m+1,+},u_{m,-})$ or $(u_{m,+},u_{m+1,-})$ for $m\ge0$, the element $x_D[a_1,a_2]$ is a non-initial cluster variable.
+    Otherwise, the element $x_{D_\WA}$ is an element of the greedy basis
+  \end{theorem}
+
+  \begin{lemma}
+    Suppose there are two factorizations
+    \[x_D=x_1^{-a_1} x_2^{-a_2} \sum_{t=0}^{a_2}\sum_{k=0}^{a_1} \nu_{k,t} x_1^{bt}(1+x_2^c)^{a_1-k}=x_1^{-a_1} x_2^{-a_2} \sum_{s=0}^{a_1}\sum_{\ell=0}^{a_2} \theta_{s,\ell} x_2^{cs}(1+x_1^b)^{a_2-\ell},\]
+    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\Sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\Sh_D(H)|=\ell$.
+    Then 
+    \[\sum_{k=0}^{a_1-s} {a_1-k\choose s} \nu_{k,t}=\sum_{\ell=0}^{a_2-t} {a_2-\ell\choose t} \theta_{s,\ell}\]
+    for all possible $s$ and $t$.
+  \end{lemma}
+  \begin{question}
+    How do such expressions behave under mutations?
+  \end{question}
+
+  \begin{lemma}
+    Choose $a_1,a_2\in\ZZ_{\ge0}$.
+    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_D$ coincides with the corresponding standard monomial basis element.
+  \end{lemma}
+
+  Our main interest will be with the following Dyck paths.
+  \begin{definition}
+    \label{def:dominant Dyck path}
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, define the \emph{dominant Dyck path} $D^{dom}=D^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$.
+  \end{definition}
+
+  To understand the structure of the dominant Dyck paths, it will be convenient to consider their initial and final segments separately.
+  \begin{definition}
+    For $s>0$, define the \emph{Dyck path prefix} $\overrightarrow{D}^s$ as the maximal Dyck path with $s$ vertical edges starting from $(0,0)$ and terminating at $(d,s)$ while staying below the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, where $d=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
+    Call this $d$ the \emph{depth} of $s$.
+
+    For $t>0$, define the \emph{Dyck path suffix} $\overleftarrow{D}^t$ as the maximal Dyck path with $t$ horizontal edges starting from $(0,0)$ and terminating at $(t,h)$ while staying below the line $y-h=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-t)$, where $h=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
+    Call this $h$ the \emph{height} of $t$.
+    %        y = (a2 - a1*(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(2*self._r2))/(1-(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(self._r1*self._r2+sqrt(self._r1*self._r2*(self._r1*self._r2-4))))
+    %    corner = (y*(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(2*self._r1),y)
+  \end{definition}
+  \begin{remark}
+    There often exist multiple choices of $s$ with a given depth $d$ and multiple choices of $t$ with a given height $h$.
+  \end{remark}
+
+  The following result will be useful for showing that the Dyck path prefixes and suffixes behave properly.
+  \begin{lemma}
+    For $s>0$, the Dyck path prefix $\overrightarrow{D}^s$ ends in a vertical edge.
+    Similarly, for $t>0$, the Dyck path suffix $\overleftarrow{D}^t$ begins with a horizontal edge.
+  \end{lemma}
+
+  Apart from being the prefix and suffix for the dominant Dyck path, the Dyck paths $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ can be observed inside the maximal Dyck paths defining cluster variables as follows.
+  \begin{lemma}\mbox{}
+    \begin{itemize}
+      \item For $s>0$ and any $m \ge 1$ so that $s < u_{m+1,-}$, the Dyck path prefix $\overrightarrow{D}^s$ is an initial segment of the maximal Dyck path $D^{max}[u_{m,+},u_{m+1,-}]$.
+      \item For $t>0$ and any $m \ge 1$ so that $t < u_{m+1,+}$, the Dyck path suffix $\overleftarrow{D}^t$ is a final segment of the maximal Dyck path $D^{max}[u_{m+1,+},u_{m,-}]$.
+    \end{itemize}
+  \end{lemma}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item Choose a width $t>0$ and $a_1 \ge t$.
+        Then there exists a unique $s$ of depth $a_1-t$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_2=s+\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
+      \item Choose a height $s>0$ and $a_2 \ge s$.
+        Then there exists a unique $t$ of height $a_2-s$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_1=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil+t$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{remark}
+    The decomposition of $D^{dom}[a_1,a_2]$ as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is not uniquely determined by $a_1$ and $a_2$.
+    However, there exists at most two choices of $s$ and $t$ for which such a decomposition holds.
+  \end{remark}
+
+  \begin{lemma}
+    \label{le:floors and ceilings}
+    For any real number $x$ and any real number $r>1$, we have
+    \[\lfloor x\rfloor \le \left\lfloor \lceil xr \rceil \frac{1}{r} \right\rfloor \le \lceil x\rceil \qquad \text{and} \qquad \lfloor x\rfloor \le \left\lceil \lfloor xr \rfloor \frac{1}{r} \right\rceil \le \lceil x\rceil.\]
+  \end{lemma}
+  \begin{proof}
+    Observe that
+    \[xr\le \lceil xr \rceil < xr+1 \qquad \text{and} \qquad xr-1 < \lfloor xr \rfloor \le xr\]
+    and so
+    \[x\le \lceil xr \rceil \frac{1}{r} < x+\frac{1}{r} \qquad \text{and} \qquad x-\frac{1}{r} < \lfloor xr \rfloor \frac{1}{r} \le x.\]
+    Since $0<\frac{1}{r}<1$, the result follows.
+  \end{proof}
+
+  \begin{proposition}
+    \label{prop:dominant Dyck path decomposition}
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, the dominant Dyck path $D^{dom}[a_1,a_2]$ is the concatenation of $\overrightarrow{D}^s$ followed by $\overleftarrow{D}^t$ for any choice of $s$ and $t$ satisfying $a_2-s=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$ and $a_1-t=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
+    In this case, the pair of $s$ and $t$ will be one of the following:
+    \begin{align}
+      \label{eq:lower bounds}
+      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor\\
+      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil\\
+      \label{eq:upper bounds}
+      s=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rceil\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil
+    \end{align}
+    If two such decompositions exist, they will be of the form \eqref{eq:lower bounds} and \eqref{eq:upper bounds}.
+  \end{proposition}
+  \begin{remark}
+    The irrationality of the slopes defining the Dyck path prefixes and suffixes makes it difficult to predict for a given choice of $a_1$ and $a_2$ precisely which of these choice of $s$ and $t$ will produce the desired equalities.
+  \end{remark}
+  \begin{proof}
+    (In progress)
+
+    For $s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor$, by Lemma~\ref{le:floors and ceilings} we have
+    \[\left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor \le \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil\]
+    since $0<\frac{bc-\sqrt{bc(bc-4)}}{2c}<1$.
+    It follows that
+    \[ a_1 - \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le a_1 - \left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor\]
+    and so
+    \[ \left\lfloor \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rfloor \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rceil\]
+    with one of these inequalities being an equality.
+
+    If the left hand inequality is an equality, we take $t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor$.
+
+    The desired equalities can be rewritten in the form 
+    \[s=a_2-\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil=\left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
+    and
+    \[t=a_1-\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil=\left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
+    Combining these, we seek $s$ and $t$ satisfying
+    \[s=\left\lfloor a_2 - \left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
+    and
+    \[t=\left\lfloor a_1 - \left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
+  \end{proof}
 

### 2021-08-24 dominance_regions.tex
Added intersection point.

@@
   Write $D^{max}=D^{max}[a_1,a_2]$ for the maximal Dyck path in the lattice rectangle $[0,a_1]\times[0,a_2]$, i.e.
-$D^{max}$ never crosses above the diagonal line joining $(0,0)$ to $(a_1,a_2)$ and any lattice point above $D_{max}$ also lies above the diagonal.
+$D^{max}$ never crosses above the diagonal line joining $(0,0)$ to $(a_1,a_2)$ and any lattice point above $D^{max}$ also lies above the diagonal.
 
@@
   \end{definition}
+  \begin{remark}
+    \label{rem:intersection}
+    The lines in the definition above meet at the point $\left( \frac{2ba_2-\big(bc-\sqrt{bc(bc-4)}\big)a_1}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2-2ca_1}{2\sqrt{bc(bc-4)}} \right)$.
+  \end{remark}
 
@@
 
+  The following result describes the possible decomposition of the dominant Dyck path into its prefix and suffix subpaths.
+  The intersection point from Remark~\ref{rem:intersection} is a useful point of reference.
   \begin{proposition}

### 2021-08-27 dominance_regions.tex
Dyck path mutations

@@
   For $a_1,a_2\in\ZZ_{\ge0}$, choose a Dyck path $D$ in the lattice rectangle $[0,a_1]\times[0,a_2]$.
+  When we wish to emphasize the upper right bounding corner we will write $D[a_1,a_2]$.
   Consider $D$ as the set of its edges taken as a totally ordered set along the natural labeling from $(0,0)$ to $(a_1,a_2)$.
@@
 
+  Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
+
   Write $D^{max}=D^{max}[a_1,a_2]$ for the maximal Dyck path in the lattice rectangle $[0,a_1]\times[0,a_2]$, i.e.
@@
 
-  Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
+  \begin{definition}
+    Call a Dyck path $D$ 
+    \begin{itemize}
+      \item \emph{horizontally-adapted to $b$} if no vertical edge of $D$ is immediately preceded by more than $b$ horizontal edges;
+      \item \emph{vertically-adapted to $c$} if no horizontal edge of $D$ is immediately followed by more than $c$ vertical edges.
+    \end{itemize}
+  \end{definition}
+
+  \begin{definition}
+    \label{def:Dyck path mutations}
+    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_V(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge, together with the $\ell$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-\ell$ vertical edges.
+
+    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_H(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge, together with the $\ell$ vertical edges which immediately follow it, by $c-\ell$ horizontal edges followed by a vertical edge.
+  \end{definition}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item If $a_1 < b a_2$, then $\mu_V\big(D^{max}[a_1,a_2]\big)=D^{max}[a_2,ba_2-a_1]$.
+      \item If $a_2 < c a_1$, then $\mu_H\big(D^{max}[a_1,a_2]\big)=D^{max}[ca_1-a_2,a_1]$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    The proof is identical to the proof of \cite[Lemma 2.4]{rupel} with appropriate notation changes.
+  \end{proof}
 
@@
     For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, define the \emph{dominant Dyck path} $D^{dom}=D^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$.
+
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1,-a_2+ca_1)\in\cI'$, define the \emph{dual dominant Dyck path} $D^{dom^\vee}=D^{dom^\vee}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2c}(x-a_1)$.
   \end{definition}
@@
     Call this $h$ the \emph{height} of $t$.
-    %        y = (a2 - a1*(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(2*self._r2))/(1-(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(self._r1*self._r2+sqrt(self._r1*self._r2*(self._r1*self._r2-4))))
-    %    corner = (y*(self._r1*self._r2-sqrt(self._r1*self._r2*(self._r1*self._r2-4)))/(2*self._r1),y)
   \end{definition}
@@
   \end{remark}
+
+  \begin{lemma}
+    For any $s,t>0$, the Dyck path prefix $\overrightarrow{D}^s$ and Dyck path suffix $\overleftarrow{D}^t$ are both horizontally-adapted to $b$ and vertically-adapted to $c$.
+  \end{lemma}
+
+  \begin{theorem}
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_H\big(D^{dom}[a_1,a_2]\big)=D^{dom^\vee}[a_2,ba_2-a_1]$ and $\mu_V\big(D^{dom}[a_1,a_2]\big)=D^{dom^\vee}[ca_1-a_2,a_1]$.
+  \end{theorem}
 
@@
 
+  \begin{thebibliography}{XXX}
+    \bibitem{rupel}
+      D.~Rupel: Noncommutative Laurent Phenomenon
+  \end{thebibliography}
+
 \end{document}

### 2021-08-28 dominance_regions.tex
Proof of dominant Dyck path recursion

--- 2021-08-24 dominance_regions.tex
@@
 
-  Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
+  \begin{definition}
+    Call a Dyck path $D$ 
+    \begin{itemize}
+      \item \emph{horizontally-adapted to $b$} if no vertical edge of $D$ is immediately preceded by more than $b$ horizontal edges;
+      \item \emph{vertically-adapted to $c$} if no horizontal edge of $D$ is immediately followed by more than $c$ vertical edges.
+    \end{itemize}
+  \end{definition}
+
+  \begin{definition}
+    \label{def:Dyck path mutations}
+    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_{V,b}(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge, together with the $\ell$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-\ell$ vertical edges.
+
+    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_{H,c}(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge, together with the $\ell$ vertical edges which immediately follow it, by $c-\ell$ horizontal edges followed by a vertical edge.
+  \end{definition}
+  \begin{remark}
+    Observe that $\mu_{H,a}$ and $\mu_{V,a}$ are inverse for any $a\ge1$.
+  \end{remark}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item If $a_1 < b a_2$, then $\mu_{V,b}\big(D^{max}[a_1,a_2]\big)=D^{max}[a_2,ba_2-a_1]$.
+      \item If $a_2 < c a_1$, then $\mu_{H,c}\big(D^{max}[a_1,a_2]\big)=D^{max}[ca_1-a_2,a_1]$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    The proof is identical to the proof of \cite[Lemma 2.4]{rupel} with appropriate notation changes.
+  \end{proof}
 
@@
     Choose $a_1,a_2\in\ZZ_{\ge0}$.
-    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_D$ coincides with the corresponding standard monomial basis element.
+    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_{D^{st}}$ coincides with the corresponding standard monomial basis element.
   \end{lemma}
@@
     For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, define the \emph{dominant Dyck path} $D^{dom}=D^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$.
+
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_2,-a_1+ca_2)\in\cI'$, define the \emph{dual dominant Dyck path} $D^{dom^\vee}=D^{dom^\vee}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2c}(x-a_1)$.
   \end{definition}
@@
   \end{remark}
+
+  \begin{lemma}
+    For any $s,t>0$, the Dyck path prefix $\overrightarrow{D}^s$ and Dyck path suffix $\overleftarrow{D}^t$ are both horizontally-adapted to $b$ and vertically-adapted to $c$.
+  \end{lemma}
+
+  \begin{theorem}
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{V,b}\big(D^{dom}[a_1,a_2]\big)=D^{dom^\vee}[a_2,ba_2-a_1]$ and $\mu_{H,c}\big(D^{dom}[a_1,a_2]\big)=D^{dom^\vee}[ca_1-a_2,a_1]$.
+  \end{theorem}
+  \begin{proof}
+    We prove the result for $\mu_{H,c}$ as the result for $\mu_{V,b}$ immediately follows from $\mu_{H,b}$ being its inverse.
+    Write $D'$ for the Dyck path $\mu_{H,c}\big(D^{dom}[a_1,a_2]\big)$ and observe that by construction $D'$ has $ca_1-a_2$ horizontal edges and $a_1$ vertical edges.
+    Write $v'_1,\ldots,v'_{a_1}$ for the vertical edges of $D'$ with $v'_r$ immediately preceded by $\ell_r$ horizontal edges.
+    We have to show (i) that every lattice point on $D'$ stays below the lines 
+    \[y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x \qquad \text{and} \qquad y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)\]
+    while (ii) any lattice point above $D'$ is also above one of these lines.
+
+    If there exists $t$ so that $v'_t$ passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$, then
+    \[ \frac{t}{\sum\limits_{r=1}^t \ell_r} > \frac{bc+\sqrt{bc(bc-4)}}{2c} \]
+    or, rearranging, we have
+    \[ \frac{\sum\limits_{r=1}^t \ell_r}{t} < \frac{2c}{bc+\sqrt{bc(bc-4)}} = \frac{bc-\sqrt{bc(bc-4)}}{2b} \]
+    or
+    \[ \frac{bc+\sqrt{bc(bc-4)}}{2b} < \frac{ct-\sum\limits_{r=1}^t \ell_r}{t} = \frac{\sum\limits_{r=1}^t (c-\ell_r)}{t}. \]
+    But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, contrary to the definition.
+
+    If there exists $t$ so that $v'_t$ passes above the line $y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)$, then
+    \[ \frac{bc-\sqrt{bc(bc-4)}}{2c} > \frac{a_1-t}{ca_1-a_2-\sum\limits_{r=1}^t \ell_r} \]
+    or, rearranging, we have
+    \[ \frac{ca_1-a_2-\sum\limits_{r=1}^t \ell_r}{a_1-t} > \frac{2c}{bc-\sqrt{bc(bc-4)}} = \frac{bc+\sqrt{bc(bc-4)}}{2b} \]
+    or
+    \[ \frac{bc-\sqrt{bc(bc-4)}}{2b} > \frac{ c(a_1-t) - \big(ca_1-a_2-\sum\limits_{r=1}^t \ell_r\big)}{a_1-t} = \frac{a_2-\sum\limits_{r=1}^t (c-\ell_r)}{a_1-t}. \]
+    But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$, contrary to the definition.
+
+    This proves (i), analogous calculations establish (ii). 
+  \end{proof}
 

### 2021-08-28 dominance_regions.tex
Something new

@@
   \subsection{Deformation Support}
-  The greedy basis of Lee, Li, and Zelevinsky \cite{???} can be defined as the positive pointed basis with minimal support.
+  The greedy basis of Lee, Li, and Zelevinsky \cite{lee-li-zelevinsky} can be defined as the positive pointed basis with minimal support.
   Here we identify the maximum possible support of its deformations.
@@
   \begin{theorem}[\cite{lee-li-zelevinsky}]
-    For $(a_1,a_2)=(u_{m+1,+},u_{m,-})$ or $(u_{m,+},u_{m+1,-})$ for $m\ge0$, the element $x_D[a_1,a_2]$ is a non-initial cluster variable.
-    Otherwise, the element $x_{D_\WA}$ is an element of the greedy basis
+    For $(a_1,a_2)=(u_{m+1,+},u_{m,-})$ or $(u_{m,+},u_{m+1,-})$ for $m\ge0$, the element $x_{D^{max}[a_1,a_2]}$ is a non-initial cluster variable.
+    Otherwise, the element $x_{D^{max}_\WA[a_1,a_2]}$ is an element of the greedy basis
   \end{theorem}
@@
     \label{rem:intersection}
-    The lines in the definition above meet at the point $\left( \frac{2ba_2-\big(bc-\sqrt{bc(bc-4)}\big)a_1}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2-2ca_1}{2\sqrt{bc(bc-4)}} \right)$.
+    The lines defining $D^{dom}[a_1,a_2]$ meet at the point 
+    \[m_{a_1,a_2}:=\left( \frac{2ba_2-\big(bc-\sqrt{bc(bc-4)}\big)a_1}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2-2ca_1}{2\sqrt{bc(bc-4)}} \right).\]
   \end{remark}
@@
   \begin{definition}
-    For $s>0$, define the \emph{Dyck path prefix} $\overrightarrow{D}^s$ as the maximal Dyck path with $s$ vertical edges starting from $(0,0)$ and terminating at $(d,s)$ while staying below the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, where $d=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
+    For $s>0$, define the \emph{Dyck path prefix} $\overrightarrow{D}^s$ as the maximal Dyck path with $s$ vertical edges starting from $(0,0)$ and terminating at $(d,s)$ while staying below the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, where $d=d_s=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
     Call this $d$ the \emph{depth} of $s$.
 
-    For $t>0$, define the \emph{Dyck path suffix} $\overleftarrow{D}^t$ as the maximal Dyck path with $t$ horizontal edges starting from $(0,0)$ and terminating at $(t,h)$ while staying below the line $y-h=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-t)$, where $h=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
+    For $t>0$, define the \emph{Dyck path suffix} $\overleftarrow{D}^t$ as the maximal Dyck path with $t$ horizontal edges starting from $(0,0)$ and terminating at $(t,h)$ while staying below the line $y-h=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-t)$, where $h=h_t=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
     Call this $h$ the \emph{height} of $t$.
@@
 
+  The following result will be useful for showing that the Dyck path prefixes and suffixes behave properly.
+  \begin{lemma}
+    For $s>0$, the Dyck path prefix $\overrightarrow{D}^s$ ends in a vertical edge.
+    Similarly, for $t>0$, the Dyck path suffix $\overleftarrow{D}^t$ begins with a horizontal edge.
+  \end{lemma}
+
+  \begin{lemma}
+    For $s,t>0$, $\overrightarrow{D}^s=D^{dom}[d_s,s]$ and $\overleftarrow{D}^t=D^{dom}[t,h_t]$.
+  \end{lemma}
+  \begin{proof}
+    Is this obvious?
+    %Following Remark~\ref{rem:intersection}, the intersection point of the lines defining $D^{dom}[d_s,s]$ is given by
+    %\[m_{d_s,s}=\left( \frac{2bs-\big(bc-\sqrt{bc(bc-4)}\big)d_s}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)s-2cd_s}{2\sqrt{bc(bc-4)}} \right).\]
+    %By definition of $d_s$, we have
+    %\[\frac{\big(bc+\sqrt{bc(bc-4)}\big)s-2cd_s}{2\sqrt{bc(bc-4)}} \le \frac{\big(bc+\sqrt{bc(bc-4)}\big)s-\big(bc-\sqrt{bc(bc-4)}\big)s}{2\sqrt{bc(bc-4)}} = s\]
+  \end{proof}
+
   \begin{lemma}
@@
   \end{lemma}
+  \begin{proof}
+    Observe that $\frac{c}{2}<\frac{bc+\sqrt{bc(bc-4)}}{2b}<c$.
+    This shows that $\overrightarrow{D}^s$ cannot contain more than $c$ consecutive vertical edges following a horizontal edge and so $\overrightarrow{D}^s$ must be vertically-adapted to $c$.
+    In addition, we see that $\overrightarrow{D}^s$ can only contain consecutive horizontal edges if $c=1$, in which case there are at most two consecutive horizontal edges preceding any vertical edge.
+    But, since we assume $bc\ge4$, that would imply $b\ge4$ and so $\overrightarrow{D}^s$ must be horizontally-adapted to $b$.
+  \end{proof}
 
@@
   \end{proof}
-
-  The following result will be useful for showing that the Dyck path prefixes and suffixes behave properly.
-  \begin{lemma}
-    For $s>0$, the Dyck path prefix $\overrightarrow{D}^s$ ends in a vertical edge.
-    Similarly, for $t>0$, the Dyck path suffix $\overleftarrow{D}^t$ begins with a horizontal edge.
-  \end{lemma}
 
@@
   \begin{thebibliography}{XXX}
+
+    \bibitem{lee-li-zelevinsky}
+      K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014), pp.~57--82.
+
     \bibitem{rupel}
-      D.~Rupel: Noncommutative Laurent Phenomenon
+      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
+Algebraic Combinatorics, \textbf{2} (2019) no.
+6, pp.~1239--1273.
+\href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
   \end{thebibliography}

### 2021-09-06 dominance_regions.tex
Some progress towards proving the recursions for compatible pairs on dominant Dyck paths.

@@
 \usepackage{amsmath,amssymb,latexsym,color,ulem}
-\usepackage[margin=1in]{geometry}
+\usepackage[margin=1.5in]{geometry}
 \usepackage{tikz}
@@
   It may be convenient to identify $D$ with the ordered set $[1,a_1+a_2]$.
-  Write $D=D_1\sqcup D_2$, where $D_1$ is the set of horizontal edges and $D_2$ is the set of vertical edges.
+  Write $D=D_1\sqcup D_2$, where $D_1=\{h_1,\ldots,h_{a_1}\}$ is the set of horizontal edges and $D_2=\{v_1,\ldots,v_{a_2}\}$ is the set of vertical edges.
   Clearly, $|D_1|=a_1$ and $|D_2|=a_2$.
@@
   Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
+  Given a Dyck path $D=D_1\sqcup D_2$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $\overline{D}=\overline{D}_1\sqcup \overline{D}_2$ for the Dyck path in the lattice rectangle $[0,a_2]\times[0,a_1]$ with $\overline{D}_1=a_1+a_2+1-D_2$ and $\overline{D}_2=a_1+a_2+1-D_1$.
+  This operation can be visualized as transposing the Dyck path.
+
+  Given any quantity or object $P$ whose definition depends on $b$ and $c$, write $P^\vee$ for the same quantity or object defined with $b$ and $c$ interchanged.
+  In particular, we have $u^\vee_{m,\varepsilon}=u_{m,-\varepsilon}$ for any $m$ and any $\varepsilon=\pm1$.
 
@@
   \begin{lemma}\mbox{}
+    \label{le:maximal Dyck path recursion}
     \begin{enumerate}
@@
   \begin{proof}
-    The proof is identical to the proof of \cite[Lemma 2.4]{rupel} with appropriate notation changes.
+    The proof is identical to the proof of \cite[Lemma 2.4]{rupel} with appropriate notation changes, c.f. Theorem~\ref{th:dominant Dyck path recursion} below.
   \end{proof}
 
-  For $e<e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
+  As an immediate consequence, we determine the structure of certain maximal Dyck paths.
+  We introduce the following notation for convenience:
+  \[d_m:=\begin{cases} b & \text{if $m$ is even;}\\ c & \text{if $m$ is odd;}\end{cases} \qquad \text{and} \qquad d^\vee_m:=\begin{cases} c & \text{if $m$ is even;}\\ b & \text{if $m$ is odd;}\end{cases}\]
+  The following was proven in \cite[Corollary 2.6]{rupel} and follows by a simple induction using Lemma~\ref{le:maximal Dyck path recursion}.
+  \begin{corollary}
+    Assume $b,c\ge2$ (this can be dropped with extra notation and slight modification).
+    Then, for $\varepsilon=\pm1$ and $m\ge1$, the maximal Dyck path $D_{m,\varepsilon}:=D^{max}[u_{m,\varepsilon},u_{m-1,-\varepsilon}]$ can be constructed as follows:
+    \begin{itemize}
+      \item $D_{1,\varepsilon}$ consists of a single horizontal edge;
+      \item $D_{2,\varepsilon}$ consists of $d_2$ horizontal edges followed by a vertical edge;
+      \item for $m\ge3$, $D_{m,\varepsilon}$ consists of $d_m-1$ copies of $D_{m-1,\varepsilon}$ followed by a copy of $D_{m-1,\varepsilon}$ with its first $D_{m-2,\varepsilon}$ removed;
+    \end{itemize}
+    and the maximal Dyck path $\overline{D}^\vee_{m,\varepsilon}:=D^{max}[u_{m-1,\varepsilon},u_{m,-\varepsilon}]$ can be constructed as follows:
+    \begin{itemize}
+      \item $\overline{D}^\vee_{1,\varepsilon}$ consists of a single vertical edge;
+      \item $\overline{D}^\vee_{2,\varepsilon}$ consists of a horizontal edge followed by $d^\vee_2$ vertical edges;
+      \item for $m\ge3$, $\overline{D}^\vee_{m,\varepsilon}$ consists of a copy of $\overline{D}^\vee_{m-1,\varepsilon}$ with its last $\overline{D}^\vee_{m-2,\varepsilon}$ removed followed by $d^\vee_m-1$ copies of $\overline{D}^\vee_{m-1,\varepsilon}$.
+    \end{itemize}
+  \end{corollary}
+
+  For $e \le e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
+  When $e=e'$, we take $ee'$ to be the subpath consisting of only the edge $e$.
+  \begin{definition}
+    For $H\sqcup V\subset D$ with $H\subset D_0$ and $V\subset D_2$ together with a subpath $ee'\subset D$, define the \emph{horizontal shadow statistic}:
+    \begin{equation}
+      \label{eq:horizontal shadow statistic}
+      f_H(ee')=-|ee'\cap D_2|+c|ee'\cap H|
+    \end{equation}
+    and the \emph{vertical shadow statistic}:
+    \begin{equation}
+      \label{eq:vertical shadow statistic}
+      f_V(ee')=-|ee'\cap D_1|+b|ee'\cap V|.
+    \end{equation}
+  \end{definition}
+  \begin{remark}
+    Observe that the shadow statistics are additive with respect to concatenation of subpaths.
+  \end{remark}
   \begin{definition}
     A subset $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ is \emph{compatible} if: for every $h\in H$ and $v\in V$ with $h<v$, there exists an edge $e\in hv$ such that one of the following conditions is satisfied
-    \[e\ne v \quad \text{and} \quad |he\cap D_2|=c|he\cap D_1|\]
-    \[e\ne h \quad \text{and} \quad |ev\cap D_1|=b|ev\cap D_2|\]
+    \[\tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0\]
+    \[\tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0\]
     Write $\cC_D$ for the collection of all compatible subsets of $D$.
@@
 
+  \begin{definition}
+    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$, define the \emph{shadow paths} as follows:
+    \begin{itemize}
+      \item For $h\in D_1$, write $D(h;H)$ for the shortest subpath $he \subset D$ with $f_H(he)=0$ or, if no such subpath exists, set $D(h;H)=hv_{a_2}$.
+      \item For $h\in D_1$, write $D_\WA(h;H)$ for the shortest subpath $he \subset D_\WA$ with $f_H(he)=0$ or, if no such subpath exists, set $D_\WA(h;H)=D$.
+      \item For $v\in D_2$, write $D(v;V)$ for the shortest subpath $ev \subset D$ with $f_V(ev)=0$ or, if no such subpath exists, set $D(v;V)=h_1 v$.
+      \item For $v\in D_2$, write $D_\WA(v;V)$ for the shortest subpath $ev \subset D_\WA$ with $f_V(ev)=0$ or, if no such subpath exists, set $D_\WA(v;V)=D$.
+    \end{itemize}
+  \end{definition}
+
+  \begin{lemma}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $h\in H$, take $he$ to be either the path $D(h;H)$ or $D_\WA(h;H)$.
+        The following hold:
+        \begin{enumerate}
+          \item for any proper subpath $he'\subsetneq he$, we have $f_H(he')>0$;
+          \item for any proper subpath $e'e\subsetneq he$, we have $f_H(e'e)<0$;
+          \item $e\in V$.
+        \end{enumerate}
+      \item For $v\in V$, take $ev$ to be either the path $D(v;V)$ or $D_\WA(v;V)$.
+        The following hold:
+        \begin{enumerate}
+          \item for any proper subpath $e'v\subsetneq ev$, we have $f_V(e'v)>0$;
+          \item for any proper subpath $ee'\subsetneq ev$, we have $f_V(ee')<0$;
+          \item $e\in H$.
+        \end{enumerate}
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    We prove (1), the proof of (2) is similar.
+    To see (a), note that as $e'$ traverses the path $he$ from $h$ to $e$, the value of $f_H(he')$ either increases by $c$, stays constant, or decreases by 1.
+    Since $h\in H$, we have $f_H(hh)=c>0$ and so the value of $f_H(he')$ stays positive until it first becomes 0 when $e'=e$.
+    Part (b) then follows from the additivity of $f_H$ and part (c) is the case when $e'=e$ here.
+  \end{proof}
+
   We associate to $D$ the element $x_D\in\ZZ_{\ge0}[x_1^{\pm1},x_2^{\pm1}]$ defined as follows
@@
   \begin{theorem}[\cite{lee-li-zelevinsky}]
-    For $(a_1,a_2)=(u_{m+1,+},u_{m,-})$ or $(u_{m,+},u_{m+1,-})$ for $m\ge0$, the element $x_{D^{max}[a_1,a_2]}$ is a non-initial cluster variable.
+    For $(a_1,a_2)=(u_{m,+},u_{m-1,-})$ or $(u_{m-1,+},u_{m,-})$ for $m\ge1$, the element $x_{D^{max}[a_1,a_2]}$ is a non-initial cluster variable.
     Otherwise, the element $x_{D^{max}_\WA[a_1,a_2]}$ is an element of the greedy basis
@@
   \end{remark}
+  \sayDR{ToDo: describe the analogue of Corollary 7.5 for the Dyck path prefixes and suffixes.}
 
@@
   \begin{theorem}
+    \label{th:dominant Dyck path recursion}
     For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{V,b}\big(D^{dom}[a_1,a_2]\big)=D^{dom^\vee}[a_2,ba_2-a_1]$ and $\mu_{H,c}\big(D^{dom}[a_1,a_2]\big)=D^{dom^\vee}[ca_1-a_2,a_1]$.
@@
     \begin{itemize}
-      \item For $s>0$ and any $m \ge 1$ so that $s < u_{m+1,-}$, the Dyck path prefix $\overrightarrow{D}^s$ is an initial segment of the maximal Dyck path $D^{max}[u_{m,+},u_{m+1,-}]$.
-      \item For $t>0$ and any $m \ge 1$ so that $t < u_{m+1,+}$, the Dyck path suffix $\overleftarrow{D}^t$ is a final segment of the maximal Dyck path $D^{max}[u_{m+1,+},u_{m,-}]$.
+      \item For $s>0$ and any $m \ge 2$ so that $s < u_{m,-}$, the Dyck path prefix $\overrightarrow{D}^s$ is an initial segment of the maximal Dyck path $D^{max}[u_{m-1,+},u_{m,-}]$.
+      \item For $t>0$ and any $m \ge 2$ so that $t < u_{m,+}$, the Dyck path suffix $\overleftarrow{D}^t$ is a final segment of the maximal Dyck path $D^{max}[u_{m,+},u_{m-1,-}]$.
     \end{itemize}
+  \end{lemma}
+
+  This can be made more precise as follows.
+  \begin{lemma}
+    For $s>0$, choose $m\ge2$ minimal so that $s < u_{m,-}$
   \end{lemma}
@@
 
+  \begin{definition}
+    Suppose $D^{dom}[a_1,a_2]$ decomposes as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$.
+    Call a pair of subsets $H \sqcup V$ \emph{piecewise compatible} if the intersections with $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ are compatible on the subpaths.
+  \end{definition}
+
+  \begin{theorem}
+    Suppose $H \sqcup V$ is a piecewise compatible subset of $D^{dom}[a_1,a_2]$.
+    \begin{itemize}
+      \item If the last vertical edge of $\overrightarrow{D}^s$ is contained in $V$, then $H \sqcup V$ is compatible.
+      \item If the first horizontal edge of $\overleftarrow{D}^t$ is contained in $H$, then $H \sqcup V$ is compatible.
+    \end{itemize}
+  \end{theorem}
+
   \begin{thebibliography}{XXX}

### 2021-09-07 dominance_regions.tex
Some notation changes and other edits

@@
 \newcommand{\ol}[1]{{\overline{#1}}}
+\newcommand{\vv}[1]{{{}^\vee \! #1}}
 
@@
   Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
-  Given a Dyck path $D=D_1\sqcup D_2$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $\overline{D}=\overline{D}_1\sqcup \overline{D}_2$ for the Dyck path in the lattice rectangle $[0,a_2]\times[0,a_1]$ with $\overline{D}_1=a_1+a_2+1-D_2$ and $\overline{D}_2=a_1+a_2+1-D_1$.
+  Given a Dyck path $D=D_1\sqcup D_2$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $\bar{D}=\bar{D}_1 \sqcup \bar{D}_2$ for the Dyck path in the lattice rectangle $[0,a_2]\times[0,a_1]$ with $\bar{D}_1=a_1+a_2+1-D_2$ and $\bar{D}_2=a_1+a_2+1-D_1$.
   This operation can be visualized as transposing the Dyck path.
 
-  Given any quantity or object $P$ whose definition depends on $b$ and $c$, write $P^\vee$ for the same quantity or object defined with $b$ and $c$ interchanged.
-  In particular, we have $u^\vee_{m,\varepsilon}=u_{m,-\varepsilon}$ for any $m$ and any $\varepsilon=\pm1$.
+  Given any quantity or object $P$ whose definition depends on $b$ and $c$, write $\vv{P}$ for the same quantity or object defined with $b$ and $c$ interchanged.
+  In particular, we have $\vv{u}_{m,\varepsilon}=u_{m,-\varepsilon}$ for any $m$ and any $\varepsilon=\pm1$.
 
@@
   We introduce the following notation for convenience:
-  \[d_m:=\begin{cases} b & \text{if $m$ is even;}\\ c & \text{if $m$ is odd;}\end{cases} \qquad \text{and} \qquad d^\vee_m:=\begin{cases} c & \text{if $m$ is even;}\\ b & \text{if $m$ is odd;}\end{cases}\]
+  \[d_m:=\begin{cases} b & \text{if $m$ is even;}\\ c & \text{if $m$ is odd;}\end{cases} \qquad \text{and} \qquad \vv{d}_m:=\begin{cases} c & \text{if $m$ is even;}\\ b & \text{if $m$ is odd;}\end{cases}\]
   The following was proven in \cite[Corollary 2.6]{rupel} and follows by a simple induction using Lemma~\ref{le:maximal Dyck path recursion}.
@@
     Assume $b,c\ge2$ (this can be dropped with extra notation and slight modification).
-    Then, for $\varepsilon=\pm1$ and $m\ge1$, the maximal Dyck path $D_{m,\varepsilon}:=D^{max}[u_{m,\varepsilon},u_{m-1,-\varepsilon}]$ can be constructed as follows:
+    Then, for $\varepsilon=\pm1$ and $m\ge1$, the maximal Dyck path $D^{m,\varepsilon}:=D^{max}[u_{m,\varepsilon},u_{m-1,-\varepsilon}]$ can be constructed as follows:
     \begin{itemize}
-      \item $D_{1,\varepsilon}$ consists of a single horizontal edge;
-      \item $D_{2,\varepsilon}$ consists of $d_2$ horizontal edges followed by a vertical edge;
-      \item for $m\ge3$, $D_{m,\varepsilon}$ consists of $d_m-1$ copies of $D_{m-1,\varepsilon}$ followed by a copy of $D_{m-1,\varepsilon}$ with its first $D_{m-2,\varepsilon}$ removed;
+      \item $D^{1,\varepsilon}$ consists of a single horizontal edge;
+      \item $D^{2,\varepsilon}$ consists of $d_2$ horizontal edges followed by a vertical edge;
+      \item for $m\ge3$, $D_{m,\varepsilon}$ consists of $d_m - 1$ copies of $D^{m-1,\varepsilon}$ followed by a copy of $D^{m-1,\varepsilon}$ with its first $D^{m-2,\varepsilon}$ removed;
     \end{itemize}
-    and the maximal Dyck path $\overline{D}^\vee_{m,\varepsilon}:=D^{max}[u_{m-1,\varepsilon},u_{m,-\varepsilon}]$ can be constructed as follows:
+    and the maximal Dyck path $\vv{\bar{D}}^{m,\varepsilon}:=D^{max}[u_{m-1,\varepsilon},u_{m,-\varepsilon}]$ can be constructed as follows:
     \begin{itemize}
-      \item $\overline{D}^\vee_{1,\varepsilon}$ consists of a single vertical edge;
-      \item $\overline{D}^\vee_{2,\varepsilon}$ consists of a horizontal edge followed by $d^\vee_2$ vertical edges;
-      \item for $m\ge3$, $\overline{D}^\vee_{m,\varepsilon}$ consists of a copy of $\overline{D}^\vee_{m-1,\varepsilon}$ with its last $\overline{D}^\vee_{m-2,\varepsilon}$ removed followed by $d^\vee_m-1$ copies of $\overline{D}^\vee_{m-1,\varepsilon}$.
+      \item $\vv{\bar{D}}^{1,\varepsilon}$ consists of a single vertical edge;
+      \item $\vv{\bar{D}}^{2,\varepsilon}$ consists of a horizontal edge followed by $\vv{d}_2$ vertical edges;
+      \item for $m\ge3$, $\vv{\bar{D}}^{m,\varepsilon}$ consists of a copy of $\vv{\bar{D}}^{m-1,\varepsilon}$ with its last $\vv{\bar{D}}^{m-2,\varepsilon}$ removed followed by $\vv{d}_m - 1$ copies of $\vv{\bar{D}}^{m-1,\varepsilon}$.
     \end{itemize}
@@
 
+  \subsection{Compatibility}
   For $e \le e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
@@
   \begin{definition}
-    For $H\sqcup V\subset D$ with $H\subset D_0$ and $V\subset D_2$ together with a subpath $ee'\subset D$, define the \emph{horizontal shadow statistic}:
+    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ together with a subpath $ee'\subset D$, define the \emph{horizontal shadow statistic}:
     \begin{equation}
@@
   \begin{definition}
-    A subset $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ is \emph{compatible} if: for every $h\in H$ and $v\in V$ with $h<v$, there exists an edge $e\in hv$ such that one of the following conditions is satisfied
-    \[\tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0\]
-    \[\tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0\]
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    For $h\in H$ and $v\in V$ with $h<v$, call the path $hv$ \emph{compatible} if there exists an edge $e\in hv$ such that one of the following conditions is satisfied:
+    \[\tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0;\]
+    \[\tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0.\]
+    Call the subset $H\sqcup V$ \emph{compatible} if every path $hv$ with $h\in H$ and $v\in V$ is compatible.
     Write $\cC_D$ for the collection of all compatible subsets of $D$.
+    Given a subset $H\subset D_1$, write $\cC_D(H)$ for the collection of all $V\subset D_2$ for which $H\sqcup V\in\cC_D$.
+    Define $\cC_D(V)$ for $V\subset D_2$ similarly.
   \end{definition}
   \begin{remark}
-    In the construction of the greedy basis, it is necessary to consider $D$ as closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
+    In the construction of the greedy basis, it is necessary to consider $D$ as a closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
     When we wish to emphasize that this condition should be imposed, we denote the Dyck path $D$ instead by $D_\WA$.
-    For $(a_1,a_2)=(u_{m+1,+},u_{m,-})$ or $(u_{m,+},u_{m+1,-})$, the wrap around condition does not restrict compatibility and can thus safely be omitted.
+    Following \cite[Remark 2.21]{rupel}, for $D^{m,\varepsilon}$ and $\vv{\bar{D}}^{m,\varepsilon}$ the wrap around condition does not restrict compatibility and can thus safely be omitted.
   \end{remark}
@@
   \begin{lemma}
+    \label{le:shadow statistics}
     Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
@@
   \end{lemma}
+  \begin{remark}
+    Observe that the subset $V$ has no influence on the claim of (1) and the subset $H$ has no influence on the claim of (2).
+  \end{remark}
   \begin{proof}
@@
     Part (b) then follows from the additivity of $f_H$ and part (c) is the case when $e'=e$ here.
+  \end{proof}
+
+  \begin{corollary}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $h\in H$ and a vertical edge $v\in D(h;H)$, the condition (HGC) is not satisfied for the pair $(h,v)$ but for any $V\in\cC_D(H)$ the condition (VGC) is satisfied for the pair $(h,v)$.
+        In particular, $D(v;V)$ is a proper subpath of $hv$ for any $V\in\cC_D(H)$.
+      \item For $v\in V$ and a horizontal edge $h\in D(v;V)$, the condition (VGC) is not satisfied for the pair $(h,v)$ but for any $H\in\cC_D(V)$ the condition (HGC) is satisfied for the pair $(h,v)$.
+        In particular, $D(h;H)$ is a proper subpath of $hv$ for any $H\in\cC_D(V)$.
+    \end{enumerate}
+  \end{corollary}
+  \begin{proof}
+    We prove (1), the proof of (2) is similar.
+    By Lemma~\ref{le:shadow statistics}, $f_H(he)>0$ for every proper subpath of $D(h;H)=hv$ and so the condition (HGC) is not satisfied for the path $hv$, but then, since $V\in\cC_D(H)$, the condition (VGC) must be satisfied.
   \end{proof}
@@
 
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_2,-a_1+ca_2)\in\cI'$, define the \emph{dual dominant Dyck path} $D^{dom^\vee}=D^{dom^\vee}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2c}(x-a_1)$.
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_2,-a_1+ca_2)\in\cI'$, define the \emph{dual dominant Dyck path} $\vv{D}^{dom}=\vv{D}^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2c}(x-a_1)$.
   \end{definition}
@@
     \label{th:dominant Dyck path recursion}
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{V,b}\big(D^{dom}[a_1,a_2]\big)=D^{dom^\vee}[a_2,ba_2-a_1]$ and $\mu_{H,c}\big(D^{dom}[a_1,a_2]\big)=D^{dom^\vee}[ca_1-a_2,a_1]$.
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{V,b}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[a_2,ba_2-a_1]$ and $\mu_{H,c}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[ca_1-a_2,a_1]$.
   \end{theorem}

### 2021-09-14 dominance_regions.tex
More work in section 7

@@
 \newcommand{\diag}{\operatorname{diag}}
+\newcommand{\dpt}{\operatorname{dp}}
+\newcommand{\hgt}{\operatorname{ht}}
 \newcommand{\Id}{\operatorname{Id}}
@@
 \newcommand{\ot}{{\overline{t}}}
+\newcommand{\rsh}{{\operatorname{rsh}}}
+\newcommand{\sh}{{\operatorname{sh}}}
 \newcommand{\WA}{{W\!\!A}}
 \newcommand{\wt}{{\operatorname{wt}}}
-\newcommand{\Sh}{{\operatorname{Sh}}}
 
@@
 
-  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_kB=(b'_{ij})$ given by
+  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_k B=(b'_{ij})$ given by
   \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
@@
   Write $D=D_1\sqcup D_2$, where $D_1=\{h_1,\ldots,h_{a_1}\}$ is the set of horizontal edges and $D_2=\{v_1,\ldots,v_{a_2}\}$ is the set of vertical edges.
-  Clearly, $|D_1|=a_1$ and $|D_2|=a_2$.
+  For $h\in D_1$, define the \emph{height} $\hgt(h)$ as the number of $v\in D_2$ with $v<h$.
+  For $v\in D_2$, define the \emph{depth} $\dpt(v)$ as the number of $h\in D_1$ with $h<v$.
 
   Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
-  Given a Dyck path $D=D_1\sqcup D_2$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $\bar{D}=\bar{D}_1 \sqcup \bar{D}_2$ for the Dyck path in the lattice rectangle $[0,a_2]\times[0,a_1]$ with $\bar{D}_1=a_1+a_2+1-D_2$ and $\bar{D}_2=a_1+a_2+1-D_1$.
+  Given a Dyck path $D=D_1\sqcup D_2$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $\bar{D}=\bar{D}_1 \sqcup \bar{D}_2$ for the Dyck path (under the identification with $[1,a_1+a_2]$) in the lattice rectangle $[0,a_2]\times[0,a_1]$ with $\bar{D}_1=a_1+a_2+1-D_2$ and $\bar{D}_2=a_1+a_2+1-D_1$.
   This operation can be visualized as transposing the Dyck path.
@@
     \label{def:Dyck path mutations}
-    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_{V,b}(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge, together with the $\ell$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-\ell$ vertical edges.
-
-    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_{H,c}(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge, together with the $\ell$ vertical edges which immediately follow it, by $c-\ell$ horizontal edges followed by a vertical edge.
+    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_{1,c}(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge of $D$, together with the $\ell$ vertical edges which immediately follow it, by $c-\ell$ horizontal edges followed by a vertical edge.
+    This provides a canonical identification of the horizontal edges of $D$ with the vertical edges of $\mu_{1,c}(D)$, this identification is again denoted by $\mu_{1,c}$.
+
+    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_{2,b}(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge of $D$, together with the $\ell$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-\ell$ vertical edges.
+    This provides a canonical identification of the vertical edges of $D$ with the horizontal edges of $\mu_{2,b}(D)$, this identification is again denoted by $\mu_{2,b}$.
   \end{definition}
   \begin{remark}
-    Observe that $\mu_{H,a}$ and $\mu_{V,a}$ are inverse for any $a\ge1$.
+    Observe that $\mu_{1,a}$ and $\mu_{2,a}$ are inverse for any $a\ge1$ whenever they are defined.
   \end{remark}
 
+  The following result is proven in \cite[Lemma 2.4]{rupel} with appropriate notation changes, c.f. Theorem~\ref{th:dominant Dyck path recursion} for a slight modification and explicit proof.
   \begin{lemma}\mbox{}
@@
     \begin{enumerate}
-      \item If $a_1 < b a_2$, then $\mu_{V,b}\big(D^{max}[a_1,a_2]\big)=D^{max}[a_2,ba_2-a_1]$.
-      \item If $a_2 < c a_1$, then $\mu_{H,c}\big(D^{max}[a_1,a_2]\big)=D^{max}[ca_1-a_2,a_1]$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    The proof is identical to the proof of \cite[Lemma 2.4]{rupel} with appropriate notation changes, c.f. Theorem~\ref{th:dominant Dyck path recursion} below.
-  \end{proof}
+      \item If $a_2 < c a_1$, then $\mu_{1,c}\big(D^{max}[a_1,a_2]\big)=D^{max}[ca_1-a_2,a_1]$.
+      \item If $a_1 < b a_2$, then $\mu_{2,b}\big(D^{max}[a_1,a_2]\big)=D^{max}[a_2,ba_2-a_1]$.
+    \end{enumerate}
+  \end{lemma}
 
@@
   \subsection{Compatibility}
+  The results of this section can mostly be found in \cite{lee-li-zelevinsky,rupel}.
+  However since we work in arbitrary Dyck paths instead of just the maximal ones, we recall and adapt the proofs as needed.
+
   For $e \le e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
+  %Take $\overline{e}e'$ and $e\overline{e}'$ to be the subpaths of $ee'$ with $e$ and $e'$ removed, respectively.
   When $e=e'$, we take $ee'$ to be the subpath consisting of only the edge $e$.
+  For $e \le h\in D$ with $h\in D_1$, write $eh^{\!\uparrow}$ for the subpath $eh$ together with all vertical edges immediately following $h$.
+  For $v \le e\in D$ with $v\in D_2$, write ${}^\leftarrow\!\!\! ve$ for the subpath $ve$ together with all horizontal edges immediately preceding $v$.
   \begin{definition}
@@
       \label{eq:horizontal shadow statistic}
-      f_H(ee')=-|ee'\cap D_2|+c|ee'\cap H|
+      f_H(ee')=-|ee' \cap D_2|+c|ee'\cap H|
     \end{equation}
@@
       \label{eq:vertical shadow statistic}
-      f_V(ee')=-|ee'\cap D_1|+b|ee'\cap V|.
+      f_V(ee')=-|ee' \cap D_1|+b|ee'\cap V|.
     \end{equation}
@@
   \end{remark}
+
+  \begin{lemma}
+    Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
+    For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
+    Then for any $h_i<h_j \in D_1$, we have $f_H(h_i h_j^{\!\uparrow})=-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_i v'_j)$.
+  \end{lemma}
+  \begin{proof}
+    By definition, we have 
+    \begin{align*}
+      -\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)&=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap V'|\\
+      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \big(D'_2\setminus \mu_{1,c}(H)\big)\big|\\
+      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_2|+c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \mu_{1,c}(H)\big|.
+    \end{align*}
+    But, by construction of $\mu_{1,c}(D)$ and since $\mu_{2,c}(D')=D$, we have
+    \[\big|{}^\leftarrow\!\!\!
+v'_i v'_j \cap \mu_{1,c}(H)\big|=|h_i h_j^{\!\uparrow} \cap H| \qquad \text{and} \qquad c|{}^\leftarrow\!\!\!
+v'_i v'_j \cap D'_2|-|{}^\leftarrow\!\!\!
+v'_i v'_j \cap D'_1|=|h_i h_j^{\!\uparrow} \cap D_2|\]
+    giving
+    \[-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)=-|h_i h_j^{\!\uparrow} \cap D_2|+c|h_i h_j^{\!\uparrow} \cap H|=f_H(h_i h_j^{\!\uparrow})\]
+    as desired.
+  \end{proof}
+
   \begin{definition}
@@
     For $h\in H$ and $v\in V$ with $h<v$, call the path $hv$ \emph{compatible} if there exists an edge $e\in hv$ such that one of the following conditions is satisfied:
-    \[\tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0;\]
-    \[\tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0.\]
+    \begin{equation}
+      \label{eq:HGC}
+      \tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0;
+    \end{equation}
+    \begin{equation}
+      \label{eq:VGC}
+      \tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0.
+    \end{equation}
     Call the subset $H\sqcup V$ \emph{compatible} if every path $hv$ with $h\in H$ and $v\in V$ is compatible.
@@
   \begin{definition}
+    \label{def:shadows}
     For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$, define the \emph{shadow paths} as follows:
     \begin{itemize}
-      \item For $h\in D_1$, write $D(h;H)$ for the shortest subpath $he \subset D$ with $f_H(he)=0$ or, if no such subpath exists, set $D(h;H)=hv_{a_2}$.
-      \item For $h\in D_1$, write $D_\WA(h;H)$ for the shortest subpath $he \subset D_\WA$ with $f_H(he)=0$ or, if no such subpath exists, set $D_\WA(h;H)=D$.
-      \item For $v\in D_2$, write $D(v;V)$ for the shortest subpath $ev \subset D$ with $f_V(ev)=0$ or, if no such subpath exists, set $D(v;V)=h_1 v$.
-      \item For $v\in D_2$, write $D_\WA(v;V)$ for the shortest subpath $ev \subset D_\WA$ with $f_V(ev)=0$ or, if no such subpath exists, set $D_\WA(v;V)=D$.
+      \item For $h\in D_1$, write $D(h;H)$ (resp.
+$D_\WA(h;H)$) for the shortest subpath $he \subset D$ (resp.
+$he \subset D_\WA$) with $f_H(he)=0$ or, if no such subpath exists, set $D(h;H)=hv_{a_2}$ (resp.
+set $D_\WA(h;H)=D$).
+      \item For $v\in D_2$, write $D(v;V)$ (resp.
+$D_\WA(v;V)$) for the shortest subpath $ev \subset D$ (resp.
+$ev \subset D_\WA$) with $f_V(ev)=0$ or, if no such subpath exists, set $D(v;V)=h_1 v$ (resp.
+set $D_\WA(v;V)=D$).
     \end{itemize}
+    Write 
+    \[D(H):=\bigcup_{h\in H} D(h;H) \qquad \text{and} \qquad D(V):=\bigcup_{v\in V} D(v;V).\]
+    Define the \emph{shadow} of $H$ (resp.
+\emph{shadow} of $V$) as the set $\sh_D(H):=D(H)\cap D_2$ (resp.
+$\sh_D(V):=D(V)\cap D_1$) and the \emph{local shadow} of $h\in H$ (resp.
+of $v\in V$) as the set $\sh_D(h;H)=D(h;H)\cap D_2$ (resp.
+$\sh_D(v;V)=D(v;V)\cap D_1$).
+    Define shadows and local shadows for $D_\WA$ similarly.
   \end{definition}
@@
           \item for any proper subpath $he'\subsetneq he$, we have $f_H(he')>0$;
-          \item for any proper subpath $e'e\subsetneq he$, we have $f_H(e'e)<0$;
+          \item if $f_H(he)=0$, then for any proper subpath $e'e\subsetneq he$, we have $f_H(e'e)<0$;
           \item $e\in V$.
@@
           \item for any proper subpath $e'v\subsetneq ev$, we have $f_V(e'v)>0$;
-          \item for any proper subpath $ee'\subsetneq ev$, we have $f_V(ee')<0$;
+          \item if $f_V(ev)=0$, then for any proper subpath $ee'\subsetneq ev$, we have $f_V(ee')<0$;
           \item $e\in H$.
@@
     \begin{enumerate}
-      \item For $h\in H$ and a vertical edge $v\in D(h;H)$, the condition (HGC) is not satisfied for the pair $(h,v)$ but for any $V\in\cC_D(H)$ the condition (VGC) is satisfied for the pair $(h,v)$.
+      \item For $h\in H$ and a vertical edge $v\in D(h;H)$, the condition \eqref{eq:HGC} is not satisfied for the path $hv$ but for any $V\in\cC_D(H)$ the condition \eqref{eq:VGC} is satisfied for the path $hv$.
         In particular, $D(v;V)$ is a proper subpath of $hv$ for any $V\in\cC_D(H)$.
-      \item For $v\in V$ and a horizontal edge $h\in D(v;V)$, the condition (VGC) is not satisfied for the pair $(h,v)$ but for any $H\in\cC_D(V)$ the condition (HGC) is satisfied for the pair $(h,v)$.
+      \item For $v\in V$ and a horizontal edge $h\in D(v;V)$, the condition \eqref{eq:VGC} is not satisfied for the pair $hv$ but for any $H\in\cC_D(V)$ the condition \eqref{eq:HGC} is satisfied for the path $hv$.
         In particular, $D(h;H)$ is a proper subpath of $hv$ for any $H\in\cC_D(V)$.
@@
     We prove (1), the proof of (2) is similar.
-    By Lemma~\ref{le:shadow statistics}, $f_H(he)>0$ for every proper subpath of $D(h;H)=hv$ and so the condition (HGC) is not satisfied for the path $hv$, but then, since $V\in\cC_D(H)$, the condition (VGC) must be satisfied.
-  \end{proof}
+    By Lemma~\ref{le:shadow statistics}, $f_H(he)>0$ for every proper subpath of $D(h;H)=hv$ and so the condition \eqref{eq:HGC} is not satisfied for the path $hv$, but then, since $V\in\cC_D(H)$, the condition \eqref{eq:VGC} must be satisfied for this path.
+  \end{proof}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item For $H\subset D_1$ and $h,h'\in H$, the local shadows $\sh_D(h;H)$ and $\sh_D(h';H)$ are either disjoint or one is contained in the other.
+      \item For $V\subset D_2$ and $v,v'\in V$, the local shadows $\sh_D(v;V)$ and $\sh_D(v';V)$ are either disjoint or one is contained in the other.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    We prove (1), the proof of (2) is similar.
+    For $h=h'$ or $D(h;H)=D$ or $D(h';H)=D$ there is nothing to show, so assume both shadow paths are proper subpaths of $D$.
+    Suppose the intersection of $D(h;H)$ and $D(h';H)$ is nonempty, say with $h'\in D(h;H)=he$.
+    If $e=v_{a_2}$, then $D(h';H)=h'v_{a_2}\subset D(h;H)$.
+    Otherwise, denote by $e'\in D$ the edge immediately preceding $h'$ in $he$.
+    If $e\in D(h';H)$, Lemma~\ref{le:shadow statistics} shows that $f_H(he)=f_H(he')+f_H(h'e)>0$, in contradiction to the definition of $D(h;H)$.
+  \end{proof}
+
+  \begin{definition}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $H$, by removing for each $d\in[1,a_1]$ the (up to) $c$ vertical edges of depth $d$ immediately following $h_d$.
+      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $V$, by removing for each $\ell\in[1,a_2]$ the (up to) $b$ horizontal edges of height $\ell-1$ immediately preceding $v_\ell$.
+    \end{enumerate}
+  \end{definition}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item For $H\subset D_1$, $V\in\cC_D(H)$ if and only if $V$ is disjoint from $\sh_D(H)\setminus\rsh_D(H)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in H$ and $v\in\rsh_D(H)$.
+      \item For $V\subset D_2$, $H\in\cC_D(V)$ if and only if $H$ is disjoint from $\sh_D(V)\setminus\rsh_D(V)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in\rsh_D(V)$ and $v\in V$.
+    \end{enumerate}
+  \end{lemma}
+
+  \begin{definition}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $0 < j,d \le a_1$ with $h_j\in H$, denote by $\rsh_D(H)_{j;d}$ the set of all $v\in\rsh_D(H)$ of depth $d$ such that $v\in\sh(h_j;H)$ and $h_j$ is the first horizontal edge before $v$ with this property.
+        Define the \emph{local remote shadow} of the edge $h_j$ by $\rsh_D(h_j;H):=\bigsqcup_{d\in[1,a_1]} \rsh_D(H)_{j;d}$.
+      \item For $0 < k \le a_2$ with $v_k\in V$ and $0\le \ell < a_2$, denote by $\rsh_D(V)_{k;\ell}$ the set of all $h\in\rsh_D(V)$ of height $\ell$ such that $h\in\sh(v_k;V)$ and $v_k$ is the first vertical edge after $h$ with this property.
+        Define the \emph{local remote shadow} of the edge $v_k$ by $\rsh_D(v_k;V):=\bigsqcup_{\ell\in[0,a_2-1]} \rsh_D(V)_{k;\ell}$.
+    \end{enumerate}
+  \end{definition}
 
@@
     \[x_D=x_1^{-a_1} x_2^{-a_2} \sum_{t=0}^{a_2}\sum_{k=0}^{a_1} \nu_{k,t} x_1^{bt}(1+x_2^c)^{a_1-k}=x_1^{-a_1} x_2^{-a_2} \sum_{s=0}^{a_1}\sum_{\ell=0}^{a_2} \theta_{s,\ell} x_2^{cs}(1+x_1^b)^{a_2-\ell},\]
-    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\Sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\Sh_D(H)|=\ell$.
+    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\sh_D(H)|=\ell$.
     Then 
@@
     \label{th:dominant Dyck path recursion}
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{V,b}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[a_2,ba_2-a_1]$ and $\mu_{H,c}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[ca_1-a_2,a_1]$.
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[ca_1-a_2,a_1]$ and $\mu_{2,b}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[a_2,ba_2-a_1]$.
   \end{theorem}
   \begin{proof}
-    We prove the result for $\mu_{H,c}$ as the result for $\mu_{V,b}$ immediately follows from $\mu_{H,b}$ being its inverse.
-    Write $D'$ for the Dyck path $\mu_{H,c}\big(D^{dom}[a_1,a_2]\big)$ and observe that by construction $D'$ has $ca_1-a_2$ horizontal edges and $a_1$ vertical edges.
+    We prove the result for $\mu_{1,c}$ as the result for $\mu_{2,b}$ immediately follows from $\mu_{1,b}$ being its inverse.
+    Write $D'$ for the Dyck path $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)$ and observe that by construction $D'$ has $ca_1-a_2$ horizontal edges and $a_1$ vertical edges.
     Write $v'_1,\ldots,v'_{a_1}$ for the vertical edges of $D'$ with $v'_r$ immediately preceded by $\ell_r$ horizontal edges.

### 2021-10-04 dominance_regions.tex
Getting close to finishing the bijection we need.  Also some reorganization.

@@
   When we wish to emphasize the upper right bounding corner we will write $D[a_1,a_2]$.
-  Consider $D$ as the set of its edges taken as a totally ordered set along the natural labeling from $(0,0)$ to $(a_1,a_2)$.
+  Consider $D$ as the totally ordered set of its edges along the natural labeling from $(0,0)$ to $(a_1,a_2)$.
   It may be convenient to identify $D$ with the ordered set $[1,a_1+a_2]$.
   Write $D=D_1\sqcup D_2$, where $D_1=\{h_1,\ldots,h_{a_1}\}$ is the set of horizontal edges and $D_2=\{v_1,\ldots,v_{a_2}\}$ is the set of vertical edges.
-  For $h\in D_1$, define the \emph{height} $\hgt(h)$ as the number of $v\in D_2$ with $v<h$.
-  For $v\in D_2$, define the \emph{depth} $\dpt(v)$ as the number of $h\in D_1$ with $h<v$.
+  Define the \emph{height}, $\hgt(h)$ for $h\in D_1$, as one more than the number of $v\in D_2$ with $v<h$.
+  Define the \emph{depth}, $\dpt(v)$ for $v\in D_2$, as the number of $h\in D_1$ with $h<v$.
+  \begin{remark}
+    The seemingly different conventions for computing height and depth provide uniformity later.
+    Indeed, the vertical edges immediately following $h_d$ have depth $d$, while this convention allows the horizontal edges immediately preceding $v_\ell$ to similarly be said to have height $\ell$.
+  \end{remark}
 
@@
 
+  \subsection{Structure of Dyck Paths}
+
   Write $D^{max}=D^{max}[a_1,a_2]$ for the maximal Dyck path in the lattice rectangle $[0,a_1]\times[0,a_2]$, i.e.
 $D^{max}$ never crosses above the diagonal line joining $(0,0)$ to $(a_1,a_2)$ and any lattice point above $D^{max}$ also lies above the diagonal.
+  Observe that $\bar{D}^{max}[a_1,a_2]=D^{max}[a_2,a_1]$.
 
@@
     \label{def:Dyck path mutations}
-    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_{1,c}(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge of $D$, together with the $\ell$ vertical edges which immediately follow it, by $c-\ell$ horizontal edges followed by a vertical edge.
+    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_{1,c}(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge of $D$, together with the $r$ vertical edges which immediately follow it, by $c-r$ horizontal edges followed by a vertical edge.
     This provides a canonical identification of the horizontal edges of $D$ with the vertical edges of $\mu_{1,c}(D)$, this identification is again denoted by $\mu_{1,c}$.
 
-    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_{2,b}(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge of $D$, together with the $\ell$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-\ell$ vertical edges.
+    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_{2,b}(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge of $D$, together with the $r$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-r$ vertical edges.
     This provides a canonical identification of the vertical edges of $D$ with the horizontal edges of $\mu_{2,b}(D)$, this identification is again denoted by $\mu_{2,b}$.
@@
 
-  \subsection{Compatibility}
-  The results of this section can mostly be found in \cite{lee-li-zelevinsky,rupel}.
-  However since we work in arbitrary Dyck paths instead of just the maximal ones, we recall and adapt the proofs as needed.
-
-  For $e \le e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
-  %Take $\overline{e}e'$ and $e\overline{e}'$ to be the subpaths of $ee'$ with $e$ and $e'$ removed, respectively.
-  When $e=e'$, we take $ee'$ to be the subpath consisting of only the edge $e$.
-  For $e \le h\in D$ with $h\in D_1$, write $eh^{\!\uparrow}$ for the subpath $eh$ together with all vertical edges immediately following $h$.
-  For $v \le e\in D$ with $v\in D_2$, write ${}^\leftarrow\!\!\! ve$ for the subpath $ve$ together with all horizontal edges immediately preceding $v$.
-  \begin{definition}
-    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ together with a subpath $ee'\subset D$, define the \emph{horizontal shadow statistic}:
-    \begin{equation}
-      \label{eq:horizontal shadow statistic}
-      f_H(ee')=-|ee' \cap D_2|+c|ee'\cap H|
-    \end{equation}
-    and the \emph{vertical shadow statistic}:
-    \begin{equation}
-      \label{eq:vertical shadow statistic}
-      f_V(ee')=-|ee' \cap D_1|+b|ee'\cap V|.
-    \end{equation}
-  \end{definition}
-  \begin{remark}
-    Observe that the shadow statistics are additive with respect to concatenation of subpaths.
-  \end{remark}
-
-  \begin{lemma}
-    Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
-    For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
-    Then for any $h_i<h_j \in D_1$, we have $f_H(h_i h_j^{\!\uparrow})=-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_i v'_j)$.
-  \end{lemma}
-  \begin{proof}
-    By definition, we have 
-    \begin{align*}
-      -\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)&=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap V'|\\
-      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \big(D'_2\setminus \mu_{1,c}(H)\big)\big|\\
-      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_2|+c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \mu_{1,c}(H)\big|.
-    \end{align*}
-    But, by construction of $\mu_{1,c}(D)$ and since $\mu_{2,c}(D')=D$, we have
-    \[\big|{}^\leftarrow\!\!\!
-v'_i v'_j \cap \mu_{1,c}(H)\big|=|h_i h_j^{\!\uparrow} \cap H| \qquad \text{and} \qquad c|{}^\leftarrow\!\!\!
-v'_i v'_j \cap D'_2|-|{}^\leftarrow\!\!\!
-v'_i v'_j \cap D'_1|=|h_i h_j^{\!\uparrow} \cap D_2|\]
-    giving
-    \[-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)=-|h_i h_j^{\!\uparrow} \cap D_2|+c|h_i h_j^{\!\uparrow} \cap H|=f_H(h_i h_j^{\!\uparrow})\]
-    as desired.
-  \end{proof}
-
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    For $h\in H$ and $v\in V$ with $h<v$, call the path $hv$ \emph{compatible} if there exists an edge $e\in hv$ such that one of the following conditions is satisfied:
-    \begin{equation}
-      \label{eq:HGC}
-      \tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0;
-    \end{equation}
-    \begin{equation}
-      \label{eq:VGC}
-      \tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0.
-    \end{equation}
-    Call the subset $H\sqcup V$ \emph{compatible} if every path $hv$ with $h\in H$ and $v\in V$ is compatible.
-    Write $\cC_D$ for the collection of all compatible subsets of $D$.
-    Given a subset $H\subset D_1$, write $\cC_D(H)$ for the collection of all $V\subset D_2$ for which $H\sqcup V\in\cC_D$.
-    Define $\cC_D(V)$ for $V\subset D_2$ similarly.
-  \end{definition}
-  \begin{remark}
-    In the construction of the greedy basis, it is necessary to consider $D$ as a closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
-    When we wish to emphasize that this condition should be imposed, we denote the Dyck path $D$ instead by $D_\WA$.
-    Following \cite[Remark 2.21]{rupel}, for $D^{m,\varepsilon}$ and $\vv{\bar{D}}^{m,\varepsilon}$ the wrap around condition does not restrict compatibility and can thus safely be omitted.
-  \end{remark}
-
-  \begin{definition}
-    \label{def:shadows}
-    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$, define the \emph{shadow paths} as follows:
-    \begin{itemize}
-      \item For $h\in D_1$, write $D(h;H)$ (resp.
-$D_\WA(h;H)$) for the shortest subpath $he \subset D$ (resp.
-$he \subset D_\WA$) with $f_H(he)=0$ or, if no such subpath exists, set $D(h;H)=hv_{a_2}$ (resp.
-set $D_\WA(h;H)=D$).
-      \item For $v\in D_2$, write $D(v;V)$ (resp.
-$D_\WA(v;V)$) for the shortest subpath $ev \subset D$ (resp.
-$ev \subset D_\WA$) with $f_V(ev)=0$ or, if no such subpath exists, set $D(v;V)=h_1 v$ (resp.
-set $D_\WA(v;V)=D$).
-    \end{itemize}
-    Write 
-    \[D(H):=\bigcup_{h\in H} D(h;H) \qquad \text{and} \qquad D(V):=\bigcup_{v\in V} D(v;V).\]
-    Define the \emph{shadow} of $H$ (resp.
-\emph{shadow} of $V$) as the set $\sh_D(H):=D(H)\cap D_2$ (resp.
-$\sh_D(V):=D(V)\cap D_1$) and the \emph{local shadow} of $h\in H$ (resp.
-of $v\in V$) as the set $\sh_D(h;H)=D(h;H)\cap D_2$ (resp.
-$\sh_D(v;V)=D(v;V)\cap D_1$).
-    Define shadows and local shadows for $D_\WA$ similarly.
-  \end{definition}
-
-  \begin{lemma}
-    \label{le:shadow statistics}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $h\in H$, take $he$ to be either the path $D(h;H)$ or $D_\WA(h;H)$.
-        The following hold:
-        \begin{enumerate}
-          \item for any proper subpath $he'\subsetneq he$, we have $f_H(he')>0$;
-          \item if $f_H(he)=0$, then for any proper subpath $e'e\subsetneq he$, we have $f_H(e'e)<0$;
-          \item $e\in V$.
-        \end{enumerate}
-      \item For $v\in V$, take $ev$ to be either the path $D(v;V)$ or $D_\WA(v;V)$.
-        The following hold:
-        \begin{enumerate}
-          \item for any proper subpath $e'v\subsetneq ev$, we have $f_V(e'v)>0$;
-          \item if $f_V(ev)=0$, then for any proper subpath $ee'\subsetneq ev$, we have $f_V(ee')<0$;
-          \item $e\in H$.
-        \end{enumerate}
-    \end{enumerate}
-  \end{lemma}
-  \begin{remark}
-    Observe that the subset $V$ has no influence on the claim of (1) and the subset $H$ has no influence on the claim of (2).
-  \end{remark}
-  \begin{proof}
-    We prove (1), the proof of (2) is similar.
-    To see (a), note that as $e'$ traverses the path $he$ from $h$ to $e$, the value of $f_H(he')$ either increases by $c$, stays constant, or decreases by 1.
-    Since $h\in H$, we have $f_H(hh)=c>0$ and so the value of $f_H(he')$ stays positive until it first becomes 0 when $e'=e$.
-    Part (b) then follows from the additivity of $f_H$ and part (c) is the case when $e'=e$ here.
-  \end{proof}
-
-  \begin{corollary}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $h\in H$ and a vertical edge $v\in D(h;H)$, the condition \eqref{eq:HGC} is not satisfied for the path $hv$ but for any $V\in\cC_D(H)$ the condition \eqref{eq:VGC} is satisfied for the path $hv$.
-        In particular, $D(v;V)$ is a proper subpath of $hv$ for any $V\in\cC_D(H)$.
-      \item For $v\in V$ and a horizontal edge $h\in D(v;V)$, the condition \eqref{eq:VGC} is not satisfied for the pair $hv$ but for any $H\in\cC_D(V)$ the condition \eqref{eq:HGC} is satisfied for the path $hv$.
-        In particular, $D(h;H)$ is a proper subpath of $hv$ for any $H\in\cC_D(V)$.
-    \end{enumerate}
-  \end{corollary}
-  \begin{proof}
-    We prove (1), the proof of (2) is similar.
-    By Lemma~\ref{le:shadow statistics}, $f_H(he)>0$ for every proper subpath of $D(h;H)=hv$ and so the condition \eqref{eq:HGC} is not satisfied for the path $hv$, but then, since $V\in\cC_D(H)$, the condition \eqref{eq:VGC} must be satisfied for this path.
-  \end{proof}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item For $H\subset D_1$ and $h,h'\in H$, the local shadows $\sh_D(h;H)$ and $\sh_D(h';H)$ are either disjoint or one is contained in the other.
-      \item For $V\subset D_2$ and $v,v'\in V$, the local shadows $\sh_D(v;V)$ and $\sh_D(v';V)$ are either disjoint or one is contained in the other.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    We prove (1), the proof of (2) is similar.
-    For $h=h'$ or $D(h;H)=D$ or $D(h';H)=D$ there is nothing to show, so assume both shadow paths are proper subpaths of $D$.
-    Suppose the intersection of $D(h;H)$ and $D(h';H)$ is nonempty, say with $h'\in D(h;H)=he$.
-    If $e=v_{a_2}$, then $D(h';H)=h'v_{a_2}\subset D(h;H)$.
-    Otherwise, denote by $e'\in D$ the edge immediately preceding $h'$ in $he$.
-    If $e\in D(h';H)$, Lemma~\ref{le:shadow statistics} shows that $f_H(he)=f_H(he')+f_H(h'e)>0$, in contradiction to the definition of $D(h;H)$.
-  \end{proof}
-
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $H$, by removing for each $d\in[1,a_1]$ the (up to) $c$ vertical edges of depth $d$ immediately following $h_d$.
-      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $V$, by removing for each $\ell\in[1,a_2]$ the (up to) $b$ horizontal edges of height $\ell-1$ immediately preceding $v_\ell$.
-    \end{enumerate}
-  \end{definition}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item For $H\subset D_1$, $V\in\cC_D(H)$ if and only if $V$ is disjoint from $\sh_D(H)\setminus\rsh_D(H)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in H$ and $v\in\rsh_D(H)$.
-      \item For $V\subset D_2$, $H\in\cC_D(V)$ if and only if $H$ is disjoint from $\sh_D(V)\setminus\rsh_D(V)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in\rsh_D(V)$ and $v\in V$.
-    \end{enumerate}
-  \end{lemma}
-
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $0 < j,d \le a_1$ with $h_j\in H$, denote by $\rsh_D(H)_{j;d}$ the set of all $v\in\rsh_D(H)$ of depth $d$ such that $v\in\sh(h_j;H)$ and $h_j$ is the first horizontal edge before $v$ with this property.
-        Define the \emph{local remote shadow} of the edge $h_j$ by $\rsh_D(h_j;H):=\bigsqcup_{d\in[1,a_1]} \rsh_D(H)_{j;d}$.
-      \item For $0 < k \le a_2$ with $v_k\in V$ and $0\le \ell < a_2$, denote by $\rsh_D(V)_{k;\ell}$ the set of all $h\in\rsh_D(V)$ of height $\ell$ such that $h\in\sh(v_k;V)$ and $v_k$ is the first vertical edge after $h$ with this property.
-        Define the \emph{local remote shadow} of the edge $v_k$ by $\rsh_D(v_k;V):=\bigsqcup_{\ell\in[0,a_2-1]} \rsh_D(V)_{k;\ell}$.
-    \end{enumerate}
-  \end{definition}
-
-  We associate to $D$ the element $x_D\in\ZZ_{\ge0}[x_1^{\pm1},x_2^{\pm1}]$ defined as follows
-  \[x_D:=x_1^{-a_1} x_2^{-a_2} \sum_{H\sqcup V\in\cC_D} x_1^{b|V|} x_2^{c|H|}.\]
-
-  \begin{theorem}[\cite{lee-li-zelevinsky}]
-    For $(a_1,a_2)=(u_{m,+},u_{m-1,-})$ or $(u_{m-1,+},u_{m,-})$ for $m\ge1$, the element $x_{D^{max}[a_1,a_2]}$ is a non-initial cluster variable.
-    Otherwise, the element $x_{D^{max}_\WA[a_1,a_2]}$ is an element of the greedy basis
-  \end{theorem}
-
-  \begin{lemma}
-    Suppose there are two factorizations
-    \[x_D=x_1^{-a_1} x_2^{-a_2} \sum_{t=0}^{a_2}\sum_{k=0}^{a_1} \nu_{k,t} x_1^{bt}(1+x_2^c)^{a_1-k}=x_1^{-a_1} x_2^{-a_2} \sum_{s=0}^{a_1}\sum_{\ell=0}^{a_2} \theta_{s,\ell} x_2^{cs}(1+x_1^b)^{a_2-\ell},\]
-    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\sh_D(H)|=\ell$.
-    Then 
-    \[\sum_{k=0}^{a_1-s} {a_1-k\choose s} \nu_{k,t}=\sum_{\ell=0}^{a_2-t} {a_2-\ell\choose t} \theta_{s,\ell}\]
-    for all possible $s$ and $t$.
-  \end{lemma}
-  \begin{question}
-    How do such expressions behave under mutations?
-  \end{question}
-
-  \begin{lemma}
-    Choose $a_1,a_2\in\ZZ_{\ge0}$.
-    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_{D^{st}}$ coincides with the corresponding standard monomial basis element.
-  \end{lemma}
-
   Our main interest will be with the following Dyck paths.
@@
     Write $D'$ for the Dyck path $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)$ and observe that by construction $D'$ has $ca_1-a_2$ horizontal edges and $a_1$ vertical edges.
-    Write $v'_1,\ldots,v'_{a_1}$ for the vertical edges of $D'$ with $v'_r$ immediately preceded by $\ell_r$ horizontal edges.
+    Write $v'_1,\ldots,v'_{a_1}$ for the vertical edges of $D'$ with $v'_k$ immediately preceded by $r_k$ horizontal edges.
     We have to show (i) that every lattice point on $D'$ stays below the lines 
@@
     If there exists $t$ so that $v'_t$ passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$, then
-    \[ \frac{t}{\sum\limits_{r=1}^t \ell_r} > \frac{bc+\sqrt{bc(bc-4)}}{2c} \]
+    \[ \frac{t}{\sum\limits_{k=1}^t r_k} > \frac{bc+\sqrt{bc(bc-4)}}{2c} \]
     or, rearranging, we have
-    \[ \frac{\sum\limits_{r=1}^t \ell_r}{t} < \frac{2c}{bc+\sqrt{bc(bc-4)}} = \frac{bc-\sqrt{bc(bc-4)}}{2b} \]
+    \[ \frac{\sum\limits_{k=1}^t r_k}{t} < \frac{2c}{bc+\sqrt{bc(bc-4)}} = \frac{bc-\sqrt{bc(bc-4)}}{2b} \]
     or
-    \[ \frac{bc+\sqrt{bc(bc-4)}}{2b} < \frac{ct-\sum\limits_{r=1}^t \ell_r}{t} = \frac{\sum\limits_{r=1}^t (c-\ell_r)}{t}. \]
+    \[ \frac{bc+\sqrt{bc(bc-4)}}{2b} < \frac{ct-\sum\limits_{k=1}^t r_k}{t} = \frac{\sum\limits_{k=1}^t (c-r_k)}{t}. \]
     But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, contrary to the definition.
@@
     If there exists $t$ so that $v'_t$ passes above the line $y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)$, then
-    \[ \frac{bc-\sqrt{bc(bc-4)}}{2c} > \frac{a_1-t}{ca_1-a_2-\sum\limits_{r=1}^t \ell_r} \]
+    \[ \frac{bc-\sqrt{bc(bc-4)}}{2c} > \frac{a_1-t}{ca_1-a_2-\sum\limits_{k=1}^t r_k} \]
     or, rearranging, we have
-    \[ \frac{ca_1-a_2-\sum\limits_{r=1}^t \ell_r}{a_1-t} > \frac{2c}{bc-\sqrt{bc(bc-4)}} = \frac{bc+\sqrt{bc(bc-4)}}{2b} \]
+    \[ \frac{ca_1-a_2-\sum\limits_{k=1}^t r_k}{a_1-t} > \frac{2c}{bc-\sqrt{bc(bc-4)}} = \frac{bc+\sqrt{bc(bc-4)}}{2b} \]
     or
-    \[ \frac{bc-\sqrt{bc(bc-4)}}{2b} > \frac{ c(a_1-t) - \big(ca_1-a_2-\sum\limits_{r=1}^t \ell_r\big)}{a_1-t} = \frac{a_2-\sum\limits_{r=1}^t (c-\ell_r)}{a_1-t}. \]
+    \[ \frac{bc-\sqrt{bc(bc-4)}}{2b} > \frac{ c(a_1-t) - \big(ca_1-a_2-\sum\limits_{k=1}^t r_k\big)}{a_1-t} = \frac{a_2-\sum\limits_{k=1}^t (c-r_k)}{a_1-t}. \]
     But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$, contrary to the definition.
@@
     \end{itemize}
-  \end{lemma}
-
-  This can be made more precise as follows.
-  \begin{lemma}
-    For $s>0$, choose $m\ge2$ minimal so that $s < u_{m,-}$
   \end{lemma}
@@
 
+  \subsection{Compatibility}
+  The results of this section can mostly be found in \cite{lee-li-zelevinsky,rupel}.
+  However since we work in arbitrary Dyck paths instead of just the maximal ones, some results and proofs will need to be adapted.
+
+  For $e \le e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
+  When $e=e'$, we take $ee'$ to be the subpath consisting of only the edge $e$.
+  \begin{definition}
+    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ together with a subpath $ee'\subset D$, define the \emph{horizontal shadow statistic}:
+    \begin{equation}
+      \label{eq:horizontal shadow statistic}
+      f_H(ee')=-|ee' \cap D_2|+c|ee'\cap H|
+    \end{equation}
+    and the \emph{vertical shadow statistic}:
+    \begin{equation}
+      \label{eq:vertical shadow statistic}
+      f_V(ee')=-|ee' \cap D_1|+b|ee'\cap V|.
+    \end{equation}
+  \end{definition}
+  \begin{remark}
+    Observe that the shadow statistics are additive with respect to concatenation of subpaths.
+  \end{remark}
+
+  A key notion from \cite{lee-li-zelevinsky} is that of ``compatible subsets of a maximal Dyck path'', this construction immediately generalizes to arbitrary Dyck paths as follows.
+  \begin{definition}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    For $h\in H$ and $v\in V$ with $h<v$, call the path $hv$ \emph{compatible} if there exists an edge $e\in hv$ such that one of the following conditions is satisfied:
+    \begin{equation}
+      \label{eq:HGC}
+      \tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0;
+    \end{equation}
+    \begin{equation}
+      \label{eq:VGC}
+      \tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0.
+    \end{equation}
+    Call the subset $H\sqcup V$ \emph{compatible} if every path $hv$ with $h\in H$ and $v\in V$ is compatible.
+    Write $\cC_D$ for the collection of all compatible subsets of $D$.
+    Given a subset $H\subset D_1$, write $\cC_D(H)$ for the collection of all $V\subset D_2$ for which $H\sqcup V\in\cC_D$.
+    Define $\cC_D(V)$ for $V\subset D_2$ similarly.
+  \end{definition}
+  \begin{remark}
+    In the construction of the greedy basis, it is necessary to consider $D$ as a closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
+    When we wish to emphasize that this condition should be imposed, we denote the Dyck path $D$ instead by $D_\WA$.
+    Following \cite[Remark 2.21]{rupel}, for $D^{m,\varepsilon}$ and $\vv{\bar{D}}^{m,\varepsilon}$ the wrap around condition does not restrict compatibility and can thus safely be omitted.
+  \end{remark}
+
+  The crucial result from \cite{lee-li-zelevinsky} can be stated as follows: if a Dyck path $D$ is vertically-adapted to $c$ (resp.
+horizontally adapted to $b$), then there is a bijection between certain compatible subsets of $D$ and certain compatible subsets of $\mu_{1,c}(D)$ (resp.
+of $\mu_{2,b}(D)$).
+  The main step in the proof that needs to be adapted to the general situation is the following.
+  For $e \le h\in D$ with $h=h_d\in D_1$, write $eh^{\!\uparrow}$ for the subpath $eh$ together with all vertical edges of depth $d$ immediately following $h$.
+  For $v \le e\in D$ with $v=v_\ell\in D_2$, write ${}^\leftarrow\!\!\! ve$ for the subpath $ve$ together with all horizontal edges of height $\ell$ immediately preceding $v$.
+  \begin{lemma}\mbox{}
+    \label{le:shadow statistic recursion}
+    \begin{enumerate}
+      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
+        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
+        Then for any $h_i \le h_j \in D_1$, we have $f_H(h_i h_j^{\!\uparrow})=-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_i v'_j)$.
+      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
+        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
+        Then for any $v_i \le v_j \in D_2$, we have $f_V({}^\leftarrow\!\!\! v_i v_j)=-\vv{f}_{H''}(h''_i {h''_j}^{\!\uparrow})$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    Claim (2) is immediate from claim (1). 
+    By definition, we have 
+    \begin{align*}
+      -\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)&=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap V'|\\
+      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \big(D'_2\setminus \mu_{1,c}(H)\big)\big|\\
+      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_2|+c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \mu_{1,c}(H)\big|.
+    \end{align*}
+    But, by construction of $\mu_{1,c}(D)$ and since $\mu_{2,c}(D')=D$, we have
+    \[\big|{}^\leftarrow\!\!\!
+v'_i v'_j \cap \mu_{1,c}(H)\big|=|h_i h_j^{\!\uparrow} \cap H| \qquad \text{and} \qquad c|{}^\leftarrow\!\!\!
+v'_i v'_j \cap D'_2|-|{}^\leftarrow\!\!\!
+v'_i v'_j \cap D'_1|=|h_i h_j^{\!\uparrow} \cap D_2|\]
+    giving
+    \[-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)=-|h_i h_j^{\!\uparrow} \cap D_2|+c|h_i h_j^{\!\uparrow} \cap H|=f_H(h_i h_j^{\!\uparrow})\]
+    as desired.
+  \end{proof}
+
+  The desired bijection of compatible subsets is constructed in terms of certain subpaths determined from each compatible subset.
+  \begin{definition}
+    \label{def:shadows}
+    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$, define the \emph{shadow paths} as follows:
+    \begin{itemize}
+      \item For $h\in D_1$, write $D(h;H)$ for the shortest subpath $he \subset D$ with $f_H(he)=0$ or, if no such subpath exists, set $D(h;H)=hv_{a_2}$.
+      \item For $v\in D_2$, write $D(v;V)$ for the shortest subpath $ev \subset D$ with $f_V(ev)=0$ or, if no such subpath exists, set $D(v;V)=h_1 v$.
+    \end{itemize}
+    Write 
+    \[D(H):=\bigcup_{h\in H} D(h;H) \qquad \text{and} \qquad D(V):=\bigcup_{v\in V} D(v;V).\]
+    Define the \emph{shadow} of $H$ (resp.
+the \emph{shadow} of $V$) as the set $\sh_D(H):=D(H)\cap D_2$ (resp.~$\sh_D(V):=D(V)\cap D_1$) and the \emph{local shadow} of $h\in H$ (resp.
+of $v\in V$) as the set $\sh_D(h;H)=D(h;H)\cap D_2$ (resp.
+$\sh_D(v;V)=D(v;V)\cap D_1$).
+  \end{definition}
+
+  The proofs of the following results are identical to the proof of the analogous results from \cite{lee-li-zelevinsky,rupel} for maximal Dyck paths.
+  \begin{lemma}
+    \label{le:shadow statistics}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $h\in H$, take $he$ to be the path $D(h;H)$.
+        The following hold:
+        \begin{enumerate}
+          \item for any proper subpath $he'\subsetneq he$, we have $f_H(he')>0$;
+          \item if $f_H(he)=0$, then for any proper subpath $e'e\subsetneq he$, we have $f_H(e'e)<0$;
+          \item $e\in V$.
+        \end{enumerate}
+      \item For $v\in V$, take $ev$ to be the path $D(v;V)$.
+        The following hold:
+        \begin{enumerate}
+          \item for any proper subpath $e'v\subsetneq ev$, we have $f_V(e'v)>0$;
+          \item if $f_V(ev)=0$, then for any proper subpath $ee'\subsetneq ev$, we have $f_V(ee')<0$;
+          \item $e\in H$.
+        \end{enumerate}
+    \end{enumerate}
+  \end{lemma}
+  \begin{remark}
+    Observe that the subset $V$ has no influence on the claim of (1) and the subset $H$ has no influence on the claim of (2).
+  \end{remark}
+
+  \begin{corollary}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $h\in H$ and a vertical edge $v\in D(h;H)$, the condition \eqref{eq:HGC} is not satisfied for the path $hv$ but for any $V\in\cC_D(H)$ the condition \eqref{eq:VGC} is satisfied for the path $hv$.
+        In particular, $D(v;V)$ is a proper subpath of $hv$ for any $V\in\cC_D(H)$.
+      \item For $v\in V$ and a horizontal edge $h\in D(v;V)$, the condition \eqref{eq:VGC} is not satisfied for the pair $hv$ but for any $H\in\cC_D(V)$ the condition \eqref{eq:HGC} is satisfied for the path $hv$.
+        In particular, $D(h;H)$ is a proper subpath of $hv$ for any $H\in\cC_D(V)$.
+    \end{enumerate}
+  \end{corollary}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item For $H\subset D_1$ and $h,h'\in H$, the local shadows $\sh_D(h;H)$ and $\sh_D(h';H)$ are either disjoint or one is contained in the other.
+      \item For $V\subset D_2$ and $v,v'\in V$, the local shadows $\sh_D(v;V)$ and $\sh_D(v';V)$ are either disjoint or one is contained in the other.
+    \end{enumerate}
+  \end{lemma}
+
+  \begin{definition}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $H$, by removing for each $d\in[1,a_1]$ the first (up to) $c$ vertical edges of depth $d$ immediately following $h_d$.
+      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $V$, by removing for each $\ell\in[0,a_2-1]$ the first (up to) $b$ horizontal edges of height $\ell$ immediately preceding $v_{\ell+1}$.
+    \end{enumerate}
+  \end{definition}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item For $H\subset D_1$, $V\in\cC_D(H)$ if and only if $V$ is disjoint from $\sh_D(H)\setminus\rsh_D(H)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in H$ and $v\in\rsh_D(H)$.
+      \item For $V\subset D_2$, $H\in\cC_D(V)$ if and only if $H$ is disjoint from $\sh_D(V)\setminus\rsh_D(V)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in\rsh_D(V)$ and $v\in V$.
+    \end{enumerate}
+  \end{lemma}
+
+  \begin{definition}
+    For $H\subset D_1$, write $\cC_D^{rsh}(H)$ for the subset of $V\in\cC_D(H)$ with $V\subset\rsh_D(H)$.
+    For $V\subset D_2$, write $\cC_D^{rsh}(V)$ for the subset of $H\in\cC_D(V)$ with $H\subset\rsh_D(V)$.
+  \end{definition}
+
+  \begin{definition}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $1 \le j < d \le a_1$ with $h_j\in H$, denote by $\rsh_D(H)_{j;d}$ the set of all $v\in\rsh_D(H)$ of depth $d$ such that $v\in\sh(h_j;H)$ and $h_j$ is the first horizontal edge before $v$ with this property.
+        Define the \emph{local remote shadow} of the edge $h_j$ by $\rsh_D(h_j;H):=\bigsqcup\limits_{d\in[j+1,a_1]} \rsh_D(H)_{j;d}$.
+      \item For $1 \le \ell <  k \le a_2$ with $v_k\in V$, denote by $\rsh_D(V)_{k;\ell}$ the set of all $h\in\rsh_D(V)$ of height $\ell$ such that $h\in\sh(v_k;V)$ and $v_k$ is the first vertical edge after $h$ with this property.
+        Define the \emph{local remote shadow} of the edge $v_k$ by $\rsh_D(v_k;V):=\bigsqcup\limits_{\ell\in[1,k-1]} \rsh_D(V)_{k;\ell}$.
+    \end{enumerate}
+  \end{definition}
+
+  As shown in \cite{lee-li-zelevinsky} for maximal Dyck paths, the remote shadow can be characterized as follows.
+  \begin{lemma}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $1 \le d < j \le a_1$, we have $\rsh_D(H)_{j;d} \ne \varnothing$ if and only if $f_H(h'h_d^{\!\uparrow}) < 0 < f_H(h_jh^{\!\uparrow})$ for every pair of consecutive horizontal edges $h<h'$ in the path $h_j h_d^{\!\uparrow}$.
+      \item For $1 \le \ell < k \le a_2$, we have $\rsh_D(V)_{k;\ell} \ne \varnothing$ if and only if $f_V({}^\leftarrow\!\!\!
+v_\ell v) < 0 < f_V({}^\leftarrow\!\!\!
+v' v_k)$ for every pair of consecutive vertical edges $v<v'$ in the path ${}^\leftarrow\!\!\!
+v_\ell v_k$.
+    \end{enumerate}
+  \end{lemma}
+
+  \begin{lemma}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item Let $1 \le d < j \le a_1$ and suppose $\rsh_D(H)_{j;d} \ne \varnothing$, then
+        \[|\rsh_D(H)_{j;d}| = \min\limits_{h_j \le h < h' \le h_d} \min\big( -f_H(h'h_d^{\!\uparrow}) , f_H(h_jh^{\!\uparrow}) \big).\]
+      \item Let $1 \le \ell < k \le a_2$ and suppose $\rsh_D(V)_{k;\ell} \ne \varnothing$, then
+        \[|\rsh_D(V)_{k;\ell}| = \min\limits_{v_\ell \le v < v' \le v_k} \min\big( -f_V({}^\leftarrow\!\!\! v_\ell v) , f_V({}^\leftarrow\!\!\! v' v_k) \big).\]
+    \end{enumerate}
+  \end{lemma}
+
+  Then the following result immediately follows from Lemma~\ref{le:shadow statistic recursion}.
+  \begin{corollary}\mbox{}
+    \begin{enumerate}
+      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
+        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
+        Then, for $1 \le d < j \le a_1$, we have $|\rsh_D(H)_{j;d}|=|\rsh_{D'}(V')_{d;j}|$.
+      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
+        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
+        Then, for $1 \le \ell < k \le a_2$, we have $|\rsh_D(V)_{k;\ell}|=|\rsh_{D''}(H'')_{\ell;k}$.
+    \end{enumerate}
+  \end{corollary}
+
+  It follows that, for $H\subset D_1$ and $1 \le d < j \le a_1$, we may define an order-reversing bijection $\theta(H)_{j;d} : \rsh_D(H)_{j;d} \to \rsh_{D'}(V')_{d;j}$.
+  Similarly, for $V\subset D_2$ and $1 \le \ell < k \le a_2$, we may define an order-reversing bijection $\theta(V)_{k;\ell} : \rsh_D(V)_{k;\ell} \to \rsh_{D''}(H'')_{\ell;k}$.
+
+  We associate to $D$ the element $x_D\in\ZZ_{\ge0}[x_1^{\pm1},x_2^{\pm1}]$ defined as follows
+  \[x_D:=x_1^{-a_1} x_2^{-a_2} \sum_{H\sqcup V\in\cC_D} x_1^{b|V|} x_2^{c|H|}.\]
+
+  \begin{theorem}[\cite{lee-li-zelevinsky}]
+    For $(a_1,a_2)=(u_{m,+},u_{m-1,-})$ or $(u_{m-1,+},u_{m,-})$ for $m\ge1$, the element $x_{D^{max}[a_1,a_2]}$ is a non-initial cluster variable.
+    Otherwise, the element $x_{D^{max}_\WA[a_1,a_2]}$ is an element of the greedy basis
+  \end{theorem}
+
+  \begin{lemma}
+    Suppose there are two factorizations
+    \[x_D=x_1^{-a_1} x_2^{-a_2} \sum_{t=0}^{a_2}\sum_{k=0}^{a_1} \nu_{k,t} x_1^{bt}(1+x_2^c)^{a_1-k}=x_1^{-a_1} x_2^{-a_2} \sum_{s=0}^{a_1}\sum_{\ell=0}^{a_2} \theta_{s,\ell} x_2^{cs}(1+x_1^b)^{a_2-\ell},\]
+    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\sh_D(H)|=\ell$.
+    Then 
+    \[\sum_{k=0}^{a_1-s} {a_1-k\choose s} \nu_{k,t}=\sum_{\ell=0}^{a_2-t} {a_2-\ell\choose t} \theta_{s,\ell}\]
+    for all possible $s$ and $t$.
+  \end{lemma}
+  \begin{question}
+    How do such expressions behave under mutations?
+  \end{question}
+
+  \begin{lemma}
+    Choose $a_1,a_2\in\ZZ_{\ge0}$.
+    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_{D^{st}}$ coincides with the corresponding standard monomial basis element.
+  \end{lemma}
+
   \begin{definition}

### 2021-10-05 dominance_regions.tex
Finished explaining the bijection between compatible subsets.

@@
   \begin{corollary}\mbox{}
+    \label{cor:remote shadows}
     \begin{enumerate}
@@
 
-  It follows that, for $H\subset D_1$ and $1 \le d < j \le a_1$, we may define an order-reversing bijection $\theta(H)_{j;d} : \rsh_D(H)_{j;d} \to \rsh_{D'}(V')_{d;j}$.
-  Similarly, for $V\subset D_2$ and $1 \le \ell < k \le a_2$, we may define an order-reversing bijection $\theta(V)_{k;\ell} : \rsh_D(V)_{k;\ell} \to \rsh_{D''}(H'')_{\ell;k}$.
+  In the results below, we keep the notation and assumptions from Corollary~\ref{cor:remote shadows}.
+  It follows that, for $H\subset D_1$ and $1 \le d < j \le a_1$, we may define an order-reversing bijection $\theta^H_{j;d} : \rsh_D(H)_{j;d} \to \rsh_{D'}(V')_{d;j}$.
+  Similarly, for $V\subset D_2$ and $1 \le \ell < k \le a_2$, we may define an order-reversing bijection $\theta^V_{k;\ell} : \rsh_D(V)_{k;\ell} \to \rsh_{D''}(H'')_{\ell;k}$.
+  \begin{definition}\mbox{}
+    \begin{enumerate}
+      \item For $H\subset D_1$ and $V \subset \rsh_D(H)$, define $\Omega_H(V) \subset \rsh_{D'}(V')$ by
+        \[\Omega_H(V)=\{\theta^H_{j;d}(v) : v \in \rsh_D(H)_{j;d}, 1 \le d < j \le a_1\}.\]
+      \item For $V\subset D_2$ and $H \subset \rsh_D(V)$, define $\Omega_V(H) \subset \rsh_{D''}(H'')$ by
+        \[\Omega_V(H)=\{\theta^V_{k;\ell}(h) : h \in \rsh_D(V)_{k;\ell}, 1 \le \ell < k \le a_2\}.\]
+    \end{enumerate}
+  \end{definition}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item Consider $H\subset D_1$ and $V \subset \rsh_D(H)$.
+        Suppose $h'=\theta^H_{j;d}(v)$ for $v\in V$.
+        Then $f_{\Omega_H(V)}(h'v'_d)=f_V(h_j v)$.
+      \item Consider $V\subset D_2$ and $H \subset \rsh_D(V)$.
+        Suppose $v''=\theta^V_{k;\ell}(h)$ for $h\in H$.
+        Then $f_{\Omega_V(H)}(h''_\ell v'')=f_V(h v_k)$.
+    \end{enumerate}
+  \end{lemma}
+
+  The following equivalence of compatibilities is the main result we need.
+  \begin{corollary}\mbox{}
+    \begin{enumerate}
+      \item For $H \subset D_1$ and $V \subset \rsh_D(H)$, we have $V\in\cC_D(H)$ if and only if $\Omega_H(V)\in\cC_{D'}(V')$.
+      \item For $V \subset D_2$ and $H \subset \rsh_D(V)$, we have $H\in\cC_D(V)$ if and only if $\Omega_V(H)\in\cC_{D''}(H'')$.
+    \end{enumerate}
+  \end{corollary}
 

### 2021-12-31 dominance_regions.tex
Mutations stay in the correct subspace.

@@
     \item Is any change required in the theory to handle quantum/generalized or both cases together?
-    \item What do our results mean geometrically in terms of the cluster variety?  Is this constructing an affine chart?
+    \item What do our results mean geometrically in terms of the cluster variety?
   \end{enumerate}
@@
   In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_{\ell'} k_\ell}\ge 0$.
-  The sequence $(k_1,\ldots,k_n)$ (resp. $(k_n,\ldots,k_1)$) is said to be \emph{source-adapted} (resp. \emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
+  The sequence $(k_1,\ldots,k_n)$ (resp.
+$(k_n,\ldots,k_1)$) is then said to be \emph{source-adapted} (resp.
+\emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
   %\sayDR{We need to pin down this convention.}
@@
   For $b\in\ZZ$, write $[b]_+=max(b,0)$.
-  Given a sign $\varepsilon\in\{\pm\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
+  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
   \begin{equation}
@@
   Observe that $E^2_{k,\varepsilon}=\Id$ and $F^2_{k,\varepsilon}=\Id$ for any $k$ and any choice of $\varepsilon$.
+  \begin{lemma}
+    For $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, we have $E_{k,-\varepsilon}E_{k,\varepsilon}=I_n+\varepsilon B^{\bullet k}$ and $E_{k,\varepsilon}-E_{k,-\varepsilon}=\varepsilon B^{\bullet k}$.
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equality $\varepsilon b_{ij}=[\varepsilon b_{ij}]_+-[-\varepsilon b_{ij}]_+$.
+  \end{proof}
 
@@
     Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-    If $\lambda\in\Col(B^t)$, then $\phi^t_k(\lambda)\in\Col(B^{t'})$.
-  \end{lemma}
-  \begin{proof}
-    Suppose $\lambda=B^t\alpha$ for some $\alpha\in\RR^n$.
+    If $\mu\in\lambda+\Col(B^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+  \end{lemma}
+  \begin{proof}
+    Suppose $\mu=\lambda+B^t\alpha$ for some $\alpha\in\RR^n$.
+    Let $\varepsilon$ (resp. $\varepsilon'$) be such that $\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu$ (resp. $\phi^t_k(\lambda)=E^t_{k,\varepsilon'}\lambda$).
     Then 
-    \[\phi^t_k(\lambda)=E^t_{k,\pm}\lambda=E^t_{k,\pm} B^t\alpha=E^t_{k,\pm} B^t F^t_{k,\pm} F^t_{k,\pm}\alpha=B^{t'} F^t_{k,\pm}\alpha\]
-    so that $\phi^t_k(\lambda)\in\Col(B^{t'})$.
+    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+B^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + B^{t'} F^t_{k,\varepsilon}\alpha.\]
+    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + B^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+    Otherwise, 
+    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(B^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(B^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon B^{t'} \lambda_k \mathbf{e}_k\]
+    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
   \end{proof}
@@
 
+  \begin{definition}
+    Given two Dyck paths $D,D'$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $D'\succ D$ if no lattice point of $D'$ lies below a lattice point of $D$.
+  \end{definition}
+  \begin{remark}
+    Equivalently, $D'\succ D$ if no lattice point of $D'$ lies to the right of a lattice point of $D$.
+  \end{remark}
+
+  \begin{proposition}
+    Let $D,D'$ be two Dyck paths in the lattice rectangle $[0,a_1]\times[0,a_2]$ with $D'\succ D$.
+    Identify $D_1$ with $D'_1$ and $D_2$ with $D'_2$ along the natural left-to-right ordering.
+    For subsets $H\subset D_1$ and $V\subset D_2$, write $H'\subset D'_1$ and $V'\subset D'_2$ for the corresponding subsets under the identification above.
+    If $(H,V) \in \cC_D$, then $(H',V') \in \cC_{D'}$.
+  \end{proposition}
+  \begin{proof}
+    It suffices, by induction, to show that the result holds if $D'$ is an immediate successor of $D$, i.e.
+when a single pair of a horizontal followed by a vertical is replaced by a vertical followed by a horizontal.
+    Assume $D'$ is obtained from $D$ in this way, say with horizontal edge $h_i$ and vertical edge $v_j$ satisfying $v_j=h_i+1$ in $D$ replaced by the vertical edge $v'_j$ and the horizontal edge $h'_i$ satisfying $h'_i=v'_j+1$ in $D'$.
+
+    Consider $(H,V) \in \cC_D$.
+    For $h\in H$ and $v\in V$, write $h'\in H'$ and $v'\in V'$ for the corresponding edges.
+    We claim that the condition \eqref{eq:HGC} (resp. \eqref{eq:VGC}) being satisfied for the path $hv$ in $D$ implies the same condition is satisfied for the path $h'v'$ in $D'$.
+
+    Suppose \eqref{eq:HGC} is satisfied for the path $hv$ and write $D(h;H)=he$ for $e\in V$ with $e<v$.
+    If $h_i,v_j\notin D(h;H)$, then under the identification with $D'$ we have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
+    Alternatively, since $e\in V$, we must have both $h_i,v_j\in D(h;H)$.
+    If $h_i\notin H$, then again we have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
+    Thus, we assume $h_i\in H$.
+
+    We begin by assuming $h_i\ne h$.
+    This gives two possibilities for $D(h';H')$ depending on $D(h'_i;H')$.
+    First, observe that $D(h_i;H)$ is a proper subpath of $h_ie$, for otherwise $f_H(h_ie)=0$ and, by the additivity of $f_H$, $he$ would not be the shortest subpath with $f_H(he)=0$.
+    Thus, if $D(h_i;H)$ is followed by at least two vertical edges inside $D(h;H)$, we again have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
+    Otherwise, $D(h';H')$ is an initial subpath of $D(h;H)$ under the identification of $D'$ with $D$ and again \eqref{eq:HGC} is satisfied for the path $h'v'$.
+
+    Now if $h_i=h$...
+  \end{proof}
+
   \begin{corollary}

### 2022-02-14 dominance_regions.tex
More equation massaging
Fixed inequalities

@@
 
-  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following six inequalities:
-  \begin{align}
-    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following inequalities:
+%  \begin{align}
+%    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
+%  \end{align}
+%  Are any of these better forms?
+%  \begin{align}
+%    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%  \end{align}
+%  Another proposal (I also changed the order of the equations)
+%  \begin{align}
+%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
+%    \\
+%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
+%    \\
+%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
+%    \\
+%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{align}
+%  Maybe this one:
+%  \begin{align}
+%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
+%    \\
+%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
+%    \\
+%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
+%    \\
+%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{align}
+%
+%  Yet another version:
+% 
+% {
+%    \everymath={\displaystyle}
+%  \[
+%  \begin{array}{rcccl}
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
+%    \\
+%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
+%    \\
+%    - b \lambda_2 & \geq & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) 
+%    \\
+%    0 & \geq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{array}
+%\]
+%}
+%
+%Or: (Maybe at this point we can remove $c/c$ and $b/b$)
+%
+% {
+%    \everymath={\displaystyle}
+%  \[
+%  \begin{array}{rcccl}
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
+%    \\
+%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2  & \leq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & 0
+%    \\
+%    & & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)  & \leq & - b \lambda_2
+%  \end{array}
+%\]
+%}
+%
+%
+%Or Or: (Maybe at this point we can remove $c/c$ and $b/b$)
+%
+%
+% The following, and possibly all the one before, has a typo
+% {
+%    \everymath={\displaystyle}
+%    \def\arraystretch{2.8}
+%  \[
+%  \begin{array}{rcccl}
+%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
+%    \\
+%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
+%    \\
+%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
+%  \end{array}
+%\]
+%}
+% {
+%    \everymath={\displaystyle}
+%    \def\arraystretch{2.8}
+%  \[
+%  \begin{array}{rcccl}
+%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
+%    \\
+%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
+%    \\
+%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
+%  \end{array}
+%\]
+%}
+  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
+ {
+    \everymath={\displaystyle}
+    \def\arraystretch{2.8}
+  \[
+  \begin{array}{rcccl}
+    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
     \\
-    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+    \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
     \\
-    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
     \\
-    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-    \\
-    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-    \\
-    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
-  \end{align}
-  Are any of these better forms?
-  \begin{align}
-    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-    \\
-    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
-    \\
-    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-    \\
-    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-    \\
-    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-    \\
-    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-    \\
-    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-    \\
-    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-    \\
-    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-    \\
-    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-  \end{align}
-  Another proposal (I also changed the order of the equations)
-  \begin{align}
-    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
-    \\
-    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
-    \\
-    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-    \\
-    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
-    \\
-    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
-    \\
-    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
-  \end{align}
-  Maybe this one:
-  \begin{align}
-    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
-    \\
-    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
-    \\
-    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-    \\
-    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
-    \\
-    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
-    \\
-    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
-  \end{align}
+    \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
+  \end{array}
+\]
+}
 

### 2022-02-21 dominance_regions.tex
Started an introduction, committing to pull.

--- 2021-12-31 dominance_regions.tex
@@
   \begin{abstract}
-    We investigate the shapes of the polytopes defining the dominance order for $\bfg$-vectors in acyclic affine cluster algebras and acyclic cluster algebras of rank two.
-    In both cases, we arrive at a complete description: 
+    We investigate the shapes of the polytopes defining the dominance order for $\bfg$-vectors in cluster algebras of rank two.
+    We arrive at a complete description: 
     \begin{itemize}
       \item cluster monomials are never deformable;
-      \item in affine types, the imaginary $\bfg$-vectors have dominance polytopes which are segments of imaginary $\bfg$-vectors except possibly for a single point on the boundary of an imaginary cone;
-      \item a strange difference emerges in rank two wild types: the imaginary dominance polytopes are kites, triangles, or trapezoids which extend far outside the imaginary cone, the triangles appearing along rays corresponding to columns of the associated Cartan matrix.
+      \item the imaginary dominance polytopes are kites, triangles, or trapezoids which extend far outside the imaginary cone, the triangles appearing along rays corresponding to columns of the associated Cartan matrix.
     \end{itemize}
@@
     \item To what extent can we explicitly/combinatorially describe the eigenvalues/eigenvectors of the twist automorphism/Auslander-Reiten translation acting on imaginary $\bfg$-vectors given a maximal green sequence?
-    \item What role do coefficients play in the dominance order on pointed bases?
     \item Is any change required in the theory to handle quantum/generalized or both cases together?
@@
   \section{Introduction}
-  The investigations of this paper are inspired by the dominance order on the tropical labelings for bases of cluster algebras.
-  This dominance order is used by Qin to understand how these bases may be deformed in the case when there is a green-to-red sequence of mutations.
-  In particular, these calculations can be carried out for any acyclic cluster algebra.
-
-  Our calculations reveal the maximal support possible for a pointed basis which reproduces under mutations.
+  Cluster algebras can be understood geometrically by gluing a collection of algebraic tori along birational morphisms known as mutations.
+  While such a description seems simple at first glance, this structure has been found across much of the range of mathematical objects under current consideration in the literature.
+  To give an idea of how fundamental the process of cluster mutation has come to be understood within mathematics, we note the following (far from exhaustive list of) areas to which this notion is connected: representation theory of artin algebras, especially reflection functors and tilting theory \cite{???}; representation theory of algebraic groups, especially Coxeter groups, double Bruhat cells, and (dual) canonical bases \cite{???}; hyperbolic geometry of surfaces \cite{???}; mathematical physics, especially quiver gauge theories \cite{???}; knot theory, especially the Alexander polynomial \cite{some papers of Schiffler}; algebraic geometry, especially log Calabi-Yau varieties \cite{GHK, GHKK}.
+  To say the least, any advance in the fundamental understanding of cluster algebras is likely to find broad application throughout mathematics.
+
+  The investigations of this paper are inspired by a study of Qin on the deformability of bases which are well-behaved under mutations.
+  More precisely, we study the notion of dominance order on the tropical labellings for bases of cluster algebras pioneered by Qin.
+  As no explicit calculation is carried out in his works, we aim here to initiate a thorough study of the dominance regions for cluster algebras.
+
+  Our calculations reveal the maximal support possible for a pointed basis which remain pointed under all possible mutations.
   In particular, any candidate basis can be ruled out using these results based upon their support alone.

### 2022-02-21 dominance_regions.tex
Some more intro edits

@@
 
+\newcommand{\cA}{\mathcal{A}}
 \newcommand{\cC}{\mathcal{C}}
@@
 \newcommand{\CC}{\mathbb{C}}
+\newcommand{\QQ}{\mathbb{Q}}
 \newcommand{\RR}{\mathbb{R}}
@@
 
-\title{Dominance Regions for Imaginary $\bfg$-vectors}
+\title{Dominance Regions for Rank Two Cluster Algebras}
 
@@
       \item cluster monomials are never deformable;
-      \item the imaginary dominance polytopes are kites, triangles, or trapezoids which extend far outside the imaginary cone, the triangles appearing along rays corresponding to columns of the associated Cartan matrix.
+      \item the imaginary dominance polytopes are kites, triangles, or trapezoids which extend far outside the imaginary cone; the triangles appearing along rays corresponding to columns of the associated Cartan matrix.
     \end{itemize}
@@
   While such a description seems simple at first glance, this structure has been found across much of the range of mathematical objects under current consideration in the literature.
-  To give an idea of how fundamental the process of cluster mutation has come to be understood within mathematics, we note the following (far from exhaustive list of) areas to which this notion is connected: representation theory of artin algebras, especially reflection functors and tilting theory \cite{???}; representation theory of algebraic groups, especially Coxeter groups, double Bruhat cells, and (dual) canonical bases \cite{???}; hyperbolic geometry of surfaces \cite{???}; mathematical physics, especially quiver gauge theories \cite{???}; knot theory, especially the Alexander polynomial \cite{some papers of Schiffler}; algebraic geometry, especially log Calabi-Yau varieties \cite{GHK, GHKK}.
+  To give an idea of how fundamental the process of cluster mutation has come to be understood within mathematics, we note the following (far from exhaustive list of) areas to which this notion is connected: representation theory of artin algebras, especially reflection functors and tilting theory \cite{???}; representation theory of algebraic groups, especially Coxeter groups, double Bruhat cells, and (dual) canonical bases \cite{???}; hyperbolic geometry of Riemann surfaces \cite{???}; mathematical physics, especially quiver gauge theories \cite{???}; knot theory, especially the Alexander polynomial \cite{some papers of Schiffler}; algebraic geometry, especially log Calabi-Yau varieties \cite{GHK, GHKK}.
   To say the least, any advance in the fundamental understanding of cluster algebras is likely to find broad application throughout mathematics.
@@
   As no explicit calculation is carried out in his works, we aim here to initiate a thorough study of the dominance regions for cluster algebras.
-
-  Our calculations reveal the maximal support possible for a pointed basis which remain pointed under all possible mutations.
+  We begin in the setting of cluster algebras of rank 2, i.e. containing a pair of mutable cluster variables, with no frozen variables.
+
+  Fix integers $b,c>0$ and assume $bc\ge4$.
+  When $bc\le3$, the cluster algebra will be of finite-type and the resulting basis of cluster monomials is not deformable \cite{???}.
+  The cluster algebra $\cA(b,c)$ is the $\ZZ$-subalgebra of $\QQ(x_1,x_2)$ generated by \emph{cluster variables} $x_m$, $m\in\ZZ$, defined recursively by
+  \begin{equation}
+    x_{m-1}x_{m+1}=\begin{cases} x_m^b+1 & \text{if $m$ is odd;}\\ x_m^c+1 & \text{if $m$ is even.} \end{cases}
+  \end{equation}
+  By the Laurent Phenomenon \cite{fomin-zelevinsky}, each $x_m$ is actually an element of $\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for any $k\in\ZZ$.
+  Moreover, these Laurent polynomials are known to have positive coefficients \cite{lee-schiffler,GHKK}.
+
+  Our goal in this note is to explicitly compute the possible bases which are \emph{pointed} with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
+  That is, each basis element can be written in the form $\sum\limits_{a_1,a_2 \ge 0} c_{a_1,a_2} x_1^{\lambda_1-ba_1} x_2^{\lambda_2+ca_2}$ with $c_{0,0}=1$ for some $\lambda\in\ZZ^2$ and this structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
+
+  Our calculations reveal the maximal support possible for a pointed basis which remains pointed under all possible mutations.
   In particular, any candidate basis can be ruled out using these results based upon their support alone.
+
+  \begin{theorem}
+    The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
+    {
+      \everymath={\displaystyle}
+      \def\arraystretch{2.8}
+      \[
+        \begin{array}{rcccl}
+          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
+          \\
+          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
+          \\
+          0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
+          \\
+          \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
+        \end{array}
+      \]
+    }
+  \end{theorem}
 

### 2022-02-21 dominance_regions.tex
More thoughts into the introduction.

@@
   Our goal in this note is to explicitly compute the possible bases which are \emph{pointed} with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
-  That is, each basis element can be written in the form $\sum\limits_{a_1,a_2 \ge 0} c_{a_1,a_2} x_1^{\lambda_1-ba_1} x_2^{\lambda_2+ca_2}$ with $c_{0,0}=1$ for some $\lambda\in\ZZ^2$ and this structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
-
-  Our calculations reveal the maximal support possible for a pointed basis which remains pointed under all possible mutations.
-  In particular, any candidate basis can be ruled out using these results based upon their support alone.
-
+  That is, each basis element $x_\lambda$, with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$, can be written in the form $\sum\limits_{a_1,a_2 \ge 0} c^\lambda_{a_1,a_2} x_1^{\lambda_1-ba_1} x_2^{\lambda_2+ca_2}$ with $c_{0,0}=1$ and this structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
+
+  More specifically, we compute the possible transitions between any two pointed bases.
+  The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
   \begin{theorem}
@@
   \end{theorem}
+
+  Our calculations reveal the maximal support possible for a pointed basis which remains pointed under all possible mutations.
+  In particular, any candidate basis can be ruled out using these results based upon their support alone.
+
+  A number of bases for rank two cluster algebras with various defining properties have been defined.
+  A natural starting basis is the so-called \emph{greedy basis} in which all $c^\lambda_{a_1,a_2}$ are non-negative and these coefficients are chosen to be minimal.
+  It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
+  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications with the subalgebras of $\ZZ[x_1^{\pm1},x_2^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
+  However, these bases depend on $k$ and the triangular basis is defined by a triangular transition with the stipulation that the basis does not depend on the choice of starting cluster.
+  It would be useful to explicitly (or combinatorially) compute the transitions between these bases.
+  However, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.
 

### 2022-02-21 dominance_regions.tex
Edits while talking

@@
 \usepackage{amsmath,amssymb,latexsym,color,ulem}
-\usepackage[margin=1.5in]{geometry}
+\usepackage[margin=1in]{geometry}
 \usepackage{tikz}
@@
   However, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.
+
+  \begin{theorem}
+    There are six classes of dominance polytopes.
+    \begin{enumerate}
+      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cC(\lambda)$ is the point $\lambda$. 
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}((2-bc)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2)$.
+      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cC(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
+      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,-c\lambda_1+(2-bc)\lambda_2)$.
+    \end{enumerate}
+  \end{theorem}
+  \begin{proof}
+    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
+    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
+    or 
+    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
+    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
+    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
+  \end{proof}
+
+  \begin{remark}
+    Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
+    This unexpected coincidence is one of our reasons for deciding to write down these results.
+  \end{remark}
 

### 2022-03-07 dominance_regions.tex
more intro edits

@@
 \documentclass{amsart}
-\usepackage{amsmath,amssymb,latexsym,color,ulem}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{latexsym}
+\usepackage{color}
+%\usepackage{ulem}
 \usepackage[margin=1in]{geometry}
@@
 \newtheorem{remark}[theorem]{Remark}
+\newtheorem{conjecture}[theorem]{Conjecture}
 \newtheorem{question}{Question}
@@
 
+\newcommand{\bfa}{\boldsymbol{a}}
 \newcommand{\bfc}{\boldsymbol{c}}
@@
 
+\newcommand{\kk}{\Bbbk}
+
 \title{Dominance Regions for Rank Two Cluster Algebras}
@@
     \end{itemize}
-    We conjecture how our observations might generalize to higher dimensions.
   \end{abstract}
@@
 
-  \section{Questions}
-  \begin{enumerate}
-    \item To what extent can we explicitly/combinatorially describe the eigenvalues/eigenvectors of the twist automorphism/Auslander-Reiten translation acting on imaginary $\bfg$-vectors given a maximal green sequence?
-    \item Is any change required in the theory to handle quantum/generalized or both cases together?
-    \item What do our results mean geometrically in terms of the cluster variety?
-  \end{enumerate}
-
   \section{Introduction}
-  Cluster algebras can be understood geometrically by gluing a collection of algebraic tori along birational morphisms known as mutations.
-  While such a description seems simple at first glance, this structure has been found across much of the range of mathematical objects under current consideration in the literature.
-  To give an idea of how fundamental the process of cluster mutation has come to be understood within mathematics, we note the following (far from exhaustive list of) areas to which this notion is connected: representation theory of artin algebras, especially reflection functors and tilting theory \cite{???}; representation theory of algebraic groups, especially Coxeter groups, double Bruhat cells, and (dual) canonical bases \cite{???}; hyperbolic geometry of Riemann surfaces \cite{???}; mathematical physics, especially quiver gauge theories \cite{???}; knot theory, especially the Alexander polynomial \cite{some papers of Schiffler}; algebraic geometry, especially log Calabi-Yau varieties \cite{GHK, GHKK}.
-  To say the least, any advance in the fundamental understanding of cluster algebras is likely to find broad application throughout mathematics.
-
-  The investigations of this paper are inspired by a study of Qin on the deformability of bases which are well-behaved under mutations.
-  More precisely, we study the notion of dominance order on the tropical labellings for bases of cluster algebras pioneered by Qin.
-  As no explicit calculation is carried out in his works, we aim here to initiate a thorough study of the dominance regions for cluster algebras.
-  We begin in the setting of cluster algebras of rank 2, i.e. containing a pair of mutable cluster variables, with no frozen variables.
-
-  Fix integers $b,c>0$ and assume $bc\ge4$.
-  When $bc\le3$, the cluster algebra will be of finite-type and the resulting basis of cluster monomials is not deformable \cite{???}.
-  The cluster algebra $\cA(b,c)$ is the $\ZZ$-subalgebra of $\QQ(x_1,x_2)$ generated by \emph{cluster variables} $x_m$, $m\in\ZZ$, defined recursively by
+  Cluster algebras were introduced by Fomin and Zelevinsky as a tool in the study of Lusztig's (dual) canonical bases.
+  Since their inception they have found application in a variety of different areas in mathematics, nevertheless a fundamental problem in the theory remains constructing bases with ``good'' properties.
+
+  Over time several bases have been constructed in a variety of generalities \cite{foo,bar,baz}. 
+  All of them share a property of being ``pointed''.
+  Being pointed turned out to be a desireable feature for a basis to have and a natural question is to find all bases enjoying this property.
+  Recently Qin introduced the notion of \emph{dominance} and showed that it completely encapsulates the deformability of pointed bases whenever the cluster algebra has full rank \cite{Qin}. 
+  As no explicit calculation is carried out in his work, we aim here at describing explicitly the space of deformability of pointed bases in rank 2, i.e.
+when clusters contain a pair of mutable cluster variables.
+  In this setting, frozen variables do not carry any additional information and we can work in the coefficient-free case.
+
+  Fix integers $b,c>0$.  The cluster algebra $\cA(b,c)$ is the $\ZZ$-subalgebra of $\QQ(x_1,x_2)$ generated by \emph{cluster variables} $x_m$, $m\in\ZZ$, defined recursively by
   \begin{equation}
@@
   Our goal in this note is to explicitly compute the possible bases which are \emph{pointed} with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
-  That is, each basis element $x_\lambda$, with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$, can be written in the form $\sum\limits_{a_1,a_2 \ge 0} c^\lambda_{a_1,a_2} x_1^{\lambda_1-ba_1} x_2^{\lambda_2+ca_2}$ with $c_{0,0}=1$ and this structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
-
-  More specifically, we compute the possible transitions between any two pointed bases.
-  The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
+  That is, a basis element, with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$ when expanded in terms of $\{x_1,x_2\}$, can be written in the form
+  \[
+    x_1^{\lambda_1}x_2^{\lambda_2}\sum\limits_{a_1,a_2 \ge 0} c^\lambda_{a_1,a_2} x_1^{-ba_1} x_2^{ca_2}
+  \]
+  with $c_{0,0}=1$ and an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
+  %The collection of all $\bfg$-vectors $\lambda\in\ZZ^2$ parametrize the elements of any pointed basis.
+
+  Important examples of pointed elements are the \emph{cluster monomials} of $\cA(b,c)$, i.e.
+the elements that can be written in the form $x_k^{a_k}x_{k+1}^{a_{k+1}}$ for some $k\in\ZZ$ and $a_k,a_{k+1}$ non-negative integers.
+  Indeed, by [someresult of Qin] cluster monomials are part of any pointed basis in any cluster algebra.
+  \say{Check if this needs full rank}
+
+  Elements of any pointed basis are parametrized by their $\bfg$-vectors.
+  Qin introduced a partial order on $\bfg$-vectors called the \emph{dominance order} and showed that given two pointed basis $x=\{x_\lambda\}$, $y=\{y_\lambda\}$, $y_\mu$ can appear in the expansion of $x_\lambda$ in terms of $y$ only if $\lambda$ dominates $\mu$ (cf.
+\cite[Mainthm]{Qin} and \ref{below}).
+
+  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
+  We will therefore assume that $bc\ge4$.
+  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\lambda+(b\ZZ\oplus c\ZZ)$-lattice points in its \emph{dominance polygon}.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$ inside its \emph{dominance polygon} for integers $a_1,a_2$.
+  %In this case, we compute the possible transitions between any two pointed bases.
+  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
   \begin{theorem}
@@
 
-  Suppose $B$ is acyclic.
-  Given a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, define a quiver $Q_{B,\varepsilon}$ from $Q_B$ by removing all arrows starting at vertex $i$ whenever $\varepsilon_i=-1$.
-  For $1\le j\le n$, define $\cP_j(Q_{B,\varepsilon})$ as the set of paths in $Q_{B,\varepsilon}$ starting at vertex $j$.
-  Elements of $\cP_j(Q_{B,\varepsilon})$ are sequences of vertices $(p_1,\ldots,p_r)$ with $p_1=j$ and $b_{p_{t+1}p_t}>0$ for $1\le t\le r-1$.
-  Given a path $p\in\cP_j(Q_{B,\varepsilon})$, a vertex $i\in Q_0$, and a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, set
-  \[\wt_{i,\varepsilon}(p):=-b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}\prod_{t=1}^{r-1} b_{p_{t+1}p_t},\]
-  where the prefactor $b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}$ is omitted if $i=p_r$ or $\varepsilon_{p_r}=-1$.
-  \begin{lemma}
-    Suppose $B$ is acyclic with source-adapted sequence $k_1,\ldots,k_n$.
-    Consider $t_1,\ldots,t_n\in\TT_n$ so that $t_{\ell-1}$ is joined to $t_\ell$ by an edge in $\TT_n$ labeled by $k_\ell$ for $1\le\ell\le n$.
-    For a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, the product $E^{t_{n-1}}_{k_n,\varepsilon_{k_n}}\cdots E^{t_0}_{k_1,\varepsilon_{k_1}}$ is given by $\tau=(\tau_{ij})$ with
-    \begin{equation}
-      \label{eq:tropical twist}
-      \tau_{ij}=\sum_{p\in\cP_j(Q_{B,\varepsilon})}^* \wt_{i,\varepsilon}(p),
-    \end{equation}
-    where the $*$ indicates that the summation includes the trivial path at $j$ only if $i\le j$ when $\varepsilon_j=1$ and only if $i=j$ when $\varepsilon_j=-1$.
-
-    Then $\phi_{t_n}$ is the following piecewise-linear automorphism:
-    \begin{equation}
-      \label{eq:tropical twist}
-      \text{(This is going to require casework with the possible signs, we'll really only need it for imaginary $\bfg$-vectors though.)}
-    \end{equation}
-    The answer comes from selectively ``turning off'' arrows out of chosen vertices as indicated by choosing $\varepsilon_i=-1$.
-  \end{lemma}
-  \begin{proof}
-    We prove the following modified formula for the product $E^{t_{n-1}}_{k_n,\varepsilon_{k_n}}\cdots E^{t_{m-1}}_{k_m,\varepsilon_{k_m}}$ for $1\le m\le n$ by reverse induction on $m$.
-    Writing this matrix as $\tau^{(m)}=(\tau^{(m)}_{ij})$, we claim that
-    \begin{equation}
-      \label{eq:tropical twist}
-      \tau^{(m)}_{ij}=\begin{cases} \sum\limits_{p\in\cP_j(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) & \text{if $j=k_\ell$ with $m\le\ell$;}\\ \delta_{ij} & \text{otherwise;} \end{cases}
-    \end{equation}
-    where $Q_{B,\varepsilon}^{(m)}$ is the full subquiver of $Q_{B,\varepsilon}$ on vertices $k_m,\ldots,k_n$.
-    Note that the weight function follows the same definition as above.
-
-    Since the sequence $k_1,\ldots,k_n$ is source-adapted, the matrix $E^{t_{m-1}}_{k_m,\varepsilon_m}$, for $1\le m\le n$, has entries $e^{(m)}_{ij}$ given by
-    \begin{equation}
-      \label{eq:source mutation matrix}
-      e^{(m)}_{ij}=\begin{cases} 1 & \text{if $i=j\ne k_m$;}\\ -1 & \text{if $i=j=k_m$;}\\ [-\varepsilon_{k_m} b_{ik_m}]_+ & \text{if $i=k_\ell$, $j=k_m$, $\ell<m$;}\\ [\varepsilon_{k_m} b_{ik_m}]_+ & \text{if $i=k_\ell$, $j=k_m$, $m<\ell$;}\\ 0 & \text{otherwise;} \end{cases}
-    \end{equation}
-    the entries for $\ell<m$ picking up the sign from the prior matrix mutations.
-
-    For $m=n$, it is clear that $\tau^{(n)}_{ij}=e^{(n)}_{ij}$ for $j\ne k_n$.
-    If $\varepsilon_{k_n}=1$, there is only the trivial path $(k_n)$ in $Q_{B,\varepsilon}^{(n)}$ and we have $\tau^{(n)}_{ik_n}=-b_{ik_n}$, which agrees with $e^{(n)}_{ik_n}$ in this case.
-    Otherwise, $\varepsilon_{k_n}=-1$ and the sum is empty for $i\ne k_n$ giving $\tau^{(n)}_{ik_n}=0=e^{(n)}_{ik_n}$ or only takes the trivial path for $i=k_n$ giving $\tau^{(n)}_{k_nk_n}=-1=e^{(n)}_{k_nk_n}$.
-    This gives the base of the induction.
-
-    Now suppose the matrix $\tau^{(m)}$ is given as above.
-    Using equation \eqref{eq:source mutation matrix}, we need to check that 
-    \begin{equation}
-      \label{eq:twist matrix recursion}
-      \tau^{(m-1)}_{ij}=\sum\limits_{p=1}^n \tau^{(m)}_{ip} e^{(m-1)}_{pj}=\begin{cases} \tau^{(m)}_{ij} & \text{if $j\ne k_{m-1}$;}\\ -\tau^{(m)}_{ik_{m-1}} + \sum\limits_{\ell=1}^{m-2} \tau^{(m)}_{i k_\ell} [-\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ + \sum\limits_{\ell=m}^n \tau^{(m)}_{i k_\ell} [\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ & \text{if $j=k_{m-1}$;}\end{cases}
-    \end{equation}
-    is computed by the formula above.
-    First observe that $\tau^{(m-1)}_{ij}=\tau^{(m)}_{ij}=\delta_{ij}$ if $j=k_\ell$ with $\ell<m-1$.  
-    Second observe that $\cP_j(Q_{B,\varepsilon}^{(m-1)})=\cP_j(Q_{B,\varepsilon}^{(m)})$ whenever $j=k_\ell$ with $m\le\ell$, i.e.
-the purported formulas for $\tau^{(m-1)}_{ij}$ and $\tau^{(m)}_{ij}$ agree in this case.
-    Therefore it remains to show that
-    \[
-      \tau^{(m-1)}_{i k_{m-1}}=-\delta_{ik_{m-1}} + \sum\limits_{\ell=1}^{m-2} \delta_{i k_\ell} [-\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ + \sum\limits_{\ell=m}^n \sum\limits_{p\in\cP_{k_\ell}(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) [\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+
-    \]
-    agrees with the desired expression.
-    Indeed, for $\varepsilon_{k_{m-1}}=-1$ this reduces to $\tau^{(m-1)}_{i k_{m-1}}=-\delta_{i k_{m-1}}$ which matches with the desired expression in this case.
-    Then assuming $\varepsilon_{k_{m-1}}=1$, we are comparing with
-    \[
-      \tau^{(m-1)}_{i k_{m-1}}=-\delta_{ik_{m-1}} - \sum\limits_{\ell=1}^{m-2} \delta_{i k_\ell} b_{k_\ell k_{m-1}} + \sum\limits_{\ell=m}^n \sum\limits_{p\in\cP_{k_\ell}(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) b_{k_\ell k_{m-1}}.
-    \]
-    But observe that the final summation above contributes the nontrivial paths to the summation $\sum\limits_{p\in\cP_{k_{m-1}}(Q_{B,\varepsilon}^{(m-1)})}^* \wt_{i,\varepsilon}(p)$ while the first two terms above give the contribution, depending on $i$, corresponding to the trivial path $(k_{m-1})$.
-  \end{proof}
-  \begin{question}
-    Is the trace of $\tau$ an invariant of matrix mutations?
-P.A.: It is invariant under sink and source mutations since the trace is a class function and these mutations simply enact a cyclic shift in the factors of $\tau$.
-  \end{question}
-
   For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
@@
     \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
-  \end{proof}
-
-  \section{Affine Types}
-  Associated to an acyclic skew-symmetrizable matrix $B=(b_{ij})$ there is a Cartan matrix $A=(a_{ij})$ with $a_{ii}=2$ and $a_{ij}=-|b_{ij}|$.
-  We say that $B$ is of affine type if its associated Cartan matrix gives rise to an affine Dynkin diagram.
-  In this section, we focus on understanding the dominance polytopes for affine matrices $B$.
-
-  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable matrix of affine type with associated Cartan matrix $A=(a_{ij})$.
-
-  \begin{lemma}
-    One column is always in the positive span of the other columns.
-  \end{lemma}
-
-  \begin{definition}
-    Describe imaginary $\bfg$-vectors and those corresponding to cluster monomials.
-  \end{definition}
-
-  \begin{lemma}
-    Let $\lambda\in\ZZ^n$ correspond to a cluster monomial.
-    Then $\cP(\lambda)=\{\lambda\}$.
-  \end{lemma}
-  \begin{proof}
-    An explicit sequence of sink/source mutations should suffice.
   \end{proof}
@@
 
+  \section{Chebyshev}
+  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
+  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
+
+  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
+  This leads to the following more general recursive structure.
+  \begin{lemma}
+    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
+    \begin{equation}
+      \label{eq:long Chebyshev recursion}
+      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
+    \end{equation}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
+    Using the claim for $j>0$ and then the defining recursion twice, we get
+    \begin{align*}
+      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
+    \end{align*}
+    which is the claimed recursion for $\ell+1$.
+    These calculations can be reversed to show the result for $\ell<0$.
+  \end{proof}
+
+  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
+  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
+  By the equalities 
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
+  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+  \begin{remark}
+    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
+    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
+  \end{remark}
+
+  \begin{lemma}
+    We have
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+  \end{lemma}
+  \begin{proof}
+    For any $i\ge 1$, we have
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
+    It follows that
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    which is equivalent to the desired expression.
+    Similarly, 
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
+    so that
+    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    which is again equivalent to the desired expression.
+  \end{proof}
+
+  \section{The affine case}
+  In this section we compare our main result with the construction of \cite{RSW19} in the case $b=c=2$.
+  We show that the continuous family of bases constructed there is precisely the deformation family constructed by \cite{Qin}.
+
+We want to show that our continuous family of generalized minors from \cite[Theorem 4.6]{RSW19} coincide with the family of bases constructed in \cite[Theorem 1.2.1]{Qin19}.
+
+This boils down to show, for any $n>1$, that
+\begin{enumerate}
+  \item 
+    the set of $\bfg$-vectors that are dominated by $n\omega^\circ$ with respect to any seed is 
+    \[
+      \left\{(n-2r)\omega^\circ \right\}_{r\in\left[1,\left\lfloor\frac{1}{2}\right\rfloor\right]}
+    \]
+
+  \item
+    we can choose a specific basis and rewrite the last formula in \cite[Proposition 4.4]{RSW19} as in \cite[Theorem 1.2.1]{Qin19} with coefficients being functions of the point $\bfa\in(\kk^\times)^n$.
+\end{enumerate}
+
+For a partition $\lambda \vdash n$ let $e_\lambda$, $s_\lambda$, and $m_\lambda$ denote the elementary, Shur, and monomial symmetric functions associated to the partition $\lambda$ evaluated at $\bfa$.
+Recall that $m_{1^{(n)}} = s_{1^{(n)}} = e_n$.
+
+\begin{lemma}
+  For every $r\in\left[1,\left\lfloor\frac{1}{2}\right\rfloor\right]$ we have $m_{1^{(n)}} S_{\bfa,r} = m_{2^{(r)},1^{(n-2r)}}$.
+\end{lemma}
+\begin{proof}
+  This is immediate from the definition.
+\end{proof}
+
+Let $F_{n\omega^\circ}^\Delta$, $F_{n\omega^\circ}^{gr}$, $F_{n\omega^\circ}^{tr}$, and $F_{n\omega^\circ}^{ge}$ be the $F$-polynomials of the generalized minor, greedy basis element, triangular basis element, and generic basis element with $\bfg$-vector $n\omega^\circ$.
+We think of $F$-polynomials as polynomials in the variables $u_1$ and $u_2$.
+
+I did not try yet to prove (1) but it should be straightforward.
+It suffices to establish (2) for the $F$-polynomials.
+
+\begin{proposition}
+  \[
+    m_{1^{(n)}} F_{n\omega^\circ}^\Delta
+    =
+    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
+    m_{2^{(k)},1^{(n-2r)}}
+    u_1^r u_2^r
+    F_{(n-2r)\omega^\circ}^{ge}
+  \]
+\end{proposition}
+\begin{proof}
+  From \cite[Proposition 4.4]{RSW19} we get the following expression for $F_{n\omega^\circ}^\Delta$:
+  \[
+     F_{n\omega^\circ}^\Delta 
+     =
+     \sum_{0 \le k \le \ell \le n}
+     \sum_{r=0}^\ell
+     {\ell -r \choose k}
+     {n-2r \choose \ell-r}
+     S_{\bfa,r}
+     u_1^\ell u_2^{\ell-k}.
+   \]
+  From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor \frac{n}{2} \rfloor$.
+  We compute
+  \begin{align*}
+    m_{1^{(n)}}  F_{n\omega^\circ}^\Delta 
+    &
+    =
+    \sum_{0 \le k \le \ell \le n}
+    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
+    {\ell -r \choose k}
+    {n-2r \choose \ell-r}
+    m_{2^{(r)},1^{(n-2r)}}
+    u_1^\ell u_2^{\ell-k}
+    \\
+    &=
+    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
+    m_{2^{(r)},1^{(n-2r)}}
+    u_1^r u_2^r
+    \sum_{0 \le k \le \ell \le n}
+    {\ell -r \choose k}
+    {n-2r \choose \ell-r}
+    u_1^{\ell-r} u_2^{\ell-r-k}
+    \\
+    &=
+    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
+    m_{2^{(r)},1^{(n-2r)}}
+    u_1^r u_2^r
+    F_{(n-2r)\omega^\circ}^{ge}.
+  \end{align*}
+  The last identity follows immediately by comparing with the formula for generic basis elements in \cite{RSW19}.
+  \saySS{Thank you Dylan for fixing my stupidity.}
+\end{proof}
+
+We do not need the following two formulas but I think they are still neat.
+\begin{conjecture}
+  \begin{align*} 
+    m_{1^{(n)}} F_{n\omega^\circ}^\Delta
+    &=
+    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
+    s_{2^{(k)},1^{(n-2r)}}
+    u_1^r u_2^r
+    F_{(n-2r)\omega^\circ}^{tr}
+    \\&=
+    \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
+    e_{r,n-r}
+    u_1^r u_2^r
+    F_{(n-2r)\omega^\circ}^{gr}
+  \end{align*}
+\end{conjecture}
+
 \end{document}

### 2022-03-28 dominance_regions.tex
Finished typing Theorem 1.4, other random edits.

@@
 \newcommand{\cQ}{\mathcal{Q}}
+\newcommand{\cS}{\mathcal{S}}
 
@@
   In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
-  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\lambda+(b\ZZ\oplus c\ZZ)$-lattice points in its \emph{dominance polygon}.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\lambda+(b\ZZ\oplus c\ZZ)$-lattice points in its \emph{dominance polygon} $\cP(\lambda)$.
   Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$ inside its \emph{dominance polygon} for integers $a_1,a_2$.
@@
     \begin{enumerate}
-      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cC(\lambda)$ is the point $\lambda$. 
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}((2-bc)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2)$.
-      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cC(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
-      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,-c\lambda_1+(2-bc)\lambda_2)$.
+      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
     \end{enumerate}
   \end{theorem}
-  \begin{proof}
-    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
-    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
-    or 
-    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
-    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
-    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
-  \end{proof}
 
@@
   \end{remark}
+
+  Given a Laurent polynomial in $\ZZ[x_1^{\pm1},x_2^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
+  \begin{theorem}
+    For a $\bfg$-vector $\lambda=(\lambda_1,\lambda_2)\in\ZZ^2$ the support for a pointed basis vector $x_\lambda$ is contained in the (possibly degenerate) lattice quadrilateral $\cS_\lambda$ given as follows:
+    \begin{enumerate}
+      \item If $\lambda$ lies outside of $\cI$, there are the following possibilities:
+        \begin{enumerate}
+          \item If $0\le\lambda_1,\lambda_2$, then $\cS_\lambda$ is just the point $\lambda$.
+          \item If $\lambda_1 < 0$ and $0\le\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1,-c\lambda_1+\lambda_2)$.
+          \item If $\lambda_2 < 0$ and $0\le\lambda_1+b\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1+b\lambda_2,\lambda_2)$.
+          \item If $\lambda_1,\lambda_2 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(\lambda_1,-c\lambda_1+\lambda_2)$.
+          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc-1)\lambda_1+(b^2c-2b)\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
+          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $0 < -c\lambda_1-(bc-1)\lambda_2$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(0,0)$.
+        \end{enumerate}
+      \item If $\lambda$ lies inside of $\cI$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
+    \end{enumerate}
+  \end{theorem}
+  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
+  For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
+  \begin{enumerate}
+    \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
+    \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
+    \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
+    \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
+    \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
+    \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
+    $$\aligned
+    R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
+    &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
+    &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
+    \endaligned
+    $$
+  \end{enumerate}
+  Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
+\end{theorem}
+\begin{figure}[h!]
+  \centering
+  \begin{tikzpicture}[scale=.7]
+    %(1)
+    \begin{scope}[shift={(-2.75, 5.5)}]
+      \usetikzlibrary{patterns}
+      \draw[-] (-0.5,0.25) -- (3,0.25);
+      \draw[-] (0,-0.25) -- (0,3);
+      \fill[white] (0,0.25) circle (2pt);
+      \draw (0,0.25) circle (2pt);
+      \draw (0,0.25) node[anchor=south west] {\tiny $O$};
+      \fill (1.5,1.75) circle (2pt);
+      \draw (1.5,1.75) node[anchor=east] {\tiny $B$};
+      \draw (1.07,-.6) node[anchor=north] {\footnotesize (1) $a_1,a_2\le0$};
+    \end{scope}
+    %(2)
+    \begin{scope}[shift={(2.75, 5.5)}]
+      \usetikzlibrary{patterns}
+      \draw[-] (-0.5,1.5) -- (3,1.5);
+      \draw[-] (0,-0.25) -- (0,3);
+      \fill[white] (0,1.5) circle (2pt);
+      \draw (0,1.5) circle (2pt);
+      \draw (0,1.5) node[anchor=south west] {\tiny $O$};
+      \fill (2.25,0.5) circle (2pt);
+      \draw (2.25,0.5) node[anchor=west] {\tiny$A$};
+      \fill (0.75,0.5) circle (2pt);
+      \draw (0.75,0.5) node[anchor=east] {\tiny$B$};
+      \draw [thick] (0.75,0.5) -- (2.25,0.5);
+      \draw (1.27,-.6) node[anchor=north] {\footnotesize (2) $a_1\le 0<a_2$};
+    \end{scope}
+    %(3)
+    \begin{scope}[shift={(8.25,5.5)}]
+      \usetikzlibrary{patterns}
+      \draw [thick] (0.25,1) -- (0.25,2.5);
+      \draw[-] (-0.5,0.25) -- (3,0.25);
+      \draw[-] (1,-0.25) -- (1,3);
+      \fill[white] (1,0.25) circle (2pt);
+      \draw (1,0.25) circle (2pt);
+      \draw (1,0.25) node[anchor=south west] {\tiny $O$};
+      \fill (0.25,1) circle (2pt);
+      \draw (0.25,1) node[anchor=east] {\tiny$B$};
+      \fill (0.25,2.5) circle (2pt);
+      \draw (0.25,2.5) node[anchor=east] {\tiny$C$};
+      \draw (1.27,-.6) node[anchor=north] {\footnotesize (3) $a_2\le0<a_1$};
+    \end{scope}
+    %(4)
+    \begin{scope}[shift={(0,0)}]
+      \usetikzlibrary{patterns}
+      \fill[black!10] (0,3)--(1.5,1.5)--(1.5,0)--(0,0)--(0,3);
+      \draw[thick] (0,3)--(1.5,1.5)--(1.5,0)--(0,0)--(0,3);
+      \draw[dashed,thick](0,3)--(2.15,1.25) (2.15,1.15)--(1.5,0);
+      \draw[-] (-0.5,1.2) -- (3.5,1.2);
+      \draw[-] (2.2,-0.25) -- (2.2,3.5);
+      \fill[white] (2.2,1.2) circle (2pt);
+      \draw (2.2,1.2) circle (2pt);
+      \draw (2.2,1.2) node[anchor=north west] {\tiny$O$};
+      \fill (1.5,0) circle (2pt);
+      \draw (1.5,0) node[anchor=west] {\tiny$A$};
+      \fill (0,0) circle (2pt);
+      \draw (0,0) node[anchor=east] {\tiny$B$};
+      \fill (0,3) circle (2pt);
+      \draw (0,3) node[anchor=east] {\tiny$C$};
+      \fill (1.5,1.5) circle (2pt);
+      \draw (1.5,1.5) node[anchor=east] {\tiny$D_1$};
+      \draw (1.37,-0.5) node[anchor=north] {\footnotesize (4) $0<ba_2\leq a_1$};
+    \end{scope}
+    %(5)
+    \begin{scope}[shift={(5.5,0)}]
+      \usetikzlibrary{patterns}
+      \fill[black!10] (3,0)--(1.3,1)--(0,1)--(0,0)--(3,0);
+      \draw[thick] (3,0)--(1.3,1)--(0,1)--(0,0)--(3,0);
+      \draw[dashed,thick](3,0)--(0.75,1.75)--(0,1);
+      \draw[-] (-0.5,1.75) -- (3.5,1.75);
+      \draw[-] (0.75,-0.25) -- (0.75,3.5);
+      \fill[white] (0.75,1.75) circle (2pt);
+      \draw (0.75,1.75) circle (2pt);
+      \draw (0.75,1.75) node[anchor=south west] {\tiny$O$};
+      \fill (3,0) circle (2pt);
+      \draw (3,0) node[anchor=west] {\tiny$A$};
+      \fill (0,0) circle (2pt);
+      \draw (0,0) node[anchor=east] {\tiny$B$};
+      \fill (0,1) circle (2pt);
+      \draw (0,1) node[anchor=east] {\tiny$C$};
+      \fill (1.3,1) circle (2pt);
+      \draw (1.3,1) node[anchor=north] {\tiny$D_2$};
+      \draw (1.37,-.5) node[anchor=north] {\footnotesize (5) $0<ca_1\leq a_2$};
+    \end{scope}
+    %(6)
+    \begin{scope}[shift={(0,-5.5)}]
+      \usetikzlibrary{patterns}
+      \fill[black!10]  (0,3)--(1.5,2.3)--(2,0)--(0,0)--(0,3);
+      \draw[thick] (0,3)--(0,0)--(2,0); 
+      \draw[dashed,thick] (0,3)--(1.5,2.3)--(2,0);
+      \draw[-] (-0.5,2.3) -- (3.5,2.3);
+      \draw[-] (1.5,-0.25) -- (1.5,3.5);
+      \fill[white] (1.5,2.3) circle (2pt);
+      \draw (1.5,2.3) circle (2pt);
+      \draw (1.5,2.3) node[anchor=south west] {\tiny$O$};
+      \fill (2,0) circle (2pt);
+      \draw (2,0) node[anchor=west] {\tiny$A$};
+      \fill (0,0) circle (2pt);
+      \draw (0,0) node[anchor=east] {\tiny$B$};
+      \fill (0,3) circle (2pt);
+      \draw (0,3) node[anchor=east] {\tiny$C$};
+      \draw (1.42,-.5) node[anchor=north] {\footnotesize (6) $0<a_1<ba_2$,};
+      \draw (1.46,-1) node[anchor=north] {\footnotesize \hspace{10pt} $0<a_2<ca_1$,};
+      \draw (1.17,-1.5) node[anchor=north] {\footnotesize \hspace{10pt} \tiny{$(a_1,a_2):$ non-imaginary root}};
+    \end{scope}
+    %(6')
+    \begin{scope}[shift={(5.5,-5.5)}]
+      \usetikzlibrary{patterns}
+      \fill[black!10]  (0,3)--(1,0.5)--(2.25,0)--(0,0)--(0,3);
+      \draw[thick] (0,3)--(0,0)--(2.25,0);
+      \draw[dashed,thick] (0,3)--(1,0.5)--(2.25,0);
+      \draw[-] (-0.5,0.5) -- (3.5,0.5);
+      \draw[-] (1,-0.25) -- (1,3.5);
+      \fill[white] (1,0.5) circle (2pt);
+      \draw (1,0.5) circle (2pt);
+      \draw (1,0.5) node[anchor=south west] {\tiny$O$};
+      \fill (2.25,0) circle (2pt);
+      \draw (2.25,0) node[anchor=west] {\tiny$A$};
+      \fill (0,0) circle (2pt);
+      \draw (0,0) node[anchor=east] {\tiny$B$};
+      \fill (0,3) circle (2pt);
+      \draw (0,3) node[anchor=east] {\tiny$C$};
+      \draw (1.47,-.5) node[anchor=north] {\footnotesize (6) $0<a_1<ba_2$,};
+      \draw (1.51,-1) node[anchor=north] {\footnotesize \hspace{10pt} $0<a_2<ca_1$,};
+      \draw (1.27,-1.5) node[anchor=north] {\footnotesize \hspace{10pt} \tiny{$(a_1,a_2):$ imaginary root}};
+    \end{scope}
+  \end{tikzpicture}
+  \caption{Consider the points $O=(0,0)$, $A=(-a_1+ba_2,-a_2)$, $B=(-a_1,-a_2)$, $C=(-a_1,-a_2+ca_1)$, $D_1=(-a_1+ba_{2},ca_{1}-(bc+1)a_{2})$, and $D_2=(ba_{2}-(bc+1)a_{1},-a_2+ca_{1})$.
+Then the support region of $x[a_1,a_2]$ can be visualized as above.}
+  \label{fig:greedy polytopes}
+\end{figure}
 
@@
   \begin{proof}
-    It is enough to consider $\phi_{t_{-2}}^{-1}\cC(\phi_{t_{-2}}\lambda) \cap \cC(\lambda) \cap \phi_{t_2}^{-1}\cC(\phi_{t_2}\lambda)$, we leave the details to the reader.
+    It is enough to consider $\phi_{t_{-2}}^{-1}\cC_{t_{-2}}(\phi_{t_{-2}}\lambda) \cap \cC_{t_0}(\lambda) \cap \phi_{t_2}^{-1}\cC_{t_2}(\phi_{t_2}\lambda)$, we leave the details to the reader.
   \end{proof}
@@
     \begin{enumerate}
-      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
-      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
+      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
+      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
     \end{enumerate}
@@
     We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
-    We first show that $\cC(\lambda) \cap \phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)\supsetneq \cC(\lambda) \cap \phi_{t_j}^{-1}\cC(\phi_{t_j}\lambda)$ for $0\le i<j$.
+    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
   \end{proof}
@@
     \begin{enumerate}
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
-      \item if $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cC(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
-      \item if $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and ???.
+      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
+      \item if $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
+      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
+      \item if $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
+      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and ???.
     \end{enumerate}

### 2022-03-28 dominance_regions.tex
Some figures

@@
 \usepackage{tikz}
+\usetikzlibrary{math}
 \usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
@@
   Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$.
+
+\begin{figure}[h!]
+  \centering
+    \newcommand{\boundingrays}{
+      \tikzmath{\b = 2; \c =2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
+      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
+      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
+      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
+      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
+      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / (\b * \c -1));
+      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \bcms / (2 * \b)); 
+      \draw [color=lightgray, thick] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
+    }
+  \begin{tikzpicture}[scale=.3]
+    \begin{scope}[shift={(0.0)}]
+      \boundingrays;
+      \tikzmath{ \l = 1; }
+      \fill (\l,\l) circle (4pt);
+    \end{scope}
+    \begin{scope}[shift={(13,0)}]
+      \boundingrays;
+      \tikzmath{ \l = 1; }
+      \fill (\l *\b + \l, - \l)  circle (4pt);
+      \draw [very thick] (\l * \b + \l, -\l) -- (\l,-\l);
+    \end{scope}
+    \begin{scope}[shift={(26,0)}]
+      \boundingrays;
+      \tikzmath{ \l = 1; }
+      \fill (-\l, \l)  circle (4pt);
+      \draw [very thick] (-\l, \l) -- (-\l,\l + \l*\c);
+    \end{scope}
+    \begin{scope}[shift={(39, 0)}]
+      \boundingrays;
+      \tikzmath{ \l = 1; }
+      \fill (-\l, -\l)  circle (4pt);
+      \draw [very thick] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
+    \end{scope}
+    \begin{scope}[shift={(0,-13)}]
+      \boundingrays;
+      \tikzmath{ \l = 1; }
+      \fill (\b * \l - \l / 2 / \c , -\l)  circle (4pt);
+      \draw [very thick] (\b * \l  - \l / 2 / \c , -\l) -- (- \l / 2 / \c , -\l) -- (- \l / 2 / \c , -\l/2) -- ( , -\l/2) --  cycle);
+    \end{scope}
+  \end{tikzpicture}
+\end{figure}
 \end{theorem}

### 2022-04-03 dominance_regions.tex
Committing to pull

--- 2022-03-28 dominance_regions.tex
@@
           \item If $\lambda_1,\lambda_2 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(\lambda_1,-c\lambda_1+\lambda_2)$.
-          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc-1)\lambda_1+(b^2c-2b)\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
+          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc-1)\lambda_1+b^2c\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
           \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $0 < -c\lambda_1-(bc-1)\lambda_2$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(0,0)$.

### 2022-04-03 dominance_regions.tex
Finished the pictures

@@
           \item If $0\le\lambda_1,\lambda_2$, then $\cS_\lambda$ is just the point $\lambda$.
+          \item If $\lambda_2 < 0$ and $0\le\lambda_1+b\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1+b\lambda_2,\lambda_2)$.
           \item If $\lambda_1 < 0$ and $0\le\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1,-c\lambda_1+\lambda_2)$.
-          \item If $\lambda_2 < 0$ and $0\le\lambda_1+b\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1+b\lambda_2,\lambda_2)$.
           \item If $\lambda_1,\lambda_2 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(\lambda_1,-c\lambda_1+\lambda_2)$.
-          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc-1)\lambda_1+b^2c\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
+          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc+1)\lambda_1-b^2c\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
           \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $0 < -c\lambda_1-(bc-1)\lambda_2$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(0,0)$.
@@
   \end{theorem}
-  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
-  For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
-  \begin{enumerate}
-    \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
-    \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
-    \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
-    \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
-    \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
-    \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
-    $$\aligned
-    R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
-    &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
-    &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
-    \endaligned
-    $$
-  \end{enumerate}
-  Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$.
 
@@
     \newcommand{\boundingrays}{
-      \tikzmath{\b = 2; \c =2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
+      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
       \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
@@
       \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
-      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / (\b * \c -1));
-      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \bcms / (2 * \b)); 
+      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
+      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
       \draw [color=lightgray, thick] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
@@
   \begin{tikzpicture}[scale=.3]
-    \begin{scope}[shift={(0.0)}]
+    \begin{scope}[shift={(0,0)}]
       \boundingrays;
       \tikzmath{ \l = 1; }
-      \fill (\l,\l) circle (4pt);
+      \fill (\l,\l) circle (6pt);
     \end{scope}
@@
       \tikzmath{ \l = 1; }
-      \fill (\l *\b + \l, - \l)  circle (4pt);
+      \fill (\l *\b + \l, - \l)  circle (6pt);
       \draw [very thick] (\l * \b + \l, -\l) -- (\l,-\l);
@@
       \tikzmath{ \l = 1; }
-      \fill (-\l, \l)  circle (4pt);
+      \fill (-\l, \l)  circle (6pt);
       \draw [very thick] (-\l, \l) -- (-\l,\l + \l*\c);
@@
       \tikzmath{ \l = 1; }
-      \fill (-\l, -\l)  circle (4pt);
+      \fill (-\l, -\l)  circle (6pt);
       \draw [very thick] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
@@
       \boundingrays;
-      \tikzmath{ \l = 1; }
-      \fill (\b * \l - \l / 2 / \c , -\l)  circle (4pt);
-      \draw [very thick] (\b * \l  - \l / 2 / \c , -\l) -- (- \l / 2 / \c , -\l) -- (- \l / 2 / \c , -\l/2) -- ( , -\l/2) --  cycle);
+      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c; \y = -\l; }
+      \fill (\b * \l - \l / 2 / \c , -\l)  circle (6pt);
+      \draw [very thick] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
+    \end{scope}
+    \begin{scope}[shift={(13,-13)}]
+      \boundingrays;
+      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c; \y = -\l - 3*\l/10;}
+      \fill (\x,\y)  circle (6pt);
+      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
+    \end{scope}
+    \begin{scope}[shift={(26,-13)}]
+      \boundingrays;
+      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
+      \fill (\l / 2 / \c , -\l)  circle (6pt);
+      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
+    \end{scope}
+    \begin{scope}[shift={(39,-13)}]
+      \boundingrays;
+      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
+      \fill (\x , \y)  circle (6pt);
+      \draw [very thick] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  cycle;
     \end{scope}
@@
 \end{figure}
-\end{theorem}
 \begin{figure}[h!]
@@
 
+  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
+  For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
+  \begin{enumerate}
+    \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
+    \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
+    \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
+    \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
+    \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
+    \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
+    $$\aligned
+    R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
+    &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
+    &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
+    \endaligned
+    $$
+  \end{enumerate}
+  Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
+\end{theorem}
   \subsection{Deformation Support}

### 2022-04-04 dominance_regions.tex
Some reorganization -- not finished

@@
   \begin{theorem}
+    \label{th:dominance inequalities}
     The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
@@
   \begin{theorem}
+    \label{th:dominance vertices}
     There are six classes of dominance polytopes.
@@
   \begin{theorem}
+    \label{th:maximum support}
     For a $\bfg$-vector $\lambda=(\lambda_1,\lambda_2)\in\ZZ^2$ the support for a pointed basis vector $x_\lambda$ is contained in the (possibly degenerate) lattice quadrilateral $\cS_\lambda$ given as follows:
@@
 \end{figure}
+
+  \section{Lattice Mutations and Linear Inequalities}
+  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e.
+there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
+  Write $\Col(B)$ for the span of the columns of $B$ inside $\RR^n$ and $\Col^+(B)$ for their non-negative span.
+  Define $\Col_\ZZ(B)$ and $\Col^+_\ZZ(B)$ analogously over the integers.
+
+  The matrix $B$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_m,i_{m+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le m$.
+  This condition is naturally interpreted in terms of an associated quiver $Q_B$ with $n$ vertices and an arrow $i\to j$ whenever $b_{ji}>0$ (if we need to use representation theory at any point we'll have to change this to be $\gcd(b_{ij},b_{ji})$ arrows $i\to j$).
+  Indeed, this is precisely the condition that $Q_B$ has no oriented cycles.
+  In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_{\ell'} k_\ell}\ge 0$.
+  The sequence $(k_1,\ldots,k_n)$ (resp.
+$(k_n,\ldots,k_1)$) is then said to be \emph{source-adapted} (resp.
+\emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
+  %\sayDR{We need to pin down this convention.}
+
+  For $b\in\ZZ$, write $[b]_+=max(b,0)$.
+  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
+  \begin{equation}
+    \label{eq:left mutation matrix}
+    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise;} \end{cases}
+  \end{equation}
+  and a matrix $F_{k,\varepsilon}=(f_{ij})$ with
+  \begin{equation}
+    \label{eq:right mutation matrix}
+    f_{ij}=\begin{cases} 1 & \text{if $k\ne i=j$;}\\ -1 & \text{if $k=i=j$;}\\ [-\varepsilon b_{kj}]_+ & \text{if $k=i\ne j$;}\\ 0 & \text{otherwise.} \end{cases}
+  \end{equation}
+  Observe that $E^2_{k,\varepsilon}=\Id$ and $F^2_{k,\varepsilon}=\Id$ for any $k$ and any choice of $\varepsilon$.
+  \begin{lemma}
+    For $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, we have $E_{k,-\varepsilon}E_{k,\varepsilon}=I_n+\varepsilon B^{\bullet k}$ and $E_{k,\varepsilon}-E_{k,-\varepsilon}=\varepsilon B^{\bullet k}$.
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equality $\varepsilon b_{ij}=[\varepsilon b_{ij}]_+-[-\varepsilon b_{ij}]_+$.
+  \end{proof}
+
+  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_k B=(b'_{ij})$ given by
+  \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
+  One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
+  \begin{remark}
+    Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
+  \end{remark}
+
+  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
+  \begin{itemize}
+    \item $B^{t_0}=B$;
+    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $B^{t'}=\mu_k B^t$.
+  \end{itemize}
+
+  (DR: I changed to $\RR$ because it didn't seem like we really cared about integer points at the moment, when we try to link up with minors this will need to be added.)
+  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
+  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
+  where the entries of $E^t_{k,\varepsilon}$ are given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
+  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
+  \begin{lemma}
+    Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
+    If $\mu\in\lambda+\Col(B^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+  \end{lemma}
+  \begin{proof}
+    Suppose $\mu=\lambda+B^t\alpha$ for some $\alpha\in\RR^n$.
+    Let $\varepsilon$ (resp. $\varepsilon'$) be such that $\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu$ (resp. $\phi^t_k(\lambda)=E^t_{k,\varepsilon'}\lambda$).
+    Then 
+    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+B^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + B^{t'} F^t_{k,\varepsilon}\alpha.\]
+    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + B^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+    Otherwise, 
+    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(B^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(B^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon B^{t'} \lambda_k \mathbf{e}_k\]
+    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+  \end{proof}
+
+  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
+  \begin{itemize}
+    \item $\phi_{t_0}=\Id$;
+    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
+  \end{itemize}
+
+  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
+  \begin{definition}
+    For $\lambda\in\RR^n$, define the \emph{dominance region} 
+    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
+    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
+  \end{definition}
+  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
+  \begin{lemma}
+    The sets $\cP(\lambda)$ are polytopes.
+  \end{lemma}
+
+  \begin{lemma}
+    \label{le:transformed inequalities}
+    Let $A$ be an invertible $n\times n$ matrix.
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equalities
+    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
+  \end{proof}
+
+  \section{Rank Two}
+  Fix integers $b,c>0$ and assume $bc\ge 4$.
+  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
+  Here we may take the 2-regular tree $\TT_2$ to have vertices labeled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labeled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labeled $2$.
+  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
+
+  Observe that $\phi_{t_1}:=\phi_1^{t_0}$ is the piecewise-linear map given by
+  \begin{equation}
+    \label{eq:forward mutation 1}
+    \phi_{t_1}(\lambda)=\begin{cases} (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1\ge0$;}\\ (-\lambda_1,\lambda_2) & \text{if $\lambda_1<0$;} \end{cases}
+  \end{equation}
+  and $\phi_{t_2}:=\phi_2^{t_1}\phi_1^{t_0}$ is the piecewise-linear map given by
+  \begin{equation}
+    \label{eq:forward two step mutation}
+    \phi_{t_2}(\lambda)=\begin{cases} \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\ (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\ (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}\end{cases}
+  \end{equation}
+  while $\phi_{t_2}^{-1}=\phi_{t_{-2}}$ is the piecewise-linear map given by
+  \begin{equation}
+    \label{eq:backward two step mutation}
+    \phi_{t_2}^{-1}(\lambda)=\begin{cases} \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\ (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\ (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$;}\end{cases}
+  \end{equation}
+
+  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
+  \begin{lemma}
+    Any nonzero eigenvector of $\phi_{t_2}$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  \end{lemma}
+  \begin{proof}
+    First observe that the equation $\phi_{t_2}^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
+    In this region, $\phi_{t_2}$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
+    We thus require that 
+    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
+    or, equivalently, that
+    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
+    As these represent the same relation, the result immediately follows by inspection.
+  \end{proof}
+
+  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
+  \begin{lemma}
+    The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
+  \end{proof}
+  \begin{lemma}
+    \label{le:imaginary stability}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
+  \end{lemma}
+  \begin{proof}
+    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$, respectively.
+    The claim is immediate for $\phi_{t_2}$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_{t_2}$ is linear in $\cI$.
+    Now, since $b>0$, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_{t_1}$ in this region.
+  \end{proof}
+
+  It will be useful to have explicit expressions for $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
+  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
+  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
+
+  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
+  This leads to the following more general recursive structure.
+  \begin{lemma}
+    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
+    \begin{equation}
+      \label{eq:long Chebyshev recursion}
+      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
+    \end{equation}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
+    Using the claim for $j>0$ and then the defining recursion twice, we get
+    \begin{align*}
+      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
+    \end{align*}
+    which is the claimed recursion for $\ell+1$.
+    These calculations can be reversed to show the result for $\ell<0$.
+  \end{proof}
+
+  The following gives the desired expressions for $\phi_{t_i}(\lambda)$ when $\lambda\in\cI$.
+  \begin{lemma}
+    \label{le:imaginary transformations}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have
+    \begin{align*}
+      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
+      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
+    \end{align*}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $j$, the case $j=0$ being clear from the definitions.
+    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$.
+    For $\lambda\in\cI$, the action of $\phi_{t_2}$ from \eqref{eq:forward two step mutation} can be rewritten as
+    \[\phi_{t_2}(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
+    and so
+    \begin{align*}
+      \phi_{t_{2j+2}(\lambda)}&=\phi_{t_2}\phi_{t_{2j}}(\lambda)\\
+      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
+      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
+      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
+    \end{align*}
+    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
+
+    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
+  \end{proof}
+
+  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
+  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
+  By the equalities 
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
+  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+  \begin{remark}
+    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
+    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
+  \end{remark}
+
+  \begin{lemma}
+    We have
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+  \end{lemma}
+  \begin{proof}
+    For any $i\ge 1$, we have
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
+    It follows that
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    which is equivalent to the desired expression.
+    Similarly, 
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
+    so that
+    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    which is again equivalent to the desired expression.
+  \end{proof}
+
+  \begin{lemma}
+    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
+  \end{lemma}
+  \begin{proof}
+    It is enough to consider $\phi_{t_{-2}}^{-1}\cC_{t_{-2}}(\phi_{t_{-2}}\lambda) \cap \cC_{t_0}(\lambda) \cap \phi_{t_2}^{-1}\cC_{t_2}(\phi_{t_2}\lambda)$, we leave the details to the reader.
+  \end{proof}
+
+  \begin{lemma}
+    \label{le:one direction}
+    For $\lambda\in\cI\cap\ZZ^2$, 
+    \begin{enumerate}
+      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
+      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
+    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
+  \end{proof}
+
+  \begin{theorem}
+    There are six classes of dominance polytopes.
+    \begin{enumerate}
+      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
+    \end{enumerate}
+  \end{theorem}
+  \begin{proof}
+    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
+    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
+    or 
+    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
+    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
+    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
+  \end{proof}
+
+  \begin{remark}
+    Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
+    This unexpected coincidence is one of our reasons for deciding to write down these results.
+  \end{remark}
+
+%  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following inequalities:
+%  \begin{align}
+%    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
+%  \end{align}
+%  Are any of these better forms?
+%  \begin{align}
+%    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%  \end{align}
+%  Another proposal (I also changed the order of the equations)
+%  \begin{align}
+%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
+%    \\
+%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
+%    \\
+%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
+%    \\
+%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{align}
+%  Maybe this one:
+%  \begin{align}
+%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
+%    \\
+%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
+%    \\
+%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
+%    \\
+%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{align}
+%
+%  Yet another version:
+% 
+% {
+%    \everymath={\displaystyle}
+%  \[
+%  \begin{array}{rcccl}
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
+%    \\
+%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
+%    \\
+%    - b \lambda_2 & \geq & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) 
+%    \\
+%    0 & \geq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{array}
+%\]
+%}
+%
+%Or: (Maybe at this point we can remove $c/c$ and $b/b$)
+%
+% {
+%    \everymath={\displaystyle}
+%  \[
+%  \begin{array}{rcccl}
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
+%    \\
+%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2  & \leq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & 0
+%    \\
+%    & & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)  & \leq & - b \lambda_2
+%  \end{array}
+%\]
+%}
+%
+%
+%Or Or: (Maybe at this point we can remove $c/c$ and $b/b$)
+%
+%
+% The following, and possibly all the one before, has a typo
+% {
+%    \everymath={\displaystyle}
+%    \def\arraystretch{2.8}
+%  \[
+%  \begin{array}{rcccl}
+%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
+%    \\
+%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
+%    \\
+%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
+%  \end{array}
+%\]
+%}
+% {
+%    \everymath={\displaystyle}
+%    \def\arraystretch{2.8}
+%  \[
+%  \begin{array}{rcccl}
+%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
+%    \\
+%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
+%    \\
+%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
+%  \end{array}
+%\]
+%}
+  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
+ {
+    \everymath={\displaystyle}
+    \def\arraystretch{2.8}
+  \[
+  \begin{array}{rcccl}
+    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
+    \\
+    \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
+    \\
+    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
+    \\
+    \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
+  \end{array}
+\]
+}
+
+  \section{The Total Domination Polyhedron}
+
+  Define the \emph{total domination polyhedron} $\cD:=\{(\lambda,\mu):\mu\in\cP(\lambda)\}$, i.e. this is the set of all pairs where $\lambda$ dominates $\mu$.
+  Write $\pi_1:\cD\to\RR^n$ for the projection to $\lambda$ and $\pi_2:\cD\to\RR^n$ for the projection to $\mu$.
+  \begin{itemize}
+    \item Is it a polyhedron?
+    \item The lemma below might suggest so.  
+      Indeed, if it is, by the Decomposition Theorem, we can write $\cD$ as the Minkowski sum of a polyhedral cone (almost certainly $\cI$) and a convex polytope (what is it?).
+      I am ignoring that it should really be the union of this polyhedron with a plane if the previous sentence holds any water.
+    \item Actually, we might need to take the union of several polyhedra to account for the variations in the fibers $\pi_1^{-1}(\lambda)$.
+  \end{itemize}
+
+  Is the following result true beyond rank 2?
+  \begin{lemma}
+    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
+  \end{lemma}
+  \begin{proof}
+    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_1,\lambda_2)$ where
+    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
+    (This comes from setting $\mu$ to be the vertex opposite $\lambda$ inside the dominance region $\cP(\lambda)$ and then solving for $\lambda$.)
+  \end{proof}
+  \begin{remark}
+    We want to understand what the curve is that results when we have $\mu$ lie along the unit circle, this should be possible by plugging $(\cos(\theta),\sin(\theta))$ into this formula for $\lambda$ and seeing what ellipse we get.
+  \end{remark}
+
+  \begin{thebibliography}{XXX}
+
+    \bibitem{lee-li-zelevinsky}
+      K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014), pp.~57--82.
+
+    \bibitem{rupel}
+      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
+Algebraic Combinatorics, \textbf{2} (2019) no.
+6, pp.~1239--1273.
+\href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
+  \end{thebibliography}
+
+  \section{Chebyshev}
+  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
+  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
+
+  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
+  This leads to the following more general recursive structure.
+  \begin{lemma}
+    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
+    \begin{equation}
+      \label{eq:long Chebyshev recursion}
+      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
+    \end{equation}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
+    Using the claim for $j>0$ and then the defining recursion twice, we get
+    \begin{align*}
+      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
+    \end{align*}
+    which is the claimed recursion for $\ell+1$.
+    These calculations can be reversed to show the result for $\ell<0$.
+  \end{proof}
+
+  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
+  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
+  By the equalities 
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
+  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+  \begin{remark}
+    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
+    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
+  \end{remark}
+
+  \begin{lemma}
+    We have
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+  \end{lemma}
+  \begin{proof}
+    For any $i\ge 1$, we have
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
+    It follows that
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    which is equivalent to the desired expression.
+    Similarly, 
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
+    so that
+    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    which is again equivalent to the desired expression.
+  \end{proof}
+
+  \section{Proof of Theorem~\ref{th:dominance inequalities}}
+
+  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP(\lambda)$ for $\lambda\in\cI$.
+  \begin{lemma}
+    \label{le:transformed inequalities}
+    Let $A=(a_{ij})$ be an invertible $2\times 2$ matrix.
+    Under the action of $A$, the region inside $\RR^2$ defined by the inequality $rx+sy\le t$ is transformed to the region defined by the inequality \[\frac{ra_{22}-sa_{21}}{a_{11}a_{22}-a_{12}a_{21}}x + \frac{-ra_{12}+sa_{11}}{a_{11}a_{22}-a_{12}a_{21}}y\le t.\]
+  \end{lemma}
+  \begin{proof}
+    Assume $r,s,t\ne0$, the cases when one of these vanishes follows by the continuity of the transformation.
+    Observe that the points $\big(\frac{t}{r},0\big)$ and $\big(0,\frac{t}{s}\big)$ lie on the boundary line of the region defined by the inequality $rx+sy\le t$.
+    These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
+    By the linearity of the transformation of $\RR^2$ given by the matrix $A$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
+  \end{proof}
+
+  \begin{lemma}
+    For $i\ge1$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+    \begin{align}
+      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
+      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+    \end{align}
+
+    given as in the figure below:
+    \[
+      \begin{tikzpicture}
+        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
+        \draw[-] (-8,0) -- (5,0);
+        \draw[-] (0,-5) -- (0,5);
+        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
+        \draw[-] (0,0) -- (5,-2.113);
+        \draw[-] (0,0) -- (3.17,-5);
+        \node at (1,-0.9) {$\cI$};
+        \draw[fill=black] (3.5,-3) circle (2pt);
+        \node[below right] at (3.5,-3) {$\lambda$};
+        \draw[->,thick] (3.5,-3) -- (47/10,-5);
+        \draw[-,thick] (3.5,-3) -- (0,26/10);
+        \draw[-,thick] (0,26/10) -- (-26/4,0);
+        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
+        \node at (4.5,-4) {\eqref{ineq:1}};
+        \node at (2.5,-0.5) {\eqref{ineq:2}};
+        \node at (-3,1.75) {\eqref{ineq:3}};
+        \node at (-5.5,-3) {\eqref{ineq:4}};
+      \end{tikzpicture}
+    \]
+  \end{lemma}
+  \begin{proof}
+    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
+
+    For $i=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
+    We inductively compute the region $\phi_{t_{2j}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{t_{2j}}^{-1}=\phi_{t_2}^{-j}$.
+
+    \subsubsection*{Claim:} For $k>0$, $\phi_{t_{2k}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ is the region determined by the inequalities 
+    \begin{align*}
+      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
+      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
+    \end{align*}
+
+    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$ which corresponds to (a) with $k=1$.
+    Similarly, the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\dagger$) intersects three domains of linearity in which $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $k=1$.
+    This establishes the base of an induction on $k$.
+
+    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
+    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
+    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
+    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
+    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
+    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
+    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (b) for $k+1$.
+    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
+    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
+    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
+    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
+    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
+    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
+    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
+    This completes the induction on $k$, proving the Claim and the result for $i$ even.
+
+    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
+    Using that $\phi_{t_{2j+1}}^{-1}=\phi_{t_2}^{-j}\phi_{t_1}^{-1}$, we compute the image inductively as above.
+    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_{t_1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_{t_1}^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
+    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_{t_1}^{-1}$ and thus produces the inequalities
+    \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]
+
+    \subsubsection*{Claim:} For $k\ge 0$, $\phi_{t_{2k+1}}^{-1}\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ is the region determined by the inequalities 
+    \begin{align*}
+      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
+      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
+      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
+    \end{align*}
+    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_{t_2}^{-1}$ and this completes the proof.
+  \end{proof}
+
+  \section{Proof of Theorem~\ref{th:dominance vertices}}
+
+  \section{Proof of Theorem~\ref{th:maximum support}}
+
+  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
+    For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
+    \begin{enumerate}
+      \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
+      \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
+      \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
+      \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
+      \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
+      \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
+      $$\aligned
+      R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
+      &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
+      &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
+      \endaligned
+      $$
+    \end{enumerate}
+    Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
+  \end{theorem}
   \begin{figure}[h!]
@@
 
-  \section{Lattice Mutations and Linear Inequalities}
-  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e.
-there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
-  Write $\Col(B)$ for the span of the columns of $B$ inside $\RR^n$ and $\Col^+(B)$ for their non-negative span.
-  Define $\Col_\ZZ(B)$ and $\Col^+_\ZZ(B)$ analogously over the integers.
-
-  The matrix $B$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_m,i_{m+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le m$.
-  This condition is naturally interpreted in terms of an associated quiver $Q_B$ with $n$ vertices and an arrow $i\to j$ whenever $b_{ji}>0$ (if we need to use representation theory at any point we'll have to change this to be $\gcd(b_{ij},b_{ji})$ arrows $i\to j$).
-  Indeed, this is precisely the condition that $Q_B$ has no oriented cycles.
-  In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_{\ell'} k_\ell}\ge 0$.
-  The sequence $(k_1,\ldots,k_n)$ (resp.
-$(k_n,\ldots,k_1)$) is then said to be \emph{source-adapted} (resp.
-\emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
-  %\sayDR{We need to pin down this convention.}
-
-  For $b\in\ZZ$, write $[b]_+=max(b,0)$.
-  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
-  \begin{equation}
-    \label{eq:left mutation matrix}
-    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise;} \end{cases}
-  \end{equation}
-  and a matrix $F_{k,\varepsilon}=(f_{ij})$ with
-  \begin{equation}
-    \label{eq:right mutation matrix}
-    f_{ij}=\begin{cases} 1 & \text{if $k\ne i=j$;}\\ -1 & \text{if $k=i=j$;}\\ [-\varepsilon b_{kj}]_+ & \text{if $k=i\ne j$;}\\ 0 & \text{otherwise.} \end{cases}
-  \end{equation}
-  Observe that $E^2_{k,\varepsilon}=\Id$ and $F^2_{k,\varepsilon}=\Id$ for any $k$ and any choice of $\varepsilon$.
-  \begin{lemma}
-    For $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, we have $E_{k,-\varepsilon}E_{k,\varepsilon}=I_n+\varepsilon B^{\bullet k}$ and $E_{k,\varepsilon}-E_{k,-\varepsilon}=\varepsilon B^{\bullet k}$.
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the equality $\varepsilon b_{ij}=[\varepsilon b_{ij}]_+-[-\varepsilon b_{ij}]_+$.
-  \end{proof}
-
-  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_k B=(b'_{ij})$ given by
-  \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
-  One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
-  \begin{remark}
-    Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
-  \end{remark}
-
-  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
-  \begin{itemize}
-    \item $B^{t_0}=B$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $B^{t'}=\mu_k B^t$.
-  \end{itemize}
-
-  (DR: I changed to $\RR$ because it didn't seem like we really cared about integer points at the moment, when we try to link up with minors this will need to be added.)
-  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
-  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
-  where the entries of $E^t_{k,\varepsilon}$ are given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
-  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-  \begin{lemma}
-    Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-    If $\mu\in\lambda+\Col(B^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-  \end{lemma}
-  \begin{proof}
-    Suppose $\mu=\lambda+B^t\alpha$ for some $\alpha\in\RR^n$.
-    Let $\varepsilon$ (resp. $\varepsilon'$) be such that $\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu$ (resp. $\phi^t_k(\lambda)=E^t_{k,\varepsilon'}\lambda$).
-    Then 
-    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+B^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + B^{t'} F^t_{k,\varepsilon}\alpha.\]
-    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + B^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-    Otherwise, 
-    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(B^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(B^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon B^{t'} \lambda_k \mathbf{e}_k\]
-    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-  \end{proof}
-
-  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
-  \begin{itemize}
-    \item $\phi_{t_0}=\Id$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
-  \end{itemize}
-
-  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
-  \begin{definition}
-    For $\lambda\in\RR^n$, define the \emph{dominance region} 
-    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
-    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
-  \end{definition}
-  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
-  \begin{lemma}
-    The sets $\cP(\lambda)$ are polytopes.
-  \end{lemma}
-
-  \begin{lemma}
-    \label{le:transformed inequalities}
-    Let $A$ be an invertible $n\times n$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the equalities
-    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
-  \end{proof}
-
-  \section{Rank Two}
-  Fix integers $b,c>0$ and assume $bc\ge 4$.
-  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
-  Here we may take the 2-regular tree $\TT_2$ to have vertices labeled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labeled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labeled $2$.
-  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
-
-  Observe that $\phi_{t_1}:=\phi_1^{t_0}$ is the piecewise-linear map given by
-  \begin{equation}
-    \label{eq:forward mutation 1}
-    \phi_{t_1}(\lambda)=\begin{cases} (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1\ge0$;}\\ (-\lambda_1,\lambda_2) & \text{if $\lambda_1<0$;} \end{cases}
-  \end{equation}
-  and $\phi_{t_2}:=\phi_2^{t_1}\phi_1^{t_0}$ is the piecewise-linear map given by
-  \begin{equation}
-    \label{eq:forward two step mutation}
-    \phi_{t_2}(\lambda)=\begin{cases} \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\ (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\ (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}\end{cases}
-  \end{equation}
-  while $\phi_{t_2}^{-1}=\phi_{t_{-2}}$ is the piecewise-linear map given by
-  \begin{equation}
-    \label{eq:backward two step mutation}
-    \phi_{t_2}^{-1}(\lambda)=\begin{cases} \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\ (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\ (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$;}\end{cases}
-  \end{equation}
-
-  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
-  \begin{lemma}
-    Any nonzero eigenvector of $\phi_{t_2}$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  \end{lemma}
-  \begin{proof}
-    First observe that the equation $\phi_{t_2}^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
-    In this region, $\phi_{t_2}$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
-    We thus require that 
-    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
-    or, equivalently, that
-    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
-    As these represent the same relation, the result immediately follows by inspection.
-  \end{proof}
-
-  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
-  \begin{lemma}
-    The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
-  \end{proof}
-  \begin{lemma}
-    \label{le:imaginary stability}
-    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
-  \end{lemma}
-  \begin{proof}
-    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$, respectively.
-    The claim is immediate for $\phi_{t_2}$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_{t_2}$ is linear in $\cI$.
-    Now, since $b>0$, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_{t_1}$ in this region.
-  \end{proof}
-
-  It will be useful to have explicit expressions for $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
-  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
-  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
-  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
-
-  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
-  This leads to the following more general recursive structure.
-  \begin{lemma}
-    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
-    \begin{equation}
-      \label{eq:long Chebyshev recursion}
-      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
-    \end{equation}
-  \end{lemma}
-  \begin{proof}
-    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
-    Using the claim for $j>0$ and then the defining recursion twice, we get
-    \begin{align*}
-      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
-    \end{align*}
-    which is the claimed recursion for $\ell+1$.
-    These calculations can be reversed to show the result for $\ell<0$.
-  \end{proof}
-
-  The following gives the desired expressions for $\phi_{t_i}(\lambda)$ when $\lambda\in\cI$.
-  \begin{lemma}
-    \label{le:imaginary transformations}
-    For $j\in\ZZ$ and $\lambda\in\cI$, we have
-    \begin{align*}
-      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
-      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
-    \end{align*}
-  \end{lemma}
-  \begin{proof}
-    We work by induction on $j$, the case $j=0$ being clear from the definitions.
-    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$.
-    For $\lambda\in\cI$, the action of $\phi_{t_2}$ from \eqref{eq:forward two step mutation} can be rewritten as
-    \[\phi_{t_2}(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
-    and so
-    \begin{align*}
-      \phi_{t_{2j+2}(\lambda)}&=\phi_{t_2}\phi_{t_{2j}}(\lambda)\\
-      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
-      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
-      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
-    \end{align*}
-    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
-
-    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
-  \end{proof}
-
-  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP(\lambda)$ for $\lambda\in\cI$.
-  \begin{lemma}
-    \label{le:transformed inequalities}
-    Let $A=(a_{ij})$ be an invertible $2\times 2$ matrix.
-    Under the action of $A$, the region inside $\RR^2$ defined by the inequality $rx+sy\le t$ is transformed to the region defined by the inequality \[\frac{ra_{22}-sa_{21}}{a_{11}a_{22}-a_{12}a_{21}}x + \frac{-ra_{12}+sa_{11}}{a_{11}a_{22}-a_{12}a_{21}}y\le t.\]
-  \end{lemma}
-  \begin{proof}
-    Assume $r,s,t\ne0$, the cases when one of these vanishes follows by the continuity of the transformation.
-    Observe that the points $\big(\frac{t}{r},0\big)$ and $\big(0,\frac{t}{s}\big)$ lie on the boundary line of the region defined by the inequality $rx+sy\le t$.
-    These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
-    By the linearity of the transformation of $\RR^2$ given by the matrix $A$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
-  \end{proof}
-
-  \begin{lemma}
-    For $i\ge1$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
-    \begin{align}
-      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
-      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
-    \end{align}
-
-    given as in the figure below:
-    \[
-      \begin{tikzpicture}
-        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
-        \draw[-] (-8,0) -- (5,0);
-        \draw[-] (0,-5) -- (0,5);
-        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
-        \draw[-] (0,0) -- (5,-2.113);
-        \draw[-] (0,0) -- (3.17,-5);
-        \node at (1,-0.9) {$\cI$};
-        \draw[fill=black] (3.5,-3) circle (2pt);
-        \node[below right] at (3.5,-3) {$\lambda$};
-        \draw[->,thick] (3.5,-3) -- (47/10,-5);
-        \draw[-,thick] (3.5,-3) -- (0,26/10);
-        \draw[-,thick] (0,26/10) -- (-26/4,0);
-        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
-        \node at (4.5,-4) {\eqref{ineq:1}};
-        \node at (2.5,-0.5) {\eqref{ineq:2}};
-        \node at (-3,1.75) {\eqref{ineq:3}};
-        \node at (-5.5,-3) {\eqref{ineq:4}};
-      \end{tikzpicture}
-    \]
-  \end{lemma}
-  \begin{proof}
-    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
-
-    For $i=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
-    We inductively compute the region $\phi_{t_{2j}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{t_{2j}}^{-1}=\phi_{t_2}^{-j}$.
-
-    \subsubsection*{Claim:} For $k>0$, $\phi_{t_{2k}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ is the region determined by the inequalities 
-    \begin{align*}
-      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
-      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
-    \end{align*}
-
-    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$ which corresponds to (a) with $k=1$.
-    Similarly, the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\dagger$) intersects three domains of linearity in which $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $k=1$.
-    This establishes the base of an induction on $k$.
-
-    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
-    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
-    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
-    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (b) for $k+1$.
-    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
-    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
-    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
-    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
-    This completes the induction on $k$, proving the Claim and the result for $i$ even.
-
-    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
-    Using that $\phi_{t_{2j+1}}^{-1}=\phi_{t_2}^{-j}\phi_{t_1}^{-1}$, we compute the image inductively as above.
-    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_{t_1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
-    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_{t_1}^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
-    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_{t_1}^{-1}$ and thus produces the inequalities
-    \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]
-
-    \subsubsection*{Claim:} For $k\ge 0$, $\phi_{t_{2k+1}}^{-1}\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ is the region determined by the inequalities 
-    \begin{align*}
-      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
-      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
-      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
-    \end{align*}
-    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_{t_2}^{-1}$ and this completes the proof.
-  \end{proof}
-
-  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
-  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
-  By the equalities 
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
-  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
-  \begin{remark}
-    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
-    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
-  \end{remark}
-
-  \begin{lemma}
-    We have
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
-  \end{lemma}
-  \begin{proof}
-    For any $i\ge 1$, we have
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
-    It follows that
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
-    which is equivalent to the desired expression.
-    Similarly, 
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
-    so that
-    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
-    which is again equivalent to the desired expression.
-  \end{proof}
-
-  \begin{lemma}
-    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
-  \end{lemma}
-  \begin{proof}
-    It is enough to consider $\phi_{t_{-2}}^{-1}\cC_{t_{-2}}(\phi_{t_{-2}}\lambda) \cap \cC_{t_0}(\lambda) \cap \phi_{t_2}^{-1}\cC_{t_2}(\phi_{t_2}\lambda)$, we leave the details to the reader.
-  \end{proof}
-
-  \begin{lemma}
-    \label{le:one direction}
-    For $\lambda\in\cI\cap\ZZ^2$, 
-    \begin{enumerate}
-      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
-      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
-    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
-  \end{proof}
-
-  \begin{theorem}
-    For $\lambda\in\cI\cap\ZZ^2$, there are five classes of dominance polytopes.
-    \begin{enumerate}
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
-      \item if $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
-      \item if $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
-      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and ???.
-    \end{enumerate}
-  \end{theorem}
-  \begin{proof}
-    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
-    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
-    or 
-    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
-    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
-    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
-  \end{proof}
-
-  \begin{remark}
-    Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
-    This unexpected coincidence is one of our reasons for deciding to write down these results.
-  \end{remark}
-
-%  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following inequalities:
-%  \begin{align}
-%    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
-%  \end{align}
-%  Are any of these better forms?
-%  \begin{align}
-%    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%  \end{align}
-%  Another proposal (I also changed the order of the equations)
-%  \begin{align}
-%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
-%    \\
-%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
-%    \\
-%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
-%    \\
-%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
-%  \end{align}
-%  Maybe this one:
-%  \begin{align}
-%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
-%    \\
-%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
-%    \\
-%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
-%    \\
-%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
-%  \end{align}
-%
-%  Yet another version:
-% 
-% {
-%    \everymath={\displaystyle}
-%  \[
-%  \begin{array}{rcccl}
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
-%    \\
-%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
-%    \\
-%    - b \lambda_2 & \geq & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) 
-%    \\
-%    0 & \geq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
-%  \end{array}
-%\]
-%}
-%
-%Or: (Maybe at this point we can remove $c/c$ and $b/b$)
-%
-% {
-%    \everymath={\displaystyle}
-%  \[
-%  \begin{array}{rcccl}
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
-%    \\
-%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2  & \leq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & 0
-%    \\
-%    & & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)  & \leq & - b \lambda_2
-%  \end{array}
-%\]
-%}
-%
-%
-%Or Or: (Maybe at this point we can remove $c/c$ and $b/b$)
-%
-%
-% The following, and possibly all the one before, has a typo
-% {
-%    \everymath={\displaystyle}
-%    \def\arraystretch{2.8}
-%  \[
-%  \begin{array}{rcccl}
-%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
-%    \\
-%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
-%    \\
-%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
-%  \end{array}
-%\]
-%}
-% {
-%    \everymath={\displaystyle}
-%    \def\arraystretch{2.8}
-%  \[
-%  \begin{array}{rcccl}
-%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    -c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
-%    \\
-%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
-%    \\
-%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
-%  \end{array}
-%\]
-%}
-  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
- {
-    \everymath={\displaystyle}
-    \def\arraystretch{2.8}
-  \[
-  \begin{array}{rcccl}
-    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
-    \\
-    \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
-    \\
-    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
-    \\
-    \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
-  \end{array}
-\]
-}
-
-  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
-  For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
-  \begin{enumerate}
-    \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
-    \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
-    \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
-    \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
-    \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
-    \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
-    $$\aligned
-    R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
-    &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
-    &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
-    \endaligned
-    $$
-  \end{enumerate}
-  Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
-\end{theorem}
-  \subsection{Deformation Support}
-  The greedy basis of Lee, Li, and Zelevinsky \cite{lee-li-zelevinsky} can be defined as the positive pointed basis with minimal support.
-  Here we identify the maximum possible support of its deformations.
-
-  It will be convenient later to have explicit expressions for the greedy basis elements so we recall here the combinatorial construction of their Laurent expansions.
-  For a $\bfg$-vector $\lambda\in\ZZ^2\setminus\ZZ_{\ge0}^2$, define the \emph{maximal Dyck path} $D_\lambda\subset\ZZ^2$ to be the lattice path with corner vertices $(0,0)$ and $(a_1,a_2):=\big([-\lambda_1+b\lambda_2]_+,[-\lambda_2]_+\big)$ which is maximal in the following sense:
-  \begin{itemize}
-    \item every lattice point of $D_\lambda$ lies below the line connecting the corner vertices;
-    \item any lattice point above $D_\lambda$ lies above the line connecting the corner vertices.
-  \end{itemize}
-  For $\lambda\in\ZZ_{\ge0}^2$, we take $D_\lambda$ to be the empty path at $(0,0)$.
-
-  We consider $D_\lambda$ to be the set of its edges ordered from $(0,0)$.
-  Write $H_\lambda,V_\lambda\subset D_\lambda$ for the subsets of horizontal and vertical edges, respectively.
-  According to the ordering of $D_\lambda$, we denote $H_\lambda=\{h_1,\ldots,h_{a_1}\}$ and $V_\lambda=\{v_1,\ldots,v_{a_2}\}$.
-  For edges $e,e'\in D_\lambda$ with $e\le e'$, write $ee'\subset D_\lambda$ for the shortest subpath of $D_\lambda$ containing $e$ and $e'$.
-  For edges $e,e'\in D_\lambda$ with $e'<e$, write $ee'\subset D_\lambda$ for the subset $ev_{a_2} \sqcup h_1e'$, which can be seen as the subpath traversing from the edge $e$ to the end of $D_\lambda$ and then continuing from the beginning of $D_\lambda$ to the edge $e'$.
-  For any subset $S\subset D_\lambda$, write $|S|_H:=|S\cap H_\lambda|$ and $|S|_V:=|S\cap V_\lambda|$; in particular, for $e,e'\in D_\lambda$, write $|ee'|_H:=|ee'\cap H_\lambda|$ and $|ee'|_V:=|ee'\cap V_\lambda|$.
-  \begin{definition}
-    A subset $S\subset D_\lambda$ is said to be \emph{compatible} if: for every $h\in S\cap H_\lambda$ and $v\in S\cap V_\lambda$, there exists an edge $e\in hv$ so that one of the following conditions is satisfied:
-    \begin{align*}
-      e\ne v \quad \text{and} \quad |he|_V=c|he\cap S|_H;\\
-      e\ne h \quad \text{and} \quad |ev|_H=b|ev\cap S|_V.
-    \end{align*}
-    Write $\cC_\lambda$ for the set of all compatible subsets $S\subset D_\lambda$.
-  \end{definition}
-
-  The \emph{greedy basis element} $x^{gr}_\lambda$ is then given by the following Laurent polynomial
-  \begin{equation}
-    \label{eq:greedy}
-    x^{gr}_\lambda=x_1^{\lambda_1}x_2^{\lambda_2} \sum_{S\in \cC_\lambda} x_1^{b(|V_\lambda|-|S|_V)} x_2^{c|S|_H}.
-  \end{equation}
-
-  Consider the deformation of the theta basis element with $\bfg$-vector $\lambda$.
-  \begin{theorem}
-    For $\lambda\in\cI\cap\ZZ^2$, the support of any deformation of the corresponding theta basis element is contained in the polytope defined by the following inequalities:
-    \begin{align*}
-       \lambda_1-b\lambda_2 &\le x\\
-       \lambda_2 &\le y\\
-    \end{align*}
-    is the convex hull of the following vertices:
-    \[\lambda, \qquad (\lambda_1-b\lambda_2,\lambda_2), \qquad (\lambda_1-b\lambda_2,\lambda_2-c\lambda_1), \qquad (?,?)\]
-    The $d$-vector is $(\lambda_1-b\lambda_2,\lambda_2)$
-
-    $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$
-
-    Slope:
-    \[\big(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(c\lambda_1+2\lambda_2)-(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)\big) /\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2)\]
-
-    $y=$
-
-    $(\lambda_1,\lambda_2)$ and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$
-
-    Slope: $-\frac{bc+\sqrt{bc(bc-4)}}{2b}$\\
-
-    Corner of dominant support?: 
-    \begin{align*}
-      \left(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2),-\frac{bc+\sqrt{bc(bc-4)}}{2b}\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2)+\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\right)\\
-      \left(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2),-\frac{bc+\sqrt{bc(bc-4)}}{2b}\frac{bc}{\sqrt{bc(bc-4)}}\lambda_1+-\frac{bc+\sqrt{bc(bc-4)}}{2}\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\lambda_2+\lambda_2\right)\\
-    \end{align*}
-
-  \end{theorem}
-
-  \section{The Total Domination Polyhedron}
-
-  Define the \emph{total domination polyhedron} $\cD:=\{(\lambda,\mu):\mu\in\cP(\lambda)\}$, i.e. this is the set of all pairs where $\lambda$ dominates $\mu$.
-  Write $\pi_1:\cD\to\RR^n$ for the projection to $\lambda$ and $\pi_2:\cD\to\RR^n$ for the projection to $\mu$.
-  \begin{itemize}
-    \item Is it a polyhedron?
-    \item The lemma below might suggest so.  
-      Indeed, if it is, by the Decomposition Theorem, we can write $\cD$ as the Minkowski sum of a polyhedral cone (almost certainly $\cI$) and a convex polytope (what is it?).
-      I am ignoring that it should really be the union of this polyhedron with a plane if the previous sentence holds any water.
-    \item Actually, we might need to take the union of several polyhedra to account for the variations in the fibers $\pi_1^{-1}(\lambda)$.
-  \end{itemize}
-
-  Is the following result true beyond rank 2?
-  \begin{lemma}
-    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
-  \end{lemma}
-  \begin{proof}
-    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_1,\lambda_2)$ where
-    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
-    (This comes from setting $\mu$ to be the vertex opposite $\lambda$ inside the dominance region $\cP(\lambda)$ and then solving for $\lambda$.)
-  \end{proof}
-  \begin{remark}
-    We want to understand what the curve is that results when we have $\mu$ lie along the unit circle, this should be possible by plugging $(\cos(\theta),\sin(\theta))$ into this formula for $\lambda$ and seeing what ellipse we get.
-  \end{remark}
-
-  \section{Bases From Compatible Pairs on Dyck Paths}
-  \sayDR{This is a bit of a repetition of the above introduction to Dyck paths, but with slightly different goals it seemed that a modified exposition was more appropriate.}
-  For $a_1,a_2\in\ZZ_{\ge0}$, choose a Dyck path $D$ in the lattice rectangle $[0,a_1]\times[0,a_2]$.
-  When we wish to emphasize the upper right bounding corner we will write $D[a_1,a_2]$.
-  Consider $D$ as the totally ordered set of its edges along the natural labeling from $(0,0)$ to $(a_1,a_2)$.
-  It may be convenient to identify $D$ with the ordered set $[1,a_1+a_2]$.
-  Write $D=D_1\sqcup D_2$, where $D_1=\{h_1,\ldots,h_{a_1}\}$ is the set of horizontal edges and $D_2=\{v_1,\ldots,v_{a_2}\}$ is the set of vertical edges.
-  Define the \emph{height}, $\hgt(h)$ for $h\in D_1$, as one more than the number of $v\in D_2$ with $v<h$.
-  Define the \emph{depth}, $\dpt(v)$ for $v\in D_2$, as the number of $h\in D_1$ with $h<v$.
-  \begin{remark}
-    The seemingly different conventions for computing height and depth provide uniformity later.
-    Indeed, the vertical edges immediately following $h_d$ have depth $d$, while this convention allows the horizontal edges immediately preceding $v_\ell$ to similarly be said to have height $\ell$.
-  \end{remark}
-
-  Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
-  Given a Dyck path $D=D_1\sqcup D_2$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $\bar{D}=\bar{D}_1 \sqcup \bar{D}_2$ for the Dyck path (under the identification with $[1,a_1+a_2]$) in the lattice rectangle $[0,a_2]\times[0,a_1]$ with $\bar{D}_1=a_1+a_2+1-D_2$ and $\bar{D}_2=a_1+a_2+1-D_1$.
-  This operation can be visualized as transposing the Dyck path.
-
-  Given any quantity or object $P$ whose definition depends on $b$ and $c$, write $\vv{P}$ for the same quantity or object defined with $b$ and $c$ interchanged.
-  In particular, we have $\vv{u}_{m,\varepsilon}=u_{m,-\varepsilon}$ for any $m$ and any $\varepsilon=\pm1$.
-
-  \subsection{Structure of Dyck Paths}
-
-  Write $D^{max}=D^{max}[a_1,a_2]$ for the maximal Dyck path in the lattice rectangle $[0,a_1]\times[0,a_2]$, i.e.
-$D^{max}$ never crosses above the diagonal line joining $(0,0)$ to $(a_1,a_2)$ and any lattice point above $D^{max}$ also lies above the diagonal.
-  Observe that $\bar{D}^{max}[a_1,a_2]=D^{max}[a_2,a_1]$.
-
-  \begin{definition}
-    Call a Dyck path $D$ 
-    \begin{itemize}
-      \item \emph{horizontally-adapted to $b$} if no vertical edge of $D$ is immediately preceded by more than $b$ horizontal edges;
-      \item \emph{vertically-adapted to $c$} if no horizontal edge of $D$ is immediately followed by more than $c$ vertical edges.
-    \end{itemize}
-  \end{definition}
-
-  \begin{definition}
-    \label{def:Dyck path mutations}
-    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_{1,c}(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge of $D$, together with the $r$ vertical edges which immediately follow it, by $c-r$ horizontal edges followed by a vertical edge.
-    This provides a canonical identification of the horizontal edges of $D$ with the vertical edges of $\mu_{1,c}(D)$, this identification is again denoted by $\mu_{1,c}$.
-
-    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_{2,b}(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge of $D$, together with the $r$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-r$ vertical edges.
-    This provides a canonical identification of the vertical edges of $D$ with the horizontal edges of $\mu_{2,b}(D)$, this identification is again denoted by $\mu_{2,b}$.
-  \end{definition}
-  \begin{remark}
-    Observe that $\mu_{1,a}$ and $\mu_{2,a}$ are inverse for any $a\ge1$ whenever they are defined.
-  \end{remark}
-
-  The following result is proven in \cite[Lemma 2.4]{rupel} with appropriate notation changes, c.f. Theorem~\ref{th:dominant Dyck path recursion} for a slight modification and explicit proof.
-  \begin{lemma}\mbox{}
-    \label{le:maximal Dyck path recursion}
-    \begin{enumerate}
-      \item If $a_2 < c a_1$, then $\mu_{1,c}\big(D^{max}[a_1,a_2]\big)=D^{max}[ca_1-a_2,a_1]$.
-      \item If $a_1 < b a_2$, then $\mu_{2,b}\big(D^{max}[a_1,a_2]\big)=D^{max}[a_2,ba_2-a_1]$.
-    \end{enumerate}
-  \end{lemma}
-
-  As an immediate consequence, we determine the structure of certain maximal Dyck paths.
-  We introduce the following notation for convenience:
-  \[d_m:=\begin{cases} b & \text{if $m$ is even;}\\ c & \text{if $m$ is odd;}\end{cases} \qquad \text{and} \qquad \vv{d}_m:=\begin{cases} c & \text{if $m$ is even;}\\ b & \text{if $m$ is odd;}\end{cases}\]
-  The following was proven in \cite[Corollary 2.6]{rupel} and follows by a simple induction using Lemma~\ref{le:maximal Dyck path recursion}.
-  \begin{corollary}
-    Assume $b,c\ge2$ (this can be dropped with extra notation and slight modification).
-    Then, for $\varepsilon=\pm1$ and $m\ge1$, the maximal Dyck path $D^{m,\varepsilon}:=D^{max}[u_{m,\varepsilon},u_{m-1,-\varepsilon}]$ can be constructed as follows:
-    \begin{itemize}
-      \item $D^{1,\varepsilon}$ consists of a single horizontal edge;
-      \item $D^{2,\varepsilon}$ consists of $d_2$ horizontal edges followed by a vertical edge;
-      \item for $m\ge3$, $D_{m,\varepsilon}$ consists of $d_m - 1$ copies of $D^{m-1,\varepsilon}$ followed by a copy of $D^{m-1,\varepsilon}$ with its first $D^{m-2,\varepsilon}$ removed;
-    \end{itemize}
-    and the maximal Dyck path $\vv{\bar{D}}^{m,\varepsilon}:=D^{max}[u_{m-1,\varepsilon},u_{m,-\varepsilon}]$ can be constructed as follows:
-    \begin{itemize}
-      \item $\vv{\bar{D}}^{1,\varepsilon}$ consists of a single vertical edge;
-      \item $\vv{\bar{D}}^{2,\varepsilon}$ consists of a horizontal edge followed by $\vv{d}_2$ vertical edges;
-      \item for $m\ge3$, $\vv{\bar{D}}^{m,\varepsilon}$ consists of a copy of $\vv{\bar{D}}^{m-1,\varepsilon}$ with its last $\vv{\bar{D}}^{m-2,\varepsilon}$ removed followed by $\vv{d}_m - 1$ copies of $\vv{\bar{D}}^{m-1,\varepsilon}$.
-    \end{itemize}
-  \end{corollary}
-
-  Our main interest will be with the following Dyck paths.
-  \begin{definition}
-    \label{def:dominant Dyck path}
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, define the \emph{dominant Dyck path} $D^{dom}=D^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$.
-
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_2,-a_1+ca_2)\in\cI'$, define the \emph{dual dominant Dyck path} $\vv{D}^{dom}=\vv{D}^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2c}(x-a_1)$.
-  \end{definition}
-  \begin{remark}
-    \label{rem:intersection}
-    The lines defining $D^{dom}[a_1,a_2]$ meet at the point 
-    \[m_{a_1,a_2}:=\left( \frac{2ba_2-\big(bc-\sqrt{bc(bc-4)}\big)a_1}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2-2ca_1}{2\sqrt{bc(bc-4)}} \right).\]
-  \end{remark}
-
-  To understand the structure of the dominant Dyck paths, it will be convenient to consider their initial and final segments separately.
-  \begin{definition}
-    For $s>0$, define the \emph{Dyck path prefix} $\overrightarrow{D}^s$ as the maximal Dyck path with $s$ vertical edges starting from $(0,0)$ and terminating at $(d,s)$ while staying below the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, where $d=d_s=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
-    Call this $d$ the \emph{depth} of $s$.
-
-    For $t>0$, define the \emph{Dyck path suffix} $\overleftarrow{D}^t$ as the maximal Dyck path with $t$ horizontal edges starting from $(0,0)$ and terminating at $(t,h)$ while staying below the line $y-h=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-t)$, where $h=h_t=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
-    Call this $h$ the \emph{height} of $t$.
-  \end{definition}
-  \begin{remark}
-    There often exist multiple choices of $s$ with a given depth $d$ and multiple choices of $t$ with a given height $h$.
-  \end{remark}
-  \sayDR{ToDo: describe the analogue of Corollary 7.5 for the Dyck path prefixes and suffixes.}
-
-  The following result will be useful for showing that the Dyck path prefixes and suffixes behave properly.
-  \begin{lemma}
-    For $s>0$, the Dyck path prefix $\overrightarrow{D}^s$ ends in a vertical edge.
-    Similarly, for $t>0$, the Dyck path suffix $\overleftarrow{D}^t$ begins with a horizontal edge.
-  \end{lemma}
-
-  \begin{lemma}
-    For $s,t>0$, $\overrightarrow{D}^s=D^{dom}[d_s,s]$ and $\overleftarrow{D}^t=D^{dom}[t,h_t]$.
-  \end{lemma}
-  \begin{proof}
-    Is this obvious?
-    %Following Remark~\ref{rem:intersection}, the intersection point of the lines defining $D^{dom}[d_s,s]$ is given by
-    %\[m_{d_s,s}=\left( \frac{2bs-\big(bc-\sqrt{bc(bc-4)}\big)d_s}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)s-2cd_s}{2\sqrt{bc(bc-4)}} \right).\]
-    %By definition of $d_s$, we have
-    %\[\frac{\big(bc+\sqrt{bc(bc-4)}\big)s-2cd_s}{2\sqrt{bc(bc-4)}} \le \frac{\big(bc+\sqrt{bc(bc-4)}\big)s-\big(bc-\sqrt{bc(bc-4)}\big)s}{2\sqrt{bc(bc-4)}} = s\]
-  \end{proof}
-
-  \begin{lemma}
-    For any $s,t>0$, the Dyck path prefix $\overrightarrow{D}^s$ and Dyck path suffix $\overleftarrow{D}^t$ are both horizontally-adapted to $b$ and vertically-adapted to $c$.
-  \end{lemma}
-  \begin{proof}
-    Observe that $\frac{c}{2}<\frac{bc+\sqrt{bc(bc-4)}}{2b}<c$.
-    This shows that $\overrightarrow{D}^s$ cannot contain more than $c$ consecutive vertical edges following a horizontal edge and so $\overrightarrow{D}^s$ must be vertically-adapted to $c$.
-    In addition, we see that $\overrightarrow{D}^s$ can only contain consecutive horizontal edges if $c=1$, in which case there are at most two consecutive horizontal edges preceding any vertical edge.
-    But, since we assume $bc\ge4$, that would imply $b\ge4$ and so $\overrightarrow{D}^s$ must be horizontally-adapted to $b$.
-  \end{proof}
-
-  \begin{theorem}
-    \label{th:dominant Dyck path recursion}
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[ca_1-a_2,a_1]$ and $\mu_{2,b}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[a_2,ba_2-a_1]$.
-  \end{theorem}
-  \begin{proof}
-    We prove the result for $\mu_{1,c}$ as the result for $\mu_{2,b}$ immediately follows from $\mu_{1,b}$ being its inverse.
-    Write $D'$ for the Dyck path $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)$ and observe that by construction $D'$ has $ca_1-a_2$ horizontal edges and $a_1$ vertical edges.
-    Write $v'_1,\ldots,v'_{a_1}$ for the vertical edges of $D'$ with $v'_k$ immediately preceded by $r_k$ horizontal edges.
-    We have to show (i) that every lattice point on $D'$ stays below the lines 
-    \[y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x \qquad \text{and} \qquad y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)\]
-    while (ii) any lattice point above $D'$ is also above one of these lines.
-
-    If there exists $t$ so that $v'_t$ passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$, then
-    \[ \frac{t}{\sum\limits_{k=1}^t r_k} > \frac{bc+\sqrt{bc(bc-4)}}{2c} \]
-    or, rearranging, we have
-    \[ \frac{\sum\limits_{k=1}^t r_k}{t} < \frac{2c}{bc+\sqrt{bc(bc-4)}} = \frac{bc-\sqrt{bc(bc-4)}}{2b} \]
-    or
-    \[ \frac{bc+\sqrt{bc(bc-4)}}{2b} < \frac{ct-\sum\limits_{k=1}^t r_k}{t} = \frac{\sum\limits_{k=1}^t (c-r_k)}{t}. \]
-    But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, contrary to the definition.
-
-    If there exists $t$ so that $v'_t$ passes above the line $y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)$, then
-    \[ \frac{bc-\sqrt{bc(bc-4)}}{2c} > \frac{a_1-t}{ca_1-a_2-\sum\limits_{k=1}^t r_k} \]
-    or, rearranging, we have
-    \[ \frac{ca_1-a_2-\sum\limits_{k=1}^t r_k}{a_1-t} > \frac{2c}{bc-\sqrt{bc(bc-4)}} = \frac{bc+\sqrt{bc(bc-4)}}{2b} \]
-    or
-    \[ \frac{bc-\sqrt{bc(bc-4)}}{2b} > \frac{ c(a_1-t) - \big(ca_1-a_2-\sum\limits_{k=1}^t r_k\big)}{a_1-t} = \frac{a_2-\sum\limits_{k=1}^t (c-r_k)}{a_1-t}. \]
-    But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$, contrary to the definition.
-
-    This proves (i), analogous calculations establish (ii). 
-  \end{proof}
-
-  Apart from being the prefix and suffix for the dominant Dyck path, the Dyck paths $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ can be observed inside the maximal Dyck paths defining cluster variables as follows.
-  \begin{lemma}\mbox{}
-    \begin{itemize}
-      \item For $s>0$ and any $m \ge 2$ so that $s < u_{m,-}$, the Dyck path prefix $\overrightarrow{D}^s$ is an initial segment of the maximal Dyck path $D^{max}[u_{m-1,+},u_{m,-}]$.
-      \item For $t>0$ and any $m \ge 2$ so that $t < u_{m,+}$, the Dyck path suffix $\overleftarrow{D}^t$ is a final segment of the maximal Dyck path $D^{max}[u_{m,+},u_{m-1,-}]$.
-    \end{itemize}
-  \end{lemma}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item Choose a width $t>0$ and $a_1 \ge t$.
-        Then there exists a unique $s$ of depth $a_1-t$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_2=s+\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
-      \item Choose a height $s>0$ and $a_2 \ge s$.
-        Then there exists a unique $t$ of height $a_2-s$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_1=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil+t$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{remark}
-    The decomposition of $D^{dom}[a_1,a_2]$ as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is not uniquely determined by $a_1$ and $a_2$.
-    However, there exists at most two choices of $s$ and $t$ for which such a decomposition holds.
-  \end{remark}
-
-  \begin{lemma}
-    \label{le:floors and ceilings}
-    For any real number $x$ and any real number $r>1$, we have
-    \[\lfloor x\rfloor \le \left\lfloor \lceil xr \rceil \frac{1}{r} \right\rfloor \le \lceil x\rceil \qquad \text{and} \qquad \lfloor x\rfloor \le \left\lceil \lfloor xr \rfloor \frac{1}{r} \right\rceil \le \lceil x\rceil.\]
-  \end{lemma}
-  \begin{proof}
-    Observe that
-    \[xr\le \lceil xr \rceil < xr+1 \qquad \text{and} \qquad xr-1 < \lfloor xr \rfloor \le xr\]
-    and so
-    \[x\le \lceil xr \rceil \frac{1}{r} < x+\frac{1}{r} \qquad \text{and} \qquad x-\frac{1}{r} < \lfloor xr \rfloor \frac{1}{r} \le x.\]
-    Since $0<\frac{1}{r}<1$, the result follows.
-  \end{proof}
-
-  The following result describes the possible decomposition of the dominant Dyck path into its prefix and suffix subpaths.
-  The intersection point from Remark~\ref{rem:intersection} is a useful point of reference.
-  \begin{proposition}
-    \label{prop:dominant Dyck path decomposition}
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, the dominant Dyck path $D^{dom}[a_1,a_2]$ is the concatenation of $\overrightarrow{D}^s$ followed by $\overleftarrow{D}^t$ for any choice of $s$ and $t$ satisfying $a_2-s=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$ and $a_1-t=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
-    In this case, the pair of $s$ and $t$ will be one of the following:
-    \begin{align}
-      \label{eq:lower bounds}
-      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor\\
-      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil\\
-      \label{eq:upper bounds}
-      s=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rceil\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil
-    \end{align}
-    If two such decompositions exist, they will be of the form \eqref{eq:lower bounds} and \eqref{eq:upper bounds}.
-  \end{proposition}
-  \begin{remark}
-    The irrationality of the slopes defining the Dyck path prefixes and suffixes makes it difficult to predict for a given choice of $a_1$ and $a_2$ precisely which of these choice of $s$ and $t$ will produce the desired equalities.
-  \end{remark}
-  \begin{proof}
-    (In progress)
-
-    For $s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor$, by Lemma~\ref{le:floors and ceilings} we have
-    \[\left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor \le \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil\]
-    since $0<\frac{bc-\sqrt{bc(bc-4)}}{2c}<1$.
-    It follows that
-    \[ a_1 - \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le a_1 - \left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor\]
-    and so
-    \[ \left\lfloor \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rfloor \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rceil\]
-    with one of these inequalities being an equality.
-
-    If the left hand inequality is an equality, we take $t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor$.
-
-    The desired equalities can be rewritten in the form 
-    \[s=a_2-\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil=\left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
-    and
-    \[t=a_1-\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil=\left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
-    Combining these, we seek $s$ and $t$ satisfying
-    \[s=\left\lfloor a_2 - \left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
-    and
-    \[t=\left\lfloor a_1 - \left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
-  \end{proof}
-
-  \subsection{Compatibility}
-  The results of this section can mostly be found in \cite{lee-li-zelevinsky,rupel}.
-  However since we work in arbitrary Dyck paths instead of just the maximal ones, some results and proofs will need to be adapted.
-
-  For $e \le e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
-  When $e=e'$, we take $ee'$ to be the subpath consisting of only the edge $e$.
-  \begin{definition}
-    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ together with a subpath $ee'\subset D$, define the \emph{horizontal shadow statistic}:
-    \begin{equation}
-      \label{eq:horizontal shadow statistic}
-      f_H(ee')=-|ee' \cap D_2|+c|ee'\cap H|
-    \end{equation}
-    and the \emph{vertical shadow statistic}:
-    \begin{equation}
-      \label{eq:vertical shadow statistic}
-      f_V(ee')=-|ee' \cap D_1|+b|ee'\cap V|.
-    \end{equation}
-  \end{definition}
-  \begin{remark}
-    Observe that the shadow statistics are additive with respect to concatenation of subpaths.
-  \end{remark}
-
-  A key notion from \cite{lee-li-zelevinsky} is that of ``compatible subsets of a maximal Dyck path'', this construction immediately generalizes to arbitrary Dyck paths as follows.
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    For $h\in H$ and $v\in V$ with $h<v$, call the path $hv$ \emph{compatible} if there exists an edge $e\in hv$ such that one of the following conditions is satisfied:
-    \begin{equation}
-      \label{eq:HGC}
-      \tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0;
-    \end{equation}
-    \begin{equation}
-      \label{eq:VGC}
-      \tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0.
-    \end{equation}
-    Call the subset $H\sqcup V$ \emph{compatible} if every path $hv$ with $h\in H$ and $v\in V$ is compatible.
-    Write $\cC_D$ for the collection of all compatible subsets of $D$.
-    Given a subset $H\subset D_1$, write $\cC_D(H)$ for the collection of all $V\subset D_2$ for which $H\sqcup V\in\cC_D$.
-    Define $\cC_D(V)$ for $V\subset D_2$ similarly.
-  \end{definition}
-  \begin{remark}
-    In the construction of the greedy basis, it is necessary to consider $D$ as a closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
-    When we wish to emphasize that this condition should be imposed, we denote the Dyck path $D$ instead by $D_\WA$.
-    Following \cite[Remark 2.21]{rupel}, for $D^{m,\varepsilon}$ and $\vv{\bar{D}}^{m,\varepsilon}$ the wrap around condition does not restrict compatibility and can thus safely be omitted.
-  \end{remark}
-
-  The crucial result from \cite{lee-li-zelevinsky} can be stated as follows: if a Dyck path $D$ is vertically-adapted to $c$ (resp.
-horizontally adapted to $b$), then there is a bijection between certain compatible subsets of $D$ and certain compatible subsets of $\mu_{1,c}(D)$ (resp.
-of $\mu_{2,b}(D)$).
-  The main step in the proof that needs to be adapted to the general situation is the following.
-  For $e \le h\in D$ with $h=h_d\in D_1$, write $eh^{\!\uparrow}$ for the subpath $eh$ together with all vertical edges of depth $d$ immediately following $h$.
-  For $v \le e\in D$ with $v=v_\ell\in D_2$, write ${}^\leftarrow\!\!\! ve$ for the subpath $ve$ together with all horizontal edges of height $\ell$ immediately preceding $v$.
-  \begin{lemma}\mbox{}
-    \label{le:shadow statistic recursion}
-    \begin{enumerate}
-      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
-        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
-        Then for any $h_i \le h_j \in D_1$, we have $f_H(h_i h_j^{\!\uparrow})=-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_i v'_j)$.
-      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
-        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
-        Then for any $v_i \le v_j \in D_2$, we have $f_V({}^\leftarrow\!\!\! v_i v_j)=-\vv{f}_{H''}(h''_i {h''_j}^{\!\uparrow})$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    Claim (2) is immediate from claim (1). 
-    By definition, we have 
-    \begin{align*}
-      -\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)&=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap V'|\\
-      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \big(D'_2\setminus \mu_{1,c}(H)\big)\big|\\
-      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_2|+c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \mu_{1,c}(H)\big|.
-    \end{align*}
-    But, by construction of $\mu_{1,c}(D)$ and since $\mu_{2,c}(D')=D$, we have
-    \[\big|{}^\leftarrow\!\!\!
-v'_i v'_j \cap \mu_{1,c}(H)\big|=|h_i h_j^{\!\uparrow} \cap H| \qquad \text{and} \qquad c|{}^\leftarrow\!\!\!
-v'_i v'_j \cap D'_2|-|{}^\leftarrow\!\!\!
-v'_i v'_j \cap D'_1|=|h_i h_j^{\!\uparrow} \cap D_2|\]
-    giving
-    \[-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)=-|h_i h_j^{\!\uparrow} \cap D_2|+c|h_i h_j^{\!\uparrow} \cap H|=f_H(h_i h_j^{\!\uparrow})\]
-    as desired.
-  \end{proof}
-
-  The desired bijection of compatible subsets is constructed in terms of certain subpaths determined from each compatible subset.
-  \begin{definition}
-    \label{def:shadows}
-    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$, define the \emph{shadow paths} as follows:
-    \begin{itemize}
-      \item For $h\in D_1$, write $D(h;H)$ for the shortest subpath $he \subset D$ with $f_H(he)=0$ or, if no such subpath exists, set $D(h;H)=hv_{a_2}$.
-      \item For $v\in D_2$, write $D(v;V)$ for the shortest subpath $ev \subset D$ with $f_V(ev)=0$ or, if no such subpath exists, set $D(v;V)=h_1 v$.
-    \end{itemize}
-    Write 
-    \[D(H):=\bigcup_{h\in H} D(h;H) \qquad \text{and} \qquad D(V):=\bigcup_{v\in V} D(v;V).\]
-    Define the \emph{shadow} of $H$ (resp.
-the \emph{shadow} of $V$) as the set $\sh_D(H):=D(H)\cap D_2$ (resp.~$\sh_D(V):=D(V)\cap D_1$) and the \emph{local shadow} of $h\in H$ (resp.
-of $v\in V$) as the set $\sh_D(h;H)=D(h;H)\cap D_2$ (resp.
-$\sh_D(v;V)=D(v;V)\cap D_1$).
-  \end{definition}
-
-  The proofs of the following results are identical to the proof of the analogous results from \cite{lee-li-zelevinsky,rupel} for maximal Dyck paths.
-  \begin{lemma}
-    \label{le:shadow statistics}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $h\in H$, take $he$ to be the path $D(h;H)$.
-        The following hold:
-        \begin{enumerate}
-          \item for any proper subpath $he'\subsetneq he$, we have $f_H(he')>0$;
-          \item if $f_H(he)=0$, then for any proper subpath $e'e\subsetneq he$, we have $f_H(e'e)<0$;
-          \item $e\in V$.
-        \end{enumerate}
-      \item For $v\in V$, take $ev$ to be the path $D(v;V)$.
-        The following hold:
-        \begin{enumerate}
-          \item for any proper subpath $e'v\subsetneq ev$, we have $f_V(e'v)>0$;
-          \item if $f_V(ev)=0$, then for any proper subpath $ee'\subsetneq ev$, we have $f_V(ee')<0$;
-          \item $e\in H$.
-        \end{enumerate}
-    \end{enumerate}
-  \end{lemma}
-  \begin{remark}
-    Observe that the subset $V$ has no influence on the claim of (1) and the subset $H$ has no influence on the claim of (2).
-  \end{remark}
-
-  \begin{definition}
-    Given two Dyck paths $D,D'$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $D'\succ D$ if no lattice point of $D'$ lies below a lattice point of $D$.
-  \end{definition}
-  \begin{remark}
-    Equivalently, $D'\succ D$ if no lattice point of $D'$ lies to the right of a lattice point of $D$.
-  \end{remark}
-
-  \begin{proposition}
-    Let $D,D'$ be two Dyck paths in the lattice rectangle $[0,a_1]\times[0,a_2]$ with $D'\succ D$.
-    Identify $D_1$ with $D'_1$ and $D_2$ with $D'_2$ along the natural left-to-right ordering.
-    For subsets $H\subset D_1$ and $V\subset D_2$, write $H'\subset D'_1$ and $V'\subset D'_2$ for the corresponding subsets under the identification above.
-    If $(H,V) \in \cC_D$, then $(H',V') \in \cC_{D'}$.
-  \end{proposition}
-  \begin{proof}
-    It suffices, by induction, to show that the result holds if $D'$ is an immediate successor of $D$, i.e.
-when a single pair of a horizontal followed by a vertical is replaced by a vertical followed by a horizontal.
-    Assume $D'$ is obtained from $D$ in this way, say with horizontal edge $h_i$ and vertical edge $v_j$ satisfying $v_j=h_i+1$ in $D$ replaced by the vertical edge $v'_j$ and the horizontal edge $h'_i$ satisfying $h'_i=v'_j+1$ in $D'$.
-
-    Consider $(H,V) \in \cC_D$.
-    For $h\in H$ and $v\in V$, write $h'\in H'$ and $v'\in V'$ for the corresponding edges.
-    We claim that the condition \eqref{eq:HGC} (resp. \eqref{eq:VGC}) being satisfied for the path $hv$ in $D$ implies the same condition is satisfied for the path $h'v'$ in $D'$.
-
-    Suppose \eqref{eq:HGC} is satisfied for the path $hv$ and write $D(h;H)=he$ for $e\in V$ with $e<v$.
-    If $h_i,v_j\notin D(h;H)$, then under the identification with $D'$ we have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
-    Alternatively, since $e\in V$, we must have both $h_i,v_j\in D(h;H)$.
-    If $h_i\notin H$, then again we have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
-    Thus, we assume $h_i\in H$.
-
-    We begin by assuming $h_i\ne h$.
-    This gives two possibilities for $D(h';H')$ depending on $D(h'_i;H')$.
-    First, observe that $D(h_i;H)$ is a proper subpath of $h_ie$, for otherwise $f_H(h_ie)=0$ and, by the additivity of $f_H$, $he$ would not be the shortest subpath with $f_H(he)=0$.
-    Thus, if $D(h_i;H)$ is followed by at least two vertical edges inside $D(h;H)$, we again have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
-    Otherwise, $D(h';H')$ is an initial subpath of $D(h;H)$ under the identification of $D'$ with $D$ and again \eqref{eq:HGC} is satisfied for the path $h'v'$.
-
-    Now if $h_i=h$...
-  \end{proof}
-
-  \begin{corollary}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $h\in H$ and a vertical edge $v\in D(h;H)$, the condition \eqref{eq:HGC} is not satisfied for the path $hv$ but for any $V\in\cC_D(H)$ the condition \eqref{eq:VGC} is satisfied for the path $hv$.
-        In particular, $D(v;V)$ is a proper subpath of $hv$ for any $V\in\cC_D(H)$.
-      \item For $v\in V$ and a horizontal edge $h\in D(v;V)$, the condition \eqref{eq:VGC} is not satisfied for the pair $hv$ but for any $H\in\cC_D(V)$ the condition \eqref{eq:HGC} is satisfied for the path $hv$.
-        In particular, $D(h;H)$ is a proper subpath of $hv$ for any $H\in\cC_D(V)$.
-    \end{enumerate}
-  \end{corollary}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item For $H\subset D_1$ and $h,h'\in H$, the local shadows $\sh_D(h;H)$ and $\sh_D(h';H)$ are either disjoint or one is contained in the other.
-      \item For $V\subset D_2$ and $v,v'\in V$, the local shadows $\sh_D(v;V)$ and $\sh_D(v';V)$ are either disjoint or one is contained in the other.
-    \end{enumerate}
-  \end{lemma}
-
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $H$, by removing for each $d\in[1,a_1]$ the first (up to) $c$ vertical edges of depth $d$ immediately following $h_d$.
-      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $V$, by removing for each $\ell\in[0,a_2-1]$ the first (up to) $b$ horizontal edges of height $\ell$ immediately preceding $v_{\ell+1}$.
-    \end{enumerate}
-  \end{definition}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item For $H\subset D_1$, $V\in\cC_D(H)$ if and only if $V$ is disjoint from $\sh_D(H)\setminus\rsh_D(H)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in H$ and $v\in\rsh_D(H)$.
-      \item For $V\subset D_2$, $H\in\cC_D(V)$ if and only if $H$ is disjoint from $\sh_D(V)\setminus\rsh_D(V)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in\rsh_D(V)$ and $v\in V$.
-    \end{enumerate}
-  \end{lemma}
-
-  \begin{definition}
-    For $H\subset D_1$, write $\cC_D^{rsh}(H)$ for the subset of $V\in\cC_D(H)$ with $V\subset\rsh_D(H)$.
-    For $V\subset D_2$, write $\cC_D^{rsh}(V)$ for the subset of $H\in\cC_D(V)$ with $H\subset\rsh_D(V)$.
-  \end{definition}
-
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $1 \le j < d \le a_1$ with $h_j\in H$, denote by $\rsh_D(H)_{j;d}$ the set of all $v\in\rsh_D(H)$ of depth $d$ such that $v\in\sh(h_j;H)$ and $h_j$ is the first horizontal edge before $v$ with this property.
-        Define the \emph{local remote shadow} of the edge $h_j$ by $\rsh_D(h_j;H):=\bigsqcup\limits_{d\in[j+1,a_1]} \rsh_D(H)_{j;d}$.
-      \item For $1 \le \ell <  k \le a_2$ with $v_k\in V$, denote by $\rsh_D(V)_{k;\ell}$ the set of all $h\in\rsh_D(V)$ of height $\ell$ such that $h\in\sh(v_k;V)$ and $v_k$ is the first vertical edge after $h$ with this property.
-        Define the \emph{local remote shadow} of the edge $v_k$ by $\rsh_D(v_k;V):=\bigsqcup\limits_{\ell\in[1,k-1]} \rsh_D(V)_{k;\ell}$.
-    \end{enumerate}
-  \end{definition}
-
-  As shown in \cite{lee-li-zelevinsky} for maximal Dyck paths, the remote shadow can be characterized as follows.
-  \begin{lemma}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $1 \le d < j \le a_1$, we have $\rsh_D(H)_{j;d} \ne \varnothing$ if and only if $f_H(h'h_d^{\!\uparrow}) < 0 < f_H(h_jh^{\!\uparrow})$ for every pair of consecutive horizontal edges $h<h'$ in the path $h_j h_d^{\!\uparrow}$.
-      \item For $1 \le \ell < k \le a_2$, we have $\rsh_D(V)_{k;\ell} \ne \varnothing$ if and only if $f_V({}^\leftarrow\!\!\!
-v_\ell v) < 0 < f_V({}^\leftarrow\!\!\!
-v' v_k)$ for every pair of consecutive vertical edges $v<v'$ in the path ${}^\leftarrow\!\!\!
-v_\ell v_k$.
-    \end{enumerate}
-  \end{lemma}
-
-  \begin{lemma}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item Let $1 \le d < j \le a_1$ and suppose $\rsh_D(H)_{j;d} \ne \varnothing$, then
-        \[|\rsh_D(H)_{j;d}| = \min\limits_{h_j \le h < h' \le h_d} \min\big( -f_H(h'h_d^{\!\uparrow}) , f_H(h_jh^{\!\uparrow}) \big).\]
-      \item Let $1 \le \ell < k \le a_2$ and suppose $\rsh_D(V)_{k;\ell} \ne \varnothing$, then
-        \[|\rsh_D(V)_{k;\ell}| = \min\limits_{v_\ell \le v < v' \le v_k} \min\big( -f_V({}^\leftarrow\!\!\! v_\ell v) , f_V({}^\leftarrow\!\!\! v' v_k) \big).\]
-    \end{enumerate}
-  \end{lemma}
-
-  Then the following result immediately follows from Lemma~\ref{le:shadow statistic recursion}.
-  \begin{corollary}\mbox{}
-    \label{cor:remote shadows}
-    \begin{enumerate}
-      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
-        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
-        Then, for $1 \le d < j \le a_1$, we have $|\rsh_D(H)_{j;d}|=|\rsh_{D'}(V')_{d;j}|$.
-      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
-        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
-        Then, for $1 \le \ell < k \le a_2$, we have $|\rsh_D(V)_{k;\ell}|=|\rsh_{D''}(H'')_{\ell;k}$.
-    \end{enumerate}
-  \end{corollary}
-
-  In the results below, we keep the notation and assumptions from Corollary~\ref{cor:remote shadows}.
-  It follows that, for $H\subset D_1$ and $1 \le d < j \le a_1$, we may define an order-reversing bijection $\theta^H_{j;d} : \rsh_D(H)_{j;d} \to \rsh_{D'}(V')_{d;j}$.
-  Similarly, for $V\subset D_2$ and $1 \le \ell < k \le a_2$, we may define an order-reversing bijection $\theta^V_{k;\ell} : \rsh_D(V)_{k;\ell} \to \rsh_{D''}(H'')_{\ell;k}$.
-  \begin{definition}\mbox{}
-    \begin{enumerate}
-      \item For $H\subset D_1$ and $V \subset \rsh_D(H)$, define $\Omega_H(V) \subset \rsh_{D'}(V')$ by
-        \[\Omega_H(V)=\{\theta^H_{j;d}(v) : v \in \rsh_D(H)_{j;d}, 1 \le d < j \le a_1\}.\]
-      \item For $V\subset D_2$ and $H \subset \rsh_D(V)$, define $\Omega_V(H) \subset \rsh_{D''}(H'')$ by
-        \[\Omega_V(H)=\{\theta^V_{k;\ell}(h) : h \in \rsh_D(V)_{k;\ell}, 1 \le \ell < k \le a_2\}.\]
-    \end{enumerate}
-  \end{definition}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item Consider $H\subset D_1$ and $V \subset \rsh_D(H)$.
-        Suppose $h'=\theta^H_{j;d}(v)$ for $v\in V$.
-        Then $f_{\Omega_H(V)}(h'v'_d)=f_V(h_j v)$.
-      \item Consider $V\subset D_2$ and $H \subset \rsh_D(V)$.
-        Suppose $v''=\theta^V_{k;\ell}(h)$ for $h\in H$.
-        Then $f_{\Omega_V(H)}(h''_\ell v'')=f_V(h v_k)$.
-    \end{enumerate}
-  \end{lemma}
-
-  The following equivalence of compatibilities is the main result we need.
-  \begin{corollary}\mbox{}
-    \begin{enumerate}
-      \item For $H \subset D_1$ and $V \subset \rsh_D(H)$, we have $V\in\cC_D(H)$ if and only if $\Omega_H(V)\in\cC_{D'}(V')$.
-      \item For $V \subset D_2$ and $H \subset \rsh_D(V)$, we have $H\in\cC_D(V)$ if and only if $\Omega_V(H)\in\cC_{D''}(H'')$.
-    \end{enumerate}
-  \end{corollary}
-
-  We associate to $D$ the element $x_D\in\ZZ_{\ge0}[x_1^{\pm1},x_2^{\pm1}]$ defined as follows
-  \[x_D:=x_1^{-a_1} x_2^{-a_2} \sum_{H\sqcup V\in\cC_D} x_1^{b|V|} x_2^{c|H|}.\]
-
-  \begin{theorem}[\cite{lee-li-zelevinsky}]
-    For $(a_1,a_2)=(u_{m,+},u_{m-1,-})$ or $(u_{m-1,+},u_{m,-})$ for $m\ge1$, the element $x_{D^{max}[a_1,a_2]}$ is a non-initial cluster variable.
-    Otherwise, the element $x_{D^{max}_\WA[a_1,a_2]}$ is an element of the greedy basis
-  \end{theorem}
-
-  \begin{lemma}
-    Suppose there are two factorizations
-    \[x_D=x_1^{-a_1} x_2^{-a_2} \sum_{t=0}^{a_2}\sum_{k=0}^{a_1} \nu_{k,t} x_1^{bt}(1+x_2^c)^{a_1-k}=x_1^{-a_1} x_2^{-a_2} \sum_{s=0}^{a_1}\sum_{\ell=0}^{a_2} \theta_{s,\ell} x_2^{cs}(1+x_1^b)^{a_2-\ell},\]
-    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\sh_D(H)|=\ell$.
-    Then 
-    \[\sum_{k=0}^{a_1-s} {a_1-k\choose s} \nu_{k,t}=\sum_{\ell=0}^{a_2-t} {a_2-\ell\choose t} \theta_{s,\ell}\]
-    for all possible $s$ and $t$.
-  \end{lemma}
-  \begin{question}
-    How do such expressions behave under mutations?
-  \end{question}
-
-  \begin{lemma}
-    Choose $a_1,a_2\in\ZZ_{\ge0}$.
-    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_{D^{st}}$ coincides with the corresponding standard monomial basis element.
-  \end{lemma}
-
-  \begin{definition}
-    Suppose $D^{dom}[a_1,a_2]$ decomposes as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$.
-    Call a pair of subsets $H \sqcup V$ \emph{piecewise compatible} if the intersections with $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ are compatible on the subpaths.
-  \end{definition}
-
-  \begin{theorem}
-    Suppose $H \sqcup V$ is a piecewise compatible subset of $D^{dom}[a_1,a_2]$.
-    \begin{itemize}
-      \item If the last vertical edge of $\overrightarrow{D}^s$ is contained in $V$, then $H \sqcup V$ is compatible.
-      \item If the first horizontal edge of $\overleftarrow{D}^t$ is contained in $H$, then $H \sqcup V$ is compatible.
-    \end{itemize}
-  \end{theorem}
-
-  \begin{thebibliography}{XXX}
-
-    \bibitem{lee-li-zelevinsky}
-      K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014), pp.~57--82.
-
-    \bibitem{rupel}
-      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
-Algebraic Combinatorics, \textbf{2} (2019) no.
-6, pp.~1239--1273.
-\href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
-  \end{thebibliography}
-
-  \section{Chebyshev}
-  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
-  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
-  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
-
-  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
-  This leads to the following more general recursive structure.
-  \begin{lemma}
-    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
-    \begin{equation}
-      \label{eq:long Chebyshev recursion}
-      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
-    \end{equation}
-  \end{lemma}
-  \begin{proof}
-    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
-    Using the claim for $j>0$ and then the defining recursion twice, we get
-    \begin{align*}
-      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
-    \end{align*}
-    which is the claimed recursion for $\ell+1$.
-    These calculations can be reversed to show the result for $\ell<0$.
-  \end{proof}
-
-  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
-  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
-  By the equalities 
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
-  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
-  \begin{remark}
-    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
-    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
-  \end{remark}
-
-  \begin{lemma}
-    We have
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
-  \end{lemma}
-  \begin{proof}
-    For any $i\ge 1$, we have
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
-    It follows that
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
-    which is equivalent to the desired expression.
-    Similarly, 
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
-    so that
-    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
-    which is again equivalent to the desired expression.
-  \end{proof}
-
 \section{The affine case}
@@
 \end{document}
+
+  \section{Bases From Compatible Pairs on Dyck Paths}
+  \sayDR{This is a bit of a repetition of the above introduction to Dyck paths, but with slightly different goals it seemed that a modified exposition was more appropriate.}
+  For $a_1,a_2\in\ZZ_{\ge0}$, choose a Dyck path $D$ in the lattice rectangle $[0,a_1]\times[0,a_2]$.
+  When we wish to emphasize the upper right bounding corner we will write $D[a_1,a_2]$.
+  Consider $D$ as the totally ordered set of its edges along the natural labeling from $(0,0)$ to $(a_1,a_2)$.
+  It may be convenient to identify $D$ with the ordered set $[1,a_1+a_2]$.
+  Write $D=D_1\sqcup D_2$, where $D_1=\{h_1,\ldots,h_{a_1}\}$ is the set of horizontal edges and $D_2=\{v_1,\ldots,v_{a_2}\}$ is the set of vertical edges.
+  Define the \emph{height}, $\hgt(h)$ for $h\in D_1$, as one more than the number of $v\in D_2$ with $v<h$.
+  Define the \emph{depth}, $\dpt(v)$ for $v\in D_2$, as the number of $h\in D_1$ with $h<v$.
+  \begin{remark}
+    The seemingly different conventions for computing height and depth provide uniformity later.
+    Indeed, the vertical edges immediately following $h_d$ have depth $d$, while this convention allows the horizontal edges immediately preceding $v_\ell$ to similarly be said to have height $\ell$.
+  \end{remark}
+
+  Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
+  Given a Dyck path $D=D_1\sqcup D_2$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $\bar{D}=\bar{D}_1 \sqcup \bar{D}_2$ for the Dyck path (under the identification with $[1,a_1+a_2]$) in the lattice rectangle $[0,a_2]\times[0,a_1]$ with $\bar{D}_1=a_1+a_2+1-D_2$ and $\bar{D}_2=a_1+a_2+1-D_1$.
+  This operation can be visualized as transposing the Dyck path.
+
+  Given any quantity or object $P$ whose definition depends on $b$ and $c$, write $\vv{P}$ for the same quantity or object defined with $b$ and $c$ interchanged.
+  In particular, we have $\vv{u}_{m,\varepsilon}=u_{m,-\varepsilon}$ for any $m$ and any $\varepsilon=\pm1$.
+
+  \subsection{Structure of Dyck Paths}
+
+  Write $D^{max}=D^{max}[a_1,a_2]$ for the maximal Dyck path in the lattice rectangle $[0,a_1]\times[0,a_2]$, i.e.
+$D^{max}$ never crosses above the diagonal line joining $(0,0)$ to $(a_1,a_2)$ and any lattice point above $D^{max}$ also lies above the diagonal.
+  Observe that $\bar{D}^{max}[a_1,a_2]=D^{max}[a_2,a_1]$.
+
+  \begin{definition}
+    Call a Dyck path $D$ 
+    \begin{itemize}
+      \item \emph{horizontally-adapted to $b$} if no vertical edge of $D$ is immediately preceded by more than $b$ horizontal edges;
+      \item \emph{vertically-adapted to $c$} if no horizontal edge of $D$ is immediately followed by more than $c$ vertical edges.
+    \end{itemize}
+  \end{definition}
+
+  \begin{definition}
+    \label{def:Dyck path mutations}
+    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_{1,c}(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge of $D$, together with the $r$ vertical edges which immediately follow it, by $c-r$ horizontal edges followed by a vertical edge.
+    This provides a canonical identification of the horizontal edges of $D$ with the vertical edges of $\mu_{1,c}(D)$, this identification is again denoted by $\mu_{1,c}$.
+
+    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_{2,b}(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge of $D$, together with the $r$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-r$ vertical edges.
+    This provides a canonical identification of the vertical edges of $D$ with the horizontal edges of $\mu_{2,b}(D)$, this identification is again denoted by $\mu_{2,b}$.
+  \end{definition}
+  \begin{remark}
+    Observe that $\mu_{1,a}$ and $\mu_{2,a}$ are inverse for any $a\ge1$ whenever they are defined.
+  \end{remark}
+
+  The following result is proven in \cite[Lemma 2.4]{rupel} with appropriate notation changes, c.f. Theorem~\ref{th:dominant Dyck path recursion} for a slight modification and explicit proof.
+  \begin{lemma}\mbox{}
+    \label{le:maximal Dyck path recursion}
+    \begin{enumerate}
+      \item If $a_2 < c a_1$, then $\mu_{1,c}\big(D^{max}[a_1,a_2]\big)=D^{max}[ca_1-a_2,a_1]$.
+      \item If $a_1 < b a_2$, then $\mu_{2,b}\big(D^{max}[a_1,a_2]\big)=D^{max}[a_2,ba_2-a_1]$.
+    \end{enumerate}
+  \end{lemma}
+
+  As an immediate consequence, we determine the structure of certain maximal Dyck paths.
+  We introduce the following notation for convenience:
+  \[d_m:=\begin{cases} b & \text{if $m$ is even;}\\ c & \text{if $m$ is odd;}\end{cases} \qquad \text{and} \qquad \vv{d}_m:=\begin{cases} c & \text{if $m$ is even;}\\ b & \text{if $m$ is odd;}\end{cases}\]
+  The following was proven in \cite[Corollary 2.6]{rupel} and follows by a simple induction using Lemma~\ref{le:maximal Dyck path recursion}.
+  \begin{corollary}
+    Assume $b,c\ge2$ (this can be dropped with extra notation and slight modification).
+    Then, for $\varepsilon=\pm1$ and $m\ge1$, the maximal Dyck path $D^{m,\varepsilon}:=D^{max}[u_{m,\varepsilon},u_{m-1,-\varepsilon}]$ can be constructed as follows:
+    \begin{itemize}
+      \item $D^{1,\varepsilon}$ consists of a single horizontal edge;
+      \item $D^{2,\varepsilon}$ consists of $d_2$ horizontal edges followed by a vertical edge;
+      \item for $m\ge3$, $D_{m,\varepsilon}$ consists of $d_m - 1$ copies of $D^{m-1,\varepsilon}$ followed by a copy of $D^{m-1,\varepsilon}$ with its first $D^{m-2,\varepsilon}$ removed;
+    \end{itemize}
+    and the maximal Dyck path $\vv{\bar{D}}^{m,\varepsilon}:=D^{max}[u_{m-1,\varepsilon},u_{m,-\varepsilon}]$ can be constructed as follows:
+    \begin{itemize}
+      \item $\vv{\bar{D}}^{1,\varepsilon}$ consists of a single vertical edge;
+      \item $\vv{\bar{D}}^{2,\varepsilon}$ consists of a horizontal edge followed by $\vv{d}_2$ vertical edges;
+      \item for $m\ge3$, $\vv{\bar{D}}^{m,\varepsilon}$ consists of a copy of $\vv{\bar{D}}^{m-1,\varepsilon}$ with its last $\vv{\bar{D}}^{m-2,\varepsilon}$ removed followed by $\vv{d}_m - 1$ copies of $\vv{\bar{D}}^{m-1,\varepsilon}$.
+    \end{itemize}
+  \end{corollary}
+
+  Our main interest will be with the following Dyck paths.
+  \begin{definition}
+    \label{def:dominant Dyck path}
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, define the \emph{dominant Dyck path} $D^{dom}=D^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$.
+
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_2,-a_1+ca_2)\in\cI'$, define the \emph{dual dominant Dyck path} $\vv{D}^{dom}=\vv{D}^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2c}(x-a_1)$.
+  \end{definition}
+  \begin{remark}
+    \label{rem:intersection}
+    The lines defining $D^{dom}[a_1,a_2]$ meet at the point 
+    \[m_{a_1,a_2}:=\left( \frac{2ba_2-\big(bc-\sqrt{bc(bc-4)}\big)a_1}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2-2ca_1}{2\sqrt{bc(bc-4)}} \right).\]
+  \end{remark}
+
+  To understand the structure of the dominant Dyck paths, it will be convenient to consider their initial and final segments separately.
+  \begin{definition}
+    For $s>0$, define the \emph{Dyck path prefix} $\overrightarrow{D}^s$ as the maximal Dyck path with $s$ vertical edges starting from $(0,0)$ and terminating at $(d,s)$ while staying below the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, where $d=d_s=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
+    Call this $d$ the \emph{depth} of $s$.
+
+    For $t>0$, define the \emph{Dyck path suffix} $\overleftarrow{D}^t$ as the maximal Dyck path with $t$ horizontal edges starting from $(0,0)$ and terminating at $(t,h)$ while staying below the line $y-h=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-t)$, where $h=h_t=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
+    Call this $h$ the \emph{height} of $t$.
+  \end{definition}
+  \begin{remark}
+    There often exist multiple choices of $s$ with a given depth $d$ and multiple choices of $t$ with a given height $h$.
+  \end{remark}
+  \sayDR{ToDo: describe the analogue of Corollary 7.5 for the Dyck path prefixes and suffixes.}
+
+  The following result will be useful for showing that the Dyck path prefixes and suffixes behave properly.
+  \begin{lemma}
+    For $s>0$, the Dyck path prefix $\overrightarrow{D}^s$ ends in a vertical edge.
+    Similarly, for $t>0$, the Dyck path suffix $\overleftarrow{D}^t$ begins with a horizontal edge.
+  \end{lemma}
+
+  \begin{lemma}
+    For $s,t>0$, $\overrightarrow{D}^s=D^{dom}[d_s,s]$ and $\overleftarrow{D}^t=D^{dom}[t,h_t]$.
+  \end{lemma}
+  \begin{proof}
+    Is this obvious?
+    %Following Remark~\ref{rem:intersection}, the intersection point of the lines defining $D^{dom}[d_s,s]$ is given by
+    %\[m_{d_s,s}=\left( \frac{2bs-\big(bc-\sqrt{bc(bc-4)}\big)d_s}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)s-2cd_s}{2\sqrt{bc(bc-4)}} \right).\]
+    %By definition of $d_s$, we have
+    %\[\frac{\big(bc+\sqrt{bc(bc-4)}\big)s-2cd_s}{2\sqrt{bc(bc-4)}} \le \frac{\big(bc+\sqrt{bc(bc-4)}\big)s-\big(bc-\sqrt{bc(bc-4)}\big)s}{2\sqrt{bc(bc-4)}} = s\]
+  \end{proof}
+
+  \begin{lemma}
+    For any $s,t>0$, the Dyck path prefix $\overrightarrow{D}^s$ and Dyck path suffix $\overleftarrow{D}^t$ are both horizontally-adapted to $b$ and vertically-adapted to $c$.
+  \end{lemma}
+  \begin{proof}
+    Observe that $\frac{c}{2}<\frac{bc+\sqrt{bc(bc-4)}}{2b}<c$.
+    This shows that $\overrightarrow{D}^s$ cannot contain more than $c$ consecutive vertical edges following a horizontal edge and so $\overrightarrow{D}^s$ must be vertically-adapted to $c$.
+    In addition, we see that $\overrightarrow{D}^s$ can only contain consecutive horizontal edges if $c=1$, in which case there are at most two consecutive horizontal edges preceding any vertical edge.
+    But, since we assume $bc\ge4$, that would imply $b\ge4$ and so $\overrightarrow{D}^s$ must be horizontally-adapted to $b$.
+  \end{proof}
+
+  \begin{theorem}
+    \label{th:dominant Dyck path recursion}
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[ca_1-a_2,a_1]$ and $\mu_{2,b}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[a_2,ba_2-a_1]$.
+  \end{theorem}
+  \begin{proof}
+    We prove the result for $\mu_{1,c}$ as the result for $\mu_{2,b}$ immediately follows from $\mu_{1,b}$ being its inverse.
+    Write $D'$ for the Dyck path $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)$ and observe that by construction $D'$ has $ca_1-a_2$ horizontal edges and $a_1$ vertical edges.
+    Write $v'_1,\ldots,v'_{a_1}$ for the vertical edges of $D'$ with $v'_k$ immediately preceded by $r_k$ horizontal edges.
+    We have to show (i) that every lattice point on $D'$ stays below the lines 
+    \[y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x \qquad \text{and} \qquad y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)\]
+    while (ii) any lattice point above $D'$ is also above one of these lines.
+
+    If there exists $t$ so that $v'_t$ passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$, then
+    \[ \frac{t}{\sum\limits_{k=1}^t r_k} > \frac{bc+\sqrt{bc(bc-4)}}{2c} \]
+    or, rearranging, we have
+    \[ \frac{\sum\limits_{k=1}^t r_k}{t} < \frac{2c}{bc+\sqrt{bc(bc-4)}} = \frac{bc-\sqrt{bc(bc-4)}}{2b} \]
+    or
+    \[ \frac{bc+\sqrt{bc(bc-4)}}{2b} < \frac{ct-\sum\limits_{k=1}^t r_k}{t} = \frac{\sum\limits_{k=1}^t (c-r_k)}{t}. \]
+    But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, contrary to the definition.
+
+    If there exists $t$ so that $v'_t$ passes above the line $y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)$, then
+    \[ \frac{bc-\sqrt{bc(bc-4)}}{2c} > \frac{a_1-t}{ca_1-a_2-\sum\limits_{k=1}^t r_k} \]
+    or, rearranging, we have
+    \[ \frac{ca_1-a_2-\sum\limits_{k=1}^t r_k}{a_1-t} > \frac{2c}{bc-\sqrt{bc(bc-4)}} = \frac{bc+\sqrt{bc(bc-4)}}{2b} \]
+    or
+    \[ \frac{bc-\sqrt{bc(bc-4)}}{2b} > \frac{ c(a_1-t) - \big(ca_1-a_2-\sum\limits_{k=1}^t r_k\big)}{a_1-t} = \frac{a_2-\sum\limits_{k=1}^t (c-r_k)}{a_1-t}. \]
+    But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$, contrary to the definition.
+
+    This proves (i), analogous calculations establish (ii). 
+  \end{proof}
+
+  Apart from being the prefix and suffix for the dominant Dyck path, the Dyck paths $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ can be observed inside the maximal Dyck paths defining cluster variables as follows.
+  \begin{lemma}\mbox{}
+    \begin{itemize}
+      \item For $s>0$ and any $m \ge 2$ so that $s < u_{m,-}$, the Dyck path prefix $\overrightarrow{D}^s$ is an initial segment of the maximal Dyck path $D^{max}[u_{m-1,+},u_{m,-}]$.
+      \item For $t>0$ and any $m \ge 2$ so that $t < u_{m,+}$, the Dyck path suffix $\overleftarrow{D}^t$ is a final segment of the maximal Dyck path $D^{max}[u_{m,+},u_{m-1,-}]$.
+    \end{itemize}
+  \end{lemma}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item Choose a width $t>0$ and $a_1 \ge t$.
+        Then there exists a unique $s$ of depth $a_1-t$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_2=s+\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
+      \item Choose a height $s>0$ and $a_2 \ge s$.
+        Then there exists a unique $t$ of height $a_2-s$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_1=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil+t$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{remark}
+    The decomposition of $D^{dom}[a_1,a_2]$ as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is not uniquely determined by $a_1$ and $a_2$.
+    However, there exists at most two choices of $s$ and $t$ for which such a decomposition holds.
+  \end{remark}
+
+  \begin{lemma}
+    \label{le:floors and ceilings}
+    For any real number $x$ and any real number $r>1$, we have
+    \[\lfloor x\rfloor \le \left\lfloor \lceil xr \rceil \frac{1}{r} \right\rfloor \le \lceil x\rceil \qquad \text{and} \qquad \lfloor x\rfloor \le \left\lceil \lfloor xr \rfloor \frac{1}{r} \right\rceil \le \lceil x\rceil.\]
+  \end{lemma}
+  \begin{proof}
+    Observe that
+    \[xr\le \lceil xr \rceil < xr+1 \qquad \text{and} \qquad xr-1 < \lfloor xr \rfloor \le xr\]
+    and so
+    \[x\le \lceil xr \rceil \frac{1}{r} < x+\frac{1}{r} \qquad \text{and} \qquad x-\frac{1}{r} < \lfloor xr \rfloor \frac{1}{r} \le x.\]
+    Since $0<\frac{1}{r}<1$, the result follows.
+  \end{proof}
+
+  The following result describes the possible decomposition of the dominant Dyck path into its prefix and suffix subpaths.
+  The intersection point from Remark~\ref{rem:intersection} is a useful point of reference.
+  \begin{proposition}
+    \label{prop:dominant Dyck path decomposition}
+    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, the dominant Dyck path $D^{dom}[a_1,a_2]$ is the concatenation of $\overrightarrow{D}^s$ followed by $\overleftarrow{D}^t$ for any choice of $s$ and $t$ satisfying $a_2-s=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$ and $a_1-t=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
+    In this case, the pair of $s$ and $t$ will be one of the following:
+    \begin{align}
+      \label{eq:lower bounds}
+      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor\\
+      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil\\
+      \label{eq:upper bounds}
+      s=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rceil\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil
+    \end{align}
+    If two such decompositions exist, they will be of the form \eqref{eq:lower bounds} and \eqref{eq:upper bounds}.
+  \end{proposition}
+  \begin{remark}
+    The irrationality of the slopes defining the Dyck path prefixes and suffixes makes it difficult to predict for a given choice of $a_1$ and $a_2$ precisely which of these choice of $s$ and $t$ will produce the desired equalities.
+  \end{remark}
+  \begin{proof}
+    (In progress)
+
+    For $s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor$, by Lemma~\ref{le:floors and ceilings} we have
+    \[\left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor \le \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil\]
+    since $0<\frac{bc-\sqrt{bc(bc-4)}}{2c}<1$.
+    It follows that
+    \[ a_1 - \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le a_1 - \left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor\]
+    and so
+    \[ \left\lfloor \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rfloor \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rceil\]
+    with one of these inequalities being an equality.
+
+    If the left hand inequality is an equality, we take $t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor$.
+
+    The desired equalities can be rewritten in the form 
+    \[s=a_2-\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil=\left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
+    and
+    \[t=a_1-\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil=\left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
+    Combining these, we seek $s$ and $t$ satisfying
+    \[s=\left\lfloor a_2 - \left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
+    and
+    \[t=\left\lfloor a_1 - \left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
+  \end{proof}
+
+  \subsection{Compatibility}
+  The results of this section can mostly be found in \cite{lee-li-zelevinsky,rupel}.
+  However since we work in arbitrary Dyck paths instead of just the maximal ones, some results and proofs will need to be adapted.
+
+  For $e \le e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
+  When $e=e'$, we take $ee'$ to be the subpath consisting of only the edge $e$.
+  \begin{definition}
+    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ together with a subpath $ee'\subset D$, define the \emph{horizontal shadow statistic}:
+    \begin{equation}
+      \label{eq:horizontal shadow statistic}
+      f_H(ee')=-|ee' \cap D_2|+c|ee'\cap H|
+    \end{equation}
+    and the \emph{vertical shadow statistic}:
+    \begin{equation}
+      \label{eq:vertical shadow statistic}
+      f_V(ee')=-|ee' \cap D_1|+b|ee'\cap V|.
+    \end{equation}
+  \end{definition}
+  \begin{remark}
+    Observe that the shadow statistics are additive with respect to concatenation of subpaths.
+  \end{remark}
+
+  A key notion from \cite{lee-li-zelevinsky} is that of ``compatible subsets of a maximal Dyck path'', this construction immediately generalizes to arbitrary Dyck paths as follows.
+  \begin{definition}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    For $h\in H$ and $v\in V$ with $h<v$, call the path $hv$ \emph{compatible} if there exists an edge $e\in hv$ such that one of the following conditions is satisfied:
+    \begin{equation}
+      \label{eq:HGC}
+      \tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0;
+    \end{equation}
+    \begin{equation}
+      \label{eq:VGC}
+      \tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0.
+    \end{equation}
+    Call the subset $H\sqcup V$ \emph{compatible} if every path $hv$ with $h\in H$ and $v\in V$ is compatible.
+    Write $\cC_D$ for the collection of all compatible subsets of $D$.
+    Given a subset $H\subset D_1$, write $\cC_D(H)$ for the collection of all $V\subset D_2$ for which $H\sqcup V\in\cC_D$.
+    Define $\cC_D(V)$ for $V\subset D_2$ similarly.
+  \end{definition}
+  \begin{remark}
+    In the construction of the greedy basis, it is necessary to consider $D$ as a closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
+    When we wish to emphasize that this condition should be imposed, we denote the Dyck path $D$ instead by $D_\WA$.
+    Following \cite[Remark 2.21]{rupel}, for $D^{m,\varepsilon}$ and $\vv{\bar{D}}^{m,\varepsilon}$ the wrap around condition does not restrict compatibility and can thus safely be omitted.
+  \end{remark}
+
+  The crucial result from \cite{lee-li-zelevinsky} can be stated as follows: if a Dyck path $D$ is vertically-adapted to $c$ (resp.
+horizontally adapted to $b$), then there is a bijection between certain compatible subsets of $D$ and certain compatible subsets of $\mu_{1,c}(D)$ (resp.
+of $\mu_{2,b}(D)$).
+  The main step in the proof that needs to be adapted to the general situation is the following.
+  For $e \le h\in D$ with $h=h_d\in D_1$, write $eh^{\!\uparrow}$ for the subpath $eh$ together with all vertical edges of depth $d$ immediately following $h$.
+  For $v \le e\in D$ with $v=v_\ell\in D_2$, write ${}^\leftarrow\!\!\! ve$ for the subpath $ve$ together with all horizontal edges of height $\ell$ immediately preceding $v$.
+  \begin{lemma}\mbox{}
+    \label{le:shadow statistic recursion}
+    \begin{enumerate}
+      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
+        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
+        Then for any $h_i \le h_j \in D_1$, we have $f_H(h_i h_j^{\!\uparrow})=-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_i v'_j)$.
+      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
+        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
+        Then for any $v_i \le v_j \in D_2$, we have $f_V({}^\leftarrow\!\!\! v_i v_j)=-\vv{f}_{H''}(h''_i {h''_j}^{\!\uparrow})$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    Claim (2) is immediate from claim (1). 
+    By definition, we have 
+    \begin{align*}
+      -\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)&=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap V'|\\
+      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \big(D'_2\setminus \mu_{1,c}(H)\big)\big|\\
+      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_2|+c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \mu_{1,c}(H)\big|.
+    \end{align*}
+    But, by construction of $\mu_{1,c}(D)$ and since $\mu_{2,c}(D')=D$, we have
+    \[\big|{}^\leftarrow\!\!\!
+v'_i v'_j \cap \mu_{1,c}(H)\big|=|h_i h_j^{\!\uparrow} \cap H| \qquad \text{and} \qquad c|{}^\leftarrow\!\!\!
+v'_i v'_j \cap D'_2|-|{}^\leftarrow\!\!\!
+v'_i v'_j \cap D'_1|=|h_i h_j^{\!\uparrow} \cap D_2|\]
+    giving
+    \[-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)=-|h_i h_j^{\!\uparrow} \cap D_2|+c|h_i h_j^{\!\uparrow} \cap H|=f_H(h_i h_j^{\!\uparrow})\]
+    as desired.
+  \end{proof}
+
+  The desired bijection of compatible subsets is constructed in terms of certain subpaths determined from each compatible subset.
+  \begin{definition}
+    \label{def:shadows}
+    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$, define the \emph{shadow paths} as follows:
+    \begin{itemize}
+      \item For $h\in D_1$, write $D(h;H)$ for the shortest subpath $he \subset D$ with $f_H(he)=0$ or, if no such subpath exists, set $D(h;H)=hv_{a_2}$.
+      \item For $v\in D_2$, write $D(v;V)$ for the shortest subpath $ev \subset D$ with $f_V(ev)=0$ or, if no such subpath exists, set $D(v;V)=h_1 v$.
+    \end{itemize}
+    Write 
+    \[D(H):=\bigcup_{h\in H} D(h;H) \qquad \text{and} \qquad D(V):=\bigcup_{v\in V} D(v;V).\]
+    Define the \emph{shadow} of $H$ (resp.
+the \emph{shadow} of $V$) as the set $\sh_D(H):=D(H)\cap D_2$ (resp.~$\sh_D(V):=D(V)\cap D_1$) and the \emph{local shadow} of $h\in H$ (resp.
+of $v\in V$) as the set $\sh_D(h;H)=D(h;H)\cap D_2$ (resp.
+$\sh_D(v;V)=D(v;V)\cap D_1$).
+  \end{definition}
+
+  The proofs of the following results are identical to the proof of the analogous results from \cite{lee-li-zelevinsky,rupel} for maximal Dyck paths.
+  \begin{lemma}
+    \label{le:shadow statistics}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $h\in H$, take $he$ to be the path $D(h;H)$.
+        The following hold:
+        \begin{enumerate}
+          \item for any proper subpath $he'\subsetneq he$, we have $f_H(he')>0$;
+          \item if $f_H(he)=0$, then for any proper subpath $e'e\subsetneq he$, we have $f_H(e'e)<0$;
+          \item $e\in V$.
+        \end{enumerate}
+      \item For $v\in V$, take $ev$ to be the path $D(v;V)$.
+        The following hold:
+        \begin{enumerate}
+          \item for any proper subpath $e'v\subsetneq ev$, we have $f_V(e'v)>0$;
+          \item if $f_V(ev)=0$, then for any proper subpath $ee'\subsetneq ev$, we have $f_V(ee')<0$;
+          \item $e\in H$.
+        \end{enumerate}
+    \end{enumerate}
+  \end{lemma}
+  \begin{remark}
+    Observe that the subset $V$ has no influence on the claim of (1) and the subset $H$ has no influence on the claim of (2).
+  \end{remark}
+
+  \begin{definition}
+    Given two Dyck paths $D,D'$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $D'\succ D$ if no lattice point of $D'$ lies below a lattice point of $D$.
+  \end{definition}
+  \begin{remark}
+    Equivalently, $D'\succ D$ if no lattice point of $D'$ lies to the right of a lattice point of $D$.
+  \end{remark}
+
+  \begin{proposition}
+    Let $D,D'$ be two Dyck paths in the lattice rectangle $[0,a_1]\times[0,a_2]$ with $D'\succ D$.
+    Identify $D_1$ with $D'_1$ and $D_2$ with $D'_2$ along the natural left-to-right ordering.
+    For subsets $H\subset D_1$ and $V\subset D_2$, write $H'\subset D'_1$ and $V'\subset D'_2$ for the corresponding subsets under the identification above.
+    If $(H,V) \in \cC_D$, then $(H',V') \in \cC_{D'}$.
+  \end{proposition}
+  \begin{proof}
+    It suffices, by induction, to show that the result holds if $D'$ is an immediate successor of $D$, i.e.
+when a single pair of a horizontal followed by a vertical is replaced by a vertical followed by a horizontal.
+    Assume $D'$ is obtained from $D$ in this way, say with horizontal edge $h_i$ and vertical edge $v_j$ satisfying $v_j=h_i+1$ in $D$ replaced by the vertical edge $v'_j$ and the horizontal edge $h'_i$ satisfying $h'_i=v'_j+1$ in $D'$.
+
+    Consider $(H,V) \in \cC_D$.
+    For $h\in H$ and $v\in V$, write $h'\in H'$ and $v'\in V'$ for the corresponding edges.
+    We claim that the condition \eqref{eq:HGC} (resp. \eqref{eq:VGC}) being satisfied for the path $hv$ in $D$ implies the same condition is satisfied for the path $h'v'$ in $D'$.
+
+    Suppose \eqref{eq:HGC} is satisfied for the path $hv$ and write $D(h;H)=he$ for $e\in V$ with $e<v$.
+    If $h_i,v_j\notin D(h;H)$, then under the identification with $D'$ we have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
+    Alternatively, since $e\in V$, we must have both $h_i,v_j\in D(h;H)$.
+    If $h_i\notin H$, then again we have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
+    Thus, we assume $h_i\in H$.
+
+    We begin by assuming $h_i\ne h$.
+    This gives two possibilities for $D(h';H')$ depending on $D(h'_i;H')$.
+    First, observe that $D(h_i;H)$ is a proper subpath of $h_ie$, for otherwise $f_H(h_ie)=0$ and, by the additivity of $f_H$, $he$ would not be the shortest subpath with $f_H(he)=0$.
+    Thus, if $D(h_i;H)$ is followed by at least two vertical edges inside $D(h;H)$, we again have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
+    Otherwise, $D(h';H')$ is an initial subpath of $D(h;H)$ under the identification of $D'$ with $D$ and again \eqref{eq:HGC} is satisfied for the path $h'v'$.
+
+    Now if $h_i=h$...
+  \end{proof}
+
+  \begin{corollary}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $h\in H$ and a vertical edge $v\in D(h;H)$, the condition \eqref{eq:HGC} is not satisfied for the path $hv$ but for any $V\in\cC_D(H)$ the condition \eqref{eq:VGC} is satisfied for the path $hv$.
+        In particular, $D(v;V)$ is a proper subpath of $hv$ for any $V\in\cC_D(H)$.
+      \item For $v\in V$ and a horizontal edge $h\in D(v;V)$, the condition \eqref{eq:VGC} is not satisfied for the pair $hv$ but for any $H\in\cC_D(V)$ the condition \eqref{eq:HGC} is satisfied for the path $hv$.
+        In particular, $D(h;H)$ is a proper subpath of $hv$ for any $H\in\cC_D(V)$.
+    \end{enumerate}
+  \end{corollary}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item For $H\subset D_1$ and $h,h'\in H$, the local shadows $\sh_D(h;H)$ and $\sh_D(h';H)$ are either disjoint or one is contained in the other.
+      \item For $V\subset D_2$ and $v,v'\in V$, the local shadows $\sh_D(v;V)$ and $\sh_D(v';V)$ are either disjoint or one is contained in the other.
+    \end{enumerate}
+  \end{lemma}
+
+  \begin{definition}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $H$, by removing for each $d\in[1,a_1]$ the first (up to) $c$ vertical edges of depth $d$ immediately following $h_d$.
+      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $V$, by removing for each $\ell\in[0,a_2-1]$ the first (up to) $b$ horizontal edges of height $\ell$ immediately preceding $v_{\ell+1}$.
+    \end{enumerate}
+  \end{definition}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item For $H\subset D_1$, $V\in\cC_D(H)$ if and only if $V$ is disjoint from $\sh_D(H)\setminus\rsh_D(H)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in H$ and $v\in\rsh_D(H)$.
+      \item For $V\subset D_2$, $H\in\cC_D(V)$ if and only if $H$ is disjoint from $\sh_D(V)\setminus\rsh_D(V)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in\rsh_D(V)$ and $v\in V$.
+    \end{enumerate}
+  \end{lemma}
+
+  \begin{definition}
+    For $H\subset D_1$, write $\cC_D^{rsh}(H)$ for the subset of $V\in\cC_D(H)$ with $V\subset\rsh_D(H)$.
+    For $V\subset D_2$, write $\cC_D^{rsh}(V)$ for the subset of $H\in\cC_D(V)$ with $H\subset\rsh_D(V)$.
+  \end{definition}
+
+  \begin{definition}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $1 \le j < d \le a_1$ with $h_j\in H$, denote by $\rsh_D(H)_{j;d}$ the set of all $v\in\rsh_D(H)$ of depth $d$ such that $v\in\sh(h_j;H)$ and $h_j$ is the first horizontal edge before $v$ with this property.
+        Define the \emph{local remote shadow} of the edge $h_j$ by $\rsh_D(h_j;H):=\bigsqcup\limits_{d\in[j+1,a_1]} \rsh_D(H)_{j;d}$.
+      \item For $1 \le \ell <  k \le a_2$ with $v_k\in V$, denote by $\rsh_D(V)_{k;\ell}$ the set of all $h\in\rsh_D(V)$ of height $\ell$ such that $h\in\sh(v_k;V)$ and $v_k$ is the first vertical edge after $h$ with this property.
+        Define the \emph{local remote shadow} of the edge $v_k$ by $\rsh_D(v_k;V):=\bigsqcup\limits_{\ell\in[1,k-1]} \rsh_D(V)_{k;\ell}$.
+    \end{enumerate}
+  \end{definition}
+
+  As shown in \cite{lee-li-zelevinsky} for maximal Dyck paths, the remote shadow can be characterized as follows.
+  \begin{lemma}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item For $1 \le d < j \le a_1$, we have $\rsh_D(H)_{j;d} \ne \varnothing$ if and only if $f_H(h'h_d^{\!\uparrow}) < 0 < f_H(h_jh^{\!\uparrow})$ for every pair of consecutive horizontal edges $h<h'$ in the path $h_j h_d^{\!\uparrow}$.
+      \item For $1 \le \ell < k \le a_2$, we have $\rsh_D(V)_{k;\ell} \ne \varnothing$ if and only if $f_V({}^\leftarrow\!\!\!
+v_\ell v) < 0 < f_V({}^\leftarrow\!\!\!
+v' v_k)$ for every pair of consecutive vertical edges $v<v'$ in the path ${}^\leftarrow\!\!\!
+v_\ell v_k$.
+    \end{enumerate}
+  \end{lemma}
+
+  \begin{lemma}
+    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
+    \begin{enumerate}
+      \item Let $1 \le d < j \le a_1$ and suppose $\rsh_D(H)_{j;d} \ne \varnothing$, then
+        \[|\rsh_D(H)_{j;d}| = \min\limits_{h_j \le h < h' \le h_d} \min\big( -f_H(h'h_d^{\!\uparrow}) , f_H(h_jh^{\!\uparrow}) \big).\]
+      \item Let $1 \le \ell < k \le a_2$ and suppose $\rsh_D(V)_{k;\ell} \ne \varnothing$, then
+        \[|\rsh_D(V)_{k;\ell}| = \min\limits_{v_\ell \le v < v' \le v_k} \min\big( -f_V({}^\leftarrow\!\!\! v_\ell v) , f_V({}^\leftarrow\!\!\! v' v_k) \big).\]
+    \end{enumerate}
+  \end{lemma}
+
+  Then the following result immediately follows from Lemma~\ref{le:shadow statistic recursion}.
+  \begin{corollary}\mbox{}
+    \label{cor:remote shadows}
+    \begin{enumerate}
+      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
+        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
+        Then, for $1 \le d < j \le a_1$, we have $|\rsh_D(H)_{j;d}|=|\rsh_{D'}(V')_{d;j}|$.
+      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
+        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
+        Then, for $1 \le \ell < k \le a_2$, we have $|\rsh_D(V)_{k;\ell}|=|\rsh_{D''}(H'')_{\ell;k}$.
+    \end{enumerate}
+  \end{corollary}
+
+  In the results below, we keep the notation and assumptions from Corollary~\ref{cor:remote shadows}.
+  It follows that, for $H\subset D_1$ and $1 \le d < j \le a_1$, we may define an order-reversing bijection $\theta^H_{j;d} : \rsh_D(H)_{j;d} \to \rsh_{D'}(V')_{d;j}$.
+  Similarly, for $V\subset D_2$ and $1 \le \ell < k \le a_2$, we may define an order-reversing bijection $\theta^V_{k;\ell} : \rsh_D(V)_{k;\ell} \to \rsh_{D''}(H'')_{\ell;k}$.
+  \begin{definition}\mbox{}
+    \begin{enumerate}
+      \item For $H\subset D_1$ and $V \subset \rsh_D(H)$, define $\Omega_H(V) \subset \rsh_{D'}(V')$ by
+        \[\Omega_H(V)=\{\theta^H_{j;d}(v) : v \in \rsh_D(H)_{j;d}, 1 \le d < j \le a_1\}.\]
+      \item For $V\subset D_2$ and $H \subset \rsh_D(V)$, define $\Omega_V(H) \subset \rsh_{D''}(H'')$ by
+        \[\Omega_V(H)=\{\theta^V_{k;\ell}(h) : h \in \rsh_D(V)_{k;\ell}, 1 \le \ell < k \le a_2\}.\]
+    \end{enumerate}
+  \end{definition}
+
+  \begin{lemma}\mbox{}
+    \begin{enumerate}
+      \item Consider $H\subset D_1$ and $V \subset \rsh_D(H)$.
+        Suppose $h'=\theta^H_{j;d}(v)$ for $v\in V$.
+        Then $f_{\Omega_H(V)}(h'v'_d)=f_V(h_j v)$.
+      \item Consider $V\subset D_2$ and $H \subset \rsh_D(V)$.
+        Suppose $v''=\theta^V_{k;\ell}(h)$ for $h\in H$.
+        Then $f_{\Omega_V(H)}(h''_\ell v'')=f_V(h v_k)$.
+    \end{enumerate}
+  \end{lemma}
+
+  The following equivalence of compatibilities is the main result we need.
+  \begin{corollary}\mbox{}
+    \begin{enumerate}
+      \item For $H \subset D_1$ and $V \subset \rsh_D(H)$, we have $V\in\cC_D(H)$ if and only if $\Omega_H(V)\in\cC_{D'}(V')$.
+      \item For $V \subset D_2$ and $H \subset \rsh_D(V)$, we have $H\in\cC_D(V)$ if and only if $\Omega_V(H)\in\cC_{D''}(H'')$.
+    \end{enumerate}
+  \end{corollary}
+
+  We associate to $D$ the element $x_D\in\ZZ_{\ge0}[x_1^{\pm1},x_2^{\pm1}]$ defined as follows
+  \[x_D:=x_1^{-a_1} x_2^{-a_2} \sum_{H\sqcup V\in\cC_D} x_1^{b|V|} x_2^{c|H|}.\]
+
+  \begin{theorem}[\cite{lee-li-zelevinsky}]
+    For $(a_1,a_2)=(u_{m,+},u_{m-1,-})$ or $(u_{m-1,+},u_{m,-})$ for $m\ge1$, the element $x_{D^{max}[a_1,a_2]}$ is a non-initial cluster variable.
+    Otherwise, the element $x_{D^{max}_\WA[a_1,a_2]}$ is an element of the greedy basis
+  \end{theorem}
+
+  \begin{lemma}
+    Suppose there are two factorizations
+    \[x_D=x_1^{-a_1} x_2^{-a_2} \sum_{t=0}^{a_2}\sum_{k=0}^{a_1} \nu_{k,t} x_1^{bt}(1+x_2^c)^{a_1-k}=x_1^{-a_1} x_2^{-a_2} \sum_{s=0}^{a_1}\sum_{\ell=0}^{a_2} \theta_{s,\ell} x_2^{cs}(1+x_1^b)^{a_2-\ell},\]
+    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\sh_D(H)|=\ell$.
+    Then 
+    \[\sum_{k=0}^{a_1-s} {a_1-k\choose s} \nu_{k,t}=\sum_{\ell=0}^{a_2-t} {a_2-\ell\choose t} \theta_{s,\ell}\]
+    for all possible $s$ and $t$.
+  \end{lemma}
+  \begin{question}
+    How do such expressions behave under mutations?
+  \end{question}
+
+  \begin{lemma}
+    Choose $a_1,a_2\in\ZZ_{\ge0}$.
+    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_{D^{st}}$ coincides with the corresponding standard monomial basis element.
+  \end{lemma}
+
+  \begin{definition}
+    Suppose $D^{dom}[a_1,a_2]$ decomposes as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$.
+    Call a pair of subsets $H \sqcup V$ \emph{piecewise compatible} if the intersections with $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ are compatible on the subpaths.
+  \end{definition}
+
+  \begin{theorem}
+    Suppose $H \sqcup V$ is a piecewise compatible subset of $D^{dom}[a_1,a_2]$.
+    \begin{itemize}
+      \item If the last vertical edge of $\overrightarrow{D}^s$ is contained in $V$, then $H \sqcup V$ is compatible.
+      \item If the first horizontal edge of $\overleftarrow{D}^t$ is contained in $H$, then $H \sqcup V$ is compatible.
+    \end{itemize}
+  \end{theorem}
+
+\end{document}

### 2022-04-04 dominance_regions.tex
Random intro edits

@@
 
-  Over time several bases have been constructed in a variety of generalities \cite{foo,bar,baz}. 
+  Over time several bases for cluster algebras have been constructed in a variety of generalities \cite{foo,bar,baz}. 
   All of them share a property of being ``pointed''.
-  Being pointed turned out to be a desireable feature for a basis to have and a natural question is to find all bases enjoying this property.
+  Being pointed turned out to be a desirable feature for a basis to have and a natural question is to find all bases enjoying this property.
   Recently Qin introduced the notion of \emph{dominance} and showed that it completely encapsulates the deformability of pointed bases whenever the cluster algebra has full rank \cite{Qin}. 
-  As no explicit calculation is carried out in his work, we aim here at describing explicitly the space of deformability of pointed bases in rank 2, i.e.
+  As no explicit calculation is carried out in his work, we aim here at describing explicitly the space of deformability for pointed bases in rank 2, i.e.
 when clusters contain a pair of mutable cluster variables.
@@
   By the Laurent Phenomenon \cite{fomin-zelevinsky}, each $x_m$ is actually an element of $\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for any $k\in\ZZ$.
-  Moreover, these Laurent polynomials are known to have positive coefficients \cite{lee-schiffler,GHKK}.
+  Moreover, these Laurent polynomials are known to have positive coefficients \cite{LLZ,lee-schiffler,GHKK}.
 
   Our goal in this note is to explicitly compute the possible bases which are \emph{pointed} with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
-  That is, a basis element, with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$ when expanded in terms of $\{x_1,x_2\}$, can be written in the form
+  That is, a basis element with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$ when expanded in terms of $\{x_1,x_2\}$ can be written in the form
   \[
@@
   \]
-  with $c_{0,0}=1$ and an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
+  with $c^\lambda_{0,0}=1$ and an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
   %The collection of all $\bfg$-vectors $\lambda\in\ZZ^2$ parametrize the elements of any pointed basis.
@@
   \end{theorem}
-
-  Our calculations reveal the maximal support possible for a pointed basis which remains pointed under all possible mutations.
-  In particular, any candidate basis can be ruled out using these results based upon their support alone.
 
@@
 \end{figure}
+
+\begin{remark}
+  This result reveals the maximal support possible for a pointed basis which remains pointed under all possible mutations.
+  In particular, any candidate basis could be ruled out using these results based upon their support alone.
+\end{remark}
 

### 2022-04-04 dominance_regions.tex
Pictures

@@
       \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
-      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
-      \draw [color=lightgray, thick] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
+      \draw [color=lightgray, thick, dashed] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
+      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
     }
@@
       \fill (\l *\b + \l, - \l)  circle (6pt);
-      \draw [very thick] (\l * \b + \l, -\l) -- (\l,-\l);
+      \draw [very thick, join=round] (\l * \b + \l, -\l) -- (\l,-\l);
     \end{scope}
@@
       \fill (-\l, \l)  circle (6pt);
-      \draw [very thick] (-\l, \l) -- (-\l,\l + \l*\c);
+      \draw [very thick, join=round] (-\l, \l) -- (-\l,\l + \l*\c);
     \end{scope}
@@
       \fill (-\l, -\l)  circle (6pt);
-      \draw [very thick] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
+      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
     \end{scope}
@@
       \fill (\b * \l - \l / 2 / \c , -\l)  circle (6pt);
-      \draw [very thick] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
+      \draw [very thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
     \end{scope}
@@
       \boundingrays;
-      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c; \y = -\l - 3*\l/10;}
+      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c + 0.15; \y = -\l - 3*\l/10;}
       \fill (\x,\y)  circle (6pt);
-      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
+      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
+      \draw [very thick, dashed, join=round] (0,0) --  (\x , \y);
     \end{scope}
@@
       \fill (\l / 2 / \c , -\l)  circle (6pt);
-      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
+      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
+      \draw [very thick, dashed, join=round] (0,0) --  (\x , \y);
     \end{scope}
@@
       \fill (\x , \y)  circle (6pt);
-      \draw [very thick] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  cycle;
+      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
+      \draw [very thick, dashed, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
     \end{scope}

### 2022-04-04 dominance_regions.tex
Pictures
Intro edit

@@
   In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
-  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\lambda+(b\ZZ\oplus c\ZZ)$-lattice points in its \emph{dominance polygon} $\cP(\lambda)$.
-  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$ inside its \emph{dominance polygon} for integers $a_1,a_2$.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$, $a_1,a_2\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
   %In this case, we compute the possible transitions between any two pointed bases.
@@
       \boundingrays;
-      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c; \y = -\l; }
-      \fill (\b * \l - \l / 2 / \c , -\l)  circle (6pt);
+      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c -0.1; \y = -\l; }
+      \fill (\x,\y) circle (6pt);
       \draw [very thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
@@
       \fill (\x,\y) circle (6pt);
+      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
       \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
@@
       \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
-      \fill (\l / 2 / \c , -\l)  circle (6pt);
+      \fill (\x,\y) circle (6pt);
+      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
       \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
@@
       \fill (\x , \y)  circle (6pt);
+      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
       \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);

### 2022-04-04 dominance_regions.tex
Pictures

@@
     \label{th:dominance inequalities}
-    The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
+    The dominance polygon $\cP(\lambda)$ pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
     {
@@
 
-  A number of bases for rank two cluster algebras with various defining properties have been defined.
+  A number of bases for rank two cluster algebras with various defining properties have been constructed.
   A natural starting basis is the so-called \emph{greedy basis} in which all $c^\lambda_{a_1,a_2}$ are non-negative and these coefficients are chosen to be minimal.
@@
       \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
-      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
-      \draw [very thick, dashed, join=round] (0,0) --  (\x , \y);
+      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
+      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
     \end{scope}
@@
       \draw [very thick, dashed, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
+      \draw [very thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
     \end{scope}
@@
   \end{theorem}
-  \begin{figure}[h!]
-    \centering
-    \begin{tikzpicture}[scale=.7]
-      %(1)
-      \begin{scope}[shift={(-2.75, 5.5)}]
-        \usetikzlibrary{patterns}
-        \draw[-] (-0.5,0.25) -- (3,0.25);
-        \draw[-] (0,-0.25) -- (0,3);
-        \fill[white] (0,0.25) circle (2pt);
-        \draw (0,0.25) circle (2pt);
-        \draw (0,0.25) node[anchor=south west] {\tiny $O$};
-        \fill (1.5,1.75) circle (2pt);
-        \draw (1.5,1.75) node[anchor=east] {\tiny $B$};
-        \draw (1.07,-.6) node[anchor=north] {\footnotesize (1) $a_1,a_2\le0$};
-      \end{scope}
-      %(2)
-      \begin{scope}[shift={(2.75, 5.5)}]
-        \usetikzlibrary{patterns}
-        \draw[-] (-0.5,1.5) -- (3,1.5);
-        \draw[-] (0,-0.25) -- (0,3);
-        \fill[white] (0,1.5) circle (2pt);
-        \draw (0,1.5) circle (2pt);
-        \draw (0,1.5) node[anchor=south west] {\tiny $O$};
-        \fill (2.25,0.5) circle (2pt);
-        \draw (2.25,0.5) node[anchor=west] {\tiny$A$};
-        \fill (0.75,0.5) circle (2pt);
-        \draw (0.75,0.5) node[anchor=east] {\tiny$B$};
-        \draw [thick] (0.75,0.5) -- (2.25,0.5);
-        \draw (1.27,-.6) node[anchor=north] {\footnotesize (2) $a_1\le 0<a_2$};
-      \end{scope}
-      %(3)
-      \begin{scope}[shift={(8.25,5.5)}]
-        \usetikzlibrary{patterns}
-        \draw [thick] (0.25,1) -- (0.25,2.5);
-        \draw[-] (-0.5,0.25) -- (3,0.25);
-        \draw[-] (1,-0.25) -- (1,3);
-        \fill[white] (1,0.25) circle (2pt);
-        \draw (1,0.25) circle (2pt);
-        \draw (1,0.25) node[anchor=south west] {\tiny $O$};
-        \fill (0.25,1) circle (2pt);
-        \draw (0.25,1) node[anchor=east] {\tiny$B$};
-        \fill (0.25,2.5) circle (2pt);
-        \draw (0.25,2.5) node[anchor=east] {\tiny$C$};
-        \draw (1.27,-.6) node[anchor=north] {\footnotesize (3) $a_2\le0<a_1$};
-      \end{scope}
-      %(4)
-      \begin{scope}[shift={(0,0)}]
-        \usetikzlibrary{patterns}
-        \fill[black!10] (0,3)--(1.5,1.5)--(1.5,0)--(0,0)--(0,3);
-        \draw[thick] (0,3)--(1.5,1.5)--(1.5,0)--(0,0)--(0,3);
-        \draw[dashed,thick](0,3)--(2.15,1.25) (2.15,1.15)--(1.5,0);
-        \draw[-] (-0.5,1.2) -- (3.5,1.2);
-        \draw[-] (2.2,-0.25) -- (2.2,3.5);
-        \fill[white] (2.2,1.2) circle (2pt);
-        \draw (2.2,1.2) circle (2pt);
-        \draw (2.2,1.2) node[anchor=north west] {\tiny$O$};
-        \fill (1.5,0) circle (2pt);
-        \draw (1.5,0) node[anchor=west] {\tiny$A$};
-        \fill (0,0) circle (2pt);
-        \draw (0,0) node[anchor=east] {\tiny$B$};
-        \fill (0,3) circle (2pt);
-        \draw (0,3) node[anchor=east] {\tiny$C$};
-        \fill (1.5,1.5) circle (2pt);
-        \draw (1.5,1.5) node[anchor=east] {\tiny$D_1$};
-        \draw (1.37,-0.5) node[anchor=north] {\footnotesize (4) $0<ba_2\leq a_1$};
-      \end{scope}
-      %(5)
-      \begin{scope}[shift={(5.5,0)}]
-        \usetikzlibrary{patterns}
-        \fill[black!10] (3,0)--(1.3,1)--(0,1)--(0,0)--(3,0);
-        \draw[thick] (3,0)--(1.3,1)--(0,1)--(0,0)--(3,0);
-        \draw[dashed,thick](3,0)--(0.75,1.75)--(0,1);
-        \draw[-] (-0.5,1.75) -- (3.5,1.75);
-        \draw[-] (0.75,-0.25) -- (0.75,3.5);
-        \fill[white] (0.75,1.75) circle (2pt);
-        \draw (0.75,1.75) circle (2pt);
-        \draw (0.75,1.75) node[anchor=south west] {\tiny$O$};
-        \fill (3,0) circle (2pt);
-        \draw (3,0) node[anchor=west] {\tiny$A$};
-        \fill (0,0) circle (2pt);
-        \draw (0,0) node[anchor=east] {\tiny$B$};
-        \fill (0,1) circle (2pt);
-        \draw (0,1) node[anchor=east] {\tiny$C$};
-        \fill (1.3,1) circle (2pt);
-        \draw (1.3,1) node[anchor=north] {\tiny$D_2$};
-        \draw (1.37,-.5) node[anchor=north] {\footnotesize (5) $0<ca_1\leq a_2$};
-      \end{scope}
-      %(6)
-      \begin{scope}[shift={(0,-5.5)}]
-        \usetikzlibrary{patterns}
-        \fill[black!10]  (0,3)--(1.5,2.3)--(2,0)--(0,0)--(0,3);
-        \draw[thick] (0,3)--(0,0)--(2,0); 
-        \draw[dashed,thick] (0,3)--(1.5,2.3)--(2,0);
-        \draw[-] (-0.5,2.3) -- (3.5,2.3);
-        \draw[-] (1.5,-0.25) -- (1.5,3.5);
-        \fill[white] (1.5,2.3) circle (2pt);
-        \draw (1.5,2.3) circle (2pt);
-        \draw (1.5,2.3) node[anchor=south west] {\tiny$O$};
-        \fill (2,0) circle (2pt);
-        \draw (2,0) node[anchor=west] {\tiny$A$};
-        \fill (0,0) circle (2pt);
-        \draw (0,0) node[anchor=east] {\tiny$B$};
-        \fill (0,3) circle (2pt);
-        \draw (0,3) node[anchor=east] {\tiny$C$};
-        \draw (1.42,-.5) node[anchor=north] {\footnotesize (6) $0<a_1<ba_2$,};
-        \draw (1.46,-1) node[anchor=north] {\footnotesize \hspace{10pt} $0<a_2<ca_1$,};
-        \draw (1.17,-1.5) node[anchor=north] {\footnotesize \hspace{10pt} \tiny{$(a_1,a_2):$ non-imaginary root}};
-      \end{scope}
-      %(6')
-      \begin{scope}[shift={(5.5,-5.5)}]
-        \usetikzlibrary{patterns}
-        \fill[black!10]  (0,3)--(1,0.5)--(2.25,0)--(0,0)--(0,3);
-        \draw[thick] (0,3)--(0,0)--(2.25,0);
-        \draw[dashed,thick] (0,3)--(1,0.5)--(2.25,0);
-        \draw[-] (-0.5,0.5) -- (3.5,0.5);
-        \draw[-] (1,-0.25) -- (1,3.5);
-        \fill[white] (1,0.5) circle (2pt);
-        \draw (1,0.5) circle (2pt);
-        \draw (1,0.5) node[anchor=south west] {\tiny$O$};
-        \fill (2.25,0) circle (2pt);
-        \draw (2.25,0) node[anchor=west] {\tiny$A$};
-        \fill (0,0) circle (2pt);
-        \draw (0,0) node[anchor=east] {\tiny$B$};
-        \fill (0,3) circle (2pt);
-        \draw (0,3) node[anchor=east] {\tiny$C$};
-        \draw (1.47,-.5) node[anchor=north] {\footnotesize (6) $0<a_1<ba_2$,};
-        \draw (1.51,-1) node[anchor=north] {\footnotesize \hspace{10pt} $0<a_2<ca_1$,};
-        \draw (1.27,-1.5) node[anchor=north] {\footnotesize \hspace{10pt} \tiny{$(a_1,a_2):$ imaginary root}};
-      \end{scope}
-    \end{tikzpicture}
-    \caption{Consider the points $O=(0,0)$, $A=(-a_1+ba_2,-a_2)$, $B=(-a_1,-a_2)$, $C=(-a_1,-a_2+ca_1)$, $D_1=(-a_1+ba_{2},ca_{1}-(bc+1)a_{2})$, and $D_2=(ba_{2}-(bc+1)a_{1},-a_2+ca_{1})$.
-Then the support region of $x[a_1,a_2]$ can be visualized as above.}
-    \label{fig:greedy polytopes}
-  \end{figure}
 

### 2022-04-04 dominance_regions.tex
Pictures

@@
       \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
-      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
-      \draw [very thick, dashed, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
-      \draw [very thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dotted] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
+      \draw [very thick, dotted, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
+      \draw [very thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
     \end{scope}

### 2022-04-05 dominance_regions.tex
figures
Some more reorganization and edits

@@
       \boundingrays;
-      \tikzmath{ \l = 1; }
-      \fill (\l,\l) circle (6pt);
+      \tikzmath{ \r=1; \s=1; \x = \r; \y=\s; }
+      \fill (\x,\y) circle (6pt);
     \end{scope}
@@
       \boundingrays;
-      \tikzmath{ \l = 1; }
-      \fill (\l *\b + \l, - \l) circle (6pt);
-      \draw [very thick, join=round] (\l * \b + \l, -\l) -- (\l,-\l);
+    \tikzmath{ \r=1; \s=1; \x = \r + \b*\s; \y=-\s; }
+      \fill (\x, \y) circle (6pt);
+      \draw [very thick, join=round] (\x, \y) -- ({\x+\b * \y},\y);
     \end{scope}
@@
       \boundingrays;
-      \tikzmath{ \l = 1; }
-      \fill (-\l, \l) circle (6pt);
-      \draw [very thick, join=round] (-\l, \l) -- (-\l,\l + \l*\c);
+      \tikzmath{ \r=1; \s=1; \x=-\r; \y=\s; }
+      \fill (\x, \y) circle (6pt);
+      \draw [very thick, join=round] (\x, \y) -- (\x,{\y - \c * \x});
     \end{scope}
@@
       \boundingrays;
-      \tikzmath{ \l = 1; }
-      \fill (-\l, -\l) circle (6pt);
-      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
+      \tikzmath{ \r=1; \s=1; \x=-\r; \y=-\s; }
+      \fill (\x, \y) circle (6pt);
+%      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
+      \draw [very thick, join=round] (\x, \y) -- ({\x + \b * \y}, \y) -- ({\x + \b * \y}, {\y -\c*(\x + \b * \y)}) -- (\x, {\y - \c*\x}) -- cycle;
     \end{scope}
@@
       \boundingrays;
-      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c -0.1; \y = -\l; }
+      \tikzmath{ \r=1; \s=1; \x={\r*\b+\s*(\b*\c-1) }; \y = {-\r -\c*\s};  }
       \fill (\x,\y) circle (6pt);
@@
       \boundingrays;
-      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c + 0.15; \y = -\l - 3*\l/10;}
+      \tikzmath{ \r=1/2; \s=1; \x={2*\r*\b+\s*(\b*\c-1) }; \y = {-\r*\bcms -\c*\s};  }
       \fill (\x,\y) circle (6pt);
@@
       \boundingrays;
-      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
+      \tikzmath{ \r=0.3; \s=1; \x={2*\r*\b }; \y = {-\r*\bcps -\s};  }
       \fill (\x,\y) circle (6pt);
@@
       \boundingrays;
-      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
+      \tikzmath{ \r=0.5; \s=0.7; \x={2*(\r+\s)*\b }; \y = {-\r*\bcps -\s*\bcms};  }
       \fill (\x , \y)  circle (6pt);
@@
 \end{remark}
+
+The paper is organized as follows.
+In Section~\ref{sec:chebyshev}, we collect useful results related to two-parameter Chebyshev polynomials which support our main calculations.
+
+\section{Chebyshev Polynomials}
+  \label{sec:chebyshev}
+  Define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
+  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
+
+  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
+  This leads to the following more general recursive structure.
+  \begin{lemma}
+    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
+    \begin{equation}
+      \label{eq:long Chebyshev recursion}
+      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
+    \end{equation}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
+    Using the claim for $j>0$ and then the defining recursion twice, we get
+    \begin{align*}
+      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
+    \end{align*}
+    which is the claimed recursion for $\ell+1$.
+    These calculations can be reversed to show the result for $\ell<0$.
+  \end{proof}
+
+  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
+  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
+  By the equalities 
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
+  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+  \begin{remark}
+    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
+    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
+  \end{remark}
+
+  \begin{lemma}
+    We have
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+  \end{lemma}
+  \begin{proof}
+    For any $i\ge 1$, we have
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
+    It follows that
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    which is equivalent to the desired expression.
+    Similarly, 
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
+    so that
+    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    which is again equivalent to the desired expression.
+  \end{proof}
+
+\section{Rank Two Lattice Mutations}
+  We begin by studying transformations of $\RR^2$ which determine the transformation of $\bfg$-vectors under mutations.
+
+  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1},\phi_{\pm 2}:\RR^2\to\RR^2$ as follows:
+  \begin{equation}
+    \phi_1(\lambda)
+    =
+    \begin{cases} 
+      (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1 \ge 0$;}\\
+      (-\lambda_1,\lambda_2) & \text{if $\lambda_1 < 0$;}
+    \end{cases}
+    \qquad
+    \phi_{-1}(\lambda)
+    =
+    \begin{cases} 
+      (\lambda_1,-\lambda_2) & \text{if $\lambda_2 \ge 0$;}\\
+      (\lambda_1+b\lambda_2,-\lambda_2) & \text{if $\lambda_2 < 0$;}
+    \end{cases}
+  \end{equation}
+  \begin{equation}
+    \label{eq:forward two step mutation}
+    \phi_2(\lambda)
+    =
+    \begin{cases}
+      \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\
+      (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\
+      (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\
+      (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}
+    \end{cases}
+  \end{equation}
+  \begin{equation}
+    \label{eq:backward two step mutation}
+    \phi_{-2}(\lambda)
+    =
+    \begin{cases}
+      \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\
+      (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\
+      (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\
+      (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$.}
+    \end{cases}
+  \end{equation}
+
+  For $|k|>2$, define piecewise-linear maps
+  \[\phi_k
+    :=
+    \begin{cases}
+      \phi_1\phi_2^j & \text{if $k>0$ and $k=2j+1$;}\\
+      \phi_{-1}\phi_{-2}^j & \text{if $k<0$ and $k=-2j-1$;}\\
+      \phi_2^j & \text{if $k>0$ and $k=2j$;}\\
+      \phi_{-2}^j & \text{if $k<0$ and $k=-2j$;}\\
+    \end{cases}
+  \]
+  and observe that $\phi_{2j}^{-1}=\phi_{-2j}$ for $j\in\ZZ$.
+
+  \begin{definition}
+    For $\lambda\in\ZZ^2$, define cones $\cC(\lambda):=\lambda-b\RR_{\ge0}+c\RR_{\ge0}$ and $\cC'(\lambda):=\lambda+b\RR_{\ge0}-c\RR_{\ge0}$.
+    The \emph{dominance region} $\cP(\lambda)$ is the intersection of $\bigcap_{j\in\ZZ}\phi_{2j}^{-1}\cC(\phi_{2j}\lambda)$ and $\bigcap_{j\in\ZZ} \phi_{2j+1}^{-1}\cC'(\phi_{2j+1}\lambda)$
+  \end{definition}
+
+  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k>0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
+  \begin{lemma}
+    Any nonzero eigenvector of $\phi_2$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  \end{lemma}
+  \begin{proof}
+    First observe that the equation $\phi_2^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k>0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
+    In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
+    We thus require 
+    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
+    or equivalently
+    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
+    As these represent the same relationship, the result immediately follows by inspection.
+  \end{proof}
+
+  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
+  %\begin{lemma}
+  %  The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
+  %\end{lemma}
+  %\begin{proof}
+  %  This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
+  %\end{proof}
+  \begin{lemma}
+    \label{le:imaginary stability}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{2j}(\lambda)\in\cI$ and $\phi_{2j+1}(\lambda)\in\cI'$.
+  \end{lemma}
+  \begin{proof}
+    Since $\phi_{2j}=\phi_2^j$ and $\phi_{2j+1}=\phi_1\phi_{t_2}^j$, the result follows from the cases $j=1$ and $j=0$, respectively.
+    The claim is immediate for $\phi_2$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_2$ is linear in $\cI$.
+    Now, since $b>0$, we have $\phi_1(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_1\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_1$ in this region.
+  \end{proof}
+
+  It will be useful to have explicit expressions for $\phi_k(\lambda)$ for $\lambda\in\cI$.
+  \begin{lemma}
+    \label{le:imaginary transformations}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have
+    \begin{align*}
+      \phi_{2j}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
+      \phi_{2j+1}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
+    \end{align*}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $j$, the case $j=0$ being clear from the definitions.
+    For $\lambda\in\cI$, the action of $\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
+    \[\phi_2(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
+    and so
+    \begin{align*}
+      \phi_{2j+2}(\lambda)&=\phi_2\phi_{2j}(\lambda)\\
+      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
+      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
+      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
+    \end{align*}
+    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
+
+    Similarly, using $\phi_1(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
+  \end{proof}
+
+\section{Proof of Theorem~\ref{th:dominance inequalities}}
+
+  \begin{lemma}
+    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
+  \end{lemma}
+  \begin{proof}
+    It is enough to consider $\phi_{t_{-2}}^{-1}\cC_{t_{-2}}(\phi_{t_{-2}}\lambda) \cap \cC_{t_0}(\lambda) \cap \phi_{t_2}^{-1}\cC_{t_2}(\phi_{t_2}\lambda)$, we leave the details to the reader.
+  \end{proof}
+
+  \begin{lemma}
+    \label{le:one direction}
+    For $\lambda\in\cI\cap\ZZ^2$, 
+    \begin{enumerate}
+      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
+      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
+    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
+  \end{proof}
+
+  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP(\lambda)$ for $\lambda\in\cI$.
+  \begin{lemma}
+    \label{le:transformed inequalities}
+    Let $A=(a_{ij})$ be an invertible $2\times 2$ matrix.
+    Under the action of $A$, the region inside $\RR^2$ defined by the inequality $rx+sy\le t$ is transformed to the region defined by the inequality \[\frac{ra_{22}-sa_{21}}{a_{11}a_{22}-a_{12}a_{21}}x + \frac{-ra_{12}+sa_{11}}{a_{11}a_{22}-a_{12}a_{21}}y\le t.\]
+  \end{lemma}
+  \begin{proof}
+    Assume $r,s,t\ne0$, the cases when one of these vanishes follows by the continuity of the transformation.
+    Observe that the points $\big(\frac{t}{r},0\big)$ and $\big(0,\frac{t}{s}\big)$ lie on the boundary line of the region defined by the inequality $rx+sy\le t$.
+    These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
+    By the linearity of the transformation of $\RR^2$ given by the matrix $A$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
+  \end{proof}
+
+  \begin{lemma}
+    For $i\ge1$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+    \begin{align}
+      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
+      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
+      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+    \end{align}
+
+    given as in the figure below:
+    \[
+      \begin{tikzpicture}
+        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
+        \draw[-] (-8,0) -- (5,0);
+        \draw[-] (0,-5) -- (0,5);
+        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
+        \draw[dashed] (0,0) -- (5,-2.113);
+        \draw[dashed] (0,0) -- (3.17,-5);
+        \node at (1,-0.9) {$\cI$};
+        \draw[fill=black] (3.5,-3) circle (2pt);
+        \node[right] at (3.5,-3) {$\lambda$};
+        \draw[->,thick] (3.5,-3) -- (47/10,-5);
+        \draw[-,thick] (3.5,-3) -- (0,26/10);
+        \draw[-,thick] (0,26/10) -- (-26/4,0);
+        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
+        \node at (4.5,-4) {\eqref{ineq:1}};
+        \node at (2.34,-0.5) {\eqref{ineq:2}};
+        \node at (-3,1.75) {\eqref{ineq:3}};
+        \node at (-5.36,-3) {\eqref{ineq:4}};
+      \end{tikzpicture}
+    \]
+  \end{lemma}
+  \begin{proof}
+    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
+
+    For $i=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
+    We inductively compute the region $\phi_{t_{2j}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{t_{2j}}^{-1}=\phi_{t_2}^{-j}$.
+
+    \subsubsection*{Claim:} For $k>0$, $\phi_{t_{2k}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ is the region determined by the inequalities 
+    \begin{align*}
+      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
+      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
+    \end{align*}
+
+    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$ which corresponds to (a) with $k=1$.
+    Similarly, the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\dagger$) intersects three domains of linearity in which $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $k=1$.
+    This establishes the base of an induction on $k$.
+
+    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
+    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
+    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
+    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
+    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
+    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
+    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (b) for $k+1$.
+    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
+    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
+    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
+    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
+    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
+    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
+    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
+    This completes the induction on $k$, proving the Claim and the result for $i$ even.
+
+    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
+    Using that $\phi_{t_{2j+1}}^{-1}=\phi_{t_2}^{-j}\phi_{t_1}^{-1}$, we compute the image inductively as above.
+    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_{t_1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_{t_1}^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
+    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_{t_1}^{-1}$ and thus produces the inequalities
+    \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]
+
+    \subsubsection*{Claim:} For $k\ge 0$, $\phi_{t_{2k+1}}^{-1}\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ is the region determined by the inequalities 
+    \begin{align*}
+      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
+      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
+      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
+    \end{align*}
+    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_{t_2}^{-1}$ and this completes the proof.
+  \end{proof}
 
@@
   \section{Rank Two}
-  Fix integers $b,c>0$ and assume $bc\ge 4$.
-  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
-  Here we may take the 2-regular tree $\TT_2$ to have vertices labeled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labeled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labeled $2$.
-  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
-
-  Observe that $\phi_{t_1}:=\phi_1^{t_0}$ is the piecewise-linear map given by
-  \begin{equation}
-    \label{eq:forward mutation 1}
-    \phi_{t_1}(\lambda)=\begin{cases} (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1\ge0$;}\\ (-\lambda_1,\lambda_2) & \text{if $\lambda_1<0$;} \end{cases}
-  \end{equation}
-  and $\phi_{t_2}:=\phi_2^{t_1}\phi_1^{t_0}$ is the piecewise-linear map given by
-  \begin{equation}
-    \label{eq:forward two step mutation}
-    \phi_{t_2}(\lambda)=\begin{cases} \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\ (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\ (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}\end{cases}
-  \end{equation}
-  while $\phi_{t_2}^{-1}=\phi_{t_{-2}}$ is the piecewise-linear map given by
-  \begin{equation}
-    \label{eq:backward two step mutation}
-    \phi_{t_2}^{-1}(\lambda)=\begin{cases} \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\ (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\ (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$;}\end{cases}
-  \end{equation}
-
-  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
-  \begin{lemma}
-    Any nonzero eigenvector of $\phi_{t_2}$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  \end{lemma}
-  \begin{proof}
-    First observe that the equation $\phi_{t_2}^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
-    In this region, $\phi_{t_2}$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
-    We thus require that 
-    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
-    or, equivalently, that
-    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
-    As these represent the same relation, the result immediately follows by inspection.
-  \end{proof}
-
-  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
-  \begin{lemma}
-    The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
-  \end{proof}
-  \begin{lemma}
-    \label{le:imaginary stability}
-    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
-  \end{lemma}
-  \begin{proof}
-    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$, respectively.
-    The claim is immediate for $\phi_{t_2}$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_{t_2}$ is linear in $\cI$.
-    Now, since $b>0$, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_{t_1}$ in this region.
-  \end{proof}
-
-  It will be useful to have explicit expressions for $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
-  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
-  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
-  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
-
-  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
-  This leads to the following more general recursive structure.
-  \begin{lemma}
-    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
-    \begin{equation}
-      \label{eq:long Chebyshev recursion}
-      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
-    \end{equation}
-  \end{lemma}
-  \begin{proof}
-    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
-    Using the claim for $j>0$ and then the defining recursion twice, we get
-    \begin{align*}
-      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
-    \end{align*}
-    which is the claimed recursion for $\ell+1$.
-    These calculations can be reversed to show the result for $\ell<0$.
-  \end{proof}
-
-  The following gives the desired expressions for $\phi_{t_i}(\lambda)$ when $\lambda\in\cI$.
-  \begin{lemma}
-    \label{le:imaginary transformations}
-    For $j\in\ZZ$ and $\lambda\in\cI$, we have
-    \begin{align*}
-      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
-      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
-    \end{align*}
-  \end{lemma}
-  \begin{proof}
-    We work by induction on $j$, the case $j=0$ being clear from the definitions.
-    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$.
-    For $\lambda\in\cI$, the action of $\phi_{t_2}$ from \eqref{eq:forward two step mutation} can be rewritten as
-    \[\phi_{t_2}(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
-    and so
-    \begin{align*}
-      \phi_{t_{2j+2}(\lambda)}&=\phi_{t_2}\phi_{t_{2j}}(\lambda)\\
-      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
-      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
-      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
-    \end{align*}
-    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
-
-    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
-  \end{proof}
-
-  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
-  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
-  By the equalities 
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
-  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
-  \begin{remark}
-    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
-    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
-  \end{remark}
-
-  \begin{lemma}
-    We have
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
-  \end{lemma}
-  \begin{proof}
-    For any $i\ge 1$, we have
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
-    It follows that
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
-    which is equivalent to the desired expression.
-    Similarly, 
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
-    so that
-    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
-    which is again equivalent to the desired expression.
-  \end{proof}
-
-  \begin{lemma}
-    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
-  \end{lemma}
-  \begin{proof}
-    It is enough to consider $\phi_{t_{-2}}^{-1}\cC_{t_{-2}}(\phi_{t_{-2}}\lambda) \cap \cC_{t_0}(\lambda) \cap \phi_{t_2}^{-1}\cC_{t_2}(\phi_{t_2}\lambda)$, we leave the details to the reader.
-  \end{proof}
-
-  \begin{lemma}
-    \label{le:one direction}
-    For $\lambda\in\cI\cap\ZZ^2$, 
-    \begin{enumerate}
-      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
-      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
-    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
-  \end{proof}
 
@@
   \end{proof}
-
-  \begin{remark}
-    Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
-    This unexpected coincidence is one of our reasons for deciding to write down these results.
-  \end{remark}
 
@@
   \end{thebibliography}
-
-  \section{Chebyshev}
-  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
-  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
-  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
-
-  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
-  This leads to the following more general recursive structure.
-  \begin{lemma}
-    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
-    \begin{equation}
-      \label{eq:long Chebyshev recursion}
-      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
-    \end{equation}
-  \end{lemma}
-  \begin{proof}
-    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
-    Using the claim for $j>0$ and then the defining recursion twice, we get
-    \begin{align*}
-      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
-    \end{align*}
-    which is the claimed recursion for $\ell+1$.
-    These calculations can be reversed to show the result for $\ell<0$.
-  \end{proof}
-
-  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
-  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
-  By the equalities 
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
-  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
-  \begin{remark}
-    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
-    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
-  \end{remark}
-
-  \begin{lemma}
-    We have
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
-  \end{lemma}
-  \begin{proof}
-    For any $i\ge 1$, we have
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
-    It follows that
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
-    which is equivalent to the desired expression.
-    Similarly, 
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
-    so that
-    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
-    which is again equivalent to the desired expression.
-  \end{proof}
-
-  \section{Proof of Theorem~\ref{th:dominance inequalities}}
-
-  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP(\lambda)$ for $\lambda\in\cI$.
-  \begin{lemma}
-    \label{le:transformed inequalities}
-    Let $A=(a_{ij})$ be an invertible $2\times 2$ matrix.
-    Under the action of $A$, the region inside $\RR^2$ defined by the inequality $rx+sy\le t$ is transformed to the region defined by the inequality \[\frac{ra_{22}-sa_{21}}{a_{11}a_{22}-a_{12}a_{21}}x + \frac{-ra_{12}+sa_{11}}{a_{11}a_{22}-a_{12}a_{21}}y\le t.\]
-  \end{lemma}
-  \begin{proof}
-    Assume $r,s,t\ne0$, the cases when one of these vanishes follows by the continuity of the transformation.
-    Observe that the points $\big(\frac{t}{r},0\big)$ and $\big(0,\frac{t}{s}\big)$ lie on the boundary line of the region defined by the inequality $rx+sy\le t$.
-    These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
-    By the linearity of the transformation of $\RR^2$ given by the matrix $A$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
-  \end{proof}
-
-  \begin{lemma}
-    For $i\ge1$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
-    \begin{align}
-      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
-      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
-    \end{align}
-
-    given as in the figure below:
-    \[
-      \begin{tikzpicture}
-        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
-        \draw[-] (-8,0) -- (5,0);
-        \draw[-] (0,-5) -- (0,5);
-        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
-        \draw[-] (0,0) -- (5,-2.113);
-        \draw[-] (0,0) -- (3.17,-5);
-        \node at (1,-0.9) {$\cI$};
-        \draw[fill=black] (3.5,-3) circle (2pt);
-        \node[below right] at (3.5,-3) {$\lambda$};
-        \draw[->,thick] (3.5,-3) -- (47/10,-5);
-        \draw[-,thick] (3.5,-3) -- (0,26/10);
-        \draw[-,thick] (0,26/10) -- (-26/4,0);
-        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
-        \node at (4.5,-4) {\eqref{ineq:1}};
-        \node at (2.5,-0.5) {\eqref{ineq:2}};
-        \node at (-3,1.75) {\eqref{ineq:3}};
-        \node at (-5.5,-3) {\eqref{ineq:4}};
-      \end{tikzpicture}
-    \]
-  \end{lemma}
-  \begin{proof}
-    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
-
-    For $i=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
-    We inductively compute the region $\phi_{t_{2j}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{t_{2j}}^{-1}=\phi_{t_2}^{-j}$.
-
-    \subsubsection*{Claim:} For $k>0$, $\phi_{t_{2k}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ is the region determined by the inequalities 
-    \begin{align*}
-      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
-      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
-    \end{align*}
-
-    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$ which corresponds to (a) with $k=1$.
-    Similarly, the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\dagger$) intersects three domains of linearity in which $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $k=1$.
-    This establishes the base of an induction on $k$.
-
-    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
-    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
-    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
-    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (b) for $k+1$.
-    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
-    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
-    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
-    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
-    This completes the induction on $k$, proving the Claim and the result for $i$ even.
-
-    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
-    Using that $\phi_{t_{2j+1}}^{-1}=\phi_{t_2}^{-j}\phi_{t_1}^{-1}$, we compute the image inductively as above.
-    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_{t_1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
-    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_{t_1}^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
-    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_{t_1}^{-1}$ and thus produces the inequalities
-    \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]
-
-    \subsubsection*{Claim:} For $k\ge 0$, $\phi_{t_{2k+1}}^{-1}\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ is the region determined by the inequalities 
-    \begin{align*}
-      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
-      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
-      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
-    \end{align*}
-    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_{t_2}^{-1}$ and this completes the proof.
-  \end{proof}
 

### 2022-04-05 dominance_regions.tex
Section 3 edits

@@
 
-\section{Rank Two Lattice Mutations}
-  We begin by studying transformations of $\RR^2$ which determine the transformation of $\bfg$-vectors under mutations.
-
-  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1},\phi_{\pm 2}:\RR^2\to\RR^2$ as follows:
+\section{$\bfg$-vector Mutations}
+  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors under mutations.
+  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1}:\RR^2\to\RR^2$ as follows:
   \begin{equation}
@@
       (\lambda_1,-\lambda_2) & \text{if $\lambda_2 \ge 0$;}\\
-      (\lambda_1+b\lambda_2,-\lambda_2) & \text{if $\lambda_2 < 0$;}
+      (\lambda_1+b\lambda_2,-\lambda_2) & \text{if $\lambda_2 < 0$.}
     \end{cases}
   \end{equation}
+  For $k\in\ZZ$ with $|k|>1$, define piecewise-linear maps
+  \[\phi_k
+    :=
+    \begin{cases}
+      (\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j$;}\\
+      \phi_1(\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j+1$.}\\
+    \end{cases}
+  \]
+  These determine the dominance region as follows.
+  \begin{definition}
+    For $\lambda\in\ZZ^2$, define cones 
+    \[\cC(\lambda):=\{(\lambda_1-r,\lambda_2+s):r,s\in\RR_{\ge0}\}\quad\text{ and }\quad \cC'(\lambda):=\{(\lambda_1+r,\lambda_2-s):r,s\in\RR_{\ge0}\}.\]
+    The \emph{dominance region} $\cP(\lambda)$ is the intersection of $\bigcap_{j\in\ZZ}\phi_{2j}^{-1}\cC(\phi_{2j}\lambda)$ and $\bigcap_{j\in\ZZ} \phi_{2j+1}^{-1}\cC'(\phi_{2j+1}\lambda)$.
+  \end{definition}
+
+  We record here a few useful calculations relating to the tropical transformations $\phi_k$.
+  First observe the following explicit expression for $\phi_2$:
   \begin{equation}
@@
   \end{equation}
-  \begin{equation}
-    \label{eq:backward two step mutation}
-    \phi_{-2}(\lambda)
-    =
-    \begin{cases}
-      \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\
-      (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\
-      (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\
-      (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$.}
-    \end{cases}
-  \end{equation}
-
-  For $|k|>2$, define piecewise-linear maps
-  \[\phi_k
-    :=
-    \begin{cases}
-      \phi_1\phi_2^j & \text{if $k>0$ and $k=2j+1$;}\\
-      \phi_{-1}\phi_{-2}^j & \text{if $k<0$ and $k=-2j-1$;}\\
-      \phi_2^j & \text{if $k>0$ and $k=2j$;}\\
-      \phi_{-2}^j & \text{if $k<0$ and $k=-2j$;}\\
-    \end{cases}
-  \]
-  and observe that $\phi_{2j}^{-1}=\phi_{-2j}$ for $j\in\ZZ$.
-
-  \begin{definition}
-    For $\lambda\in\ZZ^2$, define cones $\cC(\lambda):=\lambda-b\RR_{\ge0}+c\RR_{\ge0}$ and $\cC'(\lambda):=\lambda+b\RR_{\ge0}-c\RR_{\ge0}$.
-    The \emph{dominance region} $\cP(\lambda)$ is the intersection of $\bigcap_{j\in\ZZ}\phi_{2j}^{-1}\cC(\phi_{2j}\lambda)$ and $\bigcap_{j\in\ZZ} \phi_{2j+1}^{-1}\cC'(\phi_{2j+1}\lambda)$
-  \end{definition}
+  %\begin{equation}
+  %  \label{eq:backward two step mutation}
+  %  \phi_{-2}(\lambda)
+  %  =
+  %  \begin{cases}
+  %    \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\
+  %    (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\
+  %    (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\
+  %    (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$.}
+  %  \end{cases}
+  %\end{equation}
 
@@
     The claim is immediate for $\phi_2$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_2$ is linear in $\cI$.
-    Now, since $b>0$, we have $\phi_1(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_1\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_1$ in this region.
+    Now, since $b>0$, we have $\phi_1(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$.
+    It follows that $\phi_1\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$.
+    The result then follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_1$ in this region.
   \end{proof}
@@
     For $\lambda\in\cI$, the action of $\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
-    \[\phi_2(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
-    and so
+    \[\phi_2(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2).\]
+    Therefore
     \begin{align*}
@@
 
-    Similarly, using $\phi_1(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
+    Similarly, using $\phi_1(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$ together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
   \end{proof}

### 2022-04-05 dominance_regions.tex
More reorganization and edits

@@
   \begin{definition}
-    For $\lambda\in\ZZ^2$, define cones 
-    \[\cC(\lambda):=\{(\lambda_1-r,\lambda_2+s):r,s\in\RR_{\ge0}\}\quad\text{ and }\quad \cC'(\lambda):=\{(\lambda_1+r,\lambda_2-s):r,s\in\RR_{\ge0}\}.\]
-    The \emph{dominance region} $\cP(\lambda)$ is the intersection of $\bigcap_{j\in\ZZ}\phi_{2j}^{-1}\cC(\phi_{2j}\lambda)$ and $\bigcap_{j\in\ZZ} \phi_{2j+1}^{-1}\cC'(\phi_{2j+1}\lambda)$.
+    For $\lambda\in\ZZ^2$ and $k\in\ZZ$, define cones 
+    \[\cC_k(\lambda)
+      :=
+      \begin{cases}
+        \{(\lambda_1-r,\lambda_2+s):r,s\in\RR_{\ge0}\} & \text{if $k=2j$;}\\
+        \{(\lambda_1+r,\lambda_2-s):r,s\in\RR_{\ge0}\} & \text{if $k=2j+1$.}
+      \end{cases}
+    \]
+    The \emph{dominance region} $\cP(\lambda)$ is the intersection  $\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$.
+    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
   \end{definition}
@@
   Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP(\lambda)$ for $\lambda\in\cI$.
+
+  \begin{lemma}
+    \label{le:transformed inequalities}
+    Let $A$ be an invertible $n\times n$ matrix.
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equalities
+    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
+  \end{proof}
+
   \begin{lemma}
@@
 \section{Lattice Mutations and Linear Inequalities}
-  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e.
-there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
-  Write $\Col(B)$ for the span of the columns of $B$ inside $\RR^n$ and $\Col^+(B)$ for their non-negative span.
-  Define $\Col_\ZZ(B)$ and $\Col^+_\ZZ(B)$ analogously over the integers.
-
-  The matrix $B$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_m,i_{m+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le m$.
-  This condition is naturally interpreted in terms of an associated quiver $Q_B$ with $n$ vertices and an arrow $i\to j$ whenever $b_{ji}>0$ (if we need to use representation theory at any point we'll have to change this to be $\gcd(b_{ij},b_{ji})$ arrows $i\to j$).
-  Indeed, this is precisely the condition that $Q_B$ has no oriented cycles.
-  In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_{\ell'} k_\ell}\ge 0$.
-  The sequence $(k_1,\ldots,k_n)$ (resp.
-$(k_n,\ldots,k_1)$) is then said to be \emph{source-adapted} (resp.
-\emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
-  %\sayDR{We need to pin down this convention.}
 
@@
     and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-  \end{proof}
-
-  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
-  \begin{itemize}
-    \item $\phi_{t_0}=\Id$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
-  \end{itemize}
-
-  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
-  \begin{definition}
-    For $\lambda\in\RR^n$, define the \emph{dominance region} 
-    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
-    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
-  \end{definition}
-  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
-  \begin{lemma}
-    The sets $\cP(\lambda)$ are polytopes.
-  \end{lemma}
-
-  \begin{lemma}
-    \label{le:transformed inequalities}
-    Let $A$ be an invertible $n\times n$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the equalities
-    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
   \end{proof}
@@
 
-  \begin{thebibliography}{XXX}
-
-    \bibitem{lee-li-zelevinsky}
-      K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014), pp.~57--82.
-
-    \bibitem{rupel}
-      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
-Algebraic Combinatorics, \textbf{2} (2019) no.
-6, pp.~1239--1273.
-\href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
-  \end{thebibliography}
-
 \section{Proof of Theorem~\ref{th:dominance vertices}}
@@
 \section{The affine case}
+  \label{sec:affine}
   In this section we compare our main result with the construction of \cite{RSW19} in the case $b=c=2$.
@@
 
+  \begin{thebibliography}{XXX}
+
+    \bibitem{lee-li-zelevinsky}
+      K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014), pp.~57--82.
+
+    \bibitem{rupel}
+      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
+Algebraic Combinatorics, \textbf{2} (2019) no.
+6, pp.~1239--1273.
+\href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
+  \end{thebibliography}
+
 \end{document}

### 2022-04-05 dominance_regions.tex
figures

--- 2022-04-05 dominance_regions.tex
@@
   \centering
+    \newcommand{\setconstants}{
+      \tikzmath{\b = 3.5; \c = 4.4 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
+      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
+      \clip (\xmin,\ymin) rectangle (\xmax,\ymax);
+    }
     \newcommand{\boundingrays}{
-      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
-      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
-      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
-      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
-      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
-      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
-      \draw [color=lightgray, thick, dashed] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
-      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
+      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
+      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
+      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
+      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
+      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
+      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
     }
@@
     \begin{scope}[shift={(0,0)}]
+      \setconstants;
+      \draw[draw=none, fill=gray!20] (0,0) -- (2*\xmax,0) -- (2*\xmax,2*\ymax) --  (0,2*\ymax) -- cycle; 
       \boundingrays;
-      \tikzmath{ \r=1; \s=1; \x = \r; \y=\s; }
+      \tikzmath{ \t=3; \r=1; \s=1; \xx = \r; \yy=\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (6pt);
@@
     \begin{scope}[shift={(13,0)}]
+      \setconstants;
+      \draw[draw=none, fill=gray!20] (0,0) -- (2*\xmax,0) -- (4*\xmax,-2*\xmax / \b) --  (2*\xmax,-2*\xmax / \b) -- cycle; 
       \boundingrays;
-    \tikzmath{ \r=1; \s=1; \x = \r + \b*\s; \y=-\s; }
+      \tikzmath{ \t=5; \r=2; \s=1; \xx = \r + \b*\s; \yy=-\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (6pt);
@@
     \begin{scope}[shift={(26,0)}]
+      \setconstants;
+      \draw[draw=none, fill=gray!20] (0,0) -- (2*\xmin,0) -- (2*\xmin,2*\ymax) --  (0,2*\ymax) -- cycle; 
       \boundingrays;
-      \tikzmath{ \r=1; \s=1; \x=-\r; \y=\s; }
+      \tikzmath{ \t=3; \r=1; \s=1; \xx=-\r; \yy=\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (6pt);
@@
     \begin{scope}[shift={(39, 0)}]
+      \setconstants;
+      \draw[draw=none, fill=gray!20] (0,0) -- (2*\xmin,0) -- (2*\xmin,2*\ymin) --  (0,2*\ymin) -- cycle; 
       \boundingrays;
-      \tikzmath{ \r=1; \s=1; \x=-\r; \y=-\s; }
+      \tikzmath{ \t=1; \r=1; \s=1; \xx=-\r; \yy=-\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (6pt);
@@
     \begin{scope}[shift={(0,-13)}]
+      \setconstants;
+      \draw[draw=none, fill=gray!20] (0,0) -- (2*\xmax, -2*\xmax / \b) -- (4*\xmax, -2*\xmax / \b-2*\xmax * \c / \bcmo ) --  (2*\xmax, -2*\xmax * \c / \bcmo ) -- cycle; 
       \boundingrays;
-      \tikzmath{ \r=1; \s=1; \x={\r*\b+\s*(\b*\c-1) }; \y = {-\r -\c*\s};  }
+      \tikzmath{ \t=5; \r=1; \s=1; \xx={\r*\b+\s*(\b*\c-1) }; \yy = {-\r -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (6pt);
@@
     \begin{scope}[shift={(13,-13)}]
+      \setconstants;
+      \draw[draw=none, fill=gray!20] (0,0) --  (2*\xmax, -2*\xmax * \c / \bcmo ) -- (4*\xmax, -2*\xmax * \c / \bcmo -\xmax * \bcms / \b) -- (2*\xmax, -\xmax * \bcms / \b) -- cycle; 
       \boundingrays;
-      \tikzmath{ \r=1/2; \s=1; \x={2*\r*\b+\s*(\b*\c-1) }; \y = {-\r*\bcms -\c*\s};  }
+      \tikzmath{ \t=5; \r=1; \s=2; \xx={2*\r*\b+\s*(\b*\c-1) }; \yy = {-\r*\bcms -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (6pt);
@@
     \begin{scope}[shift={(26,-13)}]
+      \setconstants;
+      \draw[draw=none, fill=gray!20] (0,0) -- (0, 2*\ymin) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin +2*\ymin) --  ( - 4 * \b * \ymin / \bcps, 2*\ymin) -- cycle; 
       \boundingrays;
-      \tikzmath{ \r=0.3; \s=1; \x={2*\r*\b }; \y = {-\r*\bcps -\s};  }
+      \tikzmath{ \t=2; \r=0.3; \s=1; \xx={2*\r*\b }; \yy = {-\r*\bcps -\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (6pt);
@@
     \begin{scope}[shift={(39,-13)}]
+      \setconstants;
+      \draw[draw=none, fill=gray!20] (0,0) -- (2*\xmax, -\xmax * \bcms / \b) -- ( - 4 * \b * \ymin / \bcps + 2*\xmax, 2*\ymin  -\xmax * \bcms / \b) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin) -- cycle; 
       \boundingrays;
-      \tikzmath{ \r=0.5; \s=0.7; \x={2*(\r+\s)*\b }; \y = {-\r*\bcps -\s*\bcms};  }
+      \tikzmath{ \t=5; \r=1; \s=2; \xx={2*(\r+\s)*\b }; \yy = {-\r*\bcps -\s*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
       \fill (\x , \y)  circle (6pt);
@@
 
-The paper is organized as follows.
-In Section~\ref{sec:chebyshev}, we collect useful results related to two-parameter Chebyshev polynomials which support our main calculations.
-
-\section{Chebyshev Polynomials}
-  \label{sec:chebyshev}
-  Define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+\section{Lattice Mutations and Linear Inequalities}
+  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e.
+there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
+  Write $\Col(B)$ for the span of the columns of $B$ inside $\RR^n$ and $\Col^+(B)$ for their non-negative span.
+  Define $\Col_\ZZ(B)$ and $\Col^+_\ZZ(B)$ analogously over the integers.
+
+  The matrix $B$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_m,i_{m+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le m$.
+  This condition is naturally interpreted in terms of an associated quiver $Q_B$ with $n$ vertices and an arrow $i\to j$ whenever $b_{ji}>0$ (if we need to use representation theory at any point we'll have to change this to be $\gcd(b_{ij},b_{ji})$ arrows $i\to j$).
+  Indeed, this is precisely the condition that $Q_B$ has no oriented cycles.
+  In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_{\ell'} k_\ell}\ge 0$.
+  The sequence $(k_1,\ldots,k_n)$ (resp.
+$(k_n,\ldots,k_1)$) is then said to be \emph{source-adapted} (resp.
+\emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
+  %\sayDR{We need to pin down this convention.}
+
+  For $b\in\ZZ$, write $[b]_+=max(b,0)$.
+  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
+  \begin{equation}
+    \label{eq:left mutation matrix}
+    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise;} \end{cases}
+  \end{equation}
+  and a matrix $F_{k,\varepsilon}=(f_{ij})$ with
+  \begin{equation}
+    \label{eq:right mutation matrix}
+    f_{ij}=\begin{cases} 1 & \text{if $k\ne i=j$;}\\ -1 & \text{if $k=i=j$;}\\ [-\varepsilon b_{kj}]_+ & \text{if $k=i\ne j$;}\\ 0 & \text{otherwise.} \end{cases}
+  \end{equation}
+  Observe that $E^2_{k,\varepsilon}=\Id$ and $F^2_{k,\varepsilon}=\Id$ for any $k$ and any choice of $\varepsilon$.
+  \begin{lemma}
+    For $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, we have $E_{k,-\varepsilon}E_{k,\varepsilon}=I_n+\varepsilon B^{\bullet k}$ and $E_{k,\varepsilon}-E_{k,-\varepsilon}=\varepsilon B^{\bullet k}$.
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equality $\varepsilon b_{ij}=[\varepsilon b_{ij}]_+-[-\varepsilon b_{ij}]_+$.
+  \end{proof}
+
+  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_k B=(b'_{ij})$ given by
+  \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
+  One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
+  \begin{remark}
+    Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
+  \end{remark}
+
+  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
+  \begin{itemize}
+    \item $B^{t_0}=B$;
+    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $B^{t'}=\mu_k B^t$.
+  \end{itemize}
+
+  (DR: I changed to $\RR$ because it didn't seem like we really cared about integer points at the moment, when we try to link up with minors this will need to be added.)
+  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
+  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
+  where the entries of $E^t_{k,\varepsilon}$ are given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
+  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
+  \begin{lemma}
+    Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
+    If $\mu\in\lambda+\Col(B^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+  \end{lemma}
+  \begin{proof}
+    Suppose $\mu=\lambda+B^t\alpha$ for some $\alpha\in\RR^n$.
+    Let $\varepsilon$ (resp. $\varepsilon'$) be such that $\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu$ (resp. $\phi^t_k(\lambda)=E^t_{k,\varepsilon'}\lambda$).
+    Then 
+    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+B^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + B^{t'} F^t_{k,\varepsilon}\alpha.\]
+    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + B^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+    Otherwise, 
+    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(B^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(B^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon B^{t'} \lambda_k \mathbf{e}_k\]
+    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+  \end{proof}
+
+  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
+  \begin{itemize}
+    \item $\phi_{t_0}=\Id$;
+    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
+  \end{itemize}
+
+  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
+  \begin{definition}
+    For $\lambda\in\RR^n$, define the \emph{dominance region} 
+    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
+    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
+  \end{definition}
+  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
+  \begin{lemma}
+    The sets $\cP(\lambda)$ are polytopes.
+  \end{lemma}
+
+  \begin{lemma}
+    \label{le:transformed inequalities}
+    Let $A$ be an invertible $n\times n$ matrix.
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equalities
+    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
+  \end{proof}
+
+  \section{Rank Two}
+  Fix integers $b,c>0$ and assume $bc\ge 4$.
+  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
+  Here we may take the 2-regular tree $\TT_2$ to have vertices labeled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labeled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labeled $2$.
+  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.
+
+  Observe that $\phi_{t_1}:=\phi_1^{t_0}$ is the piecewise-linear map given by
+  \begin{equation}
+    \label{eq:forward mutation 1}
+    \phi_{t_1}(\lambda)=\begin{cases} (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1\ge0$;}\\ (-\lambda_1,\lambda_2) & \text{if $\lambda_1<0$;} \end{cases}
+  \end{equation}
+  and $\phi_{t_2}:=\phi_2^{t_1}\phi_1^{t_0}$ is the piecewise-linear map given by
+  \begin{equation}
+    \label{eq:forward two step mutation}
+    \phi_{t_2}(\lambda)=\begin{cases} \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\ (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\ (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}\end{cases}
+  \end{equation}
+  while $\phi_{t_2}^{-1}=\phi_{t_{-2}}$ is the piecewise-linear map given by
+  \begin{equation}
+    \label{eq:backward two step mutation}
+    \phi_{t_2}^{-1}(\lambda)=\begin{cases} \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\ (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\ (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$;}\end{cases}
+  \end{equation}
+
+  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
+  \begin{lemma}
+    Any nonzero eigenvector of $\phi_{t_2}$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  \end{lemma}
+  \begin{proof}
+    First observe that the equation $\phi_{t_2}^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
+    In this region, $\phi_{t_2}$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
+    We thus require that 
+    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
+    or, equivalently, that
+    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
+    As these represent the same relation, the result immediately follows by inspection.
+  \end{proof}
+
+  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
+  \begin{lemma}
+    The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
+  \end{proof}
+  \begin{lemma}
+    \label{le:imaginary stability}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
+  \end{lemma}
+  \begin{proof}
+    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$, respectively.
+    The claim is immediate for $\phi_{t_2}$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_{t_2}$ is linear in $\cI$.
+    Now, since $b>0$, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_{t_1}$ in this region.
+  \end{proof}
+
+  It will be useful to have explicit expressions for $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
+  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
   \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
@@
     These calculations can be reversed to show the result for $\ell<0$.
+  \end{proof}
+
+  The following gives the desired expressions for $\phi_{t_i}(\lambda)$ when $\lambda\in\cI$.
+  \begin{lemma}
+    \label{le:imaginary transformations}
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have
+    \begin{align*}
+      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
+      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
+    \end{align*}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $j$, the case $j=0$ being clear from the definitions.
+    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$.
+    For $\lambda\in\cI$, the action of $\phi_{t_2}$ from \eqref{eq:forward two step mutation} can be rewritten as
+    \[\phi_{t_2}(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
+    and so
+    \begin{align*}
+      \phi_{t_{2j+2}(\lambda)}&=\phi_{t_2}\phi_{t_{2j}}(\lambda)\\
+      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
+      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
+      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
+    \end{align*}
+    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
+
+    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
   \end{proof}
@@
 
-\section{Rank Two Lattice Mutations}
-  We begin by studying transformations of $\RR^2$ which determine the transformation of $\bfg$-vectors under mutations.
-
-  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1},\phi_{\pm 2}:\RR^2\to\RR^2$ as follows:
-  \begin{equation}
-    \phi_1(\lambda)
-    =
-    \begin{cases} 
-      (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1 \ge 0$;}\\
-      (-\lambda_1,\lambda_2) & \text{if $\lambda_1 < 0$;}
-    \end{cases}
-    \qquad
-    \phi_{-1}(\lambda)
-    =
-    \begin{cases} 
-      (\lambda_1,-\lambda_2) & \text{if $\lambda_2 \ge 0$;}\\
-      (\lambda_1+b\lambda_2,-\lambda_2) & \text{if $\lambda_2 < 0$;}
-    \end{cases}
-  \end{equation}
-  \begin{equation}
-    \label{eq:forward two step mutation}
-    \phi_2(\lambda)
-    =
-    \begin{cases}
-      \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\
-      (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\
-      (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\
-      (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}
-    \end{cases}
-  \end{equation}
-  \begin{equation}
-    \label{eq:backward two step mutation}
-    \phi_{-2}(\lambda)
-    =
-    \begin{cases}
-      \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\
-      (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\
-      (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\
-      (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$.}
-    \end{cases}
-  \end{equation}
-
-  For $|k|>2$, define piecewise-linear maps
-  \[\phi_k
-    :=
-    \begin{cases}
-      \phi_1\phi_2^j & \text{if $k>0$ and $k=2j+1$;}\\
-      \phi_{-1}\phi_{-2}^j & \text{if $k<0$ and $k=-2j-1$;}\\
-      \phi_2^j & \text{if $k>0$ and $k=2j$;}\\
-      \phi_{-2}^j & \text{if $k<0$ and $k=-2j$;}\\
-    \end{cases}
-  \]
-  and observe that $\phi_{2j}^{-1}=\phi_{-2j}$ for $j\in\ZZ$.
-
-  \begin{definition}
-    For $\lambda\in\ZZ^2$, define cones $\cC(\lambda):=\lambda-b\RR_{\ge0}+c\RR_{\ge0}$ and $\cC'(\lambda):=\lambda+b\RR_{\ge0}-c\RR_{\ge0}$.
-    The \emph{dominance region} $\cP(\lambda)$ is the intersection of $\bigcap_{j\in\ZZ}\phi_{2j}^{-1}\cC(\phi_{2j}\lambda)$ and $\bigcap_{j\in\ZZ} \phi_{2j+1}^{-1}\cC'(\phi_{2j+1}\lambda)$
-  \end{definition}
-
-  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k>0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
-  \begin{lemma}
-    Any nonzero eigenvector of $\phi_2$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  \end{lemma}
-  \begin{proof}
-    First observe that the equation $\phi_2^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k>0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
-    In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
-    We thus require 
-    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
-    or equivalently
-    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
-    As these represent the same relationship, the result immediately follows by inspection.
-  \end{proof}
-
-  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
-  %\begin{lemma}
-  %  The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
-  %\end{lemma}
-  %\begin{proof}
-  %  This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
-  %\end{proof}
-  \begin{lemma}
-    \label{le:imaginary stability}
-    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{2j}(\lambda)\in\cI$ and $\phi_{2j+1}(\lambda)\in\cI'$.
-  \end{lemma}
-  \begin{proof}
-    Since $\phi_{2j}=\phi_2^j$ and $\phi_{2j+1}=\phi_1\phi_{t_2}^j$, the result follows from the cases $j=1$ and $j=0$, respectively.
-    The claim is immediate for $\phi_2$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_2$ is linear in $\cI$.
-    Now, since $b>0$, we have $\phi_1(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_1\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_1$ in this region.
-  \end{proof}
-
-  It will be useful to have explicit expressions for $\phi_k(\lambda)$ for $\lambda\in\cI$.
-  \begin{lemma}
-    \label{le:imaginary transformations}
-    For $j\in\ZZ$ and $\lambda\in\cI$, we have
-    \begin{align*}
-      \phi_{2j}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
-      \phi_{2j+1}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
-    \end{align*}
-  \end{lemma}
-  \begin{proof}
-    We work by induction on $j$, the case $j=0$ being clear from the definitions.
-    For $\lambda\in\cI$, the action of $\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
-    \[\phi_2(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
-    and so
-    \begin{align*}
-      \phi_{2j+2}(\lambda)&=\phi_2\phi_{2j}(\lambda)\\
-      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
-      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
-      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
-    \end{align*}
-    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
-
-    Similarly, using $\phi_1(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
-  \end{proof}
-
-\section{Proof of Theorem~\ref{th:dominance inequalities}}
-
   \begin{lemma}
@@
   \end{proof}
+
+  \begin{theorem}
+    There are six classes of dominance polytopes.
+    \begin{enumerate}
+      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
+    \end{enumerate}
+  \end{theorem}
+  \begin{proof}
+    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
+    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
+    or 
+    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
+    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
+    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
+  \end{proof}
+
+  \begin{remark}
+    Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
+    This unexpected coincidence is one of our reasons for deciding to write down these results.
+  \end{remark}
+
+%  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following inequalities:
+%  \begin{align}
+%    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
+%  \end{align}
+%  Are any of these better forms?
+%  \begin{align}
+%    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    \\
+%    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%  \end{align}
+%  Another proposal (I also changed the order of the equations)
+%  \begin{align}
+%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
+%    \\
+%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
+%    \\
+%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
+%    \\
+%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{align}
+%  Maybe this one:
+%  \begin{align}
+%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
+%    \\
+%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
+%    \\
+%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
+%    \\
+%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{align}
+%
+%  Yet another version:
+% 
+% {
+%    \everymath={\displaystyle}
+%  \[
+%  \begin{array}{rcccl}
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
+%    \\
+%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
+%    \\
+%    - b \lambda_2 & \geq & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) 
+%    \\
+%    0 & \geq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%  \end{array}
+%\]
+%}
+%
+%Or: (Maybe at this point we can remove $c/c$ and $b/b$)
+%
+% {
+%    \everymath={\displaystyle}
+%  \[
+%  \begin{array}{rcccl}
+%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
+%    \\
+%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2  & \leq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & 0
+%    \\
+%    & & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)  & \leq & - b \lambda_2
+%  \end{array}
+%\]
+%}
+%
+%
+%Or Or: (Maybe at this point we can remove $c/c$ and $b/b$)
+%
+%
+% The following, and possibly all the one before, has a typo
+% {
+%    \everymath={\displaystyle}
+%    \def\arraystretch{2.8}
+%  \[
+%  \begin{array}{rcccl}
+%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
+%    \\
+%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
+%    \\
+%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
+%  \end{array}
+%\]
+%}
+% {
+%    \everymath={\displaystyle}
+%    \def\arraystretch{2.8}
+%  \[
+%  \begin{array}{rcccl}
+%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
+%    \\
+%    -c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
+%    \\
+%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
+%    \\
+%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
+%  \end{array}
+%\]
+%}
+  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
+ {
+    \everymath={\displaystyle}
+    \def\arraystretch{2.8}
+  \[
+  \begin{array}{rcccl}
+    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
+    \\
+    \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
+    \\
+    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
+    \\
+    \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
+  \end{array}
+\]
+}
+
+  \section{The Total Domination Polyhedron}
+
+  Define the \emph{total domination polyhedron} $\cD:=\{(\lambda,\mu):\mu\in\cP(\lambda)\}$, i.e. this is the set of all pairs where $\lambda$ dominates $\mu$.
+  Write $\pi_1:\cD\to\RR^n$ for the projection to $\lambda$ and $\pi_2:\cD\to\RR^n$ for the projection to $\mu$.
+  \begin{itemize}
+    \item Is it a polyhedron?
+    \item The lemma below might suggest so.  
+      Indeed, if it is, by the Decomposition Theorem, we can write $\cD$ as the Minkowski sum of a polyhedral cone (almost certainly $\cI$) and a convex polytope (what is it?).
+      I am ignoring that it should really be the union of this polyhedron with a plane if the previous sentence holds any water.
+    \item Actually, we might need to take the union of several polyhedra to account for the variations in the fibers $\pi_1^{-1}(\lambda)$.
+  \end{itemize}
+
+  Is the following result true beyond rank 2?
+  \begin{lemma}
+    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
+  \end{lemma}
+  \begin{proof}
+    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_1,\lambda_2)$ where
+    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
+    (This comes from setting $\mu$ to be the vertex opposite $\lambda$ inside the dominance region $\cP(\lambda)$ and then solving for $\lambda$.)
+  \end{proof}
+  \begin{remark}
+    We want to understand what the curve is that results when we have $\mu$ lie along the unit circle, this should be possible by plugging $(\cos(\theta),\sin(\theta))$ into this formula for $\lambda$ and seeing what ellipse we get.
+  \end{remark}
+
+  \begin{thebibliography}{XXX}
+
+    \bibitem{lee-li-zelevinsky}
+      K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014), pp.~57--82.
+
+    \bibitem{rupel}
+      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
+Algebraic Combinatorics, \textbf{2} (2019) no.
+6, pp.~1239--1273.
+\href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
+  \end{thebibliography}
+
+  \section{Chebyshev}
+  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
+  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
+
+  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
+  This leads to the following more general recursive structure.
+  \begin{lemma}
+    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
+    \begin{equation}
+      \label{eq:long Chebyshev recursion}
+      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
+    \end{equation}
+  \end{lemma}
+  \begin{proof}
+    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
+    Using the claim for $j>0$ and then the defining recursion twice, we get
+    \begin{align*}
+      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
+      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
+    \end{align*}
+    which is the claimed recursion for $\ell+1$.
+    These calculations can be reversed to show the result for $\ell<0$.
+  \end{proof}
+
+  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
+  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
+  By the equalities 
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
+  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
+  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+  \begin{remark}
+    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
+    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
+  \end{remark}
+
+  \begin{lemma}
+    We have
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+  \end{lemma}
+  \begin{proof}
+    For any $i\ge 1$, we have
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
+    It follows that
+    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    which is equivalent to the desired expression.
+    Similarly, 
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
+    so that
+    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    which is again equivalent to the desired expression.
+  \end{proof}
+
+  \section{Proof of Theorem~\ref{th:dominance inequalities}}
 
@@
         %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
-        \draw[dashed] (0,0) -- (5,-2.113);
-        \draw[dashed] (0,0) -- (3.17,-5);
+        \draw[-] (0,0) -- (5,-2.113);
+        \draw[-] (0,0) -- (3.17,-5);
         \node at (1,-0.9) {$\cI$};
         \draw[fill=black] (3.5,-3) circle (2pt);
-        \node[right] at (3.5,-3) {$\lambda$};
+        \node[below right] at (3.5,-3) {$\lambda$};
         \draw[->,thick] (3.5,-3) -- (47/10,-5);
@@
         \node at (4.5,-4) {\eqref{ineq:1}};
-        \node at (2.34,-0.5) {\eqref{ineq:2}};
+        \node at (2.5,-0.5) {\eqref{ineq:2}};
         \node at (-3,1.75) {\eqref{ineq:3}};
-        \node at (-5.36,-3) {\eqref{ineq:4}};
+        \node at (-5.5,-3) {\eqref{ineq:4}};
       \end{tikzpicture}
@@
   \end{proof}
-
-\section{Lattice Mutations and Linear Inequalities}
-  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e.
-there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
-  Write $\Col(B)$ for the span of the columns of $B$ inside $\RR^n$ and $\Col^+(B)$ for their non-negative span.
-  Define $\Col_\ZZ(B)$ and $\Col^+_\ZZ(B)$ analogously over the integers.
-
-  The matrix $B$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_m,i_{m+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le m$.
-  This condition is naturally interpreted in terms of an associated quiver $Q_B$ with $n$ vertices and an arrow $i\to j$ whenever $b_{ji}>0$ (if we need to use representation theory at any point we'll have to change this to be $\gcd(b_{ij},b_{ji})$ arrows $i\to j$).
-  Indeed, this is precisely the condition that $Q_B$ has no oriented cycles.
-  In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_{\ell'} k_\ell}\ge 0$.
-  The sequence $(k_1,\ldots,k_n)$ (resp.
-$(k_n,\ldots,k_1)$) is then said to be \emph{source-adapted} (resp.
-\emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
-  %\sayDR{We need to pin down this convention.}
-
-  For $b\in\ZZ$, write $[b]_+=max(b,0)$.
-  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
-  \begin{equation}
-    \label{eq:left mutation matrix}
-    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise;} \end{cases}
-  \end{equation}
-  and a matrix $F_{k,\varepsilon}=(f_{ij})$ with
-  \begin{equation}
-    \label{eq:right mutation matrix}
-    f_{ij}=\begin{cases} 1 & \text{if $k\ne i=j$;}\\ -1 & \text{if $k=i=j$;}\\ [-\varepsilon b_{kj}]_+ & \text{if $k=i\ne j$;}\\ 0 & \text{otherwise.} \end{cases}
-  \end{equation}
-  Observe that $E^2_{k,\varepsilon}=\Id$ and $F^2_{k,\varepsilon}=\Id$ for any $k$ and any choice of $\varepsilon$.
-  \begin{lemma}
-    For $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, we have $E_{k,-\varepsilon}E_{k,\varepsilon}=I_n+\varepsilon B^{\bullet k}$ and $E_{k,\varepsilon}-E_{k,-\varepsilon}=\varepsilon B^{\bullet k}$.
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the equality $\varepsilon b_{ij}=[\varepsilon b_{ij}]_+-[-\varepsilon b_{ij}]_+$.
-  \end{proof}
-
-  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_k B=(b'_{ij})$ given by
-  \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
-  One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
-  \begin{remark}
-    Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
-  \end{remark}
-
-  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
-  \begin{itemize}
-    \item $B^{t_0}=B$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $B^{t'}=\mu_k B^t$.
-  \end{itemize}
-
-  (DR: I changed to $\RR$ because it didn't seem like we really cared about integer points at the moment, when we try to link up with minors this will need to be added.)
-  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
-  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
-  where the entries of $E^t_{k,\varepsilon}$ are given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
-  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-  \begin{lemma}
-    Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-    If $\mu\in\lambda+\Col(B^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-  \end{lemma}
-  \begin{proof}
-    Suppose $\mu=\lambda+B^t\alpha$ for some $\alpha\in\RR^n$.
-    Let $\varepsilon$ (resp. $\varepsilon'$) be such that $\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu$ (resp. $\phi^t_k(\lambda)=E^t_{k,\varepsilon'}\lambda$).
-    Then 
-    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+B^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + B^{t'} F^t_{k,\varepsilon}\alpha.\]
-    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + B^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-    Otherwise, 
-    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(B^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(B^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon B^{t'} \lambda_k \mathbf{e}_k\]
-    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-  \end{proof}
-
-  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
-  \begin{itemize}
-    \item $\phi_{t_0}=\Id$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
-  \end{itemize}
-
-  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
-  \begin{definition}
-    For $\lambda\in\RR^n$, define the \emph{dominance region} 
-    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
-    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
-  \end{definition}
-  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
-  \begin{lemma}
-    The sets $\cP(\lambda)$ are polytopes.
-  \end{lemma}
-
-  \begin{lemma}
-    \label{le:transformed inequalities}
-    Let $A$ be an invertible $n\times n$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the equalities
-    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
-  \end{proof}
-
-  \section{Rank Two}
-
-  \begin{theorem}
-    There are six classes of dominance polytopes.
-    \begin{enumerate}
-      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
-    \end{enumerate}
-  \end{theorem}
-  \begin{proof}
-    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
-    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
-    or 
-    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
-    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
-    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
-  \end{proof}
-
-%  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following inequalities:
-%  \begin{align}
-%    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
-%  \end{align}
-%  Are any of these better forms?
-%  \begin{align}
-%    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%  \end{align}
-%  Another proposal (I also changed the order of the equations)
-%  \begin{align}
-%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
-%    \\
-%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
-%    \\
-%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
-%    \\
-%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
-%  \end{align}
-%  Maybe this one:
-%  \begin{align}
-%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
-%    \\
-%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
-%    \\
-%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
-%    \\
-%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
-%  \end{align}
-%
-%  Yet another version:
-% 
-% {
-%    \everymath={\displaystyle}
-%  \[
-%  \begin{array}{rcccl}
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
-%    \\
-%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
-%    \\
-%    - b \lambda_2 & \geq & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) 
-%    \\
-%    0 & \geq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
-%  \end{array}
-%\]
-%}
-%
-%Or: (Maybe at this point we can remove $c/c$ and $b/b$)
-%
-% {
-%    \everymath={\displaystyle}
-%  \[
-%  \begin{array}{rcccl}
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
-%    \\
-%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2  & \leq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & 0
-%    \\
-%    & & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)  & \leq & - b \lambda_2
-%  \end{array}
-%\]
-%}
-%
-%
-%Or Or: (Maybe at this point we can remove $c/c$ and $b/b$)
-%
-%
-% The following, and possibly all the one before, has a typo
-% {
-%    \everymath={\displaystyle}
-%    \def\arraystretch{2.8}
-%  \[
-%  \begin{array}{rcccl}
-%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
-%    \\
-%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
-%    \\
-%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
-%  \end{array}
-%\]
-%}
-% {
-%    \everymath={\displaystyle}
-%    \def\arraystretch{2.8}
-%  \[
-%  \begin{array}{rcccl}
-%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    -c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
-%    \\
-%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
-%    \\
-%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
-%  \end{array}
-%\]
-%}
-  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
- {
-    \everymath={\displaystyle}
-    \def\arraystretch{2.8}
-  \[
-  \begin{array}{rcccl}
-    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
-    \\
-    \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
-    \\
-    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
-    \\
-    \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
-  \end{array}
-\]
-}
-
-  \section{The Total Domination Polyhedron}
-
-  Define the \emph{total domination polyhedron} $\cD:=\{(\lambda,\mu):\mu\in\cP(\lambda)\}$, i.e. this is the set of all pairs where $\lambda$ dominates $\mu$.
-  Write $\pi_1:\cD\to\RR^n$ for the projection to $\lambda$ and $\pi_2:\cD\to\RR^n$ for the projection to $\mu$.
-  \begin{itemize}
-    \item Is it a polyhedron?
-    \item The lemma below might suggest so.  
-      Indeed, if it is, by the Decomposition Theorem, we can write $\cD$ as the Minkowski sum of a polyhedral cone (almost certainly $\cI$) and a convex polytope (what is it?).
-      I am ignoring that it should really be the union of this polyhedron with a plane if the previous sentence holds any water.
-    \item Actually, we might need to take the union of several polyhedra to account for the variations in the fibers $\pi_1^{-1}(\lambda)$.
-  \end{itemize}
-
-  Is the following result true beyond rank 2?
-  \begin{lemma}
-    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
-  \end{lemma}
-  \begin{proof}
-    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_1,\lambda_2)$ where
-    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
-    (This comes from setting $\mu$ to be the vertex opposite $\lambda$ inside the dominance region $\cP(\lambda)$ and then solving for $\lambda$.)
-  \end{proof}
-  \begin{remark}
-    We want to understand what the curve is that results when we have $\mu$ lie along the unit circle, this should be possible by plugging $(\cos(\theta),\sin(\theta))$ into this formula for $\lambda$ and seeing what ellipse we get.
-  \end{remark}
-
-  \begin{thebibliography}{XXX}
-
-    \bibitem{lee-li-zelevinsky}
-      K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014), pp.~57--82.
-
-    \bibitem{rupel}
-      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
-Algebraic Combinatorics, \textbf{2} (2019) no.
-6, pp.~1239--1273.
-\href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
-  \end{thebibliography}
 

### 2022-04-05 dominance_regions.tex
Section 4 edits

--- 2022-04-05 dominance_regions.tex
@@
     \label{le:transformed inequalities}
-    Let $A$ be an invertible $n\times n$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
+    Let $A$ be an invertible $2\times 2$ matrix.
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
   \end{lemma}
@@
   \begin{lemma}
-    \label{le:transformed inequalities}
-    Let $A=(a_{ij})$ be an invertible $2\times 2$ matrix.
-    Under the action of $A$, the region inside $\RR^2$ defined by the inequality $rx+sy\le t$ is transformed to the region defined by the inequality \[\frac{ra_{22}-sa_{21}}{a_{11}a_{22}-a_{12}a_{21}}x + \frac{-ra_{12}+sa_{11}}{a_{11}a_{22}-a_{12}a_{21}}y\le t.\]
-  \end{lemma}
-  \begin{proof}
-    Assume $r,s,t\ne0$, the cases when one of these vanishes follows by the continuity of the transformation.
-    Observe that the points $\big(\frac{t}{r},0\big)$ and $\big(0,\frac{t}{s}\big)$ lie on the boundary line of the region defined by the inequality $rx+sy\le t$.
-    These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
-    By the linearity of the transformation of $\RR^2$ given by the matrix $A$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
-  \end{proof}
-
-  \begin{lemma}
-    For $i\ge1$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+    For $k\ge1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
     \begin{align}
@@
       \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
+    \end{align}
+    \begin{align}
+      \label{ineq:1} u_{k,-}(x-\lambda_1)+u_{k-1,+}(y-\lambda_2) &\le 0;\\
+      \label{ineq:2} u_{k+1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le 0;\\
+      \label{ineq:3} -u_{k-1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1;\\
+      \label{ineq:4} -u_{k-1,-}(x-\lambda_1)-u_{k-2,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1+bu_{k-1,-}\lambda_2.
     \end{align}
@@
 
-    For $i=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
+    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
     \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
-    We inductively compute the region $\phi_{t_{2j}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{t_{2j}}^{-1}=\phi_{t_2}^{-j}$.
-
-    \subsubsection*{Claim:} For $k>0$, $\phi_{t_{2k}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ is the region determined by the inequalities 
+    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
+
+    \subsubsection*{Claim:} For $i>0$, $\phi_{2i}^{-1}\cC_{2j}(\phi_{2j}\lambda)$ is the region determined by the inequalities 
     \begin{align*}
-      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
-      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
+      \tag{a} u_{2i,-}x+u_{2i-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
+      \tag{b} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{c} -u_{2i-1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{d} -u_{2i-1,-}x-u_{2i-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
     \end{align*}
 
-    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$ which corresponds to (a) with $k=1$.
-    Similarly, the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\dagger$) intersects three domains of linearity in which $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $k=1$.
-    This establishes the base of an induction on $k$.
-
-    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
-    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
+    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2$ which corresponds to (a) with $i=1$.
+    Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $i=1$.
+    This establishes the base of an induction on $i$.
+
+    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
+    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
-    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    \[u_{2i+2,-}x+u_{2i+1,+}y=(u_{3,+}u_{2i,-}-u_{2,-}u_{2i-1,+})x+(u_{2,+}u_{2i,-}-u_{1,-}u_{2i-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
+    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
+    \[-u_{2i+1,-}x-u_{2i,+}y=(-u_{3,+}u_{2i-1,-}+u_{2,-}u_{2i-2,+})x+(-u_{2,+}u_{2i-1,-}+u_{1,-}u_{2i-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
     which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (b) for $k+1$.
-    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
+    \[u_{2i+3,-}x+u_{2i+2,+}y=(u_{3,+}u_{2i+1,-}-u_{2,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (b) for $i+1$.
+    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
     Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
-    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
+    \[-u_{2i+1,-}x-u_{2i,+}y=(u_{1,+}u_{2i-1,-}-u_{2,-}u_{2i,+})x+(-u_{0,+}u_{2i-1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
+    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
     Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
-    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    \[-u_{2i+1,-}x+u_{2i+2,+}y=(-u_{1,+}u_{2i+1,-}+u_{0,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
+    \[-u_{2i+1,-}x-u_{2i,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
     which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
-    This completes the induction on $k$, proving the Claim and the result for $i$ even.
-
-    For $i=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)\subset\RR^2$ is given by the inequalities 
+    This completes the induction on $i$, proving the Claim and the result for $k$ even.
+
+    For $k=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
     \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
-    Using that $\phi_{t_{2j+1}}^{-1}=\phi_{t_2}^{-j}\phi_{t_1}^{-1}$, we compute the image inductively as above.
-    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_{t_1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
-    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_{t_1}^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
-    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_{t_1}^{-1}$ and thus produces the inequalities
+    Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
+    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
+    The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
     \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]
 
-    \subsubsection*{Claim:} For $k\ge 0$, $\phi_{t_{2k+1}}^{-1}\cC_{t_{2j+1}}(\phi_{t_{2j+1}}\lambda)$ is the region determined by the inequalities 
+    \subsubsection*{Claim:} For $i\ge 0$, $\phi_{2i+1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
     \begin{align*}
-      \tag{a$'$} u_{2k+1,-}x+u_{2k,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{b$'$} u_{2k+2,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
-      \tag{c$'$} -u_{2k,-}x+u_{2k+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
-      \tag{d$'$} -u_{2k,-}x-u_{2k-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
+      \tag{a$'$} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
+      \tag{b$'$} u_{2i+2,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
+      \tag{c$'$} -u_{2i,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
+      \tag{d$'$} -u_{2i,-}x-u_{2i-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
     \end{align*}
-    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_{t_2}^{-1}$ and this completes the proof.
+    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
   \end{proof}

### 2022-04-06 dominance_regions.tex
Too much time trying to get Lemma 4.1 right, check that I am not being dumb

@@
   Recently Qin introduced the notion of \emph{dominance} and showed that it completely encapsulates the deformability of pointed bases whenever the cluster algebra has full rank \cite{Qin}. 
-  As no explicit calculation is carried out in his work, we aim here at describing explicitly the space of deformability for pointed bases in rank 2, i.e.
+  As no explicit calculation is carried out in his work, we aim here at describing explicitly the space of deformability for pointed bases in rank two, i.e.
 when clusters contain a pair of mutable cluster variables.
@@
 
-  Our goal in this note is to explicitly compute the possible bases which are \emph{pointed} with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
+  Our goal in this note is to explicitly compute the possible bases which are pointed with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
   That is, a basis element with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$ when expanded in terms of $\{x_1,x_2\}$ can be written in the form
-  \[
+  \begin{equation}
+    \label{eq:pointed}
     x_1^{\lambda_1}x_2^{\lambda_2}\sum\limits_{a_1,a_2 \ge 0} c^\lambda_{a_1,a_2} x_1^{-ba_1} x_2^{ca_2}
-  \]
-  with $c^\lambda_{0,0}=1$ and an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
+  \end{equation}
+  with $c^\lambda_{0,0}=1$.
+  Being \emph{pointed} means an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
   %The collection of all $\bfg$-vectors $\lambda\in\ZZ^2$ parametrize the elements of any pointed basis.
@@
   Elements of any pointed basis are parametrized by their $\bfg$-vectors.
-  Qin introduced a partial order on $\bfg$-vectors called the \emph{dominance order} and showed that given two pointed basis $x=\{x_\lambda\}$, $y=\{y_\lambda\}$, $y_\mu$ can appear in the expansion of $x_\lambda$ in terms of $y$ only if $\lambda$ dominates $\mu$ (cf.
+  Qin introduced a partial order on $\bfg$-vectors called the \emph{dominance order} and showed that given two pointed bases $x=\{x_\lambda\}$, $y=\{y_\lambda\}$, $y_\mu$ can appear in the expansion of $x_\lambda$ in terms of $y$ only if $\lambda$ dominates $\mu$ (cf.
 \cite[Mainthm]{Qin} and \ref{below}).
@@
     We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
-    Using the claim for $j>0$ and then the defining recursion twice, we get
+    Using the claim for $\ell>0$ and then the defining recursion twice, we get
     \begin{align*}
@@
 
-  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
+  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_0=0$, $u_1=1$, $u_{i+1}=ru_i-u_{i-1}$, which can be computed explicitly as
   \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
@@
 \section{$\bfg$-vector Mutations}
-  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors under mutations.
+  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors when expanding a pointed expression of the form~\eqref{eq:pointed} in terms of another cluster.
   Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1}:\RR^2\to\RR^2$ as follows:
@@
 
+  Here we explicitly compute the dominance regions $\cP(\lambda)$.
+  When $\lambda$ is not imaginary, the dominance region is particularly simple.
   \begin{lemma}
@@
   \begin{proof}
-    It is enough to consider $\phi_{t_{-2}}^{-1}\cC_{t_{-2}}(\phi_{t_{-2}}\lambda) \cap \cC_{t_0}(\lambda) \cap \phi_{t_2}^{-1}\cC_{t_2}(\phi_{t_2}\lambda)$, we leave the details to the reader.
+    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{a_1}x_{k+1}^{a_2}$.
+    Then $\phi_{k-2}^{-1}\cC_{k-2}(\phi_{k-2}\lambda) \cap \phi_k^{-1}\cC_k(\phi_k\lambda)$ is precisely $\{\lambda\}$. 
+    \sayDR{Check this, I am definitely convinced it works when $k$ is even.}
   \end{proof}

### 2022-04-06 dominance_regions.tex
Small notation change, I like it and I hate it, thoughts?

@@
 
-  Fix integers $b,c>0$.  The cluster algebra $\cA(b,c)$ is the $\ZZ$-subalgebra of $\QQ(x_1,x_2)$ generated by \emph{cluster variables} $x_m$, $m\in\ZZ$, defined recursively by
+  Fix integers $b,c>0$.  The cluster algebra $\cA(b,c)$ is the $\ZZ$-subalgebra of $\QQ(x_0,x_1)$ generated by \emph{cluster variables} $x_m$, $m\in\ZZ$, defined recursively by
   \begin{equation}
-    x_{m-1}x_{m+1}=\begin{cases} x_m^b+1 & \text{if $m$ is odd;}\\ x_m^c+1 & \text{if $m$ is even.} \end{cases}
+    x_{m-1}x_{m+1}=\begin{cases} x_m^b+1 & \text{if $m$ is even;}\\ x_m^c+1 & \text{if $m$ is odd.} \end{cases}
   \end{equation}
@@
   Our goal in this note is to explicitly compute the possible bases which are pointed with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
-  That is, a basis element with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$ when expanded in terms of $\{x_1,x_2\}$ can be written in the form
+  That is, a basis element with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$ when expanded in terms of $\{x_0,x_1\}$ can be written in the form
   \begin{equation}
     \label{eq:pointed}
-    x_1^{\lambda_1}x_2^{\lambda_2}\sum\limits_{a_1,a_2 \ge 0} c^\lambda_{a_1,a_2} x_1^{-ba_1} x_2^{ca_2}
+    x_0^{\lambda_1}x_1^{\lambda_2}\sum\limits_{a_1,a_2 \ge 0} c^\lambda_{a_1,a_2} x_0^{-ba_1} x_1^{ca_2}
   \end{equation}
@@
   Important examples of pointed elements are the \emph{cluster monomials} of $\cA(b,c)$, i.e.
-the elements that can be written in the form $x_k^{a_k}x_{k+1}^{a_{k+1}}$ for some $k\in\ZZ$ and $a_k,a_{k+1}$ non-negative integers.
+the elements that can be written in the form $x_k^{a_1}x_{k+1}^{a_2}$ for some $k\in\ZZ$ and $a_1,a_2$ non-negative integers.
   Indeed, by [someresult of Qin] cluster monomials are part of any pointed basis in any cluster algebra.
@@
   It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
-  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications with the subalgebras of $\ZZ[x_1^{\pm1},x_2^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
+  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications with the subalgebras of $\ZZ[x_0^{\pm1},x_1^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
   However, these bases depend on $k$ and the triangular basis is defined by a triangular transition with the stipulation that the basis does not depend on the choice of starting cluster.
@@
 
-  Given a Laurent polynomial in $\ZZ[x_1^{\pm1},x_2^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
+  Given a Laurent polynomial in $\ZZ[x_0^{\pm1},x_1^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
   \begin{theorem}
@@
 \section{$\bfg$-vector Mutations}
-  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors when expanding a pointed expression of the form~\eqref{eq:pointed} in terms of another cluster.
+  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors when expanding a pointed expression of the form~\eqref{eq:pointed} in terms of a cluster $\{x_k,x_{k+1}\}$.
   Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1}:\RR^2\to\RR^2$ as follows:
@@
 
-  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k>0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
+  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $n>0$, there exists a scalar $\nu_n$ so that $\phi^n(\lambda)=\nu_n\lambda$.
   \begin{lemma}
@@
   \begin{proof}
-    First observe that the equation $\phi_2^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k>0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
+    First observe that the equation $\phi_2^n(\lambda)=\nu_n\lambda$ cannot be satisfied for all $n>0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
     In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
@@
     Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{a_1}x_{k+1}^{a_2}$.
-    Then $\phi_{k-2}^{-1}\cC_{k-2}(\phi_{k-2}\lambda) \cap \phi_k^{-1}\cC_k(\phi_k\lambda)$ is precisely $\{\lambda\}$. 
-    \sayDR{Check this, I am definitely convinced it works when $k$ is even.}
+    Then $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ is precisely $\{\lambda\}$. 
+    \sayDR{Check this, I am definitely convinced it works when $k$ is odd.}
   \end{proof}

### 2022-04-06 dominance_regions.tex
Section 4 edits, cluster monomial proof is finished

@@
   \end{proof}
-
-  \begin{lemma}
-    \label{le:one direction}
-    For $\lambda\in\cI\cap\ZZ^2$, 
-    \begin{enumerate}
-      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
-      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
-    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
-  \end{proof}
+  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
+  \begin{itemize}
+    \item if $\lambda_1 \le 0$ and $\lambda_2 \ge 0$, the second and fourth inequalities become equations for lines which intersect at $\lambda$;
+    \item if $\lambda_1 > 0$ and $\lambda_2 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_1$, the first and second inequalities become equations for lines which intersect at $\lambda$;
+    \item if $\lambda_2 < 0$ and $\lambda_1 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_2$, the third and fourth inequalities become equations for lines which intersect at $\lambda$.
+  \end{itemize}
+  This proves Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.
 
@@
     By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
+  \end{proof}
+
+  \begin{lemma}
+    \label{le:one direction}
+    For $\lambda\in\cI\cap\ZZ^2$, 
+    \begin{enumerate}
+      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
+      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
+    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
   \end{proof}

### 2022-04-06 dominance_regions.tex
figures

--- 2022-04-06 dominance_regions.tex
@@
       \tikzmath{ \t=3; \r=1; \s=1; \xx = \r; \yy=\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x,\y) circle (6pt);
+      \fill (\x,\y) circle (5pt);
     \end{scope}
@@
       \tikzmath{ \t=5; \r=2; \s=1; \xx = \r + \b*\s; \yy=-\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x, \y) circle (6pt);
-      \draw [very thick, join=round] (\x, \y) -- ({\x+\b * \y},\y);
+      \fill (\x, \y) circle (5pt);
+      \draw [thick, join=round] (\x, \y) -- ({\x+\b * \y},\y);
+      \draw [thick, fill=white] ({\x+\b * \y},\y) circle (5pt);
     \end{scope}
@@
       \tikzmath{ \t=3; \r=1; \s=1; \xx=-\r; \yy=\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x, \y) circle (6pt);
-      \draw [very thick, join=round] (\x, \y) -- (\x,{\y - \c * \x});
+      \fill (\x, \y) circle (5pt);
+      \draw [thick, join=round] (\x, \y) -- (\x,{\y - \c * \x});
+      \draw [thick, fill=white] (\x,{\y - \c * \x}) circle (5pt);
     \end{scope}
@@
       \tikzmath{ \t=1; \r=1; \s=1; \xx=-\r; \yy=-\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x, \y) circle (6pt);
-%      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
-      \draw [very thick, join=round] (\x, \y) -- ({\x + \b * \y}, \y) -- ({\x + \b * \y}, {\y -\c*(\x + \b * \y)}) -- (\x, {\y - \c*\x}) -- cycle;
+      \fill (\x, \y) circle (5pt);
+      \draw [thick, join=round] (\x, \y) -- ({\x + \b * \y}, \y) -- ({\x + \b * \y}, {\y -\c*(\x + \b * \y)}) -- (\x, {\y - \c*\x}) -- cycle;
+      \draw [thick, fill=white] ({\x + \b * \y}, {\y -\c*(\x + \b * \y)})  circle (5pt);
     \end{scope}
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \s=1; \xx={\r*\b+\s*(\b*\c-1) }; \yy = {-\r -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x,\y) circle (6pt);
-      \draw [very thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
+      \tikzmath{ \t=5; \r=1; \s=2; \xx={\r*\b+\s*(\b*\c-1) }; \yy = {-\r -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \fill (\x,\y) circle (5pt);
+      \draw [thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
+      \draw [dashed, thick]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) -- (\x,\y);
+      \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
     \end{scope}
@@
       \tikzmath{ \t=5; \r=1; \s=2; \xx={2*\r*\b+\s*(\b*\c-1) }; \yy = {-\r*\bcms -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x,\y) circle (6pt);
-      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
-      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
-      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
+      \fill (\x,\y) circle (5pt);
+      %\fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
+      \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);
+      \draw [thick, dash dot, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
     \end{scope}
@@
       \tikzmath{ \t=2; \r=0.3; \s=1; \xx={2*\r*\b }; \yy = {-\r*\bcps -\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x,\y) circle (6pt);
-      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
-      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
-      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
+      \fill (\x,\y) circle (5pt);
+      %\fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
+      \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);
+      \draw [thick, dash dot, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
     \end{scope}
@@
       \tikzmath{ \t=5; \r=1; \s=2; \xx={2*(\r+\s)*\b }; \yy = {-\r*\bcps -\s*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
-      \fill (\x , \y)  circle (6pt);
-      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
-      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dotted] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
-      \draw [very thick, dotted, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
-      \draw [very thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \fill (\x , \y)  circle (5pt);
+      %\fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
+      \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
+      \draw [thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
+      \draw [thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
     \end{scope}

### 2022-04-06 dominance_regions.tex
More details in the proof of Lemma 4.1

@@
     Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{a_1}x_{k+1}^{a_2}$.
-    Then $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ is precisely $\{\lambda\}$. 
-    \sayDR{Check this, I am definitely convinced it works when $k$ is odd.}
+    In this case the intersection
+    \[\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)\]
+    is precisely $\{\lambda\}$. 
+    Indeed, when $k$ is odd (resp.
+even) the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ (resp.
+$\cC_{k+1}(\phi_{k+1}\lambda)$) lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$ (resp.
+$\phi_{k+1}^{-1}$).
+    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ (resp.
+$\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$) is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
+    On the contrary, when $k$ is odd (resp.
+even) the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ (resp.
+$\cC_{k-1}(\phi_{k-1}\lambda)$) intersects the domain of linearity for $\phi_{k+1}^{-1}$ (resp.
+$\phi_{k-1}^{-1}$) containing $\phi_{k+1}\lambda$ (resp.
+$\phi_{k-1}\lambda$) in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$ (resp.
+$\phi_{k-1}\lambda$).
+    In particular, $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ (resp.
+$\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$) is a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\lambda$.
+    The result follows.
   \end{proof}

### 2022-04-06 dominance_regions.tex
I don't hate starting at 0

@@
   Our goal in this note is to explicitly compute the possible bases which are pointed with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
-  That is, a basis element with \emph{$\bfg$-vector} $\lambda\in\ZZ^2$ when expanded in terms of $\{x_0,x_1\}$ can be written in the form
+  That is, a basis element with \emph{$\bfg$-vector} $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ when expanded in terms of $\{x_0,x_1\}$ can be written in the form
   \begin{equation}
     \label{eq:pointed}
-    x_0^{\lambda_1}x_1^{\lambda_2}\sum\limits_{a_1,a_2 \ge 0} c^\lambda_{a_1,a_2} x_0^{-ba_1} x_1^{ca_2}
+    x_0^{\lambda_0}x_1^{\lambda_1}\sum\limits_{a_0,a_1 \ge 0} c^\lambda_{a_0,a_1} x_0^{-ba_0} x_1^{ca_1}
   \end{equation}
@@
     is precisely $\{\lambda\}$. 
-    Indeed, when $k$ is odd (resp.
-even) the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ (resp.
-$\cC_{k+1}(\phi_{k+1}\lambda)$) lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$ (resp.
-$\phi_{k+1}^{-1}$).
-    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ (resp.
-$\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$) is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
-    On the contrary, when $k$ is odd (resp.
-even) the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ (resp.
-$\cC_{k-1}(\phi_{k-1}\lambda)$) intersects the domain of linearity for $\phi_{k+1}^{-1}$ (resp.
-$\phi_{k-1}^{-1}$) containing $\phi_{k+1}\lambda$ (resp.
+    Indeed, when $k$ is odd the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
+    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
+    On the contrary, when $k$ is odd the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ (resp.
 $\phi_{k-1}\lambda$) in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$ (resp.

### 2022-04-07 dominance_regions.tex
Small notation changes, some section 4 edits

@@
   Important examples of pointed elements are the \emph{cluster monomials} of $\cA(b,c)$, i.e.
-the elements that can be written in the form $x_k^{a_1}x_{k+1}^{a_2}$ for some $k\in\ZZ$ and $a_1,a_2$ non-negative integers.
+the elements that can be written in the form $x_k^{a_k}x_{k+1}^{a_{k+1}}$ for some $k\in\ZZ$ and $a_k,a_{k+1}$ non-negative integers.
   Indeed, by [someresult of Qin] cluster monomials are part of any pointed basis in any cluster algebra.
@@
   In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
-  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$, $a_1,a_2\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b a_0 ,c a_1)$, $a_0,a_1\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
   %In this case, we compute the possible transitions between any two pointed bases.
@@
   \begin{proof}
-    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{a_1}x_{k+1}^{a_2}$.
+    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{a_k}x_{k+1}^{a_{k+1}}$.
     In this case the intersection
@@
     \begin{align}
-      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
-      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
-      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
-    \end{align}
-    \begin{align}
-      \label{ineq:1} u_{k,-}(x-\lambda_1)+u_{k-1,+}(y-\lambda_2) &\le 0;\\
-      \label{ineq:2} u_{k+1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le 0;\\
-      \label{ineq:3} -u_{k-1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1;\\
-      \label{ineq:4} -u_{k-1,-}(x-\lambda_1)-u_{k-2,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1+bu_{k-1,-}\lambda_2.
+      \label{ineq:1} u_{k,-}x+u_{k-1,+}y &\le u_{k,-}\lambda_1+u_{k-1,+}\lambda_2;\\
+      \label{ineq:2} u_{k+1,-}x+u_{k,+}y &\le u_{k+1,-}\lambda_1+u_{k,+}\lambda_2;\\
+      \label{ineq:3} -u_{k-1,-}x+u_{k,+}y &\le u_{k+1,-}\lambda_1+u_{k,+}\lambda_2;\\
+      \label{ineq:4} -u_{k-1,-}x-u_{k-2,+}y &\le u_{k+1,-}\lambda_1+u_{k,+}\lambda_2.
     \end{align}
@@
     For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ x - u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \le 0 \qquad\text{and}\qquad 0 \le y + u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
+    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
+    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
+
+    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
     \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
@@
   \end{proof}
+  The following consequence is easily seen from the Chebyshev recursion.
+  \begin{corollary}
+    \begin{align*}
+      u_{k,-}(x-\lambda_1)+u_{k-1,+}(y-\lambda_2) &\le 0;\\
+      u_{k+1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le 0;\\
+      -u_{k-1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1;\\
+      -u_{k-1,-}(x-\lambda_1)-u_{k-2,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1+bu_{k-1,-}\lambda_2.
+    \end{align*}
+  \end{corollary}
 

### 2022-04-07 dominance_regions.tex
Monotonicity

@@
     \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+    Moreover, each of these sequences is monotonic.
   \end{lemma}
@@
     which is again equivalent to the desired expression.
+
+    For the final claim, observe that $\frac{-u_{i,-\varepsilon}}{u_{i-1,\varepsilon}}<\frac{-u_{i+1,-\varepsilon}}{u_{i,\varepsilon}}$ and $\frac{-u_{i,-\varepsilon}}{u_{i+1,\varepsilon}}<\frac{-u_{i-1,-\varepsilon}}{u_{i,\varepsilon}}$ are both equivalent to $u_{i+1,-\varepsilon}u_{i-1,\varepsilon}<u_{i,-\varepsilon}u_{i,\varepsilon}$.
+    This is immediate from the following induction:
+    \begin{align*}
+      u_{i+1,-\varepsilon}u_{i-1,\varepsilon}
+      &=(cu_{i,\varepsilon}-u_{i-1,-\varepsilon})u_{i-1,\varepsilon}
+      =cu_{i,\varepsilon}u_{i-1,\varepsilon}-u_{i-1,-\varepsilon}u_{i-1,\varepsilon}\\
+      &<cu_{i,\varepsilon}u_{i-1,\varepsilon}-u_{i,\varepsilon}u_{i-2,-\varepsilon}
+      =u_{i,\varepsilon}(cu_{i-1,\varepsilon}-u_{i-2,-\varepsilon})\\
+      &=u_{i,\varepsilon}u_{i,-\varepsilon}.
+    \end{align*}
   \end{proof}

### 2022-04-07 dominance_regions.tex
Monotonicity

@@
     Let $A$ be an invertible $2\times 2$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet\bfx \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet\bfy\le t.\]
   \end{lemma}
@@
     This is immediate from the equalities
-    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
+    \[\bfr\bullet\bfx=\bfr^T\bfx=\bfr^TA^{-1}A\bfx=(A^{-T}\bfr)^TA\bfx=(A^{-T}\bfr)\bullet\bfy.\]
   \end{proof}

### 2022-04-07 dominance_regions.tex
Some section 4 edits

@@
     For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ x - u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \le 0 \qquad\text{and}\qquad 0 \le y + u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
-    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
-    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
-
-    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
     \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
@@
 
-    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
+    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
     Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
@@
     \[-u_{2i+1,-}x-u_{2i,+}y=(-u_{3,+}u_{2i-1,-}+u_{2,-}u_{2i-2,+})x+(-u_{2,+}u_{2i-1,-}+u_{1,-}u_{2i-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
-    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
+    which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
     \[u_{2i+3,-}x+u_{2i+2,+}y=(u_{3,+}u_{2i+1,-}-u_{2,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]

### 2022-04-07 dominance_regions.tex
mu's in Theorem 1.1

@@
     \label{th:dominance inequalities}
-    The dominance polygon $\cP(\lambda)$ pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
+    The dominance polygon $\cP(\lambda)$ pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_1 \leq \lambda_1, \mu_2 \geq\lambda_2$, and the following inequalities:
     {
@@
         \begin{array}{rcccl}
-          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
+          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_1-\lambda_1)+(\mu_2-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
           \\
-          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
+          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_1-\lambda_1)-(\mu_2-\lambda_2) & \leq & 0
           \\
-          0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
+          0 & \leq &  -(\mu_1-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_2-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
           \\
-          \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
+          \min\left(b \lambda_2,0\right) & \leq & (\mu_1-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_2-\lambda_2) & \leq & 0
         \end{array}

### 2022-04-07 dominance_regions.tex
Lots of symbols
another way
superscripts

@@
     \label{eq:pointed}
-    x_0^{\lambda_0}x_1^{\lambda_1}\sum\limits_{a_0,a_1 \ge 0} c^\lambda_{a_0,a_1} x_0^{-ba_0} x_1^{ca_1}
+    x_0^{\lambda_0}x_1^{\lambda_1}\sum\limits_{\alpha_0,\alpha_1 \ge 0} \rho_{\alpha_0,\alpha_1} x_0^{-b\alpha_0} x_1^{c\alpha_1}
   \end{equation}
-  with $c^\lambda_{0,0}=1$.
+  with $c_{0,0}=1$.
   Being \emph{pointed} means an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
@@
   \label{sec:chebyshev}
-  Define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
-  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
-  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.
+  Define \emph{two-parameter Chebyshev polynomials} $u_i^\varepsilon$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
+  \[u_0^\varepsilon=0,\quad u_1^\varepsilon=1,\quad u_{i+1}^\varepsilon=\begin{cases} bu_i^{-\varepsilon}-u_{i-1}^\varepsilon & \text{if $\varepsilon=+$;}\\ cu_i^{-\varepsilon}-u_{i-1}^\varepsilon & \text{if $\varepsilon=-$.} \end{cases}\]
+    Observe that, by an easy induction, $u_{-i}^\varepsilon=-u_i^\varepsilon$.
 

### 2022-04-07 dominance_regions.tex
More superscripts

@@
   Define \emph{two-parameter Chebyshev polynomials} $u_i^\varepsilon$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
-  \[u_0^\varepsilon=0,\quad u_1^\varepsilon=1,\quad u_{i+1}^\varepsilon=\begin{cases} bu_i^{-\varepsilon}-u_{i-1}^\varepsilon & \text{if $\varepsilon=+$;}\\ cu_i^{-\varepsilon}-u_{i-1}^\varepsilon & \text{if $\varepsilon=-$.} \end{cases}\]
+  \[u_0^\varepsilon=0,\quad u_1^\varepsilon=1,\quad u_{i+1}^\varepsilon=\begin{cases} bu_i^- -u_{i-1}^+ & \text{if $\varepsilon=+$;}\\ cu_i^+-u_{i-1}^- & \text{if $\varepsilon=-$.} \end{cases}\]
     Observe that, by an easy induction, $u_{-i}^\varepsilon=-u_i^\varepsilon$.
@@
       u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
+    \end{equation}
+    \begin{equation}
+      \label{eq:long Chebyshev recursion}
+      u_{i+\ell}^\varepsilon=\begin{cases} u_{\ell+1}^\varepsilon u_i^{-\varepsilon}-u_\ell^{-\varepsilon} u_{i-1}^\varepsilon & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1}^{-\varepsilon} u_i^\varepsilon-u_\ell^\varepsilon u_{i-1}^{-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
     \end{equation}

### 2022-04-07 dominance_regions.tex
More superscripts

@@
 
-  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
+  The recursion can be written more succinctly as $u_{i+1}^\varepsilon=u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon$ with the additional initial condition $u_2^\varepsilon=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
   This leads to the following more general recursive structure.
@@
     For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
-    \begin{equation}
-      \label{eq:long Chebyshev recursion}
-      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
-    \end{equation}
     \begin{equation}
@@
     \begin{align*}
-      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
-      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
+      u_{i+\ell+1}^\varepsilon
+      &=
+      \begin{cases} 
+        u_{\ell+1}^\varepsilon u_{i+1}^{-\varepsilon}-u_\ell^{-\varepsilon} u_i^\varepsilon & \text{if $\ell$ is odd;}\\
+        u_{\ell+1}^{-\varepsilon} u_{i+1}^\varepsilon-u_\ell^\varepsilon u_i^{-\varepsilon} & \text{if $\ell$ is even;} 
+      \end{cases}\\
+      &=
+      \begin{cases} 
+        (u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon} & \text{if $\ell$ is odd;}\\ 
+        (u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon & \text{if $\ell$ is even;}
+      \end{cases}\\
+      &=
+      \begin{cases}
+        u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon} & \text{if $\ell+1$ is even;}\\ 
+        u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon & \text{if $\ell+1$ is odd;}
+      \end{cases}
     \end{align*}

### 2022-04-07 dominance_regions.tex
Proof of Lemma 2.1

@@
       &=
-      \begin{cases} 
-        u_{\ell+1}^\varepsilon u_{i+1}^{-\varepsilon}-u_\ell^{-\varepsilon} u_i^\varepsilon & \text{if $\ell$ is odd;}\\
-        u_{\ell+1}^{-\varepsilon} u_{i+1}^\varepsilon-u_\ell^\varepsilon u_i^{-\varepsilon} & \text{if $\ell$ is even;} 
-      \end{cases}\\
+      u_{\ell+1}^\varepsilon u_{i+1}^{-\varepsilon}-u_\ell^{-\varepsilon} u_i^\varepsilon
+      =(u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
+      =u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
+      \qquad \text{if $\ell$ is odd;}\\ 
+      u_{i+\ell+1}^\varepsilon
       &=
-      \begin{cases} 
-        (u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon} & \text{if $\ell$ is odd;}\\ 
-        (u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon & \text{if $\ell$ is even;}
-      \end{cases}\\
-      &=
-      \begin{cases}
-        u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon} & \text{if $\ell+1$ is even;}\\ 
-        u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon & \text{if $\ell+1$ is odd;}
-      \end{cases}
+      u_{\ell+1}^{-\varepsilon} u_{i+1}^\varepsilon-u_\ell^\varepsilon u_i^{-\varepsilon}
+      =(u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon
+      =u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon
+      \qquad \text{if $\ell$ is even;} 
     \end{align*}
-    which is the claimed recursion for $\ell+1$.
+    which gives the claimed recursion for $\ell+1$.
     These calculations can be reversed to show the result for $\ell<0$.

### 2022-04-07 dominance_regions.tex
Section 2 superscripts

@@
   By the equalities 
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
-  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
-  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+  \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
+  it follows that $u_i^\varepsilon$ can be computed explicitly as
+  \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
   \begin{remark}
-    Note that $u_{2j+1,+}=u_{2j+1,-}$ for all $j\in\ZZ$.
-    Moreover, since $u_{-i,\varepsilon}=-u_{i,\varepsilon}$, these formulas can also easily be seen to hold for $i<0$.
+    Note that $u_{2j+1}^+=u_{2j+1}^-$ for all $j\in\ZZ$.
+    Moreover, since $u_{-i}^\varepsilon=-u_i^\varepsilon$, these formulas can also easily be seen to hold for $i<0$.
   \end{remark}
@@
     We have
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
     Moreover, each of these sequences is monotonic.
@@
     It follows that
-    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
     which is equivalent to the desired expression.
@@
     so that
-    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    \[\lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
     which is again equivalent to the desired expression.
 
-    For the final claim, observe that $\frac{-u_{i,-\varepsilon}}{u_{i-1,\varepsilon}}<\frac{-u_{i+1,-\varepsilon}}{u_{i,\varepsilon}}$ and $\frac{-u_{i,-\varepsilon}}{u_{i+1,\varepsilon}}<\frac{-u_{i-1,-\varepsilon}}{u_{i,\varepsilon}}$ are both equivalent to $u_{i+1,-\varepsilon}u_{i-1,\varepsilon}<u_{i,-\varepsilon}u_{i,\varepsilon}$.
+    For the final claim, observe that $\frac{-u_i^{-\varepsilon}}{u_{i-1}^\varepsilon}<\frac{-u_{i+1}^{-\varepsilon}}{u_i^\varepsilon}$ and $\frac{-u_i^{-\varepsilon}}{u_{i+1}^\varepsilon}<\frac{-u_{i-1}^{-\varepsilon}}{u_i^\varepsilon}$ are both equivalent to $u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon<u_i^{-\varepsilon}u_i^\varepsilon$.
     This is immediate from the following induction:
     \begin{align*}
-      u_{i+1,-\varepsilon}u_{i-1,\varepsilon}
-      &=(cu_{i,\varepsilon}-u_{i-1,-\varepsilon})u_{i-1,\varepsilon}
-      =cu_{i,\varepsilon}u_{i-1,\varepsilon}-u_{i-1,-\varepsilon}u_{i-1,\varepsilon}\\
-      &<cu_{i,\varepsilon}u_{i-1,\varepsilon}-u_{i,\varepsilon}u_{i-2,-\varepsilon}
-      =u_{i,\varepsilon}(cu_{i-1,\varepsilon}-u_{i-2,-\varepsilon})\\
-      &=u_{i,\varepsilon}u_{i,-\varepsilon}.
+      u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon
+      &=(cu_i^\varepsilon-u_{i-1}^{-\varepsilon})u_{i-1}^\varepsilon
+      =cu_i^\varepsilon u_{i-1}^\varepsilon-u_{i-1}^{-\varepsilon} u_{i-1}^\varepsilon\\
+      &<cu_i^\varepsilon u_{i-1}^\varepsilon-u_i^\varepsilon u_{i-2}^{-\varepsilon}
+      =u_i^\varepsilon(cu_{i-1}^\varepsilon-u_{i-2}^{-\varepsilon})\\
+      &=u_i^\varepsilon u_i^{-\varepsilon}.
     \end{align*}

### 2022-04-07 dominance_regions.tex
Lemma 2.3 proof edit
lambda0

@@
     \label{th:dominance inequalities}
-    The dominance polygon $\cP(\lambda)$ pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_1 \leq \lambda_1, \mu_2 \geq\lambda_2$, and the following inequalities:
+    The dominance polygon $\cP(\lambda)$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
     {
@@
         \begin{array}{rcccl}
-          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_1-\lambda_1)+(\mu_2-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
+          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \leq & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
           \\
-          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_1-\lambda_1)-(\mu_2-\lambda_2) & \leq & 0
+          \min\left(-c\lambda_0,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & 0
           \\
-          0 & \leq &  -(\mu_1-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_2-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
+          0 & \leq &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
           \\
-          \min\left(b \lambda_2,0\right) & \leq & (\mu_1-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_2-\lambda_2) & \leq & 0
+          \min\left(b \lambda_1,0\right) & \leq & (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \leq & 0
         \end{array}
@@
       \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
       \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
       \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
     \end{enumerate}
@@
     \label{th:maximum support}
-    For a $\bfg$-vector $\lambda=(\lambda_1,\lambda_2)\in\ZZ^2$ the support for a pointed basis vector $x_\lambda$ is contained in the (possibly degenerate) lattice quadrilateral $\cS_\lambda$ given as follows:
+    For a $\bfg$-vector $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ the support for a pointed basis vector $x_\lambda$ is contained in the (possibly degenerate) lattice quadrilateral $\cS_\lambda$ given as follows:
     \begin{enumerate}
@@
         \begin{enumerate}
-          \item If $0\le\lambda_1,\lambda_2$, then $\cS_\lambda$ is just the point $\lambda$.
-          \item If $\lambda_2 < 0$ and $0\le\lambda_1+b\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1+b\lambda_2,\lambda_2)$.
-          \item If $\lambda_1 < 0$ and $0\le\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1,-c\lambda_1+\lambda_2)$.
-          \item If $\lambda_1,\lambda_2 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(\lambda_1,-c\lambda_1+\lambda_2)$.
-          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc+1)\lambda_1-b^2c\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
-          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $0 < -c\lambda_1-(bc-1)\lambda_2$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(0,0)$.
-        \end{enumerate}
-      \item If $\lambda$ lies inside of $\cI$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
+          \item If $0\le\lambda_0,\lambda_1$, then $\cS_\lambda$ is just the point $\lambda$.
+          \item If $\lambda_1 < 0$ and $0\le\lambda_0+b\lambda_1$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_0+b\lambda_1,\lambda_1)$.
+          \item If $\lambda_0 < 0$ and $0\le\lambda_1$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_0,-c\lambda_0+\lambda_1)$.
+          \item If $\lambda_0,\lambda_1 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $(\lambda_0,-c\lambda_0+\lambda_1)$.
+          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $-c\lambda_0-(bc-1)\lambda_1\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\big((bc+1)\lambda_0-b^2c\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$.
+          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $0 < -c\lambda_0-(bc-1)\lambda_1$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $(0,0)$.
+        \end{enumerate}
+      \item If $\lambda$ lies inside of $\cI$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
     \end{enumerate}
@@
       u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon
-      &=(cu_i^\varepsilon-u_{i-1}^{-\varepsilon})u_{i-1}^\varepsilon
-      =cu_i^\varepsilon u_{i-1}^\varepsilon-u_{i-1}^{-\varepsilon} u_{i-1}^\varepsilon\\
-      &<cu_i^\varepsilon u_{i-1}^\varepsilon-u_i^\varepsilon u_{i-2}^{-\varepsilon}
-      =u_i^\varepsilon(cu_{i-1}^\varepsilon-u_{i-2}^{-\varepsilon})\\
-      &=u_i^\varepsilon u_i^{-\varepsilon}.
+      =(cu_i^\varepsilon-u_{i-1}^{-\varepsilon})u_{i-1}^\varepsilon
+      =cu_i^\varepsilon u_{i-1}^\varepsilon-u_{i-1}^{-\varepsilon} u_{i-1}^\varepsilon
+      <cu_i^\varepsilon u_{i-1}^\varepsilon-u_i^\varepsilon u_{i-2}^{-\varepsilon}
+      =u_i^\varepsilon(cu_{i-1}^\varepsilon-u_{i-2}^{-\varepsilon})
+      =u_i^\varepsilon u_i^{-\varepsilon}.
     \end{align*}
@@
     \begin{cases} 
-      (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1 \ge 0$;}\\
-      (-\lambda_1,\lambda_2) & \text{if $\lambda_1 < 0$;}
+      (-\lambda_0,c\lambda_0+\lambda_1) & \text{if $\lambda_0 \ge 0$;}\\
+      (-\lambda_0,\lambda_1) & \text{if $\lambda_0 < 0$;}
     \end{cases}
@@
     \begin{cases} 
-      (\lambda_1,-\lambda_2) & \text{if $\lambda_2 \ge 0$;}\\
-      (\lambda_1+b\lambda_2,-\lambda_2) & \text{if $\lambda_2 < 0$.}
+      (\lambda_0,-\lambda_1) & \text{if $\lambda_1 \ge 0$;}\\
+      (\lambda_0+b\lambda_1,-\lambda_1) & \text{if $\lambda_1 < 0$.}
     \end{cases}
@@
       \begin{cases}
-        \{(\lambda_1-r,\lambda_2+s):r,s\in\RR_{\ge0}\} & \text{if $k=2j$;}\\
-        \{(\lambda_1+r,\lambda_2-s):r,s\in\RR_{\ge0}\} & \text{if $k=2j+1$.}
+        \{(\lambda_0-r,\lambda_1+s):r,s\in\RR_{\ge0}\} & \text{if $k=2j$;}\\
+        \{(\lambda_0+r,\lambda_1-s):r,s\in\RR_{\ge0}\} & \text{if $k=2j+1$.}
       \end{cases}
@@
     \begin{cases}
-      \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\
-      (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\
-      (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\
-      (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}
+      \big((bc-1)\lambda_0+b\lambda_1, -c\lambda_0-\lambda_1\big) & \text{if $\lambda_0\ge 0$ and $c\lambda_0+\lambda_1\ge 0$;}\\
+      (-\lambda_0, -c\lambda_0-\lambda_1) & \text{if $\lambda_0\ge 0$ and $c\lambda_0+\lambda_1<0$;}\\
+      (-\lambda_0+b\lambda_1, -\lambda_1) & \text{if $\lambda_0<0$ and $\lambda_1\ge 0$;}\\
+      (-\lambda_0,-\lambda_1) & \text{if $\lambda_0<0$ and $\lambda_1<0$;}
     \end{cases}
@@
   %  \begin{cases}
-  %    \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\
-  %    (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\
-  %    (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\
-  %    (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$.}
+  %    \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
+  %    (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
+  %    (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
+  %    (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
   %  \end{cases}
@@
   \begin{proof}
-    First observe that the equation $\phi_2^n(\lambda)=\nu_n\lambda$ cannot be satisfied for all $n>0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
+    First observe that the equation $\phi_2^n(\lambda)=\nu_n\lambda$ cannot be satisfied for all $n>0$ unless $\lambda_0\ge 0$ and $c\lambda_0+\lambda_1\ge 0$.
     In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
     We thus require 
-    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
+    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_0=(bc-1)\lambda_0+b\lambda_1 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1= -c\lambda_0-\lambda_1,\]
     or equivalently
-    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
+    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_0=\lambda_1 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_1=\lambda_0.\]
     As these represent the same relationship, the result immediately follows by inspection.
@@
     The claim is immediate for $\phi_2$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_2$ is linear in $\cI$.
-    Now, since $b>0$, we have $\phi_1(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$.
+    Now, since $b>0$, we have $\phi_1(\lambda)=(-\lambda_0,c\lambda_0+\lambda_1)$.
     It follows that $\phi_1\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$.
@@
     \begin{align*}
-      \phi_{2j}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
-      \phi_{2j+1}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
+      \phi_{2j}(\lambda)&=(u_{2j+1,+}\lambda_0+u_{2j,+}\lambda_1,-u_{2j,-}\lambda_0-u_{2j-1,-}\lambda_1);\\
+      \phi_{2j+1}(\lambda)&=(-u_{2j+1,+}\lambda_0-u_{2j,+}\lambda_1,u_{2j+2,-}\lambda_0+u_{2j+1,-}\lambda_1).
     \end{align*}
@@
     For $\lambda\in\cI$, the action of $\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
-    \[\phi_2(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2).\]
+    \[\phi_2(\lambda)=(u_{3,-}\lambda_0+u_{2,+}\lambda_1,-u_{2,-}\lambda_0-u_{1,+}\lambda_1).\]
     Therefore
@@
       \phi_{2j+2}(\lambda)&=\phi_2\phi_{2j}(\lambda)\\
-      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
-      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
-      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
+      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_0+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_1,\\
+      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_0-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_1 \big)\\
+      &=(u_{2j+3,+}\lambda_0+u_{2j+2,+}\lambda_1, -u_{2j+2,-}\lambda_0-u_{2j+1,-}\lambda_1),
     \end{align*}
@@
 
-    Similarly, using $\phi_1(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$ together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
+    Similarly, using $\phi_1(\lambda)=(-\lambda_0,u_{2,-}\lambda_0+u_{1,+}\lambda_1)$ for $\lambda\in\cI$ together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
   \end{proof}
@@
   \begin{itemize}
-    \item if $\lambda_1 \le 0$ and $\lambda_2 \ge 0$, the second and fourth inequalities become equations for lines which intersect at $\lambda$;
-    \item if $\lambda_1 > 0$ and $\lambda_2 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_1$, the first and second inequalities become equations for lines which intersect at $\lambda$;
-    \item if $\lambda_2 < 0$ and $\lambda_1 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_2$, the third and fourth inequalities become equations for lines which intersect at $\lambda$.
+    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth inequalities become equations for lines which intersect at $\lambda$;
+    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second inequalities become equations for lines which intersect at $\lambda$;
+    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth inequalities become equations for lines which intersect at $\lambda$.
   \end{itemize}
@@
     \begin{align}
-      \label{ineq:1} u_{k,-}x+u_{k-1,+}y &\le u_{k,-}\lambda_1+u_{k-1,+}\lambda_2;\\
-      \label{ineq:2} u_{k+1,-}x+u_{k,+}y &\le u_{k+1,-}\lambda_1+u_{k,+}\lambda_2;\\
-      \label{ineq:3} -u_{k-1,-}x+u_{k,+}y &\le u_{k+1,-}\lambda_1+u_{k,+}\lambda_2;\\
-      \label{ineq:4} -u_{k-1,-}x-u_{k-2,+}y &\le u_{k+1,-}\lambda_1+u_{k,+}\lambda_2.
+      \label{ineq:1} u_{k,-}x+u_{k-1,+}y &\le u_{k,-}\lambda_0+u_{k-1,+}\lambda_1;\\
+      \label{ineq:2} u_{k+1,-}x+u_{k,+}y &\le u_{k+1,-}\lambda_0+u_{k,+}\lambda_1;\\
+      \label{ineq:3} -u_{k-1,-}x+u_{k,+}y &\le u_{k+1,-}\lambda_0+u_{k,+}\lambda_1;\\
+      \label{ineq:4} -u_{k-1,-}x-u_{k-2,+}y &\le u_{k+1,-}\lambda_0+u_{k,+}\lambda_1.
     \end{align}
@@
     For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
+    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_0+u_{2j,+}\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_0+u_{2j-1,-}\lambda_1. \]
     We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
@@
     \begin{align*}
-      \tag{a} u_{2i,-}x+u_{2i-1,+}y &\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2;\\
-      \tag{b} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{c} -u_{2i-1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{d} -u_{2i-1,-}x-u_{2i-2,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2.
+      \tag{a} u_{2i,-}x+u_{2i-1,+}y &\le u_{2j,-}\lambda_0+u_{2j-1,+}\lambda_1;\\
+      \tag{b} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1;\\
+      \tag{c} -u_{2i-1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1;\\
+      \tag{d} -u_{2i-1,-}x-u_{2i-2,+}y &\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1.
     \end{align*}
@@
     We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2$ which corresponds to (a) with $i=1$.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{2j,-}\lambda_0+u_{2j-1,+}\lambda_1$ which corresponds to (a) with $i=1$.
     Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-    \[u_{2i+2,-}x+u_{2i+1,+}y=(u_{3,+}u_{2i,-}-u_{2,-}u_{2i-1,+})x+(u_{2,+}u_{2i,-}-u_{1,-}u_{2i-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
+    \[u_{2i+2,-}x+u_{2i+1,+}y=(u_{3,+}u_{2i,-}-u_{2,-}u_{2i-1,+})x+(u_{2,+}u_{2i,-}-u_{1,-}u_{2i-1,+})y\le u_{2j,-}\lambda_0+u_{2j-1,+}\lambda_1,\]
     which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[-u_{2i+1,-}x-u_{2i,+}y=(-u_{3,+}u_{2i-1,-}+u_{2,-}u_{2i-2,+})x+(-u_{2,+}u_{2i-1,-}+u_{1,-}u_{2i-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    \[-u_{2i+1,-}x-u_{2i,+}y=(-u_{3,+}u_{2i-1,-}+u_{2,-}u_{2i-2,+})x+(-u_{2,+}u_{2i-1,-}+u_{1,-}u_{2i-2,+})y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
     which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-    \[u_{2i+3,-}x+u_{2i+2,+}y=(u_{3,+}u_{2i+1,-}-u_{2,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    \[u_{2i+3,-}x+u_{2i+2,+}y=(u_{3,+}u_{2i+1,-}-u_{2,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
     which is the inequality (b) for $i+1$.
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-    \[-u_{2i+1,-}x-u_{2i,+}y=(u_{1,+}u_{2i-1,-}-u_{2,-}u_{2i,+})x+(-u_{0,+}u_{2i-1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    \[-u_{2i+1,-}x-u_{2i,+}y=(u_{1,+}u_{2i-1,-}-u_{2,-}u_{2i,+})x+(-u_{0,+}u_{2i-1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
     which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
@@
     Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[-u_{2i+1,-}x+u_{2i+2,+}y=(-u_{1,+}u_{2i+1,-}+u_{0,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    \[-u_{2i+1,-}x+u_{2i+2,+}y=(-u_{1,+}u_{2i+1,-}+u_{0,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
     which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
-    \[-u_{2i+1,-}x-u_{2i,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
+    \[-u_{2i+1,-}x-u_{2i,+}y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
     which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
@@
     For $k=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2.\]
+    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_0+u_{2j,+}\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_0+u_{2j+1,-}\lambda_1.\]
     Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
     From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
-    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_0+u_{2j,+}\lambda_1$.
     The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
-    \[ cx+y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_1+u_{2j+1,+}\lambda_2.\]
+    \[ cx+y\le u_{2j+2,+}\lambda_0+u_{2j+1,+}\lambda_1 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_0+u_{2j+1,+}\lambda_1.\]
 
@@
     \begin{align*}
-      \tag{a$'$} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2;\\
-      \tag{b$'$} u_{2i+2,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
-      \tag{c$'$} -u_{2i,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2;\\
-      \tag{d$'$} -u_{2i,-}x-u_{2i-1,+}y &\le u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2.
+      \tag{a$'$} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1;\\
+      \tag{b$'$} u_{2i+2,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_0+u_{2j+1,+}\lambda_1;\\
+      \tag{c$'$} -u_{2i,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_0+u_{2j+1,+}\lambda_1;\\
+      \tag{d$'$} -u_{2i,-}x-u_{2i-1,+}y &\le u_{2j+2,-}\lambda_0+u_{2j+1,+}\lambda_1.
     \end{align*}
@@
     \begin{align*}
-      u_{k,-}(x-\lambda_1)+u_{k-1,+}(y-\lambda_2) &\le 0;\\
-      u_{k+1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le 0;\\
-      -u_{k-1,-}(x-\lambda_1)+u_{k,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1;\\
-      -u_{k-1,-}(x-\lambda_1)-u_{k-2,+}(y-\lambda_2) &\le cu_{k,+}\lambda_1+bu_{k-1,-}\lambda_2.
+      u_{k,-}(x-\lambda_0)+u_{k-1,+}(y-\lambda_1) &\le 0;\\
+      u_{k+1,-}(x-\lambda_0)+u_{k,+}(y-\lambda_1) &\le 0;\\
+      -u_{k-1,-}(x-\lambda_0)+u_{k,+}(y-\lambda_1) &\le cu_{k,+}\lambda_0;\\
+      -u_{k-1,-}(x-\lambda_0)-u_{k-2,+}(y-\lambda_1) &\le cu_{k,+}\lambda_0+bu_{k-1,-}\lambda_1.
     \end{align*}
@@
     \begin{enumerate}
-      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
-      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
+      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-b\lambda_1,\lambda_1)$.
+      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1)$, and $(\lambda_0,-c\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1)$.
     \end{enumerate}
@@
     Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
-    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
+    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1=\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\]
     or 
-    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
-    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
+    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1.\]
+    The first equations reduces to $c\lambda_0+2\lambda_1=0$, while the second reduces to $2\lambda_0+b\lambda_1=0$.
     In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
@@
 
-%  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following inequalities:
+%  The dominance polygon pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region defined by the following inequalities:
 %  \begin{align}
-%    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    -\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_1+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_0+\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_0 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_0+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_1+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_0-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_0+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_1+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
 %  \end{align}
@@
 %  \begin{align}
-%    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
-%    \\
-%    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
+%    (x-\lambda_0)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
+%    \\
+%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1)\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)\geq0
+%    \\
+%    \nonumber \iff -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)\geq0
+%    \\
+%    \nonumber \iff -b\lambda_1 + (x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_0+(x-\lambda_0)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
+%    \\
+%    \nonumber \iff c\lambda_0+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)\geq0
+%    \\
+%    -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)\geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_0+b\lambda_1+(x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
 %  \end{align}
@@
 %  \begin{align}
-%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
-%    \\
-%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
-%    \\
-%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
-%    \\
-%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \geq0
+%    \\
+%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0-b\lambda_1)-(y-\lambda_1) & \geq 0
+%    \\
+%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)& \geq c\lambda_0+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1
+%    \\
+%    -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)& \geq0
+%    \\
+%    (x-\lambda_0)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1-c\lambda_0) & \geq 0
+%    \\
+%    (x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1
 %  \end{align}
@@
 %  \begin{array}{rcccl}
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
-%    \\
-%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
-%    \\
-%    - b \lambda_2 & \geq & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) 
-%    \\
-%    0 & \geq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
+%    -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \geq & 0
+%    \\
+%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1) & \geq & c\lambda_0
+%    \\
+%    - b \lambda_1 & \geq & - (x-\lambda_0) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1) 
+%    \\
+%    0 & \geq & (x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1
 %  \end{array}
@@
 %  \begin{array}{rcccl}
-%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
-%    \\
-%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2  & \leq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & 0
-%    \\
-%    & & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)  & \leq & - b \lambda_2
+%    -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \geq & 0
+%    \\
+%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1) & \geq & c\lambda_0
+%    \\
+%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1  & \leq & (x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \leq & 0
+%    \\
+%    & & - (x-\lambda_0) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1)  & \leq & - b \lambda_1
 %  \end{array}
@@
 %  \begin{array}{rcccl}
-%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
-%    \\
-%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
-%    \\
-%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
+%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \leq & -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1
+%    \\
+%    c\lambda_0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)
+%    \\
+%    0 & \leq &  -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1
+%    \\
+%    b \lambda_1 & \leq & (x-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1)
 %  \end{array}
@@
 %  \begin{array}{rcccl}
-%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
-%    \\
-%    -c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
-%    \\
-%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
-%    \\
-%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
+%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \leq & -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1
+%    \\
+%    -c\lambda_0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)
+%    \\
+%    0 & \leq &  -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1
+%    \\
+%    b \lambda_1 & \leq & (x-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1)
 %  \end{array}
@@
 %}
-  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
+  The dominance polygon pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region defined by $x\leq \lambda_0, y\geq\lambda_1$, and the following inequalities:
  {
@@
   \begin{array}{rcccl}
-    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
+    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \leq & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
     \\
-    \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
+    \min\left(-c\lambda_0,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1) & \leq & 0
     \\
-    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
+    0 & \leq &  -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
     \\
-    \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
+    \min\left(b \lambda_1,0\right) & \leq & (x-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1) & \leq & 0
   \end{array}
@@
   \begin{proof}
-    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_1,\lambda_2)$ where
-    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
+    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_0,\lambda_1)$ where
+    \[\lambda_0=\frac{2b\mu_1-4\mu_0}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_1=\frac{2c\mu_0-4\mu_1}{bc-4+\sqrt{bc(bc-4)}}.\]
     (This comes from setting $\mu$ to be the vertex opposite $\lambda$ inside the dominance region $\cP(\lambda)$ and then solving for $\lambda$.)

### 2022-04-07 dominance_regions.tex
Superscripts section 4

@@
   Important examples of pointed elements are the \emph{cluster monomials} of $\cA(b,c)$, i.e.
-the elements that can be written in the form $x_k^{a_k}x_{k+1}^{a_{k+1}}$ for some $k\in\ZZ$ and $a_k,a_{k+1}$ non-negative integers.
+the elements that can be written in the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $a_k,a_{k+1}$ non-negative integers.
   Indeed, by [someresult of Qin] cluster monomials are part of any pointed basis in any cluster algebra.
@@
   In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
-  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b a_0 ,c a_1)$, $a_0,a_1\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
   %In this case, we compute the possible transitions between any two pointed bases.
@@
   A number of bases for rank two cluster algebras with various defining properties have been constructed.
-  A natural starting basis is the so-called \emph{greedy basis} in which all $c^\lambda_{a_1,a_2}$ are non-negative and these coefficients are chosen to be minimal.
+  A natural starting basis is the so-called \emph{greedy basis} in which all $c_{\alpha_0,\alpha_1}$ are non-negative and these coefficients are chosen to be minimal.
   It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
@@
   \end{equation}
-  %\begin{equation}
-  %  \label{eq:backward two step mutation}
-  %  \phi_{-2}(\lambda)
-  %  =
-  %  \begin{cases}
-  %    \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
-  %    (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
-  %    (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
-  %    (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
-  %  \end{cases}
-  %\end{equation}
+  \begin{equation}
+    \label{eq:backward two step mutation}
+    \phi_{-2}(\lambda)
+    =
+    \begin{cases}
+      \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
+      (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
+      (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
+      (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
+    \end{cases}
+  \end{equation}
 
@@
     \begin{align*}
-      \phi_{2j}(\lambda)&=(u_{2j+1,+}\lambda_0+u_{2j,+}\lambda_1,-u_{2j,-}\lambda_0-u_{2j-1,-}\lambda_1);\\
-      \phi_{2j+1}(\lambda)&=(-u_{2j+1,+}\lambda_0-u_{2j,+}\lambda_1,u_{2j+2,-}\lambda_0+u_{2j+1,-}\lambda_1).
+      \phi_{2j}(\lambda)&=(u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1,-u_{2j}^-\lambda_0-u_{2j-1}^-\lambda_1);\\
+      \phi_{2j+1}(\lambda)&=(-u_{2j+1}^+\lambda_0-u_{2j}^+\lambda_1,u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1).
     \end{align*}
@@
     For $\lambda\in\cI$, the action of $\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
-    \[\phi_2(\lambda)=(u_{3,-}\lambda_0+u_{2,+}\lambda_1,-u_{2,-}\lambda_0-u_{1,+}\lambda_1).\]
+    \[\phi_2(\lambda)=(u_3^-\lambda_0+u_2^+\lambda_1,-u_2^-\lambda_0-u_1^+\lambda_1).\]
     Therefore
@@
       \phi_{2j+2}(\lambda)&=\phi_2\phi_{2j}(\lambda)\\
-      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_0+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_1,\\
-      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_0-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_1 \big)\\
-      &=(u_{2j+3,+}\lambda_0+u_{2j+2,+}\lambda_1, -u_{2j+2,-}\lambda_0-u_{2j+1,-}\lambda_1),
+      &=\big( (u_3^- u_{2j+1}^+-u_2^+u_{2j}^-)\lambda_0+(u_3^-u_{2j}^+-u_2^+u_{2j-1}^-)\lambda_1,-(u_2^-u_{2j+1}^+-u_1^+u_{2j}^-)\lambda_0-(u_2^-u_{2j}^+-u_1^+u_{2j-1}^-)\lambda_1 \big)\\
+      &=(u_{2j+3}^+\lambda_0+u_{2j+2}^+\lambda_1, -u_{2j+2}^-\lambda_0-u_{2j+1}^-\lambda_1),
     \end{align*}
@@
 
-    Similarly, using $\phi_1(\lambda)=(-\lambda_0,u_{2,-}\lambda_0+u_{1,+}\lambda_1)$ for $\lambda\in\cI$ together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
+    Similarly, using $\phi_1(\lambda)=(-\lambda_0,u_2^-\lambda_0+u_1^+\lambda_1)$ for $\lambda\in\cI$ together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
   \end{proof}
@@
   \begin{proof}
-    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{a_k}x_{k+1}^{a_{k+1}}$.
+    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$.
     In this case the intersection
@@
     Let $A$ be an invertible $2\times 2$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet\bfx \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet\bfy\le t.\]
+    Under the left action of $A$, say $A\mu=\mu'$ for $\mu,\mu'\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet\mu \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet\mu'\le t.\]
   \end{lemma}
@@
     This is immediate from the equalities
-    \[\bfr\bullet\bfx=\bfr^T\bfx=\bfr^TA^{-1}A\bfx=(A^{-T}\bfr)^TA\bfx=(A^{-T}\bfr)\bullet\bfy.\]
+    \[\bfr\bullet\mu=\bfr^T\mu=\bfr^TA^{-1}A\mu=(A^{-T}\bfr)^TA\mu=(A^{-T}\bfr)\bullet\mu'.\]
   \end{proof}
@@
     \begin{align}
-      \label{ineq:1} u_{k,-}x+u_{k-1,+}y &\le u_{k,-}\lambda_0+u_{k-1,+}\lambda_1;\\
-      \label{ineq:2} u_{k+1,-}x+u_{k,+}y &\le u_{k+1,-}\lambda_0+u_{k,+}\lambda_1;\\
-      \label{ineq:3} -u_{k-1,-}x+u_{k,+}y &\le u_{k+1,-}\lambda_0+u_{k,+}\lambda_1;\\
-      \label{ineq:4} -u_{k-1,-}x-u_{k-2,+}y &\le u_{k+1,-}\lambda_0+u_{k,+}\lambda_1.
+      \label{ineq:1} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
+      \label{ineq:2} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
+      \label{ineq:3} -u_{k-1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
+      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1.
     \end{align}
@@
     For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_0+u_{2j,+}\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_0+u_{2j-1,-}\lambda_1. \]
+    \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
     We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
@@
     \begin{align*}
-      \tag{a} u_{2i,-}x+u_{2i-1,+}y &\le u_{2j,-}\lambda_0+u_{2j-1,+}\lambda_1;\\
-      \tag{b} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1;\\
-      \tag{c} -u_{2i-1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1;\\
-      \tag{d} -u_{2i-1,-}x-u_{2i-2,+}y &\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1.
+      \tag{a} u_{2i}^-x+u_{2i-1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
+      \tag{b} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+      \tag{c} -u_{2i-1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+      \tag{d} -u_{2i-1}^-x-u_{2i-2}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1.
     \end{align*}
@@
     We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{2j,-}\lambda_0+u_{2j-1,+}\lambda_1$ which corresponds to (a) with $i=1$.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$ which corresponds to (a) with $i=1$.
     Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-    \[u_{2i+2,-}x+u_{2i+1,+}y=(u_{3,+}u_{2i,-}-u_{2,-}u_{2i-1,+})x+(u_{2,+}u_{2i,-}-u_{1,-}u_{2i-1,+})y\le u_{2j,-}\lambda_0+u_{2j-1,+}\lambda_1,\]
+    \[u_{2i+2}^-x+u_{2i+1}^+y=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)x+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
     which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[-u_{2i+1,-}x-u_{2i,+}y=(-u_{3,+}u_{2i-1,-}+u_{2,-}u_{2i-2,+})x+(-u_{2,+}u_{2i-1,-}+u_{1,-}u_{2i-2,+})y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
+    \[-u_{2i+1}^-x-u_{2i}^+y=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)x+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-    \[u_{2i+3,-}x+u_{2i+2,+}y=(u_{3,+}u_{2i+1,-}-u_{2,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
+    \[u_{2i+3}^-x+u_{2i+2}^+y=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which is the inequality (b) for $i+1$.
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-    \[-u_{2i+1,-}x-u_{2i,+}y=(u_{1,+}u_{2i-1,-}-u_{2,-}u_{2i,+})x+(-u_{0,+}u_{2i-1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
+    \[-u_{2i+1}^-x-u_{2i}^+y=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)x+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
@@
     Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[-u_{2i+1,-}x+u_{2i+2,+}y=(-u_{1,+}u_{2i+1,-}+u_{0,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
+    \[-u_{2i+1}^-x+u_{2i+2}^+y=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
-    \[-u_{2i+1,-}x-u_{2i,+}y\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1,\]
+    \[-u_{2i+1}^-x-u_{2i}^+y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
@@
     For $k=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger')\ -x\le u_{2j+1,+}\lambda_0+u_{2j,+}\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2,-}\lambda_0+u_{2j+1,-}\lambda_1.\]
+    \[ (\dagger')\ -x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1.\]
     Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
     From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
-    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1,+}\lambda_0+u_{2j,+}\lambda_1$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$.
     The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
-    \[ cx+y\le u_{2j+2,+}\lambda_0+u_{2j+1,+}\lambda_1 \qquad\text{and}\qquad  y\le u_{2j+2,+}\lambda_0+u_{2j+1,+}\lambda_1.\]
+    \[ cx+y\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad y\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1.\]
 
@@
     \begin{align*}
-      \tag{a$'$} u_{2i+1,-}x+u_{2i,+}y &\le u_{2j+1,-}\lambda_0+u_{2j,+}\lambda_1;\\
-      \tag{b$'$} u_{2i+2,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_0+u_{2j+1,+}\lambda_1;\\
-      \tag{c$'$} -u_{2i,-}x+u_{2i+1,+}y &\le u_{2j+2,-}\lambda_0+u_{2j+1,+}\lambda_1;\\
-      \tag{d$'$} -u_{2i,-}x-u_{2i-1,+}y &\le u_{2j+2,-}\lambda_0+u_{2j+1,+}\lambda_1.
+      \tag{a$'$} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+      \tag{b$'$} u_{2i+2}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
+      \tag{c$'$} -u_{2i}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
+      \tag{d$'$} -u_{2i}^-x-u_{2i-1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
     \end{align*}
@@
     \begin{align*}
-      u_{k,-}(x-\lambda_0)+u_{k-1,+}(y-\lambda_1) &\le 0;\\
-      u_{k+1,-}(x-\lambda_0)+u_{k,+}(y-\lambda_1) &\le 0;\\
-      -u_{k-1,-}(x-\lambda_0)+u_{k,+}(y-\lambda_1) &\le cu_{k,+}\lambda_0;\\
-      -u_{k-1,-}(x-\lambda_0)-u_{k-2,+}(y-\lambda_1) &\le cu_{k,+}\lambda_0+bu_{k-1,-}\lambda_1.
+      u_k^-(x-\lambda_0)+u_{k-1}^+(y-\lambda_1) &\le 0;\\
+      u_{k+1}^-(x-\lambda_0)+u_k^+(y-\lambda_1) &\le 0;\\
+      -u_{k-1}^-(x-\lambda_0)+u_k^+(y-\lambda_1) &\le cu_k^+\lambda_0;\\
+      -u_{k-1}^-(x-\lambda_0)-u_{k-2}^+(y-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1.
     \end{align*}
   \end{corollary}
-
-  \begin{lemma}
-    \label{le:one direction}
-    For $\lambda\in\cI\cap\ZZ^2$, 
-    \begin{enumerate}
-      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-b\lambda_1,\lambda_1)$.
-      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1)$, and $(\lambda_0,-c\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1)$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
-    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
-  \end{proof}
 
@@
 
-%  The dominance polygon pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region defined by the following inequalities:
-%  \begin{align}
-%    -\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_1+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_0+\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_0 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_0+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_1+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_0-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_0+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_1+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
-%  \end{align}
-%  Are any of these better forms?
-%  \begin{align}
-%    (x-\lambda_0)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
-%    \\
-%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1)\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)\geq0
-%    \\
-%    \nonumber \iff -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)\geq0
-%    \\
-%    \nonumber \iff -b\lambda_1 + (x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_0+(x-\lambda_0)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
-%    \\
-%    \nonumber \iff c\lambda_0+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)\geq0
-%    \\
-%    -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)\geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_0+b\lambda_1+(x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)\geq0
-%  \end{align}
-%  Another proposal (I also changed the order of the equations)
-%  \begin{align}
-%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0-b\lambda_1)-(y-\lambda_1) & \geq 0
-%    \\
-%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)& \geq c\lambda_0+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1
-%    \\
-%    -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)& \geq0
-%    \\
-%    (x-\lambda_0)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1-c\lambda_0) & \geq 0
-%    \\
-%    (x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1
-%  \end{align}
-%  Maybe this one:
-%  \begin{align}
-%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \geq0
-%    \\
-%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0-b\lambda_1)-(y-\lambda_1) & \geq 0
-%    \\
-%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)& \geq c\lambda_0+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1
-%    \\
-%    -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1)& \geq0
-%    \\
-%    (x-\lambda_0)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1-c\lambda_0) & \geq 0
-%    \\
-%    (x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1
-%  \end{align}
-%
-%  Yet another version:
-% 
-% {
-%    \everymath={\displaystyle}
-%  \[
-%  \begin{array}{rcccl}
-%    -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \geq & 0
-%    \\
-%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1) & \geq & c\lambda_0
-%    \\
-%    - b \lambda_1 & \geq & - (x-\lambda_0) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1) 
-%    \\
-%    0 & \geq & (x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1
-%  \end{array}
-%\]
-%}
-%
-%Or: (Maybe at this point we can remove $c/c$ and $b/b$)
-%
-% {
-%    \everymath={\displaystyle}
-%  \[
-%  \begin{array}{rcccl}
-%    -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \geq & 0
-%    \\
-%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1) & \geq & c\lambda_0
-%    \\
-%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1  & \leq & (x-\lambda_0)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \leq & 0
-%    \\
-%    & & - (x-\lambda_0) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1)  & \leq & - b \lambda_1
-%  \end{array}
-%\]
-%}
-%
-%
-%Or Or: (Maybe at this point we can remove $c/c$ and $b/b$)
-%
-%
-% The following, and possibly all the one before, has a typo
-% {
-%    \everymath={\displaystyle}
-%    \def\arraystretch{2.8}
-%  \[
-%  \begin{array}{rcccl}
-%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \leq & -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1
-%    \\
-%    c\lambda_0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)
-%    \\
-%    0 & \leq &  -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1
-%    \\
-%    b \lambda_1 & \leq & (x-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1)
-%  \end{array}
-%\]
-%}
-% {
-%    \everymath={\displaystyle}
-%    \def\arraystretch{2.8}
-%  \[
-%  \begin{array}{rcccl}
-%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \leq & -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1
-%    \\
-%    -c\lambda_0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1)
-%    \\
-%    0 & \leq &  -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1
-%    \\
-%    b \lambda_1 & \leq & (x-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1)
-%  \end{array}
-%\]
-%}
   The dominance polygon pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region defined by $x\leq \lambda_0, y\geq\lambda_1$, and the following inequalities:
@@
 
+  \begin{lemma}
+    \label{le:one direction}
+    For $\lambda\in\cI\cap\ZZ^2$, 
+    \begin{enumerate}
+      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-b\lambda_1,\lambda_1)$.
+      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1)$, and $(\lambda_0,-c\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1)$.
+    \end{enumerate}
+  \end{lemma}
+  \begin{proof}
+    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
+    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
+  \end{proof}
 \section{The Total Domination Polyhedron}

### 2022-04-08 dominance_regions.tex
Inequalities for negative mutations

@@
   \begin{lemma}
-    For $k\ge1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
     \begin{align}
@@
     \end{align}
+    when $k\ge1$ and by the following inequalities:
+    \begin{align*}
+      u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
+      u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
+      u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
+      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
+    \end{align*}
+    when $k\le -1$.
 
@@
     For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+    \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 = u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.
+\]
     We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
@@
 
-    For $k=2j+1$, $j>0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
+    For $k=2j+1$, $j\ge0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
     \[ (\dagger')\ -x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1.\]
@@
     \subsubsection*{Claim:} For $i\ge 0$, $\phi_{2i+1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
+    \begin{align*}
+      \tag{a$'$} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+      \tag{b$'$} u_{2i+2}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
+      \tag{c$'$} -u_{2i}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
+      \tag{d$'$} -u_{2i}^-x-u_{2i-1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
+    \end{align*}
+    By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
+  \end{proof}
+  The following consequence is easily seen from the Chebyshev recursion.
+  \begin{corollary}
+    \begin{align*}
+      u_k^-(x-\lambda_0)+u_{k-1}^+(y-\lambda_1) &\le 0;\\
+      u_{k+1}^-(x-\lambda_0)+u_k^+(y-\lambda_1) &\le 0;\\
+      -u_{k-1}^-(x-\lambda_0)+u_k^+(y-\lambda_1) &\le cu_k^+\lambda_0;\\
+      -u_{k-1}^-(x-\lambda_0)-u_{k-2}^+(y-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1.
+    \end{align*}
+  \end{corollary}
+
+  \begin{lemma}
+    For $k \le -1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+    \begin{align}
+      \label{ineq:1} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
+      \label{ineq:2} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
+      \label{ineq:3} u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
+      \label{ineq:4} -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
+    \end{align}
+
+    given as in the figure below:
+    \[
+      \begin{tikzpicture}
+        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
+        \draw[-] (-8,0) -- (5,0);
+        \draw[-] (0,-5) -- (0,5);
+        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
+        \draw[dashed] (0,0) -- (5,-2.113);
+        \draw[dashed] (0,0) -- (3.17,-5);
+        \node at (1,-0.9) {$\cI$};
+        \draw[fill=black] (3.5,-3) circle (2pt);
+        \node[right] at (3.5,-3) {$\lambda$};
+        \draw[->,thick] (3.5,-3) -- (47/10,-5);
+        \draw[-,thick] (3.5,-3) -- (0,26/10);
+        \draw[-,thick] (0,26/10) -- (-26/4,0);
+        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
+        \node at (4.5,-4) {\eqref{ineq:1}};
+        \node at (2.34,-0.5) {\eqref{ineq:2}};
+        \node at (-3,1.75) {\eqref{ineq:3}};
+        \node at (-5.36,-3) {\eqref{ineq:4}};
+      \end{tikzpicture}
+    \]
+  \end{lemma}
+  \begin{proof}
+    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
+
+    For $k=2j$, $j<0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
+
+    \subsubsection*{Claim:} For $i<0$, $\phi_{2i}^{-1}\cC_{2j}(\phi_{2j}\lambda)$ is the region determined by the inequalities 
+    \begin{align*}
+      \tag{a} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+      \tag{b} u_{2i}^-x+u_{2i-1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
+      \tag{c} u_{2i}^-x-u_{2i+1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
+      \tag{d} -u_{2i+2}^-x-u_{2i+1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.
+    \end{align*}
+
+    We see from \eqref{eq:two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) lies entirely in the region in which $\phi_2$ acts according to the matrix $\left[ \begin{array}{cc} bc-1 & b\\ -c & -1 \end{array}\right]$ of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) transforms into the inequality $-x-by\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$ which corresponds to (a) with $i=-1$.
+    Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) intersects the three domains of linearity in which $\phi_2$ acts according to the matrices $\left[ \begin{array}{cc} bc-1 & b\\ -c & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ -c & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $i=-1$.
+    \[ -cx-(bc-1)y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+    \[ -cx+y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+    \[ y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+    This establishes the base of a downward induction on $i$.
+
+    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2$.
+    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
+    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
+    \[u_{2i+2}^-x+u_{2i+1}^+y=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)x+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
+    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
+    \[-u_{2i+1}^-x-u_{2i}^+y=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)x+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
+    \[u_{2i+3}^-x+u_{2i+2}^+y=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    which is the inequality (b) for $i+1$.
+    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
+    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
+    \[-u_{2i+1}^-x-u_{2i}^+y=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)x+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
+    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
+    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
+    \[-u_{2i+1}^-x+u_{2i+2}^+y=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
+    \[-u_{2i+1}^-x-u_{2i}^+y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
+    This completes the induction on $i$, proving the Claim and the result for $k$ even.
+
+    For $k=2j-1$, $j \le 0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
+    \[ (\dagger')\ -x\le u_{2j-1}^+\lambda_0+u_{2j-2}^+\lambda_1 = u_{2j-1}^-\lambda_0+u_{2j-2}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.\]
+    Using that $\phi_{2j-1}^{-1}=\phi_2^{-j}\phi_{-1}^{-1}$, we compute the image inductively as above.
+    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\ddagger'$) lies entirely in the region in which $\phi_{-1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ of determinant $-1$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger'$) is transformed by $\phi_{-1}^{-1}$ into the inequality $-y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$.
+    The boundary ray corresponding to ($\dagger'$) intersects both domains of linearity for $\phi_{-1}^{-1}$ and thus produces the inequalities
+    \[ -x-by\le u_{2j-1}^-\lambda_0+u_{2j-2}^+\lambda_1 \qquad\text{and}\qquad -x\le u_{2j-1}^+\lambda_0+u_{2j-2}^+\lambda_1.\]
+
+    \subsubsection*{Claim:} For $i\le 0$, $\phi_{2i-1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
     \begin{align*}

### 2022-04-08 dominance_regions.tex
Corollary 4.4

--- 2022-04-07 dominance_regions.tex
@@
   \begin{proof}
+    We prove the claim for $k\ge1$, the proof for $k\le-1$ is similar.
     Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
@@
   \begin{corollary}
+    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
     \begin{align*}
-      u_k^-(x-\lambda_0)+u_{k-1}^+(y-\lambda_1) &\le 0;\\
-      u_{k+1}^-(x-\lambda_0)+u_k^+(y-\lambda_1) &\le 0;\\
-      -u_{k-1}^-(x-\lambda_0)+u_k^+(y-\lambda_1) &\le cu_k^+\lambda_0;\\
-      -u_{k-1}^-(x-\lambda_0)-u_{k-2}^+(y-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1.
+      u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
+      u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
+      -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
+      -u_{k-1}^-(\mu_0-\lambda_0)-u_{k-2}^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1.
     \end{align*}
+    when $k\ge1$ and by the following inequalities:
+    \begin{align*}
+      u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
+      u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
+      u_k^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le bu_k^-\lambda_1;\\
+      -u_{k+2}^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le cu_{k+1}^+\lambda_0+bu_k^-\lambda_1.
+    \end{align*}
+    when $k\le -1$.
   \end{corollary}
+
+  %\begin{lemma}
+  %  For $k \le -1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+  %  \begin{align}
+  %    \label{ineq:1} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
+  %    \label{ineq:2} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
+  %    \label{ineq:3} u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
+  %    \label{ineq:4} -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
+  %  \end{align}
+  %  
+  %  given as in the figure below:
+  %  \[
+  %    \begin{tikzpicture}
+  %      \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
+  %      \draw[-] (-8,0) -- (5,0);
+  %      \draw[-] (0,-5) -- (0,5);
+  %      %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
+  %      \draw[dashed] (0,0) -- (5,-2.113);
+  %      \draw[dashed] (0,0) -- (3.17,-5);
+  %      \node at (1,-0.9) {$\cI$};
+  %      \draw[fill=black] (3.5,-3) circle (2pt);
+  %      \node[right] at (3.5,-3) {$\lambda$};
+  %      \draw[->,thick] (3.5,-3) -- (47/10,-5);
+  %      \draw[-,thick] (3.5,-3) -- (0,26/10);
+  %      \draw[-,thick] (0,26/10) -- (-26/4,0);
+  %      \draw[->,thick] (-26/4,0) -- (-16/4,-5);
+  %      \node at (4.5,-4) {\eqref{ineq:1}};
+  %      \node at (2.34,-0.5) {\eqref{ineq:2}};
+  %      \node at (-3,1.75) {\eqref{ineq:3}};
+  %      \node at (-5.36,-3) {\eqref{ineq:4}};
+  %    \end{tikzpicture}
+  %  \]
+  %\end{lemma}
+  %\begin{proof}
+  %  Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
+
+  %  For $k=2j$, $j<0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
+  %  \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+  %  We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
+
+  %  \subsubsection*{Claim:} For $i<0$, $\phi_{2i}^{-1}\cC_{2j}(\phi_{2j}\lambda)$ is the region determined by the inequalities 
+  %  \begin{align*}
+  %    \tag{a} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+  %    \tag{b} u_{2i}^-x+u_{2i-1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
+  %    \tag{c} u_{2i}^-x-u_{2i+1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
+  %    \tag{d} -u_{2i+2}^-x-u_{2i+1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.
+  %  \end{align*}
+
+  %  We see from \eqref{eq:two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) lies entirely in the region in which $\phi_2$ acts according to the matrix $\left[ \begin{array}{cc} bc-1 & b\\ -c & -1 \end{array}\right]$ of determinant 1.
+  %  By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) transforms into the inequality $-x-by\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$ which corresponds to (a) with $i=-1$.
+  %  Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) intersects the three domains of linearity in which $\phi_2$ acts according to the matrices $\left[ \begin{array}{cc} bc-1 & b\\ -c & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ -c & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
+  %  By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $i=-1$.
+  %  \[ -cx-(bc-1)y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+  %  \[ -cx+y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+  %  \[ y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
+  %  This establishes the base of a downward induction on $i$.
+
+  %  Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2$.
+  %  Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
+  %  Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
+  %  \[u_{2i+2}^-x+u_{2i+1}^+y=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)x+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
+  %  which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
+  %  \[-u_{2i+1}^-x-u_{2i}^+y=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)x+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+  %  which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
+  %  \[u_{2i+3}^-x+u_{2i+2}^+y=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+  %  which is the inequality (b) for $i+1$.
+  %  Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
+  %  Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
+  %  \[-u_{2i+1}^-x-u_{2i}^+y=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)x+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+  %  which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
+  %  Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
+  %  Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
+  %  \[-u_{2i+1}^-x+u_{2i+2}^+y=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+  %  which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
+  %  \[-u_{2i+1}^-x-u_{2i}^+y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+  %  which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
+  %  This completes the induction on $i$, proving the Claim and the result for $k$ even.
+
+  %  For $k=2j-1$, $j \le 0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
+  %  \[ (\dagger')\ -x\le u_{2j-1}^+\lambda_0+u_{2j-2}^+\lambda_1 = u_{2j-1}^-\lambda_0+u_{2j-2}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.\]
+  %  Using that $\phi_{2j-1}^{-1}=\phi_2^{-j}\phi_{-1}^{-1}$, we compute the image inductively as above.
+  %  From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\ddagger'$) lies entirely in the region in which $\phi_{-1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ of determinant $-1$.
+  %  Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger'$) is transformed by $\phi_{-1}^{-1}$ into the inequality $-y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$.
+  %  The boundary ray corresponding to ($\dagger'$) intersects both domains of linearity for $\phi_{-1}^{-1}$ and thus produces the inequalities
+  %  \[ -x-by\le u_{2j-1}^-\lambda_0+u_{2j-2}^+\lambda_1 \qquad\text{and}\qquad -x\le u_{2j-1}^+\lambda_0+u_{2j-2}^+\lambda_1.\]
+
+  %  \subsubsection*{Claim:} For $i\le 0$, $\phi_{2i-1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
+  %  \begin{align*}
+  %    \tag{a$'$} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+  %    \tag{b$'$} u_{2i+2}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
+  %    \tag{c$'$} -u_{2i}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
+  %    \tag{d$'$} -u_{2i}^-x-u_{2i-1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
+  %  \end{align*}
+  %  By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
+  %\end{proof}
 

### 2022-04-08 dominance_regions.tex
Some work towards proving Theorem 1

@@
   \begin{lemma}
+    \label{le:dominance inequalities}
     For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
@@
       \label{ineq:3} -u_{k-1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
-      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1.
+      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;
     \end{align}
-    when $k\ge1$ and by the following inequalities:
+    when $k>0$ and by the following inequalities:
     \begin{align*}
@@
     \end{align*}
-    when $k\le -1$.
+    when $k<0$.
 
@@
   \begin{proof}
-    We prove the claim for $k\ge1$, the proof for $k\le-1$ is similar.
+    We prove the claim for $k>0$, the proof for $k<0$ is similar or can be deduced from the other case by a symmetry argument.
     Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
@@
     For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 = u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.
+    \[ (\dagger)\ \mu_0 \le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 = u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.
 \]
@@
     \begin{align*}
-      \tag{a} u_{2i}^-x+u_{2i-1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
-      \tag{b} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
-      \tag{c} -u_{2i-1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
-      \tag{d} -u_{2i-1}^-x-u_{2i-2}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1.
+      \tag{a} u_{2i}^-\mu_0+u_{2i-1}^+\mu_1 &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
+      \tag{b} u_{2i+1}^-\mu_0+u_{2i}^+\mu_1 &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+      \tag{c} -u_{2i-1}^-\mu_0+u_{2i}^+\mu_1 &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+      \tag{d} -u_{2i-1}^-\mu_0-u_{2i-2}^+\mu_1 &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1.
     \end{align*}
@@
     We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $cx+y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$ which corresponds to (a) with $i=1$.
+    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $c\mu_0+\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$ which corresponds to (a) with $i=1$.
     Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-    \[u_{2i+2}^-x+u_{2i+1}^+y=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)x+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
+    \[u_{2i+2}^-\mu_0+u_{2i+1}^+\mu_1=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)\mu_0+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
     which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[-u_{2i+1}^-x-u_{2i}^+y=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)x+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)\mu_0+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-    \[u_{2i+3}^-x+u_{2i+2}^+y=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    \[u_{2i+3}^-\mu_0+u_{2i+2}^+\mu_1=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which is the inequality (b) for $i+1$.
@@
     Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-    \[-u_{2i+1}^-x-u_{2i}^+y=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)x+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)\mu_0+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
@@
     Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[-u_{2i+1}^-x+u_{2i+2}^+y=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    \[-u_{2i+1}^-\mu_0+u_{2i+2}^+\mu_1=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
-    \[-u_{2i+1}^-x-u_{2i}^+y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
     which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
@@
     For $k=2j+1$, $j\ge0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger')\ -x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1.\]
+    \[ (\dagger')\ -\mu_0\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1.\]
     Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
     From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
-    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $\mu_0\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$.
     The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
-    \[ cx+y\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad y\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1.\]
+    \[ c\mu_0+\mu_1\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad \mu_1\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1.\]
 
@@
     \begin{align*}
-      \tag{a$'$} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
-      \tag{b$'$} u_{2i+2}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
-      \tag{c$'$} -u_{2i}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
-      \tag{d$'$} -u_{2i}^-x-u_{2i-1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
+      \tag{a$'$} u_{2i+1}^-\mu_0+u_{2i}^+\mu_1 &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
+      \tag{b$'$} u_{2i+2}^-\mu_0+u_{2i+1}^+\mu_1 &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
+      \tag{c$'$} -u_{2i}^-\mu_0+u_{2i+1}^+\mu_1 &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
+      \tag{d$'$} -u_{2i}^-\mu_0-u_{2i-1}^+\mu_1 &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
     \end{align*}
@@
   \end{proof}
-  The following consequence is easily seen from the Chebyshev recursion.
-  \begin{corollary}
-    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+
+  We are now ready to prove Theorem~\ref{th:dominance inequalities}.
+  The dominance region $\cP(\lambda)=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.
+
+  To begin we rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
+  For $k>0$, we get
   \begin{align*}
@@
     -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
-      -u_{k-1}^-(\mu_0-\lambda_0)-u_{k-2}^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1.
+    -u_{k-1}^-(\mu_0-\lambda_0)-u_{k-2}^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1;
   \end{align*}
-    when $k\ge1$ and by the following inequalities:
+  and, for $k<0$, we get
   \begin{align*}
@@
   \end{align*}
-    when $k\le -1$.
-  \end{corollary}
+  The first inequality in each list is redundant so we drop them.
+  Moreover, for $k=1$ the third and fourth inequalities in the first list are the same so we can increment $k$ in the last equality without losing any information and similarly for $k=-1$ in the second list.
+  This gives
+  \begin{align*}
+    u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
+    -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
+    -u_k^-(\mu_0-\lambda_0)-u_{k-1}^+(\mu_1-\lambda_1) &\le cu_{k+1}^+\lambda_0+bu_k^-\lambda_1;
+  \end{align*}
+  for $k>0$ and
+  \begin{align*}
+    u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
+    u_k^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le bu_k^-\lambda_1;\\
+    -u_{k+1}^-(\mu_0-\lambda_0)-u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1;
+  \end{align*}
+  for $k<0$.
+  Then using that $u_k^\varepsilon>0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$ we divide by these to rewrite the inequalities again as
+  \begin{align*}
+    \frac{u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) &\le 0;\\
+    \frac{-u_{k-1}^-}{u_k^+}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) &\le c\lambda_0;\\
+    -(\mu_0-\lambda_0)-\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1) &\le c\frac{u_{k+1}^+}{u_k^-}\lambda_0+b\lambda_1;
+  \end{align*}
+  and
+  \begin{align*}
+    0 &\le (\mu_0-\lambda_0)+\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1);\\
+    b\lambda_1 &\le (\mu_0-\lambda_0)-\frac{u_{k+1}^+}{u_k^-}(\mu_1-\lambda_1);\\
+    c\lambda_0+b\frac{u_{k-1}^-}{u_k^+}\lambda_1 &\le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).
+  \end{align*}
 

### 2022-04-08 dominance_regions.tex
Proof of Theorem 1, but something went wrong, we need to check the indexing for the inequalities in Lemma 4.3 for k<0

@@
   for $k<0$.
-  Then using that $u_k^\varepsilon>0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$ we divide by these to rewrite the inequalities again as
-  \begin{align*}
-    \frac{u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) &\le 0;\\
-    \frac{-u_{k-1}^-}{u_k^+}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) &\le c\lambda_0;\\
-    -(\mu_0-\lambda_0)-\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1) &\le c\frac{u_{k+1}^+}{u_k^-}\lambda_0+b\lambda_1;
-  \end{align*}
+  Then using that $-u_k^\varepsilon<0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$ we divide by these to rewrite the inequalities again as
+  \begin{align}
+    \label{ieq1} 0 & \le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
+    \label{ieq2} -c\lambda_0 & \le \frac{u_{k-1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
+    \label{ieq3} -(\mu_0-\lambda_0)-\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1) &\le c\frac{u_{k+1}^+}{u_k^-}\lambda_0+b\lambda_1;
+  \end{align}
   and
-  \begin{align*}
-    0 &\le (\mu_0-\lambda_0)+\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1);\\
-    b\lambda_1 &\le (\mu_0-\lambda_0)-\frac{u_{k+1}^+}{u_k^-}(\mu_1-\lambda_1);\\
-    c\lambda_0+b\frac{u_{k-1}^-}{u_k^+}\lambda_1 &\le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).
-  \end{align*}
+  \begin{align}
+    \label{ieq4} 0 &\le (\mu_0-\lambda_0)+\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1);\\
+    \label{ieq5} b\lambda_1 &\le (\mu_0-\lambda_0)-\frac{u_{k+1}^+}{u_k^-}(\mu_1-\lambda_1);\\
+    \label{ieq6} c\lambda_0+b\frac{u_{k-1}^-}{u_k^+}\lambda_1 &\le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).
+  \end{align}
+  We now study each sequence of inequalities in turn.
+
+  For $\mu_1-\lambda_1\ge 0$, the inequalities \eqref{ieq1} become more restrictive as $k$ gets larger since the sequence $\frac{-u_{k+1}^-}{u_k^+}$ of slopes is monotonically decreasing.
+  Thus in the limit as $k\to\infty$, we obtain the inequality 
+  \[ 0 \le \frac{-bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
+  or equivalently
+  \[ 0 \le -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \]
+  determining a boundary of $\cP(\lambda)$.
+
+  Similarly, the inequalities \eqref{ieq2} become more restrictive for $\mu_0\le0$ and $\mu_1\ge0$ as $k$ gets larger since the sequence of slopes $\frac{u_{k-1}^-}{u_k^+}$ is monotonically increasing and the intersection with \eqref{ieq1} moves lower on the $\mu_1$-axis as $k$ increases.
+  Thus in the limit as $k\to\infty$, we obtain the inequality
+  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
+  determining a boundary of $\cP(\lambda)$.
+  Observe further that $\mu_0-\lambda0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
+  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]
+
+  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence of slopes $\frac{-u_{k-1}^+}{u_k^-}$ is monotonically increasing and the intersection with \eqref{ieq2} moves to the right on the $\mu_0$-axis as $k$ increases.
+  Thus in the limit as $k\to\infty$, we obtain the inequality
+  \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1 \]
+  determining a boundary of $\cP(\lambda)$.
+
+  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP(\lambda)$:
+  \[ 0 \le (\mu_0-\lambda_0)+\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
+  \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
+  \[ c\lambda_0+b\frac{bc-\sqrt{bc(bc-4)}}{2b}\lambda_1 \le -\frac{bc+\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).\]
 

### 2022-04-08 dominance_regions.tex
Proof of Theorem 1

@@
     We have
-    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
+    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b};\]
+    \[\lim_{i\to-\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to-\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b}.\]
     Moreover, each of these sequences is monotonic.
@@
   \begin{proof}
-    For any $i\ge 1$, we have
+    For any $i\ne1$, we have
     \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
@@
     which is equivalent to the desired expression.
-    Similarly, 
+    Similarly, for $i\ne0$ we have
     \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
@@
     which is again equivalent to the desired expression.
+    This proves the claim for $i\to\infty$, the cases $i\to-\infty$ follow from these using $u_{-i}^\varepsilon=-u_i^\varepsilon$.
 
@@
   Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP(\lambda)$:
-  \[ 0 \le (\mu_0-\lambda_0)+\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
-  \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
-  \[ c\lambda_0+b\frac{bc-\sqrt{bc(bc-4)}}{2b}\lambda_1 \le -\frac{bc+\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).\]
-
+  \[ 0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1);\]
+  \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le 0;\]
+  \[ \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) \le -c\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2b}b\lambda_1.\]
+
+  This completes the proof of Theorem~\ref{th:dominance inequalities}.
   %\begin{lemma}

### 2022-04-08 dominance_regions.tex
Typos

@@
     \label{le:dominance inequalities}
-    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
+    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is determined by the following inequalities:
     \begin{align}
@@
       u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
-      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
+      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;
     \end{align*}
@@
   We are now ready to prove Theorem~\ref{th:dominance inequalities}.
-  The dominance region $\cP(\lambda)=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.
-
-  To begin we rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
+  The dominance region $\cP(\lambda)=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of the inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.
+
+  To begin, observe that the boundary lines for \eqref{ineq:2} and \eqref{ineq:3} (and hence \eqref{ieq1} and \eqref{ieq2} below) intersect where $\mu_0=0$ and the boundary lines for \eqref{ineq:3} and \eqref{ineq:4} (and hence \eqref{ieq2} and \eqref{ieq3} below) intersect where $\mu_1=0$.
+  We then rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
   For $k>0$, we get
@@
   Thus in the limit as $k\to\infty$, we obtain the inequality
-  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
+  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
   determining a boundary of $\cP(\lambda)$.
-  Observe further that $\mu_0-\lambda0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
-  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]
+  Observe further that $\mu_0-\lambda_0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
+  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]
 

### 2022-04-08 dominance_regions.tex
Reference (sort of) and intro edits

@@
 the elements that can be written in the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $a_k,a_{k+1}$ non-negative integers.
-  Indeed, by [someresult of Qin] cluster monomials are part of any pointed basis in any cluster algebra.
-  \say{Check if this needs full rank}
+  Indeed, by \cite[Lemma 3.4.12]{qin} cluster monomials are part of any pointed basis in any cluster algebra.
+  We achieve the same conclusion in our setting by elementary calculations (c.f. Lemma~\ref{le:cluster monomials}).
 
@@
   Qin introduced a partial order on $\bfg$-vectors called the \emph{dominance order} and showed that given two pointed bases $x=\{x_\lambda\}$, $y=\{y_\lambda\}$, $y_\mu$ can appear in the expansion of $x_\lambda$ in terms of $y$ only if $\lambda$ dominates $\mu$ (cf.
-\cite[Mainthm]{Qin} and \ref{below}).
+\cite[Mainthm]{qin} and \ref{def:dominance}).
 
@@
   \begin{definition}
+    \label{def:dominance}
     For $\lambda\in\ZZ^2$ and $k\in\ZZ$, define cones 
@@
   \begin{lemma}
+    \label{le:cluster monomials}
     If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
@@
   This completes the proof of Theorem~\ref{th:dominance inequalities}.
-  %\begin{lemma}
-  %  For $k \le -1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
-  %  \begin{align}
-  %    \label{ineq:1} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
-  %    \label{ineq:2} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
-  %    \label{ineq:3} u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
-  %    \label{ineq:4} -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
-  %  \end{align}
-  %  
-  %  given as in the figure below:
-  %  \[
-  %    \begin{tikzpicture}
-  %      \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
-  %      \draw[-] (-8,0) -- (5,0);
-  %      \draw[-] (0,-5) -- (0,5);
-  %      %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
-  %      \draw[dashed] (0,0) -- (5,-2.113);
-  %      \draw[dashed] (0,0) -- (3.17,-5);
-  %      \node at (1,-0.9) {$\cI$};
-  %      \draw[fill=black] (3.5,-3) circle (2pt);
-  %      \node[right] at (3.5,-3) {$\lambda$};
-  %      \draw[->,thick] (3.5,-3) -- (47/10,-5);
-  %      \draw[-,thick] (3.5,-3) -- (0,26/10);
-  %      \draw[-,thick] (0,26/10) -- (-26/4,0);
-  %      \draw[->,thick] (-26/4,0) -- (-16/4,-5);
-  %      \node at (4.5,-4) {\eqref{ineq:1}};
-  %      \node at (2.34,-0.5) {\eqref{ineq:2}};
-  %      \node at (-3,1.75) {\eqref{ineq:3}};
-  %      \node at (-5.36,-3) {\eqref{ineq:4}};
-  %    \end{tikzpicture}
-  %  \]
-  %\end{lemma}
-  %\begin{proof}
-  %  Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
-
-  %  For $k=2j$, $j<0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
-  %  \[ (\dagger)\ x\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
-  %  We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
-
-  %  \subsubsection*{Claim:} For $i<0$, $\phi_{2i}^{-1}\cC_{2j}(\phi_{2j}\lambda)$ is the region determined by the inequalities 
-  %  \begin{align*}
-  %    \tag{a} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
-  %    \tag{b} u_{2i}^-x+u_{2i-1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
-  %    \tag{c} u_{2i}^-x-u_{2i+1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1;\\
-  %    \tag{d} -u_{2i+2}^-x-u_{2i+1}^+y &\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.
-  %  \end{align*}
-
-  %  We see from \eqref{eq:two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) lies entirely in the region in which $\phi_2$ acts according to the matrix $\left[ \begin{array}{cc} bc-1 & b\\ -c & -1 \end{array}\right]$ of determinant 1.
-  %  By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) transforms into the inequality $-x-by\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$ which corresponds to (a) with $i=-1$.
-  %  Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) intersects the three domains of linearity in which $\phi_2$ acts according to the matrices $\left[ \begin{array}{cc} bc-1 & b\\ -c & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ -c & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
-  %  By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $i=-1$.
-  %  \[ -cx-(bc-1)y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
-  %  \[ -cx+y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
-  %  \[ y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1. \]
-  %  This establishes the base of a downward induction on $i$.
-
-  %  Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2$.
-  %  Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
-  %  Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
-  %  \[u_{2i+2}^-x+u_{2i+1}^+y=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)x+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
-  %  which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-  %  \[-u_{2i+1}^-x-u_{2i}^+y=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)x+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
-  %  which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
-  %  \[u_{2i+3}^-x+u_{2i+2}^+y=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
-  %  which is the inequality (b) for $i+1$.
-  %  Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
-  %  Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
-  %  \[-u_{2i+1}^-x-u_{2i}^+y=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)x+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
-  %  which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
-  %  Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
-  %  Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-  %  \[-u_{2i+1}^-x+u_{2i+2}^+y=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)x+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
-  %  which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
-  %  \[-u_{2i+1}^-x-u_{2i}^+y\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
-  %  which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
-  %  This completes the induction on $i$, proving the Claim and the result for $k$ even.
-
-  %  For $k=2j-1$, $j \le 0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
-  %  \[ (\dagger')\ -x\le u_{2j-1}^+\lambda_0+u_{2j-2}^+\lambda_1 = u_{2j-1}^-\lambda_0+u_{2j-2}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ y\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.\]
-  %  Using that $\phi_{2j-1}^{-1}=\phi_2^{-j}\phi_{-1}^{-1}$, we compute the image inductively as above.
-  %  From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\ddagger'$) lies entirely in the region in which $\phi_{-1}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ of determinant $-1$.
-  %  Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger'$) is transformed by $\phi_{-1}^{-1}$ into the inequality $-y\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$.
-  %  The boundary ray corresponding to ($\dagger'$) intersects both domains of linearity for $\phi_{-1}^{-1}$ and thus produces the inequalities
-  %  \[ -x-by\le u_{2j-1}^-\lambda_0+u_{2j-2}^+\lambda_1 \qquad\text{and}\qquad -x\le u_{2j-1}^+\lambda_0+u_{2j-2}^+\lambda_1.\]
-
-  %  \subsubsection*{Claim:} For $i\le 0$, $\phi_{2i-1}^{-1}\cC_{2j+1}(\phi_{2j+1}\lambda)$ is the region determined by the inequalities 
-  %  \begin{align*}
-  %    \tag{a$'$} u_{2i+1}^-x+u_{2i}^+y &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1;\\
-  %    \tag{b$'$} u_{2i+2}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
-  %    \tag{c$'$} -u_{2i}^-x+u_{2i+1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1;\\
-  %    \tag{d$'$} -u_{2i}^-x-u_{2i-1}^+y &\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.
-  %  \end{align*}
-  %  By essentially the same calculations as above, these inequalities reproduce under the action of $\phi_2^{-1}$ and this completes the proof.
-  %\end{proof}
-
-\section{Lattice Mutations and Linear Inequalities}
-
-  For $b\in\ZZ$, write $[b]_+=max(b,0)$.
-  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
-  \begin{equation}
-    \label{eq:left mutation matrix}
-    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise;} \end{cases}
-  \end{equation}
-  and a matrix $F_{k,\varepsilon}=(f_{ij})$ with
-  \begin{equation}
-    \label{eq:right mutation matrix}
-    f_{ij}=\begin{cases} 1 & \text{if $k\ne i=j$;}\\ -1 & \text{if $k=i=j$;}\\ [-\varepsilon b_{kj}]_+ & \text{if $k=i\ne j$;}\\ 0 & \text{otherwise.} \end{cases}
-  \end{equation}
-  Observe that $E^2_{k,\varepsilon}=\Id$ and $F^2_{k,\varepsilon}=\Id$ for any $k$ and any choice of $\varepsilon$.
-  \begin{lemma}
-    For $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, we have $E_{k,-\varepsilon}E_{k,\varepsilon}=I_n+\varepsilon B^{\bullet k}$ and $E_{k,\varepsilon}-E_{k,-\varepsilon}=\varepsilon B^{\bullet k}$.
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the equality $\varepsilon b_{ij}=[\varepsilon b_{ij}]_+-[-\varepsilon b_{ij}]_+$.
-  \end{proof}
-
-  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_k B=(b'_{ij})$ given by
-  \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
-  One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
-  \begin{remark}
-    Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
-  \end{remark}
-
-  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
-  \begin{itemize}
-    \item $B^{t_0}=B$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $B^{t'}=\mu_k B^t$.
-  \end{itemize}
-
-  (DR: I changed to $\RR$ because it didn't seem like we really cared about integer points at the moment, when we try to link up with minors this will need to be added.)
-  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
-  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
-  where the entries of $E^t_{k,\varepsilon}$ are given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
-  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-  \begin{lemma}
-    Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-    If $\mu\in\lambda+\Col(B^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-  \end{lemma}
-  \begin{proof}
-    Suppose $\mu=\lambda+B^t\alpha$ for some $\alpha\in\RR^n$.
-    Let $\varepsilon$ (resp. $\varepsilon'$) be such that $\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu$ (resp. $\phi^t_k(\lambda)=E^t_{k,\varepsilon'}\lambda$).
-    Then 
-    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+B^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + B^{t'} F^t_{k,\varepsilon}\alpha.\]
-    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + B^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-    Otherwise, 
-    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(B^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(B^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon B^{t'} \lambda_k \mathbf{e}_k\]
-    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
-  \end{proof}
 
@@
   \end{proof}
-
-  The dominance polygon pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region defined by $x\leq \lambda_0, y\geq\lambda_1$, and the following inequalities:
- {
-    \everymath={\displaystyle}
-    \def\arraystretch{2.8}
-  \[
-  \begin{array}{rcccl}
-    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)+(y-\lambda_1) & \leq & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
-    \\
-    \min\left(-c\lambda_0,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_0)-(y-\lambda_1) & \leq & 0
-    \\
-    0 & \leq &  -(x-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_1) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
-    \\
-    \min\left(b \lambda_1,0\right) & \leq & (x-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_1) & \leq & 0
-  \end{array}
-\]
-}
 
@@
 
+    \bibitem{qin}
+      Fan's paper
+
     \bibitem{rupel}

### 2022-04-09 dominance_regions.tex
more intro edits
Organization overview

@@
   Qin introduced a partial order on $\bfg$-vectors called the \emph{dominance order} and showed that given two pointed bases $x=\{x_\lambda\}$, $y=\{y_\lambda\}$, $y_\mu$ can appear in the expansion of $x_\lambda$ in terms of $y$ only if $\lambda$ dominates $\mu$ (cf.
-\cite[Mainthm]{qin} and \ref{def:dominance}).
+\cite[Theorem 1.2.1]{qin}).
 
@@
 
-  \begin{theorem}
-    \label{th:dominance vertices}
+  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  \begin{corollary}
+    \label{cor:dominance vertices}
     There are six classes of dominance polytopes.
@@
     \end{enumerate}
-  \end{theorem}
+  \end{corollary}
 
@@
       \draw [thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
-      \draw [dashed, thick]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) -- (\x,\y);
+      %\draw [dashed, thick]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) -- (\x,\y);
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
@@
 In Section~\ref{sec:chebyshev}, we collect useful results related to two-parameter Chebyshev polynomials which support our main calculations.
+Section~\ref{sec:tropical} contains calculations related to the transformation of $\bfg$-vectors under mutations.
+Section~\ref{sec:dominance inequalities} proves Theorem~\ref{th:dominance inequalities}.
+Section~\ref{sec:dominance vertices} proves Corollary~\ref{cor:dominance vertices}.
+Section~\ref{sec:maximum support} proves Theorem~\ref{th:maximum support}.
+The paper ends with Section~\ref{sec:affine} interpreting the dominance polygon in terms of generalized minors in the cases where $bc=4$.
 
@@
 \section{$\bfg$-vector Mutations}
+\label{sec:tropical}
+
   We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors when expanding a pointed expression of the form~\eqref{eq:pointed} in terms of a cluster $\{x_k,x_{k+1}\}$.
@@
 
-  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
   %\begin{lemma}
@@
     \label{le:imaginary stability}
-    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{2j}(\lambda)\in\cI$ and $\phi_{2j+1}(\lambda)\in\cI'$.
-  \end{lemma}
-  \begin{proof}
-    Since $\phi_{2j}=\phi_2^j$ and $\phi_{2j+1}=\phi_1\phi_{t_2}^j$, the result follows from the cases $j=1$ and $j=0$, respectively.
-    The claim is immediate for $\phi_2$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_2$ is linear in $\cI$.
-    Now, since $b>0$, we have $\phi_1(\lambda)=(-\lambda_0,c\lambda_0+\lambda_1)$.
-    It follows that $\phi_1\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$.
-    The result then follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_1$ in this region.
+    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{2j}(\lambda)\in\cI$.
+  \end{lemma}
+  \begin{proof}
+    Since $\phi_{2j}=\phi_2^j$, the result follows from the cases $j=1$.
+    But this is immediate for $\phi_2$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_2$ is linear in $\cI$.
   \end{proof}
@@
 \section{Proof of Theorem~\ref{th:dominance inequalities}}
+\label{sec:dominance inequalities}
 
@@
 
-\section{Rank Two}
-
-  \begin{theorem}
-    There are six classes of dominance polytopes.
-    \begin{enumerate}
-      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
-    \end{enumerate}
-  \end{theorem}
-  \begin{proof}
-    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
-    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1=\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\]
-    or 
-    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1.\]
-    The first equations reduces to $c\lambda_0+2\lambda_1=0$, while the second reduces to $2\lambda_0+b\lambda_1=0$.
-    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
-  \end{proof}
-
-  \begin{lemma}
-    \label{le:one direction}
-    For $\lambda\in\cI\cap\ZZ^2$, 
-    \begin{enumerate}
-      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_0-b\lambda_1,\lambda_1)$.
-      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1)$, and $(\lambda_0,-c\lambda_0+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1)$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
-    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
-  \end{proof}
-\section{The Total Domination Polyhedron}
-
-  Define the \emph{total domination polyhedron} $\cD:=\{(\lambda,\mu):\mu\in\cP(\lambda)\}$, i.e. this is the set of all pairs where $\lambda$ dominates $\mu$.
-  Write $\pi_1:\cD\to\RR^n$ for the projection to $\lambda$ and $\pi_2:\cD\to\RR^n$ for the projection to $\mu$.
-  \begin{itemize}
-    \item Is it a polyhedron?
-    \item The lemma below might suggest so.  
-      Indeed, if it is, by the Decomposition Theorem, we can write $\cD$ as the Minkowski sum of a polyhedral cone (almost certainly $\cI$) and a convex polytope (what is it?).
-      I am ignoring that it should really be the union of this polyhedron with a plane if the previous sentence holds any water.
-    \item Actually, we might need to take the union of several polyhedra to account for the variations in the fibers $\pi_1^{-1}(\lambda)$.
-  \end{itemize}
-
-  Is the following result true beyond rank 2?
-  \begin{lemma}
-    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
-  \end{lemma}
-  \begin{proof}
-    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_0,\lambda_1)$ where
-    \[\lambda_0=\frac{2b\mu_1-4\mu_0}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_1=\frac{2c\mu_0-4\mu_1}{bc-4+\sqrt{bc(bc-4)}}.\]
-    (This comes from setting $\mu$ to be the vertex opposite $\lambda$ inside the dominance region $\cP(\lambda)$ and then solving for $\lambda$.)
-  \end{proof}
-  \begin{remark}
-    We want to understand what the curve is that results when we have $\mu$ lie along the unit circle, this should be possible by plugging $(\cos(\theta),\sin(\theta))$ into this formula for $\lambda$ and seeing what ellipse we get.
-  \end{remark}
-
-\section{Proof of Theorem~\ref{th:dominance vertices}}
+\section{Proof of Corollary~\ref{cor:dominance vertices}}
+\label{sec:dominance vertices}
+
+  This follows from basic manipulations finding the intersection points of the boundary segments determined by the inequalities from Theorem~\ref{th:dominance inequalities}.
+  Note that in each of the cases (2), (4), and (6) there are only four inequalities to consider while in cases (3) and (5) there are only three inequalities to consider.
+  We leave the details as an exercise for the reader.
 
 \section{Proof of Theorem~\ref{th:maximum support}}
+\label{sec:maximum support}
 
@@
 \label{sec:affine}
+
   In this section we compare our main result with the construction of \cite{RSW19} in the case $b=c=2$.
@@
 
-  For a partition $\lambda \vdash n$ let $e_\lambda$, $s_\lambda$, and $m_\lambda$ denote the elementary, Shur, and monomial symmetric functions associated to the partition $\lambda$ evaluated at $\bfa$.
+  For a partition $\lambda \vdash n$ let $e_\lambda$, $s_\lambda$, and $m_\lambda$ denote the elementary, Schur, and monomial symmetric functions associated to the partition $\lambda$ evaluated at $\bfa$.
   Recall that $m_{1^{(n)}} = s_{1^{(n)}} = e_n$.
@@
   \begin{thebibliography}{XXX}
+    \bibitem{cgmmrsw}
+      our other paper
+
+    \bibitem{ghkk}
+      Gross et al
 
@@
 \href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
+
+    \bibitem{RSW19}
+      Our paper
   \end{thebibliography}

### 2022-04-09 dominance_regions.tex
Lemma 2.3 and Remark 2.4

@@
     We have
-    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b};\]
-    \[\lim_{i\to-\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to-\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b}.\]
+    \[\lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+}=\frac{bc+\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+}=\frac{bc-\sqrt{bc(bc-4)}}{2b};\]
+    \[\lim_{i\to-\infty} \frac{u_{i-1}^-}{u_i^+}=\frac{bc+\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to-\infty} \frac{u_i^-}{u_{i-1}^+}=\frac{bc-\sqrt{bc(bc-4)}}{2b}.\]
     Moreover, each of these sequences is monotonic.
   \end{lemma}
+  \begin{remark}
+    The analogous limits with $+$ and $-$ reversed are obtained from these by interchanging the roles of $b$ and $c$.
+  \end{remark}
   \begin{proof}
@@
     It follows that
-    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    \[\lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
     which is equivalent to the desired expression.
@@
     so that
-    \[\lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    \[\lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
     which is again equivalent to the desired expression.
@@
 
-    For the final claim, observe that $\frac{-u_i^{-\varepsilon}}{u_{i-1}^\varepsilon}<\frac{-u_{i+1}^{-\varepsilon}}{u_i^\varepsilon}$ and $\frac{-u_i^{-\varepsilon}}{u_{i+1}^\varepsilon}<\frac{-u_{i-1}^{-\varepsilon}}{u_i^\varepsilon}$ are both equivalent to $u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon<u_i^{-\varepsilon}u_i^\varepsilon$.
+    For the final claim, observe that $\frac{u_{i+1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i-1}^\varepsilon}<$ and $\frac{u_{i-1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i+1}^\varepsilon}$ are both equivalent to $u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon<u_i^{-\varepsilon}u_i^\varepsilon$.
     This is immediate from the following induction:

### 2022-04-09 dominance_regions.tex
Section 4 edit

@@
   Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP(\lambda)$:
-  \[ 0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1);\]
+  \[ 0 \le (\mu_0-\lambda_0)+\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
   \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le 0;\]
-  \[ \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) \le -c\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2b}b\lambda_1.\]
-
-  This completes the proof of Theorem~\ref{th:dominance inequalities}.
+  \[ c\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2b}b\lambda_1 \le -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).\]
+  These can easily be seen to be equivalent to the remaining inequalities from Theorem~\ref{th:dominance inequalities} and this complete the proof.
 

### 2022-04-09 dominance_regions.tex
opposite g-vectors
Preparing for the proof of Theorem 1.4

@@
 \newcommand{\cD}{\mathcal{D}}
+\newcommand{\cG}{\mathcal{G}}
 \newcommand{\cI}{\mathcal{I}}
@@
   In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
-  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance polygon} $\cP_\lambda$.
+  \sayDR{Should we write $\cD_\lambda$ instead for "dominance"?}
   %In this case, we compute the possible transitions between any two pointed bases.
@@
     \label{th:dominance inequalities}
-    The dominance polygon $\cP(\lambda)$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
+    The dominance polygon $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
     {
@@
     \begin{enumerate}
-      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
+      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP_\lambda$ is the point $\lambda$. 
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP_\lambda$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP_\lambda$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP_\lambda$ is the kite with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP_\lambda$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP_\lambda$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
     \end{enumerate}
@@
     \]
-    The \emph{dominance region} $\cP(\lambda)$ is the intersection  $\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$.
-    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
+    The \emph{dominance region} $\cP_\lambda$ is the intersection  $\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$.
+    When $\mu\in\cP_\lambda$, we say \emph{$\lambda$ dominates $\mu$}.
   \end{definition}
@@
 
-  Here we explicitly compute the dominance regions $\cP(\lambda)$.
+  Here we explicitly compute the dominance regions $\cP_\lambda$.
   When $\lambda$ is not imaginary, the dominance region is particularly simple.
@@
     \label{le:cluster monomials}
-    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
+    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP_\lambda=\{\lambda\}$.
   \end{lemma}
@@
 
-  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP(\lambda)$ for $\lambda\in\cI$.
+  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP_\lambda$ for $\lambda\in\cI$.
 
@@
   We are now ready to prove Theorem~\ref{th:dominance inequalities}.
-  The dominance region $\cP(\lambda)=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of the inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.
+  The dominance region $\cP_\lambda=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of the inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.
 
@@
   \[ 0 \le -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \]
-  determining a boundary of $\cP(\lambda)$.
+  determining a boundary of $\cP_\lambda$.
 
@@
   \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
-  determining a boundary of $\cP(\lambda)$.
+  determining a boundary of $\cP_\lambda$.
   Observe further that $\mu_0-\lambda_0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
@@
   \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1 \]
-  determining a boundary of $\cP(\lambda)$.
-
-  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP(\lambda)$:
+  determining a boundary of $\cP_\lambda$.
+
+  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
   \[ 0 \le (\mu_0-\lambda_0)+\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
@@
 \label{sec:maximum support}
+
+  Every pointed basis element for $\cA(b,c)$ admits an opposite $\bfg$-vector arising by interchanging the roles of $b$, $c$ and $x_0$, $x_1$ in \eqref{eq:pointed}. 
+  \begin{lemma}
+    Given a $\bfg$-vector $\lambda$, the opposite $\bfg$-vector $\lambda'$ is obtained as follows:
+    \begin{itemize}
+      \item if $\lambda_0,\lambda_1\ge0$, then $\lambda'=\lambda$;
+      \item if $\lambda_1\ge0$ and $\lambda_0<0$, then $\lambda'=(\lambda_0,-c\lambda_0+\lambda_1)$;
+      \item if $\lambda_0>0$ and $\lambda_0+b\lambda_1>0$, then $\lambda'=(\lambda_0+b\lambda_1,\lambda_1)$;
+      \item otherwise, $\lambda'=(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1)$.
+    \end{itemize}
+  \end{lemma}
+
+  The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{LLZ,cgmmrsw}.
+  This is indicated by the solid and dashed lines in Theorem~\ref{th:maximum support} where dashed lines indicate points that are excluded from the support (note that the white dot does not indicate that this point is excluded).
+  For our purposes, it is enough to observe the following closure property for the greedy support.
+  \begin{definition}
+    A subset $\cS\subset\RR^2$ is called \emph{DL-convex} if $\lambda,\mu\in\cS$ implies $\big(\min(\mu_0,\lambda_0),\min(\mu_1,\lambda_1)\big)\in\cS$.
+  \end{definition}
+  In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector indicated by a black dot and the opposite $\bfg$-vector indicated by a white dot in Theorem~\ref{th:maximum support}.
+  Write $\overline{\cG}_\lambda$ for the cone of the DL-closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
+  Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.
 

### 2022-04-09 dominance_regions.tex
More towards the proof of Theorem 1.4

@@
   \end{lemma}
+  In particular, we obtain an opposite dominance region $\cP'_\lambda$ for each $\bfg$-vector $\lambda$.
+  \begin{lemma}
+    For $\lambda\in\cI$, the opposite dominance region $\cP'_\lambda$ is determined by the following inequalities:
+    The opposite dominance polygon $\cP'_\lambda$ pointed at $\lambda'=(\lambda'_0,\lambda'_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \geq \lambda'_0, \mu_1 \leq\lambda'_1$, and the following inequalities:
+    \sayDR{These still need to be changed}
+    {
+      \everymath={\displaystyle}
+      \def\arraystretch{2.8}
+      \[
+        \begin{array}{rcccl}
+          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \leq & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
+          \\
+          \min\left(-c\lambda_0,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & 0
+          \\
+          0 & \leq &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
+          \\
+          \min\left(b \lambda_1,0\right) & \leq & (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \leq & 0
+        \end{array}
+      \]
+    }
+  \end{lemma}
 
@@
   \begin{definition}
-    A subset $\cS\subset\RR^2$ is called \emph{DL-convex} if $\lambda,\mu\in\cS$ implies $\big(\min(\mu_0,\lambda_0),\min(\mu_1,\lambda_1)\big)\in\cS$.
+    A subset $\cS\subset\RR^2$ is called \emph{DL-convex} if $\lambda,\mu\in\cS$ implies $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)\in\cS$.
   \end{definition}
-  In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector indicated by a black dot and the opposite $\bfg$-vector indicated by a white dot in Theorem~\ref{th:maximum support}.
+  In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector $\lambda$ indicated by a black dot and the opposite $\bfg$-vector $\lambda'$ indicated by a white dot in Theorem~\ref{th:maximum support}.
   Write $\overline{\cG}_\lambda$ for the cone of the DL-closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
   Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.
+
+  Recall the regions $\cS_\lambda$ from Theorem~\ref{th:maximum support}.
 

### 2022-04-09 dominance_regions.tex
Cleanup

@@
 
-  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
-    For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
-    \begin{enumerate}
-      \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
-      \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
-      \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
-      \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
-      \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
-      \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
-      $$\aligned
-      R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
-      &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
-      &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
-      \endaligned
-      $$
-    \end{enumerate}
-    Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
-  \end{theorem}
-
 \section{The affine case}

### 2022-04-09 dominance_regions.tex
min-convex

@@
   Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance polygon} $\cP_\lambda$.
-  \sayDR{Should we write $\cD_\lambda$ instead for "dominance"?}
   %In this case, we compute the possible transitions between any two pointed bases.
@@
   \begin{definition}
-    A subset $\cS\subset\RR^2$ is called \emph{DL-convex} if $\lambda,\mu\in\cS$ implies $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)\in\cS$.
+    A subset $\cS\subset\RR^2$ is called \emph{min-convex} if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
   \end{definition}
   In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector $\lambda$ indicated by a black dot and the opposite $\bfg$-vector $\lambda'$ indicated by a white dot in Theorem~\ref{th:maximum support}.
-  Write $\overline{\cG}_\lambda$ for the cone of the DL-closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
+  Write $\overline{\cG}_\lambda$ for the cone of the min-convex-closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
   Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.

### 2022-04-09 dominance_regions.tex
inequalities

@@
     The opposite dominance polygon $\cP'_\lambda$ pointed at $\lambda'=(\lambda'_0,\lambda'_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \geq \lambda'_0, \mu_1 \leq\lambda'_1$, and the following inequalities:
-    \sayDR{These still need to be changed}
     {
@@
         \begin{array}{rcccl}
-          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \leq & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
+          0 & \leq & (\mu_0-\lambda_0)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & -\frac{b c-\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1
           \\
-          \min\left(-c\lambda_0,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & 0
+          -c\lambda'_0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda'_0)-(\mu_1-\lambda'_1) & \leq & 0
           \\
-          0 & \leq &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
+          0 & \leq &  -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & c\lambda_0+\frac{b c-\sqrt{b c (b c-4)}}{2b}b\lambda_1
           \\
-          \min\left(b \lambda_1,0\right) & \leq & (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \leq & 0
+          b \lambda'_1 & \leq & (\mu_0-\lambda'_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda'_1) & \leq & 0
         \end{array}
@@
   In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector $\lambda$ indicated by a black dot and the opposite $\bfg$-vector $\lambda'$ indicated by a white dot in Theorem~\ref{th:maximum support}.
-  Write $\overline{\cG}_\lambda$ for the cone of the min-convex-closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
+  Write $\overline{\cG}_\lambda$ for the cone of the min-convex closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
   Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.

### 2022-04-11 dominance_regions.tex
inequalities
Just gross...please tell me I made a mistake

@@
         \begin{array}{rcccl}
-          0 & \leq & (\mu_0-\lambda_0)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & -\frac{b c-\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1
+          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \leq & -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1
           \\
@@
   \end{lemma}
+  \begin{proof}
+    As stated above, we obtain the opposite $\bfg$-vector by interchanging $b$, $c$ and $\lambda_0,\lambda_1$.
+    It follows that the opposite dominance region is given by the following inequalities (c.f. Theorem~\ref{th:dominance inequalities}):
+    {
+      \everymath={\displaystyle}
+      \def\arraystretch{2.8}
+      \[
+        \begin{array}{rcccl}
+          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) & \leq & -b\lambda'_1-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda'_0
+          \\
+          -b\lambda'_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)-(\mu_0-\lambda'_0)
+          \\
+          0 & \leq &  -(\mu_1-\lambda'_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda'_0) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda'_1+c\lambda'_0
+          \\
+          c \lambda'_0 & \leq & (\mu_1-\lambda'_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 b} (\mu_0-\lambda'_0)
+        \end{array}
+      \]
+    }
+    {
+      \everymath={\displaystyle}
+      \def\arraystretch{2.8}
+      \[
+        \begin{array}{rcccl}
+          0 & \leq & -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & c\lambda_0 + \frac{b c-\sqrt{b c (b c-4)}}{2 b}b\lambda_1
+          \\
+           & & (\mu_0-\lambda_0) -\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & -\frac{b c+\sqrt{b c (b c-4)}}{2}(\lambda_0+b\lambda_1)+2b\lambda_1
+          \\
+          \frac{b c - 2 +\sqrt{b c (b c-4)}}{2}(c\lambda_0+(bc-2)\lambda_1) -c\lambda_0 -2\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) & \leq & -c\lambda_0 - \frac{b c+\sqrt{b c (b c-4)}}{2 b}b\lambda_1
+          \\
+          -c\lambda_0+\frac{b c-2+\sqrt{b c (b c-4)}}{2}(c\lambda_0 + \sqrt{b c (b c-4)}\lambda_1) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) & \leq & -c\lambda_0 - \frac{b c+\sqrt{b c (b c-4)}}{2 b}b\lambda_1
+          \\
+          b\lambda_1 & \leq & - (\mu_0-\lambda_0) + \frac{b c+\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) 
+        \end{array}
+      \]
+    }
+    where we note that the max/min and the right hand "$\le0$" can be dropped inside the imaginary cone.
+    The claimed inequalities can be obtained from these using $\lambda'_0=\lambda_0+b\lambda_1$ and $\lambda'_1=-c\lambda_0-(bc-1)\lambda_1$.
+    We leave the details to the reader.
+  \end{proof}
 

### 2022-04-19 dominance_regions.tex
Total support inequalities
Some proof of Theorem 1.4

--- 2022-04-09 dominance_regions.tex
@@
-\documentclass{amsart}
+\documentclass[a3paper]{amsart}
 \usepackage{amsmath}
@@
   \end{lemma}
+
   In particular, we obtain an opposite dominance region $\cP'_\lambda$ for each $\bfg$-vector $\lambda$.
   \begin{lemma}
-    For $\lambda\in\cI$, the opposite dominance region $\cP'_\lambda$ is determined by the following inequalities:
-    The opposite dominance polygon $\cP'_\lambda$ pointed at $\lambda'=(\lambda'_0,\lambda'_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \geq \lambda'_0, \mu_1 \leq\lambda'_1$, and the following inequalities:
+    For $\lambda\in\cI$, the opposite dominance polygon $\cP'_\lambda$ pointed at its opposite $\bfg$-vector $\lambda'=(\lambda'_0,\lambda'_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \geq \lambda'_0, \mu_1 \leq\lambda'_1$, and the following inequalities:
     {
@@
         \begin{array}{rcccl}
-          0 & \leq & (\mu_0-\lambda_0)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & -\frac{b c-\sqrt{b c (b c-4)}}{2c}c\lambda_0-b\lambda_1
+          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) & \leq & -b\lambda'_1-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda'_0
           \\
-          -c\lambda'_0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda'_0)-(\mu_1-\lambda'_1) & \leq & 0
+          -b\lambda'_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)-(\mu_0-\lambda'_0)
           \\
-          0 & \leq &  -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & c\lambda_0+\frac{b c-\sqrt{b c (b c-4)}}{2b}b\lambda_1
+          0 & \leq &  -(\mu_1-\lambda'_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda'_0) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda'_1+c\lambda'_0
           \\
-          b \lambda'_1 & \leq & (\mu_0-\lambda'_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda'_1) & \leq & 0
+          c \lambda'_0 & \leq & (\mu_1-\lambda'_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 b} (\mu_0-\lambda'_0)
         \end{array}
@@
   \end{lemma}
+  \begin{proof}
+    As stated above, we obtain the opposite $\bfg$-vector by interchanging $b$, $c$ and swapping the roles of $\lambda_0,\lambda_1$.
+    Translating from Theorem~\ref{th:dominance inequalities}, it immediately follows that the opposite dominance region is given by the claimed inequalities.
+    %{
+    %  \everymath={\displaystyle}
+    %  \def\arraystretch{2.8}
+    %  \[
+    %    \begin{array}{rcccl}
+    %      0 & \leq & -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & c\lambda_0 + \frac{b c-\sqrt{b c (b c-4)}}{2 b}b\lambda_1
+    %      \\
+    %       & & (\mu_0-\lambda_0) -\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & -\frac{b c+\sqrt{b c (b c-4)}}{2}(\lambda_0+b\lambda_1)+2b\lambda_1
+    %      \\
+    %      \frac{b c - 2 +\sqrt{b c (b c-4)}}{2}(c\lambda_0+(bc-2)\lambda_1) -c\lambda_0 -2\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) & \leq & -c\lambda_0 - \frac{b c+\sqrt{b c (b c-4)}}{2 b}b\lambda_1
+    %      \\
+    %      -c\lambda_0+\frac{b c-2+\sqrt{b c (b c-4)}}{2}(c\lambda_0 + \sqrt{b c (b c-4)}\lambda_1) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) & \leq & -c\lambda_0 - \frac{b c+\sqrt{b c (b c-4)}}{2 b}b\lambda_1
+    %      \\
+    %      b\lambda_1 & \leq & - (\mu_0-\lambda_0) + \frac{b c+\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) 
+    %    \end{array}
+    %  \]
+    %}
+  \end{proof}
+
+  For $\lambda\in\cI$, the maximal support $\cS_\lambda$ is determined by the following inequalities:
+  \begin{align*}
+    \lambda_1 &\leq \mu_1\\
+    \lambda'_0 &\leq \mu_0\\
+    0 &\leq -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1)\\
+    0 &\leq -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda'_0) -(\mu_1-\lambda'_1)
+  \end{align*}
+  We claim that $\cP_\lambda,\cP'_\lambda\subset\cS_\lambda$.
+
+  Observe that the last equality can be rewritten as
+  \[ \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) \leq -c\lambda_0 - \frac{b c + \sqrt{b c (b c-4)}}{2 } \lambda_1,\]
+  which together with the second to last inequality gives two boundaries for the dominance region $\cP_\lambda$.
+  Note then that, under the assumption $\mu_0\leq\lambda_0$, the inequality 
+  \[0 \leq \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1)\]
+  defining another boundary of $\cP_\lambda$ is more restrictive than the inequality $\lambda_1\leq\mu_1$ bounding $\cS_\lambda$.
+
+  For $\lambda\in\cI$, it follows from Corollary~\ref{cor:dominance vertices} that the minimum value for $\mu_0$ inside $\cP_\lambda$ occurs when $\mu_1=0$, i.e.
+either at the point $\big( \lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1 , 0 \big)$ when $0 \leq c\lambda_0+2\lambda_1$ or at the point $-\frac{bc+\sqrt{bc(bc-4)}}{2c} \big( \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1 , 0 \big)$ when $c\lambda_0+2\lambda_1 \leq 0$.
+  The second point can be rewritten as
+  \[\big(\lambda_0 -\frac{bc+\sqrt{bc(bc-4)}}{2c} c\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c} \lambda_1 , 0 \big)\]
+  but, since $c\lambda_0\le -2\lambda_1$, the first coordinate is greater than $\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1$.
+  Then, using $\frac{bc+\sqrt{bc(bc-4)}}{2c}<b$, we see that the minimum value of $\mu_0$ inside $\cP_\lambda$ satisfies the inequality $\lambda_0+b\lambda_1 \leq \mu_0$.
+  In particular, combining with the observation above, we see that $\cP_\lambda\subset\cS_\lambda$.
+
+  Similarly, the second to last inequality can be rewritten as
+  \[ \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) \leq -b\lambda'_1-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda'_0,\]
+  which together with the last inequality gives two boundaries for the opposite dominance region $\cP'_\lambda$.
+  Note then that, under the assumption $\mu_1\leq\lambda'_1$, the inequality
+  \[ 0 \leq \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) \]
+  defining another boundary of $\cP_\lambda$ is more restrictive than the inequality $\lambda'_0\leq\mu_0$ bounding $\cS_\lambda$.
+  As above, the minimum value of $\mu_1$ inside $\cP'_\lambda$ occurs when $\mu_0=0$, i.e. either at the point ... when ... or at the point ... when ...
+  Then arguing as above, we see that the minimum value of $\mu_1$ inside $\cP'_\lambda$ satisfies the inequality $\lambda_1\leq\mu_1$ and so $\cP'_\lambda\subset\cS_\lambda$.
+  \sayDR{We just need to write down the intersection points of $\cP'_\lambda$ and the $y$-axis.}
 

### 2022-04-19 dominance_regions.tex
Finished the proof the dominance regions are contained in the total support region

@@
 
-  For $\lambda\in\cI$, it follows from Corollary~\ref{cor:dominance vertices} that the minimum value for $\mu_0$ inside $\cP_\lambda$ occurs when $\mu_1=0$, i.e.
-either at the point $\big( \lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1 , 0 \big)$ when $0 \leq c\lambda_0+2\lambda_1$ or at the point $-\frac{bc+\sqrt{bc(bc-4)}}{2c} \big( \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1 , 0 \big)$ when $c\lambda_0+2\lambda_1 \leq 0$.
+  It follows from Corollary~\ref{cor:dominance vertices} that the minimum value for $\mu_0$ inside $\cP_\lambda$ occurs when $\mu_1=0$, i.e.
+either at the point $\big( \lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1 , 0 \big)$ when $0 \leq c\lambda_0+2\lambda_1$ or at the point $-\frac{bc+\sqrt{bc(bc-4)}}{2c} \big( \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1 , 0 \big)$ when $c\lambda_0+2\lambda_1<0$.
   The second point can be rewritten as
   \[\big(\lambda_0 -\frac{bc+\sqrt{bc(bc-4)}}{2c} c\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c} \lambda_1 , 0 \big)\]
-  but, since $c\lambda_0\le -2\lambda_1$, the first coordinate is greater than $\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1$.
-  Then, using $\frac{bc+\sqrt{bc(bc-4)}}{2c}<b$, we see that the minimum value of $\mu_0$ inside $\cP_\lambda$ satisfies the inequality $\lambda_0+b\lambda_1 \leq \mu_0$.
+  but, since $c\lambda_0 < -2\lambda_1$, the first coordinate is greater than $\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1$.
+  Then, using $\frac{bc+\sqrt{bc(bc-4)}}{2c}<b$ and $\lambda_1<0$, we see that the minimum value of $\mu_0$ inside $\cP_\lambda$ satisfies the inequality $\lambda'_0=\lambda_0+b\lambda_1 \leq \mu_0$.
   In particular, combining with the observation above, we see that $\cP_\lambda\subset\cS_\lambda$.
@@
   defining another boundary of $\cP_\lambda$ is more restrictive than the inequality $\lambda'_0\leq\mu_0$ bounding $\cS_\lambda$.
-  As above, the minimum value of $\mu_1$ inside $\cP'_\lambda$ occurs when $\mu_0=0$, i.e. either at the point ... when ... or at the point ... when ...
-  Then arguing as above, we see that the minimum value of $\mu_1$ inside $\cP'_\lambda$ satisfies the inequality $\lambda_1\leq\mu_1$ and so $\cP'_\lambda\subset\cS_\lambda$.
-  \sayDR{We just need to write down the intersection points of $\cP'_\lambda$ and the $y$-axis.}
+  As above, the minimum value of $\mu_1$ inside $\cP'_\lambda$ occurs when $\mu_0=0$, i.e. either at the point $\big(0, \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1 \big)$
+  %\[\big(0, \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1 \big) = \big(0, -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\lambda_0+b\lambda_1)+\lambda_1 \big)\]
+  when $0 \leq 2\lambda'_0+b\lambda'_1$ or at the point $-\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, \lambda'_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda'_1 \big)$
+  %\[-\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, \lambda'_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda'_1 \big) = -\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, -\frac{bc-2+\sqrt{bc(bc-4)}}{2}(\lambda_0+b\lambda_1)+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1 \big)\]
+  when $2\lambda'_0+b\lambda'_1<0$.
+  The second point can be rewritten as
+  \[\big(0, -\frac{bc+\sqrt{bc(bc-4)}}{2b} \lambda'_0-\frac{bc+\sqrt{bc(bc-4)}}{2b} b\lambda'_1+\lambda'_1 \big)\]
+  but, since $b\lambda'_1\le -2\lambda'_0$, the first coordinate is greater than $\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1$.
+  Then, using $\frac{bc+\sqrt{bc(bc-4}}{2b}<c$ and $\lambda'_0<0$, we see that the minimum value of $\mu_1$ inside $\cP'_\lambda$ satisfies the inequality $\lambda_1=c\lambda'_0+\lambda'_1\le\mu_1$ and so $\cP'_\lambda\subset\cS_\lambda$.
 

### 2022-04-25 dominance_regions.tex
A little more of the proof of Theorem 1.4
Finished proof of Theorem 1.4

@@
 \newcommand{\cQ}{\mathcal{Q}}
+\newcommand{\cR}{\mathcal{R}}
 \newcommand{\cS}{\mathcal{S}}
@@
 
-  Recall the regions $\cS_\lambda$ from Theorem~\ref{th:maximum support}.
+  As we saw above, for any $\bfg$-vector $\mu\in\cP_\lambda$ its opposite $\bfg$-vector $\mu'$ is also contained in $\cS_\lambda$.
+  But $\cS_\lambda$ is min-convex and closed under downward scaling, i.e. for any $\mu\in\cS_\lambda$ we have $t\mu\in\cS_\lambda$ for $0\le t\le 1$.
+  It follows that $\overline{\cG}_\mu\subset\cS_\lambda$ for any $\mu\in\cP_\lambda$.
+
+  In particular, $\cG_\lambda\subset\cS_\lambda$.
+  Note also that the dominance region $\cP_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR_1$ defined by the inequalities $\mu_0\ge0$ and $\lambda_1\mu_0-\lambda_0\mu_1\ge0$.
+  Similarly, the opposite dominance region $\cP'_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR_2$ defined by the inequalities $\mu_1\ge0$ and $-\lambda'_1\mu_0+\lambda'_0\mu_1\ge0$.
+  But $\cS_\lambda=\cG_\lambda\cup\cR_1\cup\cR_2$ and so $\cS_\lambda$ is the maximum possible support for an element pointed at $\lambda$.
 

### 2022-04-25 dominance_regions.tex
Better

@@
   Similarly, the opposite dominance region $\cP'_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR_2$ defined by the inequalities $\mu_1\ge0$ and $-\lambda'_1\mu_0+\lambda'_0\mu_1\ge0$.
-  But $\cS_\lambda=\cG_\lambda\cup\cR_1\cup\cR_2$ and so $\cS_\lambda$ is the maximum possible support for an element pointed at $\lambda$.
+  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR_1)\cup(\cS_\lambda\cap\cR_2)$ and so $\cS_\lambda$ is the maximum possible support for an element pointed at $\lambda$.
 

### 2022-04-25 dominance_regions.tex
Better still
Edits

@@
   In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
-  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance polygon} $\cP_\lambda$.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance region} $\cP_\lambda$.
   %In this case, we compute the possible transitions between any two pointed bases.
@@
     \label{th:dominance inequalities}
-    The dominance polygon $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
+    The dominance region $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
     {
@@
     \label{cor:dominance vertices}
-    There are six classes of dominance polytopes.
+    There are six classes of dominance regions, these are (possibly degenerate) polygons given as follows.
     \begin{enumerate}
@@
     \begin{enumerate}
-      \item If $\lambda$ lies outside of $\cI$, there are the following possibilities:
+      \item If $\lambda$ lies outside of $\cI$, then the support of $x_\lambda$ is precisely the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cS_\lambda$ given as follows:
         \begin{enumerate}
@@
   Every pointed basis element for $\cA(b,c)$ admits an opposite $\bfg$-vector arising by interchanging the roles of $b$, $c$ and $x_0$, $x_1$ in \eqref{eq:pointed}. 
+  One can easily compute the following correspondence.
   \begin{lemma}
@@
   In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector $\lambda$ indicated by a black dot and the opposite $\bfg$-vector $\lambda'$ indicated by a white dot in Theorem~\ref{th:maximum support}.
-  Write $\overline{\cG}_\lambda$ for the cone of the min-convex closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
+  Write $\overline{\cG}_\lambda$ for the downward scaling of the min-convex closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
   Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.
@@
   But $\cS_\lambda$ is min-convex and closed under downward scaling, i.e. for any $\mu\in\cS_\lambda$ we have $t\mu\in\cS_\lambda$ for $0\le t\le 1$.
-  It follows that $\overline{\cG}_\mu\subset\cS_\lambda$ for any $\mu\in\cP_\lambda$.
+  It follows that $\overline{\cG}_\mu\subset\cS_\lambda$ for any $\mu\in\cP_\lambda$ and so the support of any basis element pointed at $\lambda$ is contained in $\cS_\lambda$.
 

### 2022-04-25 dominance_regions.tex
Edits

@@
   Given a Laurent polynomial in $\ZZ[x_0^{\pm1},x_1^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
+  Given a $\bfg$-vector $\lambda$, in the next result we identify a region $\cS_\lambda$ whose lattice points are the maximum possible support of a pointed basis element $x_\lambda$. 
   \begin{theorem}
     \label{th:maximum support}
-    For a $\bfg$-vector $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ the support for a pointed basis vector $x_\lambda$ is contained in the (possibly degenerate) lattice quadrilateral $\cS_\lambda$ given as follows:
+    Let $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ be the $\bfg$-vector for a pointed basis element $x_\lambda$.
     \begin{enumerate}

### 2022-04-25 dominance_regions.tex
Edits

@@
     \label{th:dominance inequalities}
-    The dominance region $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
+    The dominance region $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the polygon consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
     {
@@
     \label{cor:dominance vertices}
-    There are six classes of dominance regions, these are (possibly degenerate) polygons given as follows.
+    There are six classes of dominance polygons.
     \begin{enumerate}
@@
         \end{enumerate}
-      \item If $\lambda$ lies inside of $\cI$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
+      \item If $\lambda$ lies inside of $\cI$, then the support of $x_\lambda$ is contained in $\cS_\lambda$ with corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
+        Moreover, there is an element $x_\lambda\in\cA(b,c)$ whose support is precisely the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cS_\lambda$.
     \end{enumerate}

### 2022-04-25 dominance_regions.tex
Edits

@@
       \item If $\lambda$ lies inside of $\cI$, then the support of $x_\lambda$ is contained in $\cS_\lambda$ with corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
-        Moreover, there is an element $x_\lambda\in\cA(b,c)$ whose support is precisely the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cS_\lambda$.
+        Moreover, there is an element pointed at $\lambda$ whose support is precisely the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cS_\lambda$.
     \end{enumerate}

### 2022-04-25 dominance_regions.tex
Edits

@@
   Given a Laurent polynomial in $\ZZ[x_0^{\pm1},x_1^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
-  Given a $\bfg$-vector $\lambda$, in the next result we identify a region $\cS_\lambda$ whose lattice points are the maximum possible support of a pointed basis element $x_\lambda$. 
+  Given a $\bfg$-vector $\lambda$, in the next result we identify a polygon $\cS_\lambda$ whose lattice points are the maximum possible support of a pointed basis element $x_\lambda$. 
   \begin{theorem}

### 2022-05-01 dominance_regions.tex
Minor intro edits

@@
   \end{equation}
-  with $c_{0,0}=1$.
+  with $\rho_{0,0}=1$.
   Being \emph{pointed} means an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
@@
   Important examples of pointed elements are the \emph{cluster monomials} of $\cA(b,c)$, i.e.
-the elements that can be written in the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $a_k,a_{k+1}$ non-negative integers.
+the elements that can be written in the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $\alpha_k,\alpha_{k+1}$ non-negative integers.
   Indeed, by \cite[Lemma 3.4.12]{qin} cluster monomials are part of any pointed basis in any cluster algebra.
@@
     \label{th:dominance inequalities}
-    The dominance region $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the polygon consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
+    The dominance region $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the polygon consisting of those $\mu=(\mu_0,\mu_1)\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
     {
@@
 
-  A number of bases for rank two cluster algebras with various defining properties have been constructed.
-  A natural starting basis is the so-called \emph{greedy basis} in which all $c_{\alpha_0,\alpha_1}$ are non-negative and these coefficients are chosen to be minimal.
-  It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
-  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications with the subalgebras of $\ZZ[x_0^{\pm1},x_1^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
-  However, these bases depend on $k$ and the triangular basis is defined by a triangular transition with the stipulation that the basis does not depend on the choice of starting cluster.
-  It would be useful to explicitly (or combinatorially) compute the transitions between these bases.
-  However, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.
-
   Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
@@
   \end{remark}
+
+  A number of bases for rank two cluster algebras with various defining properties have been constructed.
+  A natural starting basis is the so-called \emph{greedy basis} in which all $\rho_{\alpha_0,\alpha_1}$ are non-negative and these coefficients are chosen to be minimal.
+  It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
+  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications of $\cA(b,c)$ with the subalgebras of $\ZZ[x_0^{\pm1},x_1^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
+  However, these bases depend on $k$ and the triangular basis is defined by a triangular transition with the stipulation that the basis does not depend on the choice of starting cluster.
+  It would be useful to explicitly (or combinatorially) compute the transitions between these and other known bases.
+  However, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.
 

### 2022-05-02 dominance_regions.tex
Intro edit

@@
   The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications of $\cA(b,c)$ with the subalgebras of $\ZZ[x_0^{\pm1},x_1^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
-  However, these bases depend on $k$ and the triangular basis is defined by a triangular transition with the stipulation that the basis does not depend on the choice of starting cluster.
-  It would be useful to explicitly (or combinatorially) compute the transitions between these and other known bases.
-  However, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.
+  However, these bases are not mutation invariant.
+  The \emph{triangular basis} is defined by a triangular transition from the standard monomial basis.
+  The \emph{generic basis} is defined from the categorification of $\cA(b,c)$ using generic representations of an associated quiver.
+  It would be useful to explicitly (or combinatorially) compute the transitions between these known bases.
+  Interestingly, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.
 

### 2022-05-02 dominance_regions.tex
Some edits in sections 2, 3, and 4

@@
 
-  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_0=0$, $u_1=1$, $u_{i+1}=ru_i-u_{i-1}$, which can be computed explicitly as
+  The standard Chebyshev polynomials (normalized, of the second kind) are defined by the recursion $u_0=0$, $u_1=1$, $u_{i+1}=ru_i-u_{i-1}$, which can be computed explicitly as
   \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
@@
     We have
-    \[\lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+}=\frac{bc+\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+}=\frac{bc-\sqrt{bc(bc-4)}}{2b};\]
-    \[\lim_{i\to-\infty} \frac{u_{i-1}^-}{u_i^+}=\frac{bc+\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to-\infty} \frac{u_i^-}{u_{i-1}^+}=\frac{bc-\sqrt{bc(bc-4)}}{2b}.\]
+    \[\lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+}=\frac{bc+\sqrt{bc(bc-4)}}{2b}=\lim_{i\to-\infty} \frac{u_{i-1}^-}{u_i^+};\]
+    \[\lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+}=\frac{bc-\sqrt{bc(bc-4)}}{2b}=\lim_{i\to-\infty} \frac{u_i^-}{u_{i-1}^+}.\]
     Moreover, each of these sequences is monotonic.
@@
 
-    For the final claim, observe that $\frac{u_{i+1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i-1}^\varepsilon}<$ and $\frac{u_{i-1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i+1}^\varepsilon}$ are both equivalent to $u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon<u_i^{-\varepsilon}u_i^\varepsilon$.
+    For the final claim, observe that $\frac{u_{i+1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i-1}^\varepsilon}$ and $\frac{u_{i-1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i+1}^\varepsilon}$ are both equivalent to $u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon<u_i^{-\varepsilon}u_i^\varepsilon$.
     This is immediate from the following induction:
@@
   \end{equation}
-  \begin{equation}
-    \label{eq:backward two step mutation}
-    \phi_{-2}(\lambda)
-    =
-    \begin{cases}
-      \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
-      (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
-      (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
-      (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
-    \end{cases}
-  \end{equation}
+  %\begin{equation}
+  %  \label{eq:backward two step mutation}
+  %  \phi_{-2}(\lambda)
+  %  =
+  %  \begin{cases}
+  %    \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
+  %    (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
+  %    (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
+  %    (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
+  %  \end{cases}
+  %\end{equation}
 
@@
     Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$.
-    In this case the intersection
+    In this case, the intersection
     \[\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)\]
     is precisely $\{\lambda\}$. 
-    Indeed, when $k$ is odd the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
+    Indeed, for $k$ odd, the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
     In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
-    On the contrary, when $k$ is odd the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ (resp.
-$\phi_{k-1}\lambda$) in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$ (resp.
-$\phi_{k-1}\lambda$).
-    In particular, $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ (resp.
-$\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$) is a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\lambda$.
-    The result follows.
+    On the contrary, for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$.
+    In particular, the intersection of $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ with the cone containing $\lambda$ is a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\lambda$.
+    The result follows for $k$ odd, the case of even $k$ is similar.
   \end{proof}

### 2022-05-07 dominance_regions.tex
Minor intro edits
Fixed proof of Lemma 2.3

@@
     }
+    %\begin{align}
+    %  0 & \leq \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) && \leq \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
+    %  \\
+    %  \min\left(-c\lambda_0,0\right) & \leq \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) && \leq 0
+    %  \\
+    %  0 & \leq -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) && \leq \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
+    %  \\
+    %  \min\left(b \lambda_1,0\right) & \leq (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) && \leq 0
+    %\end{align}
+
   \end{theorem}
@@
           \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $0 < -c\lambda_0-(bc-1)\lambda_1$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $(0,0)$.
+Here the point $(0,0)$ and its adjacent open segments are excluded from $\cS_\lambda$.
         \end{enumerate}
@@
     For any $i\ne1$, we have
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
     It follows that
-    \[\lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    \[\lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{\sqrt{c}}{2\sqrt{b}}\cdot\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
     which is equivalent to the desired expression.
     Similarly, for $i\ne0$ we have
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
+    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
     so that
-    \[\lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    \[\lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{2\sqrt{c}}{\sqrt{b}}\cdot\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
     which is again equivalent to the desired expression.

### 2022-05-08 dominance_regions.tex
Some cleanup in section 4

@@
   \begin{lemma}
+    \label{le:limits}
     We have
@@
   \begin{equation}
+    \label{eq:forward mutation 1}
     \phi_1(\lambda)
-    =
+    :=
     \begin{cases} 
@@
     \phi_{-1}(\lambda)
-    =
+    :=
     \begin{cases} 
@@
 
+  \begin{theorem}
+    \cite{qin}
+    \sayDR{Quote Fan's result here.}
+  \end{theorem}
+
   We record here a few useful calculations relating to the tropical transformations $\phi_k$.
@@
   \end{equation}
-  %\begin{equation}
-  %  \label{eq:backward two step mutation}
-  %  \phi_{-2}(\lambda)
-  %  =
-  %  \begin{cases}
-  %    \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
-  %    (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
-  %    (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
-  %    (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
-  %  \end{cases}
-  %\end{equation}
 
@@
     In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
-    On the contrary, for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$.
+    Next, again for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$.
     In particular, the intersection of $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ with the cone containing $\lambda$ is a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\lambda$.
-    The result follows for $k$ odd, the case of even $k$ is similar.
+    Combining these observations proves the result for $k$ odd, the case of even $k$ is similar.
   \end{proof}
@@
   \begin{itemize}
-    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth inequalities become equations for lines which intersect at $\lambda$;
-    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second inequalities become equations for lines which intersect at $\lambda$;
-    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth inequalities become equations for lines which intersect at $\lambda$.
+    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth pairs of inequalities become equations for lines which intersect at $\lambda$;
+    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second pairs of inequalities become equations for lines which intersect at $\lambda$;
+    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth pairs of inequalities become equations for lines which intersect at $\lambda$.
   \end{itemize}
@@
     \label{le:dominance inequalities}
-    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is determined by the following inequalities:
+    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is determined by the following inequalities when $k>0$:
     \begin{align}
@@
     \end{align}
-    when $k>0$ and by the following inequalities:
+    and by the following inequalities when $k<0$:
     \begin{align*}
@@
       u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
-      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;
+      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
     \end{align*}
-    when $k<0$.
 
@@
     We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
+    First observe that $\phi_2^{-1}=\phi_{-2}$ is given as follows:
+    \begin{equation}
+      \label{eq:backward two step mutation}
+      \phi_{-2}(\lambda)
+      =
+      \begin{cases}
+        \big(-\lambda_0-b\lambda_1, c\lambda_0+(bc-1)\lambda_1\big) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1\le 0$;}\\
+        (-\lambda_0-b\lambda_1, -\lambda_1) & \text{if $\lambda_1\le 0$ and $\lambda_0+b\lambda_1>0$;}\\
+        (-\lambda_0, c\lambda_0-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0\le 0$;}\\
+        (-\lambda_0,-\lambda_1) & \text{if $\lambda_1>0$ and $\lambda_0>0$.}
+      \end{cases}
+    \end{equation}
 
@@
     Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
-    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
+    Both of the boundary rays corresponding to the inequalities (a) and (d) lie entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
@@
 
-  To begin, observe that the boundary lines for \eqref{ineq:2} and \eqref{ineq:3} (and hence \eqref{ieq1} and \eqref{ieq2} below) intersect where $\mu_0=0$ and the boundary lines for \eqref{ineq:3} and \eqref{ineq:4} (and hence \eqref{ieq2} and \eqref{ieq3} below) intersect where $\mu_1=0$.
+  To begin, observe that the boundary lines for \eqref{ineq:2} and \eqref{ineq:3} (and hence \eqref{ieq1} and \eqref{ieq2} below) intersect where $\mu_0=0$ and the boundary lines for \eqref{ineq:3} and \eqref{ineq:4} (and hence \eqref{ieq2} and \eqref{ieq3} with $k-1$) intersect where $\mu_1=0$.
   We then rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
@@
   for $k<0$.
-  Then using that $-u_k^\varepsilon<0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$ we divide by these to rewrite the inequalities again as
+  Then, using that $-u_k^\varepsilon<0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$, we divide by these to rewrite the inequalities again as
   \begin{align}
@@
   \end{align}
-  and
+  for $k>0$ and
   \begin{align}
@@
     \label{ieq5} b\lambda_1 &\le (\mu_0-\lambda_0)-\frac{u_{k+1}^+}{u_k^-}(\mu_1-\lambda_1);\\
-    \label{ieq6} c\lambda_0+b\frac{u_{k-1}^-}{u_k^+}\lambda_1 &\le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).
+    \label{ieq6} c\lambda_0+b\frac{u_{k-1}^-}{u_k^+}\lambda_1 &\le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);
   \end{align}
+  for $k<0$.
   We now study each sequence of inequalities in turn.
 
-  For $\mu_1-\lambda_1\ge 0$, the inequalities \eqref{ieq1} become more restrictive as $k$ gets larger since the sequence $\frac{-u_{k+1}^-}{u_k^+}$ of slopes is monotonically decreasing.
-  Thus in the limit as $k\to\infty$, we obtain the inequality 
+  For $\mu_1-\lambda_1\ge 0$, the inequalities \eqref{ieq1} become more restrictive as $k$ gets larger since the sequence $\frac{-u_{k+1}^-}{u_k^+}$ of negative slopes is monotonically increasing (c.f.
+Lemma~\ref{le:limits}).
+  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality 
   \[ 0 \le \frac{-bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
-  or equivalently
+  or, equivalently,
   \[ 0 \le -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \]
@@
 
-  Similarly, the inequalities \eqref{ieq2} become more restrictive for $\mu_0\le0$ and $\mu_1\ge0$ as $k$ gets larger since the sequence of slopes $\frac{u_{k-1}^-}{u_k^+}$ is monotonically increasing and the intersection with \eqref{ieq1} moves lower on the $\mu_1$-axis as $k$ increases.
-  Thus in the limit as $k\to\infty$, we obtain the inequality
+  Similarly, the inequalities \eqref{ieq2} become more restrictive for $\mu_0\le0$ and $\mu_1\ge0$ as $k$ gets larger since the sequence $\frac{u_{k-1}^-}{u_k^+}$ of positive slopes is monotonically increasing and the intersection with \eqref{ieq1} moves lower on the $\mu_1$-axis as $k$ increases.
+  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality
   \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
   determining a boundary of $\cP_\lambda$.
-  Observe further that $\mu_0-\lambda_0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
+  Observe further that the inequalities $\mu_0-\lambda_0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
   \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]
 
-  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence of slopes $\frac{-u_{k-1}^+}{u_k^-}$ is monotonically increasing and the intersection with \eqref{ieq2} moves to the right on the $\mu_0$-axis as $k$ increases.
-  Thus in the limit as $k\to\infty$, we obtain the inequality
+  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence $\frac{-u_k^-}{u_{k-1}^+}$ of negative slopes is monotonically increasing (c.f.
+Lemma~\ref{le:limits}) and the intersection with \eqref{ieq2} (for $k+1$) moves to the right on the $\mu_0$-axis as $k$ increases.
+  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality
   \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1 \]

### 2022-05-08 dominance_regions.tex
Section 6 cleanup

@@
   \begin{theorem}
+    \label{th:dominance}
     \cite{qin}
@@
   \[ \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) \leq -c\lambda_0 - \frac{b c + \sqrt{b c (b c-4)}}{2 } \lambda_1,\]
-  which together with the second to last inequality gives two boundaries for the dominance region $\cP_\lambda$.
+  which together with the second to last inequality already gives two of the boundaries for the dominance region $\cP_\lambda$.
   Note then that, under the assumption $\mu_0\leq\lambda_0$, the inequality 
@@
   \[ \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) \leq -b\lambda'_1-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda'_0,\]
-  which together with the last inequality gives two boundaries for the opposite dominance region $\cP'_\lambda$.
+  which together with the last inequality already gives two of the boundaries for the opposite dominance region $\cP'_\lambda$.
   Note then that, under the assumption $\mu_1\leq\lambda'_1$, the inequality
@@
 
+  To continue, we compare the support for an arbitrary basis element pointed at $\lambda\in\cI$ with the corresponding greedy basis elements with $\bfg$-vectors inside the dominance polygon $\cP_\lambda$.
+
   The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{LLZ,cgmmrsw}.
@@
   But $\cS_\lambda$ is min-convex and closed under downward scaling, i.e. for any $\mu\in\cS_\lambda$ we have $t\mu\in\cS_\lambda$ for $0\le t\le 1$.
-  It follows that $\overline{\cG}_\mu\subset\cS_\lambda$ for any $\mu\in\cP_\lambda$ and so the support of any basis element pointed at $\lambda$ is contained in $\cS_\lambda$.
+  It follows that $\overline{\cG}_\mu\subset\cS_\lambda$ for any $\mu\in\cP_\lambda$ and hence, following Theorem~\ref{th:dominance}, the support of any basis element pointed at $\lambda$ is contained in $\cS_\lambda$.
 

### 2022-05-08 dominance_regions.tex
More edits?
Citing Qin

@@
-\documentclass[a3paper]{amsart}
+\documentclass{amsart}
 \usepackage{amsmath}
@@
   Indeed, by \cite[Lemma 3.4.12]{qin} cluster monomials are part of any pointed basis in any cluster algebra.
-  We achieve the same conclusion in our setting by elementary calculations (c.f. Lemma~\ref{le:cluster monomials}).
+  We achieve the same conclusion in our setting by elementary calculations (cf. Lemma~\ref{le:cluster monomials}).
 
   Elements of any pointed basis are parametrized by their $\bfg$-vectors.
-  Qin introduced a partial order on $\bfg$-vectors called the \emph{dominance order} and showed that given two pointed bases $x=\{x_\lambda\}$, $y=\{y_\lambda\}$, $y_\mu$ can appear in the expansion of $x_\lambda$ in terms of $y$ only if $\lambda$ dominates $\mu$ (cf.
-\cite[Theorem 1.2.1]{qin}).
+  Qin introduced a partial order $\preceq$ on $\bfg$-vectors called the \emph{dominance order} and showed the following result characterizing pointed bases which motivates this paper.
+
+  \begin{theorem}
+    \label{th:dominance}
+    \cite[Theorem 1.2.1]{qin}
+    Let $x=\{x_\lambda\}$ and $y=\{y_\lambda\}$ be pointed bases of $\cA(b,c)$.
+    Then for each $\lambda\in\ZZ^2$, there exist scalars $a_{\lambda,\mu}\in\ZZ$ for $\mu\prec\lambda$ such that
+    \[y_\lambda=x_\lambda+\sum_{\mu\prec\lambda} a_{\lambda,\mu} x_\mu.\]
+  \end{theorem}
 
@@
 Section~\ref{sec:maximum support} proves Theorem~\ref{th:maximum support}.
-The paper ends with Section~\ref{sec:affine} interpreting the dominance polygon in terms of generalized minors in the cases where $bc=4$.
+The paper ends with Section~\ref{sec:affine} interpreting the dominance polygon in terms of generalized minors in the cases where $b=c=2$.
 
@@
   \end{definition}
-
-  \begin{theorem}
-    \label{th:dominance}
-    \cite{qin}
-    \sayDR{Quote Fan's result here.}
-  \end{theorem}
 
@@
 
-  For $\mu_1-\lambda_1\ge 0$, the inequalities \eqref{ieq1} become more restrictive as $k$ gets larger since the sequence $\frac{-u_{k+1}^-}{u_k^+}$ of negative slopes is monotonically increasing (c.f.
+  For $\mu_1-\lambda_1\ge 0$, the inequalities \eqref{ieq1} become more restrictive as $k$ gets larger since the sequence $\frac{-u_{k+1}^-}{u_k^+}$ of negative slopes is monotonically increasing (cf.
 Lemma~\ref{le:limits}).
@@
 
-  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence $\frac{-u_k^-}{u_{k-1}^+}$ of negative slopes is monotonically increasing (c.f.
+  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence $\frac{-u_k^-}{u_{k-1}^+}$ of negative slopes is monotonically increasing (cf.
 Lemma~\ref{le:limits}) and the intersection with \eqref{ieq2} (for $k+1$) moves to the right on the $\mu_0$-axis as $k$ increases.
@@
 
-  The following result is proven in \cite[Lemma 2.4]{rupel} with appropriate notation changes, c.f. Theorem~\ref{th:dominant Dyck path recursion} for a slight modification and explicit proof.
+  The following result is proven in \cite[Lemma 2.4]{rupel} with appropriate notation changes, cf. Theorem~\ref{th:dominant Dyck path recursion} for a slight modification and explicit proof.
   \begin{lemma}\mbox{}

### 2022-05-08 dominance_regions.tex
Intro edits

@@
   Being pointed turned out to be a desirable feature for a basis to have and a natural question is to find all bases enjoying this property.
-  Recently Qin introduced the notion of \emph{dominance} and showed that it completely encapsulates the deformability of pointed bases whenever the cluster algebra has full rank \cite{Qin}. 
+  Recently Qin studied the deformability of pointed bases whenever the cluster algebra has full rank \cite{qin}. 
   As no explicit calculation is carried out in his work, we aim here at describing explicitly the space of deformability for pointed bases in rank two, i.e.
@@
 
-  Elements of any pointed basis are parametrized by their $\bfg$-vectors.
-  Qin introduced a partial order $\preceq$ on $\bfg$-vectors called the \emph{dominance order} and showed the following result characterizing pointed bases which motivates this paper.
+  Elements of any pointed basis are parametrized by $\ZZ^2$ thought of as the collection of possible $\bfg$-vectors.
+  Qin introduced a partial order $\preceq$ on $\bfg$-vectors called the \emph{dominance order} and showed that it provides a characterization of pointed bases.
+  We restate his results in the generality needed for this paper and using our notation.
 
@@
     Let $x=\{x_\lambda\}$ and $y=\{y_\lambda\}$ be pointed bases of $\cA(b,c)$.
-    Then for each $\lambda\in\ZZ^2$, there exist scalars $a_{\lambda,\mu}\in\ZZ$ for $\mu\prec\lambda$ such that
+    Then for each $\lambda\in\ZZ^2$, there exist scalars $a_{\lambda,\mu}$ for $\mu\prec\lambda$ such that
     \[y_\lambda=x_\lambda+\sum_{\mu\prec\lambda} a_{\lambda,\mu} x_\mu.\]

### 2022-05-09 dominance_regions.tex
Theorem 1.1 edit
Halfway through section 7

@@
   We restate his results in the generality needed for this paper and using our notation.
-
   \begin{theorem}
@@
     Let $x=\{x_\lambda\}$ and $y=\{y_\lambda\}$ be pointed bases of $\cA(b,c)$.
-    Then for each $\lambda\in\ZZ^2$, there exist scalars $a_{\lambda,\mu}$ for $\mu\prec\lambda$ such that
-    \[y_\lambda=x_\lambda+\sum_{\mu\prec\lambda} a_{\lambda,\mu} x_\mu.\]
+    Then for each $\lambda\in\ZZ^2$, there exist scalars $q_{\lambda,\mu}$ for $\mu\prec\lambda$ such that
+    \[y_\lambda=x_\lambda+\sum_{\mu\prec\lambda} q_{\lambda,\mu} x_\mu.\]
+    Moreover, any choice of scalars $q_{\lambda,\mu}$, for $\mu\prec\lambda$, $\lambda\in\ZZ^2$, as above provides a basis of $\cA(b,c)$.
   \end{theorem}
@@
   In this section we compare our main result with the construction of \cite{RSW19} in the case $b=c=2$.
+  To match conventions, in this section, we work over an algebraically closed field $\kk$ of characteristic 0.
+  Because the exchange matrix is full rank there is no loss of generality in continuing to work in the coefficient-free case.
+  We will identify the family of bases from Theorem \ref{th:dominance} with the continuous family of bases of $\cA(2,2)$ constructed in \cite{RSW19} from generalized minors which we recast here with the current notation.
+
+  \begin{theorem}[{\cite[Theorem 4.6]{RSW19}}]
+    Choose a point $\bfa\in(\kk^\times)^n$ for each $n\geq1$.
+    Then the elements 
+    \[
+      x_{(n,-n)}^{\bfa}:= x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+    \]
+    with
+    \[
+      S_{\bfa,r}=\sum\limits_{\substack{I,J\subseteq[1,n]\\|I|=r=|J|\\ I\cap J=\varnothing}}\frac{\prod_{i\in I} a_i}{\prod_{j\in J} a_j}
+    \]
+    together with all cluster monomials form a linear basis of $\cA(2,2)$.
+  \end{theorem}
+
+  We begin by noting that when $b=c=2$ the imaginary cone $\cI$ degenerates to the ray spanned by $(1,-1)$.
+  For any $\lambda\in\cI$, the dominance region $\cP_\lambda$ is the segment connecting $\lambda$ to the origin.
+  It follows that $\bfg$-vectors dominated by $\lambda=(n,-n)$ are of the form $(n-2r,-n+2r)$ for $0\leq r \leq n/2$.
+
+  In order to use Theorem \ref{th:dominance} we need to fix a reference pointed basis of $\cA(2,2)$; to simplify our computations, we choose to work with the \emph{generic basis}.
+  This basis consists of the cluster monomials of $\cA(2,2)$ together with the elements
+  \[
+    x_{(n,-n)}^{ge}
+    :=
+		\Big(x_0 x_1^{-1} + x_0^{-1}x_1^{-1} + x_0^{-1}x_1\Big)^n
+		=
+    x_0^{-n} x_1^{-n}
+    \sum_{0 \leq k \leq \ell \leq n}
+    {\ell\choose k} {n\choose \ell}
+    \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+  \]
+
+	\begin{theorem}
+    \[
+      x_{(n,-n)}^{\bfa}
+      =
+      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
+      S_{\bfa,r}
+      x_{(n-2r,-n+2r)}^{ge}
+    \]
+  \end{theorem}
+  \begin{proof}
+    \begin{align*}
+      x_{(n,-n)}^{\bfa}
+      & =
+      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+    \end{align*}
+    From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor \frac{n}{2} \rfloor$.
+    \begin{align*}
+      x_{(n,-n)}^{\bfa}
+      & =
+      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+      \\
+      & =
+      \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} S_{\bfa,r}\, x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+      \\
+      & =
+      \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} S_{\bfa,r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k-r)} x_1^{2(n-\ell-r)}
+  \end{align*}
+  \end{proof}
+
+	For a chosen point $\bfa\in(\kk^\times)^n$, let $m_{1^{(n)}}$ denote the monomial symmetric function $\prod_{i\in[1,n]} a_i$.
+
   We show that the continuous family of bases constructed there is precisely the deformation family constructed by \cite{Qin}.

### 2022-05-11 dominance_regions.tex
Minor section 7 edits

@@
   Because the exchange matrix is full rank there is no loss of generality in continuing to work in the coefficient-free case.
-  We will identify the family of bases from Theorem \ref{th:dominance} with the continuous family of bases of $\cA(2,2)$ constructed in \cite{RSW19} from generalized minors which we recast here with the current notation.
+  We will identify the family of bases in Theorem \ref{th:dominance} with the continuous family of bases of $\cA(2,2)$ constructed in \cite{RSW19} from generalized minors, which we recast here with the current notation.
 
@@
     Choose a point $\bfa\in(\kk^\times)^n$ for each $n\geq1$.
-    Then the elements 
+    Then, together with all cluster monomials, the elements 
     \[
@@
     \]
-    together with all cluster monomials form a linear basis of $\cA(2,2)$.
+    form a linear basis of $\cA(2,2)$.
   \end{theorem}
@@
       =
-      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
+      \sum_{r=0}^{\lfloor n/2 \rfloor}
       S_{\bfa,r}
@@
     \end{align*}
-    From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor \frac{n}{2} \rfloor$.
+    From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor n/2 \rfloor$.
     \begin{align*}
@@
       & =
-      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^{\lfloor n/2 \rfloor} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
       \\
       & =
-      \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} S_{\bfa,r}\, x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+      \sum\limits_{r=0}^{\lfloor n/2 \rfloor} S_{\bfa,r}\, x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k)} x_1^{2(n-\ell)}
       \\
       & =
-      \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} S_{\bfa,r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k-r)} x_1^{2(n-\ell-r)}
+      \sum\limits_{r=0}^{\lfloor n/2 \rfloor} S_{\bfa,r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k-r)} x_1^{2(n-\ell-r)}
   \end{align*}

### 2022-05-16 dominance_regions.tex
Proof of Theorem 7.2

@@
     Then, together with all cluster monomials, the elements 
-    \[
+    \begin{equation}
+      \label{eq:generalized minor}
       x_{(n,-n)}^{\bfa}:= x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
-    \]
+    \end{equation}
     with
@@
   \begin{theorem}
+    For $n\ge0$, we have
     \[
@@
       S_{\bfa,r}
-      x_{(n-2r,-n+2r)}^{ge}
+      x_{(n-2r,-n+2r)}^{ge}.
     \]
@@
   \begin{proof}
+    To begin, we observe that \eqref{eq:generalized minor} may be rewritten as
+    \[
+      x_{(n,-n)}^{\bfa} = x_0^{-n} x_1^{-n} \sum_{k=0}^n \sum_{\ell=k}^n \sum_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}.
+    \]
+    The first binomial coefficient above is zero if $0 \le \ell-r < k$ while the second is zero for $\ell < r \le \lfloor n/2\rfloor$ or if $n-r < \ell$, therefore $x_{(n,-n)}^{\bfa}$ can be expressed as
     \begin{align*}
       x_{(n,-n)}^{\bfa}
-      & =
-      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+      &=
+      x_0^{-n} x_1^{-n} \sum_{k=0}^n \sum_{r=0}^{\lfloor n/2\rfloor} \sum_{\ell=k+r}^{n-r} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}.
     \end{align*}
-    From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor n/2 \rfloor$.
+    But then rearranging terms and replacing $\ell$ by $\ell+r$, this becomes
     \begin{align*}
       x_{(n,-n)}^{\bfa}
-      & =
-      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^{\lfloor n/2 \rfloor} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
-      \\
-      & =
-      \sum\limits_{r=0}^{\lfloor n/2 \rfloor} S_{\bfa,r}\, x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k)} x_1^{2(n-\ell)}
-      \\
-      & =
-      \sum\limits_{r=0}^{\lfloor n/2 \rfloor} S_{\bfa,r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k-r)} x_1^{2(n-\ell-r)}
+      &=
+      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa,r} x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}\\
+      &=
+      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa,r} x_{n-2r,-n+2r}^{ge}
     \end{align*}
-  \end{proof}
-
-	For a chosen point $\bfa\in(\kk^\times)^n$, let $m_{1^{(n)}}$ denote the monomial symmetric function $\prod_{i\in[1,n]} a_i$.
+    as desired.
+  \end{proof}
 

### 2022-05-16 dominance_regions.tex
Some section 7 cleanup

@@
 
-  We show that the continuous family of bases constructed there is precisely the deformation family constructed by \cite{Qin}.
-
   We want to show that our continuous family of generalized minors from \cite[Theorem 4.6]{RSW19} coincide with the family of bases constructed in \cite[Theorem 1.2.1]{Qin19}.
-
-  This boils down to show, for any $n>1$, that
-  \begin{enumerate}
-    \item 
-      the set of $\bfg$-vectors that are dominated by $n\omega^\circ$ with respect to any seed is 
-      \[
-        \left\{(n-2r)\omega^\circ \right\}_{r\in\left[1,\left\lfloor\frac{1}{2}\right\rfloor\right]}
-      \]
-
-    \item
-      we can choose a specific basis and rewrite the last formula in \cite[Proposition 4.4]{RSW19} as in \cite[Theorem 1.2.1]{Qin19} with coefficients being functions of the point $\bfa\in(\kk^\times)^n$.
-  \end{enumerate}
-
-  For a partition $\lambda \vdash n$ let $e_\lambda$, $s_\lambda$, and $m_\lambda$ denote the elementary, Schur, and monomial symmetric functions associated to the partition $\lambda$ evaluated at $\bfa$.
-  Recall that $m_{1^{(n)}} = s_{1^{(n)}} = e_n$.
-
-  \begin{lemma}
-    For every $r\in\left[1,\left\lfloor\frac{1}{2}\right\rfloor\right]$ we have $m_{1^{(n)}} S_{\bfa,r} = m_{2^{(r)},1^{(n-2r)}}$.
-  \end{lemma}
-  \begin{proof}
-    This is immediate from the definition.
-  \end{proof}
 
@@
   We think of $F$-polynomials as polynomials in the variables $u_1$ and $u_2$.
-
-  I did not try yet to prove (1) but it should be straightforward.
-  It suffices to establish (2) for the $F$-polynomials.
-
-  \begin{proposition}
-    \[
-      m_{1^{(n)}} F_{n\omega^\circ}^\Delta
-      =
-      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
-      m_{2^{(k)},1^{(n-2r)}}
-      u_1^r u_2^r
-      F_{(n-2r)\omega^\circ}^{ge}
-    \]
-  \end{proposition}
-  \begin{proof}
-    From \cite[Proposition 4.4]{RSW19} we get the following expression for $F_{n\omega^\circ}^\Delta$:
-    \[
-       F_{n\omega^\circ}^\Delta 
-       =
-       \sum_{0 \le k \le \ell \le n}
-       \sum_{r=0}^\ell
-       {\ell -r \choose k}
-       {n-2r \choose \ell-r}
-       S_{\bfa,r}
-       u_1^\ell u_2^{\ell-k}.
-    \]
-    From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor \frac{n}{2} \rfloor$.
-    We compute
-    \begin{align*}
-      m_{1^{(n)}}  F_{n\omega^\circ}^\Delta 
-      &
-      =
-      \sum_{0 \le k \le \ell \le n}
-      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
-      {\ell -r \choose k}
-      {n-2r \choose \ell-r}
-      m_{2^{(r)},1^{(n-2r)}}
-      u_1^\ell u_2^{\ell-k}
-      \\
-      &=
-      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
-      m_{2^{(r)},1^{(n-2r)}}
-      u_1^r u_2^r
-      \sum_{0 \le k \le \ell \le n}
-      {\ell -r \choose k}
-      {n-2r \choose \ell-r}
-      u_1^{\ell-r} u_2^{\ell-r-k}
-      \\
-      &=
-      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
-      m_{2^{(r)},1^{(n-2r)}}
-      u_1^r u_2^r
-      F_{(n-2r)\omega^\circ}^{ge}.
-    \end{align*}
-    The last identity follows immediately by comparing with the formula for generic basis elements in \cite{RSW19}.
-    \saySS{Thank you Dylan for fixing my stupidity.}
-  \end{proof}
 

### 2022-05-16 dominance_regions.tex
Stashing
Remark in section 7

@@
 
-  We want to show that our continuous family of generalized minors from \cite[Theorem 4.6]{RSW19} coincide with the family of bases constructed in \cite[Theorem 1.2.1]{Qin19}.
-
-  Let $F_{n\omega^\circ}^\Delta$, $F_{n\omega^\circ}^{gr}$, $F_{n\omega^\circ}^{tr}$, and $F_{n\omega^\circ}^{ge}$ be the $F$-polynomials of the generalized minor, greedy basis element, triangular basis element, and generic basis element with $\bfg$-vector $n\omega^\circ$.
-  We think of $F$-polynomials as polynomials in the variables $u_1$ and $u_2$.
-
-  We do not need the following two formulas but I think they are still neat.
-  \begin{conjecture}
-    \begin{align*} 
-      m_{1^{(n)}} F_{n\omega^\circ}^\Delta
-      &=
-      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
-      s_{2^{(k)},1^{(n-2r)}}
-      u_1^r u_2^r
-      F_{(n-2r)\omega^\circ}^{tr}
-      \\&=
-      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
-      e_{r,n-r}
-      u_1^r u_2^r
-      F_{(n-2r)\omega^\circ}^{gr}
-    \end{align*}
-  \end{conjecture}
+  \begin{remark}
+    Observe that $S_{\bfa,r}$ can be expressed in terms of monomial symmetric functions evaluated at $\bfa$ as $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$.
+    Analogous expansions of $x_{(n,-n)}^{\bfa}$ in terms of triangular or greedy basis elements lead to Schur functions or elementary symmetric functions evaluated at $\bfa$ as $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ and $\frac{e_{r,n-r}}{e_n}$, respectively.
+    We leave the details to the interested reader.
+  \end{remark}
 

### 2022-05-16 dominance_regions.tex
edit in section 7

@@
   \begin{remark}
-    Observe that $S_{\bfa,r}$ can be expressed in terms of monomial symmetric functions evaluated at $\bfa$ as $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$.
+    Observe that the expansion coefficients $S_{\bfa,r}$ can be expressed in terms of monomial symmetric functions evaluated at $\bfa$ as $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$.
     Analogous expansions of $x_{(n,-n)}^{\bfa}$ in terms of triangular or greedy basis elements lead to Schur functions or elementary symmetric functions evaluated at $\bfa$ as $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ and $\frac{e_{r,n-r}}{e_n}$, respectively.

### 2022-05-16 dominance_regions.tex
edit in section 7

@@
     Observe that the expansion coefficients $S_{\bfa,r}$ can be expressed in terms of monomial symmetric functions evaluated at $\bfa$ as $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$.
-    Analogous expansions of $x_{(n,-n)}^{\bfa}$ in terms of triangular or greedy basis elements lead to Schur functions or elementary symmetric functions evaluated at $\bfa$ as $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ and $\frac{e_{r,n-r}}{e_n}$, respectively.
+    The analogous expansion coefficients when $x_{(n,-n)}^{\bfa}$ is expressed in terms of triangular or greedy basis elements lead to Schur functions or elementary symmetric functions evaluated at $\bfa$ as $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ and $\frac{e_{r,n-r}}{e_n}$, respectively.
     We leave the details to the interested reader.

### 2022-05-16 dominance_regions.tex
edit in section 7

--- 2022-05-16 dominance_regions.tex
@@
   \begin{remark}
-    Observe that $S_{\bfa,r}$ can be expressed in terms of monomial symmetric functions evaluated at $\bfa$ as $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$.
-    Analogous expansions of $x_{(n,-n)}^{\bfa}$ in terms of triangular or greedy basis elements lead to Schur functions or elementary symmetric functions evaluated at $\bfa$ as $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ and $\frac{e_{r,n-r}}{e_n}$, respectively.
+    Observe that the expansion coefficients $S_{\bfa,r}$ can be expressed as the ratio of monomial symmetric functions $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$ evaluated at $\bfa$.
+    The analogous expansion coefficients when $x_{(n,-n)}^{\bfa}$ is expressed in terms of the triangular basis (resp.
+greedy basis) lead to the ratios of Schur functions $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ (resp.
+ratios of elementary symmetric functions $\frac{e_{r,n-r}}{e_n}$) evaluated at $\bfa$.
     We leave the details to the interested reader.

### 2022-05-17 dominance_regions.tex
Edits from our session
wrong k
Done with proofs

--- 2022-05-16 dominance_regions.tex
@@
     given as in the figure below:
-    \[
-      \begin{tikzpicture}
-        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
-        \draw[-] (-8,0) -- (5,0);
-        \draw[-] (0,-5) -- (0,5);
-        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
-        \draw[dashed] (0,0) -- (5,-2.113);
-        \draw[dashed] (0,0) -- (3.17,-5);
-        \node at (1,-0.9) {$\cI$};
-        \draw[fill=black] (3.5,-3) circle (2pt);
-        \node[right] at (3.5,-3) {$\lambda$};
-        \draw[->,thick] (3.5,-3) -- (47/10,-5);
-        \draw[-,thick] (3.5,-3) -- (0,26/10);
-        \draw[-,thick] (0,26/10) -- (-26/4,0);
-        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
-        \node at (4.5,-4) {\eqref{ineq:1}};
-        \node at (2.34,-0.5) {\eqref{ineq:2}};
-        \node at (-3,1.75) {\eqref{ineq:3}};
-        \node at (-5.36,-3) {\eqref{ineq:4}};
+\begin{figure}[h!]
+  \centering
+    \newcommand{\setconstants}{
+      \tikzmath{\b = 3.5; \c = 4.4 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
+      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
+      \clip (\xmin,\ymin) rectangle (\xmax,\ymax);
+    }
+    \newcommand{\boundingrays}{
+      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
+      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
+      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
+      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
+      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
+      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
+    }
+  \begin{tikzpicture}[scale=.3]
+    \begin{scope}[shift={(0,0)}]
+      \setconstants;
+      %\draw[draw=none, fill=gray!20] (0,0) -- (2*\xmax,0) -- (2*\xmax,2*\ymax) --  (0,2*\ymax) -- cycle; 
+      \boundingrays;
+      \tikzmath{ \t=5; \r=1; \s=2; \xx={2*(\r+\s)*\b }; \yy = {-\r*\bcps -\s*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \fill (\x , \y)  circle (5pt);
+      \fill[fill=gray!20] (\xmax, {min(\ymin,-\c*(\xmax-\x)+\y)}) -- (\xmax, {-\c*(\xmax-\x)+\y}) -- (\x,\y) -- (0, {(\b*\c-1)/\b*\x+\y}) -- ({-(\b*\c-1)*\x-\b*\y},0);
+      \draw [variable=\m, domain=\x:\xmax,thick] plot({\m}, {-\c*(\m-\x)+\y});
+      \draw [variable=\m, domain=0:\x,thick] plot({\m}, {-(\b*\c-1)/\b*(\m-\x)+\y});
+    \end{scope}
   \end{tikzpicture}
-    \]
+\end{figure}
+
+%    \[
+%      \begin{tikzpicture}
+%        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
+%        \draw[-] (-8,0) -- (5,0);
+%        \draw[-] (0,-5) -- (0,5);
+%        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
+%        \draw[dashed] (0,0) -- (5,-2.113);
+%        \draw[dashed] (0,0) -- (3.17,-5);
+%        \node at (1,-0.9) {$\cI$};
+%        \draw[fill=black] (3.5,-3) circle (2pt);
+%        \node[right] at (3.5,-3) {$\lambda$};
+%        \draw[->,thick] (3.5,-3) -- (47/10,-5);
+%        \draw[-,thick] (3.5,-3) -- (0,26/10);
+%        \draw[-,thick] (0,26/10) -- (-26/4,0);
+%        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
+%        \node at (4.5,-4) {\eqref{ineq:1}};
+%        \node at (2.34,-0.5) {\eqref{ineq:2}};
+%        \node at (-3,1.75) {\eqref{ineq:3}};
+%        \node at (-5.36,-3) {\eqref{ineq:4}};
+%      \end{tikzpicture}
+%    \]
   \end{lemma}
@@
   \begin{theorem}[{\cite[Theorem 4.6]{RSW19}}]
-    Choose a point $\bfa\in(\kk^\times)^n$ for each $n\geq1$.
+    \label{thm:rsw}
+    Choose a point $\bfa^{(n)}=(a_1,\dots,a_n)\in(\kk^\times)^n$ for each $n\geq1$.
     Then, together with all cluster monomials, the elements 
@@
       \label{eq:generalized minor}
-      x_{(n,-n)}^{\bfa}:= x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+      x_{(n,-n)}^{\bfa^{(n)}}:= x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa^{(n)},r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
     \end{equation}
@@
     \[
-      S_{\bfa,r}=\sum\limits_{\substack{I,J\subseteq[1,n]\\|I|=r=|J|\\ I\cap J=\varnothing}}\frac{\prod_{i\in I} a_i}{\prod_{j\in J} a_j}
+      S_{\bfa^{(n)},r}=\sum\limits_{\substack{I,J\subseteq[1,n]\\|I|=r=|J|\\ I\cap J=\varnothing}}\frac{\prod_{i\in I} a_i}{\prod_{j\in J} a_j}
     \]
@@
 
-  \begin{theorem}
+  \begin{proposition}
+    \label{prop:rewrite}
     For $n\ge0$, we have
     \[
-      x_{(n,-n)}^{\bfa}
+      x_{(n,-n)}^{\bfa^{(n)}}
       =
       \sum_{r=0}^{\lfloor n/2 \rfloor}
-      S_{\bfa,r}
+      S_{\bfa^{(n)},r}
       x_{(n-2r,-n+2r)}^{ge}.
     \]
-  \end{theorem}
+  \end{proposition}
   \begin{proof}
@@
     \[
-      x_{(n,-n)}^{\bfa} = x_0^{-n} x_1^{-n} \sum_{k=0}^n \sum_{\ell=k}^n \sum_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}.
+      x_{(n,-n)}^{\bfa^{(n)}} = x_0^{-n} x_1^{-n} \sum_{k=0}^n \sum_{\ell=k}^n \sum_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa^{(n)},r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}.
     \]
-    The first binomial coefficient above is zero if $0 \le \ell-r < k$ while the second is zero for $\ell < r \le \lfloor n/2\rfloor$ or if $n-r < \ell$, therefore $x_{(n,-n)}^{\bfa}$ can be expressed as
+    The first binomial coefficient above is zero if $0 \le \ell-r < k$ while the second is zero for $\ell < r \le \lfloor n/2\rfloor$ or if $n-r < \ell$, therefore $x_{(n,-n)}^{\bfa^{(n)}}$ can be expressed as
     \begin{align*}
-      x_{(n,-n)}^{\bfa}
+      x_{(n,-n)}^{\bfa^{(n)}}
       &=
-      x_0^{-n} x_1^{-n} \sum_{k=0}^n \sum_{r=0}^{\lfloor n/2\rfloor} \sum_{\ell=k+r}^{n-r} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}.
+      x_0^{-n} x_1^{-n} \sum_{k=0}^n \sum_{r=0}^{\lfloor n/2\rfloor} \sum_{\ell=k+r}^{n-r} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa^{(n)},r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}.
     \end{align*}
@@
     \begin{align*}
-      x_{(n,-n)}^{\bfa}
+      x_{(n,-n)}^{\bfa^{(n)}}
       &=
-      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa,r} x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}\\
+      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r} x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}\\
       &=
-      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa,r} x_{n-2r,-n+2r}^{ge}
+      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r} x_{n-2r,-n+2r}^{ge}
     \end{align*}
@@
   \begin{remark}
-    Observe that the expansion coefficients $S_{\bfa,r}$ can be expressed in terms of monomial symmetric functions evaluated at $\bfa$ as $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$.
-    Analogous expansions of $x_{(n,-n)}^{\bfa}$ in terms of triangular or greedy basis elements lead to Schur functions or elementary symmetric functions evaluated at $\bfa$ as $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ and $\frac{e_{r,n-r}}{e_n}$, respectively.
+    \label{rk:symmetric}
+    Observe that the expansion coefficients $S_{\bfa^{(n)},r}$ can be expressed as the ratio of monomial symmetric functions $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$ evaluated at $\bfa^{(n)}$.
+    The analogous expansion coefficients when $x_{(n,-n)}^{\bfa^{(n)}}$ is expressed in terms of the triangular basis (resp.
+greedy basis) are the ratios of Schur functions $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ (resp.
+ratios of elementary symmetric functions $\frac{e_{r,n-r}}{e_n}$) evaluated at $\bfa^{(n)}$.
     We leave the details to the interested reader.
   \end{remark}
+
+  \begin{theorem}
+    As the points $\bfa^{(n)}$ vary in $(\kk^\times)^n$, the bases in Theorem \ref{thm:rsw} recover precisely all the pointed bases of $\cA(2,2)$.
+  \end{theorem}
+  \begin{proof}
+    By Theorem \ref{th:dominance}, in view of Proposition \ref{prop:rewrite} and the discussion immediately before it, it suffices to show that as $\bfa^{(n)}$ vary in $(\kk^\times)^n$ the tuple of coefficients $\big(S_{\bfa^{(n)},r}\big)_{1\leq r \leq \lfloor n/2\rfloor}$ assume all the values in $\kk^{\lfloor n/2\rfloor}$.
+    (The fact that $S_{\bfa^{(n)},0}=1$ is immediate from the definition.)
+
+    By Remark \ref{rk:symmetric}, this is equivalent to the fact that the symmetric monomial functions in $n$ variables $m_{2^{(r)},1^{(n-2r)}}$ are algebraically independent.
+    But this follows immediately from the observation that 
+    \[ 
+      m_{2^{(r)},1^{(n-2r)}} = \sum_{i=0}^r c_i\, e_{n-i,i}
+    \]
+    for some coefficients $c_i$ with $c_r=1$, and the fundamental theorem of symmetric polynomials. 
+  \end{proof}
 

### 2022-05-17 dominance_regions.tex
Figure
Stashing
Main figure

@@
 \begin{document}
+
   \begin{abstract}
@@
 
+\begin{figure}[h!]
+  \centering
+    \newcommand{\setconstants}{
+      \tikzmath{\b = 3; \c = 6 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
+      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -4; \ymax = 8;}
+      \clip ({\xmin-0.2},{\ymin-0.2}) rectangle ({\xmax+0.2},{\ymax+0.2});
+    }
+    \newcommand{\boundingrays}{
+      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
+      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
+      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
+      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
+    }
+  \begin{tikzpicture}[scale=.5]
+      \setconstants;
+      \foreach \x in {\xmin,...,\xmax} {
+        \foreach \y in {\ymin,...,\ymax} {
+          \fill[color=gray] (\x,\y) circle (0.05);
+        }
+      };
+      \tikzmath{ \x=4; \y=-3;};
+      \boundingrays;
+      \fill [fill=gray!30, fill opacity=0.4] (\x,\y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- cycle;
+      \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcms/(2*\b)*\x+\y}) -- cycle;
+      \fill [fill=green!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
+      \draw [red, thick, join=round]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcms/(2*\b)*\x+\y}) -- cycle;
+      \draw [green, thick, join=round] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
+      \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
+      \draw [thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
+      \draw [thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt) node[above left]{$\lambda'$};
+      \fill (\x , \y)  circle (5pt) node[below right]{$\lambda$};
+      \foreach \x/\y in { 1/-1, 1/1, -2/1 } {
+        \fill[color=blue] (\x,\y) circle (4pt);
+      };
+      \draw (-5.5,-3.5) node{$\cS_\lambda$};
+      \draw [darkgreen](2.5,1) node{$\cP_\lambda$};
+      \draw [red](-2,6.5) node{$\cP'_\lambda$};
+  \end{tikzpicture}
+\end{figure}
   \section{Introduction}
@@
       \boundingrays;
-      \tikzmath{ \t=3; \r=1; \s=1; \xx = \r; \yy=\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=3; \r=1; \q=1; \xx = \r; \yy=\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=2; \s=1; \xx = \r + \b*\s; \yy=-\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=5; \r=2; \q=1; \xx = \r + \b*\q; \yy=-\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=3; \r=1; \s=1; \xx=-\r; \yy=\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=3; \r=1; \q=1; \xx=-\r; \yy=\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=1; \r=1; \s=1; \xx=-\r; \yy=-\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=1; \r=1; \q=1; \xx=-\r; \yy=-\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \s=2; \xx={\r*\b+\s*(\b*\c-1) }; \yy = {-\r -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=5; \r=1; \q=2; \xx={\r*\b+\q*(\b*\c-1) }; \yy = {-\r -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \s=2; \xx={2*\r*\b+\s*(\b*\c-1) }; \yy = {-\r*\bcms -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=5; \r=1; \q=2; \xx={2*\r*\b+\q*(\b*\c-1) }; \yy = {-\r*\bcms -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=2; \r=0.3; \s=1; \xx={2*\r*\b }; \yy = {-\r*\bcps -\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=2; \r=0.3; \q=1; \xx={2*\r*\b }; \yy = {-\r*\bcps -\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \s=2; \xx={2*(\r+\s)*\b }; \yy = {-\r*\bcps -\s*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \tikzmath{ \t=5; \r=1; \q=2; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
       \fill (\x , \y)  circle (5pt);
@@
     \end{align}
-    and by the following inequalities when $k<0$:
+    and by the following inequalities when $k<0$: \saySS{the third equation here is wrong!}
     \begin{align*}
@@
 
-    given as in the figure below:
+    %given as in the figure below:
 \begin{figure}[h!]
@@
     \newcommand{\setconstants}{
-      \tikzmath{\b = 3.5; \c = 4.4 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
+      \tikzmath{\b = 3; \c = 6 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
       \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
@@
       \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
-      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
-      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
+      %\draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
+      %\draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
       \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
@@
       \setconstants;
-      %\draw[draw=none, fill=gray!20] (0,0) -- (2*\xmax,0) -- (2*\xmax,2*\ymax) --  (0,2*\ymax) -- cycle; 
+      \tikzmath{ \t=3; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \fill[fill=gray!20] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \s=2; \xx={2*(\r+\s)*\b }; \yy = {-\r*\bcps -\s*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
-      \fill (\x , \y)  circle (5pt);
-      \fill[fill=gray!20] (\xmax, {min(\ymin,-\c*(\xmax-\x)+\y)}) -- (\xmax, {-\c*(\xmax-\x)+\y}) -- (\x,\y) -- (0, {(\b*\c-1)/\b*\x+\y}) -- ({-(\b*\c-1)*\x-\b*\y},0);
-      \draw [variable=\m, domain=\x:\xmax,thick] plot({\m}, {-\c*(\m-\x)+\y});
-      \draw [variable=\m, domain=0:\x,thick] plot({\m}, {-(\b*\c-1)/\b*(\m-\x)+\y});
+      \fill (\x , \y)  circle (5pt) node[below]{$\lambda$};
+      \draw[thick] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
+			%\draw [align=center, below] (0,\ymin) node{$\phi_k^{-1}\cC_k(\phi_k\lambda)$};
     \end{scope}
+		\draw (0,-7) node{$\phi_{-3}^{-1}\cC_{-3}(\phi_{-3}\lambda)$};
+    \begin{scope}[shift={(15,0)}]
+      \setconstants;
+      \tikzmath{ \t=3; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \fill[fill=gray!20] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
+      \boundingrays;
+      \fill (\x , \y)  circle (5pt) node[right]{$\lambda$};
+      \draw[thick] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
+    \end{scope}
+		\draw (15,-7) node{$\phi_{3}^{-1}\cC_{3}(\phi_{3}\lambda)$};
   \end{tikzpicture}
@@
 
-  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
+  %Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
+  Similar arguments using \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
   \[ 0 \le (\mu_0-\lambda_0)+\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
@@
   Similarly, the opposite dominance region $\cP'_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR_2$ defined by the inequalities $\mu_1\ge0$ and $-\lambda'_1\mu_0+\lambda'_0\mu_1\ge0$.
-  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR_1)\cup(\cS_\lambda\cap\cR_2)$ and so $\cS_\lambda$ is the maximum possible support for an element pointed at $\lambda$.
+  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR_1)\cup(\cS_\lambda\cap\cR_2)$ and so $\cS_\lambda$ is the maximum possible support for an element pointed at~$\lambda$.
 
@@
       S_{\bfa^{(n)},r}
+      \,
       x_{(n-2r,-n+2r)}^{ge}.
@@
       &=
-      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r} x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}\\
+      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}\\
       &=
-      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r} x_{n-2r,-n+2r}^{ge}
+      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r}\, x_{n-2r,-n+2r}^{ge}
     \end{align*}

### 2022-05-17 dominance_regions.tex
more points
move legend
14 pages

@@
       \fill (\x , \y)  circle (5pt) node[below right]{$\lambda$};
+      \foreach \x/\y in { 1/-3, -2/-3, -5/-3, -2/-1, -5/-1, -5/1, -2/3, -5/3, -2/5, -5/5 } {
+        \draw[color=blue, fill=white] (\x,\y) circle (4pt);
+      };
       \foreach \x/\y in { 1/-1, 1/1, -2/1 } {
@@
       };
-      \draw (-5.5,-3.5) node{$\cS_\lambda$};
+      \draw (-3.5,-3.5) node{$\cS_\lambda$};
       \draw [darkgreen](2.5,1) node{$\cP_\lambda$};
@@
   Similarly, the opposite dominance region $\cP'_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR_2$ defined by the inequalities $\mu_1\ge0$ and $-\lambda'_1\mu_0+\lambda'_0\mu_1\ge0$.
-  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR_1)\cup(\cS_\lambda\cap\cR_2)$ and so $\cS_\lambda$ is the maximum possible support for an element pointed at~$\lambda$.
+  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR_1)\cup(\cS_\lambda\cap\cR_2)$ so $\cS_\lambda$ is the maximum possible support for an element pointed at~$\lambda$.
 
@@
       &=
-      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}\\
-      &=
+      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}
+      =
       \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r}\, x_{n-2r,-n+2r}^{ge}
@@
 ratios of elementary symmetric functions $\frac{e_{r,n-r}}{e_n}$) evaluated at $\bfa^{(n)}$.
-    We leave the details to the interested reader.
+    We leave the details to the reader.
   \end{remark}
@@
 
-    \bibitem{rupel}
-      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
+    %\bibitem{rupel}
+      %D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
 Algebraic Combinatorics, \textbf{2} (2019) no.

### 2022-05-17 dominance_regions.tex
Formating

@@
       \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP_\lambda$ is the point $\lambda$. 
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP_\lambda$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP_\lambda$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP_\lambda$ is the kite with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP_\lambda$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP_\lambda$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP_\lambda$ is the trapezoid with  vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP_\lambda$ is the triangle with  vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP_\lambda$ is the kite with  vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP_\lambda$ is the triangle with  vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
+      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP_\lambda$ is the trapezoid with  vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
     \end{enumerate}
@@
           \item If $\lambda_0 < 0$ and $0\le\lambda_1$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_0,-c\lambda_0+\lambda_1)$.
-          \item If $\lambda_0,\lambda_1 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $(\lambda_0,-c\lambda_0+\lambda_1)$.
-          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $-c\lambda_0-(bc-1)\lambda_1\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\big((bc+1)\lambda_0-b^2c\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$.
-          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $0 < -c\lambda_0-(bc-1)\lambda_1$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $(0,0)$.
+          \item If $\lambda_0,\lambda_1 < 0$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and ${(\lambda_0,-c\lambda_0+\lambda_1)}$.
+          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $-c\lambda_0-(bc-1)\lambda_1\le 0$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\big((bc+1)\lambda_0-b^2c\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$.
+          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $0 < -c\lambda_0-(bc-1)\lambda_1$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $(0,0)$.
 Here the point $(0,0)$ and its adjacent open segments are excluded from $\cS_\lambda$.
         \end{enumerate}
-      \item If $\lambda$ lies inside of $\cI$, then the support of $x_\lambda$ is contained in $\cS_\lambda$ with corner vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
+      \item If $\lambda$ lies inside of $\cI$, then the support of $x_\lambda$ is contained in $\cS_\lambda$ with  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
         Moreover, there is an element pointed at $\lambda$ whose support is precisely the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cS_\lambda$.

### 2022-05-17 dominance_regions.tex
minor edit
Wrong figure, corrected!
started on references

@@
       \fill [fill=gray!30, fill opacity=0.4] (\x,\y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- cycle;
-      \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcms/(2*\b)*\x+\y}) -- cycle;
+      \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) --  (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
       \fill [fill=green!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
-      \draw [red, thick, join=round]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcms/(2*\b)*\x+\y}) -- cycle;
+      \draw [red, thick, join=round]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
       \draw [green, thick, join=round] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
@@
   \section{Introduction}
-  Cluster algebras were introduced by Fomin and Zelevinsky as a tool in the study of Lusztig's (dual) canonical bases.
+  Cluster algebras were introduced by Fomin and Zelevinsky as a tool in the study of Lusztig's dual canonical bases.
   Since their inception they have found application in a variety of different areas in mathematics, nevertheless a fundamental problem in the theory remains constructing bases with ``good'' properties.
 
-  Over time several bases for cluster algebras have been constructed in a variety of generalities \cite{foo,bar,baz}. 
+  Over time several bases for cluster algebras have been constructed in a variety of generalities \cite{CI12,DT13,SZ04,LLZ14, Dup11,Dup12,Pla13, MSW13,T14,BZ14,GHKK18}.
   All of them share a property of being ``pointed''.

### 2022-05-18 dominance_regions.tex

--- 2022-05-17 dominance_regions.tex
@@
 \begin{document}
-
   \begin{abstract}
@@
 
-\begin{figure}[h!]
-  \centering
-    \newcommand{\setconstants}{
-      \tikzmath{\b = 3; \c = 6 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
-      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -4; \ymax = 8;}
-      \clip ({\xmin-0.2},{\ymin-0.2}) rectangle ({\xmax+0.2},{\ymax+0.2});
-    }
-    \newcommand{\boundingrays}{
-      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
-      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
-      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
-      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
-    }
-  \begin{tikzpicture}[scale=.5]
-      \setconstants;
-      \foreach \x in {\xmin,...,\xmax} {
-        \foreach \y in {\ymin,...,\ymax} {
-          \fill[color=gray] (\x,\y) circle (0.05);
-        }
-      };
-      \tikzmath{ \x=4; \y=-3;};
-      \boundingrays;
-      \fill [fill=gray!30, fill opacity=0.4] (\x,\y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- cycle;
-      \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcms/(2*\b)*\x+\y}) -- cycle;
-      \fill [fill=green!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
-      \draw [red, thick, join=round]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcms/(2*\b)*\x+\y}) -- cycle;
-      \draw [green, thick, join=round] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
-      \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
-      \draw [thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
-      \draw [thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
-      \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt) node[above left]{$\lambda'$};
-      \fill (\x , \y)  circle (5pt) node[below right]{$\lambda$};
-      \foreach \x/\y in { 1/-3, -2/-3, -5/-3, -2/-1, -5/-1, -5/1, -2/3, -5/3, -2/5, -5/5 } {
-        \draw[color=blue, fill=white] (\x,\y) circle (4pt);
-      };
-      \foreach \x/\y in { 1/-1, 1/1, -2/1 } {
-        \fill[color=blue] (\x,\y) circle (4pt);
-      };
-      \draw (-3.5,-3.5) node{$\cS_\lambda$};
-      \draw [darkgreen](2.5,1) node{$\cP_\lambda$};
-      \draw [red](-2,6.5) node{$\cP'_\lambda$};
-  \end{tikzpicture}
-\end{figure}
   \section{Introduction}
@@
       \boundingrays;
-      \tikzmath{ \t=3; \r=1; \q=1; \xx = \r; \yy=\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=3; \r=1; \s=1; \xx = \r; \yy=\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=2; \q=1; \xx = \r + \b*\q; \yy=-\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=5; \r=2; \s=1; \xx = \r + \b*\s; \yy=-\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=3; \r=1; \q=1; \xx=-\r; \yy=\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=3; \r=1; \s=1; \xx=-\r; \yy=\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=1; \r=1; \q=1; \xx=-\r; \yy=-\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=1; \r=1; \s=1; \xx=-\r; \yy=-\s; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x, \y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \q=2; \xx={\r*\b+\q*(\b*\c-1) }; \yy = {-\r -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=5; \r=1; \s=2; \xx={\r*\b+\s*(\b*\c-1) }; \yy = {-\r -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \q=2; \xx={2*\r*\b+\q*(\b*\c-1) }; \yy = {-\r*\bcms -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=5; \r=1; \s=2; \xx={2*\r*\b+\s*(\b*\c-1) }; \yy = {-\r*\bcms -\c*\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=2; \r=0.3; \q=1; \xx={2*\r*\b }; \yy = {-\r*\bcps -\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=2; \r=0.3; \s=1; \xx={2*\r*\b }; \yy = {-\r*\bcps -\s};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \q=2; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \tikzmath{ \t=5; \r=1; \s=2; \xx={2*(\r+\s)*\b }; \yy = {-\r*\bcps -\s*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
       \fill (\x , \y)  circle (5pt);
@@
     \end{align}
-    and by the following inequalities when $k<0$: \saySS{the third equation here is wrong!}
+    and by the following inequalities when $k<0$: \saySS{the third equation here is wrong!} \sayDR{I am not seeing what is wrong with it, doesn't it match the points you plotted?}
     \begin{align*}
@@
   \begin{tikzpicture}[scale=.3]
+    %negatives k=-3
     \begin{scope}[shift={(0,0)}]
       \setconstants;
-      \tikzmath{ \t=3; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \tikzmath{ \t=3; \r=1; \s=1.6; \xx={2*(\r+\s)*\b }; \yy = {-\r*\bcps -\s*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
       \fill[fill=gray!20] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
       \boundingrays;
-      \fill (\x , \y)  circle (5pt) node[below]{$\lambda$};
+      \fill (\x , \y)  circle (5pt);
       \draw[thick] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
@@
     \draw (0,-7) node{$\phi_{-3}^{-1}\cC_{-3}(\phi_{-3}\lambda)$};
+    %positives k=3
     \begin{scope}[shift={(15,0)}]
       \setconstants;
-      \tikzmath{ \t=3; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \tikzmath{ \t=3; \r=1; \s=1.6; \xx={2*(\r+\s)*\b }; \yy = {-\r*\bcps -\s*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
       \fill[fill=gray!20] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
       \boundingrays;
-      \fill (\x , \y)  circle (5pt) node[right]{$\lambda$};
+      \fill (\x , \y)  circle (5pt);
       \draw[thick] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
@@
 
-  %Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
-  Similar arguments using \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
+  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
   \[ 0 \le (\mu_0-\lambda_0)+\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
@@
   Similarly, the opposite dominance region $\cP'_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR_2$ defined by the inequalities $\mu_1\ge0$ and $-\lambda'_1\mu_0+\lambda'_0\mu_1\ge0$.
-  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR_1)\cup(\cS_\lambda\cap\cR_2)$ so $\cS_\lambda$ is the maximum possible support for an element pointed at~$\lambda$.
+  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR_1)\cup(\cS_\lambda\cap\cR_2)$ and so $\cS_\lambda$ is the maximum possible support for an element pointed at $\lambda$.
 
@@
       &=
-      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}
-      =
+      \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{k=0}^n \sum_{\ell=k}^{n-2r} {\ell\choose k} {n-2r\choose \ell} \, x_0^{2(\ell-k)} x_1^{2(n-2r-\ell)}\\
+      &=
       \sum_{r=0}^{\lfloor n/2\rfloor} S_{\bfa^{(n)},r}\, x_{n-2r,-n+2r}^{ge}
@@
 ratios of elementary symmetric functions $\frac{e_{r,n-r}}{e_n}$) evaluated at $\bfa^{(n)}$.
-    We leave the details to the reader.
+    We leave the details to the interested reader.
   \end{remark}
@@
 
-    %\bibitem{rupel}
-      %D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
+    \bibitem{rupel}
+      D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
 Algebraic Combinatorics, \textbf{2} (2019) no.

### 2022-05-18 dominance_regions.tex
Small tweak to the first image
Debugging equation

--- 2022-05-17 dominance_regions.tex
@@
       \tikzmath{\b = 3; \c = 6 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
-      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -4; \ymax = 8;}
+      \tikzmath{ \xmin = -6; \xmax = 5; \ymin = -4; \ymax = 8;}
       \clip ({\xmin-0.2},{\ymin-0.2}) rectangle ({\xmax+0.2},{\ymax+0.2});
@@
       \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) --  (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
-      \fill [fill=green!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
+      \fill [fill=darkgreen!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
       \draw [red, thick, join=round]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
-      \draw [green, thick, join=round] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
+      \draw [darkgreen, thick, join=round] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
@@
     \end{align}
-    and by the following inequalities when $k<0$: \saySS{the third equation here is wrong!}
+    and by the following inequalities when $k<0$: \saySS{the third equation here is wrong!} \sayDR{I am not seeing what is wrong with it, doesn't it match the points you plotted?}
+    \saySS{It looks to me the current equation is the red one in the picture (wrong) and the correct one is the blue one. They differ in signs.}
     \begin{align*}
@@
   \begin{tikzpicture}[scale=.3]
+    %negatives k=-3
     \begin{scope}[shift={(0,0)}]
@@
       \draw[thick] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, red] plot ({\p}, {(\b*\c-1)*(\x-\p)/\b+(\b*\c-2)*\y});
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, blue] plot ({\p}, {(\b*\c-1)*(-\x+\p)/\b-(\b*\c-2)*\y});
 			%\draw [align=center, below] (0,\ymin) node{$\phi_k^{-1}\cC_k(\phi_k\lambda)$};
@@
     \draw (0,-7) node{$\phi_{-3}^{-1}\cC_{-3}(\phi_{-3}\lambda)$};
+    %positives k=3
     \begin{scope}[shift={(15,0)}]

### 2022-05-18 dominance_regions.tex
Trying to higligt equations in the fegure of lemma 4.3
More of the same
very thin

@@
     \newcommand{\setconstants}{
-      \tikzmath{\b = 3; \c = 6 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
+      \tikzmath{\b = 2.5; \c =4.5 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
       \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
@@
       \setconstants;
-      \tikzmath{ \t=3; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \tikzmath{ \t=4.5; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
       \fill[fill=gray!20] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
@@
       \setconstants;
-      \tikzmath{ \t=3; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \tikzmath{ \t=4.5; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
       \fill[fill=gray!20] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
       \boundingrays;
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {(\b*\c-1)*(\x-\p)/\b+\y});
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {\c*(\b*\c-2)/(\b*\c-1)*(\x-\p)+\y});
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {\c*(\b*\c-2)/(\b*\c-1)*\x+\c/(\b*\c-1)*\p +\y});
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {-\c*(\b*\c-2)*\x-\c*\p -(\b*\c-1)*\y});
       \fill (\x , \y)  circle (5pt) node[right]{$\lambda$};
@@
 
-%    \[
-%      \begin{tikzpicture}
-%        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
-%        \draw[-] (-8,0) -- (5,0);
-%        \draw[-] (0,-5) -- (0,5);
-%        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
-%        \draw[dashed] (0,0) -- (5,-2.113);
-%        \draw[dashed] (0,0) -- (3.17,-5);
-%        \node at (1,-0.9) {$\cI$};
-%        \draw[fill=black] (3.5,-3) circle (2pt);
-%        \node[right] at (3.5,-3) {$\lambda$};
-%        \draw[->,thick] (3.5,-3) -- (47/10,-5);
-%        \draw[-,thick] (3.5,-3) -- (0,26/10);
-%        \draw[-,thick] (0,26/10) -- (-26/4,0);
-%        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
-%        \node at (4.5,-4) {\eqref{ineq:1}};
-%        \node at (2.34,-0.5) {\eqref{ineq:2}};
-%        \node at (-3,1.75) {\eqref{ineq:3}};
-%        \node at (-5.36,-3) {\eqref{ineq:4}};
-%      \end{tikzpicture}
-%    \]
   \end{lemma}

### 2022-05-18 dominance_regions.tex
Figures with lines

@@
     \end{align}
-    and by the following inequalities when $k<0$: \saySS{the third equation here is wrong!} \sayDR{I am not seeing what is wrong with it, doesn't it match the points you plotted?}
-    \saySS{It looks to me the current equation is the red one in the picture (wrong) and the correct one is the blue one. They differ in signs.}
+    and by the following inequalities when $k<0$:
     \begin{align*}
@@
       \boundingrays;
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {\c*(\x-\p)/(\b*\c-1)+\y});
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {(\b*\c-1)/(\b*\c-2)/\b*(\x-\p)+\y});
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {(\b*\c-1)*(-\x+\p)/\b-(\b*\c-2)*\y});
+      \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {-((\b*\c-1)*\x+\b*(\b*\c-2)*\y+\p)/\b});
       \fill (\x , \y)  circle (5pt) node[below]{$\lambda$};
       \draw[thick] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
-      \draw[domain=\xmin:\xmax, smooth, variable=\p, red] plot ({\p}, {(\b*\c-1)*(\x-\p)/\b+(\b*\c-2)*\y});
-      \draw[domain=\xmin:\xmax, smooth, variable=\p, blue] plot ({\p}, {(\b*\c-1)*(-\x+\p)/\b-(\b*\c-2)*\y});
-			%\draw [align=center, below] (0,\ymin) node{$\phi_k^{-1}\cC_k(\phi_k\lambda)$};
     \end{scope}

### 2022-05-18 dominance_regions.tex
Figures with shades

@@
       \tikzmath{ \t=4.5; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
-      \fill[fill=gray!20] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
+      %\fill[fill=gray!20] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
       \boundingrays;
+	    \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p] plot ({\p}, {\c*(\x-\p)/(\b*\c-1)+\y}) -- (\xmax,\ymax) -- (\xmin,\ymax) -- cycle;
+      \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p] plot ({\p}, {(\b*\c-1)/(\b*\c-2)/\b*(\x-\p)+\y}) -- (\xmax,\ymax) -- (\xmin,\ymax) -- cycle;
+      \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p] plot ({\p}, {(\b*\c-1)*(-\x+\p)/\b-(\b*\c-2)*\y}) -- (\xmax,\ymax) -- (\xmax,\ymin) -- cycle;
+      \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p] plot ({\p}, {-((\b*\c-1)*\x+\b*(\b*\c-2)*\y+\p)/\b}) -- (\xmax,\ymin) -- (\xmin,\ymin) -- cycle;
       \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {\c*(\x-\p)/(\b*\c-1)+\y});
@@
       \tikzmath{ \t=4.5; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
-      \fill[fill=gray!20] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
+      %\fill[fill=gray!20] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
       \boundingrays;
+      \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p]plot ({\p}, {(\b*\c-1)*(\x-\p)/\b+\y}) -- (\xmin,\ymin) -- (\xmin,\ymax) -- cycle;
+      \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p]plot ({\p}, {\c*(\b*\c-2)/(\b*\c-1)*(\x-\p)+\y}) -- (\xmin,\ymin) -- (\xmin,\ymax) -- cycle;
+      \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p]plot ({\p}, {\c*(\b*\c-2)/(\b*\c-1)*\x+\c/(\b*\c-1)*\p +\y}) -- (\xmax,\ymin) -- (\xmin,\ymin) -- cycle;
+      \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p]plot ({\p}, {-\c*(\b*\c-2)*\x-\c*\p -(\b*\c-1)*\y}) -- (\xmax,\ymin) -- (\xmax,\ymax) -- (\xmin,\ymax) -- cycle;
       \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {(\b*\c-1)*(\x-\p)/\b+\y});

### 2022-05-19 dominance_regions.tex
Obsessing about the figures
Obsessing even more

@@
     \newcommand{\boundingrays}{
-      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
-      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
-      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
-      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
+      \draw [color=gray, thick] (2*\xmin,0) -- (2*\xmax,0);
+      \draw [color=gray, thick] (0,2*\ymin) -- (0, 2*\ymax);
+      \draw [color=gray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
+      \draw [color=gray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
     }
@@
       \setconstants;
+      \tikzmath{ \x=4; \y=-3;};
+      \fill [fill=black!30, fill opacity=0.4] (\x,\y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- cycle;
+      \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) --  (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
+      \fill [fill=darkgreen!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
       \foreach \x in {\xmin,...,\xmax} {
@@
       };
-      \tikzmath{ \x=4; \y=-3;};
       \boundingrays;
-      \fill [fill=gray!30, fill opacity=0.4] (\x,\y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- cycle;
-      \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) --  (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
-      \fill [fill=darkgreen!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
       \draw [red, thick, join=round]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
@@
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
-      \draw [thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
-      \draw [thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      %\draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
+      %\draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
       \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt) node[above left]{$\lambda'$};
@@
     \newcommand{\boundingrays}{
-      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
-      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
-      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
-      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
-      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
-      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
+      \draw [color=gray, thick] (2*\xmin,0) -- (2*\xmax,0);
+      \draw [color=gray, thick] (0,2*\ymin) -- (0, 2*\ymax);
+      \draw [color=gray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
+      \draw [color=gray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
+      \draw [color=gray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
+      \draw [color=gray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
     }
@@
       \boundingrays;
-      \tikzmath{ \t=5; \r=1; \q=2; \xx={\r*\b+\q*(\b*\c-1) }; \yy = {-\r -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
+      \tikzmath{ \t=5; \r=1; \q=1; \xx={\r*\b+\q*(\b*\c-1) }; \yy = {-\r -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
       \fill (\x,\y) circle (5pt);
@@
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);
-      \draw [thick, dash dot, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth on 4\pgflinewidth off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
@@
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
-      \draw [thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
-      \draw [thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
       \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
@@
     \newcommand{\boundingrays}{
-      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
-      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
+      \draw [color=gray, thick] (2*\xmin,0) -- (2*\xmax,0);
+      \draw [color=gray, thick] (0,2*\ymin) -- (0, 2*\ymax);
+      \draw [color=gray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
+      \draw [color=gray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
       %\draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
       %\draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
-      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
-      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
     }
@@
       %\fill[fill=gray!20] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
-      \boundingrays;
 	    \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p] plot ({\p}, {\c*(\x-\p)/(\b*\c-1)+\y}) -- (\xmax,\ymax) -- (\xmin,\ymax) -- cycle;
@@
       \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p] plot ({\p}, {-((\b*\c-1)*\x+\b*(\b*\c-2)*\y+\p)/\b}) -- (\xmax,\ymin) -- (\xmin,\ymin) -- cycle;
+      \boundingrays;
       \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {\c*(\x-\p)/(\b*\c-1)+\y});
@@
       %\fill[fill=gray!20] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
-      \boundingrays;
       \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p]plot ({\p}, {(\b*\c-1)*(\x-\p)/\b+\y}) -- (\xmin,\ymin) -- (\xmin,\ymax) -- cycle;
@@
       \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p]plot ({\p}, {-\c*(\b*\c-2)*\x-\c*\p -(\b*\c-1)*\y}) -- (\xmax,\ymin) -- (\xmax,\ymax) -- (\xmin,\ymax) -- cycle;
+      \boundingrays;
       \draw[domain=\xmin:\xmax, smooth, variable=\p, black!60, very thin] plot ({\p}, {(\b*\c-1)*(\x-\p)/\b+\y});
@@
   The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{LLZ,cgmmrsw}.
-  This is indicated by the solid and dashed lines in Theorem~\ref{th:maximum support} where dashed lines indicate points that are excluded from the support (note that the white dot does not indicate that this point is excluded).
+  This is indicated by the solid and dotted lines in Theorem~\ref{th:maximum support} where dotted lines indicate points that are excluded from the support (note that the white dot does not indicate that this point is excluded).
   For our purposes, it is enough to observe the following closure property for the greedy support.

### 2022-05-19 dominance_regions.tex
Intensifies

@@
       %\draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
-      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
-      \draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
+      \tikzmath{ \gap=3; }
+      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off {\gap*\pgflinewidth}] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, join=round, line cap=round, dash pattern=on {\gap*\pgflinewidth} off {2*\gap*\pgflinewidth}] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
       \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt) node[above left]{$\lambda'$};
@@
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);
-      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth on 4\pgflinewidth off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \tikzmath{ \gap=3.1; }
+      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off {\gap*\pgflinewidth} on {\gap*\pgflinewidth} off {\gap*\pgflinewidth}] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
@@
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
-      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
-      \draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
+      \tikzmath{ \gap=3.1; }
+      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off {\gap*\pgflinewidth}] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
+      \draw [thick, join=round, line cap=round, dash pattern=on {\gap*\pgflinewidth} off {2*\gap*\pgflinewidth} ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
       \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);

### 2022-05-19 dominance_regions.tex
more shading
Minor edits in section 7

@@
       \setconstants;
-      \tikzmath{ \t=4.5; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
-      %\fill[fill=gray!20] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
+      \tikzmath{ \t=4.2; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \fill[fill=black!50] (\xmax, {\c*(\x-\xmax)/(\b*\c-1)+\y}) --  (\x,\y) -- ({\x+\b*(\b*\c-2)*\y/(\b*\c-1)},0) -- (0,{-(\b*\c-1)*\x/\b-(\b*\c-2)*\y}) -- (\xmax, {-(\b*\c-1)*\x/\b-(\b*\c-2)*\y-\xmax/\b});
 	    \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p] plot ({\p}, {\c*(\x-\p)/(\b*\c-1)+\y}) -- (\xmax,\ymax) -- (\xmin,\ymax) -- cycle;
@@
       \setconstants;
-      \tikzmath{ \t=4.5; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
-      %\fill[fill=gray!20] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
+      \tikzmath{ \t=4.2; \r=1; \q=1.6; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
+      \fill[fill=black!50] ({\x+\b*(\y-\ymin)/(\b*\c-1)}, \ymin) -- (\x,\y) -- (0, {\c*(\b*\c-2)*\x/(\b*\c-1)+\y}) -- ({-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},0) -- ({-\ymin/\c-(\b*\c-2)*\x-(\b*\c-1)*\y/\c},\ymin);
       \fill[fill=black!25, opacity=0.3, domain=\xmin:\xmax, smooth, variable=\p]plot ({\p}, {(\b*\c-1)*(\x-\p)/\b+\y}) -- (\xmin,\ymin) -- (\xmin,\ymax) -- cycle;
@@
 
-    By Remark \ref{rk:symmetric}, this is equivalent to the fact that the symmetric monomial functions in $n$ variables $m_{2^{(r)},1^{(n-2r)}}$ are algebraically independent.
+    By Remark \ref{rk:symmetric}, this is equivalent to the fact that the monomial symmetric functions in $n$ variables $m_{2^{(r)},1^{(n-2r)}}$ are algebraically independent.
     But this follows immediately from the observation that 
@@
     \]
-    for some coefficients $c_i$ with $c_r=1$, and the fundamental theorem of symmetric polynomials. 
+    for some coefficients $c_i$ with $c_r=1$, and the Fundamental Theorem of Symmetric Polynomials. 
   \end{proof}

### 2022-05-20 dominance_regions.tex
Bibliography

@@
 
-  Over time several bases for cluster algebras have been constructed in a variety of generalities \cite{CI12,DT13,SZ04,LLZ14, Dup11,Dup12,Pla13, MSW13,T14,BZ14,GHKK18}.
+  Over time several bases for cluster algebras have been constructed in a variety of generalities \cite{BZ14,CI12,DT13,Dup11,Dup12,GHKK18,LLZ14,MSW13,Pla13,SZ04,T14}.
   All of them share a property of being ``pointed''.
   Being pointed turned out to be a desirable feature for a basis to have and a natural question is to find all bases enjoying this property.
-  Recently Qin studied the deformability of pointed bases whenever the cluster algebra has full rank \cite{qin}. 
+  Recently Qin studied the deformability of pointed bases whenever the cluster algebra has full rank \cite{Qin19}. 
   As no explicit calculation is carried out in his work, we aim here at describing explicitly the space of deformability for pointed bases in rank two, i.e.
@@
   \end{equation}
-  By the Laurent Phenomenon \cite{fomin-zelevinsky}, each $x_m$ is actually an element of $\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for any $k\in\ZZ$.
-  Moreover, these Laurent polynomials are known to have positive coefficients \cite{LLZ,lee-schiffler,GHKK}.
+  By the Laurent Phenomenon \cite{FZ02}, each $x_m$ is actually an element of $\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for any $k\in\ZZ$.
+  Moreover, these Laurent polynomials are known to have positive coefficients \cite{GHKK18,LLZ14,LS15}.
 
@@
 the elements that can be written in the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $\alpha_k,\alpha_{k+1}$ non-negative integers.
-  Indeed, by \cite[Lemma 3.4.12]{qin} cluster monomials are part of any pointed basis in any cluster algebra.
+  Indeed, by \cite[Lemma 3.4.12]{Qin19} cluster monomials are part of any pointed basis in any cluster algebra.
   We achieve the same conclusion in our setting by elementary calculations (cf. Lemma~\ref{le:cluster monomials}).
@@
     \label{th:dominance}
-    \cite[Theorem 1.2.1]{qin}
+    \cite[Theorem 1.2.1]{Qin19}
     Let $x=\{x_\lambda\}$ and $y=\{y_\lambda\}$ be pointed bases of $\cA(b,c)$.
@@
   A natural starting basis is the so-called \emph{greedy basis} in which all $\rho_{\alpha_0,\alpha_1}$ are non-negative and these coefficients are chosen to be minimal.
-  It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
+  It is known that this choice coincides with the theta basis \cite{CGMMRSW17,GHKK18}.
   The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications of $\cA(b,c)$ with the subalgebras of $\ZZ[x_0^{\pm1},x_1^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
@@
 
-  The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{LLZ,cgmmrsw}.
+  The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{CGMMRSW17,LLZ14}.
   This is indicated by the solid and dotted lines in Theorem~\ref{th:maximum support} where dotted lines indicate points that are excluded from the support (note that the white dot does not indicate that this point is excluded).
@@
     \[ 
-      m_{2^{(r)},1^{(n-2r)}} = \sum_{i=0}^r c_i\, e_{n-i,i}
+      m_{2^{(r)},1^{(n-2r)}} = \sum_{i=0}^r \gamma_i\, e_{n-i,i}
     \]
-    for some coefficients $c_i$ with $c_r=1$, and the Fundamental Theorem of Symmetric Polynomials. 
+    for some coefficients $\gamma_i$ with $\gamma_r=1$, and the Fundamental Theorem of Symmetric Polynomials. 
   \end{proof}
 
-  \begin{thebibliography}{XXX}
-    \bibitem{cgmmrsw}
-      our other paper
-
-    \bibitem{ghkk}
-      Gross et al
-
-    \bibitem{lee-li-zelevinsky}
-      K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Math. \textbf{20} (2014), pp.~57--82.
-
-    \bibitem{qin}
-      Fan's paper
-
-    %\bibitem{rupel}
-      %D.~Rupel: Rank two non-commutative Laurent phenomenon and pseudo-positivity.
-Algebraic Combinatorics, \textbf{2} (2019) no.
-6, pp.~1239--1273.
-\href{https://doi.org/10.5802/alco.81}{DOI: 10.5802/alco.81}.
-
-    \bibitem{RSW19}
-      Our paper
-  \end{thebibliography}
+% bibliography
+% because of conflicts some keys needs to be fixed by hand.
+% to regenerate the bibliography delete the one below, uncomment the following two lines and recompile, comment the two lines again, edit monomialminors.bbl as needed and paste its content here
+\bibliographystyle{amsalpha}
+\bibliography{bibliography}
 
 \end{document}
-
-  \section{Bases From Compatible Pairs on Dyck Paths}
-  \sayDR{This is a bit of a repetition of the above introduction to Dyck paths, but with slightly different goals it seemed that a modified exposition was more appropriate.}
-  For $a_1,a_2\in\ZZ_{\ge0}$, choose a Dyck path $D$ in the lattice rectangle $[0,a_1]\times[0,a_2]$.
-  When we wish to emphasize the upper right bounding corner we will write $D[a_1,a_2]$.
-  Consider $D$ as the totally ordered set of its edges along the natural labeling from $(0,0)$ to $(a_1,a_2)$.
-  It may be convenient to identify $D$ with the ordered set $[1,a_1+a_2]$.
-  Write $D=D_1\sqcup D_2$, where $D_1=\{h_1,\ldots,h_{a_1}\}$ is the set of horizontal edges and $D_2=\{v_1,\ldots,v_{a_2}\}$ is the set of vertical edges.
-  Define the \emph{height}, $\hgt(h)$ for $h\in D_1$, as one more than the number of $v\in D_2$ with $v<h$.
-  Define the \emph{depth}, $\dpt(v)$ for $v\in D_2$, as the number of $h\in D_1$ with $h<v$.
-  \begin{remark}
-    The seemingly different conventions for computing height and depth provide uniformity later.
-    Indeed, the vertical edges immediately following $h_d$ have depth $d$, while this convention allows the horizontal edges immediately preceding $v_\ell$ to similarly be said to have height $\ell$.
-  \end{remark}
-
-  Observe that the data of $D$ is just the data of a bipartition of a finite totally ordered set $D=D_1\sqcup D_2$.
-  Given a Dyck path $D=D_1\sqcup D_2$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $\bar{D}=\bar{D}_1 \sqcup \bar{D}_2$ for the Dyck path (under the identification with $[1,a_1+a_2]$) in the lattice rectangle $[0,a_2]\times[0,a_1]$ with $\bar{D}_1=a_1+a_2+1-D_2$ and $\bar{D}_2=a_1+a_2+1-D_1$.
-  This operation can be visualized as transposing the Dyck path.
-
-  Given any quantity or object $P$ whose definition depends on $b$ and $c$, write $\vv{P}$ for the same quantity or object defined with $b$ and $c$ interchanged.
-  In particular, we have $\vv{u}_{m,\varepsilon}=u_{m,-\varepsilon}$ for any $m$ and any $\varepsilon=\pm1$.
-
-  \subsection{Structure of Dyck Paths}
-
-  Write $D^{max}=D^{max}[a_1,a_2]$ for the maximal Dyck path in the lattice rectangle $[0,a_1]\times[0,a_2]$, i.e.
-$D^{max}$ never crosses above the diagonal line joining $(0,0)$ to $(a_1,a_2)$ and any lattice point above $D^{max}$ also lies above the diagonal.
-  Observe that $\bar{D}^{max}[a_1,a_2]=D^{max}[a_2,a_1]$.
-
-  \begin{definition}
-    Call a Dyck path $D$ 
-    \begin{itemize}
-      \item \emph{horizontally-adapted to $b$} if no vertical edge of $D$ is immediately preceded by more than $b$ horizontal edges;
-      \item \emph{vertically-adapted to $c$} if no horizontal edge of $D$ is immediately followed by more than $c$ vertical edges.
-    \end{itemize}
-  \end{definition}
-
-  \begin{definition}
-    \label{def:Dyck path mutations}
-    Given a Dyck path $D=D[a_1,a_2]$ which is vertically-adapted to $c$, define a Dyck path $\mu_{1,c}(D)$ inside the lattice rectangle $[0,ca_1-a_2]\times[0,a_1]$ by replacing each horizontal edge of $D$, together with the $r$ vertical edges which immediately follow it, by $c-r$ horizontal edges followed by a vertical edge.
-    This provides a canonical identification of the horizontal edges of $D$ with the vertical edges of $\mu_{1,c}(D)$, this identification is again denoted by $\mu_{1,c}$.
-
-    Given a Dyck path $D=D[a_1,a_2]$ which is horizontally-adapted to $b$, define a Dyck path $\mu_{2,b}(D)$ inside the lattice rectangle $[0,a_2]\times[0,ba_2-a_1]$ by replacing each vertical edge of $D$, together with the $r$ horizontal edges which immediately precede it, by a horizontal edge followed by $b-r$ vertical edges.
-    This provides a canonical identification of the vertical edges of $D$ with the horizontal edges of $\mu_{2,b}(D)$, this identification is again denoted by $\mu_{2,b}$.
-  \end{definition}
-  \begin{remark}
-    Observe that $\mu_{1,a}$ and $\mu_{2,a}$ are inverse for any $a\ge1$ whenever they are defined.
-  \end{remark}
-
-  The following result is proven in \cite[Lemma 2.4]{rupel} with appropriate notation changes, cf. Theorem~\ref{th:dominant Dyck path recursion} for a slight modification and explicit proof.
-  \begin{lemma}\mbox{}
-    \label{le:maximal Dyck path recursion}
-    \begin{enumerate}
-      \item If $a_2 < c a_1$, then $\mu_{1,c}\big(D^{max}[a_1,a_2]\big)=D^{max}[ca_1-a_2,a_1]$.
-      \item If $a_1 < b a_2$, then $\mu_{2,b}\big(D^{max}[a_1,a_2]\big)=D^{max}[a_2,ba_2-a_1]$.
-    \end{enumerate}
-  \end{lemma}
-
-  As an immediate consequence, we determine the structure of certain maximal Dyck paths.
-  We introduce the following notation for convenience:
-  \[d_m:=\begin{cases} b & \text{if $m$ is even;}\\ c & \text{if $m$ is odd;}\end{cases} \qquad \text{and} \qquad \vv{d}_m:=\begin{cases} c & \text{if $m$ is even;}\\ b & \text{if $m$ is odd;}\end{cases}\]
-  The following was proven in \cite[Corollary 2.6]{rupel} and follows by a simple induction using Lemma~\ref{le:maximal Dyck path recursion}.
-  \begin{corollary}
-    Assume $b,c\ge2$ (this can be dropped with extra notation and slight modification).
-    Then, for $\varepsilon=\pm1$ and $m\ge1$, the maximal Dyck path $D^{m,\varepsilon}:=D^{max}[u_{m,\varepsilon},u_{m-1,-\varepsilon}]$ can be constructed as follows:
-    \begin{itemize}
-      \item $D^{1,\varepsilon}$ consists of a single horizontal edge;
-      \item $D^{2,\varepsilon}$ consists of $d_2$ horizontal edges followed by a vertical edge;
-      \item for $m\ge3$, $D_{m,\varepsilon}$ consists of $d_m - 1$ copies of $D^{m-1,\varepsilon}$ followed by a copy of $D^{m-1,\varepsilon}$ with its first $D^{m-2,\varepsilon}$ removed;
-    \end{itemize}
-    and the maximal Dyck path $\vv{\bar{D}}^{m,\varepsilon}:=D^{max}[u_{m-1,\varepsilon},u_{m,-\varepsilon}]$ can be constructed as follows:
-    \begin{itemize}
-      \item $\vv{\bar{D}}^{1,\varepsilon}$ consists of a single vertical edge;
-      \item $\vv{\bar{D}}^{2,\varepsilon}$ consists of a horizontal edge followed by $\vv{d}_2$ vertical edges;
-      \item for $m\ge3$, $\vv{\bar{D}}^{m,\varepsilon}$ consists of a copy of $\vv{\bar{D}}^{m-1,\varepsilon}$ with its last $\vv{\bar{D}}^{m-2,\varepsilon}$ removed followed by $\vv{d}_m - 1$ copies of $\vv{\bar{D}}^{m-1,\varepsilon}$.
-    \end{itemize}
-  \end{corollary}
-
-  Our main interest will be with the following Dyck paths.
-  \begin{definition}
-    \label{def:dominant Dyck path}
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, define the \emph{dominant Dyck path} $D^{dom}=D^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$.
-
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_2,-a_1+ca_2)\in\cI'$, define the \emph{dual dominant Dyck path} $\vv{D}^{dom}=\vv{D}^{dom}[a_1,a_2]$ to be the maximal Dyck path starting from $(0,0)$ and terminating at $(a_1,a_2)$ while staying below the lines $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$ and $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2c}(x-a_1)$.
-  \end{definition}
-  \begin{remark}
-    \label{rem:intersection}
-    The lines defining $D^{dom}[a_1,a_2]$ meet at the point 
-    \[m_{a_1,a_2}:=\left( \frac{2ba_2-\big(bc-\sqrt{bc(bc-4)}\big)a_1}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2-2ca_1}{2\sqrt{bc(bc-4)}} \right).\]
-  \end{remark}
-
-  To understand the structure of the dominant Dyck paths, it will be convenient to consider their initial and final segments separately.
-  \begin{definition}
-    For $s>0$, define the \emph{Dyck path prefix} $\overrightarrow{D}^s$ as the maximal Dyck path with $s$ vertical edges starting from $(0,0)$ and terminating at $(d,s)$ while staying below the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, where $d=d_s=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
-    Call this $d$ the \emph{depth} of $s$.
-
-    For $t>0$, define the \emph{Dyck path suffix} $\overleftarrow{D}^t$ as the maximal Dyck path with $t$ horizontal edges starting from $(0,0)$ and terminating at $(t,h)$ while staying below the line $y-h=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-t)$, where $h=h_t=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
-    Call this $h$ the \emph{height} of $t$.
-  \end{definition}
-  \begin{remark}
-    There often exist multiple choices of $s$ with a given depth $d$ and multiple choices of $t$ with a given height $h$.
-  \end{remark}
-  \sayDR{ToDo: describe the analogue of Corollary 7.5 for the Dyck path prefixes and suffixes.}
-
-  The following result will be useful for showing that the Dyck path prefixes and suffixes behave properly.
-  \begin{lemma}
-    For $s>0$, the Dyck path prefix $\overrightarrow{D}^s$ ends in a vertical edge.
-    Similarly, for $t>0$, the Dyck path suffix $\overleftarrow{D}^t$ begins with a horizontal edge.
-  \end{lemma}
-
-  \begin{lemma}
-    For $s,t>0$, $\overrightarrow{D}^s=D^{dom}[d_s,s]$ and $\overleftarrow{D}^t=D^{dom}[t,h_t]$.
-  \end{lemma}
-  \begin{proof}
-    Is this obvious?
-    %Following Remark~\ref{rem:intersection}, the intersection point of the lines defining $D^{dom}[d_s,s]$ is given by
-    %\[m_{d_s,s}=\left( \frac{2bs-\big(bc-\sqrt{bc(bc-4)}\big)d_s}{2\sqrt{bc(bc-4)}} , \frac{\big(bc+\sqrt{bc(bc-4)}\big)s-2cd_s}{2\sqrt{bc(bc-4)}} \right).\]
-    %By definition of $d_s$, we have
-    %\[\frac{\big(bc+\sqrt{bc(bc-4)}\big)s-2cd_s}{2\sqrt{bc(bc-4)}} \le \frac{\big(bc+\sqrt{bc(bc-4)}\big)s-\big(bc-\sqrt{bc(bc-4)}\big)s}{2\sqrt{bc(bc-4)}} = s\]
-  \end{proof}
-
-  \begin{lemma}
-    For any $s,t>0$, the Dyck path prefix $\overrightarrow{D}^s$ and Dyck path suffix $\overleftarrow{D}^t$ are both horizontally-adapted to $b$ and vertically-adapted to $c$.
-  \end{lemma}
-  \begin{proof}
-    Observe that $\frac{c}{2}<\frac{bc+\sqrt{bc(bc-4)}}{2b}<c$.
-    This shows that $\overrightarrow{D}^s$ cannot contain more than $c$ consecutive vertical edges following a horizontal edge and so $\overrightarrow{D}^s$ must be vertically-adapted to $c$.
-    In addition, we see that $\overrightarrow{D}^s$ can only contain consecutive horizontal edges if $c=1$, in which case there are at most two consecutive horizontal edges preceding any vertical edge.
-    But, since we assume $bc\ge4$, that would imply $b\ge4$ and so $\overrightarrow{D}^s$ must be horizontally-adapted to $b$.
-  \end{proof}
-
-  \begin{theorem}
-    \label{th:dominant Dyck path recursion}
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, we have $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[ca_1-a_2,a_1]$ and $\mu_{2,b}\big(D^{dom}[a_1,a_2]\big)=\vv{D}^{dom}[a_2,ba_2-a_1]$.
-  \end{theorem}
-  \begin{proof}
-    We prove the result for $\mu_{1,c}$ as the result for $\mu_{2,b}$ immediately follows from $\mu_{1,b}$ being its inverse.
-    Write $D'$ for the Dyck path $\mu_{1,c}\big(D^{dom}[a_1,a_2]\big)$ and observe that by construction $D'$ has $ca_1-a_2$ horizontal edges and $a_1$ vertical edges.
-    Write $v'_1,\ldots,v'_{a_1}$ for the vertical edges of $D'$ with $v'_k$ immediately preceded by $r_k$ horizontal edges.
-    We have to show (i) that every lattice point on $D'$ stays below the lines 
-    \[y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x \qquad \text{and} \qquad y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)\]
-    while (ii) any lattice point above $D'$ is also above one of these lines.
-
-    If there exists $t$ so that $v'_t$ passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2c}x$, then
-    \[ \frac{t}{\sum\limits_{k=1}^t r_k} > \frac{bc+\sqrt{bc(bc-4)}}{2c} \]
-    or, rearranging, we have
-    \[ \frac{\sum\limits_{k=1}^t r_k}{t} < \frac{2c}{bc+\sqrt{bc(bc-4)}} = \frac{bc-\sqrt{bc(bc-4)}}{2b} \]
-    or
-    \[ \frac{bc+\sqrt{bc(bc-4)}}{2b} < \frac{ct-\sum\limits_{k=1}^t r_k}{t} = \frac{\sum\limits_{k=1}^t (c-r_k)}{t}. \]
-    But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y=\frac{bc+\sqrt{bc(bc-4)}}{2b}x$, contrary to the definition.
-
-    If there exists $t$ so that $v'_t$ passes above the line $y-a_1=\frac{bc-\sqrt{bc(bc-4)}}{2c}\big(x-(ca_1-a_2)\big)$, then
-    \[ \frac{bc-\sqrt{bc(bc-4)}}{2c} > \frac{a_1-t}{ca_1-a_2-\sum\limits_{k=1}^t r_k} \]
-    or, rearranging, we have
-    \[ \frac{ca_1-a_2-\sum\limits_{k=1}^t r_k}{a_1-t} > \frac{2c}{bc-\sqrt{bc(bc-4)}} = \frac{bc+\sqrt{bc(bc-4)}}{2b} \]
-    or
-    \[ \frac{bc-\sqrt{bc(bc-4)}}{2b} > \frac{ c(a_1-t) - \big(ca_1-a_2-\sum\limits_{k=1}^t r_k\big)}{a_1-t} = \frac{a_2-\sum\limits_{k=1}^t (c-r_k)}{a_1-t}. \]
-    But this states that the subpath of $D^{dom}[a_1,a_2]$ consisting of the first $t$ horizontal edges and all their trailing vertical edges passes above the line $y-a_2=\frac{bc-\sqrt{bc(bc-4)}}{2b}(x-a_1)$, contrary to the definition.
-
-    This proves (i), analogous calculations establish (ii). 
-  \end{proof}
-
-  Apart from being the prefix and suffix for the dominant Dyck path, the Dyck paths $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ can be observed inside the maximal Dyck paths defining cluster variables as follows.
-  \begin{lemma}\mbox{}
-    \begin{itemize}
-      \item For $s>0$ and any $m \ge 2$ so that $s < u_{m,-}$, the Dyck path prefix $\overrightarrow{D}^s$ is an initial segment of the maximal Dyck path $D^{max}[u_{m-1,+},u_{m,-}]$.
-      \item For $t>0$ and any $m \ge 2$ so that $t < u_{m,+}$, the Dyck path suffix $\overleftarrow{D}^t$ is a final segment of the maximal Dyck path $D^{max}[u_{m,+},u_{m-1,-}]$.
-    \end{itemize}
-  \end{lemma}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item Choose a width $t>0$ and $a_1 \ge t$.
-        Then there exists a unique $s$ of depth $a_1-t$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_2=s+\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$.
-      \item Choose a height $s>0$ and $a_2 \ge s$.
-        Then there exists a unique $t$ of height $a_2-s$ so that $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is the dominant Dyck path $D^{dom}[a_1,a_2]$ with $a_1=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil+t$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{remark}
-    The decomposition of $D^{dom}[a_1,a_2]$ as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$ is not uniquely determined by $a_1$ and $a_2$.
-    However, there exists at most two choices of $s$ and $t$ for which such a decomposition holds.
-  \end{remark}
-
-  \begin{lemma}
-    \label{le:floors and ceilings}
-    For any real number $x$ and any real number $r>1$, we have
-    \[\lfloor x\rfloor \le \left\lfloor \lceil xr \rceil \frac{1}{r} \right\rfloor \le \lceil x\rceil \qquad \text{and} \qquad \lfloor x\rfloor \le \left\lceil \lfloor xr \rfloor \frac{1}{r} \right\rceil \le \lceil x\rceil.\]
-  \end{lemma}
-  \begin{proof}
-    Observe that
-    \[xr\le \lceil xr \rceil < xr+1 \qquad \text{and} \qquad xr-1 < \lfloor xr \rfloor \le xr\]
-    and so
-    \[x\le \lceil xr \rceil \frac{1}{r} < x+\frac{1}{r} \qquad \text{and} \qquad x-\frac{1}{r} < \lfloor xr \rfloor \frac{1}{r} \le x.\]
-    Since $0<\frac{1}{r}<1$, the result follows.
-  \end{proof}
-
-  The following result describes the possible decomposition of the dominant Dyck path into its prefix and suffix subpaths.
-  The intersection point from Remark~\ref{rem:intersection} is a useful point of reference.
-  \begin{proposition}
-    \label{prop:dominant Dyck path decomposition}
-    For $a_1,a_2\in\ZZ_{\ge0}$ with $(-a_1+ba_2,-a_2)\in\cI$, the dominant Dyck path $D^{dom}[a_1,a_2]$ is the concatenation of $\overrightarrow{D}^s$ followed by $\overleftarrow{D}^t$ for any choice of $s$ and $t$ satisfying $a_2-s=\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil$ and $a_1-t=\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil$.
-    In this case, the pair of $s$ and $t$ will be one of the following:
-    \begin{align}
-      \label{eq:lower bounds}
-      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor\\
-      s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil\\
-      \label{eq:upper bounds}
-      s=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rceil\qquad &\text{and}\qquad t=\left\lceil\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rceil
-    \end{align}
-    If two such decompositions exist, they will be of the form \eqref{eq:lower bounds} and \eqref{eq:upper bounds}.
-  \end{proposition}
-  \begin{remark}
-    The irrationality of the slopes defining the Dyck path prefixes and suffixes makes it difficult to predict for a given choice of $a_1$ and $a_2$ precisely which of these choice of $s$ and $t$ will produce the desired equalities.
-  \end{remark}
-  \begin{proof}
-    (In progress)
-
-    For $s=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_2 - 2 c a_1}{2\sqrt{bc(bc-4)}}\right\rfloor$, by Lemma~\ref{le:floors and ceilings} we have
-    \[\left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor \le \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil\]
-    since $0<\frac{bc-\sqrt{bc(bc-4)}}{2c}<1$.
-    It follows that
-    \[ a_1 - \left\lceil \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rceil \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le a_1 - \left\lfloor \frac{2 b a_2 -\big(bc-\sqrt{bc(bc-4)}\big) a_1}{2\sqrt{bc(bc-4)}} \right\rfloor\]
-    and so
-    \[ \left\lfloor \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rfloor \le a_1 - \left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c} \right\rceil \le \left\lceil \frac{ \big(bc+\sqrt{bc(bc-4)}\big) a_1 - 2 b a_2 }{2\sqrt{bc(bc-4)}} \right\rceil\]
-    with one of these inequalities being an equality.
-
-    If the left hand inequality is an equality, we take $t=\left\lfloor\frac{\big(bc+\sqrt{bc(bc-4)}\big)a_1 - 2 b a_2}{2\sqrt{bc(bc-4)}}\right\rfloor$.
-
-    The desired equalities can be rewritten in the form 
-    \[s=a_2-\left\lceil t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rceil=\left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
-    and
-    \[t=a_1-\left\lceil s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rceil=\left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
-    Combining these, we seek $s$ and $t$ satisfying
-    \[s=\left\lfloor a_2 - \left\lfloor a_1 - s \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor\]
-    and
-    \[t=\left\lfloor a_1 - \left\lfloor a_2 - t \frac{bc-\sqrt{bc(bc-4)}}{2b}\right\rfloor \frac{bc-\sqrt{bc(bc-4)}}{2c}\right\rfloor.\]
-  \end{proof}
-
-  \subsection{Compatibility}
-  The results of this section can mostly be found in \cite{lee-li-zelevinsky,rupel}.
-  However since we work in arbitrary Dyck paths instead of just the maximal ones, some results and proofs will need to be adapted.
-
-  For $e \le e'\in D$, write $ee'$ for the subpath of $D$ beginning with $e$ and ending with $e'$.
-  When $e=e'$, we take $ee'$ to be the subpath consisting of only the edge $e$.
-  \begin{definition}
-    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$ together with a subpath $ee'\subset D$, define the \emph{horizontal shadow statistic}:
-    \begin{equation}
-      \label{eq:horizontal shadow statistic}
-      f_H(ee')=-|ee' \cap D_2|+c|ee'\cap H|
-    \end{equation}
-    and the \emph{vertical shadow statistic}:
-    \begin{equation}
-      \label{eq:vertical shadow statistic}
-      f_V(ee')=-|ee' \cap D_1|+b|ee'\cap V|.
-    \end{equation}
-  \end{definition}
-  \begin{remark}
-    Observe that the shadow statistics are additive with respect to concatenation of subpaths.
-  \end{remark}
-
-  A key notion from \cite{lee-li-zelevinsky} is that of ``compatible subsets of a maximal Dyck path'', this construction immediately generalizes to arbitrary Dyck paths as follows.
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    For $h\in H$ and $v\in V$ with $h<v$, call the path $hv$ \emph{compatible} if there exists an edge $e\in hv$ such that one of the following conditions is satisfied:
-    \begin{equation}
-      \label{eq:HGC}
-      \tag{HGC} e\ne v \quad \text{and} \quad f_H(he)=0;
-    \end{equation}
-    \begin{equation}
-      \label{eq:VGC}
-      \tag{VGC} e\ne h \quad \text{and} \quad f_V(ev)=0.
-    \end{equation}
-    Call the subset $H\sqcup V$ \emph{compatible} if every path $hv$ with $h\in H$ and $v\in V$ is compatible.
-    Write $\cC_D$ for the collection of all compatible subsets of $D$.
-    Given a subset $H\subset D_1$, write $\cC_D(H)$ for the collection of all $V\subset D_2$ for which $H\sqcup V\in\cC_D$.
-    Define $\cC_D(V)$ for $V\subset D_2$ similarly.
-  \end{definition}
-  \begin{remark}
-    In the construction of the greedy basis, it is necessary to consider $D$ as a closed cycle by identifying $(0,0)$ with $(a_1,a_2)$ and allowing subpaths $ee'$ with $e'<e$ to ``wrap around'' $D$ in the obvious way.
-    When we wish to emphasize that this condition should be imposed, we denote the Dyck path $D$ instead by $D_\WA$.
-    Following \cite[Remark 2.21]{rupel}, for $D^{m,\varepsilon}$ and $\vv{\bar{D}}^{m,\varepsilon}$ the wrap around condition does not restrict compatibility and can thus safely be omitted.
-  \end{remark}
-
-  The crucial result from \cite{lee-li-zelevinsky} can be stated as follows: if a Dyck path $D$ is vertically-adapted to $c$ (resp.
-horizontally adapted to $b$), then there is a bijection between certain compatible subsets of $D$ and certain compatible subsets of $\mu_{1,c}(D)$ (resp.
-of $\mu_{2,b}(D)$).
-  The main step in the proof that needs to be adapted to the general situation is the following.
-  For $e \le h\in D$ with $h=h_d\in D_1$, write $eh^{\!\uparrow}$ for the subpath $eh$ together with all vertical edges of depth $d$ immediately following $h$.
-  For $v \le e\in D$ with $v=v_\ell\in D_2$, write ${}^\leftarrow\!\!\! ve$ for the subpath $ve$ together with all horizontal edges of height $\ell$ immediately preceding $v$.
-  \begin{lemma}\mbox{}
-    \label{le:shadow statistic recursion}
-    \begin{enumerate}
-      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
-        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
-        Then for any $h_i \le h_j \in D_1$, we have $f_H(h_i h_j^{\!\uparrow})=-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_i v'_j)$.
-      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
-        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
-        Then for any $v_i \le v_j \in D_2$, we have $f_V({}^\leftarrow\!\!\! v_i v_j)=-\vv{f}_{H''}(h''_i {h''_j}^{\!\uparrow})$.
-    \end{enumerate}
-  \end{lemma}
-  \begin{proof}
-    Claim (2) is immediate from claim (1). 
-    By definition, we have 
-    \begin{align*}
-      -\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)&=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap V'|\\
-      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \big(D'_2\setminus \mu_{1,c}(H)\big)\big|\\
-      &=|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_1|-c|{}^\leftarrow\!\!\! v'_i v'_j \cap D'_2|+c\big|{}^\leftarrow\!\!\! v'_i v'_j \cap \mu_{1,c}(H)\big|.
-    \end{align*}
-    But, by construction of $\mu_{1,c}(D)$ and since $\mu_{2,c}(D')=D$, we have
-    \[\big|{}^\leftarrow\!\!\!
-v'_i v'_j \cap \mu_{1,c}(H)\big|=|h_i h_j^{\!\uparrow} \cap H| \qquad \text{and} \qquad c|{}^\leftarrow\!\!\!
-v'_i v'_j \cap D'_2|-|{}^\leftarrow\!\!\!
-v'_i v'_j \cap D'_1|=|h_i h_j^{\!\uparrow} \cap D_2|\]
-    giving
-    \[-\vv{f}_{V'}({}^\leftarrow\!\!\! v'_iv'_j)=-|h_i h_j^{\!\uparrow} \cap D_2|+c|h_i h_j^{\!\uparrow} \cap H|=f_H(h_i h_j^{\!\uparrow})\]
-    as desired.
-  \end{proof}
-
-  The desired bijection of compatible subsets is constructed in terms of certain subpaths determined from each compatible subset.
-  \begin{definition}
-    \label{def:shadows}
-    For $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$, define the \emph{shadow paths} as follows:
-    \begin{itemize}
-      \item For $h\in D_1$, write $D(h;H)$ for the shortest subpath $he \subset D$ with $f_H(he)=0$ or, if no such subpath exists, set $D(h;H)=hv_{a_2}$.
-      \item For $v\in D_2$, write $D(v;V)$ for the shortest subpath $ev \subset D$ with $f_V(ev)=0$ or, if no such subpath exists, set $D(v;V)=h_1 v$.
-    \end{itemize}
-    Write 
-    \[D(H):=\bigcup_{h\in H} D(h;H) \qquad \text{and} \qquad D(V):=\bigcup_{v\in V} D(v;V).\]
-    Define the \emph{shadow} of $H$ (resp.
-the \emph{shadow} of $V$) as the set $\sh_D(H):=D(H)\cap D_2$ (resp.~$\sh_D(V):=D(V)\cap D_1$) and the \emph{local shadow} of $h\in H$ (resp.
-of $v\in V$) as the set $\sh_D(h;H)=D(h;H)\cap D_2$ (resp.
-$\sh_D(v;V)=D(v;V)\cap D_1$).
-  \end{definition}
-
-  The proofs of the following results are identical to the proof of the analogous results from \cite{lee-li-zelevinsky,rupel} for maximal Dyck paths.
-  \begin{lemma}
-    \label{le:shadow statistics}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $h\in H$, take $he$ to be the path $D(h;H)$.
-        The following hold:
-        \begin{enumerate}
-          \item for any proper subpath $he'\subsetneq he$, we have $f_H(he')>0$;
-          \item if $f_H(he)=0$, then for any proper subpath $e'e\subsetneq he$, we have $f_H(e'e)<0$;
-          \item $e\in V$.
-        \end{enumerate}
-      \item For $v\in V$, take $ev$ to be the path $D(v;V)$.
-        The following hold:
-        \begin{enumerate}
-          \item for any proper subpath $e'v\subsetneq ev$, we have $f_V(e'v)>0$;
-          \item if $f_V(ev)=0$, then for any proper subpath $ee'\subsetneq ev$, we have $f_V(ee')<0$;
-          \item $e\in H$.
-        \end{enumerate}
-    \end{enumerate}
-  \end{lemma}
-  \begin{remark}
-    Observe that the subset $V$ has no influence on the claim of (1) and the subset $H$ has no influence on the claim of (2).
-  \end{remark}
-
-  \begin{definition}
-    Given two Dyck paths $D,D'$ in the lattice rectangle $[0,a_1]\times[0,a_2]$, write $D'\succ D$ if no lattice point of $D'$ lies below a lattice point of $D$.
-  \end{definition}
-  \begin{remark}
-    Equivalently, $D'\succ D$ if no lattice point of $D'$ lies to the right of a lattice point of $D$.
-  \end{remark}
-
-  \begin{proposition}
-    Let $D,D'$ be two Dyck paths in the lattice rectangle $[0,a_1]\times[0,a_2]$ with $D'\succ D$.
-    Identify $D_1$ with $D'_1$ and $D_2$ with $D'_2$ along the natural left-to-right ordering.
-    For subsets $H\subset D_1$ and $V\subset D_2$, write $H'\subset D'_1$ and $V'\subset D'_2$ for the corresponding subsets under the identification above.
-    If $(H,V) \in \cC_D$, then $(H',V') \in \cC_{D'}$.
-  \end{proposition}
-  \begin{proof}
-    It suffices, by induction, to show that the result holds if $D'$ is an immediate successor of $D$, i.e.
-when a single pair of a horizontal followed by a vertical is replaced by a vertical followed by a horizontal.
-    Assume $D'$ is obtained from $D$ in this way, say with horizontal edge $h_i$ and vertical edge $v_j$ satisfying $v_j=h_i+1$ in $D$ replaced by the vertical edge $v'_j$ and the horizontal edge $h'_i$ satisfying $h'_i=v'_j+1$ in $D'$.
-
-    Consider $(H,V) \in \cC_D$.
-    For $h\in H$ and $v\in V$, write $h'\in H'$ and $v'\in V'$ for the corresponding edges.
-    We claim that the condition \eqref{eq:HGC} (resp. \eqref{eq:VGC}) being satisfied for the path $hv$ in $D$ implies the same condition is satisfied for the path $h'v'$ in $D'$.
-
-    Suppose \eqref{eq:HGC} is satisfied for the path $hv$ and write $D(h;H)=he$ for $e\in V$ with $e<v$.
-    If $h_i,v_j\notin D(h;H)$, then under the identification with $D'$ we have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
-    Alternatively, since $e\in V$, we must have both $h_i,v_j\in D(h;H)$.
-    If $h_i\notin H$, then again we have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
-    Thus, we assume $h_i\in H$.
-
-    We begin by assuming $h_i\ne h$.
-    This gives two possibilities for $D(h';H')$ depending on $D(h'_i;H')$.
-    First, observe that $D(h_i;H)$ is a proper subpath of $h_ie$, for otherwise $f_H(h_ie)=0$ and, by the additivity of $f_H$, $he$ would not be the shortest subpath with $f_H(he)=0$.
-    Thus, if $D(h_i;H)$ is followed by at least two vertical edges inside $D(h;H)$, we again have $D(h';H')=D(h;H)$ and \eqref{eq:HGC} is satisfied for the path $h'v'$.
-    Otherwise, $D(h';H')$ is an initial subpath of $D(h;H)$ under the identification of $D'$ with $D$ and again \eqref{eq:HGC} is satisfied for the path $h'v'$.
-
-    Now if $h_i=h$...
-  \end{proof}
-
-  \begin{corollary}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $h\in H$ and a vertical edge $v\in D(h;H)$, the condition \eqref{eq:HGC} is not satisfied for the path $hv$ but for any $V\in\cC_D(H)$ the condition \eqref{eq:VGC} is satisfied for the path $hv$.
-        In particular, $D(v;V)$ is a proper subpath of $hv$ for any $V\in\cC_D(H)$.
-      \item For $v\in V$ and a horizontal edge $h\in D(v;V)$, the condition \eqref{eq:VGC} is not satisfied for the pair $hv$ but for any $H\in\cC_D(V)$ the condition \eqref{eq:HGC} is satisfied for the path $hv$.
-        In particular, $D(h;H)$ is a proper subpath of $hv$ for any $H\in\cC_D(V)$.
-    \end{enumerate}
-  \end{corollary}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item For $H\subset D_1$ and $h,h'\in H$, the local shadows $\sh_D(h;H)$ and $\sh_D(h';H)$ are either disjoint or one is contained in the other.
-      \item For $V\subset D_2$ and $v,v'\in V$, the local shadows $\sh_D(v;V)$ and $\sh_D(v';V)$ are either disjoint or one is contained in the other.
-    \end{enumerate}
-  \end{lemma}
-
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $H$, by removing for each $d\in[1,a_1]$ the first (up to) $c$ vertical edges of depth $d$ immediately following $h_d$.
-      \item Define $\rsh_D(H)\subset\sh_D(H)$, the \emph{remote shadow} of $V$, by removing for each $\ell\in[0,a_2-1]$ the first (up to) $b$ horizontal edges of height $\ell$ immediately preceding $v_{\ell+1}$.
-    \end{enumerate}
-  \end{definition}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item For $H\subset D_1$, $V\in\cC_D(H)$ if and only if $V$ is disjoint from $\sh_D(H)\setminus\rsh_D(H)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in H$ and $v\in\rsh_D(H)$.
-      \item For $V\subset D_2$, $H\in\cC_D(V)$ if and only if $H$ is disjoint from $\sh_D(V)\setminus\rsh_D(V)$ and one of the conditions \eqref{eq:HGC} or \eqref{eq:VGC} is satisfied for each path $hv$ with $h\in\rsh_D(V)$ and $v\in V$.
-    \end{enumerate}
-  \end{lemma}
-
-  \begin{definition}
-    For $H\subset D_1$, write $\cC_D^{rsh}(H)$ for the subset of $V\in\cC_D(H)$ with $V\subset\rsh_D(H)$.
-    For $V\subset D_2$, write $\cC_D^{rsh}(V)$ for the subset of $H\in\cC_D(V)$ with $H\subset\rsh_D(V)$.
-  \end{definition}
-
-  \begin{definition}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $1 \le j < d \le a_1$ with $h_j\in H$, denote by $\rsh_D(H)_{j;d}$ the set of all $v\in\rsh_D(H)$ of depth $d$ such that $v\in\sh(h_j;H)$ and $h_j$ is the first horizontal edge before $v$ with this property.
-        Define the \emph{local remote shadow} of the edge $h_j$ by $\rsh_D(h_j;H):=\bigsqcup\limits_{d\in[j+1,a_1]} \rsh_D(H)_{j;d}$.
-      \item For $1 \le \ell <  k \le a_2$ with $v_k\in V$, denote by $\rsh_D(V)_{k;\ell}$ the set of all $h\in\rsh_D(V)$ of height $\ell$ such that $h\in\sh(v_k;V)$ and $v_k$ is the first vertical edge after $h$ with this property.
-        Define the \emph{local remote shadow} of the edge $v_k$ by $\rsh_D(v_k;V):=\bigsqcup\limits_{\ell\in[1,k-1]} \rsh_D(V)_{k;\ell}$.
-    \end{enumerate}
-  \end{definition}
-
-  As shown in \cite{lee-li-zelevinsky} for maximal Dyck paths, the remote shadow can be characterized as follows.
-  \begin{lemma}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item For $1 \le d < j \le a_1$, we have $\rsh_D(H)_{j;d} \ne \varnothing$ if and only if $f_H(h'h_d^{\!\uparrow}) < 0 < f_H(h_jh^{\!\uparrow})$ for every pair of consecutive horizontal edges $h<h'$ in the path $h_j h_d^{\!\uparrow}$.
-      \item For $1 \le \ell < k \le a_2$, we have $\rsh_D(V)_{k;\ell} \ne \varnothing$ if and only if $f_V({}^\leftarrow\!\!\!
-v_\ell v) < 0 < f_V({}^\leftarrow\!\!\!
-v' v_k)$ for every pair of consecutive vertical edges $v<v'$ in the path ${}^\leftarrow\!\!\!
-v_\ell v_k$.
-    \end{enumerate}
-  \end{lemma}
-
-  \begin{lemma}
-    Consider $H\sqcup V\subset D$ with $H\subset D_1$ and $V\subset D_2$.
-    \begin{enumerate}
-      \item Let $1 \le d < j \le a_1$ and suppose $\rsh_D(H)_{j;d} \ne \varnothing$, then
-        \[|\rsh_D(H)_{j;d}| = \min\limits_{h_j \le h < h' \le h_d} \min\big( -f_H(h'h_d^{\!\uparrow}) , f_H(h_jh^{\!\uparrow}) \big).\]
-      \item Let $1 \le \ell < k \le a_2$ and suppose $\rsh_D(V)_{k;\ell} \ne \varnothing$, then
-        \[|\rsh_D(V)_{k;\ell}| = \min\limits_{v_\ell \le v < v' \le v_k} \min\big( -f_V({}^\leftarrow\!\!\! v_\ell v) , f_V({}^\leftarrow\!\!\! v' v_k) \big).\]
-    \end{enumerate}
-  \end{lemma}
-
-  Then the following result immediately follows from Lemma~\ref{le:shadow statistic recursion}.
-  \begin{corollary}\mbox{}
-    \label{cor:remote shadows}
-    \begin{enumerate}
-      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
-        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
-        Then, for $1 \le d < j \le a_1$, we have $|\rsh_D(H)_{j;d}|=|\rsh_{D'}(V')_{d;j}|$.
-      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
-        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
-        Then, for $1 \le \ell < k \le a_2$, we have $|\rsh_D(V)_{k;\ell}|=|\rsh_{D''}(H'')_{\ell;k}$.
-    \end{enumerate}
-  \end{corollary}
-
-  In the results below, we keep the notation and assumptions from Corollary~\ref{cor:remote shadows}.
-  It follows that, for $H\subset D_1$ and $1 \le d < j \le a_1$, we may define an order-reversing bijection $\theta^H_{j;d} : \rsh_D(H)_{j;d} \to \rsh_{D'}(V')_{d;j}$.
-  Similarly, for $V\subset D_2$ and $1 \le \ell < k \le a_2$, we may define an order-reversing bijection $\theta^V_{k;\ell} : \rsh_D(V)_{k;\ell} \to \rsh_{D''}(H'')_{\ell;k}$.
-  \begin{definition}\mbox{}
-    \begin{enumerate}
-      \item For $H\subset D_1$ and $V \subset \rsh_D(H)$, define $\Omega_H(V) \subset \rsh_{D'}(V')$ by
-        \[\Omega_H(V)=\{\theta^H_{j;d}(v) : v \in \rsh_D(H)_{j;d}, 1 \le d < j \le a_1\}.\]
-      \item For $V\subset D_2$ and $H \subset \rsh_D(V)$, define $\Omega_V(H) \subset \rsh_{D''}(H'')$ by
-        \[\Omega_V(H)=\{\theta^V_{k;\ell}(h) : h \in \rsh_D(V)_{k;\ell}, 1 \le \ell < k \le a_2\}.\]
-    \end{enumerate}
-  \end{definition}
-
-  \begin{lemma}\mbox{}
-    \begin{enumerate}
-      \item Consider $H\subset D_1$ and $V \subset \rsh_D(H)$.
-        Suppose $h'=\theta^H_{j;d}(v)$ for $v\in V$.
-        Then $f_{\Omega_H(V)}(h'v'_d)=f_V(h_j v)$.
-      \item Consider $V\subset D_2$ and $H \subset \rsh_D(V)$.
-        Suppose $v''=\theta^V_{k;\ell}(h)$ for $h\in H$.
-        Then $f_{\Omega_V(H)}(h''_\ell v'')=f_V(h v_k)$.
-    \end{enumerate}
-  \end{lemma}
-
-  The following equivalence of compatibilities is the main result we need.
-  \begin{corollary}\mbox{}
-    \begin{enumerate}
-      \item For $H \subset D_1$ and $V \subset \rsh_D(H)$, we have $V\in\cC_D(H)$ if and only if $\Omega_H(V)\in\cC_{D'}(V')$.
-      \item For $V \subset D_2$ and $H \subset \rsh_D(V)$, we have $H\in\cC_D(V)$ if and only if $\Omega_V(H)\in\cC_{D''}(H'')$.
-    \end{enumerate}
-  \end{corollary}
-
-  We associate to $D$ the element $x_D\in\ZZ_{\ge0}[x_1^{\pm1},x_2^{\pm1}]$ defined as follows
-  \[x_D:=x_1^{-a_1} x_2^{-a_2} \sum_{H\sqcup V\in\cC_D} x_1^{b|V|} x_2^{c|H|}.\]
-
-  \begin{theorem}[\cite{lee-li-zelevinsky}]
-    For $(a_1,a_2)=(u_{m,+},u_{m-1,-})$ or $(u_{m-1,+},u_{m,-})$ for $m\ge1$, the element $x_{D^{max}[a_1,a_2]}$ is a non-initial cluster variable.
-    Otherwise, the element $x_{D^{max}_\WA[a_1,a_2]}$ is an element of the greedy basis
-  \end{theorem}
-
-  \begin{lemma}
-    Suppose there are two factorizations
-    \[x_D=x_1^{-a_1} x_2^{-a_2} \sum_{t=0}^{a_2}\sum_{k=0}^{a_1} \nu_{k,t} x_1^{bt}(1+x_2^c)^{a_1-k}=x_1^{-a_1} x_2^{-a_2} \sum_{s=0}^{a_1}\sum_{\ell=0}^{a_2} \theta_{s,\ell} x_2^{cs}(1+x_1^b)^{a_2-\ell},\]
-    where $\nu_{k,t}$ is the number of subsets $V\subseteq_t D_2$ with $|\sh_D(V)|=k$ and $\theta_{s,\ell}$ is the number of subsets $H\subseteq_s D_1$ with $|\sh_D(H)|=\ell$.
-    Then 
-    \[\sum_{k=0}^{a_1-s} {a_1-k\choose s} \nu_{k,t}=\sum_{\ell=0}^{a_2-t} {a_2-\ell\choose t} \theta_{s,\ell}\]
-    for all possible $s$ and $t$.
-  \end{lemma}
-  \begin{question}
-    How do such expressions behave under mutations?
-  \end{question}
-
-  \begin{lemma}
-    Choose $a_1,a_2\in\ZZ_{\ge0}$.
-    For $D^{st}:=D_1\sqcup D_2$ with $D_2=[1,a_2]$ and $D_1=[1,a_1]+a_2$, the element $x_{D^{st}}$ coincides with the corresponding standard monomial basis element.
-  \end{lemma}
-
-  \begin{definition}
-    Suppose $D^{dom}[a_1,a_2]$ decomposes as $\overrightarrow{D}^s \sqcup \overleftarrow{D}^t$.
-    Call a pair of subsets $H \sqcup V$ \emph{piecewise compatible} if the intersections with $\overrightarrow{D}^s$ and $\overleftarrow{D}^t$ are compatible on the subpaths.
-  \end{definition}
-
-  \begin{theorem}
-    Suppose $H \sqcup V$ is a piecewise compatible subset of $D^{dom}[a_1,a_2]$.
-    \begin{itemize}
-      \item If the last vertical edge of $\overrightarrow{D}^s$ is contained in $V$, then $H \sqcup V$ is compatible.
-      \item If the first horizontal edge of $\overleftarrow{D}^t$ is contained in $H$, then $H \sqcup V$ is compatible.
-    \end{itemize}
-  \end{theorem}
-
-\end{document}

### 2022-05-20 dominance_regions.tex
Started reading through

@@
 
-  Over time several bases for cluster algebras have been constructed in a variety of generalities \cite{BZ14,CI12,DT13,Dup11,Dup12,GHKK18,LLZ14,MSW13,Pla13,SZ04,T14}.
-  All of them share a property of being ``pointed''.
-  Being pointed turned out to be a desirable feature for a basis to have and a natural question is to find all bases enjoying this property.
+  Over time several bases for cluster algebras have been described in different generalities \cite{BZ14,CI12,DT13,Dup11,Dup12,GHKK18,LLZ14,MSW13,Pla13,SZ04,T14}.
+  All of their elements share the property of being ``pointed''; this turned out to be a desirable feature for a basis to have and a natural question is to find all bases enjoying this property.
   Recently Qin studied the deformability of pointed bases whenever the cluster algebra has full rank \cite{Qin19}. 
@@
 when clusters contain a pair of mutable cluster variables.
-  In this setting, frozen variables do not carry any additional information and we can work in the coefficient-free case.
-
-  Fix integers $b,c>0$.  The cluster algebra $\cA(b,c)$ is the $\ZZ$-subalgebra of $\QQ(x_0,x_1)$ generated by \emph{cluster variables} $x_m$, $m\in\ZZ$, defined recursively by
+  In this setting, frozen variables do not carry any additional information so we will work in the coefficient-free case.
+
+  Fix integers $b,c>0$.
+  The cluster algebra $\cA(b,c)$ is the $\ZZ$-subalgebra of $\QQ(x_0,x_1)$ generated by the \emph{cluster variables} $x_m$, $m\in\ZZ$, defined recursively by
   \begin{equation}
@@
 
-  Our goal in this note is to explicitly compute the possible bases which are pointed with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
-  That is, a basis element with \emph{$\bfg$-vector} $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ when expanded in terms of $\{x_0,x_1\}$ can be written in the form
+  An element of $\cA(a,b)$ has \emph{$\bfg$-vector} $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$, with respect to the embedding ${\cA(b,c)\into\ZZ[x_0^{\pm1},x_{1}^{\pm1}]}$, if it can be written in the form
   \begin{equation}
@@
   with $\rho_{0,0}=1$.
-  Being \emph{pointed} means an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
-  %The collection of all $\bfg$-vectors $\lambda\in\ZZ^2$ parametrize the elements of any pointed basis.
+  An element of $\cA(a,b)$ is \emph{pointed} if an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$; a basis is pointed if it consists entirely of pointed elements.
 
   Important examples of pointed elements are the \emph{cluster monomials} of $\cA(b,c)$, i.e.
-the elements that can be written in the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $\alpha_k,\alpha_{k+1}$ non-negative integers.
-  Indeed, by \cite[Lemma 3.4.12]{Qin19} cluster monomials are part of any pointed basis in any cluster algebra.
+the elements of the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $\alpha_k,\alpha_{k+1}$ non-negative integers.
+  Indeed, by \cite[Lemma 3.4.12]{Qin19} cluster monomials are part of any pointed basis in any cluster algebra of full rank.
   We achieve the same conclusion in our setting by elementary calculations (cf. Lemma~\ref{le:cluster monomials}).
@@
     \cite[Theorem 1.2.1]{Qin19}
-    Let $x=\{x_\lambda\}$ and $y=\{y_\lambda\}$ be pointed bases of $\cA(b,c)$.
+    Let $\{x_\lambda\}$ and $\{y_\lambda\}$ be pointed bases of $\cA(b,c)$.
     Then for each $\lambda\in\ZZ^2$, there exist scalars $q_{\lambda,\mu}$ for $\mu\prec\lambda$ such that
     \[y_\lambda=x_\lambda+\sum_{\mu\prec\lambda} q_{\lambda,\mu} x_\mu.\]
-    Moreover, any choice of scalars $q_{\lambda,\mu}$, for $\mu\prec\lambda$, $\lambda\in\ZZ^2$, as above provides a basis of $\cA(b,c)$.
+    Moreover, having fixed a reference pointed basis $\{x_\lambda\}$, any choice of scalars $q_{\lambda,\mu}$ as above provides a pointed basis of $\cA(b,c)$.
   \end{theorem}
@@
     \label{th:dominance inequalities}
-    The dominance region $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the polygon consisting of those $\mu=(\mu_0,\mu_1)\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
+    The dominance region $\cP_\lambda$ of the $\bfg$-vector $\lambda=(\lambda_0,\lambda_1)$ is the polygon consisting of those $\mu=(\mu_0,\mu_1)\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
     {
@@
 
+  \saySS{HERE}
   Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.

### 2022-05-21 dominance_regions.tex
Sync

@@
 
-  \saySS{HERE}
   Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  Lattice points outside of $\cI$ are precisely the $\bfg$-vectors of cluster monomials in $\cA(a,b)$.
   \begin{corollary}
@@
     \begin{enumerate}
-      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP_\lambda$ is the point $\lambda$. 
+      \item If $\lambda$ lies outside of $\cI$, then $\cP_\lambda$ is the point $\lambda$. 
       \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP_\lambda$ is the trapezoid with  vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.

### 2022-05-21 dominance_regions.tex
Edits together

@@
 %\usepackage{ulem}
-\usepackage[margin=1in]{geometry}
+\usepackage[margin=1in,showframe]{geometry}
 \usepackage{tikz}
@@
   \begin{abstract}
-    We investigate the shapes of the polytopes defining the dominance order for $\bfg$-vectors in cluster algebras of rank two.
-    We arrive at a complete description: 
-    \begin{itemize}
-      \item cluster monomials are never deformable;
-      \item the imaginary dominance polytopes are kites, triangles, or trapezoids which extend far outside the imaginary cone; the triangles appearing along rays corresponding to columns of the associated Cartan matrix.
-    \end{itemize}
+    We study the polygons defining the dominance order on $\bfg$-vectors in cluster algebras of rank 2.
+%    We investigate the shapes of the polytopes defining the dominance order for $\bfg$-vectors in cluster algebras of rank two.
+%    We arrive at a complete description: 
+%    \begin{itemize}
+%      \item cluster monomials are never deformable;
+%      \item the imaginary dominance polytopes are kites, triangles, or trapezoids which extend far outside the imaginary cone; the triangles appearing along rays corresponding to columns of the associated Cartan matrix.
+%    \end{itemize}
   \end{abstract}
@@
 
-  An element of $\cA(a,b)$ has \emph{$\bfg$-vector} $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$, with respect to the embedding ${\cA(b,c)\into\ZZ[x_0^{\pm1},x_{1}^{\pm1}]}$, if it can be written in the form
+  An element of $\cA(b,c)$ has \emph{$\bfg$-vector} $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$, with respect to the embedding ${\cA(b,c)\into\ZZ[x_0^{\pm1},x_{1}^{\pm1}]}$, if it can be written in the form
   \begin{equation}
@@
   with $\rho_{0,0}=1$.
-  An element of $\cA(a,b)$ is \emph{pointed} if an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$; a basis is pointed if it consists entirely of pointed elements.
-
-  Important examples of pointed elements are the \emph{cluster monomials} of $\cA(b,c)$, i.e.
-the elements of the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $\alpha_k,\alpha_{k+1}$ non-negative integers.
-  Indeed, by \cite[Lemma 3.4.12]{Qin19} cluster monomials are part of any pointed basis in any cluster algebra of full rank.
+  An element of $\cA(b,c)$ is \emph{pointed} if an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$; a basis is pointed if it consists entirely of pointed elements.
+
+  Important examples of pointed elements are the \emph{cluster monomials} of $\cA(b,c)$, i.e.~the elements of the form $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$ for some $k\in\ZZ$ and $\alpha_k,\alpha_{k+1}$ non-negative integers.
+  Indeed, by \cite[Lemma 3.4.12]{Qin19} cluster monomials are part of any pointed basis in any (upper) cluster algebra of full rank.
   We achieve the same conclusion in our setting by elementary calculations (cf. Lemma~\ref{le:cluster monomials}).
@@
   When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
-  We will therefore assume that $bc\ge4$.
+  We therefore assume that $bc\ge4$.
   In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
@@
       \everymath={\displaystyle}
-      \def\arraystretch{2.8}
+      \def\arraystretch{2.2}
       \[
         \begin{array}{rcccl}
-          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \leq & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
+          0 & \!\leq\! & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \!\leq\! & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)\!\!;
           \\
-          \min\left(-c\lambda_0,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & 0
+          \min\left(-c\lambda_0,0\right) & \!\leq\! & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \!\leq\! & 0;
           \\
-          0 & \leq &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
+          0 & \!\leq\! &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \!\leq\! & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)\!\!;
           \\
-          \min\left(b \lambda_1,0\right) & \leq & (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \leq & 0
+          \min\left(b \lambda_1,0\right) & \!\leq\! & (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \!\leq\! & 0.
         \end{array}
@@
   \end{theorem}
-
+  \vspace{-0.713em}
   Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  Lattice points outside of $\cI$ are precisely the $\bfg$-vectors of cluster monomials in $\cA(a,b)$.
+  Lattice points outside of $\cI$ are precisely the $\bfg$-vectors of cluster monomials in $\cA(b,c)$.
   \begin{corollary}
@@
       \item If $\lambda$ lies outside of $\cI$, then $\cP_\lambda$ is the point $\lambda$. 
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP_\lambda$ is the trapezoid with  vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP_\lambda$ is the triangle with  vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP_\lambda$ is the kite with  vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
-      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP_\lambda$ is the triangle with  vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
-      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP_\lambda$ is the trapezoid with  vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
+      \item If $\lambda$ lies in the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP_\lambda$ is the trapezoid with  vertices $\lambda$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, and ${\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)}$.
+      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, then $\cP_\lambda$ is the triangle with vertices $\lambda$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$.
+      \item If $\lambda$ lies in the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP_\lambda$ is the kite with  vertices $\lambda$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$.
+      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, then $\cP_\lambda$ is the triangle with vertices $\lambda$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$.
+      \item If $\lambda$ lies in the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP_\lambda$ is the trapezoid with vertices $\lambda$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$.
     \end{enumerate}
@@
   \begin{remark}
-    Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
+    Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix. % $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
     This unexpected coincidence is one of our reasons for deciding to write down these results.
@@
 greedy basis) are the ratios of Schur functions $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ (resp.
-ratios of elementary symmetric functions $\frac{e_{r,n-r}}{e_n}$) evaluated at $\bfa^{(n)}$.
+ratios of elementary symmetric functions $\frac{e_{n-r,r}}{e_n}$) evaluated at $\bfa^{(n)}$.
     We leave the details to the reader.

### 2022-05-23 dominance_regions.tex
Today's conversation

@@
     }
-  \begin{tikzpicture}[scale=.5]
+  \begin{tikzpicture}[scale=.3743]
       \setconstants;
@@
       };
-      \draw (-3.5,-3.5) node{$\cS_\lambda$};
+      \draw (-3.5,-3.7) node{$\cS_\lambda$};
       \draw [darkgreen](2.5,1) node{$\cP_\lambda$};
@@
 
+  \vspace{-1.05em}
   \end{theorem}
-  \vspace{-0.713em}
+  %\vspace{-0.713em}
+  \begin{remark}
+  %Interestingly, explicit calculations reveal that the $\bfg$-vectors actually appearing in the transitions between notable bases are far smaller than the entire dominance polygon.
+    Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coeffiecients $q_{\lambda,\mu}$ are zero.
+    Understanding this phenomenon might be worth further study.
+  \end{remark}
+
   Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
@@
   \end{remark}
-
-  A number of bases for rank two cluster algebras with various defining properties have been constructed.
-  A natural starting basis is the so-called \emph{greedy basis} in which all $\rho_{\alpha_0,\alpha_1}$ are non-negative and these coefficients are chosen to be minimal.
-  It is known that this choice coincides with the theta basis \cite{CGMMRSW17,GHKK18}.
-  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications of $\cA(b,c)$ with the subalgebras of $\ZZ[x_0^{\pm1},x_1^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
-  However, these bases are not mutation invariant.
-  The \emph{triangular basis} is defined by a triangular transition from the standard monomial basis.
-  The \emph{generic basis} is defined from the categorification of $\cA(b,c)$ using generic representations of an associated quiver.
-  It would be useful to explicitly (or combinatorially) compute the transitions between these known bases.
-  Interestingly, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.
 

### 2022-05-24 dominance_regions.tex
Lost connection

@@
     Note that the rays which separate the regions inside $\cI$ correspond exactly to the columns of the associated Cartan matrix. % $\left[ \begin{array}{cc} 2 & -b \\ -c & 2 \end{array} \right]$.
-    This unexpected coincidence is one of our reasons for deciding to write down these results.
+    Moreover the expression for the dominance regions along those rays coincide.
+    These unexpected coincidences are one of our reasons for deciding to write down these results.
   \end{remark}
@@
   Given a Laurent polynomial in $\ZZ[x_0^{\pm1},x_1^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
-  Given a $\bfg$-vector $\lambda$, in the next result we identify a polygon $\cS_\lambda$ whose lattice points are the maximum possible support of a pointed basis element $x_\lambda$. 
+  Given a $\bfg$-vector $\lambda$, in the next result we identify a polygon $\cS_\lambda$ whose lattice points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$ for~$\alpha_0,\alpha_1\in\ZZ$ give the maximum possible support of a pointed basis element $x_\lambda$.
   \begin{theorem}
@@
     \begin{enumerate}
-      \item If $\lambda$ lies outside of $\cI$, then the support of $x_\lambda$ is precisely the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cS_\lambda$ given as follows:
+      \item If $\lambda$ lies outside of $\cI$, then the support of $x_\lambda$ is precisely the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside the region $\cS_\lambda$ given as follows:
         \begin{enumerate}
@@
       \fill (\x,\y) circle (5pt);
+%      \fill[white] (\xmax-2,\ymax-1.5) rectangle (\xmax-1, \ymax-0.5);
+      \draw (\xmax-1.5,\ymax-1) node{(1.a)};
     \end{scope}
@@
       \draw [thick, fill=white] ({\x+\b * \y},\y) circle (5pt);
+      \draw (\xmax-1.5,\ymax-1) node{(1.b)};
     \end{scope}
@@
       \draw [thick, fill=white] (\x,{\y - \c * \x}) circle (5pt);
+      \draw (\xmax-1.5,\ymax-1) node{(1.c)};
     \end{scope}
@@
       \draw [thick, fill=white] ({\x + \b * \y}, {\y -\c*(\x + \b * \y)})  circle (5pt);
+      \draw (\xmax-1.5,\ymax-1) node{(1.d)};
     \end{scope}
@@
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
+      \draw (\xmax-1.5,\ymax-1) node{(1.e)};
     \end{scope}
@@
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
+      \draw (\xmax-1.5,\ymax-1) node{(1.f)};
     \end{scope}
@@
       \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
+      \draw (\xmax-1.5,\ymax-1) node{(2)};
     \end{scope}

### 2022-05-27 dominance_regions.tex
Boundaries
Partial edits

@@
 %      \fill[white] (\xmax-2,\ymax-1.5) rectangle (\xmax-1, \ymax-0.5);
-      \draw (\xmax-1.5,\ymax-1) node{(1.a)};
+      \draw (\xmin+1.5,\ymin+1) node{(1.a)};
     \end{scope}
-    \begin{scope}[shift={(13,0)}]
+    \begin{scope}[shift={(14,0)}]
       \setconstants;
@@
       \draw [thick, fill=white] ({\x+\b * \y},\y) circle (5pt);
-      \draw (\xmax-1.5,\ymax-1) node{(1.b)};
+      \draw (\xmin+1.5,\ymin+1) node{(1.b)};
     \end{scope}
-    \begin{scope}[shift={(26,0)}]
+    \begin{scope}[shift={(28,0)}]
       \setconstants;
@@
       \draw [thick, fill=white] (\x,{\y - \c * \x}) circle (5pt);
-      \draw (\xmax-1.5,\ymax-1) node{(1.c)};
+      \draw (\xmin+1.5,\ymin+1) node{(1.c)};
     \end{scope}
-    \begin{scope}[shift={(39, 0)}]
+    \begin{scope}[shift={(42, 0)}]
       \setconstants;
@@
       \draw [thick, fill=white] ({\x + \b * \y}, {\y -\c*(\x + \b * \y)})  circle (5pt);
-      \draw (\xmax-1.5,\ymax-1) node{(1.d)};
+      \draw (\xmin+1.5,\ymin+1) node{(1.d)};
     \end{scope}
-    \begin{scope}[shift={(0,-13)}]
+    \begin{scope}[shift={(0,-14)}]
       \setconstants;
@@
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
-      \draw (\xmax-1.5,\ymax-1) node{(1.e)};
+      \draw (\xmin+1.5,\ymin+1) node{(1.e)};
     \end{scope}
-    \begin{scope}[shift={(13,-13)}]
+    \begin{scope}[shift={(14,-14)}]
       \setconstants;
@@
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
-      \draw (\xmax-1.5,\ymax-1) node{(1.f)};
+      \draw (\xmin+1.5,\ymin+1) node{(1.f)};
     \end{scope}
-    \begin{scope}[shift={(26,-13)}]
+    \begin{scope}[shift={(28,-14)}]
       \setconstants;
@@
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
-      \draw (\xmax-1.5,\ymax-1) node{(1.f)};
+      \draw (\xmin+1.5,\ymin+1) node{(1.f)};
     \end{scope}
-    \begin{scope}[shift={(39,-13)}]
+    \begin{scope}[shift={(42,-14)}]
       \setconstants;
@@
       \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
-      \draw (\xmax-1.5,\ymax-1) node{(2)};
+      \draw (\xmin+1.5,\ymin+1) node{(2)};
     \end{scope}
+    %\draw[black,very thick] (-6.5,6.5) -- (45.5,6.5) -- (45.5,-19.5) -- (-6.5,-19.5) -- cycle;
+    %\draw[black,very thick] (-6.5,-6.5) -- (45.5,-6.5);
+    %\draw[black,very thick] (6.5,6.5) -- (6.5,-19.5);
+    %\draw[black,very thick] (19.5,6.5) -- (19.5,-19.5);
+    %\draw[black,very thick] (32.5,6.5) -- (32.5,-19.5);
+    \draw (21,-22) node{The maximal supports $\cS_\lambda$ as described in Theorem \ref{th:maximum support}.};
   \end{tikzpicture}
 \end{figure}
-
-\begin{remark}
-  This result reveals the maximal support possible for a pointed basis which remains pointed under all possible mutations.
-  In particular, any candidate basis could be ruled out using these results based upon their support alone.
-\end{remark}
 
@@
 Section~\ref{sec:maximum support} proves Theorem~\ref{th:maximum support}.
-The paper ends with Section~\ref{sec:affine} interpreting the dominance polygon in terms of generalized minors in the cases where $b=c=2$.
+The paper ends with Section~\ref{sec:affine} interpreting the dominance polygons in terms of generalized minors in the cases where $b=c=2$.
 
@@
   \label{sec:chebyshev}
-  Define \emph{two-parameter Chebyshev polynomials} $u_i^\varepsilon$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
-  \[u_0^\varepsilon=0,\quad u_1^\varepsilon=1,\quad u_{i+1}^\varepsilon=\begin{cases} bu_i^- -u_{i-1}^+ & \text{if $\varepsilon=+$;}\\ cu_i^+-u_{i-1}^- & \text{if $\varepsilon=-$.} \end{cases}\]
+  Define \emph{two-parameter Chebyshev polynomials} $u_i^\varepsilon$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by $u_0^\varepsilon=0$, $u_1^\varepsilon=1$, and
+  \[u_{i+1}^\varepsilon=\begin{cases} bu_i^- -u_{i-1}^+ & \text{if $\varepsilon=+$;}\\ cu_i^+-u_{i-1}^- & \text{if $\varepsilon=-$.} \end{cases}\]
     Observe that, by an easy induction, $u_{-i}^\varepsilon=-u_i^\varepsilon$.
 
-  The recursion can be written more succinctly as $u_{i+1}^\varepsilon=u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon$ with the additional initial condition $u_2^\varepsilon=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
-  This leads to the following more general recursive structure.
+  %The recursion can be written more succinctly as $u_{i+1}^\varepsilon=u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon$ with the additional initial condition $u_2^\varepsilon=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
+  %This leads to the following more general recursive structure.
   \begin{lemma}

### 2022-05-27 dominance_regions.tex
Lemma 2.1
Remark 2.2

@@
     We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
-    Using the claim for $\ell>0$ and then the defining recursion twice, we get
-    \begin{align*}
-      u_{i+\ell+1}^\varepsilon
-      &=
+    Using the claim for $\ell>0$ and then the defining recursion twice, $u_{i+\ell+1}^\varepsilon$ can be rewritten as
+    \[
       u_{\ell+1}^\varepsilon u_{i+1}^{-\varepsilon}-u_\ell^{-\varepsilon} u_i^\varepsilon
+      =u_{\ell+1}^\varepsilon(u_2^{-\varepsilon}u_i^\varepsilon-u_{i-1}^{-\varepsilon}) -u_\ell^{-\varepsilon} u_i^\varepsilon 
       =(u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
       =u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
-      \qquad \text{if $\ell$ is odd;}\\ 
-      u_{i+\ell+1}^\varepsilon
-      &=
+    \]
+    for $\ell$ odd and as
+    \[
       u_{\ell+1}^{-\varepsilon} u_{i+1}^\varepsilon-u_\ell^\varepsilon u_i^{-\varepsilon}
+      =u_{\ell+1}^{-\varepsilon}(u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon) -u_\ell^\varepsilon u_i^{-\varepsilon}
       =(u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon
       =u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon
-      \qquad \text{if $\ell$ is even;} 
-    \end{align*}
-    which gives the claimed recursion for $\ell+1$.
+    \]
+    for $\ell$ even.
+    This gives the claimed recursion for $\ell+1$.
     These calculations can be reversed to show the result for $\ell<0$.
@@
     Note that $u_{2j+1}^+=u_{2j+1}^-$ for all $j\in\ZZ$.
-    Moreover, since $u_{-i}^\varepsilon=-u_i^\varepsilon$, these formulas can also easily be seen to hold for $i<0$.
   \end{remark}

### 2022-05-27 dominance_regions.tex
Lemma 2.1

@@
   \begin{proof}
-    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion, respectively.
+    We work by induction on $\ell$ for all $i$ simultaneously, the cases $\ell=0,1$ being tautological and reproducing the defining recursions, respectively.
     Using the claim for $\ell>0$ and then the defining recursion twice, $u_{i+\ell+1}^\varepsilon$ can be rewritten as

### 2022-05-27 dominance_regions.tex
Remark 2.1

@@
   \[u_{i+1}^\varepsilon=\begin{cases} bu_i^- -u_{i-1}^+ & \text{if $\varepsilon=+$;}\\ cu_i^+-u_{i-1}^- & \text{if $\varepsilon=-$.} \end{cases}\]
-    Observe that, by an easy induction, $u_{-i}^\varepsilon=-u_i^\varepsilon$.
+  \begin{remark}
+    Observe that, by easy inductions, we have $u_{-i}^\varepsilon=-u_i^\varepsilon$ for $i\in\ZZ$ and $u_{2j+1}^+=u_{2j+1}^-$ for $j\in\ZZ$.
+  \end{remark}
 
@@
   \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
-  \begin{remark}
-    Note that $u_{2j+1}^+=u_{2j+1}^-$ for all $j\in\ZZ$.
-  \end{remark}
 

### 2022-05-27 dominance_regions.tex
Lemma 2.2

@@
     We work by induction on $\ell$ for all $i$ simultaneously, the cases $\ell=0,1$ being tautological and reproducing the defining recursions, respectively.
-    Using the claim for $\ell>0$ and then the defining recursion twice, $u_{i+\ell+1}^\varepsilon$ can be rewritten as
+    Using the claim for $\ell>0$ and then the defining recursion twice, $u_{i+\ell+1}^\varepsilon$ can be rewritten for $\ell$ odd as
     \[
@@
     \]
-    for $\ell$ odd and as
+    and for $\ell$ even as
     \[
@@
       =(u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon
-      =u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon
-    \]
-    for $\ell$ even.
+      =u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon.
+    \]
     This gives the claimed recursion for $\ell+1$.

### 2022-05-28 dominance_regions.tex
Some section 2 edits

@@
   \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
-  By the equalities 
-  \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
-  it follows that $u_i^\varepsilon$ can be computed explicitly as
+  An induction on $i$ shows  
+  \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd.} \end{cases}\]
+  It follows that $u_i^\varepsilon$ can be computed explicitly as
   \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]

### 2022-05-28 dominance_regions.tex
done with l=polynomials

@@
 
-  The standard Chebyshev polynomials (normalized, of the second kind) are defined by the recursion $u_0=0$, $u_1=1$, $u_{i+1}=ru_i-u_{i-1}$, which can be computed explicitly as
-  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
-  An induction on $i$ shows  
-  \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd.} \end{cases}\]
-  It follows that $u_i^\varepsilon$ can be computed explicitly as
-  \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
-
   \begin{lemma}
@@
     \[\lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+}=\frac{bc-\sqrt{bc(bc-4)}}{2b}=\lim_{i\to-\infty} \frac{u_i^-}{u_{i-1}^+}.\]
-    Moreover, each of these sequences is monotonic.
+    Moreover, the limits in the first line converge monotonically from above and the limits in the second line converge monotonically from below.
   \end{lemma}
   \begin{remark}
-    The analogous limits with $+$ and $-$ reversed are obtained from these by interchanging the roles of $b$ and $c$.
+    The analogous limits with $\varepsilon=+$ and $\varepsilon=-$ reversed are obtained from these by interchanging the roles of $b$ and $c$.
   \end{remark}
   \begin{proof}
+    We first compute the limits for arbitrary positive real numbers $b$ and $c$ with $bc>4$; the remaining case will then follow by taking the limit as $bc$ approaches $4$.
+
+  The standard Chebyshev polynomials (normalized, of the second kind) are defined by the recursion $u_0=0$, $u_1=1$, $u_{i+1}=ru_i-u_{i-1}$, which can be computed explicitly as
+  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
+  An induction on $i$ shows that 
+  \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd.} \end{cases}\]
+  It follows that $u_i^\varepsilon$ can be computed explicitly as
+  \[u_i^\varepsilon=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]
+
     For any $i\ne1$, we have
@@
     For the final claim, observe that $\frac{u_{i+1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i-1}^\varepsilon}$ and $\frac{u_{i-1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i+1}^\varepsilon}$ are both equivalent to $u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon<u_i^{-\varepsilon}u_i^\varepsilon$.
-    This is immediate from the following induction:
-    \begin{align*}
-      u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon
-      =(cu_i^\varepsilon-u_{i-1}^{-\varepsilon})u_{i-1}^\varepsilon
-      =cu_i^\varepsilon u_{i-1}^\varepsilon-u_{i-1}^{-\varepsilon} u_{i-1}^\varepsilon
-      <cu_i^\varepsilon u_{i-1}^\varepsilon-u_i^\varepsilon u_{i-2}^{-\varepsilon}
-      =u_i^\varepsilon(cu_{i-1}^\varepsilon-u_{i-2}^{-\varepsilon})
-      =u_i^\varepsilon u_i^{-\varepsilon}.
-    \end{align*}
+    This inequality is then immediate, for $i>0$, from the following inductions:
+    \begin{align*}
+      u_{i+1}^{-}u_{i-1}^+
+      =(cu_i^+-u_{i-1}^{-})u_{i-1}^+
+      =cu_i^+ u_{i-1}^+-u_{i-1}^{-} u_{i-1}^+
+      <cu_i^+ u_{i-1}^+-u_i^+ u_{i-2}^{-}
+      =u_i^+(cu_{i-1}^+-u_{i-2}^{-})
+      =u_i^+ u_i^{-};
+      \\
+      u_{i+1}^{+}u_{i-1}^-
+      =(bu_i^--u_{i-1}^{+})u_{i-1}^-
+      =bu_i^- u_{i-1}^--u_{i-1}^{+} u_{i-1}^-
+      <bu_i^- u_{i-1}^--u_i^- u_{i-2}^{+}
+      =u_i^-(bu_{i-1}^--u_{i-2}^{+})
+      =u_i^- u_i^{+}.
+    \end{align*}
+    Again the case $i<0$ then follows from $u_{-i}^\varepsilon=-u_i^\varepsilon$.
   \end{proof}
@@
       (-\lambda_0+b\lambda_1, -\lambda_1) & \text{if $\lambda_0<0$ and $\lambda_1\ge 0$;}\\
-      (-\lambda_0,-\lambda_1) & \text{if $\lambda_0<0$ and $\lambda_1<0$;}
+      (-\lambda_0,-\lambda_1) & \text{if $\lambda_0<0$ and $\lambda_1<0$.}
     \end{cases}

### 2022-05-29 dominance_regions.tex
Added some references at the start of section 3, the statement probably needs work though.
Going to sleep

@@
   The cluster algebra $\cA(b,c)$ is the $\ZZ$-subalgebra of $\QQ(x_0,x_1)$ generated by the \emph{cluster variables} $x_m$, $m\in\ZZ$, defined recursively by
-  \begin{equation}
+  \[
     x_{m-1}x_{m+1}=\begin{cases} x_m^b+1 & \text{if $m$ is even;}\\ x_m^c+1 & \text{if $m$ is odd.} \end{cases}
-  \end{equation}
+  \]
   By the Laurent Phenomenon \cite{FZ02}, each $x_m$ is actually an element of $\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for any $k\in\ZZ$.
@@
   \begin{proof}
-    We first compute the limits for arbitrary positive real numbers $b$ and $c$ with $bc>4$; the remaining case will then follow by taking the limit as $bc$ approaches $4$.
+    When $bc=4$ it is easy to compute closed formulas for $u_i^\varepsilon$ and the claimed limits follow; we thus concentrate on the case $bc>4$.
 
@@
 
-  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors when expanding a pointed expression of the form~\eqref{eq:pointed} in terms of a cluster $\{x_k,x_{k+1}\}$.
+  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors when expanding an expression of the form~\eqref{eq:pointed} in terms of a cluster $\{x_k,x_{k+1}\}$.
+  This adapts the notation from \cite[Definition 2.1.4]{Qin19} to our setting, see also \cite[Definition 4.1]{Rea14}.
+
   Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1}:\RR^2\to\RR^2$ as follows:
@@
   \]
-  These determine the dominance region as follows.
+  These determine the dominance region as we paraphrase from \cite[Section 3.1]{Qin19}.
   \begin{definition}
     \label{def:dominance}
-    For $\lambda\in\ZZ^2$ and $k\in\ZZ$, define cones 
+    For $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ and $k\in\ZZ$, define cones 
     \[\cC_k(\lambda)
@@
 
-  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $n>0$, there exists a scalar $\nu_n$ so that $\phi^n(\lambda)=\nu_n\lambda$.
+  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $n>0$, there exists a positive scalar $\nu$ so that $\phi(\lambda)=\nu\lambda$.
   \begin{lemma}
@@
   \begin{proof}
-    First observe that the equation $\phi_2^n(\lambda)=\nu_n\lambda$ cannot be satisfied for all $n>0$ unless $\lambda_0\ge 0$ and $c\lambda_0+\lambda_1\ge 0$.
-    In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
+    First observe that, by equation \eqref{eq:forward two step mutation}, the equation $\phi_2(\lambda)=\nu\lambda$ cannot be satisfied with a positive $\nu$ unless $\lambda_0\ge 0$ and $c\lambda_0+\lambda_1\ge 0$.
+    In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e.~$\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
     We thus require 
@@
   %\end{proof}
+  Observe that the imaginary cone $\cI$ is spanned by the eigenvectors of $\phi_{2}$ and that $\phi_{2}$ is linear in $\cI$.
   \begin{lemma}
@@
   \begin{proof}
-    Since $\phi_{2j}=\phi_2^j$, the result follows from the cases $j=1$.
-    But this is immediate for $\phi_2$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_2$ is linear in $\cI$.
+    Since $\phi_{2j}=\phi_2^j$, the result follows from the case $j=1$ which is immediate.
   \end{proof}
@@
     \begin{align*}
-      \phi_{2j}(\lambda)&=(u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1,-u_{2j}^-\lambda_0-u_{2j-1}^-\lambda_1);\\
-      \phi_{2j+1}(\lambda)&=(-u_{2j+1}^+\lambda_0-u_{2j}^+\lambda_1,u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1).
+      \phi_{2j}(\lambda)&=(u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,-u_{2j}^-\lambda_0-u_{2j-1}^+\lambda_1);\\
+      \phi_{2j+1}(\lambda)&=(-u_{2j+1}^-\lambda_0-u_{2j}^+\lambda_1,u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1).
     \end{align*}

### 2022-05-30 dominance_regions.tex
Lemma 3.4 and section 4 edits

@@
   \begin{remark}
+    \label{rem:equivalences}
     Observe that, by easy inductions, we have $u_{-i}^\varepsilon=-u_i^\varepsilon$ for $i\in\ZZ$ and $u_{2j+1}^+=u_{2j+1}^-$ for $j\in\ZZ$.
@@
     \[\phi_2(\lambda)=(u_3^-\lambda_0+u_2^+\lambda_1,-u_2^-\lambda_0-u_1^+\lambda_1).\]
-    Therefore
+    Therefore, after applying the equivalences for odd Chebyshev polynomials from Remark~\ref{rem:equivalences}, we have
     \begin{align*}
@@
     \end{align*}
-    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
+    where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
+    By Remark~\ref{rem:equivalences}, this is equivalent to the desired expression.
 
@@
     For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger)\ \mu_0 \le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 = u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^-\lambda_1 = u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1.
-\]
+    \[ (\dagger)\ \mu_0 \le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1. \]
     We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
@@
     For $k=2j+1$, $j\ge0$, and $\lambda\in\cI$, we get $\cC_{2j+1}(\phi_{2j+1}\lambda)\subset\RR^2$ is given by the inequalities 
-    \[ (\dagger')\ -\mu_0\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^-\lambda_1.\]
+    \[ (\dagger')\ -\mu_0\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.\]
     Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
     From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
-    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $\mu_0\le u_{2j+1}^+\lambda_0+u_{2j}^+\lambda_1$.
+    Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $\mu_0\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1$.
     The boundary ray corresponding to ($\ddagger'$) intersects both domains of linearity for $\phi_1^{-1}$ and thus produces the inequalities
-    \[ c\mu_0+\mu_1\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad \mu_1\le u_{2j+2}^+\lambda_0+u_{2j+1}^+\lambda_1.\]
+    \[ c\mu_0+\mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1 \qquad\text{and}\qquad \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.\]
 

### 2022-05-30 dominance_regions.tex
Lemma 3.4

@@
     We work by induction on $j$, the case $j=0$ being clear from the definitions.
-    For $\lambda\in\cI$, the action of $\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
+    For $\lambda\in\cI$, the action of~$\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
     \[\phi_2(\lambda)=(u_3^-\lambda_0+u_2^+\lambda_1,-u_2^-\lambda_0-u_1^+\lambda_1).\]
@@
     where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
-    By Remark~\ref{rem:equivalences}, this is equivalent to the desired expression.
+    Using Remark~\ref{rem:equivalences} again, this is equivalent to the desired expression.
 

### 2022-05-30 dominance_regions.tex
Adjustment to proof of Lemma 4.1

@@
   \begin{proof}
-    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$.
+    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_{k+1}^{\alpha_{k+1}}x_{k+2}^{\alpha_{k+2}}$.
     In this case, the intersection
@@
     In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
-    Next, again for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$.
-    In particular, the intersection of $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ with the cone containing $\lambda$ is a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\lambda$.
+    Next, again for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at the origin and $\phi_{k+1}\lambda$.
+    In particular, the intersection of $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ with the cone containing $\lambda$ is a (possibly degenerate) convex quadrilateral with corners at the origin and $\lambda$.
     Combining these observations proves the result for $k$ odd, the case of even $k$ is similar.

### 2022-06-06 dominance_regions.tex
I'm dumb, we adjusted our initial cluster exactly for this reason (changed it back in Lemma 4.1)
Done up to section 5

@@
   \begin{proof}
-    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_{k+1}^{\alpha_{k+1}}x_{k+2}^{\alpha_{k+2}}$.
+    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$.
     In this case, the intersection
@@
   \end{itemize}
-  This proves Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.
-
-  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP_\lambda$ for $\lambda\in\cI$.
+  Since $\lambda$ satisfies all the inequalities, these observations prove Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.
+
+  Next we aim to understand how inequalities transform under the action of a piecewise-linear map.
+  The following well known fact about linear maps will suffice.
 
@@
     Let $A$ be an invertible $2\times 2$ matrix.
-    Under the left action of $A$, say $A\mu=\mu'$ for $\mu,\mu'\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\bfr\bullet\mu \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet\mu'\le t.\]
+    Under the left action of $A$, say $A\mu=\mu'$ for $\mu,\mu'\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\langle\bfr,\mu\rangle \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality
+    \[
+      \langle A^{-T}\bfr,\mu'\rangle\le t.
+    \]
   \end{lemma}
@@
     This is immediate from the equalities
-    \[\bfr\bullet\mu=\bfr^T\mu=\bfr^TA^{-1}A\mu=(A^{-T}\bfr)^TA\mu=(A^{-T}\bfr)\bullet\mu'.\]
+    \[
+      \langle \bfr,\mu\rangle
+      =
+      \bfr^T\mu
+      =
+      \bfr^TA^{-1}A\mu
+      =
+      (A^{-T}\bfr)^TA\mu
+      =
+      \langle A^{-T}\bfr,\mu'\rangle.
+    \]
   \end{proof}
 
+  The following calculation is key to our main result.
   \begin{lemma}
@@
     %positives k=3
-    \begin{scope}[shift={(15,0)}]
+    \begin{scope}[shift={(20,0)}]
       \setconstants;
@@
     \end{scope}
-    \draw (15,-7) node{$\phi_{3}^{-1}\cC_{3}(\phi_{3}\lambda)$};
+    \draw (20,-7) node{$\phi_{3}^{-1}\cC_{3}(\phi_{3}\lambda)$};
   \end{tikzpicture}
@@
     \[ (\dagger)\ \mu_0 \le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger)\ -\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1. \]
-    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.
-    First observe that $\phi_2^{-1}=\phi_{-2}$ is given as follows:
+    We compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$ using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\left(\phi_2^{-1}\right)^{j}$.
+    First observe that~$\phi_2^{-1}=\phi_{-2}$ is given as follows:
     \begin{equation}
@@
 
-    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
+    We prove the claim by induction on $i$.
+    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$.
     By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $c\mu_0+\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1$ which corresponds to (a) with $i=1$.
-    Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$, each of determinant 1.
-    By Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with $i=1$.
-    This establishes the base of an induction on $i$.
-
-    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
-    Both of the boundary rays corresponding to the inequalities (a) and (d) lie entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
+    Similarly, the boundary ray for $\cC_{2j}(\phi_{2j}\lambda)$ corresponding to ($\dagger$) intersects the three domains of linearity in which $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$, $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$.
+    By Lemma~\ref{le:transformed inequalities}, the inequality~($\dagger$) can be seen to transform by these into each of inequalities (b), (c), (d) with~$i=1$.
+    This establishes the base of our induction.
+
+    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} for $\phi_2^{-1}$.
+    Both of the boundary rays corresponding to the inequalities (a) and (d) lie entirely in the region where $\phi_2^{-1}$ acts according to the matrix~$\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
     Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
@@
     \[ (\dagger')\ -\mu_0\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1 \qquad\text{and}\qquad (\ddagger')\ \mu_1\le u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1.\]
-    Using that $\phi_{2j+1}^{-1}=\phi_2^{-j}\phi_1^{-1}$, we compute the image inductively as above.
-    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$ of determinant $-1$.
+    Using that $\phi_{2j+1}^{-1}=\left(\phi_2^{-1}\right)^j\phi_1^{-1}$, we compute the image inductively as above.
+    From \eqref{eq:forward mutation 1} and Lemma~\ref{le:imaginary stability}, we see that the boundary ray for $\cC_{2j+1}(\phi_{2j+1}\lambda)$ corresponding to ($\dagger'$) lies entirely in the region in which $\phi_1^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & 1 \end{array}\right]$.
     Thus applying Lemma~\ref{le:transformed inequalities}, the inequality ($\dagger'$) is transformed by $\phi_1^{-1}$ into the inequality $\mu_0\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1$.
@@
 
-  To begin, observe that the boundary lines for \eqref{ineq:2} and \eqref{ineq:3} (and hence \eqref{ieq1} and \eqref{ieq2} below) intersect where $\mu_0=0$ and the boundary lines for \eqref{ineq:3} and \eqref{ineq:4} (and hence \eqref{ieq2} and \eqref{ieq3} with $k-1$) intersect where $\mu_1=0$.
-  We then rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
+%  To begin, observe that the boundary lines for \eqref{ineq:2} and \eqref{ineq:3} (hence \eqref{ieq1} and \eqref{ieq2} below) intersect where $\mu_0=0$ and the boundary lines for \eqref{ineq:3} and \eqref{ineq:4} (hence \eqref{ieq2} and \eqref{ieq3} with $k-1$) intersect where $\mu_1=0$.
+  We rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
   For $k>0$, we get
@@
   for $k<0$.
-  Then, using that $-u_k^\varepsilon<0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$, we divide by these to rewrite the inequalities again as
+
+  Then, using that $-u_k^\varepsilon<0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$, we rewrite the inequalities again as
   \begin{align}
-    \label{ieq1} 0 & \le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
+    \label{ieq1} 0 & \le -(\mu_0-\lambda_0)-\frac{u_k^+}{u_{k+1}^-}(\mu_1-\lambda_1);\\
     \label{ieq2} -c\lambda_0 & \le \frac{u_{k-1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
@@
 Lemma~\ref{le:limits}).
-  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality 
-  \[ 0 \le \frac{-bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
-  or, equivalently,
-  \[ 0 \le -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \]
-  determining a boundary of $\cP_\lambda$.
+  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality below determining a boundary of $\cP_\lambda$:
+  \[ 0 \le -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1). \]
 
@@
 Lemma~\ref{le:limits}) and the intersection with \eqref{ieq2} (for $k+1$) moves to the right on the $\mu_0$-axis as $k$ increases.
-  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality
-  \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1 \]
-  determining a boundary of $\cP_\lambda$.
+  Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality below determining a boundary of $\cP_\lambda$:
+  \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1. \]
 

### 2022-06-06 dominance_regions.tex
Part of section 6

@@
 
+  We begin observing that, by Lemma~\ref{le:cluster monomials}, the dominance region $\cP_\lambda$ of any $\bfg$-vector $\lambda\not\in\cI$ is just the point~$\lambda$.
+  Therefore, by Theorem~\ref{th:dominance} the corresponding pointed element is the cluster monomial whose $\bfg$-vector is $\lambda$. 
+  The support of this element is exactly $\cS_\lambda$ by \cite[Proposition 4.1]{LLZ14}.
+
   Every pointed basis element for $\cA(b,c)$ admits an opposite $\bfg$-vector arising by interchanging the roles of $b$, $c$ and $x_0$, $x_1$ in \eqref{eq:pointed}. 
@@
 
-  For $\lambda\in\cI$, the maximal support $\cS_\lambda$ is determined by the following inequalities:
-  \begin{align*}
-    \lambda_1 &\leq \mu_1\\
-    \lambda'_0 &\leq \mu_0\\
-    0 &\leq -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1)\\
-    0 &\leq -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda'_0) -(\mu_1-\lambda'_1)
-  \end{align*}
-  We claim that $\cP_\lambda,\cP'_\lambda\subset\cS_\lambda$.
-
-  Observe that the last equality can be rewritten as
+  For $\lambda\in\cI$, the region $\cS_\lambda$ from Theorem~\ref{th:maximum support} is determined by the following inequalities:
+  \begin{align*}
+    \lambda_1 &\leq \mu_1;\\
+    \lambda'_0 &\leq \mu_0;\\
+    0 &\leq -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
+    0 &\leq -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda'_0) -(\mu_1-\lambda'_1).
+  \end{align*}
+  To begin proving that this is the maximal support we claim that $\cP_\lambda,\cP'_\lambda\subset\cS_\lambda$.
+
+  Observe that the last inequality can be rewritten as
   \[ \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) \leq -c\lambda_0 - \frac{b c + \sqrt{b c (b c-4)}}{2 } \lambda_1,\]
@@
   The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{CGMMRSW17,LLZ14}.
-  This is indicated by the solid and dotted lines in Theorem~\ref{th:maximum support} where dotted lines indicate points that are excluded from the support (note that the white dot does not indicate that this point is excluded).
+  This is indicated by the solid and dotted lines in our figures where dotted lines indicate points that are excluded from the support.
   For our purposes, it is enough to observe the following closure property for the greedy support.

### 2022-06-06 dominance_regions.tex
L-closed

@@
 \usepackage{amsmath}
+\usepackage{MnSymbol}
 \usepackage{amssymb}
@@
   \begin{definition}
-    A subset $\cS\subset\RR^2$ is called \emph{min-convex} if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
+    A subset $\cS\subset\RR^2$ is called  $\lefthalfcup$-closed  \emph{min-convex} if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
   \end{definition}

### 2022-06-08 dominance_regions.tex
L

--- 2022-06-06 dominance_regions.tex
@@
 \usepackage{amsmath}
+%\usepackage{MnSymbol}
 \usepackage{amssymb}
@@
   \begin{definition}
-    A subset $\cS\subset\RR^2$ is called \emph{min-convex} if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
+    A subset $\cS\subset\RR^2$ is called \scalebox{1.7}{$\llcorner$}-closed  \emph{min-convex} if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
+    %$\lefthalfcup$
   \end{definition}

### 2022-06-08 dominance_regions.tex
Almost done with section 6

--- 2022-06-06 dominance_regions.tex
@@
 
-  To continue, we compare the support for an arbitrary basis element pointed at $\lambda\in\cI$ with the corresponding greedy basis elements with $\bfg$-vectors inside the dominance polygon $\cP_\lambda$.
-
-  The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{CGMMRSW17,LLZ14}.
+  To continue, we compare the support for an arbitrary basis element pointed at $\lambda\in\cI$ with the greedy basis elements having $\bfg$-vector inside the dominance polygon $\cP_\lambda$.
+
+  The support region $\cG_\lambda$ of the greedy basis element with $\bfg$-vector $\lambda$ is well-known \cite{CGMMRSW17,LLZ14}.
   This is indicated by the solid and dotted lines in our figures where dotted lines indicate points that are excluded from the support.
-  For our purposes, it is enough to observe the following closure property for the greedy support.
+  (The actual support of the greedy basis element consists of the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cG_\lambda$.)
+  For our purposes, it is enough to observe the following closure property for the greedy support region which is evident from the figure in Theorem~\ref{th:maximum support}.
   \begin{definition}
-    A subset $\cS\subset\RR^2$ is called \emph{min-convex} if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
+    A subset $\cS\subset\RR^2$ is called \scalebox{1.7}{$\llcorner$}-closed if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to~$\big(\!\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
   \end{definition}
-  In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector $\lambda$ indicated by a black dot and the opposite $\bfg$-vector $\lambda'$ indicated by a white dot in Theorem~\ref{th:maximum support}.
-  Write $\overline{\cG}_\lambda$ for the downward scaling of the min-convex closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
+  In particular, (an upper bound for) the greedy support region $\cG_\lambda$ can be found using its $\bfg$-vector $\lambda$ %indicated by a black dot 
+  and its opposite $\bfg$-vector $\lambda'$. % indicated by a white dot in Theorem~\ref{th:maximum support}.
+  Write $\overline{\cG}_\lambda$ for the downward scaling of the \scalebox{1.7}{$\llcorner$}-closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\!\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
   Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.
@@
   As we saw above, for any $\bfg$-vector $\mu\in\cP_\lambda$ its opposite $\bfg$-vector $\mu'$ is also contained in $\cS_\lambda$.
-  But $\cS_\lambda$ is min-convex and closed under downward scaling, i.e. for any $\mu\in\cS_\lambda$ we have $t\mu\in\cS_\lambda$ for $0\le t\le 1$.
+  But $\cS_\lambda$ is \scalebox{1.7}{$\llcorner$}-closed and closed under downward scaling. %, i.e. for any $\mu\in\cS_\lambda$ we have $t\mu\in\cS_\lambda$ for $0\le t\le 1$.
   It follows that $\overline{\cG}_\mu\subset\cS_\lambda$ for any $\mu\in\cP_\lambda$ and hence, following Theorem~\ref{th:dominance}, the support of any basis element pointed at $\lambda$ is contained in $\cS_\lambda$.

### 2022-06-09 dominance_regions.tex
Added a missing period in section 7, everything else there looks good to me.
Done

@@
   In particular, $\cG_\lambda\subset\cS_\lambda$.
-  Note also that the dominance region $\cP_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR_1$ defined by the inequalities $\mu_0\ge0$ and $\lambda_1\mu_0-\lambda_0\mu_1\ge0$.
-  Similarly, the opposite dominance region $\cP'_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR_2$ defined by the inequalities $\mu_1\ge0$ and $-\lambda'_1\mu_0+\lambda'_0\mu_1\ge0$.
-  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR_1)\cup(\cS_\lambda\cap\cR_2)$ so $\cS_\lambda$ is the maximum possible support for an element pointed at~$\lambda$.
-
-\section{The affine case}
+  Note also that the dominance region $\cP_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR$ defined by the inequalities $\mu_0\ge0$ and $\lambda_1\mu_0-\lambda_0\mu_1\ge0$.
+  Similarly, the opposite dominance region $\cP'_\lambda$ contains the intersection of $\cS_\lambda$ with the region $\cR'$ defined by the inequalities $\mu_1\ge0$ and $-\lambda'_1\mu_0+\lambda'_0\mu_1\ge0$.
+  But $\cS_\lambda=\cG_\lambda\cup(\cS_\lambda\cap\cR)\cup(\cS_\lambda\cap\cR')$ so $\cS_\lambda$ is the maximum possible support for an element pointed at~$\lambda$.
+
+\section{The untwisted affine case}
 \label{sec:affine}
@@
     {\ell\choose k} {n\choose \ell}
-    \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+    \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}.
   \]
@@
     \end{align*}
-    But then rearranging terms and replacing $\ell$ by $\ell+r$, this becomes
+    But then, rearranging terms and replacing $\ell$ by $\ell+r$, this becomes
     \begin{align*}

### 2022-06-09 dominance_regions.tex
Bibliography
My affiliation
Affiliations SS

@@
 \usepackage{amsmath}
-%\usepackage{MnSymbol}
 \usepackage{amssymb}
@@
 %\usepackage{ulem}
-\usepackage[margin=1in,showframe]{geometry}
+%\usepackage[margin=1in,showframe]{geometry}
+\usepackage[margin=1in]{geometry}
 \usepackage{tikz}
@@
 \author{Salvatore Stella}
+\address[S.
+Stella]{\href{mailto:salvatore.stella@univaq.it}{\textup{\texttt{salvatore.stella@univaq.it}}}, Dipartimento di Ingegneria e Scienze dell'Informazione e Matematica, Università degli Studi dell'Aquila, IT}
+%\email[Salvatore Stella]{stella@math.haifa.ac.il}
+%\keywords{}
+\thanks{Salvatore Stella was partially supported by the University of Leicester, and the University of Rome ``La Sapienza''.}
+%\thanks{Nathan Reading was partially supported by the National Science Foundation under Grant Numbers DMS-1500949 and DMS-2054489 and by the Simons Foundation under award number 581608.\\
+%\indent Salvatore Stella was partially supported by ISF grant \#1144/16, the University of Haifa, the University of Leicester, and the University of Rome ``La Sapienza''.}
 
@@
   \maketitle
-
+\vspace{-1em}
 \begin{figure}[h!]
@@
 \end{figure}
+\vspace{-1em}
   \section{Introduction}

### 2022-06-09 dominance_regions.tex
Initials instead of full name
email

@@
 \author{Salvatore Stella}
+\address[D. Rupel]{\href{mailto:rupel.dylan@pusd.us}{\textup{\texttt{rupel.dylan@pusd.us}}}  Math Academy, Pasadena Unified School District, Pasadena, CA 91109 USA}
 \address[S.
@@
 %\keywords{}
-\thanks{Salvatore Stella was partially supported by the University of Leicester, and the University of Rome ``La Sapienza''.}
+\thanks{Salvatore Stella was partially supported by the University of Leicester and the University of Rome ``La Sapienza''.}
 %\thanks{Nathan Reading was partially supported by the National Science Foundation under Grant Numbers DMS-1500949 and DMS-2054489 and by the Simons Foundation under award number 581608.\\

### 2022-06-09 dominance_regions.tex
,

@@
 \author{Salvatore Stella}
-\address[D. Rupel]{\href{mailto:rupel.dylan@pusd.us}{\textup{\texttt{rupel.dylan@pusd.us}}}  Math Academy, Pasadena Unified School District, Pasadena, CA 91109 USA}
+\address[D. Rupel]{\href{mailto:rupel.dylan@pusd.us}{\textup{\texttt{rupel.dylan@pusd.us}}}, Math Academy, Pasadena Unified School District, Pasadena, CA 91109 USA}
 \address[S.

### 2022-06-09 dominance_regions.tex
Cleanup

@@
 \usepackage{color}
-%\usepackage{ulem}
-%\usepackage[margin=1in,showframe]{geometry}
 \usepackage[margin=1in]{geometry}
@@
 \usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
-
-\usepackage[draft]{say}
-\newcommand{\sayDR}[1]{\say[DR]{\color{red}{\bf DR:}\;#1}}
-\newcommand{\saySS}[1]{\say[SS]{\color{blue}{\bf SS:}\;#1}}
 
@@
 Stella]{\href{mailto:salvatore.stella@univaq.it}{\textup{\texttt{salvatore.stella@univaq.it}}}, Dipartimento di Ingegneria e Scienze dell'Informazione e Matematica, Università degli Studi dell'Aquila, IT}
-%\email[Salvatore Stella]{stella@math.haifa.ac.il}
-%\keywords{}
 \thanks{Salvatore Stella was partially supported by the University of Leicester and the University of Rome ``La Sapienza''.}
-%\thanks{Nathan Reading was partially supported by the National Science Foundation under Grant Numbers DMS-1500949 and DMS-2054489 and by the Simons Foundation under award number 581608.\\
-%\indent Salvatore Stella was partially supported by ISF grant \#1144/16, the University of Haifa, the University of Leicester, and the University of Rome ``La Sapienza''.}
 
@@
   We study the polygons defining the dominance order on $\bfg$-vectors in cluster algebras of rank 2.
-%    We investigate the shapes of the polytopes defining the dominance order for $\bfg$-vectors in cluster algebras of rank two.
-%    We arrive at a complete description: 
-%    \begin{itemize}
-%      \item cluster monomials are never deformable;
-%      \item the imaginary dominance polytopes are kites, triangles, or trapezoids which extend far outside the imaginary cone; the triangles appearing along rays corresponding to columns of the associated Cartan matrix.
-%    \end{itemize}
 \end{abstract}
@@
   Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance region} $\cP_\lambda$.
-  %In this case, we compute the possible transitions between any two pointed bases.
-  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
   \begin{theorem}
@@
     }
-    %\begin{align}
-    %  0 & \leq \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) && \leq \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
-    %  \\
-    %  \min\left(-c\lambda_0,0\right) & \leq \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) && \leq 0
-    %  \\
-    %  0 & \leq -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) && \leq \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
-    %  \\
-    %  \min\left(b \lambda_1,0\right) & \leq (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) && \leq 0
-    %\end{align}
 
@@
   \end{theorem}
-  %\vspace{-0.713em}
   \begin{remark}
-  %Interestingly, explicit calculations reveal that the $\bfg$-vectors actually appearing in the transitions between notable bases are far smaller than the entire dominance polygon.
     Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coeffiecients $q_{\lambda,\mu}$ are zero.
@@
       \fill (\x,\y) circle (5pt);
-%      \fill[white] (\xmax-2,\ymax-1.5) rectangle (\xmax-1, \ymax-0.5);
       \draw (\xmin+1.5,\ymin+1) node{(1.a)};
@@
       \draw [thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
-      %\draw [dashed, thick]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) -- (\x,\y);
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
@@
       \fill (\x,\y) circle (5pt);
-      %\fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);
@@
       \fill (\x , \y)  circle (5pt);
-      %\fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
@@
     \end{scope}
-    %\draw[black,very thick] (-6.5,6.5) -- (45.5,6.5) -- (45.5,-19.5) -- (-6.5,-19.5) -- cycle;
-    %\draw[black,very thick] (-6.5,-6.5) -- (45.5,-6.5);
-    %\draw[black,very thick] (6.5,6.5) -- (6.5,-19.5);
-    %\draw[black,very thick] (19.5,6.5) -- (19.5,-19.5);
-    %\draw[black,very thick] (32.5,6.5) -- (32.5,-19.5);
     \draw (21,-22) node{The maximal supports $\cS_\lambda$ as described in Theorem \ref{th:maximum support}.};
@@
 
-  %The recursion can be written more succinctly as $u_{i+1}^\varepsilon=u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon$ with the additional initial condition $u_2^\varepsilon=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
-  %This leads to the following more general recursive structure.
   \begin{lemma}
@@
   \begin{lemma}
-    Any nonzero eigenvector of $\phi_2$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+    Any nonzero eigenvector of $\phi_2$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)\!$.
   \end{lemma}
@@
 
-  %\begin{lemma}
-  %  The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
-  %\end{lemma}
-  %\begin{proof}
-  %  This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
-  %\end{proof}
   Observe that the imaginary cone $\cI$ is spanned by the eigenvectors of $\phi_{2}$ and that $\phi_{2}$ is linear in $\cI$.
@@
 
-    %given as in the figure below:
 \begin{figure}[h!]
@@
       \draw [color=gray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
-      %\draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
-      %\draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
     }
@@
 
-%  To begin, observe that the boundary lines for \eqref{ineq:2} and \eqref{ineq:3} (hence \eqref{ieq1} and \eqref{ieq2} below) intersect where $\mu_0=0$ and the boundary lines for \eqref{ineq:3} and \eqref{ineq:4} (hence \eqref{ieq2} and \eqref{ieq3} with $k-1$) intersect where $\mu_1=0$.
   We rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
@@
 
-  %Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
   Similar arguments using \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
@@
     Translating from Theorem~\ref{th:dominance inequalities}, it immediately follows that the opposite dominance region is given by the claimed inequalities.
-    %{
-    %  \everymath={\displaystyle}
-    %  \def\arraystretch{2.8}
-    %  \[
-    %    \begin{array}{rcccl}
-    %      0 & \leq & -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & c\lambda_0 + \frac{b c-\sqrt{b c (b c-4)}}{2 b}b\lambda_1
-    %      \\
-    %       & & (\mu_0-\lambda_0) -\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & -\frac{b c+\sqrt{b c (b c-4)}}{2}(\lambda_0+b\lambda_1)+2b\lambda_1
-    %      \\
-    %      \frac{b c - 2 +\sqrt{b c (b c-4)}}{2}(c\lambda_0+(bc-2)\lambda_1) -c\lambda_0 -2\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) & \leq & -c\lambda_0 - \frac{b c+\sqrt{b c (b c-4)}}{2 b}b\lambda_1
-    %      \\
-    %      -c\lambda_0+\frac{b c-2+\sqrt{b c (b c-4)}}{2}(c\lambda_0 + \sqrt{b c (b c-4)}\lambda_1) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) & \leq & -c\lambda_0 - \frac{b c+\sqrt{b c (b c-4)}}{2 b}b\lambda_1
-    %      \\
-    %      b\lambda_1 & \leq & - (\mu_0-\lambda_0) + \frac{b c+\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) 
-    %    \end{array}
-    %  \]
-    %}
   \end{proof}
@@
   As above, the minimum value of $\mu_1$ inside $\cP'_\lambda$ occurs when $\mu_0=0$, i.e. either at the point $\big(0, \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1 \big)$
-  %\[\big(0, \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1 \big) = \big(0, -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\lambda_0+b\lambda_1)+\lambda_1 \big)\]
   when $0 \leq 2\lambda'_0+b\lambda'_1$ or at the point $-\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, \lambda'_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda'_1 \big)$
-  %\[-\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, \lambda'_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda'_1 \big) = -\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, -\frac{bc-2+\sqrt{bc(bc-4)}}{2}(\lambda_0+b\lambda_1)+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1 \big)\]
   when $2\lambda'_0+b\lambda'_1<0$.
@@
       \label{eq:generalized minor}
-      x_{(n,-n)}^{\bfa^{(n)}}:= x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa^{(n)},r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
+      x_{(n,-n)}^{\bfa^{(n)}}:= x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa^{(n)},r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
     \end{equation}
@@
 
-% bibliography
-% because of conflicts some keys needs to be fixed by hand.
-% to regenerate the bibliography delete the one below, uncomment the following two lines and recompile, comment the two lines again, edit monomialminors.bbl as needed and paste its content here
 \bibliographystyle{amsalpha}

### 2022-06-10 affine_dominance.tex
Copied the general setup we had before into a new file, I'm not sure what here is or isn't useful.

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color,ulem}
\usepackage[margin=1.5in]{geometry}
\usepackage{tikz}
\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}

\usepackage[draft]{say}
\newcommand{\sayDR}[1]{\say[DR]{\color{red}{\bf DR:}\;#1}}
\newcommand{\saySS}[1]{\say[SS]{\color{blue}{\bf SS:}\;#1}}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}{Question}

\numberwithin{theorem}{section}

\newcommand{\bfc}{\boldsymbol{c}}
\newcommand{\bfg}{\boldsymbol{g}}
\newcommand{\bfr}{\boldsymbol{r}}
\newcommand{\bfx}{\boldsymbol{x}}
\newcommand{\bfy}{\boldsymbol{y}}

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

\newcommand{\fp}{\mathfrak{p}}

\newcommand{\CC}{\mathbb{C}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\TT}{\mathbb{T}}
\newcommand{\ZZ}{\mathbb{Z}}

\newcommand{\ol}[1]{{\overline{#1}}}
\newcommand{\vv}[1]{{{}^\vee \! #1}}

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\Col}{\operatorname{Col}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\dpt}{\operatorname{dp}}
\newcommand{\hgt}{\operatorname{ht}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}
\newcommand{\rsh}{{\operatorname{rsh}}}
\newcommand{\sh}{{\operatorname{sh}}}
\newcommand{\WA}{{W\!\!A}}
\newcommand{\wt}{{\operatorname{wt}}}

\title{Dominance Regions for Affine Cluster Algebras}

\author{Dylan Rupel}
\author{Salvatore Stella}

\begin{document}
  \begin{abstract}
    We study the dominance order for $\bfg$-vectors in affine cluster algebras.
  \end{abstract}
  \maketitle

  \section{Introduction}
  A lot of the same first paragraph we had before.

  \section{Lattice Mutations and Linear Inequalities}
  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable integer matrix, i.e. there exists a diagonal integer matrix $D=\diag(d_1,\ldots,d_n)$ so that $DB$ is skew-symmetric, more precisely we have $d_i b_{ij}=-d_j b_{ji}$.
  Write $\Col(B)$ for the span of the columns of $B$ inside $\RR^n$ and $\Col^+(B)$ for their non-negative span.
  Define $\Col_\ZZ(B)$ and $\Col^+_\ZZ(B)$ analogously over the integers.

  The matrix $B$ is \emph{acyclic} if there is no sequence $i_1,\ldots,i_m,i_{m+1}=i_1$ so that $b_{i_\ell i_{\ell+1}}>0$ for $1\le\ell\le m$.
  This condition is naturally interpreted in terms of an associated quiver $Q_B$ with $n$ vertices and an arrow $i\to j$ whenever $b_{ji}>0$ (if we need to use representation theory at any point we'll have to change this to be $\gcd(b_{ij},b_{ji})$ arrows $i\to j$).
  Indeed, this is precisely the condition that $Q_B$ has no oriented cycles.
  In the case when $B$ is acyclic, there exists a labeling $\{k_1,\ldots,k_n\}=\{1,\ldots,n\}$ so that $\ell<\ell'$ implies $b_{k_{\ell'} k_\ell}\ge 0$.
  The sequence $(k_1,\ldots,k_n)$ (resp. $(k_n,\ldots,k_1)$) is then said to be \emph{source-adapted} (resp. \emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
  %\sayDR{We need to pin down this convention.}

  For $b\in\ZZ$, write $[b]_+=max(b,0)$.
  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
  \begin{equation}
    \label{eq:left mutation matrix}
    e_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ [\varepsilon b_{ik}]_+ & \text{if $i\ne j=k$;}\\ 0 & \text{otherwise;} \end{cases}
  \end{equation}
  and a matrix $F_{k,\varepsilon}=(f_{ij})$ with
  \begin{equation}
    \label{eq:right mutation matrix}
    f_{ij}=\begin{cases} 1 & \text{if $k\ne i=j$;}\\ -1 & \text{if $k=i=j$;}\\ [-\varepsilon b_{kj}]_+ & \text{if $k=i\ne j$;}\\ 0 & \text{otherwise.} \end{cases}
  \end{equation}
  Observe that $E^2_{k,\varepsilon}=\Id$ and $F^2_{k,\varepsilon}=\Id$ for any $k$ and any choice of $\varepsilon$.
  \begin{lemma}
    For $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, we have $E_{k,-\varepsilon}E_{k,\varepsilon}=I_n+\varepsilon B^{\bullet k}$ and $E_{k,\varepsilon}-E_{k,-\varepsilon}=\varepsilon B^{\bullet k}$.
  \end{lemma}
  \begin{proof}
    This is immediate from the equality $\varepsilon b_{ij}=[\varepsilon b_{ij}]_+-[-\varepsilon b_{ij}]_+$.
  \end{proof}

  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_k B=(b'_{ij})$ given by
  \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
  One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
  \begin{remark}
    Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
  \end{remark}

  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
  \begin{itemize}
    \item $B^{t_0}=B$;
    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $B^{t'}=\mu_k B^t$.
  \end{itemize}

  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
  where the entries of $E^t_{k,\varepsilon}$ are given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labeled $k$.
  \begin{lemma}
    Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
    If $\mu\in\lambda+\Col(B^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
  \end{lemma}
  \begin{proof}
    Suppose $\mu=\lambda+B^t\alpha$ for some $\alpha\in\RR^n$.
    Let $\varepsilon$ (resp. $\varepsilon'$) be such that $\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu$ (resp. $\phi^t_k(\lambda)=E^t_{k,\varepsilon'}\lambda$).
    Then 
    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+B^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + B^{t'} F^t_{k,\varepsilon}\alpha.\]
    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + B^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
    Otherwise, 
    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(B^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(B^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon B^{t'} \lambda_k \mathbf{e}_k\]
    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
  \end{proof}

  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
  \begin{itemize}
    \item $\phi_{t_0}=\Id$;
    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
  \end{itemize}

  Suppose $B$ is acyclic.
  Given a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, define a quiver $Q_{B,\varepsilon}$ from $Q_B$ by removing all arrows starting at vertex $i$ whenever $\varepsilon_i=-1$.
  For $1\le j\le n$, define $\cP_j(Q_{B,\varepsilon})$ as the set of paths in $Q_{B,\varepsilon}$ starting at vertex $j$.
  Elements of $\cP_j(Q_{B,\varepsilon})$ are sequences of vertices $(p_1,\ldots,p_r)$ with $p_1=j$ and $b_{p_{t+1}p_t}>0$ for $1\le t\le r-1$.
  Given a path $p\in\cP_j(Q_{B,\varepsilon})$, a vertex $i\in Q_0$, and a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, set
  \[\wt_{i,\varepsilon}(p):=-b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}\prod_{t=1}^{r-1} b_{p_{t+1}p_t},\]
  where the prefactor $b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}$ is omitted if $i=p_r$ or $\varepsilon_{p_r}=-1$.
  \begin{lemma}
    Suppose $B$ is acyclic with source-adapted sequence $k_1,\ldots,k_n$.
    Consider $t_1,\ldots,t_n\in\TT_n$ so that $t_{\ell-1}$ is joined to $t_\ell$ by an edge in $\TT_n$ labeled by $k_\ell$ for $1\le\ell\le n$.
    For a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, the product $E^{t_{n-1}}_{k_n,\varepsilon_{k_n}}\cdots E^{t_0}_{k_1,\varepsilon_{k_1}}$ is given by $\tau=(\tau_{ij})$ with
    \begin{equation}
      \label{eq:tropical twist}
      \tau_{ij}=\sum_{p\in\cP_j(Q_{B,\varepsilon})}^* \wt_{i,\varepsilon}(p),
    \end{equation}
    where the $*$ indicates that the summation includes the trivial path at $j$ only if $i\le j$ when $\varepsilon_j=1$ and only if $i=j$ when $\varepsilon_j=-1$.

    Then $\phi_{t_n}$ is the following piecewise-linear automorphism:
    \begin{equation}
      \label{eq:tropical twist}
      \text{(This is going to require casework with the possible signs, we'll really only need it for imaginary $\bfg$-vectors though.)}
    \end{equation}
    The answer comes from selectively ``turning off'' arrows out of chosen vertices as indicated by choosing $\varepsilon_i=-1$.
  \end{lemma}
  \begin{proof}
    We prove the following modified formula for the product $E^{t_{n-1}}_{k_n,\varepsilon_{k_n}}\cdots E^{t_{m-1}}_{k_m,\varepsilon_{k_m}}$ for $1\le m\le n$ by reverse induction on $m$.
    Writing this matrix as $\tau^{(m)}=(\tau^{(m)}_{ij})$, we claim that
    \begin{equation}
      \label{eq:tropical twist}
      \tau^{(m)}_{ij}=\begin{cases} \sum\limits_{p\in\cP_j(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) & \text{if $j=k_\ell$ with $m\le\ell$;}\\ \delta_{ij} & \text{otherwise;} \end{cases}
    \end{equation}
    where $Q_{B,\varepsilon}^{(m)}$ is the full subquiver of $Q_{B,\varepsilon}$ on vertices $k_m,\ldots,k_n$.
    Note that the weight function follows the same definition as above.

    Since the sequence $k_1,\ldots,k_n$ is source-adapted, the matrix $E^{t_{m-1}}_{k_m,\varepsilon_m}$, for $1\le m\le n$, has entries $e^{(m)}_{ij}$ given by
    \begin{equation}
      \label{eq:source mutation matrix}
      e^{(m)}_{ij}=\begin{cases} 1 & \text{if $i=j\ne k_m$;}\\ -1 & \text{if $i=j=k_m$;}\\ [-\varepsilon_{k_m} b_{ik_m}]_+ & \text{if $i=k_\ell$, $j=k_m$, $\ell<m$;}\\ [\varepsilon_{k_m} b_{ik_m}]_+ & \text{if $i=k_\ell$, $j=k_m$, $m<\ell$;}\\ 0 & \text{otherwise;} \end{cases}
    \end{equation}
    the entries for $\ell<m$ picking up the sign from the prior matrix mutations.

    For $m=n$, it is clear that $\tau^{(n)}_{ij}=e^{(n)}_{ij}$ for $j\ne k_n$.
    If $\varepsilon_{k_n}=1$, there is only the trivial path $(k_n)$ in $Q_{B,\varepsilon}^{(n)}$ and we have $\tau^{(n)}_{ik_n}=-b_{ik_n}$, which agrees with $e^{(n)}_{ik_n}$ in this case.
    Otherwise, $\varepsilon_{k_n}=-1$ and the sum is empty for $i\ne k_n$ giving $\tau^{(n)}_{ik_n}=0=e^{(n)}_{ik_n}$ or only takes the trivial path for $i=k_n$ giving $\tau^{(n)}_{k_nk_n}=-1=e^{(n)}_{k_nk_n}$.
    This gives the base of the induction.

    Now suppose the matrix $\tau^{(m)}$ is given as above.
    Using equation \eqref{eq:source mutation matrix}, we need to check that 
    \begin{equation}
      \label{eq:twist matrix recursion}
      \tau^{(m-1)}_{ij}=\sum\limits_{p=1}^n \tau^{(m)}_{ip} e^{(m-1)}_{pj}=\begin{cases} \tau^{(m)}_{ij} & \text{if $j\ne k_{m-1}$;}\\ -\tau^{(m)}_{ik_{m-1}} + \sum\limits_{\ell=1}^{m-2} \tau^{(m)}_{i k_\ell} [-\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ + \sum\limits_{\ell=m}^n \tau^{(m)}_{i k_\ell} [\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ & \text{if $j=k_{m-1}$;}\end{cases}
    \end{equation}
    is computed by the formula above.
    First observe that $\tau^{(m-1)}_{ij}=\tau^{(m)}_{ij}=\delta_{ij}$ if $j=k_\ell$ with $\ell<m-1$.  
    Second observe that $\cP_j(Q_{B,\varepsilon}^{(m-1)})=\cP_j(Q_{B,\varepsilon}^{(m)})$ whenever $j=k_\ell$ with $m\le\ell$, i.e. the purported formulas for $\tau^{(m-1)}_{ij}$ and $\tau^{(m)}_{ij}$ agree in this case.
    Therefore it remains to show that
    \[
      \tau^{(m-1)}_{i k_{m-1}}=-\delta_{ik_{m-1}} + \sum\limits_{\ell=1}^{m-2} \delta_{i k_\ell} [-\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+ + \sum\limits_{\ell=m}^n \sum\limits_{p\in\cP_{k_\ell}(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) [\varepsilon_{k_{m-1}} b_{k_\ell k_{m-1}}]_+
    \]
    agrees with the desired expression.
    Indeed, for $\varepsilon_{k_{m-1}}=-1$ this reduces to $\tau^{(m-1)}_{i k_{m-1}}=-\delta_{i k_{m-1}}$ which matches with the desired expression in this case.
    Then assuming $\varepsilon_{k_{m-1}}=1$, we are comparing with
    \[
      \tau^{(m-1)}_{i k_{m-1}}=-\delta_{ik_{m-1}} - \sum\limits_{\ell=1}^{m-2} \delta_{i k_\ell} b_{k_\ell k_{m-1}} + \sum\limits_{\ell=m}^n \sum\limits_{p\in\cP_{k_\ell}(Q_{B,\varepsilon}^{(m)})}^* \wt_{i,\varepsilon}(p) b_{k_\ell k_{m-1}}.
    \]
    But observe that the final summation above contributes the nontrivial paths to the summation $\sum\limits_{p\in\cP_{k_{m-1}}(Q_{B,\varepsilon}^{(m-1)})}^* \wt_{i,\varepsilon}(p)$ while the first two terms above give the contribution, depending on $i$, corresponding to the trivial path $(k_{m-1})$.
  \end{proof}
  \begin{question}
    Is the trace of $\tau$ an invariant of matrix mutations?  P.A.: It is invariant under sink and source mutations since the trace is a class function and these mutations simply enact a cyclic shift in the factors of $\tau$.
  \end{question}

  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
  \begin{definition}
    For $\lambda\in\RR^n$, define the \emph{dominance region} 
    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
  \end{definition}
  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
  \begin{lemma}
    The sets $\cP(\lambda)$ are polytopes.
  \end{lemma}

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A$ be an invertible $n\times n$ matrix.
    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
  \end{lemma}
  \begin{proof}
    This is immediate from the equalities
    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
  \end{proof}

  \section{Affine Types}
  Associated to an acyclic skew-symmetrizable matrix $B=(b_{ij})$ there is a Cartan matrix $A=(a_{ij})$ with $a_{ii}=2$ and $a_{ij}=-|b_{ij}|$.
  We say that $B$ is of affine type if its associated Cartan matrix gives rise to an affine Dynkin diagram.
  In this section, we focus on understanding the dominance polytopes for affine matrices $B$.

  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable matrix of affine type with associated Cartan matrix $A=(a_{ij})$.

  \begin{lemma}
    One column is always in the positive span of the other columns.
  \end{lemma}

  \begin{definition}
    Describe imaginary $\bfg$-vectors and those corresponding to cluster monomials.
  \end{definition}

  \begin{lemma}
    Let $\lambda\in\ZZ^n$ correspond to a cluster monomial.
    Then $\cP(\lambda)=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    An explicit sequence of sink/source mutations should suffice.
  \end{proof}

\end{document}

### 2022-06-12 affine_dominance.tex
Modified our code

@@
 \emph{sink-adapted}) since the condition implies $k_1$ is a source and $k_n$ is a sink in $Q_B$.
-  %\sayDR{We need to pin down this convention.}
+
+  We work with principal coefficients.
+  Write $\tilde{B}=(b_{ij})$ for the $2n\times n$ matrix obtained from $B$ by adjoining an $n\times n$ identity matrix as the last $n$ rows.
+  Call the matrix $B$ the \emph{principal part} of $\tilde{B}$.
 
   For $b\in\ZZ$, write $[b]_+=max(b,0)$.
-  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a matrix $E_{k,\varepsilon}=(e_{ij})$ with
+  Given a sign $\varepsilon\in\{\pm1\}$ and $k\in\{1,\ldots,n\}$, define a $2n\times 2n$ matrix $E_{k,\varepsilon}=(e_{ij})$ with
   \begin{equation}
@@
   \end{equation}
-  and a matrix $F_{k,\varepsilon}=(f_{ij})$ with
+  and an $n\times n$ matrix $F_{k,\varepsilon}=(f_{ij})$ with
   \begin{equation}
@@
 
-  The index $k\in\{1,\ldots,n\}$ also determines a new skew-symmetrizable matrix $\mu_k B=(b'_{ij})$ given by
+  The index $k\in\{1,\ldots,n\}$ also determines a new matrix $\mu_k \tilde{B}=(b'_{ij})$ given by
   \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
-  One easily observes that $\mu_k B$ is again skew-symmetrizable using the same matrix $D$.
+    One easily observes that the principal part of $\mu_k \tilde{B}$ is again skew-symmetrizable using the same matrix $D$.
   \begin{remark}
-    Note that $\mu_k B=E_{k,\varepsilon} B F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
+    Note that $\mu_k \tilde{B}=E_{k,\varepsilon} \tilde{B} F_{k,\varepsilon}$ for $\varepsilon=\pm 1$, the case $\varepsilon=1$ being obvious from the definitions and the case $\varepsilon=-1$ following from the identity $b_{ij}=[b_{ij}]_+-[-b_{ij}]_+$.
   \end{remark}
 
-  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate skew-symmetrizable matrices $B^t$ for $t\in\TT_n$ satisfying:
+  To record sequences of these matrix mutations, we introduce the labeled $n$-regular rooted tree $\TT_n$ with root vertex $t_0$ and associate $2n\times n$ matrices $\tilde{B}^t$ for $t\in\TT_n$ satisfying:
   \begin{itemize}
-    \item $B^{t_0}=B$;
-    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $B^{t'}=\mu_k B^t$.
+    \item $\tilde{B}^{t_0}=\tilde{B}$;
+    \item if $t,t'\in\TT_n$ are joined by an edge labeled $k$, then $\tilde{B}^{t'}=\mu_k \tilde{B}^t$.
   \end{itemize}
 
-  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
+  For $t\in\TT_n$ and $k\in\{1,\ldots,n\}$, define $\phi^t_k:\RR^{2n}\to\RR^{2n}$ as the piecewise-linear map
   \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
@@
     Suppose $t,t'\in\TT_n$ are joined by an edge labeled $k$.
-    If $\mu\in\lambda+\Col(B^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+    If $\mu\in\lambda+\Col(\tilde{B}^t)$, then $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(\tilde{B}^{t'})$.
   \end{lemma}
   \begin{proof}
-    Suppose $\mu=\lambda+B^t\alpha$ for some $\alpha\in\RR^n$.
+    Suppose $\mu=\lambda+\tilde{B}^t\alpha$ for some $\alpha\in\RR^n$.
     Let $\varepsilon$ (resp. $\varepsilon'$) be such that $\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu$ (resp. $\phi^t_k(\lambda)=E^t_{k,\varepsilon'}\lambda$).
     Then 
-    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+B^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} B^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + B^{t'} F^t_{k,\varepsilon}\alpha.\]
-    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + B^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+\tilde{B}^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} \tilde{B}^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + \tilde{B}^{t'} F^t_{k,\varepsilon}\alpha.\]
+    If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + \tilde{B}^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(\tilde{B}^{t'})$.
     Otherwise, 
-    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(B^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(B^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon B^{t'} \lambda_k \mathbf{e}_k\]
-    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(B^{t'})$.
+    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(\tilde{B}^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(\tilde{B}^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon \tilde{B}^{t'} \lambda_k \mathbf{e}_k\]
+    and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(\tilde{B}^{t'})$.
   \end{proof}
 
-  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
+  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^{2n}\to\RR^{2n}$ by
   \begin{itemize}
@@
 
-  Suppose $B$ is acyclic.
+  Suppose the principal part $B$ of $\tilde{B}$ is acyclic.
   Given a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, define a quiver $Q_{B,\varepsilon}$ from $Q_B$ by removing all arrows starting at vertex $i$ whenever $\varepsilon_i=-1$.
@@
     Let $A$ be an invertible $n\times n$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\bfr\bullet(\bfx-\lambda)\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[(A^{-T}\bfr)\bullet(\bfy-A\lambda)\le t.\]
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\langle\bfr,\bfx-\lambda\rangle\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[\langle A^{-T}\bfr,\bfy-A\lambda\rangle\le t.\]
   \end{lemma}
@@
     This is immediate from the equalities
-    \[\bfr\bullet(\bfx-\lambda)=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=(A^{-T}\bfr)\bullet(\bfy-A\lambda).\]
+    \[\langle\bfr,\bfx-\lambda\rangle=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=\langle A^{-T}\bfr,\bfy-A\lambda\rangle.\]
   \end{proof}

### 2022-06-12 software/domination.py

@@ -4,29 +4,55 @@ class DominanceOrder(SageObject):
     """
 
     def __init__(self, B):
-        self.B = copy(B)
-        self.A = ClusterAlgebra(B, principal_coefficients=True)
-        self.Aop = ClusterAlgebra(-B, principal_coefficients=True)
+        #B is n x n
+        self.n = B.ncols()
+        self.B = copy(B).stack(identity_matrix(self.n))
+        self.A = ClusterAlgebra(self.B, principal_coefficients=True)
+        self.Aop = ClusterAlgebra((-B).stack(identity_matrix(self.n)), principal_coefficients=True)
 
     def paths_up_to_length(self, k):
         paths = [ s.path_from_initial_seed() for s in self.A.seeds(mutating_F=False, depth=k) ]
         prefixes = [ p[:-1] for p in paths ]
         return [ p for p in paths if p not in prefixes ]
 
+    def cut_along_sequence(self, g, B, seq):
+        r"""
+        Return the intersection of the cones dominated by all the translates of g along the sequence of mutations seq
+        """
+        if len(g) == self.n:
+            g = tuple(g) + tuple([0 for _ in range(self.n)])
+        g = vector(g)
+        current_cone = Polyhedron(rays=B.columns(),base_ring=QQ).translation(g)
+        if seq == []:
+            return current_cone
+        k = seq.pop()
+        Hp = Polyhedron(ieqs=[(0,)*(k+1)+(1,)+(0,)*(2*self.n-k-1)])
+        Ep = matrix(2*self.n, lambda i,j: (1 if i == j else 0) if j != k else (max(B[i,k],0) if i != k else -1) )
+        Hm = Polyhedron(ieqs=[(0,)*(k+1)+(-1,)+(0,)*(2*self.n-k-1)])
+        Em = matrix(2*self.n, lambda i,j: (1 if i == j else 0) if j != k else (max(-B[i,k],0) if i != k else -1) )
+        new_g = (Ep if g in Hp else Em) * g
+        new_B = copy(B)
+        new_B.mutate(k)
+        polytope = self.cut_along_sequence(new_g, new_B, seq)
+        polytope_p = Em*(polytope.intersection(Hp))
+        polytope_m = Ep*(polytope.intersection(Hm))
+        polytope = polytope_p.convex_hull(polytope_m)
+        return polytope.intersection(current_cone)
+
     @cached_method(key=lambda self, g, depth: (tuple(g), depth))
     def dominated_polytope(self, g, depth):
[…]

### 2022-06-16 affine_dominance.tex
Section 4
Computed the c-vector part of the extended exchange matrix for all preprojective seeds

@@
 \newcommand{\bfc}{\boldsymbol{c}}
+\newcommand{\bfe}{\boldsymbol{e}}
 \newcommand{\bfg}{\boldsymbol{g}}
+\newcommand{\bfn}{\boldsymbol{n}}
 \newcommand{\bfr}{\boldsymbol{r}}
+\newcommand{\bfu}{\boldsymbol{u}}
 \newcommand{\bfx}{\boldsymbol{x}}
@@
   The index $k\in\{1,\ldots,n\}$ also determines a new matrix $\mu_k \tilde{B}=(b'_{ij})$ given by
-  \[ b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases} \]
+  \begin{equation}
+    \label{eq:matrix mutation}
+    b'_{ij}=\begin{cases} -b_{ij} & \text{if $i=k$ or $j=k$;}\\ b_{ij}+[b_{ik}]_+b_{kj}+b_{ik}[-b_{kj}]_+ & \text{otherwise.} \end{cases}
+  \end{equation}
     One easily observes that the principal part of $\mu_k \tilde{B}$ is again skew-symmetrizable using the same matrix $D$.
@@
 
+  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
+  \begin{definition}
+    For $\lambda\in\RR^n$, define the \emph{dominance region} 
+    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
+    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
+  \end{definition}
+  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
+  \begin{lemma}
+    The sets $\cP(\lambda)$ are polytopes.
+  \end{lemma}
+
+  \begin{lemma}
+    \label{le:transformed inequalities}
+    Let $A$ be an invertible $n\times n$ matrix.
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\langle\bfn,\bfx-\lambda\rangle\le t$ with $\lambda,\bfn\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[\langle A^{-T}\bfn,\bfy-A\lambda\rangle\le t.\]
+  \end{lemma}
+  \begin{proof}
+    This is immediate from the equalities
+    \[\langle\bfn,\bfx-\lambda\rangle=\bfn^T(\bfx-\lambda)=\bfn^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfn)^T(A\bfx-A\lambda)=\langle A^{-T}\bfn,\bfy-A\lambda\rangle.\]
+  \end{proof}
+
+  \section{Affine Types}
+  Associated to an acyclic skew-symmetrizable matrix $B=(b_{ij})$ there is a Cartan matrix $A=(a_{ij})$ with $a_{ii}=2$ and $a_{ij}=-|b_{ij}|$.
+  We say that $B$ is of affine type if its associated Cartan matrix gives rise to an affine Dynkin diagram.
+  In this section, we focus on understanding the dominance polytopes for affine matrices $B$.
+
+  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable matrix of affine type with associated Cartan matrix $A=(a_{ij})$.
+
+  \begin{lemma}
+    One column is always in the positive span of the other columns.
+  \end{lemma}
+
+  \begin{definition}
+    Describe imaginary $\bfg$-vectors and those corresponding to cluster monomials.
+  \end{definition}
+
+  \begin{lemma}
+    Let $\lambda\in\ZZ^n$ correspond to a cluster monomial.
+    Then $\cP(\lambda)=\{\lambda\}$.
+  \end{lemma}
+  \begin{proof}
+    An explicit sequence of sink/source mutations should suffice.
+  \end{proof}
+
+  \section{Attempts at understanding $\tau$}
+
   Suppose the principal part $B$ of $\tilde{B}$ is acyclic.
@@
   \[\wt_{i,\varepsilon}(p):=-b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}\prod_{t=1}^{r-1} b_{p_{t+1}p_t},\]
-  where the prefactor $b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}$ is omitted if $i=p_r$ or $\varepsilon_{p_r}=-1$.
+  where the prefactor of $b_{ip_r}$ is omitted if $i=p_r$ or $\varepsilon_{p_r}=-1$.
   \begin{lemma}
@@
 
-  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
-  \begin{definition}
-    For $\lambda\in\RR^n$, define the \emph{dominance region} 
-    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
-    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
-  \end{definition}
-  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
+\section{Iterated Mutations}
+
+  Let $B=(b_{ij})$ denote an acyclic $n\times n$ exchange matrix.
+  Write $Q_B$ for the corresponding quiver, here $b_{ij}>0$ means there is an arrow from $j$ to $i$ in $Q$.
+  Without loss of generality we assume $1,\ldots,n$ is a sink adapted sequence for $Q_B$, i.e. vertex $1$ is a sink and vertex $n$ is a source in $Q$.
+  This implies $B$ has positive entries above the diagonal.
+  \sayDR{This seemed to give the cleanest calculation.}
+  Define vectors $\bfc^{(k)}_r\in\ZZ^n$ for $1\le k\le n$ and $r\in\ZZ_{\ge0}$ recursively as follows:
+  \sayDR{A slight modification is needed to handle the opposite mutation sequence.}
+  \begin{itemize}
+    \item $\bfc^{(k)}_0=\bfe_k$ is the standard basis vector 
+    \item for $1\le \ell \le n$, we have $\bfc^{(k)}_{ns+\ell}=\begin{cases} -\bfc^{(k)}_{ns+\ell-1} & \text{if $\ell=k$;}\\ \bfc^{(k)}_{ns+\ell-1}+b_{\ell k}\bfc^{(\ell)}_{ns+\ell-1} & \text{if $\ell<k$;}\\ \bfc^{(k)}_{ns+\ell-1}-b_{\ell k}\bfc^{(\ell)}_{ns+\ell-1} & \text{if $\ell>k$.} \end{cases}$
+  \end{itemize}
+  For $r\in\ZZ$ and $1\le k\le n$, write $r\equiv_n k$ if $n|(r-k)$ and $r\not\equiv_n k$ otherwise.
   \begin{lemma}
-    The sets $\cP(\lambda)$ are polytopes.
+    \label{lem:tropical signs}
+    Assume $B$ is not finite-type.
+    For $r\in\ZZ_{\ge0}$, the vector $\bfc^{(k)}_r$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
   \end{lemma}
+  \begin{proof}
+    Induction?
+  \end{proof}
 
   \begin{lemma}
-    \label{le:transformed inequalities}
-    Let $A$ be an invertible $n\times n$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\langle\bfr,\bfx-\lambda\rangle\le t$ with $\lambda,\bfr\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[\langle A^{-T}\bfr,\bfy-A\lambda\rangle\le t.\]
+    For any $s\in\ZZ_{\ge0}$ and $0\le \ell \le n-1$, the matrix $\mu_\ell\cdots\mu_1(\mu_n\cdots\mu_1)^s\tilde B$ has principal part given by $(b'_{ij})$ where $b'_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(k)}_{ns+\ell}$ for $1\le k\le n$.
   \end{lemma}
   \begin{proof}
-    This is immediate from the equalities
-    \[\langle\bfr,\bfx-\lambda\rangle=\bfr^T(\bfx-\lambda)=\bfr^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfr)^T(A\bfx-A\lambda)=\langle A^{-T}\bfr,\bfy-A\lambda\rangle.\]
-  \end{proof}
+    We work by induction on $ns+\ell$.
+    For $s=\ell=0$, we just get $\tilde B$ and the claim clearly holds.
+    Assume the claim holds for a chosen $s$ and $\ell-1$, we show the claim holds for $s$ and $\ell$ (the case $\ell=n$ gives rise to the claim for $s+1$ and $\ell=0$).
+    Write $\tilde B'=\mu_{\ell-1}\cdots\mu_1(\mu_n\cdots\mu_1)^s\tilde B$ and let $Q'_B$ denote the corresponding acyclic quiver.
 
-  \section{Affine Types}
-  Associated to an acyclic skew-symmetrizable matrix $B=(b_{ij})$ there is a Cartan matrix $A=(a_{ij})$ with $a_{ii}=2$ and $a_{ij}=-|b_{ij}|$.
-  We say that $B$ is of affine type if its associated Cartan matrix gives rise to an affine Dynkin diagram.
-  In this section, we focus on understanding the dominance polytopes for affine matrices $B$.
-
-  Let $B=(b_{ij})$ be an $n\times n$ skew-symmetrizable matrix of affine type with associated Cartan matrix $A=(a_{ij})$.
-
-  \begin{lemma}
-    One column is always in the positive span of the other columns.
-  \end{lemma}
-
-  \begin{definition}
-    Describe imaginary $\bfg$-vectors and those corresponding to cluster monomials.
-  \end{definition}
-
-  \begin{lemma}
-    Let $\lambda\in\ZZ^n$ correspond to a cluster monomial.
-    Then $\cP(\lambda)=\{\lambda\}$.
-  \end{lemma}
-  \begin{proof}
-    An explicit sequence of sink/source mutations should suffice.
+    By \eqref{eq:matrix mutation}, the mutation $\mu_\ell$ reverses the sign of the $\ell$-th row and column of $\tilde B'$.
+    It follows that the principal part of $\mu_\ell\tilde B'$ is given as follows:
+    \begin{itemize}
+      \item if $i,j<\ell$, or $i<\ell$ and $j>\ell$, or $i<\ell$ and $j>\ell$, then $(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}=(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}$;
+      \item if $i=\ell$ or $j=\ell$, then $(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}=-(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}$;
+    \end{itemize}
+    in each case we obtain the desired expression.
+    In addition, we see that the $\ell$-th $\bfc$-vector is given by $-\bfc^{(\ell)}_{ns+\ell-1}=\bfc^{(\ell)}_{ns+\ell}$ as desired.
+    By Lemma~\ref{lem:tropical signs}, the $\ell$-th $\bfc$-vector of $\tilde B'$ is non-negative.  
+    Observe further that vertex $\ell$ is a sink in $Q'_B$ so that the $\ell$-th row of $\tilde B'$ has non-negative entries, in particular we see that $b'_{ij}=-b_{ij}$ for $j<\ell$ and $b'_{ij}=b_{ij}$ for $j>\ell$.
+    It then follows from \eqref{eq:matrix mutation} that the $k$-th $\bfc$-vector of $\mu_\ell\tilde B'$ is given by $\bfc^{(k)}_{ns+\ell-1}+b_{\ell k}\bfc^{(\ell)}_{ns+\ell-1}$ if $\ell<k$ and by $\bfc^{(k)}_{ns+\ell-1}-b_{\ell k}\bfc^{(\ell)}_{ns+\ell-1}$ if $\ell>k$.
+    Each of these is equal to $\bfc^{(k)}_{ns+\ell}$ as desired.
   \end{proof}

### 2022-06-16 dominance_regions.tex
darkgreen
Tony's edits

@@
 \newcommand{\bfg}{\boldsymbol{g}}
+\newcommand{\bfn}{\boldsymbol{n}}
 \newcommand{\bfr}{\boldsymbol{r}}
@@
 \newcommand{\kk}{\Bbbk}
+
+\definecolor{darkgreen}{rgb}{0,0.7,0}
 
@@
   In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
-  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance region} $\cP_\lambda$.
+  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance region} $\cP_\lambda$ (cf.
+Definition~\ref{def:dominance}).
   \begin{theorem}
@@
     \label{le:transformed inequalities}
-    Let $A$ be an invertible $2\times 2$ matrix.
-    Under the left action of $A$, say $A\mu=\mu'$ for $\mu,\mu'\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\langle\bfr,\mu\rangle \le t$ with $\bfr\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality
-    \[
-      \langle A^{-T}\bfr,\mu'\rangle\le t.
+    Let $M$ be an invertible $2\times 2$ matrix.
+    Under the left action of $M$, say $M\mu=\mu'$ for $\mu,\mu'\in\RR^2$, the region inside $\RR^2$ defined by the inequality $\langle\alpha,\mu\rangle \le t$ with $\alpha\in\RR^2$ and $t\in\RR$ is transformed into the region defined by the inequality
+    \[
+      \langle M^{-T}\alpha,\mu'\rangle\le t.
     \]
@@
     \[
-      \langle \bfr,\mu\rangle
+      \langle \alpha,\mu\rangle
       =
-      \bfr^T\mu
+      \alpha^T\mu
       =
-      \bfr^TA^{-1}A\mu
+      \alpha^TM^{-1}M\mu
       =
-      (A^{-T}\bfr)^TA\mu
+      (M^{-T}\alpha)^TM\mu
       =
-      \langle A^{-T}\bfr,\mu'\rangle.
+      \langle M^{-T}\alpha,\mu'\rangle.
     \]

### 2022-06-16 software/domination.py

@@ -37,6 +37,7 @@ class DominanceOrder(SageObject):
         polytope_p = Em*(polytope.intersection(Hp))
         polytope_m = Ep*(polytope.intersection(Hm))
         polytope = polytope_p.convex_hull(polytope_m)
+        return polytope
         return polytope.intersection(current_cone)
 
     @cached_method(key=lambda self, g, depth: (tuple(g), depth))

### 2022-06-19 affine_dominance.tex
Mutation matrices for g-vectors along the preprojective seeds

@@
   Write $Q_B$ for the corresponding quiver, here $b_{ij}>0$ means there is an arrow from $j$ to $i$ in $Q$.
+  \sayDR{Note that $Q_B$ is only recording the orientations of edges.}
   Without loss of generality we assume $1,\ldots,n$ is a sink adapted sequence for $Q_B$, i.e. vertex $1$ is a sink and vertex $n$ is a source in $Q$.
@@
 
+  Let $\TT_n$ denote the $n$-regular labeled tree with root vertex $t_0$.
+  Define vertices $t_r\in\TT_n$ for $r\in\ZZ$ by joining $t_{r-1}$ to $t_r$ by an edge labeled $\ell$ if $r\equiv_n\ell$.
+  Since $1,\ldots,n$ is sink adapted, this labels preprojective seeds by positive integers and postinjective seeds by negative integers.
+  Write $\tilde B^{t_r}$ for the extended exchange matrix associated to the seed at $t_r$.
   \begin{lemma}
-    For any $s\in\ZZ_{\ge0}$ and $0\le \ell \le n-1$, the matrix $\mu_\ell\cdots\mu_1(\mu_n\cdots\mu_1)^s\tilde B$ has principal part given by $(b'_{ij})$ where $b'_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(k)}_{ns+\ell}$ for $1\le k\le n$.
+    For $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le \ell \le n$, the matrix $\tilde B^{t_r}$ has principal part given by $b^{t_r}_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(k)}_r$ for $1\le k\le n$.
   \end{lemma}
@@
     For $s=\ell=0$, we just get $\tilde B$ and the claim clearly holds.
-    Assume the claim holds for a chosen $s$ and $\ell-1$, we show the claim holds for $s$ and $\ell$ (the case $\ell=n$ gives rise to the claim for $s+1$ and $\ell=0$).
-    Write $\tilde B'=\mu_{\ell-1}\cdots\mu_1(\mu_n\cdots\mu_1)^s\tilde B$ and let $Q'_B$ denote the corresponding acyclic quiver.
+    Assume the claim holds for $r-1$, we show the claim holds for $r$.
 
-    By \eqref{eq:matrix mutation}, the mutation $\mu_\ell$ reverses the sign of the $\ell$-th row and column of $\tilde B'$.
-    It follows that the principal part of $\mu_\ell\tilde B'$ is given as follows:
+    By \eqref{eq:matrix mutation}, the mutation $\mu_\ell$ reverses the sign of the $\ell$-th row and column of $\tilde B^{t_{r-1}}$.
+    It follows that the principal part of $\tilde B^{t_r}$ is given as follows:
     \begin{itemize}
-      \item if $i,j<\ell$, or $i<\ell$ and $j>\ell$, or $i<\ell$ and $j>\ell$, then $(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}=(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}$;
+      \item if $i,j<\ell$, or $i<\ell$ and $j>\ell$, or $i<\ell$ and $j>\ell$, then 
+        \[b^{t_r}_{ij}=b^{t_{r-1}}_{ij}=(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij};\]
       \item if $i=\ell$ or $j=\ell$, then $(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}=-(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}$;
+        \[b^{t_r}_{ij}=-b^{t_{r-1}}_{ij}=-(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij};\]
     \end{itemize}
     in each case we obtain the desired expression.
-    In addition, we see that the $\ell$-th $\bfc$-vector is given by $-\bfc^{(\ell)}_{ns+\ell-1}=\bfc^{(\ell)}_{ns+\ell}$ as desired.
-    By Lemma~\ref{lem:tropical signs}, the $\ell$-th $\bfc$-vector of $\tilde B'$ is non-negative.  
-    Observe further that vertex $\ell$ is a sink in $Q'_B$ so that the $\ell$-th row of $\tilde B'$ has non-negative entries, in particular we see that $b'_{ij}=-b_{ij}$ for $j<\ell$ and $b'_{ij}=b_{ij}$ for $j>\ell$.
-    It then follows from \eqref{eq:matrix mutation} that the $k$-th $\bfc$-vector of $\mu_\ell\tilde B'$ is given by $\bfc^{(k)}_{ns+\ell-1}+b_{\ell k}\bfc^{(\ell)}_{ns+\ell-1}$ if $\ell<k$ and by $\bfc^{(k)}_{ns+\ell-1}-b_{\ell k}\bfc^{(\ell)}_{ns+\ell-1}$ if $\ell>k$.
-    Each of these is equal to $\bfc^{(k)}_{ns+\ell}$ as desired.
+    In addition, we see that the $\ell$-th $\bfc$-vector is given by $-\bfc^{(\ell)}_{r-1}=\bfc^{(\ell)}_r$ as desired.
+
+    By Lemma~\ref{lem:tropical signs}, the $\ell$-th $\bfc$-vector of $\tilde B^{t_{r-1}}$ is non-negative.  
+    Observe further that vertex $\ell$ being a sink implies that the $\ell$-th row of $\tilde B^{t_{r-1}}$ has non-negative entries, in particular we see that $b^{t_{r-1}}_{\ell k}=b_{\ell k}$ for $\ell<k$ and $b^{t_{r-1}}_{\ell k}=-b_{\ell k}$ for $\ell>k$.
+    It then follows from \eqref{eq:matrix mutation} that the $k$-th $\bfc$-vector of $\tilde B^{t_r}$ is given by $\bfc^{(k)}_{r-1}+b_{\ell k}\bfc^{(\ell)}_{r-1}$ if $\ell<k$ and by $\bfc^{(k)}_{r-1}-b_{\ell k}\bfc^{(\ell)}_{r-1}$ if $\ell>k$.
+    Each of these is equal to $\bfc^{(k)}_r$ as desired.
   \end{proof}
 
+  It follows that we may write explicit expressions for the $2n\times 2n$ mutation matrices $E^{t_r}_{k,\varepsilon}$ for $r\ge0$.
+  Indeed, taking $r=ns+\ell$ with $1 \le \ell \le n$ we get $E^{t_r}_{k,\varepsilon}=(e^{t_r}_{ij})$ with
+  \begin{equation}
+    \label{eq:preprojective mutation matrices}
+    e^{t_r}_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ b_{ik} & \text{if $\varepsilon=+$ and $i<j=k\le\ell$ or $j=k\le\ell<i$ or $\ell<i<j=k$;}\\ -b_{ik} & \text{if $\varepsilon=-$ and $j=k<i\le\ell$ or $i\le\ell<j=k$ or $\ell<j=k<i$;} \\ 0 & \text{otherwise;} \end{cases}
+  \end{equation}
+
+  \[
+    \left[\begin{array}{cc|c|cccc}
+      0 & + & + & - & - & \cdots & -\\
+      - & 0 & + & - & - & \cdots & -\\
+      \hline
+      - & - & 0 & - & - & \cdots & -\\
+      \hline
+      + & + & + & 0 & + & \cdots & +\\
+      + & + & + & - & 0 & \cdots & +\\
+      \vdots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots\\
+      + & + & + & - & - & \cdots & 0
+    \end{array}\right]
+  \]
+  where the bottom $n$ entries in column $k$ are given as follows:
+  \begin{itemize}
+    \item if $\varepsilon=+$, we have $\bfc^{(k)}_r$ if $r\not\equiv_n k$ and zero otherwise;
+    \item if $\varepsilon=-$, we have $-\bfc^{(k)}_r$ if $r\equiv_n k$ and zero otherwise.
+  \end{itemize}
+
 \end{document}

### 2022-06-19 software/domination.py

@@ -40,6 +40,33 @@ class DominanceOrder(SageObject):
         return polytope
         return polytope.intersection(current_cone)
 
+    def cut_along_sequence(self, g, B, seq, return_steps=1000000):
+        r"""
+        Return the intersection of the cones dominated by all the translates of g along the sequence of mutations seq
+        """
+        if len(g) == self.n:
+            g = tuple(g) + tuple([0 for _ in range(self.n)])
+        g = vector(g)
+        current_cone = Polyhedron(rays=B.columns(),base_ring=QQ).translation(g)
+        if seq == []:
+            return return_steps, current_cone
+        k = seq.pop()
+        Hp = Polyhedron(ieqs=[(0,)*(k+1)+(1,)+(0,)*(2*self.n-k-1)])
+        Ep = matrix(2*self.n, lambda i,j: (1 if i == j else 0) if j != k else (max(B[i,k],0) if i != k else -1) )
+        Hm = Polyhedron(ieqs=[(0,)*(k+1)+(-1,)+(0,)*(2*self.n-k-1)])
+        Em = matrix(2*self.n, lambda i,j: (1 if i == j else 0) if j != k else (max(-B[i,k],0) if i != k else -1) )
+        new_g = (Ep if g in Hp else Em) * g
+        new_B = copy(B)
+        new_B.mutate(k)
+        remaining_steps, polytope = self.cut_along_sequence(new_g, new_B, seq, return_steps)
+        if remaining_steps > 0:
+            polytope_p = Em*(polytope.intersection(Hp))
+            polytope_m = Ep*(polytope.intersection(Hm))
+            polytope = polytope_p.convex_hull(polytope_m)
+            remaining_steps -= 1
+        return remaining_steps, polytope
+        return polytope.intersection(current_cone)
+
     @cached_method(key=lambda self, g, depth: (tuple(g), depth))
     def dominated_polytope(self, g, depth):
         paths = self.paths_up_to_length(depth)

### 2022-06-20 affine_dominance.tex
Some more thoughts in section 5

@@
   \sayDR{This seemed to give the cleanest calculation.}
-  Define vectors $\bfc^{(k)}_r\in\ZZ^n$ for $1\le k\le n$ and $r\in\ZZ_{\ge0}$ recursively as follows:
+  Define vectors $\bfc^{(r)}_k\in\ZZ^n$ for $1\le k\le n$ and $r\in\ZZ_{\ge0}$ recursively as follows:
   \sayDR{A slight modification is needed to handle the opposite mutation sequence.}
   \begin{itemize}
-    \item $\bfc^{(k)}_0=\bfe_k$ is the standard basis vector 
-    \item for $1\le \ell \le n$, we have $\bfc^{(k)}_{ns+\ell}=\begin{cases} -\bfc^{(k)}_{ns+\ell-1} & \text{if $\ell=k$;}\\ \bfc^{(k)}_{ns+\ell-1}+b_{\ell k}\bfc^{(\ell)}_{ns+\ell-1} & \text{if $\ell<k$;}\\ \bfc^{(k)}_{ns+\ell-1}-b_{\ell k}\bfc^{(\ell)}_{ns+\ell-1} & \text{if $\ell>k$.} \end{cases}$
+    \item $\bfc^{(0)}_k=\bfe_k$ is the standard basis vector 
+    \item for $r=ns+\ell$ with $1 \le \ell \le n$, we have $\bfc^{(r)}_k=\begin{cases} -\bfc^{(r-1)}_k & \text{if $\ell=k$;}\\ \bfc^{(r-1)}_k+b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell<k$;}\\ \bfc^{(r-1)}_k-b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell>k$.} \end{cases}$
   \end{itemize}
@@
     Assume $B$ is not finite-type.
-    For $r\in\ZZ_{\ge0}$, the vector $\bfc^{(k)}_r$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
+    For $r\in\ZZ_{\ge0}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
   \end{lemma}
@@
     Induction?
+  \end{proof}
+
+  \begin{lemma}
+    Consider $r=ns+\ell$ with $1\le\ell\le n$.
+    The limiting ray $\lim_{s\to\infty} \RR_{\ge0}\bfc^{(r)}_k$ is (up to sign) independent of $k$ and $\ell$ and is spanned by an eigenvector for $\tau$ acting on roots corresponding to the largest real eigenvalue (or maybe its inverse).
+  \end{lemma}
+  \begin{proof}
+    \cite{Tak94} should be relevant to this.
   \end{proof}
@@
   \begin{lemma}
-    For $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le \ell \le n$, the matrix $\tilde B^{t_r}$ has principal part given by $b^{t_r}_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(k)}_r$ for $1\le k\le n$.
+    \label{lem:preprojective exchange matrices}
+    For $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le \ell \le n$, the matrix $\tilde B^{t_r}$ has principal part given by $b^{t_r}_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(r)}_k$ for $1\le k\le n$.
   \end{lemma}
   \begin{proof}
-    We work by induction on $ns+\ell$.
-    For $s=\ell=0$, we just get $\tilde B$ and the claim clearly holds.
+    We work by induction on $r$.
+    For $r=0$, we just get $\tilde B$ and the claim clearly holds.
     Assume the claim holds for $r-1$, we show the claim holds for $r$.
 
+    Write $r=ns+\ell$ with $1 \le \ell \le n$.
+    Then $\tilde B^{t_r}$ is obtained from $\tilde B^{t_{r-1}}$ by mutation in direction $\ell$.
     By \eqref{eq:matrix mutation}, the mutation $\mu_\ell$ reverses the sign of the $\ell$-th row and column of $\tilde B^{t_{r-1}}$.
@@
     in each case we obtain the desired expression.
-    In addition, we see that the $\ell$-th $\bfc$-vector is given by $-\bfc^{(\ell)}_{r-1}=\bfc^{(\ell)}_r$ as desired.
+    In addition, we see that the $\ell$-th $\bfc$-vector is given by $-\bfc^{(r-1)}_\ell=\bfc^{(r)}_\ell$ as desired.
 
@@
     Observe further that vertex $\ell$ being a sink implies that the $\ell$-th row of $\tilde B^{t_{r-1}}$ has non-negative entries, in particular we see that $b^{t_{r-1}}_{\ell k}=b_{\ell k}$ for $\ell<k$ and $b^{t_{r-1}}_{\ell k}=-b_{\ell k}$ for $\ell>k$.
-    It then follows from \eqref{eq:matrix mutation} that the $k$-th $\bfc$-vector of $\tilde B^{t_r}$ is given by $\bfc^{(k)}_{r-1}+b_{\ell k}\bfc^{(\ell)}_{r-1}$ if $\ell<k$ and by $\bfc^{(k)}_{r-1}-b_{\ell k}\bfc^{(\ell)}_{r-1}$ if $\ell>k$.
-    Each of these is equal to $\bfc^{(k)}_r$ as desired.
+    It then follows from \eqref{eq:matrix mutation} that the $k$-th $\bfc$-vector of $\tilde B^{t_r}$ is given by $\bfc^{(r-1)}_k+b_{\ell k}\bfc^{(r-1)}_\ell$ if $\ell<k$ and by $\bfc^{(r-1)}_k-b_{\ell k}\bfc^{(r-1)}_\ell$ if $\ell>k$.
+    Each of these is equal to $\bfc^{(r)}_k$ as desired.
   \end{proof}
+
+  Following Lemma~\ref{lem:preprojective exchange matrices}, we identify $\bfc^{(r)}_k$ with the vector $(b^{t_r}_{ik})$ with $n+1\le i\le 2n$.
 
@@
   \end{equation}
+  where the bottom $n$ entries in column $k$ are given as follows:
+  \begin{itemize}
+    \item if $\varepsilon=+$, we have $\bfc^{(r)}_k$ if $r\not\equiv_n k$ and zero otherwise;
+    \item if $\varepsilon=-$, we have $-\bfc^{(r)}_k$ if $r\equiv_n k$ and zero otherwise.
+  \end{itemize}
 
@@
   \]
-  where the bottom $n$ entries in column $k$ are given as follows:
-  \begin{itemize}
-    \item if $\varepsilon=+$, we have $\bfc^{(k)}_r$ if $r\not\equiv_n k$ and zero otherwise;
-    \item if $\varepsilon=-$, we have $-\bfc^{(k)}_r$ if $r\equiv_n k$ and zero otherwise.
-  \end{itemize}
+
+  For $\lambda\in\ZZ^n$ and $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
+  \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
+  for a sequence of signs $\varepsilon_0,\ldots,\varepsilon_{r-1}$ depending on $\lambda$.
+  \begin{lemma}
+    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_j$ above is equal to $-$.
+    \sayDR{Can we use this as a definition of imaginary $\bfg$-vectors?}
+  \end{lemma}
+  \begin{proof}
+    With $1,\ldots,n$ being sink adapted, this choice gives the most complicated transformation at each step.
+    That should mean that $\lambda$ is sufficiently far from the initial chamber and remains there under all mutations.
+  \end{proof}
+
+\bibliographystyle{amsalpha}
+\bibliography{bibliography}
 

### 2022-06-20 affine_dominance.tex
Some more edits

@@
   For $\lambda\in\ZZ^n$ and $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
-  \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
+  \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
   for a sequence of signs $\varepsilon_0,\ldots,\varepsilon_{r-1}$ depending on $\lambda$.
@@
 
+  This would imply that the $\bfc$-vector part of every $E^{t_j}_{k,\varepsilon_j}$ vanishes by Lemma~\ref{lem:tropical signs}, can this be right?
+
 \bibliographystyle{amsalpha}

### 2022-06-21 affine_dominance.tex
An interesting observation at the end of section 5

@@
 
-  This would imply that the $\bfc$-vector part of every $E^{t_j}_{k,\varepsilon_j}$ vanishes by Lemma~\ref{lem:tropical signs}, can this be right?
+  \begin{lemma}
+    For any imaginary $\bfg$-vector $\lambda\in\ZZ^n$ and any source or sink adapted sequence of mutations, the coefficient part of  
+    \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
+    stabilizes after the first $n$ mutations.
+  \end{lemma}
+  \begin{proof}
+    If the sequence is sink adapted, the coefficient part is always just zero.
+
+    For a source adapted sequence, this should follow from an explicit calculation.
+  \end{proof}
 

### 2022-06-21 affine_dominance.tex
Small correction

@@
 
+  For a $\bfg$-vector $\lambda\in\ZZ^n$, write $\tilde\lambda\in\ZZ^{2n}$ for its extension by zeros.
   \begin{lemma}
     For any imaginary $\bfg$-vector $\lambda\in\ZZ^n$ and any source or sink adapted sequence of mutations, the coefficient part of
-    \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
+    \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \tilde\lambda\]
     stabilizes after the first $n$ mutations.

### 2022-06-22 affine_dominance.tex
Section 5 edits

@@
   \sayDR{This seemed to give the cleanest calculation.}
-  Define vectors $\bfc^{(r)}_k\in\ZZ^n$ for $1\le k\le n$ and $r\in\ZZ_{\ge0}$ recursively as follows:
-  \sayDR{A slight modification is needed to handle the opposite mutation sequence.}
+  Define vectors $\bfc^{(r)}_k\in\ZZ^n$ for $1\le k\le n$ and $r\in\ZZ$ recursively as follows:
   \begin{itemize}
-    \item $\bfc^{(0)}_k=\bfe_k$ is the standard basis vector 
-    \item for $r=ns+\ell$ with $1 \le \ell \le n$, we have $\bfc^{(r)}_k=\begin{cases} -\bfc^{(r-1)}_k & \text{if $\ell=k$;}\\ \bfc^{(r-1)}_k+b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell<k$;}\\ \bfc^{(r-1)}_k-b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell>k$.} \end{cases}$
+    \item for $-n\le r\le 0$, we have $\bfc^{(r)}_k=\bfe_k$ for $1\le k\le r+n$ and $\bfc^{(r)}_k=-\bfe_k$ for $r+n<k\le n$, where $\bfe_k
+      $ is the standard basis vector;
+    \item for $r=ns+\ell>0$ with $1 \le \ell \le n$, we have $\bfc^{(r)}_k=\begin{cases} -\bfc^{(r-1)}_k & \text{if $\ell=k$;}\\ \bfc^{(r-1)}_k+b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell<k$;}\\ \bfc^{(r-1)}_k-b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell>k$.} \end{cases}$
+    \item for $r=ns+\ell<-n$ with $1 \le \ell \le n$, we have $\bfc^{(r-1)}_k=\begin{cases} -\bfc^{(r)}_k & \text{if $\ell=k$;}\\ \bfc^{(r)}_k-b_{\ell k}\bfc^{(r)}_\ell & \text{if $\ell<k$;}\\ \bfc^{(r)}_k+b_{\ell k}\bfc^{(r)}_\ell & \text{if $\ell>k$.} \end{cases}$
   \end{itemize}
@@
     Assume $B$ is not finite-type.
-    For $r\in\ZZ_{\ge0}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
+    \begin{itemize}
+      \item For $r\in\ZZ_{>0}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
+      \item For $r\in\ZZ_{<-n}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\equiv_n k$ and non-positive when $r\not\equiv_n k$.
+    \end{itemize}
   \end{lemma}
   \begin{proof}
-    Induction?
+    Induction
   \end{proof}
@@
     Consider $r=ns+\ell$ with $1\le\ell\le n$.
-    The limiting ray $\lim_{s\to\infty} \RR_{\ge0}\bfc^{(r)}_k$ is (up to sign) independent of $k$ and $\ell$ and is spanned by an eigenvector for $\tau$ acting on roots corresponding to the largest real eigenvalue (or maybe its inverse).
+    The limiting rays $\lim_{s\to\infty} \RR_{\ge0}\bfc^{(r)}_k$ and $\lim_{s\to-\infty} \RR_{\ge0}\bfc^{(r)}_k$ are each (up to sign) independent of $k$ and $\ell$ and are spanned by eigenvectors for $\tau$ acting on roots corresponding to the largest real eigenvalue and its inverse.
   \end{lemma}
@@
     \label{lem:preprojective exchange matrices}
-    For $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le \ell \le n$, the matrix $\tilde B^{t_r}$ has principal part given by $b^{t_r}_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(r)}_k$ for $1\le k\le n$.
+    For $r\in\ZZ$ with $r=ns+\ell$ for $1\le \ell \le n$, the matrix $\tilde B^{t_r}$ has principal part given by $b^{t_r}_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(r)}_k$ for $1\le k\le n$.
   \end{lemma}
   \begin{proof}
-    We work by induction on $r$.
+    We work by upward and downward induction on $r$.
+    \sayDR{Downward case still needed}
     For $r=0$, we just get $\tilde B$ and the claim clearly holds.
@@
 
-  For $\lambda\in\ZZ^n$ and $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
-  \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
-  for a sequence of signs $\varepsilon_0,\ldots,\varepsilon_{r-1}$ depending on $\lambda$.
+  For $\lambda\in\ZZ^n$ and $r\in\ZZ_{>0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
+  \[E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda\]
+  for a sequence of signs $\varepsilon_1,\ldots,\varepsilon_r$ depending on $\lambda$.
+  Similarly, the tropical transformation $\phi_{t_{-r}}(\lambda)$ is given by
+  \[E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell-1}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-2}} E^{t_0}_{n,\varepsilon_{-1}} \lambda\]
+  for a sequence of signs $\varepsilon_{-1},\ldots,\varepsilon_{-r}$ depending on $\lambda$.
   \begin{lemma}
-    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_j$ above is equal to $-$.
-    \sayDR{Can we use this as a definition of imaginary $\bfg$-vectors?}
+    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_j$ with $j>0$ above is equal to $-$ and every sign $\varepsilon_j$ with $j<0$ above is equal to $+$.
   \end{lemma}
   \begin{proof}
-    With $1,\ldots,n$ being sink adapted, this choice gives the most complicated transformation at each step.
+    With $1,\ldots,n$ being sink adapted, these choices give the most complicated transformation at each step.
     That should mean that $\lambda$ is sufficiently far from the initial chamber and remains there under all mutations.
@@
   \begin{lemma}
-    For any imaginary $\bfg$-vector $\lambda\in\ZZ^n$ and any source or sink adapted sequence of mutations, the coefficient part of
-    \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \tilde\lambda\]
-    stabilizes after the first $n$ mutations.
+    Let $\lambda\in\ZZ^n$ be an imaginary $\bfg$-vector.
+    \begin{itemize}
+      \item For any $r\in\ZZ_{>0}$, the coefficient part of $\phi_{t_r}(\tilde\lambda)$ is just the zero vector.
+      \item For $1\le r\le n$, the coefficient part of  $\phi_{t_{-r}}(\tilde\lambda)$ is given by ...
+      \item For any $r\in\ZZ_{>n}$, the coefficient part of  $\phi_{t_{-r}}(\tilde\lambda)$ is independent of $r$ and is given by ...
+    \end{itemize}
   \end{lemma}

### 2022-06-24 affine_dominance.tex
Section 5 edits

@@
   For $t\in\TT_n$ and $k\in\{1,\ldots,n\}$, define $\phi^t_k:\RR^{2n}\to\RR^{2n}$ as the piecewise-linear map
-  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
+  \[
+    \phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}
+  \]
   where the entries of $E^t_{k,\varepsilon}$ are given by \eqref{eq:left mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
@@
     Then 
-    \[\phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+\tilde{B}^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} \tilde{B}^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + \tilde{B}^{t'} F^t_{k,\varepsilon}\alpha.\]
+    \[
+      \phi^t_k(\mu)=E^t_{k,\varepsilon}\mu=E^t_{k,\varepsilon}(\lambda+\tilde{B}^t\alpha)=E^t_{k,\varepsilon}\lambda + E^t_{k,\varepsilon} \tilde{B}^t F^t_{k,\varepsilon} F^t_{k,\varepsilon}\alpha=E^t_{k,\varepsilon}\lambda + \tilde{B}^{t'} F^t_{k,\varepsilon}\alpha.
+    \]
     If $\varepsilon'=\varepsilon$, this is equal to $\phi^t_k(\lambda) + \tilde{B}^{t'} F^t_{k,\varepsilon}\alpha$ and so $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(\tilde{B}^{t'})$.
     Otherwise, 
-    \[E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(\tilde{B}^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(\tilde{B}^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon \tilde{B}^{t'} \lambda_k \mathbf{e}_k\]
+    \[
+      E^t_{k,\varepsilon}\lambda=E^t_{k,\varepsilon'}\lambda+\varepsilon(\tilde{B}^t)^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon(\tilde{B}^{t'})^{\bullet k}\lambda=\phi^t_k(\lambda)-\varepsilon \tilde{B}^{t'} \lambda_k \mathbf{e}_k
+    \]
     and again we see that $\phi^t_k(\mu)\in\phi^t_k(\lambda)+\Col(\tilde{B}^{t'})$.
@@
     For $\lambda\in\RR^n$, define the \emph{dominance region} 
-    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
+    \[
+      \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda).
+    \]
     When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
@@
     Let $A$ be an invertible $n\times n$ matrix.
-    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\langle\bfn,\bfx-\lambda\rangle\le t$ with $\lambda,\bfn\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality \[\langle A^{-T}\bfn,\bfy-A\lambda\rangle\le t.\]
+    Under the left action of $A$, say $A\bfx=\bfy$ for $\bfx,\bfy\in\RR^n$, the region inside $\RR^n$ defined by the inequality $\langle\bfn,\bfx-\lambda\rangle\le t$ with $\lambda,\bfn\in\RR^n$ and $t\in\RR$ is transformed into the region defined by the inequality $\langle A^{-T}\bfn,\bfy-A\lambda\rangle\le t$.
   \end{lemma}
@@
     This is immediate from the equalities
-    \[\langle\bfn,\bfx-\lambda\rangle=\bfn^T(\bfx-\lambda)=\bfn^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfn)^T(A\bfx-A\lambda)=\langle A^{-T}\bfn,\bfy-A\lambda\rangle.\]
+    \[
+      \langle\bfn,\bfx-\lambda\rangle=\bfn^T(\bfx-\lambda)=\bfn^TA^{-1}A(\bfx-\lambda)=(A^{-T}\bfn)^T(A\bfx-A\lambda)=\langle A^{-T}\bfn,\bfy-A\lambda\rangle.
+    \]
   \end{proof}
@@
   Given a path $p\in\cP_j(Q_{B,\varepsilon})$, a vertex $i\in Q_0$, and a sequence of signs $\varepsilon=(\varepsilon_1,\ldots,\varepsilon_n)$, set
-  \[\wt_{i,\varepsilon}(p):=-b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}\prod_{t=1}^{r-1} b_{p_{t+1}p_t},\]
+  \[
+    \wt_{i,\varepsilon}(p):=-b_{ip_r}^{(1-\delta_{ip_r})(1+\varepsilon_{p_r})/2}\prod_{t=1}^{r-1} b_{p_{t+1}p_t},
+  \]
   where the prefactor of $b_{ip_r}$ is omitted if $i=p_r$ or $\varepsilon_{p_r}=-1$.
@@
       \item if $i,j<\ell$, or $i<\ell$ and $j>\ell$, or $i<\ell$ and $j>\ell$, then 
-        \[b^{t_r}_{ij}=b^{t_{r-1}}_{ij}=(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij};\]
+        \[
+          b^{t_r}_{ij}=b^{t_{r-1}}_{ij}=(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij};
+        \]
       \item if $i=\ell$ or $j=\ell$, then $(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}=-(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}$;
-        \[b^{t_r}_{ij}=-b^{t_{r-1}}_{ij}=-(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij};\]
+        \[
+          b^{t_r}_{ij}=-b^{t_{r-1}}_{ij}=-(-1)^{\epsilon(i,\ell-1)+\epsilon(j,\ell-1)}b_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij};
+        \]
     \end{itemize}
@@
     \end{array}\right]
+    \qquad
+    \left[\begin{array}{cccc|c|cc}
+      0 & \cdots & + & + & - & - & -\\
+      \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \vdots\\
+      - & \cdots & 0 & + & - & - & -\\
+      - & \cdots & - & 0 & - & - & -\\
+      \hline
+      + & \cdots & + & + & 0 & + & +\\
+      \hline
+      + & \cdots & + & + & - & 0 & +\\
+      +& \cdots & + & + & - & - & 0
+    \end{array}\right]
   \]
@@
   For $\lambda\in\ZZ^n$ and $r\in\ZZ_{>0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
-  \[E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda\]
+  \[
+    E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda
+  \]
   for a sequence of signs $\varepsilon_1,\ldots,\varepsilon_r$ depending on $\lambda$.
   Similarly, the tropical transformation $\phi_{t_{-r}}(\lambda)$ is given by
-  \[E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell-1}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-2}} E^{t_0}_{n,\varepsilon_{-1}} \lambda\]
+  \[
+    E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell-1}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-2}} E^{t_0}_{n,\varepsilon_{-1}} \lambda
+  \]
   for a sequence of signs $\varepsilon_{-1},\ldots,\varepsilon_{-r}$ depending on $\lambda$.
   \begin{lemma}
+    \label{lem:imaginary mutations}
     If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_j$ with $j>0$ above is equal to $-$ and every sign $\varepsilon_j$ with $j<0$ above is equal to $+$.
@@
   \begin{proof}
-    With $1,\ldots,n$ being sink adapted, these choices give the most complicated transformation at each step.
+    With $1,\ldots,n$ being sink adapted, these sign choices give the most complicated transformation at each step.
     That should mean that $\lambda$ is sufficiently far from the initial chamber and remains there under all mutations.
@@
     Let $\lambda\in\ZZ^n$ be an imaginary $\bfg$-vector.
+    For $r\in\ZZ$, write $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_{2n})$.
     \begin{itemize}
-      \item For any $r\in\ZZ_{>0}$, the coefficient part of $\phi_{t_r}(\tilde\lambda)$ is just the zero vector.
-      \item For $1\le r\le n$, the coefficient part of  $\phi_{t_{-r}}(\tilde\lambda)$ is given by ...
-      \item For any $r\in\ZZ_{>n}$, the coefficient part of  $\phi_{t_{-r}}(\tilde\lambda)$ is independent of $r$ and is given by ...
+      \item For any $r\ge0$, we have $\lambda'_{n+s}=0$ for $1\le s\le n$.
+      \item For $-n\le r\le -1$, we have $\lambda'_{n+s}=0$ for $1\le s\le n+r$ and \[\lambda'_{n+s}=\lambda_s+\sum\limits_{s<i_1<\cdots<i_m\le n} b_{si_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m}\]
+      for $n+r+1\le s\le n$.
+      \item For any $r<-n$, we have 
+        \[\lambda'_{n+s}=\lambda_s+\sum\limits_{s<i_1<\cdots<i_m\le n} b_{si_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m}\]
+        for $1\le s\le n$.
     \end{itemize}
@@
   \begin{proof}
-    If the sequence is sink adapted, the coefficient part is always just zero.
+    We work by induction on $r\in\ZZ_{\ge0}$.
+    For $r=0$, the claim is immediate from the definition of $\tilde\lambda$.
+    Following Lemma~\ref{lem:imaginary mutations}, for $r>0$ we have $\varepsilon_r=-$.
+    Writing $r=ns+\ell$, from Lemma~\ref{lem:tropical signs} and Lemma~\ref{lem:preprojective exchange matrices} we see that the $\ell$-th column of $\tilde B^{t_{r-1}}$ has $\bfc$-vector part given by $\bfc^{(r-1)}_\ell$ which is a positive vector.
+    It follows that the matrix $E^{t_{r-1}}_{\ell,\varepsilon_r}$ acts as the identity in the last $n$ components and the claim for $r$ follows from the claim for $r-1$.
 
-    For a source adapted sequence, this should follow from an explicit calculation.
+    An analogous argument shows that the coefficient part of $\phi_{t_{-r}}(\tilde\lambda)$ stabilizes for $r\in\ZZ_{>n}$.
+
   \end{proof}
+
+  For $1\le r\le n$, write $\phi_{t_{-r}}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_{2n})$.
+  Then we claim that
+  \[
+    \lambda'_s=
+    \begin{cases} 
+      \lambda_s+\sum\limits_{n-r<i_1<\cdots<i_m\le n} b_{si_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m} & \text{if $1\le s\le n-r$;}\\
+      -\lambda_s-\sum\limits_{n-r<i_1<\cdots<i_m\le n} b_{si_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m} & \text{if $n-r+1\le s\le n$;}\\
+      \lambda_{s-n}+\sum\limits_{s-n<i_1<\cdots<i_m\le n} b_{s-n,i_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m} & \text{if $2n-r+1\le s\le 2n$;}\\
+      0 & \text{if $n+1\le s\le 2n-r$.}
+    \end{cases}
+  \]
+
+  For $1\le r\le n$, write $\phi_{t_r}(\lambda)=(\lambda'_1,\ldots,\lambda'_n)$.
+  Then we claim that
+  \[
+    \lambda'_s=
+    \begin{cases} 
+      \lambda_s+\sum\limits_{1\le i_1<\cdots<i_m\le r} (-1)^m b_{si_m} \prod\limits_{p=2}^m b_{i_p i_{p-1}}\lambda_{i_1} & \text{if $r+1\le s\le n$;}\\
+      -\lambda_s-\sum\limits_{1\le i_1<\cdots<i_m\le r} (-1)^m b_{si_m} \prod\limits_{p=2}^m b_{i_pi_{p-1}}\lambda_{i_1} & \text{if $1\le s\le r$;}\\
+    \end{cases}
+  \]
 

### 2022-06-24 affine_dominance.tex
Section 5 edits

@@
     \label{lem:imaginary mutations}
-    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_j$ with $j>0$ above is equal to $-$ and every sign $\varepsilon_j$ with $j<0$ above is equal to $+$.
+    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_r$ with $r>0$ above is equal to $-$ and every sign $\varepsilon_r$ with $r<0$ above is equal to $+$.
   \end{lemma}
@@
 
+  Using this we explicitly compute the action of $\phi_{t_r}$ on imaginary $\bfg$-vectors. 
   For a $\bfg$-vector $\lambda\in\ZZ^n$, write $\tilde\lambda\in\ZZ^{2n}$ for its extension by zeros.
+  \begin{proposition}
+    Suppose $\lambda\in\ZZ^n$ is imaginary.
+    For $r\in\ZZ$, write $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_{2n})$.
+    Then the following hold:
+    \begin{itemize}
+      \item For $r>0$ with $r=ns+\ell$, we have (this is for $s=0$ so far)
+        \begin{equation}
+          \label{eq:positive g-vector mutations}
+          \lambda'_k=
+            \begin{cases} 
+              \lambda_k+\sum\limits_{1\le i_1<\cdots<i_m\le \ell} (-1)^m b_{ki_m} \prod\limits_{p=2}^m b_{i_p i_{p-1}}\lambda_{i_1} & \text{if $\ell+1\le k\le n$;}\\
+              -\lambda_k-\sum\limits_{1\le i_1<\cdots<i_m\le \ell} (-1)^m b_{ki_m} \prod\limits_{p=2}^m b_{i_pi_{p-1}}\lambda_{i_1} & \text{if $1\le k\le \ell$;}\\
+            \end{cases}
+        \end{equation}
+        and $\lambda'_{n+k}=0$ for $1\le k\le n$.
+      \item For $-n\le r\le -1$, we have $\lambda'_{n+k}=0$ for $1\le k\le n+r$ and \[\lambda'_{n+k}=\lambda_k+\sum\limits_{k<i_1<\cdots<i_m\le n} b_{ki_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m}\]
+      for $n+r+1\le k\le n$.
+      \item For any $r<-n$, we have 
+        \[\lambda'_{n+k}=\lambda_k+\sum\limits_{k<i_1<\cdots<i_m\le n} b_{ki_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m}\]
+        for $1\le k\le n$.
+    \end{itemize}
+
+  \end{proposition}
   \begin{lemma}

### 2022-06-26 affine_dominance.tex
This is gross, don't hate me Salvatore

--- 2022-06-24 affine_dominance.tex
@@
 
+  Using this we explicitly compute the action of $\phi_{t_r}$ on imaginary $\bfg$-vectors. 
   For a $\bfg$-vector $\lambda\in\ZZ^n$, write $\tilde\lambda\in\ZZ^{2n}$ for its extension by zeros.
-  \begin{lemma}
-    Let $\lambda\in\ZZ^n$ be an imaginary $\bfg$-vector.
+  \begin{proposition}
+    Suppose $\lambda\in\ZZ^n$ is imaginary.
     For $r\in\ZZ$, write $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_{2n})$.
+    Then the following hold:
     \begin{itemize}
-      \item For any $r\ge0$, we have $\lambda'_{n+s}=0$ for $1\le s\le n$.
-      \item For $-n\le r\le -1$, we have $\lambda'_{n+s}=0$ for $1\le s\le n+r$ and \[\lambda'_{n+s}=\lambda_s+\sum\limits_{s<i_1<\cdots<i_m\le n} b_{si_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m}\]
-      for $n+r+1\le s\le n$.
-      \item For any $r<-n$, we have 
-        \[\lambda'_{n+s}=\lambda_s+\sum\limits_{s<i_1<\cdots<i_m\le n} b_{si_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m}\]
-        for $1\le s\le n$.
+      \item For $r>0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have (this is for $s=0$ so far)
+        \begin{equation}
+          \label{eq:positive g-vector mutations}
+          \lambda'_k=
+          \begin{cases} 
+            -\lambda_k-\sum\limits_{1\le \ell^{(0)}_1<\cdots<\ell^{(0)}_{m_0}\le \ell} (-1)^{m_0} b_{k\ell^{(0)}_{m_0}} \prod\limits_{w=2}^{m_0} b_{\ell^{(0)}_w \ell^{(0)}_{w-1}}\lambda_{\ell^{(0)}_1} & \text{if $1\le k\le \ell$.}\\
+            \lambda_k+\sum\limits_{1\le \ell^{(0)}_1<\cdots<\ell^{(0)}_{m_0}\le \ell} (-1)^{m_0} b_{k\ell^{(0)}_{m_0}} \prod\limits_{w=2}^{m_0} b_{\ell^{(0)}_w \ell^{(0)}_{w-1}}\lambda_{\ell^{(0)}_1} & \text{if $\ell+1\le k\le n$;}
+          \end{cases}
+        \end{equation}
+        \[
+          -\lambda_k-\sum\limits_{1\le \ell^{(1)}_1<\cdots<\ell^{(1)}_{m_{1}}\le n} (-1)^{m_{1}} b_{k\ell^{(1)}_{m_{1}}} \prod\limits_{w=2}^{m_{1}} b_{\ell^{(1)}_w \ell^{(1)}_{w-1}}\lambda_{\ell^{(1)}_1}
+        \]
+        \[
+          -\lambda_{\ell^{(0)}_1}-\sum\limits_{1\le \ell^{(1)}_1<\cdots<\ell^{(1)}_{m_{1}}\le n} (-1)^{m_{1}} b_{\ell^{(0)}_1 \ell^{(1)}_{m_{1}}} \prod\limits_{w=2}^{m_{1}} b_{\ell^{(1)}_w \ell^{(1)}_{w-1}}\lambda_{\ell^{(1)}_1}
+        \]
+        and $\lambda'_{n+k}=0$ for $1\le k\le n$.
+        \begin{equation}
+          \label{eq:positive g-vector mutations}
+          (-1)^s\lambda'_k=
+          \begin{cases} 
+            -\lambda_k-\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{1\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le \ell\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big((-1)^{m_{v_p}} b_{\ell^{(v_{p-1})}_1 \ell^{(v_p)}_{m_{v_p}}} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_w \ell^{(v_p)}_{w-1}}\Big)\lambda_{\ell^{(v_q)}_1} & \text{if $1\le k\le \ell$.}\\
+            \lambda_k+\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{1\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le \ell\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big((-1)^{m_{v_p}} b_{\ell^{(v_{p-1})}_1 \ell^{(v_p)}_{m_{v_p}}} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_w \ell^{(v_p)}_{w-1}}\Big)\lambda_{\ell^{(v_q)}_1} & \text{if $\ell+1\le k\le n$;}
+          \end{cases}
+        \end{equation}
+        with the convention the $\ell^{(v_{-1})}_1=k$.
+      \item For $r<0$ with $r=ns+\ell-1$ for $1\le\ell\le n$, we have (this is for $s=-1$ so far)
+        \begin{align}
+          \label{eq:first negative g-vector mutations}
+          \lambda'_k &=
+          \begin{cases} 
+            \lambda_k+\sum\limits_{\ell\le \ell_1<\cdots<\ell_m\le n} b_{k\ell_1} \prod\limits_{p=2}^m b_{\ell_{p-1} \ell_p}\lambda_{\ell_m} & \text{if $1\le k\le \ell-1$;}\\
+            -\lambda_k-\sum\limits_{\ell\le \ell_1<\cdots<\ell_m\le n} b_{k\ell_1} \prod\limits_{p=2}^m b_{\ell_{p-1} \ell_p}\lambda_{\ell_m} & \text{if $\ell\le k\le n$;}
+          \end{cases}\\
+          \nonumber
+          \lambda'_{n+k} &=
+          \begin{cases}
+            0 & \text{if $s=-1$ and $1\le k\le \ell-1$;}\\
+            \lambda_k+\sum\limits_{k<\ell_1<\cdots<\ell_m\le n} b_{k\ell_1} \prod\limits_{p=2}^m b_{\ell_{p-1} \ell_p}\lambda_{\ell_m} & \text{if $s<-1$ or $s=-1$ and $\ell\le k\le n$;}
+          \end{cases}
+        \end{align}
+        for $1\le k\le n$.
     \end{itemize}
-  \end{lemma}
+  \end{proposition}
   \begin{proof}
-    We work by induction on $r\in\ZZ_{\ge0}$.
-    For $r=0$, the claim is immediate from the definition of $\tilde\lambda$.
+    We work by induction on $r$.
     Following Lemma~\ref{lem:imaginary mutations}, for $r>0$ we have $\varepsilon_r=-$.
-    Writing $r=ns+\ell$, from Lemma~\ref{lem:tropical signs} and Lemma~\ref{lem:preprojective exchange matrices} we see that the $\ell$-th column of $\tilde B^{t_{r-1}}$ has $\bfc$-vector part given by $\bfc^{(r-1)}_\ell$ which is a positive vector.
-    It follows that the matrix $E^{t_{r-1}}_{\ell,\varepsilon_r}$ acts as the identity in the last $n$ components and the claim for $r$ follows from the claim for $r-1$.
+    Writing $r=ns+\ell$, from Lemma~\ref{lem:preprojective exchange matrices} and Lemma~\ref{lem:tropical signs} we see that the $\ell$-th column of $\tilde B^{t_{r-1}}$ has the first $n$ entries non-positive and the last $n$ entries non-negative.
+    It follows that the matrix $E^{t_{r-1}}_{\ell,\varepsilon_r}$ always acts as the identity in the last $n$ components of $\tilde\lambda$ and we get that $\lambda'_{n+k}=0$ for $1\le k\le n$.
+    Moreover, writing $\phi_{t_{r-1}}(\tilde\lambda)=(\lambda''_1,\ldots,\lambda''_{2n})$ we also see from Lemma~\ref{lem:preprojective exchange matrices} that $\phi_{t_r}(\tilde\lambda)=E^{t_{r-1}}_{\ell,\varepsilon_r}\phi_{t_{r-1}}(\tilde\lambda)$ is given by
+    \[(\lambda''_1+b_{1\ell}\lambda''_\ell,\ldots,\lambda''_{\ell-1}+b_{\ell-1,\ell}\lambda''_\ell,-\lambda''_\ell,\lambda''_{\ell-1}-b_{\ell+1,\ell}\lambda''_\ell,\ldots,\lambda''_n-b_{n\ell}\lambda''_\ell,0,\ldots,0).\]
+    Iterating this, starting from $\ell=1$, we obtain the formula
+    \begin{equation}
+      \lambda'_k=
+      \begin{cases} 
+        -\lambda_k-\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $1\le k\le \ell$.}\\
+        \lambda_k+\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $\ell+1\le k\le n$;}
+      \end{cases}
+    \end{equation}
+    for $1\le k\le n$ when $s=0$.
 
-    An analogous argument shows that the coefficient part of $\phi_{t_{-r}}(\tilde\lambda)$ stabilizes for $r\in\ZZ_{>n}$.
+    An analogous argument shows that the coefficient part of $\phi_{t_r}(\tilde\lambda)$ stabilizes for $r\in\ZZ_{<-n}$.
 
   \end{proof}
-
-  For $1\le r\le n$, write $\phi_{t_{-r}}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_{2n})$.
-  Then we claim that
-  \[
-    \lambda'_s=
-    \begin{cases} 
-      \lambda_s+\sum\limits_{n-r<i_1<\cdots<i_m\le n} b_{si_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m} & \text{if $1\le s\le n-r$;}\\
-      -\lambda_s-\sum\limits_{n-r<i_1<\cdots<i_m\le n} b_{si_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m} & \text{if $n-r+1\le s\le n$;}\\
-      \lambda_{s-n}+\sum\limits_{s-n<i_1<\cdots<i_m\le n} b_{s-n,i_1} \prod\limits_{p=2}^m b_{i_{p-1}i_p}\lambda_{i_m} & \text{if $2n-r+1\le s\le 2n$;}\\
-      0 & \text{if $n+1\le s\le 2n-r$.}
-    \end{cases}
-  \]
-
-  For $1\le r\le n$, write $\phi_{t_r}(\lambda)=(\lambda'_1,\ldots,\lambda'_n)$.
-  Then we claim that
-  \[
-    \lambda'_s=
-    \begin{cases} 
-      \lambda_s+\sum\limits_{1\le i_1<\cdots<i_m\le r} (-1)^m b_{si_m} \prod\limits_{p=2}^m b_{i_p i_{p-1}}\lambda_{i_1} & \text{if $r+1\le s\le n$;}\\
-      -\lambda_s-\sum\limits_{1\le i_1<\cdots<i_m\le r} (-1)^m b_{si_m} \prod\limits_{p=2}^m b_{i_pi_{p-1}}\lambda_{i_1} & \text{if $1\le s\le r$;}\\
-    \end{cases}
-  \]
 

### 2022-06-30 affine_dominance.tex
Another ugly formula
Something much nicer

@@
         for $1\le k\le n$.
+        \begin{equation}
+          \label{eq:negative g-vector mutations}
+          (-1)^s\lambda'_k =
+          \begin{cases} 
+            \lambda_k+\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{\ell\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le n\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big( b_{\ell^{(v_{p-1})}_{m_{v_{p-1}}}\ell^{(v_p)}_1} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_{w-1} \ell^{(v_p)}_w} \Big)\lambda_{\ell^{(v_q)}_{m_{v_q}}} & \text{if $1\le k\le \ell-1$;}\\
+            -\lambda_k-\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{\ell\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le n\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big( b_{\ell^{(v_{p-1})}_{m_{v_{p-1}}}\ell^{(v_p)}_1} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_{w-1} \ell^{(v_p)}_w} \Big)\lambda_{\ell^{(v_q)}_{m_{v_q}}} & \text{if $\ell\le k\le n$;}
+          \end{cases}
+        \end{equation}
     \end{itemize}
@@
 
+  Define an infinite quiver $\widehat{Q}$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
+  \begin{itemize}
+    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
+    \item an arrow $(k,s+1)\to (\ell,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
+    \item an arrow $(k,s+1)\to (k,s)$ of weight $-1$ whenever $s\ge0$.
+  \end{itemize}
+  Given a path $p$ in $\widehat{Q}$, write $\wt(p)$ for the product of the weights along the arrows in $p$.
+  Let $i(p)$ and $t(p)$ denote the initial and terminal vertex along the path $p$.
+  Write $\hgt(p)$ for the largest $s$ appearing as the second component of a vertex along the path $p$.
+  Then for $r<0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have
+  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]
+
 \bibliographystyle{amsalpha}

### 2022-06-30 affine_dominance.tex
Modification

@@
 \newcommand{\sh}{{\operatorname{sh}}}
+\newcommand{\uleps}{{\underline{\varepsilon}}}
 \newcommand{\WA}{{W\!\!A}}
@@
 
-  Define an infinite quiver $\widehat{Q}$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
+  Given a sequence of signs $\uleps=(\varepsilon_1,\varepsilon_2,\ldots)$ with $\varepsilon_i\in\{\pm\}$, define an infinite quiver $\widehat{Q}_\uleps$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
   \begin{itemize}
-    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
-    \item an arrow $(k,s+1)\to (\ell,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
-    \item an arrow $(k,s+1)\to (k,s)$ of weight $-1$ whenever $s\ge0$.
+    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $k<\ell$, $s\ge0$, and $\varepsilon_{ns+\ell}=-$;
+    \item an arrow $(\ell,s+1)\to (k,s)$ of weight $-b_{k\ell}$ whenever $\ell<k$, $s\ge0$, and $\varepsilon_{ns+\ell}=-$;
+    \item an arrow $(\ell,s+1)\to (\ell,s)$ of weight $-1$ whenever $s\ge0$.
   \end{itemize}

### 2022-06-30 affine_dominance.tex
Better?

@@
 \newcommand{\Aut}{\operatorname{Aut}}
+\newcommand{\beps}{{\boldsymbol{\varepsilon}}}
 \newcommand{\Col}{\operatorname{Col}}
@@
 \newcommand{\sh}{{\operatorname{sh}}}
-\newcommand{\uleps}{{\underline{\varepsilon}}}
 \newcommand{\WA}{{W\!\!A}}
@@
 
-  Given a sequence of signs $\uleps=(\varepsilon_1,\varepsilon_2,\ldots)$ with $\varepsilon_i\in\{\pm\}$, define an infinite quiver $\widehat{Q}_\uleps$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
+  Given a sequence of signs $\beps=(\varepsilon_1,\varepsilon_2,\ldots)$ with $\varepsilon_i\in\{\pm\}$, define an infinite quiver $\widehat{Q}_\beps$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
   \begin{itemize}

### 2022-07-01 affine_dominance.tex
Change of conventions (lots of clean-up still needed), but Proposition 5.7 should now be correct as stated

--- 2022-06-30 affine_dominance.tex
@@
   \sayDR{Note that $Q_B$ is only recording the orientations of edges.}
-  Without loss of generality we assume $1,\ldots,n$ is a sink adapted sequence for $Q_B$, i.e. vertex $1$ is a sink and vertex $n$ is a source in $Q$.
-  This implies $B$ has positive entries above the diagonal.
-  \sayDR{This seemed to give the cleanest calculation.}
+  Without loss of generality, we assume $1,\ldots,n$ is a source adapted sequence for $Q_B$, i.e. vertex $1$ is a source and vertex $n$ is a sink in $Q$.
+  This implies $B$ has positive entries below the diagonal.
+  \sayDR{I changed back because of a stupid discrepancy between signs.}
   Define vectors $\bfc^{(r)}_k\in\ZZ^n$ for $1\le k\le n$ and $r\in\ZZ$ recursively as follows:
   \begin{itemize}
-    \item for $-n\le r\le 0$, we have $\bfc^{(r)}_k=\bfe_k$ for $1\le k\le r+n$ and $\bfc^{(r)}_k=-\bfe_k$ for $r+n<k\le n$, where $\bfe_k
-      $ is the standard basis vector;
-    \item for $r=ns+\ell>0$ with $1 \le \ell \le n$, we have $\bfc^{(r)}_k=\begin{cases} -\bfc^{(r-1)}_k & \text{if $\ell=k$;}\\ \bfc^{(r-1)}_k+b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell<k$;}\\ \bfc^{(r-1)}_k-b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell>k$.} \end{cases}$
-    \item for $r=ns+\ell<-n$ with $1 \le \ell \le n$, we have $\bfc^{(r-1)}_k=\begin{cases} -\bfc^{(r)}_k & \text{if $\ell=k$;}\\ \bfc^{(r)}_k-b_{\ell k}\bfc^{(r)}_\ell & \text{if $\ell<k$;}\\ \bfc^{(r)}_k+b_{\ell k}\bfc^{(r)}_\ell & \text{if $\ell>k$.} \end{cases}$
+    \item for $0\le r\le n$, we have $\bfc^{(r)}_k=-\bfe_k$ for $1\le k\le r$ and $\bfc^{(r)}_k=\bfe_k$ for $r<k\le n$, where $\bfe_k$ is the standard basis vector;
+    \item for $r=ns+\ell>n$ with $1 \le \ell \le n$, we have $\bfc^{(r)}_k=\begin{cases} -\bfc^{(r-1)}_k & \text{if $k=\ell$;}\\ \bfc^{(r-1)}_k-b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $k>\ell$;}\\ \bfc^{(r-1)}_k+b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $k<\ell$.} \end{cases}$
+    \item for $r=ns+\ell\le 0$ with $1 \le \ell \le n$, we have $\bfc^{(r-1)}_k=\begin{cases} -\bfc^{(r)}_k & \text{if $k=\ell$;}\\ \bfc^{(r)}_k-b_{\ell k}\bfc^{(r)}_\ell & \text{if $k>\ell$;}\\ \bfc^{(r)}_k+b_{\ell k}\bfc^{(r)}_\ell & \text{if $k<\ell$.} \end{cases}$
   \end{itemize}
+
   For $r\in\ZZ$ and $1\le k\le n$, write $r\equiv_n k$ if $n|(r-k)$ and $r\not\equiv_n k$ otherwise.
@@
     \begin{itemize}
-      \item For $r\in\ZZ_{>0}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
-      \item For $r\in\ZZ_{<-n}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\equiv_n k$ and non-positive when $r\not\equiv_n k$.
+      \item For $r\in\ZZ_{>n}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\equiv_n k$ and non-positive when $r\not\equiv_n k$.
+      \item For $r\in\ZZ_{<0}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
     \end{itemize}
@@
   Define vertices $t_r\in\TT_n$ for $r\in\ZZ$ by joining $t_{r-1}$ to $t_r$ by an edge labeled $\ell$ if $r\equiv_n\ell$.
-  Since $1,\ldots,n$ is sink adapted, this labels preprojective seeds by positive integers and postinjective seeds by negative integers.
+  Since $1,\ldots,n$ is source adapted, this labels preprojective seeds by negative integers and postinjective seeds by positive integers.
   Write $\tilde B^{t_r}$ for the extended exchange matrix associated to the seed at $t_r$.
   \begin{lemma}
-    \label{lem:preprojective exchange matrices}
+    \label{lem:transjective exchange matrices}
     For $r\in\ZZ$ with $r=ns+\ell$ for $1\le \ell \le n$, the matrix $\tilde B^{t_r}$ has principal part given by $b^{t_r}_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(r)}_k$ for $1\le k\le n$.
@@
 
+    ***The next part needs adjustment since the source-sink convention changed***
+
     By Lemma~\ref{lem:tropical signs}, the $\ell$-th $\bfc$-vector of $\tilde B^{t_{r-1}}$ is non-negative.  
@@
 
-  It follows that we may write explicit expressions for the $2n\times 2n$ mutation matrices $E^{t_r}_{k,\varepsilon}$ for $r\ge0$.
-  Indeed, taking $r=ns+\ell$ with $1 \le \ell \le n$ we get $E^{t_r}_{k,\varepsilon}=(e^{t_r}_{ij})$ with
+  It follows that we may write explicit expressions for the $2n\times 2n$ mutation matrices $E^{t_r}_{k,\varepsilon}$.
+  Indeed, taking $r=ns+\ell>n$ with $1 \le \ell \le n$ we get $E^{t_r}_{k,\varepsilon}=(e^{t_r}_{ij})$ with
   \begin{equation}
-    \label{eq:preprojective mutation matrices}
-    e^{t_r}_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ b_{ik} & \text{if $\varepsilon=+$ and $i<j=k\le\ell$ or $j=k\le\ell<i$ or $\ell<i<j=k$;}\\ -b_{ik} & \text{if $\varepsilon=-$ and $j=k<i\le\ell$ or $i\le\ell<j=k$ or $\ell<j=k<i$;} \\ 0 & \text{otherwise;} \end{cases}
+    \label{eq:postinjective mutation matrices}
+    e^{t_r}_{ij}=
+    \begin{cases}
+      1 & \text{if $i=j\ne k$;}\\
+      -1 & \text{if $i=j=k$;}\\
+      b_{ik} & \text{if $\varepsilon=-$ and $j=k\le\ell<i$;}\\
+      -b_{ik} & \text{if $\varepsilon=-$ and $i<j=k\le\ell$ or $\ell<i<j=k$;}\\
+      b_{ik} & \text{if $\varepsilon=+$ and $j=k<i\le\ell$ or $\ell<j=k<i$;}\\
+      -b_{ik} & \text{if $\varepsilon=+$ and $i\le\ell<j=k$;}\\
+      0 & \text{otherwise;}
+    \end{cases}
   \end{equation}
@@
   \begin{itemize}
-    \item if $\varepsilon=+$, we have $\bfc^{(r)}_k$ if $r\not\equiv_n k$ and zero otherwise;
-    \item if $\varepsilon=-$, we have $-\bfc^{(r)}_k$ if $r\equiv_n k$ and zero otherwise.
+    \item if $\varepsilon=+$, we have $\bfc^{(r)}_k$ if $r\equiv_n k$ and zero otherwise;
+    \item if $\varepsilon=-$, we have $-\bfc^{(r)}_k$ if $r\not\equiv_n k$ and zero otherwise.
   \end{itemize}
 
+  \begin{remark}
+  The result after mutation:
   \[
     \left[\begin{array}{cc|c|cccc}
-      0 & + & + & - & - & \cdots & -\\
-      - & 0 & + & - & - & \cdots & -\\
+      0 & - & - & + & + & \cdots & +\\
+      + & 0 & - & + & + & \cdots & +\\
       \hline
-      - & - & 0 & - & - & \cdots & -\\
+      + & + & 0 & + & + & \cdots & +\\
       \hline
-      + & + & + & 0 & + & \cdots & +\\
-      + & + & + & - & 0 & \cdots & +\\
+      - & - & - & 0 & - & \cdots & -\\
+      - & - & - & + & 0 & \cdots & -\\
       \vdots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots\\
-      + & + & + & - & - & \cdots & 0
+      - & - & - & + & + & \cdots & 0
     \end{array}\right]
@@
     \left[\begin{array}{cccc|c|cc}
-      0 & \cdots & + & + & - & - & -\\
+      0 & \cdots & - & - & + & + & +\\
       \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \vdots\\
-      - & \cdots & 0 & + & - & - & -\\
-      - & \cdots & - & 0 & - & - & -\\
+      + & \cdots & 0 & - & + & + & +\\
+      + & \cdots & + & 0 & + & + & +\\
       \hline
-      + & \cdots & + & + & 0 & + & +\\
+      - & \cdots & - & - & 0 & - & -\\
       \hline
-      + & \cdots & + & + & - & 0 & +\\
-      +& \cdots & + & + & - & - & 0
+      - & \cdots & - & - & + & 0 & -\\
+      - & \cdots & - & - & + & + & 0
     \end{array}\right]
   \]
+  \end{remark}
 
@@
     \label{lem:imaginary mutations}
-    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_r$ with $r>0$ above is equal to $-$ and every sign $\varepsilon_r$ with $r<0$ above is equal to $+$.
+    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_r$ with $r>0$ above is equal to $+$ and every sign $\varepsilon_r$ with $r<0$ above is equal to $-$.
   \end{lemma}
   \begin{proof}
-    With $1,\ldots,n$ being sink adapted, these sign choices give the most complicated transformation at each step.
+    With $1,\ldots,n$ being source adapted, these sign choices give the most complicated transformation at each step.
     That should mean that $\lambda$ is sufficiently far from the initial chamber and remains there under all mutations.
@@
 
-  Define an infinite quiver $\widehat{Q}$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
+  Given a sequence of signs $\beps=(\varepsilon_1,\varepsilon_2,\ldots,\varepsilon_r)$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(r)}_\beps$ with vertices $(\ell,s)\in [n]\times\ZZ_{\ge0}$ satisfying $ns+\ell\le n+r$ and having the following arrows:
   \begin{itemize}
-    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
-    \item an arrow $(k,s+1)\to (\ell,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
-    \item an arrow $(k,s+1)\to (k,s)$ of weight $-1$ whenever $s\ge0$.
+    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $\ell<k$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
+    \item an arrow $(\ell,s)\to (k,s+1)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
+    \item an arrow $(\ell,s)\to (\ell,s+1)$ of weight $-1$ whenever $ns+\ell\le r$.
   \end{itemize}
-  Given a path $p$ in $\widehat{Q}$, write $\wt(p)$ for the product of the weights along the arrows in $p$.
-  Let $i(p)$ and $t(p)$ denote the initial and terminal vertex along the path $p$.
-  Write $\hgt(p)$ for the largest $s$ appearing as the second component of a vertex along the path $p$.
+  For $1\le\ell\le r$, write $\hat{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ maximal.
+  Below we freely identify each vertex $(\ell,0)$ with $\ell$.
+
+  Given a path $\fp\subset Q^{(r)}_\beps$, write $\wt(\fp)$ for the product of the weights along the arrows in $\fp$.
+  Let $i(\fp)$ and $t(\fp)$ denote the initial and terminal vertex along the path $\fp$.
+  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$.
+  \begin{proposition}
+    Consider $r>0$ with $r=ns+\ell$ for $1\le\ell\le n$.
+    For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
+    \[
+      E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda
+    \]
+    with the signs $\beps=(\varepsilon_1,\cdots,\varepsilon_r)$ determined by $\lambda$.
+    Then
+    \[
+      \lambda'_k=\sum\limits_{\fp\subset Q^{(r)}_\beps, t(\fp)=\hat{k}} \wt(\fp)\lambda_{i(\fp)}.
+    \]
+    and $\lambda'_{n+k}=0$ for $1\le k\le n$ and $r<0$ if $\varepsilon_i=-$ for all $i$.
+    \sayDR{We need this for arbitrary sequences of signs and to include $r>0$.}
+  \end{proposition}
+  \begin{proof}
+    We work by induction on $r$.
+    Write $r=ns+\ell$.
+    From Lemma~\ref{lem:transjective exchange matrices} and Lemma~\ref{lem:tropical signs}, we see that the $\ell$-th column of $\tilde B^{t_{r-1}}$ has the first $n$ entries non-negative and the last $n$ entries non-positive.
+
+    Writing $\phi_{t_{r-1}}(\tilde\lambda)=(\lambda''_1,\ldots,\lambda''_{2n})$ we also see from Lemma~\ref{lem:transjective exchange matrices} that $\phi_{t_r}(\tilde\lambda)=E^{t_{r-1}}_{\ell,\varepsilon_r}\phi_{t_{r-1}}(\tilde\lambda)$ is given by
+    \[
+      \begin{cases}
+        (\lambda''_1-b_{1\ell}\lambda''_\ell,\ldots,\lambda''_{\ell-1}-b_{\ell-1,\ell}\lambda''_\ell,-\lambda''_\ell,\lambda''_{\ell+1}+b_{\ell+1,\ell}\lambda''_\ell,\ldots,\lambda''_n+b_{n\ell}\lambda''_\ell,\lambda''_{n+1},\ldots,\lambda''_{2n}) & \text{if $\varepsilon_r=+$;}\\
+        (\lambda''_1,\ldots,\lambda''_{\ell-1},-\lambda''_\ell,\lambda''_{\ell+1},\ldots,\lambda''_n,\lambda''_{n+1}-b^{t_{r-1}}_{n+1,\ell}\lambda''_\ell,\ldots,\lambda''_{2n}-b^{t_{r-1}}_{2n,\ell}\lambda''_\ell) & \text{if $\varepsilon_r=-$.}\\
+      \end{cases}
+    \]
+    Iterating this, starting from $\ell=1$, we obtain the formula
+    \begin{equation}
+      \lambda'_k=
+      \begin{cases} 
+        -\lambda_k-\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $1\le k\le \ell$.}\\
+        \lambda_k+\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $\ell+1\le k\le n$;}
+      \end{cases}
+    \end{equation}
+    for $1\le k\le n$ when $s=0$.
+  \end{proof}
+
   Then for $r<0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have
-  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]
+  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}_\beps\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]
 

### 2022-07-01 affine_dominance.tex
The quiver for negative mutations

@@
   \[
-    E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell-1}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-2}} E^{t_0}_{n,\varepsilon_{-1}} \lambda
+    E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r+1}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns+1}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-1}} E^{t_0}_{n,\varepsilon_0} \lambda
   \]
@@
 
-  Using this we explicitly compute the action of $\phi_{t_r}$ on imaginary $\bfg$-vectors. 
+  Using this we explicitly compute the action of $\phi_{t_r}$ on $\bfg$-vectors. 
   For a $\bfg$-vector $\lambda\in\ZZ^n$, write $\tilde\lambda\in\ZZ^{2n}$ for its extension by zeros.
-  \begin{proposition}
-    Suppose $\lambda\in\ZZ^n$ is imaginary.
-    For $r\in\ZZ$, write $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_{2n})$.
-    Then the following hold:
-    \begin{itemize}
-      \item For $r>0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have (this is for $s=0$ so far)
-        \begin{equation}
-          \label{eq:positive g-vector mutations}
-          \lambda'_k=
-          \begin{cases} 
-            -\lambda_k-\sum\limits_{1\le \ell^{(0)}_1<\cdots<\ell^{(0)}_{m_0}\le \ell} (-1)^{m_0} b_{k\ell^{(0)}_{m_0}} \prod\limits_{w=2}^{m_0} b_{\ell^{(0)}_w \ell^{(0)}_{w-1}}\lambda_{\ell^{(0)}_1} & \text{if $1\le k\le \ell$.}\\
-            \lambda_k+\sum\limits_{1\le \ell^{(0)}_1<\cdots<\ell^{(0)}_{m_0}\le \ell} (-1)^{m_0} b_{k\ell^{(0)}_{m_0}} \prod\limits_{w=2}^{m_0} b_{\ell^{(0)}_w \ell^{(0)}_{w-1}}\lambda_{\ell^{(0)}_1} & \text{if $\ell+1\le k\le n$;}
-          \end{cases}
-        \end{equation}
-        \[
-          -\lambda_k-\sum\limits_{1\le \ell^{(1)}_1<\cdots<\ell^{(1)}_{m_{1}}\le n} (-1)^{m_{1}} b_{k\ell^{(1)}_{m_{1}}} \prod\limits_{w=2}^{m_{1}} b_{\ell^{(1)}_w \ell^{(1)}_{w-1}}\lambda_{\ell^{(1)}_1}
-        \]
-        \[
-          -\lambda_{\ell^{(0)}_1}-\sum\limits_{1\le \ell^{(1)}_1<\cdots<\ell^{(1)}_{m_{1}}\le n} (-1)^{m_{1}} b_{\ell^{(0)}_1 \ell^{(1)}_{m_{1}}} \prod\limits_{w=2}^{m_{1}} b_{\ell^{(1)}_w \ell^{(1)}_{w-1}}\lambda_{\ell^{(1)}_1}
-        \]
-        and $\lambda'_{n+k}=0$ for $1\le k\le n$.
-        \begin{equation}
-          \label{eq:positive g-vector mutations}
-          (-1)^s\lambda'_k=
-          \begin{cases} 
-            -\lambda_k-\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{1\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le \ell\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big((-1)^{m_{v_p}} b_{\ell^{(v_{p-1})}_1 \ell^{(v_p)}_{m_{v_p}}} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_w \ell^{(v_p)}_{w-1}}\Big)\lambda_{\ell^{(v_q)}_1} & \text{if $1\le k\le \ell$.}\\
-            \lambda_k+\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{1\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le \ell\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big((-1)^{m_{v_p}} b_{\ell^{(v_{p-1})}_1 \ell^{(v_p)}_{m_{v_p}}} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_w \ell^{(v_p)}_{w-1}}\Big)\lambda_{\ell^{(v_q)}_1} & \text{if $\ell+1\le k\le n$;}
-          \end{cases}
-        \end{equation}
-        with the convention the $\ell^{(v_{-1})}_1=k$.
-      \item For $r<0$ with $r=ns+\ell-1$ for $1\le\ell\le n$, we have (this is for $s=-1$ so far)
-        \begin{align}
-          \label{eq:first negative g-vector mutations}
-          \lambda'_k &=
-          \begin{cases} 
-            \lambda_k+\sum\limits_{\ell\le \ell_1<\cdots<\ell_m\le n} b_{k\ell_1} \prod\limits_{p=2}^m b_{\ell_{p-1} \ell_p}\lambda_{\ell_m} & \text{if $1\le k\le \ell-1$;}\\
-            -\lambda_k-\sum\limits_{\ell\le \ell_1<\cdots<\ell_m\le n} b_{k\ell_1} \prod\limits_{p=2}^m b_{\ell_{p-1} \ell_p}\lambda_{\ell_m} & \text{if $\ell\le k\le n$;}
-          \end{cases}\\
-          \nonumber
-          \lambda'_{n+k} &=
-          \begin{cases}
-            0 & \text{if $s=-1$ and $1\le k\le \ell-1$;}\\
-            \lambda_k+\sum\limits_{k<\ell_1<\cdots<\ell_m\le n} b_{k\ell_1} \prod\limits_{p=2}^m b_{\ell_{p-1} \ell_p}\lambda_{\ell_m} & \text{if $s<-1$ or $s=-1$ and $\ell\le k\le n$;}
-          \end{cases}
-        \end{align}
-        for $1\le k\le n$.
-        \begin{equation}
-          \label{eq:negative g-vector mutations}
-          (-1)^s\lambda'_k =
-          \begin{cases} 
-            \lambda_k+\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{\ell\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le n\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big( b_{\ell^{(v_{p-1})}_{m_{v_{p-1}}}\ell^{(v_p)}_1} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_{w-1} \ell^{(v_p)}_w} \Big)\lambda_{\ell^{(v_q)}_{m_{v_q}}} & \text{if $1\le k\le \ell-1$;}\\
-            -\lambda_k-\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{\ell\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le n\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big( b_{\ell^{(v_{p-1})}_{m_{v_{p-1}}}\ell^{(v_p)}_1} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_{w-1} \ell^{(v_p)}_w} \Big)\lambda_{\ell^{(v_q)}_{m_{v_q}}} & \text{if $\ell\le k\le n$;}
-          \end{cases}
-        \end{equation}
-    \end{itemize}
-  \end{proposition}
-  \begin{proof}
-    We work by induction on $r$.
-    Following Lemma~\ref{lem:imaginary mutations}, for $r>0$ we have $\varepsilon_r=-$.
-    Writing $r=ns+\ell$, from Lemma~\ref{lem:preprojective exchange matrices} and Lemma~\ref{lem:tropical signs} we see that the $\ell$-th column of $\tilde B^{t_{r-1}}$ has the first $n$ entries non-positive and the last $n$ entries non-negative.
-    It follows that the matrix $E^{t_{r-1}}_{\ell,\varepsilon_r}$ always acts as the identity in the last $n$ components of $\tilde\lambda$ and we get that $\lambda'_{n+k}=0$ for $1\le k\le n$.
-    Moreover, writing $\phi_{t_{r-1}}(\tilde\lambda)=(\lambda''_1,\ldots,\lambda''_{2n})$ we also see from Lemma~\ref{lem:preprojective exchange matrices} that $\phi_{t_r}(\tilde\lambda)=E^{t_{r-1}}_{\ell,\varepsilon_r}\phi_{t_{r-1}}(\tilde\lambda)$ is given by
-    \[(\lambda''_1+b_{1\ell}\lambda''_\ell,\ldots,\lambda''_{\ell-1}+b_{\ell-1,\ell}\lambda''_\ell,-\lambda''_\ell,\lambda''_{\ell-1}-b_{\ell+1,\ell}\lambda''_\ell,\ldots,\lambda''_n-b_{n\ell}\lambda''_\ell,0,\ldots,0).\]
-    Iterating this, starting from $\ell=1$, we obtain the formula
-    \begin{equation}
-      \lambda'_k=
-      \begin{cases} 
-        -\lambda_k-\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $1\le k\le \ell$.}\\
-        \lambda_k+\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $\ell+1\le k\le n$;}
-      \end{cases}
-    \end{equation}
-    for $1\le k\le n$ when $s=0$.
-
-    An analogous argument shows that the coefficient part of $\phi_{t_r}(\tilde\lambda)$ stabilizes for $r\in\ZZ_{<-n}$.
-
-  \end{proof}
 
@@
   For $1\le\ell\le r$, write $\hat{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ maximal.
-  Below we freely identify each vertex $(\ell,0)$ with $\ell$.
+  Below we freely identify each vertex $(\ell,0)$ with $\ell$ itself.
+
+  Given a sequence of signs $\beps=(\varepsilon_0,\varepsilon_{-1},\varepsilon_{-2},\ldots,\varepsilon_{-r+1})$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(-r)}_\beps$ with vertices $(\ell,s)\in [n]\times\ZZ_{<0}$ satisfying $-n-r<ns+\ell$ and having the following arrows:
+  \begin{itemize}
+    \item an arrow $(\ell,s)\to (k,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
+    \item an arrow $(\ell,s)\to (k,s+1)$ of weight $b_{k\ell}$ whenever $\ell<k$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
+    \item an arrow $(\ell,s)\to (\ell,s-1)$ of weight $-1$ whenever $-r<ns+\ell$.
+  \end{itemize}
+  For $1\le\ell\le r$, write $\check{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ minimal.
+  Below we freely identify each vertex $(\ell,-1)$ with $\ell$ itself.
 
@@
     with the signs $\beps=(\varepsilon_1,\cdots,\varepsilon_r)$ determined by $\lambda$.
-    Then
+    Then for $1\le k\le n$ we have
     \[
@@
     \]
-    and $\lambda'_{n+k}=0$ for $1\le k\le n$ and $r<0$ if $\varepsilon_i=-$ for all $i$.
+    and $\lambda'_{n+k}=0$ if $r<0$ and $\varepsilon_i=-$ for all $i$.
     \sayDR{We need this for arbitrary sequences of signs and to include $r>0$.}

### 2022-07-01 affine_dominance.tex
Some cleanup and improved Prop. 5.6

@@
 
-  Given a path $\fp\subset Q^{(r)}_\beps$, write $\wt(\fp)$ for the product of the weights along the arrows in $\fp$.
+  Given a path $\fp\subset Q^{(\pm r)}_\beps$, write $\wt(\fp)$ for the product of the weights along the arrows in $\fp$.
   Let $i(\fp)$ and $t(\fp)$ denote the initial and terminal vertex along the path $\fp$.
-  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$.
+  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$ and paths $\fp\subset Q^{(-r)}_\beps$ with $i(\fp)=(\ell,-1)$ for some $\ell$.
   \begin{proposition}
     Consider $r>0$ with $r=ns+\ell$ for $1\le\ell\le n$.
-    For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
+    \begin{enumerate}
+      \item For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
         \[
@@
         \[
-      \lambda'_k=\sum\limits_{\fp\subset Q^{(r)}_\beps, t(\fp)=\hat{k}} \wt(\fp)\lambda_{i(\fp)}.
+          \lambda'_k=\sum\limits_{\fp\subset Q^{(r)}_\beps\!,\, t(\fp)=\hat{k}} \wt(\fp)\lambda_{i(\fp)}.
         \]
-    and $\lambda'_{n+k}=0$ if $r<0$ and $\varepsilon_i=-$ for all $i$.
-    \sayDR{We need this for arbitrary sequences of signs and to include $r>0$.}
+      \sayDR{We still need to deal with extended $\bfg$-vectors.}
+      \item For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_{-r}}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
+        \[
+          E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r+1}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns+1}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-1}} E^{t_0}_{n,\varepsilon_0} \lambda
+        \]
+        with the signs $\beps=(\varepsilon_0,\varepsilon_{-1},\cdots,\varepsilon_{-r+1})$ determined by $\lambda$.
+        Then for $1\le k\le n$ we have
+        \[
+          \lambda'_k=\sum\limits_{\fp\subset Q^{(-r)}_\beps\!,\, t(\fp)=\check{k}} \wt(\fp)\lambda_{i(\fp)}.
+        \]
+    \end{enumerate}
   \end{proposition}
@@
     \]
-    Iterating this, starting from $\ell=1$, we obtain the formula
-    \begin{equation}
-      \lambda'_k=
-      \begin{cases} 
-        -\lambda_k-\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $1\le k\le \ell$.}\\
-        \lambda_k+\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $\ell+1\le k\le n$;}
-      \end{cases}
-    \end{equation}
-    for $1\le k\le n$ when $s=0$.
   \end{proof}
-
-  Then for $r<0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have
-  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}_\beps\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]
 

### 2022-07-02 affine_dominance.tex
Typo
Incorporated extended g-vectors into Prop 5.6

@@
 \newcommand{\sh}{{\operatorname{sh}}}
+\newcommand{\sgn}{{\operatorname{sgn}}}
 \newcommand{\WA}{{W\!\!A}}
@@
 
-  Given a sequence of signs $\beps=(\varepsilon_1,\varepsilon_2,\ldots,\varepsilon_r)$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(r)}_\beps$ with vertices $(\ell,s)\in [n]\times\ZZ_{\ge0}$ satisfying $ns+\ell\le n+r$ and having the following arrows:
+  Given a sequence of signs $\beps=(\varepsilon_1,\varepsilon_2,\ldots,\varepsilon_r)$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(r)}_\beps$ with vertices 
+  \[\{(\ell,s)\in [n]\times\ZZ_{\ge0}:ns+\ell\le n+r\}\cup\{k:n+1\le k\le 2n\}\]
+  and having the following arrows:
   \begin{itemize}
@@
     \item an arrow $(\ell,s)\to (k,s+1)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
-    \item an arrow $(\ell,s)\to (\ell,s+1)$ of weight $-1$ whenever $ns+\ell\le r$.
+    \item an arrow $(\ell,s)\to (\ell,s+1)$ of weight $-1$ whenever $ns+\ell\le r$;
+    \item an arrow $(\ell,s)\to k$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
   \end{itemize}
   For $1\le\ell\le r$, write $\hat{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ maximal.
+  For $n+1\le k\le 2n$, $\hat{k}=k$.
   Below we freely identify each vertex $(\ell,0)$ with $\ell$ itself.
 
-  Given a sequence of signs $\beps=(\varepsilon_0,\varepsilon_{-1},\varepsilon_{-2},\ldots,\varepsilon_{-r+1})$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(-r)}_\beps$ with vertices $(\ell,s)\in [n]\times\ZZ_{<0}$ satisfying $-n-r<ns+\ell$ and having the following arrows:
+  Given a sequence of signs $\beps=(\varepsilon_0,\varepsilon_{-1},\varepsilon_{-2},\ldots,\varepsilon_{-r+1})$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(-r)}_\beps$ with vertices 
+  \[\{(\ell,s)\in [n]\times\ZZ_{<0}:-n-r<ns+\ell\}\cup\{k:n+1\le k\le 2n\}\]
+  and having the following arrows:
   \begin{itemize}
     \item an arrow $(\ell,s)\to (k,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
-    \item an arrow $(\ell,s)\to (k,s+1)$ of weight $b_{k\ell}$ whenever $\ell<k$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
+    \item an arrow $(\ell,s)\to (k,s-1)$ of weight $b_{k\ell}$ whenever $\ell<k$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
     \item an arrow $(\ell,s)\to (\ell,s-1)$ of weight $-1$ whenever $-r<ns+\ell$.
+    \item an arrow $(\ell,s)\to k$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
   \end{itemize}
   For $1\le\ell\le r$, write $\check{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ minimal.
+  For $n+1\le k\le 2n$, $\check{k}=k$.
   Below we freely identify each vertex $(\ell,-1)$ with $\ell$ itself.
@@
   Let $i(\fp)$ and $t(\fp)$ denote the initial and terminal vertex along the path $\fp$.
-  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$ and paths $\fp\subset Q^{(-r)}_\beps$ with $i(\fp)=(\ell,-1)$ for some $\ell$.
+  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$ and paths $\fp\subset Q^{(-r)}_\beps$ with $i(\fp)=(\ell,-1)$ for some $\ell$ or paths with $i(\fp)=k$ for some $n+1\le k\le 2n$.
   \begin{proposition}
@@
         with the signs $\beps=(\varepsilon_1,\cdots,\varepsilon_r)$ determined by $\lambda$.
-        Then for $1\le k\le n$ we have
+        Then, for $1\le k\le 2n$, we have
         \[
@@
         \]
-      \sayDR{We still need to deal with extended $\bfg$-vectors.}
       \item For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_{-r}}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
@@
         with the signs $\beps=(\varepsilon_0,\varepsilon_{-1},\cdots,\varepsilon_{-r+1})$ determined by $\lambda$.
-        Then for $1\le k\le n$ we have
+        Then, for $1\le k\le 2n$, we have
         \[

### 2022-07-02 affine_dominance.tex
Slight modification for uniformity

@@
   Given a sequence of signs $\beps=(\varepsilon_1,\varepsilon_2,\ldots,\varepsilon_r)$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(r)}_\beps$ with vertices 
-  \[\{(\ell,s)\in [n]\times\ZZ_{\ge0}:ns+\ell\le n+r\}\cup\{k:n+1\le k\le 2n\}\]
+  \[\{(\ell,s)\in [n]\times\ZZ_{\ge0}:ns+\ell\le n+r\}\cup\{(n+k,0):1\le k\le n\}\]
   and having the following arrows:
@@
     \item an arrow $(\ell,s)\to (\ell,s+1)$ of weight $-1$ whenever $ns+\ell\le r$;
-    \item an arrow $(\ell,s)\to k$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
+    \item an arrow $(\ell,s)\to (n+k,0)$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
   \end{itemize}
   For $1\le\ell\le r$, write $\hat{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ maximal.
-  For $n+1\le k\le 2n$, $\hat{k}=k$.
   Below we freely identify each vertex $(\ell,0)$ with $\ell$ itself.
@@
   Given a sequence of signs $\beps=(\varepsilon_0,\varepsilon_{-1},\varepsilon_{-2},\ldots,\varepsilon_{-r+1})$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(-r)}_\beps$ with vertices 
-  \[\{(\ell,s)\in [n]\times\ZZ_{<0}:-n-r<ns+\ell\}\cup\{k:n+1\le k\le 2n\}\]
+  \[\{(\ell,s)\in [n]\times\ZZ_{<0}:-n-r<ns+\ell\}\cup\{(n+k,-1):1\le k\le n\}\]
   and having the following arrows:
@@
     \item an arrow $(\ell,s)\to (\ell,s-1)$ of weight $-1$ whenever $-r<ns+\ell$.
-    \item an arrow $(\ell,s)\to k$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
+    \item an arrow $(\ell,s)\to (n+k,-1)$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
   \end{itemize}
   For $1\le\ell\le r$, write $\check{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ minimal.
-  For $n+1\le k\le 2n$, $\check{k}=k$.
   Below we freely identify each vertex $(\ell,-1)$ with $\ell$ itself.
@@
   Let $i(\fp)$ and $t(\fp)$ denote the initial and terminal vertex along the path $\fp$.
-  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$ and paths $\fp\subset Q^{(-r)}_\beps$ with $i(\fp)=(\ell,-1)$ for some $\ell$ or paths with $i(\fp)=k$ for some $n+1\le k\le 2n$.
+  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$ and paths $\fp\subset Q^{(-r)}_\beps$ with $i(\fp)=(\ell,-1)$ for some $\ell$.
   \begin{proposition}

### 2022-07-09 dominance_regions.tex
Fixed a typo

@@
 
-  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $n>0$, there exists a positive scalar $\nu$ so that $\phi(\lambda)=\nu\lambda$.
+  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that there exists a positive scalar $\nu$ so that $\phi(\lambda)=\nu\lambda$.
   \begin{lemma}

### 2022-08-02 Annals of Combinatorics/submission.tex
Copied our text into their template

--- 2022-07-09 dominance_regions.tex
@@
-\documentclass{amsart}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing
+
+%%=======================================================%%
+%% to print line numbers in the margin use lineno option %%
+%%=======================================================%%
+
+%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%======================================================%%
+%% to compile with pdflatex/xelatex use pdflatex option %%
+%%======================================================%%
+
+%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+\documentclass[pdflatex,sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
+%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
+%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
+%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
+%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
+%%\documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
+%%\documentclass[default]{sn-jnl}% Default
+%%\documentclass[default,iicol]{sn-jnl}% Default with double column layout
+
+%%%% Standard Packages
 \usepackage{amsmath}
@@
 \usepackage{color}
-\usepackage[margin=1in]{geometry}
 \usepackage{tikz}
@@
 \usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
-
-\newtheorem{theorem}{Theorem}
+%%%%
+
+%%%%%=============================================================================%%%%
+%%%%  Remarks: This template is provided to aid authors with the preparation
+%%%%  of original research articles intended for submission to journals published 
+%%%%  by Springer Nature. The guidance has been prepared in partnership with 
+%%%%  production teams to conform to Springer Nature technical requirements. 
+%%%%  Editorial and presentation requirements differ among journal portfolios and 
+%%%%  research disciplines. You may find sections in this template are irrelevant 
+%%%%  to your work and are empowered to omit any such section if allowed by the 
+%%%%  journal you intend to submit to. The submission guidelines and policies 
+%%%%  of the journal take precedence. A detailed User Manual is available in the 
+%%%%  template package for technical guidance.
+%%%%%=============================================================================%%%%
+
+\jyear{2021}%
+
+%% as per the requirement new theorem styles can be included as shown below
+\theoremstyle{thmstyleone}%
+\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
 \newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
 \newtheorem{lemma}[theorem]{Lemma}
 \newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{question}{Question}
-
-\numberwithin{theorem}{section}
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+
+\theoremstyle{thmstyletwo}%
+\newtheorem{remark}[theorem]{Remark}%
+
+\theoremstyle{thmstylethree}%
+\newtheorem{definition}[theorem]{Definition}
+
+\raggedbottom
+%%\unnumbered% uncomment this for unnumbered level heads
 
 \newcommand{\bfa}{\boldsymbol{a}}
-\newcommand{\bfc}{\boldsymbol{c}}
 \newcommand{\bfg}{\boldsymbol{g}}
-\newcommand{\bfn}{\boldsymbol{n}}
-\newcommand{\bfr}{\boldsymbol{r}}
-\newcommand{\bfx}{\boldsymbol{x}}
-\newcommand{\bfy}{\boldsymbol{y}}
 
@@
 \newcommand{\cC}{\mathcal{C}}
-\newcommand{\cD}{\mathcal{D}}
 \newcommand{\cG}{\mathcal{G}}
@@
 \newcommand{\cP}{\mathcal{P}}
-\newcommand{\cQ}{\mathcal{Q}}
 \newcommand{\cR}{\mathcal{R}}
@@
 
-\newcommand{\fp}{\mathfrak{p}}
-
-\newcommand{\CC}{\mathbb{C}}
 \newcommand{\QQ}{\mathbb{Q}}
 \newcommand{\RR}{\mathbb{R}}
-\newcommand{\TT}{\mathbb{T}}
 \newcommand{\ZZ}{\mathbb{Z}}
 
-\newcommand{\ol}[1]{{\overline{#1}}}
-\newcommand{\vv}[1]{{{}^\vee \! #1}}
-
-\newcommand{\Aut}{\operatorname{Aut}}
-\newcommand{\Col}{\operatorname{Col}}
-\newcommand{\diag}{\operatorname{diag}}
-\newcommand{\dpt}{\operatorname{dp}}
-\newcommand{\hgt}{\operatorname{ht}}
-\newcommand{\Id}{\operatorname{Id}}
 \newcommand{\into}{\hookrightarrow}
-\newcommand{\obeta}{{\overline{\beta}}}
-\newcommand{\oi}{{\overline{\imath}}}
-\newcommand{\ot}{{\overline{t}}}
-\newcommand{\rsh}{{\operatorname{rsh}}}
-\newcommand{\sh}{{\operatorname{sh}}}
-\newcommand{\WA}{{W\!\!A}}
-\newcommand{\wt}{{\operatorname{wt}}}
 
@@
 
-\title{Dominance Regions for Rank Two Cluster Algebras}
-
-\author{Dylan Rupel}
-\author{Salvatore Stella}
-\address[D. Rupel]{\href{mailto:rupel.dylan@pusd.us}{\textup{\texttt{rupel.dylan@pusd.us}}}, Math Academy, Pasadena Unified School District, Pasadena, CA 91109 USA}
-\address[S.
-Stella]{\href{mailto:salvatore.stella@univaq.it}{\textup{\texttt{salvatore.stella@univaq.it}}}, Dipartimento di Ingegneria e Scienze dell'Informazione e Matematica, Università degli Studi dell'Aquila, IT}
-\thanks{Salvatore Stella was partially supported by the University of Leicester and the University of Rome ``La Sapienza''.}
-
 \begin{document}
 
-\begin{abstract}
-  We study the polygons defining the dominance order on $\bfg$-vectors in cluster algebras of rank 2.
-\end{abstract}
+\title[Dominance Regions for Rank Two Cluster Algebras]{Dominance Regions for Rank Two Cluster Algebras}
+
+%%=============================================================%%
+%% Prefix	-> \pfx{Dr}
+%% GivenName	-> \fnm{Joergen W.}
+%% Particle	-> \spfx{van der} -> surname prefix
+%% FamilyName	-> \sur{Ploeg}
+%% Suffix	-> \sfx{IV}
+%% NatureName	-> \tanm{Poet Laureate} -> Title after name
+%% Degrees	-> \dgr{MSc, PhD}
+%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate} 
+%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
+%%=============================================================%%
+
+\author[1]{\fnm{Dylan} \sur{Rupel}}\email{rupel.dylan@gmail.com}
+
+\author[2]{\fnm{Salvatore} \sur{Stella}}\email{salvatore.stella@univaq.it}
+
+\affil[1]{\orgdiv{Math Academy}, \orgname{Pasadena Unified School District}, \orgaddress{\street{351 S. Hudson Ave.}, \city{Pasadena}, \postcode{91109}, \state{California}, \country{United States}}}
+
+\affil[2]{\orgdiv{Dipartimento di Ingegneria e Scienze dell'Informazione e Matematica}, \orgname{Università degli Studi dell'Aquila}, \orgaddress{\street{Via Vetoio}, \city{L'Aquila}, \postcode{67100}, \state{AQ}, \country{Italy}}}
+
+%%==================================%%
+%% sample for unstructured abstract %%
+%%==================================%%
+
+\abstract{We study the polygons defining the dominance order on $\bfg$-vectors in cluster algebras of rank 2.}
+
+%%================================%%
+%% Sample for structured abstract %%
+%%================================%%
+
+% \abstract{\textbf{Purpose:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
+% 
+% \textbf{Methods:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
+% 
+% \textbf{Results:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
+% 
+% \textbf{Conclusion:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}
+
+\keywords{cluster algebra, dominance order, pointed bases}
+
+%%\pacs[JEL Classification]{D8, H51}
+
+\pacs[MSC Classification]{13F60}
+
 \maketitle
+
 \vspace{-1em}
@@
 \vspace{-1em}
-  \section{Introduction}
+
+\section{Introduction}\label{sec1}
+
   Cluster algebras were introduced by Fomin and Zelevinsky as a tool in the study of Lusztig's dual canonical bases.
@@
 
-\bibliographystyle{amsalpha}
-\bibliography{bibliography}
+\bmhead{Acknowledgments}
+
+Acknowledgments are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.
+
+Please refer to Journal-level guidance for any specific requirements.
+
+%%===========================================================================================%%
+%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
+%% system, please include the references within the manuscript file itself. You may do this  %%
+%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
+%% file, and delete the associated \verb+\bibliography+ commands.                            %%
+%%===========================================================================================%%
+
+\bibliography{bibliography}% common bib file
+%% if required, the content of .bbl file can be included here once bbl is generated
+%%\input sn-article.bbl
+
+%% Default %%
+%%\input sn-sample-bib.tex%
 

### 2022-08-03 Annals of Combinatorics/submission.tex
It compiles

@@
 %%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+\RequirePackage{tikz}
 \documentclass[pdflatex,sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
@@
 \usepackage{color}
-\usepackage{tikz}
 \usetikzlibrary{math}
-\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
+%\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}
 %%%%
@@
 
-\author[1]{\fnm{Dylan} \sur{Rupel}}\email{rupel.dylan@gmail.com}
+\author[1]{\fnm{Dylan} \sur{Rupel}}\email{rupel.dylan@pusd.us}
 
@@
 \keywords{cluster algebra, dominance order, pointed bases}
-
-%%\pacs[JEL Classification]{D8, H51}
 

### 2022-08-03 Annals of Combinatorics/submission.tex
Reformatting

@@
   Elements of any pointed basis are parametrized by $\ZZ^2$ thought of as the collection of possible $\bfg$-vectors.
-  Qin introduced a partial order $\preceq$ on $\bfg$-vectors called the \emph{dominance order} and showed that it provides a characterization of pointed bases.
+  Qin introduced a partial order $\preceq$ on $\bfg$-vectors called the \emph{dominance order}, refining the order used in \cite[Proposition 4.3]{CILS15}, and showed that it provides a characterization of pointed bases.
   We restate his results in the generality needed for this paper and using our notation.
@@
         \begin{array}{rcccl}
-          0 & \!\leq\! & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \!\leq\! & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)\!\!;
+          0 & \!\leq\! & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \!\leq\! & \left[-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1\right]_+\!\!;
           \\
-          \min\left(-c\lambda_0,0\right) & \!\leq\! & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \!\leq\! & 0;
+          0 & \!\leq\! & -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \!\leq\! & \left[c\lambda_0\right]_+;
           \\
-          0 & \!\leq\! &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \!\leq\! & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)\!\!;
+          0 & \!\leq\! &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \!\leq\! & \left[\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1\right]_+\!\!;
           \\
-          \min\left(b \lambda_1,0\right) & \!\leq\! & (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \!\leq\! & 0.
+          0 & \!\leq\! & -(\mu_0-\lambda_0) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \!\leq\! & \left[-b \lambda_1\right]_+;
         \end{array}
@@
     }
+    where $[x]_+:=\max(x,0)$.
 
@@
     }
-  \begin{tikzpicture}[scale=.3]
+  \begin{tikzpicture}[scale=.22]
     \begin{scope}[shift={(0,0)}]
@@
       \fill (\x,\y) circle (5pt);
-      \draw (\xmin+1.5,\ymin+1) node{(1.a)};
+      \draw (\xmin+1.5,\ymin+1) node{\small(1.a)};
     \end{scope}
@@
       \draw [thick, fill=white] ({\x+\b * \y},\y) circle (5pt);
-      \draw (\xmin+1.5,\ymin+1) node{(1.b)};
+      \draw (\xmin+1.5,\ymin+1) node{\small(1.b)};
     \end{scope}
@@
       \draw [thick, fill=white] (\x,{\y - \c * \x}) circle (5pt);
-      \draw (\xmin+1.5,\ymin+1) node{(1.c)};
+      \draw (\xmin+1.5,\ymin+1) node{\small(1.c)};
     \end{scope}
@@
       \draw [thick, fill=white] ({\x + \b * \y}, {\y -\c*(\x + \b * \y)})  circle (5pt);
-      \draw (\xmin+1.5,\ymin+1) node{(1.d)};
+      \draw (\xmin+1.5,\ymin+1) node{\small(1.d)};
     \end{scope}
@@
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
-      \draw (\xmin+1.5,\ymin+1) node{(1.e)};
+      \draw (\xmin+1.5,\ymin+1) node{\small(1.e)};
     \end{scope}
@@
       \draw [thick, fill=white] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
-      \draw (\xmin+1.5,\ymin+1) node{(1.f)};
+      \draw (\xmin+1.5,\ymin+1) node{\small(1.f)};
     \end{scope}
@@
       \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt);
-      \draw (\xmin+1.5,\ymin+1) node{(2)};
+      \draw (\xmin+1.5,\ymin+1) node{\small(2)};
     \end{scope}
@@
   \begin{align*}
-    u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
+    0 \le -u_{k+1}^-(\mu_0-\lambda_0)+u_k^-(\mu_1-\lambda_1); &\\
     -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
@@
   \begin{align*}
-    u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
+    0 \le -u_k^-(\mu_0-\lambda_0)+u_{k-1}^-(\mu_1-\lambda_1); &\\
     u_k^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le bu_k^-\lambda_1;\\
@@
   \begin{align}
-    \label{ieq1} 0 & \le -(\mu_0-\lambda_0)-\frac{u_k^+}{u_{k+1}^-}(\mu_1-\lambda_1);\\
-    \label{ieq2} -c\lambda_0 & \le \frac{u_{k-1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
+    \label{ieq1} 0 \le -(\mu_0-\lambda_0)-\frac{u_k^+}{u_{k+1}^-}(\mu_1-\lambda_1); & \\
+    \label{ieq2} -\frac{u_{k-1}^-}{u_k^+}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \le c\lambda_0;\\
     \label{ieq3} -(\mu_0-\lambda_0)-\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1) &\le c\frac{u_{k+1}^+}{u_k^-}\lambda_0+b\lambda_1;
@@
   \begin{align}
-    \label{ieq4} 0 &\le (\mu_0-\lambda_0)+\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1);\\
-    \label{ieq5} b\lambda_1 &\le (\mu_0-\lambda_0)-\frac{u_{k+1}^+}{u_k^-}(\mu_1-\lambda_1);\\
-    \label{ieq6} c\lambda_0+b\frac{u_{k-1}^-}{u_k^+}\lambda_1 &\le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);
+    \label{ieq4} 0 \le (\mu_0-\lambda_0)+\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1); & \\
+    \label{ieq5} -(\mu_0-\lambda_0)+\frac{u_{k+1}^+}{u_k^-}(\mu_1-\lambda_1) &\le -b\lambda_1;\\
+    \label{ieq6} -\frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) &\le -c\lambda_0-b\frac{u_{k-1}^-}{u_k^+}\lambda_1;
   \end{align}
@@
   Thus, following Lemma~\ref{le:limits}, in the limit as $k\to\infty$, we obtain the inequality
-  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
+  \[ -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) \le c\lambda_0 \]
   determining a boundary of $\cP_\lambda$.
   Observe further that the inequalities $\mu_0-\lambda_0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
-  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]
+  \[ 0 \le -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) \le c\lambda_0. \]
 
@@
   \[ 0 \le (\mu_0-\lambda_0)+\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
-  \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le 0;\]
-  \[ c\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2b}b\lambda_1 \le -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).\]
+  \[ 0 \le -(\mu_0-\lambda_0)+\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le -b\lambda_1;\]
+  \[ 0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) \le -c\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2b}b\lambda_1.\]
   These can easily be seen to be equivalent to the remaining inequalities from Theorem~\ref{th:dominance inequalities} and this complete the proof.
@@
           \\
-          -b\lambda'_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)-(\mu_0-\lambda'_0)
+          0 & \leq & -\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) & \leq & b\lambda'_1
           \\
@@
           \\
-          c \lambda'_0 & \leq & (\mu_1-\lambda'_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 b} (\mu_0-\lambda'_0)
+          0 & \leq & (\mu_1-\lambda'_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 b} (\mu_0-\lambda'_0) & \leq & -c \lambda'_0
         \end{array}

### 2022-08-04 Annals of Combinatorics/submission.tex
Authors and abstract

@@
 
-\author[1]{\fnm{Dylan} \sur{Rupel}}\email{rupel.dylan@pusd.us}
-
-\author[2]{\fnm{Salvatore} \sur{Stella}}\email{salvatore.stella@univaq.it}
+\author*[1]{\fnm{Dylan} \sur{Rupel}}\email{rupel.dylan@pusd.us}
+
+\author*[2]{\fnm{Salvatore} \sur{Stella}}\email{salvatore.stella@univaq.it}
 
@@
 
-\abstract{We study the polygons defining the dominance order on $\bfg$-vectors in cluster algebras of rank 2.}
+\abstract{We study the polygons defining the dominance order on $\bfg$-vectors in cluster algebras of rank 2.\hfill~}
 

### 2022-08-06 Annals of Combinatorics/submission.tex
Edits to the arXiv version

@@
   \begin{remark}
-    Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coeffiecients $q_{\lambda,\mu}$ are zero.
+    Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coefficients $q_{\lambda,\mu}$ are zero.
     Understanding this phenomenon might be worth further study.
@@
     Using the claim for $\ell>0$ and then the defining recursion twice, $u_{i+\ell+1}^\varepsilon$ can be rewritten for $\ell$ odd as
-    \[
+    \begin{align*}
       u_{\ell+1}^\varepsilon u_{i+1}^{-\varepsilon}-u_\ell^{-\varepsilon} u_i^\varepsilon
-      =u_{\ell+1}^\varepsilon(u_2^{-\varepsilon}u_i^\varepsilon-u_{i-1}^{-\varepsilon}) -u_\ell^{-\varepsilon} u_i^\varepsilon 
-      =(u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
-      =u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
-    \]
+      &=u_{\ell+1}^\varepsilon(u_2^{-\varepsilon}u_i^\varepsilon-u_{i-1}^{-\varepsilon}) -u_\ell^{-\varepsilon} u_i^\varepsilon\\
+      &=(u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}\\
+      &=u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
+    \end{align*}
     and for $\ell$ even as
-    \[
+    \begin{align*}
       u_{\ell+1}^{-\varepsilon} u_{i+1}^\varepsilon-u_\ell^\varepsilon u_i^{-\varepsilon}
-      =u_{\ell+1}^{-\varepsilon}(u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon) -u_\ell^\varepsilon u_i^{-\varepsilon}
-      =(u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon
-      =u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon.
-    \]
+      &=u_{\ell+1}^{-\varepsilon}(u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon) -u_\ell^\varepsilon u_i^{-\varepsilon}\\
+      &=(u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon\\
+      &=u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon.
+    \end{align*}
     This gives the claimed recursion for $\ell+1$.
@@
     For any $i\ne1$, we have
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
+    \[\scalebox{0.95}{$\displaystyle\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}$.}\]
     It follows that
-    \[\lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{\sqrt{c}}{2\sqrt{b}}\cdot\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
+    \begin{align*}
+      \lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+}
+      &=\lim_{i\to\infty} \left( \frac{\sqrt{c}}{2\sqrt{b}}\cdot\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right)\\
+      &=\frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),
+    \end{align*}
     which is equivalent to the desired expression.
     Similarly, for $i\ne0$ we have
-    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
+    \[\scalebox{0.925}{$\displaystyle\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}$,}\]
     so that
-    \[\lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{2\sqrt{c}}{\sqrt{b}}\cdot\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
+    \begin{align*}
+      \lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+}
+      &=\lim_{i\to\infty} \left( \frac{2\sqrt{c}}{\sqrt{b}}\cdot\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)} \right)\\
+      &=\frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),
+    \end{align*}
     which is again equivalent to the desired expression.
@@
       u_{i+1}^{-}u_{i-1}^+
-      =(cu_i^+-u_{i-1}^{-})u_{i-1}^+
-      =cu_i^+ u_{i-1}^+-u_{i-1}^{-} u_{i-1}^+
-      <cu_i^+ u_{i-1}^+-u_i^+ u_{i-2}^{-}
+      &=(cu_i^+-u_{i-1}^{-})u_{i-1}^+
+      =cu_i^+ u_{i-1}^+-u_{i-1}^{-} u_{i-1}^+\\
+      &<cu_i^+ u_{i-1}^+-u_i^+ u_{i-2}^{-}
       =u_i^+(cu_{i-1}^+-u_{i-2}^{-})
@@
       u_{i+1}^{+}u_{i-1}^-
-      =(bu_i^--u_{i-1}^{+})u_{i-1}^-
-      =bu_i^- u_{i-1}^--u_{i-1}^{+} u_{i-1}^-
-      <bu_i^- u_{i-1}^--u_i^- u_{i-2}^{+}
+      &=(bu_i^--u_{i-1}^{+})u_{i-1}^-
+      =bu_i^- u_{i-1}^--u_{i-1}^{+} u_{i-1}^-\\
+      &<bu_i^- u_{i-1}^--u_i^- u_{i-2}^{+}
       =u_i^-(bu_{i-1}^--u_{i-2}^{+})
@@
     \end{cases}
-    \qquad
+  \end{equation}
+  \[
     \phi_{-1}(\lambda)
@@
     \end{cases}
-  \end{equation}
+  \]
   For $k\in\ZZ$ with $|k|>1$, define piecewise-linear maps
@@
     We thus require 
-    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_0=(bc-1)\lambda_0+b\lambda_1 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1= -c\lambda_0-\lambda_1,\]
+    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_0=(bc-1)\lambda_0+b\lambda_1\,\,\,\text{and}\,\,\,\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1= -c\lambda_0-\lambda_1,\]
     or equivalently
@@
       \phi_{2j+2}(\lambda)&=\phi_2\phi_{2j}(\lambda)\\
-      &=\big( (u_3^- u_{2j+1}^+-u_2^+u_{2j}^-)\lambda_0+(u_3^-u_{2j}^+-u_2^+u_{2j-1}^-)\lambda_1,-(u_2^-u_{2j+1}^+-u_1^+u_{2j}^-)\lambda_0-(u_2^-u_{2j}^+-u_1^+u_{2j-1}^-)\lambda_1 \big)\\
+      &=\Big( (u_3^- u_{2j+1}^+-u_2^+u_{2j}^-)\lambda_0+(u_3^-u_{2j}^+-u_2^+u_{2j-1}^-)\lambda_1,\\
+      &\qquad-(u_2^-u_{2j+1}^+-u_1^+u_{2j}^-)\lambda_0-(u_2^-u_{2j}^+-u_1^+u_{2j-1}^-)\lambda_1 \Big)\\
       &=(u_{2j+3}^+\lambda_0+u_{2j+2}^+\lambda_1, -u_{2j+2}^-\lambda_0-u_{2j+1}^-\lambda_1),
@@
     which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
-    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)\mu_0+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    \begin{align*}
+      -u_{2i+1}^-\mu_0-u_{2i}^+\mu_1
+      &=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)\mu_0+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)\mu_1\\
+      &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,
+    \end{align*}
     which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
@@
     Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
-    \[-u_{2i+1}^-\mu_0+u_{2i+2}^+\mu_1=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
+    \begin{align*}
+      -u_{2i+1}^-\mu_0+u_{2i+2}^+\mu_1
+      &=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})\mu_1\\
+      &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,
+    \end{align*}
     which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
@@
   This basis consists of the cluster monomials of $\cA(2,2)$ together with the elements
-  \[
+  \begin{align*}
     x_{(n,-n)}^{ge}
-    :=
-		\Big(x_0 x_1^{-1} + x_0^{-1}x_1^{-1} + x_0^{-1}x_1\Big)^n
-		=
+    &:=
+    \Big(x_0 x_1^{-1} + x_0^{-1}x_1^{-1} + x_0^{-1}x_1\Big)^n\\
+    &=
     x_0^{-n} x_1^{-n}
@@
     \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}.
-  \]
+  \end{align*}
 
@@
 
-Acknowledgments are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.
-
-Please refer to Journal-level guidance for any specific requirements.
+Salvatore Stella was partially supported by the University of Leicester and the University of Rome ``La Sapienza''.
 

### 2022-08-06 dominance_regions.tex
Edits to the arXiv version

@@
     }
-
-  \vspace{-1.05em}
+    where $[x]_+:=\max(x,0)$.
+
   \end{theorem}
   \begin{remark}
-    Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coeffiecients $q_{\lambda,\mu}$ are zero.
+    Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coefficients $q_{\lambda,\mu}$ are zero.
     Understanding this phenomenon might be worth further study.

### 2022-11-03 Annals of Combinatorics/submission.tex
Added delcarations
Fixed theorem in submitted version

@@
   We therefore assume that $bc\ge4$.
-  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
+  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
+  Lattice points outside of $\cI$ are precisely the $\bfg$-vectors of cluster monomials in $\cA(b,c)$.
+
+  We give an explicit description of the dominance relation among $\bfg$-vectors.
   Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance region} $\cP_\lambda$ (cf.
@@
     \label{th:dominance inequalities}
-    The dominance region $\cP_\lambda$ of the $\bfg$-vector $\lambda=(\lambda_0,\lambda_1)$ is the polygon consisting of those $\mu=(\mu_0,\mu_1)\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
+    If $\lambda$ lies outside of $\cI$, then the dominance region $\cP_\lambda$ is the point $\lambda$.
+    Otherwise the dominance region $\cP_\lambda$ of the $\bfg$-vector $\lambda=(\lambda_0,\lambda_1)$ is the polygon consisting of those $\mu=(\mu_0,\mu_1)\in\RR^2$ satisfying the following inequalities:
     {
@@
         \begin{array}{rcccl}
-          0 & \!\leq\! & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \!\leq\! & \left[-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1\right]_+\!\!;
+          0 & \!\leq\! & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \!\leq\! & -c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1;
           \\
-          0 & \!\leq\! & -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \!\leq\! & \left[c\lambda_0\right]_+;
+          0 & \!\leq\! & -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \!\leq\! & c\lambda_0;
           \\
-          0 & \!\leq\! &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \!\leq\! & \left[\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1\right]_+\!\!;
+          0 & \!\leq\! &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \!\leq\! & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1;
           \\
-          0 & \!\leq\! & -(\mu_0-\lambda_0) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \!\leq\! & \left[-b \lambda_1\right]_+;
+          0 & \!\leq\! & -(\mu_0-\lambda_0) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \!\leq\! & -b \lambda_1.
         \end{array}
@@
     }
-    where $[x]_+:=\max(x,0)$.
-
   \vspace{-1.05em}
@@
 
-  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
-  Lattice points outside of $\cI$ are precisely the $\bfg$-vectors of cluster monomials in $\cA(b,c)$.
   \begin{corollary}
@@
   Here we explicitly compute the dominance regions $\cP_\lambda$.
-  When $\lambda$ is not imaginary, the dominance region is particularly simple.
+  The following Lemma proves Theorem~\ref{th:dominance inequalities} for~$\lambda\not\in\cI$.
   \begin{lemma}
@@
   \end{proof}
-  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
-  \begin{itemize}
-    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth pairs of inequalities become equations for lines which intersect at $\lambda$;
-    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second pairs of inequalities become equations for lines which intersect at $\lambda$;
-    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth pairs of inequalities become equations for lines which intersect at $\lambda$.
-  \end{itemize}
-  Since $\lambda$ satisfies all the inequalities, these observations prove Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.
 

### 2022-11-04 dominance_regions.tex

@@
     }
-    where $[x]_+:=\max(x,0)$.
-
   \end{theorem}
@@
     }
-  \begin{tikzpicture}[scale=.3]
+  \begin{tikzpicture}[scale=.45]
     %negatives k=-3

### 2023-01-04 Annals_of_Combinatorics/submission.tex
1/2 Review

--- 2022-11-03 Annals of Combinatorics/submission.tex
@@
 \RequirePackage{tikz}
+\usetikzlibrary{plotmarks}
 \documentclass[pdflatex,sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
@@
 
-\vspace{-1em}
+\vspace{-4.1902em}
 \begin{figure}[h!]
@@
   \end{tikzpicture}
+  \label{fig:1}
+  \begin{caption}
+    {
+    The dominance region $\cP_\lambda$, the opposite dominance region $\cP'_\lambda$, and the maximal support region $\cS_\lambda$ for $\lambda=(4,-3)$ when $b=3$ and $c=2$.
+    Highlighted lattice points in the region bounded by solid black lines and dashed lines represent the maximal support of an element pointed at $\lambda$; the dotted lines indicate which lattice points are in the support of the corresponding greedy basis element.
+    }
+  \end{caption}
 \end{figure}
@@
 when clusters contain a pair of mutable cluster variables.
+  By doing so we shed more light on the conbinatorial structure of such bases.
   In this setting, frozen variables do not carry any additional information so we will work in the coefficient-free case.
@@
   \end{equation}
-  with $\rho_{0,0}=1$.
+  with $\rho_{0,0}=1$ and $\rho_{\alpha_0,\alpha_1}\in\ZZ$.
+  This definition agrees  with the notion of $\bfg$-vector from \cite{FZ07} defined for cluster variables.
   An element of $\cA(b,c)$ is \emph{pointed} if an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$; a basis is pointed if it consists entirely of pointed elements.
@@
         \begin{enumerate}
-          \item If $0\le\lambda_0,\lambda_1$, then $\cS_\lambda$ is just the point $\lambda$.
-          \item If $\lambda_1 < 0$ and $0\le\lambda_0+b\lambda_1$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_0+b\lambda_1,\lambda_1)$.
-          \item If $\lambda_0 < 0$ and $0\le\lambda_1$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_0,-c\lambda_0+\lambda_1)$.
-          \item If $\lambda_0,\lambda_1 < 0$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and ${(\lambda_0,-c\lambda_0+\lambda_1)}$.
-          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $-c\lambda_0-(bc-1)\lambda_1\le 0$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\big((bc+1)\lambda_0-b^2c\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$.
-          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $0 < -c\lambda_0-(bc-1)\lambda_1$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $(0,0)$.
-Here the point $(0,0)$ and its adjacent open segments are excluded from $\cS_\lambda$.
+          \item If $0\le\lambda_0,\lambda_1$, then $\cS_\lambda$ is just the point $\lambda=\lambda'$.
+          \item If $\lambda_1 < 0$ and $0\le\lambda_0+b\lambda_1$, then $\cS_\lambda$ is the segment joining $\lambda$ and $\lambda'=(\lambda_0+b\lambda_1,\lambda_1)$.
+          \item If $\lambda_0 < 0$ and $0\le\lambda_1$, then $\cS_\lambda$ is the segment joining $\lambda$ and $\lambda'=(\lambda_0,-c\lambda_0+\lambda_1)$.
+          \item If $\lambda_0,\lambda_1 < 0$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\lambda'=\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and ${(\lambda_0,-c\lambda_0+\lambda_1)}$.
+          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $-c\lambda_0-(bc-1)\lambda_1\le 0$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\lambda'=\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\big((bc+1)\lambda_0-b^2c\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$.
+          \item If $\lambda_0 > 0$, $\lambda_0+b\lambda_1 < 0$, and $0 < -c\lambda_0-(bc-1)\lambda_1$, then $\cS_\lambda$ has  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\lambda'=\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $(0,0)$.
+Here the point $(0,0)$ and its adjacent open segments are excluded from $\cS_\lambda$ while both $\lambda$ and $\lambda'$ are included.
         \end{enumerate}
-      \item If $\lambda$ lies inside of $\cI$, then the support of $x_\lambda$ is contained in $\cS_\lambda$ with  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
+      \item If $\lambda$ lies inside of $\cI$, then the support of $x_\lambda$ is contained in $\cS_\lambda$ with  vertices $\lambda$, $(\lambda_0+b\lambda_1,\lambda_1)$, $\lambda'=\big(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
+This last point and its adjacent open segments are excluded from $\cS_\lambda$ while both $\lambda$ and $\lambda'$ are included.
+
         Moreover, there is an element pointed at $\lambda$ whose support is precisely the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cS_\lambda$.
@@
       \tikzmath{ \t=3; \r=1; \q=1; \xx = \r; \yy=\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x,\y) circle (5pt);
+      \draw [thick, fill=black] (\x , \y)  circle (5pt);
       \draw (\xmin+1.5,\ymin+1) node{\small(1.a)};
@@
       \tikzmath{ \t=5; \r=2; \q=1; \xx = \r + \b*\q; \yy=-\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x, \y) circle (5pt);
+      \draw [thick, fill=black] (\x , \y)  circle (5pt);
       \draw [thick, join=round] (\x, \y) -- ({\x+\b * \y},\y);
@@
       \tikzmath{ \t=3; \r=1; \q=1; \xx=-\r; \yy=\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x, \y) circle (5pt);
+      \draw [thick, fill=black] (\x , \y)  circle (5pt);
       \draw [thick, join=round] (\x, \y) -- (\x,{\y - \c * \x});
@@
       \tikzmath{ \t=1; \r=1; \q=1; \xx=-\r; \yy=-\q; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x, \y) circle (5pt);
+      \draw [thick, fill=black] (\x , \y)  circle (5pt);
       \draw [thick, join=round] (\x, \y) -- ({\x + \b * \y}, \y) -- ({\x + \b * \y}, {\y -\c*(\x + \b * \y)}) -- (\x, {\y - \c*\x}) -- cycle;
@@
       \tikzmath{ \t=5; \r=1; \q=1; \xx={\r*\b+\q*(\b*\c-1) }; \yy = {-\r -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x,\y) circle (5pt);
+      \draw [thick, fill=black] (\x , \y)  circle (5pt);
       \draw [thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
@@
       \tikzmath{ \t=5; \r=1; \q=2; \xx={2*\r*\b+\q*(\b*\c-1) }; \yy = {-\r*\bcms -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x,\y) circle (5pt);
+      \draw [thick, fill=black] (\x , \y)  circle (5pt);
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);
@@
       \tikzmath{ \t=2; \r=0.3; \q=1; \xx={2*\r*\b }; \yy = {-\r*\bcps -\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }
-      \fill (\x,\y) circle (5pt);
+      \draw [thick, fill=black] (\x , \y)  circle (5pt);
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);
@@
       \tikzmath{ \t=5; \r=1; \q=2; \xx={2*(\r+\q)*\b }; \yy = {-\r*\bcps -\q*\bcms}; \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)};  }
-      \fill (\x , \y)  circle (5pt);
+      \draw [thick, fill=black] (\x , \y)  circle (5pt);
       \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
@@
     \end{scope}
-    \draw (21,-22) node{The maximal supports $\cS_\lambda$ as described in Theorem \ref{th:maximum support}.};
   \end{tikzpicture}
+  \begin{caption}
+    {
+    The maximal supports $\cS_\lambda$ as described in Theorem \ref{th:maximum support} with $\lambda$ marked by a black dot and $\lambda'$ by a white dot.
+    Dashed edges indicate the maximal support of an element pointed at $\lambda$ while dotted edges indicate the support of the corresponding greedy basis element.
+    }
+    \label{fig:2}
+  \end{caption}
 \end{figure}
@@
   \]
-  For $k\in\ZZ$ with $|k|>1$, define piecewise-linear maps
+  For $k\in\ZZ$ with $\lvert k\rvert>1$, define piecewise-linear maps
   \[\phi_k
@@
 
-  In particular, we obtain an opposite dominance region $\cP'_\lambda$ for each $\bfg$-vector $\lambda$.
+  In particular, we get an opposite dominance region $\cP'_\lambda$ for each $\bfg$-vector $\lambda$.
   \begin{lemma}
@@
   The second point can be rewritten as
-  \[\big(\lambda_0 -\frac{bc+\sqrt{bc(bc-4)}}{2c} c\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c} \lambda_1 , 0 \big)\]
+  \[\left(\lambda_0 -\frac{bc+\sqrt{bc(bc-4)}}{2c} c\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2c} \lambda_1 , 0 \right)\]
   but, since $c\lambda_0 < -2\lambda_1$, the first coordinate is greater than $\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1$.
@@
   The second point can be rewritten as
-  \[\big(0, -\frac{bc+\sqrt{bc(bc-4)}}{2b} \lambda'_0-\frac{bc+\sqrt{bc(bc-4)}}{2b} b\lambda'_1+\lambda'_1 \big)\]
+  \[\left(0, -\frac{bc+\sqrt{bc(bc-4)}}{2b} \lambda'_0-\frac{bc+\sqrt{bc(bc-4)}}{2b} b\lambda'_1+\lambda'_1 \right)\]
   but, since $b\lambda'_1\le -2\lambda'_0$, the first coordinate is greater than $\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1$.
@@
   The support region $\cG_\lambda$ of the greedy basis element with $\bfg$-vector $\lambda$ is well-known \cite{CGMMRSW17,LLZ14}.
-  This is indicated by the solid and dotted lines in our figures where dotted lines indicate points that are excluded from the support.
+This is indicated by the solid and dotted lines in Figures \ref{fig:1} and \ref{fig:2}, where dotted lines indicate points that are excluded from the support.
   (The actual support of the greedy basis element consists of the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cG_\lambda$.)
@@
 
+\section*{Declarations}
+
+All authors certify that they have no affiliations with or involvement in any organization or entity with any financial interest or non-financial interest in the subject matter or materials discussed in this manuscript.
+
 %%===========================================================================================%%

### 2023-01-06 Annals_of_Combinatorics/submission.tex
Refereed

@@
   \begin{remark}
-    Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coefficients $q_{\lambda,\mu}$ are zero.
+    Empirical calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coefficients $q_{\lambda,\mu}$ are zero.
     Understanding this phenomenon might be worth further study.
@@
     These unexpected coincidences are one of our reasons for deciding to write down these results.
+    Unfortunately, at the moment, we are unable to explain the reason behind it.
   \end{remark}
@@
     Dashed edges indicate the maximal support of an element pointed at $\lambda$ while dotted edges indicate the support of the corresponding greedy basis element.
+    The imaginary cone $\cI$ is dashed; the shaded cones correspond to the cases in Theorem \ref{th:maximum support}.
     }
@@
   \end{tikzpicture}
+  \begin{caption}
+    {
+      Two examples of the regions in Lemma \ref{le:dominance inequalities}. 
+      Each inequlity is represented by a shaded halfspace, darker regions cosist of points satisfying multiple inequalities.
+    }
+  \end{caption}
 \end{figure}
+\vspace{-2em}
 
@@
   One can easily compute the following correspondence.
+  \vspace{-1em}
   \begin{lemma}
@@
   \end{lemma}
-
+  \vspace{-1em}
   In particular, we get an opposite dominance region $\cP'_\lambda$ for each $\bfg$-vector $\lambda$.
+  \vspace{-1em}
   \begin{lemma}
@@
   \end{lemma}
+  \vspace{-1em}
   \begin{proof}
@@
   (The actual support of the greedy basis element consists of the points of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside $\cG_\lambda$.)
-  For our purposes, it is enough to observe the following closure property for the greedy support region which is evident from the figure in Theorem~\ref{th:maximum support}.
+  For our purposes, it is enough to observe the following closure property for the greedy support region which is evident from Figure \ref{fig:2}.
   \begin{definition}
